### 2018-06-20 parts/00_abstract.tex
Added official LaTeX thesis class file, fixes issue #1

\begin{thesisabstract}
\paragraph{         }This paper is a sample document that serves as a format and content guideline for undergraduate thesis submissions to the Department of Information Systems and Computer Science. In this section, the abstract, the group should be able to give the readers a clear and concise overview of their study. The section should contain the objectives of the thesis, the methods to be used, and when available, the results of the study, the conclusion, and the recommendations for further work, all based on the intended research objectives. A good abstract should be at most around 150-200 words, or half a page. It should also not contain any references, figures, or equations.
\end{thesisabstract}

### 2018-06-20 parts/00_acknowledgements.tex
Added official LaTeX thesis class file, fixes issue #1

\begin{acknowledgments}

    \noindent
    We would like to thank Dr. Ma. Mercedes Rodrigo, Dr. Ma. Regina Estuar, and Dr. Proceso Fernandez, Jr. for initiating the creation of this thesis template for use of undergraduate thesis groups for years to come. We also extend our gratitude to Ms. Jessica Sugay for help invaluable help in automating many of the formatting of this template, especially in the creation of the custom styles, table of contents, list of figures, list of tables, and the bibliography.

    This section, as the name suggests, is the place in your paper where you may acknowledge individuals or groups who, with their help or guidance, made your study feasible and ultimately a reality. Some of these people include your adviser, volunteers for your study, other professors who may have contributed to your study, and if applicable, any group or organization who provided support in any way for your research.

\end{acknowledgments}

### 2018-06-20 parts/01_introduction_00.tex
Added official LaTeX thesis class file, fixes issue #1

\chapter{INTRODUCTION}

In this section of the paper, you want to provide the general background and motivation of your study. This can be done defining some key definitions or ideas that govern your study, presenting your context, and narrowing it down with parameters that shall concretize your study. 
This chapter is divided into four parts: the Context of the Study, the Research Objective/s, the Research Questions, the Scope and Limitations, and finally, the Significance of the Study. Each will be described in greater detail in their respective sections. Appendix A summarizes major points for each of these sections and gives sample guide questions for your reference.

\input{parts/01_introduction_01contextofstudy}
\input{parts/01_introduction_02researchquestions.tex}
\input{parts/01_introduction_03objectives.tex}
\input{parts/01_introduction_05scopeandlimitations}
\input{parts/01_introduction_04significanceofstudy}

### 2018-06-20 parts/01_introduction_01contextofstudy.tex
Added official LaTeX thesis class file, fixes issue #1

\section{Context of Study}

This subsection of the Introduction aims to discuss the fields related to your study. It is meant to benefit your readers, especially for those who have little or no background on the kind of work your study seeks to explore. You may also briefly discuss related work to help situate your reader.
A sample context can be as follows: “The use of agents within ITSs has been the subject of continuing research at the Ateneo de Manila University.  A continuum of research work has been invested particularly in the design and development of emotionally intelligent agents for Aplusix.  Early work in the area developed models of student emotion [2], [7] as well as preliminary designs for an agent [8]. The first three studies were synthesized into a working ECA [1], with an initial capability of detecting and responding to learner affect through the learner’s interaction with Aplusix. (p.2)”

### 2018-06-20 parts/01_introduction_02researchquestions.tex
Added official LaTeX thesis class file, fixes issue #1

\section{Research Questions}

This subsection mainly presents your research objective/s in question form. An ideal research question must be open-ended, meaning that there is no clear answer that may be readily given to it. The recommended format for this section is that you provide a single overall question, followed by a series of sub-questions (enumerate them for better readability) that help you in answering your main question.

\begin{enumerate}
    \item Research questions 1...
    \item Research questions 2...
    \item Research questions 3...
\end{enumerate}

### 2018-06-20 parts/01_introduction_03objectives.tex
Added official LaTeX thesis class file, fixes issue #1

\section{Research Objectives}
With your context established, it is in this section where you will now describe what you intend to achieve by the end of the study. A possible way of presenting this subsection is to first introduce what problem/s you wish to address given the current context, and based on that/these, you present the objectives that would somehow address that/these problem/s. Other common things discussed may include a brief overview of your intended methodology.

\begin{enumerate}
    \item Research objectives 1...
    \item Research objectives 2...
    \item Research objectives 3...
\end{enumerate}

### 2018-06-20 parts/01_introduction_04significanceofstudy.tex
Added official LaTeX thesis class file, fixes issue #1

\section{Significance of the Study}

If the Research Objective answers the ‘what’ of your study, this section aims to answer the ‘why’. Generally, you may address this significance in terms of its significance in the area of Computer Science and the community. However, other questions which you may also use to guide your significance are the following: “Why is your study important?” “What will your study contribute to the field of Computer Science?” “How will your study benefit not only your intended audience, but the general public, especially our country?”

### 2018-06-20 parts/01_introduction_05scopeandlimitations.tex
Added official LaTeX thesis class file, fixes issue #1

\section{Scope and Limitations of the Study}

In order for your study to be realistic, doable, and still produce a concise answer to your research questions within a particular period of time, this section provides you the opportunity to both cross-out extraneous variables, as well as set those aspects that must be controlled in your study. Some common limitation targets include the target audience for the experiment, the software to be used, portability and reusability of the software, the features it will have, and so on.

### 2018-06-20 parts/02_relatedliterature.tex
Added official LaTeX thesis class file, fixes issue #1

\chapter{REVIEW OF RELATED LITERATURE}

Now that you have established what your study is, this section provides you the ability to look into your research area in order to find out what is the state-of-the-art regarding your topic of interest. By the end of this section, you should already have an idea of what has been done in relation to your work, what findings they had about their studies, and how your own study factors into what was observed (e.g. improvements based upon the studies’ recommendations, techniques that can be borrowed, delineating where previous work ends and where your study begins).

This is an equation:
\[
    x = \frac{-b \pm \sqrt{b^2 - 4ac}}{2a}
\]

Although it discusses a variety of literature, it is still important to maintain a general flow within your discussion. Make use of transitions and other literary means to connect the ideas of each discussed article. One way to do this is to first organize your articles into general topics of discussion. You may then introduce the flow of these topics in the first few paragraphs of this section, and use the topic outline you created as your guide in delivering, comparing and contrasting what ideas you may wish to present about the literature. You can also use the themes as your sub headings. Finally, summarize your literature review by briefly going through the key ideas of previous work, identify points for improvement, and state what your study can do to contribute in addressing those points.

Last but not the least, do not forget to put proper citations to the ideas you will present. More often than not, whatever idea you state here came from another source, so ensure that you acknowledge the article/book/other reference you may have lifted it from.
In order to guide you in writing, as well as to summarize the points mentioned above, here are some questions that may help your structure your discussion:

\begin{enumerate}
\item What previous works are closely connected with your own study? Who initiated these studies?
\item What objectives did these studies have? If they presented any research questions, what were these and how similar or different are they from your own set of questions?
Describe the methods used in these studies.
If there are test subjects, what is the general profile of their subjects?
\item What instruments did they use to acquire and measure their data?
\item What were the findings gathered from the studies? 
\item What issues, if any (e.g. flaws or gaps in the methodology), were encountered during the implementation of the study? In what way did the researchers attempt to address these issues? Were they successful in resolving these issues? Why or why not?
\item What conclusions did these studies have? What recommendations did they present, and which of these recommendations may be addressed through your study?
\item What other improvements could be done that was not mentioned in the study? How will your study incorporate these improvements?
\item In what way is your study different or novel given these previous studies? Where do their studies end, and where will yours begin?
\end{enumerate}

Below is a sample entry from a literature review. You may use this as basis for your own work.

\section{Motivation and ECAs}
In applying motivational concepts to ECAs, some previous work includes studies by Rebolledo-Mendez et al. [9] and Graesser et al [4, 5].
Rebolledo-Mendez et al. [9] investigated the effect of a motivational version of Ecolab, an ITS for teaching primary school children the topic of Ecology, particularly about food chains and food webs. In implementing the motivational extension, they modeled three motivational traits identified as key in the learning context. These are effort, confidence, and independence from the tutor [9]. The motivational on-screen character, which they named as Paul, was designed to provide feedback before and after each activity. Each post-activity feedback was based on the motivational model of the learner, and using this, Paul encourages the learner: to exert more effort, to be more independent, or to become more confident [9].

%\begin{figure}[h] 
%    \centering
%    \includegraphics[width=0.6\textwidth,height=0.2\textheight]{figures/Figure_2-1.png}
%    \caption{Expressions of Paul of M-Ecolab [10].}
%    \label{fig:Figure_2-1.png}
%\end{figure}

 The results of the study showed that through modeling motivation and adjusting motivational reaction, the de-motivated, low, and average students were able to significantly increase their post-test scores. It also, however, showed that highly motivated and high ability students had no increase in test scores. The researchers noted that this could be due to the “ceiling effect”. Nevertheless, it was highlighted that the effects on learning by these motivating techniques were different, depending on the students’ ability and motivation. An example would be adjusting spoken feedback considering the learners’ motivational state as an important influence at post-activity time [9].
There were, however, some limitations to the study. One of these was that the results were derived from a very small sample. Another limitation they indicated was that adapting feedback and character’s reactions, in conjunction with a quiz, constitute only a first step in the study of motivating techniques in ITSs; thus, general guidelines could be used in order to improve student motivation [9].
On the other hand, Graesser et al. [4] developed a computer tutor called AutoTutor, which simulated the discourse patterns and pedagogical strategies of a typical human tutor. It was designed for college students in introductory computer literacy courses, who learn the fundamentals of hardware, operating systems, and the Internet [4].

\begin{figure}[!ht] 
    \centering
    \includegraphics[width=0.6\textwidth,height=0.3\textheight]{figures/Figure_2-2.png}
    \caption{The AutoTutor Interface.}
    \label{fig:Figure_2-2.png}
\end{figure}

AutoTutor works by initiating a conversation with the student. It appears as a talking head that acts as a dialogue partner with the learner, who contributes to the conversation via input from the keyboard. One thing notable about the tutor is that it encourages the learner to articulate answers that are lengthy and require deep reasoning – examples of which include answers to why, how, and what-if questions. There is a multi-turn dialogue involved between AutoTutor and the student, encouraging the student to construct the knowledge and discover what he or she has mastered, rather than bombarding the student with the information to master [4].
Results of the study show that this strategy of AutoTutor was able to influence learning and mastery of students. Comparing students who used AutoTutor to those who only reread the topic and to the control group who did not reread, AutoTutor was able to help students answer more questions which were used in an actual computer literacy course, garnering a greater score than the two other groups [4]. 
In terms of the conversational smoothness and pedagogical quality of dialogue, an experiment was done where students were asked to point out which dialogue moves were generated by human tutors and which ones were by AutoTutor. Results show that the students were unable to discriminate the dialogue moves that were computer-generated compared to those from human tutors. In reality, half of the dialogue was by human tutors and the other half by AutoTutor. This proved the ability of AutoTutor to accurately simulate a human tutor [4].
In a related study, Graesser et al. [5] was able to determine that during interactions with the AutoTutor, confusion was a great predictor of post-test scores. The study showed that when the learner is confused the learner experiences cognitive disequilibrium and thinking. It is presumed that the other frequent emotions such as frustration, bored and flow play a more prominent role in other learning environments and population of learners. It is therefore suggested that further research be conducted on these frequent emotions to discover different strategies and dialogues that will promote both learning gains and more engagement for the students [5].

\section {New Sample Subsection}
This is added in between existing subsections.

\section{Sample Subsection}
Blah blah blah blah!

\section{Sample Sample Subsection New}
This is added after the last existing subsection. Updated the TOC, it works.

### 2018-06-20 parts/03_methodology.tex
Added official LaTeX thesis class file, fixes issue #1

\chapter{METHODOLOGY}

After introducing your topic of choice, discussing and relating previous work with your own, and presenting the underlying concepts that your study will be working with, this section will enable you to go into fine detail into how you will go about your study. Essentially, whatever data you need to gather, as well as how you will intend to gather them, should be presented here.
In order to check whether or not your methodology is sound, two main questions should be answered:
\begin{enumerate}
	\item Is your methodology replicable?
	\item Is your methodology realistic and time-bound?
\end{enumerate}

\section{Methodology as Replicable}
A replicable methodology basically means that anyone who reads your methodology and intends to recreate your study to the letter must be able to obtain a similar, if not, exactly the same set of results. It is important, therefore, that you be as specific as you can when describing your methods, such as properly delineating your study’s independent, dependent, and control variables. Much like in the literature review and framework, it is good practice to organize your methodology into subsections for easier readability. Of course, apart from generating data given these variables, included in making the methodology replicable is providing the users an effective and appropriate means to collect data for analysis later on. This assumes, of course, that the data you intend to collect is actually measurable, whether it be quantitative (numerical) or qualitative (descriptive).

\section{Methodology as Realistic and Time-Bound}
On the other hand, a realistic and time-bound methodology takes into consideration the context of the researcher. Although a high-level of competency is expected from a graduating CS major, one must also ensure that the proposed study’s level of difficulty is aligned with what limited resources is available, especially time. In fact, given that the trend is that you will undergo actual implementation only after being able to defend your proposal during the first semester, the study should be accomplishable at the most within only a semester. It is therefore imperative in the methodology, especially in its initial presentation during the defense, that the timetable for the study is thoroughly laid out, with workable time frames and specific dates for deliverables.

\section{Summary and Additional Guide Questions}
The methodology, in summary, is your detailed explanation of how you intend to go about implementing your study.

### 2018-06-20 parts/04_results.tex
Added official LaTeX thesis class file, fixes issue #1

\chapter{RESULTS AND DISCUSSION}
After implementing your methodology and gathering all pertinent data, in this section, you will now present the gathered data to your reader. By the end of this section, your reader should have an idea of what exactlty happened during the experiment. 
A good way to organize your results is to group them is to present them in the same order which your methodology was presented. For instance, if your methodology included the analysis of user logs, the implementation of an application, and the testing of this application, your results should flow in the same way. In addition, more often than not, you will be presenting a large volume of data, so utilize figures and tables whenever appropriate. Table 5.1 below presents one way of how to go about presenting your data. Note the table caption and headers, as mentioned in our framework.

\begin{table}[t]
\centering
\caption {Preliminary Test Result, organized by Problem Type}
\label{tab:acc_lit} 
\begin{tabular}{ c  c  c  c  c  c  c  c  c  c  c }
\hline
Problem	&Average 	&Standard 	&Average 		&Standard		&Dominant\\
Type  &Steps   &Deviation   &Duration   &Deviation   &Affective\\
  &   &(Steps)   &(s)   &(Duration)   &State\\ \hline

A1  &14   &2.30   &23.04   &3.50   &CONF\\
A2  &2   &5.36   &32.10   &2.01   &FLOW\\
A3  &31   &1.01   &28.55   &4.03   &FLOW\\
B1  &24   &4.40   &45.30   &3.30   &BOR\\
B2  &33   &2.12   &20.56   &2.21   &FLOW\\
B3  &36   &1.05   &LOSE   &1.15   &CONF\\
C1  &22   &1.33   &LOSE   &1.40   &FLOW\\
C2  &23   &3.03   &LOSE   &1.30   &FLOW\\
D1  &30   &1.79   &LOSE   &1.45   &FLOW\\
D2  &15   &1.30   &LOSE   &1.05   &FLOW\\ \hline
\end{tabular}
\end{table}

There are, however, some additional notes that must be clarified. First, given that you will be gathering a huge volume of data, you must be able to classify which of these were critical in determining the outcome of your study, and which ones need not be presented. The critical data must be presented in this section, while the minor ones may be placed in the Appendices of your paper, which will be described later in this template.

Another clarification to be noted is that the presentation of results in this section must be objective, or `as-is'. This means that you must describe your results in a way understandable to your reader without putting any form of interpretation. In effect, this section’s intent is to provide answers to ``what happened'' questions, not ``what does it mean'' questions. The interpretation of results is the subject of a later section.

Finally, because this is a presentation of what happened in the past, all tenses used in this section must be in the past form, be it active or passive. This will also be true for the preceeding sections after the study’s implementation, especially when stating the methodology.

### 2018-06-20 parts/05_conclusions.tex
Added official LaTeX thesis class file, fixes issue #1

\chapter{CONCLUSIONS}
Upon presenting your results, the conclusion is where you will now tie up these results with the original intent of the study, as indicated by the research questions given in the Introduction. It is in this section where you will also discuss any difficulties or issues encountered during the study, as well as your recommended method for addressing these problems.

The general way to organize your conclusion is to present each research sub-question as a subsection, and thoroughly answer each of them by interpreting your results with respect to the question. With these answered, you may then tie up all of your findings in each subsection to answer your main research question, providing any needed additional information or explanation. Last on the list would be your unsolved issues and difficulties, presenting them as avenues to motivate continued work on your chosen topic.

### 2018-06-20 parts/08_appendices_a_introductionandsampleguidequestions.tex
Added official LaTeX thesis class file, fixes issue #1

\section{Introduction to the Appendices}

The Appendices is where you are enabled to present any additional or supplementary information relevant to your study, yet do not require highlighting within the actual paper, either because of its trivial nature or volume. These may in the form of figures, tables, or additional text detailing specific aspects about or related to the study.

\section{Sample Questions for Different Studies}
The following table presents three sample studies, as well as the guide questions that may help direct the discussion in each section of the paper. You may use this as another reference in writing your paper.

### 2018-06-20 parts/08_appendices_b_thesisformattingguidelines.tex
Added official LaTeX thesis class file, fixes issue #1

\section{Thesis Formatting Guidelines}

This thesis template in Word document format was created to ensure that you will spend more time generating content for your paper and less time stressing about formatting issues. To ensure, however, that your document is truly formatted according to specifications, here are some formatting guidelines which you may use to evaluate your own paper’s formatting.

\begin{enumerate}
\item There should be NO PAGE NUMBERS on the first page of every chapter/section..
\item Tables must have NO VERTICAL LINES, as well as NO INNER HORIZONTAL LINES after the table headers.
\item Figures and tables are numbered ACCORDING TO CHAPTER NUMBER (e.g. Table 3.1 must be located in Chapter 3, and Figure B.2 is in Appendix B).
\item The sequence of front matter must be as follows:
    \begin{enumerate}
    \item Title Page, in the correct formatting (e.g. Titles must be written in an inverted triangle, in ALL CAPS and boldface)
    \item Abstract
	\item Table of Contents
	\item List of Figures
	\item List of Tables
	\end{enumerate}
\item Upon binding, the front cover must contain the EXACT CONTENT AND FORMAT as that of your thesis’ title page.
\end{enumerate}

### 2018-06-20 thesis.tex
Added official LaTeX thesis class file, fixes issue #1

\documentclass[oneside,12pt]{discsugthesis}

\begin{document}
\ThesisAuthor{John H. Smith}
\ThesisTitle{THIS IS A THESIS TITLE}
\ThesisDegree{Computer Science}
\ThesisDefenseYear{2019}
\DefenseDate{}
\DepartmentHead{The Head}
\SchoolHead{The Head 2}
\FirstThesisAdviser{Ayun}
\FirstPanelMember{}
\SecondPanelMember{}
\ThirdPanelMember{}

\FrontMatter
\ThesisTitlePage
\input{parts/abstract.tex}
\tableofcontents
\listoffigures

\MainMatter
\input{parts/chapter1.tex}

\bibliography{thesis_refs}
\bibliographystyle{acm}
\nocite{*}
\end{document}

### 2018-06-20 parts/00_abstract.tex
Changed the names and did some formatting fixes

@@
 \begin{thesisabstract}
-\paragraph{         }This paper is a sample document that serves as a format and content guideline for undergraduate thesis submissions to the Department of Information Systems and Computer Science.
+    \noindent
+    This paper is a sample document that serves as a format and content guideline for undergraduate thesis submissions to the Department of Information Systems and Computer Science.
 In this section, the abstract, the group should be able to give the readers a clear and concise overview of their study.
 The section should contain the objectives of the thesis, the methods to be used, and when available, the results of the study, the conclusion, and the recommendations for further work, all based on the intended research objectives.
-A good abstract should be at most around 150-200 words, or half a page.
+A good abstract should be at most around 150--200 words, or half a page.
 It should also not contain any references, figures, or equations.

### 2018-06-23 parts/01_introduction_01contextofstudy.tex
test commit

@@
-\section{Context of Study}
+\section{Context of the Study}
 
-This subsection of the Introduction aims to discuss the fields related to your study.
-It is meant to benefit your readers, especially for those who have little or no background on the kind of work your study seeks to explore.
-You may also briefly discuss related work to help situate your reader.
-A sample context can be as follows: “The use of agents within ITSs has been the subject of continuing research at the Ateneo de Manila University.
-A continuum of research work has been invested particularly in the design and development of emotionally intelligent agents for Aplusix.
-Early work in the area developed models of student emotion [2], [7] as well as preliminary designs for an agent [8].
-The first three studies were synthesized into a working ECA [1], with an initial capability of detecting and responding to learner affect through the learner’s interaction with Aplusix.
-(p.2)”
+Data privacy and security is a growing concern in various fields \textbf{[insert fields here]}.
+To meet these needs, cryptography is often employed to secure data.
+Cryptographic encryption schemes allow data to be transmitted over a insecure channel, and thus much research has been done on the development and application of various encryption schemes.
+
+\textbf{[insert examples here]}. \textbf{[insert examples here]}.
+
+However, recently, in addition to the secure transmission of data, there is also interest in the secure modification of data. \textbf{insert examples here}.
+
+To allow for operations on encrypted data while maintaining data secrecy, homomorphic encryption schemes have been developed.
+
+\textbf{[insert brief overview of homomorphic encryption schemes]}.

### 2018-06-23 parts/01_introduction_00.tex
Tentative context and objectives

@@
 
-In this section of the paper, you want to provide the general background and motivation of your study.
-This can be done defining some key definitions or ideas that govern your study, presenting your context, and narrowing it down with parameters that shall concretize your study.
-This chapter is divided into four parts: the Context of the Study, the Research Objective/s, the Research Questions, the Scope and Limitations, and finally, the Significance of the Study.
-Each will be described in greater detail in their respective sections.
-Appendix A summarizes major points for each of these sections and gives sample guide questions for your reference.
-
 \input{parts/01_introduction_01contextofstudy}
+\input{parts/01_introduction_03objectives.tex}
 \input{parts/01_introduction_02researchquestions.tex}
-\input{parts/01_introduction_03objectives.tex}
 \input{parts/01_introduction_05scopeandlimitations}

### 2018-06-23 parts/01_introduction_01contextofstudy.tex
Tentative context and objectives

@@
 
-Data privacy and security is a growing concern in various fields \textbf{[insert fields here]}.
-To meet these needs, cryptography is often employed to secure data.
-Cryptographic encryption schemes allow data to be transmitted over a insecure channel, and thus much research has been done on the development and application of various encryption schemes.
+Digital data privacy and security is a growing concern in various fields, such as  \textbf{[insert fields here]}.
+To meet these needs, various cryptosystems have been developed.
+A cryptosystem is a system which operates on plaintexts, ciphertexts and keys.
+a cryptosystem also has an encryption algorithm, which maps a plaintext to a ciphertext, and a decryption algorithm, which maps a ciphertext to a plaintext, given an appropiate key \cite[p.119]{tilborg_encyclopedia_2005}.
+The encryption and decryption algorithms are chosen such that the plaintext cannot easily be recovered from the ciphertext without knowledge of the key.
+This allows data to be securely transmitted over a insecure channel:  and thus much research has been done on the development and application of various cryptosystems.
 
-\textbf{[insert examples here]}. \textbf{[insert examples here]}.
+One such particular application of cryptography is image encryption. \cite{arul_murugan_survey_2018}
 
-However, recently, in addition to the secure transmission of data, there is also interest in the secure modification of data. \textbf{insert examples here}.
+\textbf{[discuss image encryption briefly, note how main concern is security]}
 
-To allow for operations on encrypted data while maintaining data secrecy, homomorphic encryption schemes have been developed.
+However, research has also considered a type of cryptosystem, homomorphic cryptosystems, where in addition to allowing the secure transmission of data, it is also possible to perform computations with encrypted data.
+\cite{fontaine_survey_2007}.
 

### 2018-06-23 parts/01_introduction_03objectives.tex
Tentative context and objectives

@@
 \section{Research Objectives}
-With your context established, it is in this section where you will now describe what you intend to achieve by the end of the study.
-A possible way of presenting this subsection is to first introduce what problem/s you wish to address given the current context, and based on that/these, you present the objectives that would somehow address that/these problem/s.
-Other common things discussed may include a brief overview of your intended methodology.
-
+Our study aims to provide an objective comparision of various homomorphic cryptosystems currently in the literature, as they would be used in encrypted image manipulation.
+In this study, we wish to
 \begin{enumerate}
-    \item Research objectives 1...
-    \item Research objectives 2...
-    \item Research objectives 3...
+    \item Compare the applicability of known homorphic encryption schemes to common image processsing operations, in other words, determine which schemes permit the most operations;
+		\item Compare the security of common image processsing operations under known homorphic encryption schemes, using established statistical methods in image encryption;
+    \item Compare the efficiency of common image processsing operations under known homorphic encryption schemes;
+    \item Create a plug-in for the Open Source Computer Vision Library (OpenCV) to allow for convenient use of homomorphic encryption schemes.
 \end{enumerate}

### 2018-06-24 parts/01_introduction_01contextofstudy.tex
Added title, context of the study, research objectives.

@@
 
-Digital data privacy and security is a growing concern in various fields, such as  \textbf{[insert fields here]}.
+Digital data privacy and security is a growing concern in various fields, such as  cloud computing \cite{potey_homomorphic_2016}, health information systems \cite{kester_cryptographic_2015}, and video surveillance \cite{upmanyu_efficient_2009}.
 To meet these needs, various cryptosystems have been developed.
@@
 
-One such particular application of cryptography is image encryption. \cite{arul_murugan_survey_2018}
+One such particular application of cryptography is image encryption.
+While cryptosystems used to encrypt digital data in general, such as the Advanced Encryption System (AES) or elliptic curve cryptography, can also be used to encrypt images \cite{jain_image_2016, singh_image_2015} other algorithms created specifically for image encryption have also been developed \cite{murugan_survey_2018}.
 
-\textbf{[discuss image encryption briefly, note how main concern is security]}
-
-However, research has also considered a type of cryptosystem, homomorphic cryptosystems, where in addition to allowing the secure transmission of data, it is also possible to perform computations with encrypted data.
-\cite{fontaine_survey_2007}.
-
-\textbf{[insert brief overview of homomorphic encryption schemes]}.
+However, research has also considered a type of cryptosystem, homomorphic cryptosystems, where in addition to allowing the secure transmission of data, it is also possible to perform computations with encrypted data, the most basic of which being addition and multiplication.
+Numerous homomorphic cryptosystems exist, which allow for data to be manipulated without compromising data privacy \cite{fontaine_survey_2007, sen_homomorphic_2013}.
+In homomorphic image encryption, there is additional interest in being able to perform image manipulation operations on the encrypted data such as image adjustment, filtering, and morphological/feature extraction operations \cite{ziad_cryptoimg:_2016, gonzalez_digital_2008}.

### 2018-06-24 parts/01_introduction_02researchquestions.tex
Added title, context of the study, research objectives.

@@
 
-This subsection mainly presents your research objective/s in question form.
-An ideal research question must be open-ended, meaning that there is no clear answer that may be readily given to it.
-The recommended format for this section is that you provide a single overall question, followed by a series of sub-questions (enumerate them for better readability) that help you in answering your main question.
+In this study, we ask
 

### 2018-06-24 parts/01_introduction_03objectives.tex
Added title, context of the study, research objectives.

--- 2018-06-20 parts/01_introduction_03objectives.tex
@@
 \section{Research Objectives}
-With your context established, it is in this section where you will now describe what you intend to achieve by the end of the study.
-A possible way of presenting this subsection is to first introduce what problem/s you wish to address given the current context, and based on that/these, you present the objectives that would somehow address that/these problem/s.
-Other common things discussed may include a brief overview of your intended methodology.
 
+A paper published in 2009 by Ziad, et.
+al.
+presents \textit{CryptoImg}, a library for the  Open Source Computer Vision Library (OpenCV) which implements various homomorphic encryption and image processing routines using the Paillier homomorphic cryptosystem \cite{ziad_cryptoimg:_2016}.
+While \textit{CryptoImg} demonstrates that various image manipulation operations are possible in a homomorphic system, we believe this study can be extended by considering other known homomorphic encryption schemes, such as an elliptic curve and ElGamal based cryptosystem presented by Li, et.
+al.
+\cite{li_elliptic_2012}, and the fully homomorphic encryption scheme proposed by Smart and Vercauteren \cite{hutchison_fully_2010}.
+Our study aims to provide an objective comparision of various homomorphic cryptosystems currently in the literature, as they would be used in encrypted image manipulation.
+In this study, we wish to
 \begin{enumerate}
-    \item Research objectives 1...
-    \item Research objectives 2...
-    \item Research objectives 3...
+    \item Compare the applicability of known homomorphic encryption schemes to common image processsing operations, in other words, determine which schemes permit more image processing operations;
+		\item Compare the security of common image processsing operations under known homomorphic encryption schemes, using established statistical methods in image encryption;
+    \item Compare the efficiency of common image processsing operations under known homomorphic encryption schemes;
+    \item Create a plug-in for OpenCV to allow for convenient use of these homomorphic encryption schemes.
 \end{enumerate}

### 2018-06-24 parts/01_introduction_03objectives.tex
Contextualized objectives more, added research questions.

@@
 Our study aims to provide an objective comparision of various homomorphic cryptosystems currently in the literature, as they would be used in encrypted image manipulation.
-In this study, we wish to
+Furthermore, one of the main problems in homomorphic encryption is the practicality of homomorphic encryption schemes.
+Homomorphic cryptosystems are known to be slower compared to other cryptosystems \cite{sen_homomorphic_2013}.
+Taking the above into account, in this study, we wish to
 \begin{enumerate}

### 2018-06-24 parts/01_introduction_05scopeandlimitations.tex
Added temporary scope and limitations

@@
 
-In order for your study to be realistic, doable, and still produce a concise answer to your research questions within a particular period of time, this section provides you the opportunity to both cross-out extraneous variables, as well as set those aspects that must be controlled in your study.
-Some common limitation targets include the target audience for the experiment, the software to be used, portability and reusability of the software, the features it will have, and so on.
+Our study will be limited in terms of the cryptosystems to be tested, the image processing operations we will implement, and the statistical tests we will use to
+
+\textbf{insert listing here}
+
+Our library for OpenCV will be implmented in the C++ programming language.
+
+\textbf{insert other limitations here}

### 2018-06-24 parts/01_introduction_03objectives.tex
Completed scope and limitations

@@
 al.
-presents \textit{CryptoImg}, a library for the  Open Source Computer Vision Library (OpenCV) which implements various homomorphic encryption and image processing routines using the Paillier homomorphic cryptosystem \cite{ziad_cryptoimg:_2016}.
+presents \textit{CryptoImg}, a library for the  Open Source Computer Vision Library (OpenCV) \cite{opencv_library} which implements various homomorphic encryption and image processing routines using the Paillier homomorphic cryptosystem \cite{ziad_cryptoimg:_2016}.
 While \textit{CryptoImg} demonstrates that various image manipulation operations are possible in a homomorphic system, we believe this study can be extended by considering other known homomorphic encryption schemes, such as an elliptic curve and ElGamal based cryptosystem presented by Li, et.

### 2018-06-24 parts/01_introduction_04significanceofstudy.tex
Completed scope and limitations

@@
 
-If the Research Objective answers the ‘what’ of your study, this section aims to answer the ‘why’.
-Generally, you may address this significance in terms of its significance in the area of Computer Science and the community.
-However, other questions which you may also use to guide your significance are the following: “Why is your study important?” “What will your study contribute to the field of Computer Science?” “How will your study benefit not only your intended audience, but the general public, especially our country?”
+The results of the study will provide

### 2018-06-24 parts/01_introduction_05scopeandlimitations.tex
Completed scope and limitations

@@
 \section{Scope and Limitations of the Study}
+Our study will be limited in terms of the cryptosystems to be tested, the image processing operations we will implement, and the statistical tests we will use to gauge the security of the cryptosystems.
+Below is a listing of the scope of the study.
 
-Our study will be limited in terms of the cryptosystems to be tested, the image processing operations we will implement, and the statistical tests we will use to
+\subsection{Scope of Testing}
+We will implement and test the following algorithms:
+\begin{enumerate}
+	\item A modified version of the Paillier cryptosystem \cite{} which supports floating-point operations, used in \textit{CryptoImg} \cite{ziad_cryptoimg:_2016}.
+	\item An elliptic curve and ElGamal based cryptosystem for homomorphic encryption presented by Li, et. al. \cite{li_elliptic_2012}.
+	\item A fully homomorphic encryption scheme proposed by Smart and Vercauteren \cite{hutchison_fully_2010}, which is an improvement on the original lattice-based cryptosystem presented by Gentry \cite{gentry_fully_2009}.
+\end{enumerate}
+We will implement and test the following categories of image manipulation operations:
+\begin{enumerate}
+	\item Image adjustment
+	\item Operations based on convolution
+	\item Morphological operations
+\end{enumerate}
+We will adopt the benchmark for evaluating the performance and security of image encryption schemes presented by Ahmed, et.
+al \cite{ahmed_benchmark_2016}.
+The presented benchmark reflects many tests used in other literature \cite{ahmad_efficiency_2012, wu_npcr_2011}.
+\begin{enumerate}
+	\item Tests for preservation of image quality after encryption and decryption.
+	\begin{enumerate}
+		\item Mean Squared Error (MSE)
+		\item Peak Signal to Noise Ratio (PSNR)
+		\item Structural Similarity Index (SSIM)
+		\item Noise tolerance
+	\end{enumerate}
+	\item Tests for cryptographic security
+	\begin{enumerate}
+		\item Information entropy analysis
+		\item Correlation coefficient analysis
+		\item Differential analysis (number of pixel change rate (NPCR), universeral average change intensity (UACI))
+	\end{enumerate}
+\end{enumerate}
+A detailed overview of the above will be provided in the review of related literature.
 
-\textbf{insert listing here}
+Images used for testing will be obtained from a database maintained by Gonzalez, et. al. \cite{gonzalez_image_nodate}. Both greyscale and color images will be used.
 
-Our library for OpenCV will be implmented in the C++ programming language.
-
-\textbf{insert other limitations here}
+\subsection{Scope of Implementation}
+Our library for OpenCV will be implemented in the C++ programming language.

### 2018-06-24 parts/01_introduction_01contextofstudy.tex

@@
 The encryption and decryption algorithms are chosen such that the plaintext cannot easily be recovered from the ciphertext without knowledge of the key.
-This allows data to be securely transmitted over a insecure channel:  and thus much research has been done on the development and application of various cryptosystems.
+This allows data to be securely transmitted over an insecure channel:  and thus much research has been done on the development and application of various cryptosystems.
 
 One such particular application of cryptography is image encryption.
-While cryptosystems used to encrypt digital data in general, such as the Advanced Encryption System (AES) or elliptic curve cryptography, can also be used to encrypt images \cite{jain_image_2016, singh_image_2015} other algorithms created specifically for image encryption have also been developed \cite{murugan_survey_2018}.
+While cryptosystems used to encrypt digital data in general, such as the Advanced Encryption Standard (AES) or elliptic curve cryptography, can also be used to encrypt images \cite{jain_image_2016, singh_image_2015} other algorithms created specifically for image encryption have also been developed \cite{murugan_survey_2018}.
 

### 2018-06-24 parts/01_introduction_02researchquestions.tex

@@
 
-In this study, we ask
+In this study, we ask the following main research question: What is the best method for image data to be encrypted and manipulated for practical applications?
 
+To answer this question, we will consider the following sub-questions in our research:
 \begin{enumerate}
-    \item Research questions 1...
-    \item Research questions 2...
-    \item Research questions 3...
+    \item Which homomorphic image encryption algorithms are the most efficient in terms of time when applying image manipulation operations?
+    \item Which homomorphic image encryption algorithms are the most secure under statistical attacks?
+    \item How can a library for OpenCV be implemented for further use and study of image manipulation operations within a homomorphic cryptosystem?
 \end{enumerate}

### 2018-06-24 parts/01_introduction_05scopeandlimitations.tex

@@
 \begin{enumerate}
-	\item A modified version of the Paillier cryptosystem \cite{} which supports floating-point operations, used in \textit{CryptoImg} \cite{ziad_cryptoimg:_2016}.
+	\item A modified version of the Paillier cryptosystem \cite{stern_public-key_1999} which supports floating-point operations, used in \textit{CryptoImg} \cite{ziad_cryptoimg:_2016}.
 	\item An elliptic curve and ElGamal based cryptosystem for homomorphic encryption presented by Li, et. al. \cite{li_elliptic_2012}.

### 2018-06-24 parts/01_introduction_05scopeandlimitations.tex
did roughly half of methodology

@@
 
-\subsection{Scope of Testing}
 We will implement and test the following algorithms:
@@
 \end{enumerate}
-A detailed overview of the above will be provided in the review of related literature.
+A detailed overview of the above will be provided in the methodology.
+Both greyscale and color images will be used in the study.
 
-Images used for testing will be obtained from a database maintained by Gonzalez, et. al. \cite{gonzalez_image_nodate}. Both greyscale and color images will be used.
+Our library for OpenCV will be implemented in the C++ programming language.
 
-\subsection{Scope of Implementation}
-Our library for OpenCV will be implemented in the C++ programming language.
+The study will only consider the operation of the stated algorithms in a single computer. Client-server models for secure data storage and operation will not be considered.

### 2018-06-24 parts/03_methodology.tex
did roughly half of methodology

@@
 
-After introducing your topic of choice, discussing and relating previous work with your own, and presenting the underlying concepts that your study will be working with, this section will enable you to go into fine detail into how you will go about your study.
-Essentially, whatever data you need to gather, as well as how you will intend to gather them, should be presented here.
-In order to check whether or not your methodology is sound, two main questions should be answered:
+The study consists of two parts: first, the implementation of the three homomorphic encryption schemes and image processing operations under each scheme as an OpenCV library.
+The second part of the study consists of assessing the robustness and security of image operations under each encryption scheme using benchmarks in \cite{ahmed_benchmark_2016}.
+
+\section{Implementation of the OpenCV library}
+
+The current version of the OpenCV library (3.4.1) will be forked from the open-source GitHub repository at https://github.com/opencv \cite{opencv_library}.
+
+Three homomorphic encryption schemes will be implemented, those presented by Ziad, et al.
+\cite{ziad_cryptoimg:_2016}, Li, et al.
+\cite{li_elliptic_2012} and Smart and Vercauteren \cite{hutchison_fully_2010}.
+The encryption and decryption methods will be implemented in C++.
+
+Aside from implementing the homomorphic encryption and decryption algorithms, we will also implement library functions for the following image processing functions, as they are defined in \cite{gonzalez_digital_2008}.
+We let $R(x,y)$ denote the intensity at coordinate $(x,y)$ in the source image, and $S(x,y)$ denote the intensity at coordinate $(x,y)$ in the resulting image.
+We further suppose that the intensity values of pixels are in the range $[0, L-1]$.
+\begin{description}
+	\item[Intensity transformations.] Transformations on the intensities of each of the pixels on an image. The following definitions hold for all $x,y$.
 	\begin{enumerate}
-	\item Is your methodology replicable?
-	\item Is your methodology realistic and time-bound?
+		\item Image negation: $S(x,y) = L - 1 - R(x,y)$.
+		\item Log transformation: $S(x,y) = c\log{1 + R(x,y)}$, $c \geq 0$.
+		\item Power-law transformation: $S(x,y) = c[R(x,y)]^\gamma$, $c > 0, \gamma > 0$.
 	\end{enumerate}
+	\item[Spatial filters.] Filters implemented by performing a convolution between an $M\times N$ source image and an $m\times n$ filter matrix.
+Let $W$ be a filter matrix.
+Then the corresponding spatial filter is given by
+	\begin{equation}
+		S(x,y) = \sum_{s=1}^m{\sum_{t=1}^n{W(s,t)R(x+s,y+t)}}
+	\end{equation}
+	\item [Histogram processing / equalization]
 
-\section{Methodology as Replicable}
-A replicable methodology basically means that anyone who reads your methodology and intends to recreate your study to the letter must be able to obtain a similar, if not, exactly the same set of results.
-It is important, therefore, that you be as specific as you can when describing your methods, such as properly delineating your study’s independent, dependent, and control variables.
-Much like in the literature review and framework, it is good practice to organize your methodology into subsections for easier readability.
-Of course, apart from generating data given these variables, included in making the methodology replicable is providing the users an effective and appropriate means to collect data for analysis later on.
-This assumes, of course, that the data you intend to collect is actually measurable, whether it be quantitative (numerical) or qualitative (descriptive).
+\end{description}
 
-\section{Methodology as Realistic and Time-Bound}
-On the other hand, a realistic and time-bound methodology takes into consideration the context of the researcher.
-Although a high-level of competency is expected from a graduating CS major, one must also ensure that the proposed study’s level of difficulty is aligned with what limited resources is available, especially time.
-In fact, given that the trend is that you will undergo actual implementation only after being able to defend your proposal during the first semester, the study should be accomplishable at the most within only a semester.
-It is therefore imperative in the methodology, especially in its initial presentation during the defense, that the timetable for the study is thoroughly laid out, with workable time frames and specific dates for deliverables.
+\section{Assessment of each homomorphic encryption scheme}
 
-\section{Summary and Additional Guide Questions}
-The methodology, in summary, is your detailed explanation of how you intend to go about implementing your study.
+We will first obtain standard test images from \cite{gonzalez_image_nodate}. Both greyscale and color images will be used.
+
+For each image, we will consider each image operation listed above and generate two images: a plaintext domain transformation (PDT) and an encrypted domain transformation (EDT).
+The PDT will be generated by running the image operation on the
+
+The benchmarks to be used in the study, adopted from \cite{ahmed_benchmark_2016, ahmad_efficiency_2012, wu_npcr_2011} are listed below. We let $X_i$ denote from
+\begin{enumerate}
+	\item Tests for preservation of image quality after encryption and decryption.
+	\begin{enumerate}
+		\item Mean Squared Error (MSE)
+
+		\item Peak Signal to Noise Ratio (PSNR)
+		\item Structural Similarity Index (SSIM)
+		\item Noise tolerance
+	\end{enumerate}
+	\item Tests for cryptographic security
+	\begin{enumerate}
+		\item Information entropy analysis
+		\item Correlation coefficient analysis
+		\item Differential analysis (number of pixel change rate (NPCR), universeral average change intensity (UACI))
+	\end{enumerate}
+\end{enumerate}

### 2018-06-24 parts/02_relatedliterature.tex
Common image operations

@@
 
-Now that you have established what your study is, this section provides you the ability to look into your research area in order to find out what is the state-of-the-art regarding your topic of interest.
-By the end of this section, you should already have an idea of what has been done in relation to your work, what findings they had about their studies, and how your own study factors into what was observed (e.g.
-improvements based upon the studies’ recommendations, techniques that can be borrowed, delineating where previous work ends and where your study begins).
+\section{An Introduction to Cryptography and Cryptosystems}
+% [include mention of metrics by which they are compared]
 
-This is an equation:
-\[
-    x = \frac{-b \pm \sqrt{b^2 - 4ac}}{2a}
-\]
+In cryptography, a cryptosystem consists of an encryption function $\mathcal{E}$, a decryption function $\mathcal{D}$.
 
-Although it discusses a variety of literature, it is still important to maintain a general flow within your discussion.
-Make use of transitions and other literary means to connect the ideas of each discussed article.
-One way to do this is to first organize your articles into general topics of discussion.
-You may then introduce the flow of these topics in the first few paragraphs of this section, and use the topic outline you created as your guide in delivering, comparing and contrasting what ideas you may wish to present about the literature.
-You can also use the themes as your sub headings.
-Finally, summarize your literature review by briefly going through the key ideas of previous work, identify points for improvement, and state what your study can do to contribute in addressing those points.
+A cryptosystem is said to be homomorphic if its encryption and decryption functions are homomorphic.
 
-Last but not the least, do not forget to put proper citations to the ideas you will present.
-More often than not, whatever idea you state here came from another source, so ensure that you acknowledge the article/book/other reference you may have lifted it from.
-In order to guide you in writing, as well as to summarize the points mentioned above, here are some questions that may help your structure your discussion:
+\section{Common Image Operations}
+% skim chapters 3-4 of the book Digital Image Processing
 
-\begin{enumerate}
-\item What previous works are closely connected with your own study? Who initiated these studies?
-\item What objectives did these studies have? If they presented any research questions, what were these and how similar or different are they from your own set of questions?
-Describe the methods used in these studies.
-If there are test subjects, what is the general profile of their subjects?
-\item What instruments did they use to acquire and measure their data?
-\item What were the findings gathered from the studies? 
-\item What issues, if any (e.g.
-flaws or gaps in the methodology), were encountered during the implementation of the study?
-In what way did the researchers attempt to address these issues?
-Were they successful in resolving these issues?
-Why or why not?
-\item What conclusions did these studies have? What recommendations did they present, and which of these recommendations may be addressed through your study?
-\item What other improvements could be done that was not mentioned in the study? How will your study incorporate these improvements?
-\item In what way is your study different or novel given these previous studies? Where do their studies end, and where will yours begin?
-\end{enumerate}
+% we may refer to the classification in the CryptoImg paper
 
-Below is a sample entry from a literature review. You may use this as basis for your own work.
+In image processing, the typical image operations being done are intensity transformations which maps intensity values to another, using spatial filters to do operations such as edge detection and image blurring, and histogram processing and equalization.
 
-\section{Motivation and ECAs}
-In applying motivational concepts to ECAs, some previous work includes studies by Rebolledo-Mendez et al. [9] and Graesser et al [4, 5].
-Rebolledo-Mendez et al.
-[9] investigated the effect of a motivational version of Ecolab, an ITS for teaching primary school children the topic of Ecology, particularly about food chains and food webs.
-In implementing the motivational extension, they modeled three motivational traits identified as key in the learning context.
-These are effort, confidence, and independence from the tutor [9].
-The motivational on-screen character, which they named as Paul, was designed to provide feedback before and after each activity.
-Each post-activity feedback was based on the motivational model of the learner, and using this, Paul encourages the learner: to exert more effort, to be more independent, or to become more confident [9].
+\subsection{Intensity Transformation}
+Intensity transformations are typically point operations, where a certain operation is applied to each single pixel of the image.
+Usually, there is a function $T$ that maps a pixel value $r$ into a new value $r^\prime$, thus this transformation satisfies the relation $r^\prime = T\left(r\right)$.
+Examples of intensity transformations are image negation, log transformation, and power-law transformation.
 
-%\begin{figure}[h] 
-%    \centering
-%    \includegraphics[width=0.6\textwidth,height=0.2\textheight]{figures/Figure_2-1.png}
-%    \caption{Expressions of Paul of M-Ecolab [10].}
-%    \label{fig:Figure_2-1.png}
-%\end{figure}
+Image negation is an example of an intensity transformation, where the resulting image would be similar to a photographic negative \cite{gonzalez_digital_2008}.
+In this case, suppose the intensity levels of an image are within the range $\left[0, L-1\right]$, then image negation can be expressed by
+\begin{equation}
+    T\left(r\right) = L-1-r
+\end{equation}
 
- The results of the study showed that through modeling motivation and adjusting motivational reaction, the de-motivated, low, and average students were able to significantly increase their post-test scores.
-It also, however, showed that highly motivated and high ability students had no increase in test scores.
-The researchers noted that this could be due to the “ceiling effect”.
-Nevertheless, it was highlighted that the effects on learning by these motivating techniques were different, depending on the students’ ability and motivation.
-An example would be adjusting spoken feedback considering the learners’ motivational state as an important influence at post-activity time [9].
-There were, however, some limitations to the study.
-One of these was that the results were derived from a very small sample.
-Another limitation they indicated was that adapting feedback and character’s reactions, in conjunction with a quiz, constitute only a first step in the study of motivating techniques in ITSs; thus, general guidelines could be used in order to improve student motivation [9].
-On the other hand, Graesser et al.
-[4] developed a computer tutor called AutoTutor, which simulated the discourse patterns and pedagogical strategies of a typical human tutor.
-It was designed for college students in introductory computer literacy courses, who learn the fundamentals of hardware, operating systems, and the Internet [4].
+The log transformation is used to enhance dark pixels or increase the dark details of an image by mapping low intensity values to a wider range of values \cite{gonzalez_digital_2008}.
+This has the general form
+\begin{equation}
+    T\left(r\right) = c \log\left(1 + r\right)
+\end{equation}
+where $c$ is a constant and $r \ge 0$.
 
-\begin{figure}[!ht] 
-    \centering
-    \includegraphics[width=0.6\textwidth,height=0.3\textheight]{figures/Figure_2-2.png}
-    \caption{The AutoTutor Interface.}
-    \label{fig:Figure_2-2.png}
-\end{figure}
+The power-law transformation is a family of transformations that have the form
+\begin{equation}
+    T\left(r\right) = c r^{\gamma}
+\end{equation}
+where $c>0$ and $\gamma > 0$.
+This is especially useful since many output devices such as printers and display devices follow the power law, and so correcting the power-law response on these devices in a process called \textit{gamma correction} ensures reproducibility and accuracy of images being displayed \cite{gonzalez_digital_2008}.
 
-AutoTutor works by initiating a conversation with the student.
-It appears as a talking head that acts as a dialogue partner with the learner, who contributes to the conversation via input from the keyboard.
-One thing notable about the tutor is that it encourages the learner to articulate answers that are lengthy and require deep reasoning – examples of which include answers to why, how, and what-if questions.
-There is a multi-turn dialogue involved between AutoTutor and the student, encouraging the student to construct the knowledge and discover what he or she has mastered, rather than bombarding the student with the information to master [4].
-Results of the study show that this strategy of AutoTutor was able to influence learning and mastery of students.
-Comparing students who used AutoTutor to those who only reread the topic and to the control group who did not reread, AutoTutor was able to help students answer more questions which were used in an actual computer literacy course, garnering a greater score than the two other groups [4].
-In terms of the conversational smoothness and pedagogical quality of dialogue, an experiment was done where students were asked to point out which dialogue moves were generated by human tutors and which ones were by AutoTutor.
-Results show that the students were unable to discriminate the dialogue moves that were computer-generated compared to those from human tutors.
-In reality, half of the dialogue was by human tutors and the other half by AutoTutor.
-This proved the ability of AutoTutor to accurately simulate a human tutor [4].
-In a related study, Graesser et al.
-[5] was able to determine that during interactions with the AutoTutor, confusion was a great predictor of post-test scores.
-The study showed that when the learner is confused the learner experiences cognitive disequilibrium and thinking.
-It is presumed that the other frequent emotions such as frustration, bored and flow play a more prominent role in other learning environments and population of learners.
-It is therefore suggested that further research be conducted on these frequent emotions to discover different strategies and dialogues that will promote both learning gains and more engagement for the students [5].
+\subsection{Edge Detection and Spatial Filters}
+Edge detection is used to find and determine the boundaries in an image, commonly used in applications such as image segmentation and feature extraction.
+This works by detecting so-called \textit{edges}, areas that have abrupt changes in intensity.
+Edge detection is usually done by using gradient operators that detect such abrupt changes.
+These operators are commonly known as \textit{spatial filter}, which are usually of $3 \times 3$ size.
+A common example of spatial filters is the Sobel operator, with two matrices (also called as kernels) $g_x$ and $g_y$ representing the horizontal and vertical components respectively.
+\begin{equation}
+    g_x = 
+    \begin{bmatrix}
+        -1 & 0 & 1 \\
+        -2 & 0 & 2 \\
+        -1 & 0 & 1
+    \end{bmatrix}
+    \qquad\text{and}\qquad
+    g_y = 
+    \begin{bmatrix}
+        1 & 2 & 1 \\
+        0 & 0 & 0 \\
+        -1 & -2 & -1
+    \end{bmatrix}
+\end{equation}
 
-\section {New Sample Subsection}
-This is added in between existing subsections.
+To get the resulting image $I^\prime$, a convolution is performed between the original image $I$ of size $M \times N$ and the kernel $k$ of size $m \times n$.
+Now suppose that the pixel value of an image at point $\left(i,j\right)$ is $r_{i,j}$.
+Then, a transformation using spatial filters can be described as follows:
+\begin{align}
+    T\left(r_{i,j}\right) &= \left[k * I\right]\left(\left\lfloor\frac{m}{2}\right\rfloor, \left\lfloor\frac{n}{2}\right\rfloor \right) \\
+                         &= \sum_{u=1}^{m} \sum_{v=1}^{n} \left[k_{i,j} r_{i+u, j+v} \right]
+\end{align}
 
-\section{Sample Subsection}
-Blah blah blah blah!
+Spatial filters are not only used for edge detection, but there are filters that do image blurring (such as Gaussian blur and box blur) and image sharpening.
+% Should I put a table of other kernels too>
 
-\section{Sample Sample Subsection New}
-This is added after the last existing subsection. Updated the TOC, it works.
+\subsection{Histogram Processing and Equalization}
+\textbf{TO-DO}
+
+\section{Related Work and Previous Implementations}
+CryptoImg
+
+example of homomorphic encryption / image manipulation past work
+
+minor limitation: improvement on previous work, but not a direct comparison
+
+major limitation: does not discuss security: are modified images also secure?
+
+HElib

### 2018-06-25 parts/03_methodology.tex
fixed title, fixed formula for log operations in methodology
Added image quality tests to ch3

@@
 Aside from implementing the homomorphic encryption and decryption algorithms, we will also implement library functions for the following image processing functions, as they are defined in \cite{gonzalez_digital_2008}.
+We will also take note of whether or not a candidate operation is impossible to perform under a given cryptosystem.
 We let $R(x,y)$ denote the intensity at coordinate $(x,y)$ in the source image, and $S(x,y)$ denote the intensity at coordinate $(x,y)$ in the resulting image.
@@
 		\item Image negation: $S(x,y) = L - 1 - R(x,y)$.
-		\item Log transformation: $S(x,y) = c\log{1 + R(x,y)}$, $c \geq 0$.
+		\item Log transformation: $S(x,y) = c\log{(1 + R(x,y))}$, $c \geq 0$.
 		\item Power-law transformation: $S(x,y) = c[R(x,y)]^\gamma$, $c > 0, \gamma > 0$.
@@
 Then the corresponding spatial filter is given by
-	\begin{equation}
-		S(x,y) = \sum_{s=1}^m{\sum_{t=1}^n{W(s,t)R(x+s,y+t)}}
-	\end{equation}
+	\begin{align}
+		S(x,y) = \sum_{s=1}^m{\sum_{t=1}^n{W(s,t)R(x+s,y+t)}}.
+	\end{align}
 	\item [Histogram processing / equalization]
@@
 
-For each image, we will consider each image operation listed above and generate two images: a plaintext domain transformation (PDT) and an encrypted domain transformation (EDT).
-The PDT will be generated by running the image operation on the
+For each plaintext image (PT), we will consider each image operation listed above and generate three images: a plaintext domain transformation (PDT), a ciphertext image (CT), and an encrypted domain transformation (EDT).
+The cipherThe PDT will be generated by running the image operation on the original image.
+The CT will be generated by encrypting the image, then applying the operation, and the EDT will be generated by decrypting the CT.
+The four images (PT, PDT, CT, CDT) will then be compared using various benchmarks to evaluate the quality and security of each homomorphic encryption scheme.
 
-The benchmarks to be used in the study, adopted from \cite{ahmed_benchmark_2016, ahmad_efficiency_2012, wu_npcr_2011} are listed below. We let $X_i$ denote from
-\begin{enumerate}
-	\item Tests for preservation of image quality after encryption and decryption.
-	\begin{enumerate}
-		\item Mean Squared Error (MSE)
+The benchmarks to be used in the study, adopted from \cite{ahmed_benchmark_2016, ahmad_efficiency_2012, wu_npcr_2011} are listed below.
+We let $X_i$ denote a value in an image $X$, where $1 \leq i \leq N$.
 
-		\item Peak Signal to Noise Ratio (PSNR)
-		\item Structural Similarity Index (SSIM)
-		\item Noise tolerance
-	\end{enumerate}
-	\item Tests for cryptographic security
-	\begin{enumerate}
-		\item Information entropy analysis
-		\item Correlation coefficient analysis
-		\item Differential analysis (number of pixel change rate (NPCR), universeral average change intensity (UACI))
-	\end{enumerate}
-\end{enumerate}
+We first perform three tests to ascertain the preservation of image quality after encryption and decryption: MSE, PSNR, and SSIM.
+\begin{description}
+	\item [Mean Squared Error (MSE).] The MSE is defined \cite{ahmed_benchmark_2016} as
+	\begin{align}
+		MSE = \frac{1}{N}\sum_{i=1}^{N}{(CDT_i - PDT_i)^2}.
+	\end{align}
+	The MSE provides a measure of how much data is recovered if an image operation is applied on the encrypted image, which is then decrypted.
+Lower values of MSE indicate higher preservation of image quality \cite{ahmed_benchmark_2016, ahmad_efficiency_2012}.
+	\item [Peak Signal to Noise Ratio (PSNR).]
+	According to Ahmed, et al.
+\cite{ahmed_benchmark_2016}, PSNR is ``an estimator for human visual perception of reconstruction quality'' which is based on  It has been used to ascertain image quality in various studies and is a known meetric for image and video quality \cite{upmanyu_efficient_2009, ahmed_benchmark_2016, akramullah_video_2014}.
+Although it may produce results which do not correlate with human visual perception \cite{huynh-thu_accuracy_2012, ahmed_benchmark_2016}, it is a valid indicator of image quality when media containing the same visual content is compared \cite{huynh-thu_accuracy_2012}.
+	PSNR is defined by
+	\begin{align}
+		PSNR = 10\log_{10}{\left( \frac{L^2}{MSE} \right)}
+	\end{align}
+	where $L$ is the maximum pixel intensity value of an image.
+	Despite the known limitations of PSNR, since we are going to compare the effect of each encryption scheme on recovered image quality, given a fixed library of images, it is a valid measure of image quality for the study.
+	\item [Structural Similarity Index (SSIM)]
+	The SSIM for two random variables $X$ and $Y$ is defined \cite{ahmed_benchmark_2016, akramullah_video_2014} as
+	\begin{align}
+		SSIM(X,Y) = \frac{(2\mu_X\mu_Y+c_1)(2\sigma_{XY}+c_2)}{(\mu_X^2+\mu_Y^2+c_1)(\mu_X^2+\mu_Y^2+c_2)}
+	\end{align}
+	where
+	\begin{itemize}
+		\item $\mu_X, \mu_Y$ are the averages of $X$ and $Y$, respectively;
+		\item $\sigma_X, \sigma_Y$ are the variances of $X$ and $Y$, respectively;
+		\item $\sigma_{XY}$ is the covariance of $X$ and $Y$;
+		\item $c_1 = (k_1L)^2, c_2 = (k_2L)^2$ are two variables used to stabilize the measure when $\mu_X^2+\mu_Y^2$ is close to zero \cite{akramullah_video_2014};
+		\item $L$ is the the maximum pixel intensity value of an image;
+		\item $k_1 = 0.01, k_2 = 0.03$ by default, given in \cite{ahmed_benchmark_2016}.
+	\end{itemize}
+	The SSIM is applied to the luminance value of two images to gauge structural similarity between neighboring pixels.
+	For the study, we will compute $SSIM(PDT, CDT)$ for every image operation, under each homomorphic cryptosystem.
+\end{description}
+
+After performing tests to evaluate image quality, we then perform tests for cryptographic security, as given in \cite{ahmed_benchmark_2016}: entropy analysis, correlation coefficient analysis, NPCR and UACI.
+\begin{description}
+	\item [Information entropy analysis]
+	\item [Correlation coefficient analysis]
+	\item [Number of Pixel Change Rate (NPCR)]
+	\item [Universeral Average Change Intensity (UACI)]
+\end{description}
+
+\section{Summary and Timetable}

### 2018-06-25 parts/03_methodology.tex
Added NPCR and UACI

@@
 \begin{description}
-	\item [Mean Squared Error (MSE).] The MSE is defined \cite{ahmed_benchmark_2016} as
+	\item [Mean Squared Error (MSE).] The MSE is defined in \cite{ahmed_benchmark_2016} as
 	\begin{align}
@@
 	According to Ahmed, et al.
-\cite{ahmed_benchmark_2016}, PSNR is ``an estimator for human visual perception of reconstruction quality'' which is based on  It has been used to ascertain image quality in various studies and is a known meetric for image and video quality \cite{upmanyu_efficient_2009, ahmed_benchmark_2016, akramullah_video_2014}.
+\cite{ahmed_benchmark_2016}, PSNR is ``an estimator for human visual perception of reconstruction quality'' which is based on  It has been used to ascertain image quality in various studies and is a known meetric for image and video quality \cite{upmanyu_efficient_2009, jain_image_2016, akramullah_video_2014}.
 Although it may produce results which do not correlate with human visual perception \cite{huynh-thu_accuracy_2012, ahmed_benchmark_2016}, it is a valid indicator of image quality when media containing the same visual content is compared \cite{huynh-thu_accuracy_2012}.
@@
 	Despite the known limitations of PSNR, since we are going to compare the effect of each encryption scheme on recovered image quality, given a fixed library of images, it is a valid measure of image quality for the study.
+A higher PSNR indicates higher image quality preservation.
 	\item [Structural Similarity Index (SSIM)]
-	The SSIM for two random variables $X$ and $Y$ is defined \cite{ahmed_benchmark_2016, akramullah_video_2014} as
+	The SSIM for two random variables $X$ and $Y$ is defined in \cite{ahmed_benchmark_2016, akramullah_video_2014} as
 	\begin{align}
@@
 	For the study, we will compute $SSIM(PDT, CDT)$ for every image operation, under each homomorphic cryptosystem.
+Higher values of SSIM indicate higher structural similarity, and an SSIM of 1 indicates that the two images are identical\cite{ahmed_benchmark_2016}.
 \end{description}
 
-After performing tests to evaluate image quality, we then perform tests for cryptographic security, as given in \cite{ahmed_benchmark_2016}: entropy analysis, correlation coefficient analysis, NPCR and UACI.
+After performing tests to evaluate image quality, we then perform tests for cryptographic security, as enumerated in \cite{ahmed_benchmark_2016}: entropy analysis, correlation coefficient analysis, NPCR and UACI.
 \begin{description}
@@
 	\item [Correlation coefficient analysis]
-	\item [Number of Pixel Change Rate (NPCR)]
-	\item [Universeral Average Change Intensity (UACI)]
+	\item [NPCR and UACI]
+		The Number of Pixel Change Rate (NPCR) measures the number of pixels which are changed between the a plaintext and a ciphertext to quantify the amount of dispersion which occurs during encryption.
+
+		On the other hand, the Universal Average Change Intensity (UACI) measures the average difference in pixel intensity between two images.
+
+		The NPCR and UACI between two images $X$ and $Y$, each containing $N$ pixels indexed from $1$ to $N$ is defined in \cite{wu_npcr_2011} as
+		\begin{align}
+			NPCR(X,Y) &= \frac{1}{N}\sum_{i = 1}^{N}{D(X_i,Y_i)} \times 100\%\\
+			UACI(X,Y) &= \frac{1}{L_{max} \times N} \sum_{i = 1}^{N}{ |L(X_i) - L(Y_i)| } \times 100\%
+		\end{align}
+		where
+		\begin{itemize}
+			\item $X_i$ and $Y_i$ are the $i$th pixels of $X$ and $Y$, respectively;
+			\item $D$ is a difference function between pixels $A$ and $B$ defined by
+			\begin{align}
+				D(A,B) =
+				\begin{cases}
+					0 &  \text{if $A = B$},\\
+					1 &  \text{if $A \neq B$};
+				\end{cases}
+			\end{align}
+		\item $L_{max}$ is the maximum intensity of a pixel;
+		\item $L(X_i)$ and $L(Y_i)$ are the intensities of pixels $X_i$ and $Y_i$, respectively.
+		\end{itemize}
+		We will calculate $NPCR(PDT,CDT)$ and $UACI(PDT,CDT)$  for every for every image operation, under each homomorphic cryptosystem.
+A high NPCR and UACI are desired to ensure high dispersion and security against differential attacks \cite{ahmed_benchmark_2016}.
+Critical values for NPCR and UACI for given image sizes and bit depths are given in  \cite{wu_npcr_2011}.
 \end{description}

### 2018-06-25 parts/03_methodology.tex
Added information entropy analysis. Fixed BibTeX entries for the encyclopedia.

@@
 
+\subsection{Tests for the preservation of image quality}
 The benchmarks to be used in the study, adopted from \cite{ahmed_benchmark_2016, ahmad_efficiency_2012, wu_npcr_2011} are listed below.
 We let $X_i$ denote a value in an image $X$, where $1 \leq i \leq N$.
-
 We first perform three tests to ascertain the preservation of image quality after encryption and decryption: MSE, PSNR, and SSIM.
@@
 A higher PSNR indicates higher image quality preservation.
-	\item [Structural Similarity Index (SSIM)]
+	\item [Structural Similarity Index (SSIM).]
 	The SSIM for two random variables $X$ and $Y$ is defined in \cite{ahmed_benchmark_2016, akramullah_video_2014} as
@@
 
+\subsection{Tests for cryptographic security}
 After performing tests to evaluate image quality, we then perform tests for cryptographic security, as enumerated in \cite{ahmed_benchmark_2016}: entropy analysis, correlation coefficient analysis, NPCR and UACI.
 \begin{description}
-	\item [Information entropy analysis]
-	\item [Correlation coefficient analysis]
-	\item [NPCR and UACI]
+	\item [Information entropy analysis.] In information theory, the entropy function $H(X)$ is defined in \cite{bauer_information_2005} as
+	\begin{align}
+		H(X) = - \sum_{a:p_X(a)>0}{p_X(a)\log_2{p_X(a)}}
+	\end{align}
+	where $p_X(a)$ denotes the probability that the random variable $X$ takes on the value $a$.
+	In the analysis of image encryption, $H(X)$ is computed for the values of the ciphertext pixels.
+To ensure security against entropy attacks, $H(X)$ must be as close as possible to $\log_2{N}$, where $N$ is the number of possible pixel values \cite{ahmed_benchmark_2016}.
+For example, when each pixel in an encrypted image can take on $256$ different values, the ideal entropy value is $8$.
+	\item [Correlation coefficient analysis.]
+	\item [NPCR and UACI.]
 		The Number of Pixel Change Rate (NPCR) measures the number of pixels which are changed between the a plaintext and a ciphertext to quantify the amount of dispersion which occurs during encryption.
@@
 
-\section{Summary and Timetable}
+\section{Summary and timetable}

### 2018-06-25 parts/03_methodology.tex
Fixed ch3 headings

@@
 
-\section{Implementation of the OpenCV library}
+\section{Implementation of the OpenCV Library}
 
@@
 
-\section{Assessment of each homomorphic encryption scheme}
+\section{Assessment of Homomorphic Encryption Schemes}
 
@@
 
-\subsection{Tests for the preservation of image quality}
+\subsection{Evaluating Image Quality}
 The benchmarks to be used in the study, adopted from \cite{ahmed_benchmark_2016, ahmad_efficiency_2012, wu_npcr_2011} are listed below.
@@
 
-\subsection{Tests for cryptographic security}
+\subsection{Evaluating Cryptographic Security}
 After performing tests to evaluate image quality, we then perform tests for cryptographic security, as enumerated in \cite{ahmed_benchmark_2016}: entropy analysis, correlation coefficient analysis, NPCR and UACI.
@@
 
-\section{Summary and timetable}
+\section{Summary and Timetable}

### 2018-06-25 parts/03_methodology.tex
Summarized methods, modified research questions.

@@
 
+Lab computers in Faura Hall, Ateneo de Manila University will be used to perform the computations, and processing time will be tracked using C++ timer functions.
+The processing time for all cases will be recorded.
+
 \subsection{Evaluating Image Quality}
@@
 \subsection{Evaluating Cryptographic Security}
-After performing tests to evaluate image quality, we then perform tests for cryptographic security, as enumerated in \cite{ahmed_benchmark_2016}: entropy analysis, correlation coefficient analysis, NPCR and UACI.
+After performing tests to evaluate image quality, we then perform tests for cryptographic security, as enumerated in \cite{ahmed_benchmark_2016}: entropy analysis, correlation coefficient analysis (CC), NPCR and UACI.
 \begin{description}
@@
 To ensure security against entropy attacks, $H(X)$ must be as close as possible to $\log_2{N}$, where $N$ is the number of possible pixel values \cite{ahmed_benchmark_2016}.
-For example, when each pixel in an encrypted image can take on $256$ different values, the ideal entropy value is $8$.
-	\item [Correlation coefficient analysis.]
+
+	We will compute $H(CDT)$ for every image operation, under each homomorphic cryptosystem, and compare the effects of each image operation on the entropy of the encrypted image.
+Ideally, performing image operations on encrypted images should still maintain a high level of entropy.
+	\item [Correlation coefficient analysis (CC).]
+		Images generally have a high degree of similarity between adjacent pixels. This correlation must be hidden in the encrypted image, even after performing image operations.
+		The correlation coefficient of an image can be computed between adjacent pixels either vertically, horizontal, or diagonally, and is defined in \cite{ahmed_benchmark_2016} by:
+		\begin{align}
+			CC(X,Y) = \frac{\sigma_{X,Y}}{\sqrt{\sigma_X}\times\sqrt{\sigma_Y}}
+		\end{align}
+		where
+		\begin{itemize}
+			\item $\sigma_X, \sigma_Y$ are the variances of $X$ and $Y$, respectively;
+			\item $\sigma_{XY}$ is the covariance of $X$ and $Y$.
+		\end{itemize}
+
+		For every $CDT$ image, we will compute for the correlation coefficient (for vertical, horizontal and diagonal correlation) for every image operation, under each homomorphic cryptosystem.
 	\item [NPCR and UACI.]
@@
 		\end{itemize}
-		We will calculate $NPCR(PDT,CDT)$ and $UACI(PDT,CDT)$  for every for every image operation, under each homomorphic cryptosystem.
+		We will calculate $NPCR(PDT,CDT)$ and $UACI(PDT,CDT)$  for every image operation, under each homomorphic cryptosystem.
 A high NPCR and UACI are desired to ensure high dispersion and security against differential attacks \cite{ahmed_benchmark_2016}.
@@
 
-\section{Summary and Timetable}
+\section{Summary}
+
+We now recap the research questions and the corresponding methodology.
+\begin{itemize}
+	\item \textbf{Applicablity of homomorphic encryption algorithms for the use of image processing operations on encrypted data?} This will be addressed by the implementation of OpenCV library, and the evaluation of image quality (MSE, PSNR, SSIM).
+	\item \textbf{Time efficiency in applying image manipulation operations.} This will be addressed by the implementation of OpenCV library, and the comparison of recorded processing time for image processing operations.
+	\item \textbf{Security under differential and entropy attacks.}
+	This will be addressed by the evaluation of security benchmarks for image encryption schemes (entropy analysis, correlation coefficient analysis, NPCR, UACI).
+\end{itemize}

### 2018-06-25 parts/01_introduction_03objectives.tex
Finished ch1

@@
     \item Compare the applicability of known homomorphic encryption schemes to common image processsing operations, in other words, determine which schemes permit more image processing operations;
-		\item Compare the security of common image processsing operations under known homomorphic encryption schemes, using established statistical methods in image encryption;
+		\item Compare the security of common image processing operations under known homomorphic encryption schemes, using established statistical methods in image encryption;
     \item Compare the efficiency of common image processsing operations under known homomorphic encryption schemes;
-    \item Create a plug-in for OpenCV to allow for convenient use of these homomorphic encryption schemes.
+    \item Create a library for OpenCV to allow for convenient use and comparison of these homomorphic encryption schemes.
 \end{enumerate}

### 2018-06-25 parts/02_relatedliterature.tex
Expanded section 2.1

@@
 
-In cryptography, a cryptosystem consists of an encryption function $\mathcal{E}$, a decryption function $\mathcal{D}$.
+In cryptography, a cryptosystem consists of an encryption function $\mathcal{E}$ and a decryption function $\mathcal{D}$, along with the plaintext space $\mathcal{P}$, ciphertext space $\mathcal{C}$ and the key space $\mathcal{K}$~\cite{tilborg_encyclopedia_2005}.
+A \textit{plaintext} is text that can be easily understood by everybody.
+On the other hand, a \textit{ciphertext} is a result from encrypting the plaintext using an encryption key.
+The plaintext space consists of all the possible plaintexts.
+
+There are two kinds of cryptosystems, namely: \textit{symmetric} and \textit{asymmetric}.
+In symmetric encryption, the key is used for both encryption and decryption.
+On the other hand, asymmetric encryption uses separate keys for encryption and decryption.
+The encryption key (also called \textit{public key}) is shared to everybody, while the decryption key (also called \textit{private key}) is kept secret.
+Because of this, there is no need to agree upon some secure key sharing protocols.
+Usually, the security of asymmetric cryptosystems relies on the intractability of certain computational problems, like the RSA depends on the difficulty of integer factorization, while ElGamal depends on the difficulty of the discrete logarithmic problem.
 
@@
 
-In image processing, the typical image operations being done are intensity transformations which maps intensity values to another, using spatial filters to do operations such as edge detection and image blurring, and histogram processing and equalization.
+In image processing, the typical image operations being done are intensity transformations which maps intensity values to another, and the use of spatial filters to do operations such as edge detection and image blurring.
 
@@
 
-Image negation is an example of an intensity transformation, where the resulting image would be similar to a photographic negative \cite{gonzalez_digital_2008}.
+Image negation is an example of an intensity transformation, where the resulting image would be similar to a photographic negative~\cite{gonzalez_digital_2008}.
 In this case, suppose the intensity levels of an image are within the range $\left[0, L-1\right]$, then image negation can be expressed by
@@
 
-The log transformation is used to enhance dark pixels or increase the dark details of an image by mapping low intensity values to a wider range of values \cite{gonzalez_digital_2008}.
+The log transformation is used to enhance dark pixels or increase the dark details of an image by mapping low intensity values to a wider range of values~\cite{gonzalez_digital_2008}.
 This has the general form
@@
 where $c>0$ and $\gamma > 0$.
-This is especially useful since many output devices such as printers and display devices follow the power law, and so correcting the power-law response on these devices in a process called \textit{gamma correction} ensures reproducibility and accuracy of images being displayed \cite{gonzalez_digital_2008}.
+This is especially useful since many output devices such as printers and display devices follow the power law, and so correcting the power-law response on these devices in a process called \textit{gamma correction} ensures reproducibility and accuracy of images being displayed~\cite{gonzalez_digital_2008}.
 
@@
 Spatial filters are not only used for edge detection, but there are filters that do image blurring (such as Gaussian blur and box blur) and image sharpening.
-% Should I put a table of other kernels too>
-
-\subsection{Histogram Processing and Equalization}
-\textbf{TO-DO}
+% Should I put a table of other kernels too?
 
 \section{Related Work and Previous Implementations}
+There has been work done regarding the implementation of 
 CryptoImg
@@
 HElib
+
+\section{Summary}

### 2018-06-25 parts/02_relatedliterature.tex
Added homomorphic encryption in 2.1

@@
 In symmetric encryption, the key is used for both encryption and decryption.
-On the other hand, asymmetric encryption uses separate keys for encryption and decryption.
-The encryption key (also called \textit{public key}) is shared to everybody, while the decryption key (also called \textit{private key}) is kept secret.
+On the other hand, asymmetric cryptosystems use separate keys for encryption and decryption.
+The encryption key (also called the \textit{public key}) is shared to everybody, while the decryption key (also called the \textit{private key}) is kept secret.
 Because of this, there is no need to agree upon some secure key sharing protocols.
@@
 
-A cryptosystem is said to be homomorphic if its encryption and decryption functions are homomorphic.
+A cryptosystem is said to be homomorphic if its encryption function is homomorphic, that is, if it satisfies the relation
+\begin{equation}
+    \mathcal{E}\left(p_1 \otimes p_2\right) = \mathcal{E}\left(p_1\right) \oplus \mathcal{E}\left(p_2\right)
+\end{equation}
+where $\otimes$ and $\oplus$ are operations in $\mathcal{P}$ and $\mathcal{C}$ respectively \cite{fontaine_survey_2007}.
 

### 2018-06-25 parts/01_introduction_01contextofstudy.tex

@@
 A cryptosystem is a system which operates on plaintexts, ciphertexts and keys.
-a cryptosystem also has an encryption algorithm, which maps a plaintext to a ciphertext, and a decryption algorithm, which maps a ciphertext to a plaintext, given an appropiate key \cite[p.119]{tilborg_encyclopedia_2005}.
+a cryptosystem also has an encryption algorithm, which maps a plaintext to a ciphertext, and a decryption algorithm, which maps a ciphertext to a plaintext, given an appropiate key \cite{bauer_cryptosystem_2005}.
 The encryption and decryption algorithms are chosen such that the plaintext cannot easily be recovered from the ciphertext without knowledge of the key.

### 2018-06-25 parts/01_introduction_02researchquestions.tex

@@
 \begin{enumerate}
+	\item Which homomorphic image encryption algorithms are the most applicable for image processing operations?
 	\item Which homomorphic image encryption algorithms are the most efficient in terms of time when applying image manipulation operations?
-    \item Which homomorphic image encryption algorithms are the most secure under statistical attacks?
-    \item How can a library for OpenCV be implemented for further use and study of image manipulation operations within a homomorphic cryptosystem?
+	\item Which homomorphic image encryption algorithms are the most secure under differential and entropy attacks?
 \end{enumerate}

### 2018-06-25 parts/01_introduction_04significanceofstudy.tex

@@
 
-The results of the study will provide
+This study aims to directly address one of the current problems in the research of homomorphic cryptosystems: the practicality of homomorphic encryption \cite{sen_homomorphic_2013}.
+The literature shows existing homomorphic cryptosystems and how they support primitive operations (usually addition and multiplicaiton) on encrypted data, however, for homomorphic cryptosystems to be usable for practical image processing applications, support for more complicated operations such as image convolution must be demonstrated as well.
+While implementations of homomorphic encryption algorithms exist \cite{ziad_cryptoimg:_2016, garay_algorithms_2014}, our study targets algorithms for which statistical tests were not performed for image processing operations.
+
+By developing a library allowing for the use and comparison of various homomorphic encryption algorithms, we wish to contribute to existing models for the secure transmission and modification of image data.
+Examples include applications in cloud storage \cite{potey_homomorphic_2016} and video surveillance \cite{upmanyu_efficient_2009}.
+This allows service providers to perform image manipulation for clients without compromising data privacy.

### 2018-06-25 parts/01_introduction_03objectives.tex
Finished chapter 2 + other fixes

@@
 al.
-presents \textit{CryptoImg}, a library for the  Open Source Computer Vision Library (OpenCV) \cite{opencv_library} which implements various homomorphic encryption and image processing routines using the Paillier homomorphic cryptosystem \cite{ziad_cryptoimg:_2016}.
+presents \textit{CryptoImg}, a library for the  Open Source Computer Vision Library (OpenCV) \cite{bradski_opencv_2000} which implements various homomorphic encryption and image processing routines using the Paillier homomorphic cryptosystem \cite{ziad_cryptoimg:_2016}.
 While \textit{CryptoImg} demonstrates that various image manipulation operations are possible in a homomorphic system, we believe this study can be extended by considering other known homomorphic encryption schemes, such as an elliptic curve and ElGamal based cryptosystem presented by Li, et.

### 2018-06-25 parts/02_relatedliterature.tex
Finished chapter 2 + other fixes

@@
 
-\section{An Introduction to Cryptography and Cryptosystems}
+\section{Homomorphic Cryptosystems}
 % [include mention of metrics by which they are compared]
 
-In cryptography, a cryptosystem consists of an encryption function $\mathcal{E}$ and a decryption function $\mathcal{D}$, along with the plaintext space $\mathcal{P}$, ciphertext space $\mathcal{C}$ and the key space $\mathcal{K}$~\cite{tilborg_encyclopedia_2005}.
+In cryptography, a cryptosystem consists of an encryption function $\mathcal{E}$ and a decryption function $\mathcal{D}$, along with the plaintext space $\mathcal{P}$, ciphertext space $\mathcal{C}$ and the key space $\mathcal{K}$~\cite{bauer_cryptosystem_2005}.
 A \textit{plaintext} is text that can be easily understood by everybody.
 On the other hand, a \textit{ciphertext} is a result from encrypting the plaintext using an encryption key.
-The plaintext space consists of all the possible plaintexts.
+The \textit{plaintext space} is the set of all possible plaintexts, the \textit{ciphertext space} is the set of all possible ciphertexts, while the \textit{keyspace} consists of all possible keys.
 
 There are two kinds of cryptosystems, namely: \textit{symmetric} and \textit{asymmetric}.
-In symmetric encryption, the key is used for both encryption and decryption.
-On the other hand, asymmetric cryptosystems use separate keys for encryption and decryption.
+In symmetric-key cryptosystems, the same key is used for both encryption and decryption.
+As a consequence, the encryption and decryption functions are inverses of each other.
+Prominent examples of symmetric-key cryptosystems are the Data Encryption Standard (DES), and its replacement, the Advanced Encryption Standard (AES).
+
+On the other hand, asymmetric-key (or public-key) cryptosystems use separate keys for encryption and decryption.
 The encryption key (also called the \textit{public key}) is shared to everybody, while the decryption key (also called the \textit{private key}) is kept secret.
 Because of this, there is no need to agree upon some secure key sharing protocols.
-Usually, the security of asymmetric cryptosystems relies on the intractability of certain computational problems, like the RSA depends on the difficulty of integer factorization, while ElGamal depends on the difficulty of the discrete logarithmic problem.
+Usually, the security of asymmetric-key cryptosystems relies on the intractability of certain computational problems, like how RSA depends on the difficulty of integer factorization \cite{rivest_method_1978}, while ElGamal depends on the difficulty of the discrete logarithm problem \cite{blakley_public_1985}.
 
@@
 \begin{equation}
-    \mathcal{E}\left(p_1 \otimes p_2\right) = \mathcal{E}\left(p_1\right) \oplus \mathcal{E}\left(p_2\right)
+    \mathcal{E}_k \left(p_1 \boxplus p_2\right) = \mathcal{E}_k \left(p_1\right) \oplus \mathcal{E}_k \left(p_2\right)
 \end{equation}
-where $\otimes$ and $\oplus$ are operations in $\mathcal{P}$ and $\mathcal{C}$ respectively \cite{fontaine_survey_2007}.
+where $p_1, p_2 \in \mathcal{P}$ are the plaintexts, $k \in \mathcal{K}$ is the encryption key, and $\boxplus$ and $\oplus$ are operations in $\mathcal{P}$ and $\mathcal{C}$ respectively \cite{fontaine_survey_2007}.
+Furthermore, suppose in a public-key cryptosystem, let $\mathcal{E}_k \left(p \right)$ be the encryption function using the public key $k$, and $\mathcal{D}_l \left(c \right)$ be the decryption function using the private key $l$.
+Then this cryptosystem is homomorphic if it satisfies
+\begin{equation}
+    p_1 \boxplus p_2 = \mathcal{D}_l \left( \mathcal{E}_k \left(p_1\right) \oplus \mathcal{E}_k \left(p_2\right) \right)
+\end{equation}
+where $p_1, p_2 \in \mathcal{P}$ are the plaintexts \cite{li_elliptic_2012}.
+In other words, a homomorphic cryptosystem preserves the operations that can be typically done with the plaintext without the intermediary step of decrypting the ciphertext beforehand.
+
+Some examples of homomorphic cryptosystems include the Goldwasser-Micali cryptosystem \cite{goldwasser_probabilistic_1984} and the Paillier cryptosystem \cite{stern_public-key_1999}.
+Even the classic public-key cryptosystems are homomorphic, both RSA and ElGamal are multiplicatively homomorphic, while elliptic curve cryptosystems are additively homomorphic \cite{li_elliptic_2012}.
+
+However, there exists a \textit{fully homomorphic} cryptosystem, where instead of being limited to operations like addition or multiplication, it allows any arbitrary operations on the ciphertext.
+It is only in recent years that a fully homomorphic cryptosystem has been described.
+Gentry's cryptosystem, which uses lattice-based cryptography, allows arbitrary functions that are constructed from various addition and multiplication operations \cite{gentry_fully_2009}.
+
+A recent survey of homomorphic encryption by Sen shows that the open problems in the area deal with fully homomorphic encryption, of which the main concern is the speed of such implementations \cite{sen_homomorphic_2013}.
 
@@
 % we may refer to the classification in the CryptoImg paper
+Knowing that most of the common image operations rely on addition and multiplication operations, adopting a fully homomorphic cryptosystem enables image processing operations on encrypted images without the need of decryption.
 
@@
 
-\subsection{Edge Detection and Spatial Filters}
+\subsection{Edge Detection and Spatial Filtering}
 Edge detection is used to find and determine the boundaries in an image, commonly used in applications such as image segmentation and feature extraction.
 This works by detecting so-called \textit{edges}, areas that have abrupt changes in intensity.
+
 Edge detection is usually done by using gradient operators that detect such abrupt changes.
@@
 \end{equation}
-
 To get the resulting image $I^\prime$, a convolution is performed between the original image $I$ of size $M \times N$ and the kernel $k$ of size $m \times n$.
@@
 
-Spatial filters are not only used for edge detection, but there are filters that do image blurring (such as Gaussian blur and box blur) and image sharpening.
+Spatial filters are not only used for edge detection, but there are also filters that do image smoothing (such as Gaussian blur and box blur, $b_g$ and $b$ respectively in Equation~\ref{eqn:smooth-filters}) and image sharpening, to name a few \cite{gonzalez_digital_2008}.
+\begin{equation}
+    \label{eqn:smooth-filters}
+    b_g = \frac{1}{16}
+    \begin{bmatrix}
+        1 & 2 & 1 \\
+        2 & 4 & 2 \\
+        1 & 2 & 1
+    \end{bmatrix}
+    \qquad
+    b = \frac{1}{9}
+    \begin{bmatrix}
+        1 & 1 & 1 \\
+        1 & 1 & 1 \\
+        1 & 1 & 1
+    \end{bmatrix}
+\end{equation}
 % Should I put a table of other kernels too?
@@
 \section{Related Work and Previous Implementations}
-There has been work done regarding the implementation of 
-CryptoImg
+% CryptoImg
 
-example of homomorphic encryption / image manipulation past work
+% example of homomorphic encryption / image manipulation past work
 
-minor limitation: improvement on previous work, but not a direct comparison
+% minor limitation: improvement on previous work, but not a direct comparison
 
-major limitation: does not discuss security: are modified images also secure?
+% major limitation: does not discuss security: are modified images also secure?
 
-HElib
+There has been work done regarding the application of homomorphic cryptosystems in image processing.
+In particular, Ziad, et al.
+introduced a library called \textit{CryptoImg} that uses the homomorphic properties of the Paillier cryptosystem to apply image operations securely \cite{ziad_cryptoimg:_2016}.
+This shows that it is indeed possible to do various image operations in a homomorphic cryptosystem.
+
+However, a major limitation of \textit{CryptoImg} is that it does not seem to tackle the problem of security.
+Even though the authors claim that the operations in \textit{CryptoImg} are privacy-preserving, it is not clear whether the modified images are secure as well.
+This study can be further improved by also considering the use of other homomorphic cryptosystems like the elliptic curve-based ElGamal cryptosystem by Li, et al.
+\cite{li_elliptic_2012} and a fully homomorphic cryptosystem introduced by Smart and Vercauteren \cite{hutchison_fully_2010}, which is a variant of Gentry's lattice-based cryptosystem.
+
+% HElib
+Another related work would be the implementation of a fully homomorphic encryption.
+Halevi and Shoup \cite{garay_algorithms_2014} introduced \textit{HElib}, a library that implements the Brakerski-Gentry-Vaikuntanathan (BGV) homomorphic cryptosystem.
+This library also makes use of various optimizations to speed up the homomorphic operations, due to homomorphic cryptosystems being slower than other cryptosystems \cite{sen_homomorphic_2013}.
 
 \section{Summary}
+We have seen how various image processing operations make use of a series of additions and multiplications.
+Because of this, it is possible to use a homomorphic cryptosystem in order to apply image operations directly on encrypted images, as demonstrated by the \textit{CryptoImg} library.
+
+In particular, we aim to address the shortcoming of \textit{CryptoImg} by developing a library to test various homomorphic encryption schemes with the help of the \textit{HElib} library to be able to implement fully homomorphic encryption schemes.
+This helps us determine the practicality of using homomorphic cryptosystems in image processing, especially when dealing with more complex image operations.

### 2018-06-25 parts/03_methodology.tex
Finished chapter 2 + other fixes

@@
 
-The current version of the OpenCV library (3.4.1) will be forked from the open-source GitHub repository at https://github.com/opencv \cite{opencv_library}.
+The current version of the OpenCV library (3.4.1) will be forked from the open-source GitHub repository at \url{https://github.com/opencv/opencv} \cite{bradski_opencv_2000}.
 
@@
 	\end{align}
-	\item [Histogram processing / equalization]
-
+	Morphological operations such as erosion and dilation can be achieved using convolution as well.
 \end{description}
@@
 For each plaintext image (PT), we will consider each image operation listed above and generate three images: a plaintext domain transformation (PDT), a ciphertext image (CT), and an encrypted domain transformation (EDT).
-The cipherThe PDT will be generated by running the image operation on the original image.
+The PDT will be generated by running the image operation on the original image.
 The CT will be generated by encrypting the image, then applying the operation, and the EDT will be generated by decrypting the CT.
@@
 	\begin{align}
-		MSE = \frac{1}{N}\sum_{i=1}^{N}{(CDT_i - PDT_i)^2}.
+		\mathrm{MSE} = \frac{1}{N}\sum_{i=1}^{N}{(\mathrm{CDT}_i - \mathrm{PDT}_i)^2}.
 	\end{align}
@@
 	According to Ahmed, et al.
-\cite{ahmed_benchmark_2016}, PSNR is ``an estimator for human visual perception of reconstruction quality'' which is based on  It has been used to ascertain image quality in various studies and is a known meetric for image and video quality \cite{upmanyu_efficient_2009, jain_image_2016, akramullah_video_2014}.
+\cite{ahmed_benchmark_2016}, PSNR is ``an estimator for human visual perception of reconstruction quality'' which is based on  It has been used to ascertain image quality in various studies and is a known metric for image and video quality \cite{upmanyu_efficient_2009, jain_image_2016, akramullah_video_2014}.
 Although it may produce results which do not correlate with human visual perception \cite{huynh-thu_accuracy_2012, ahmed_benchmark_2016}, it is a valid indicator of image quality when media containing the same visual content is compared \cite{huynh-thu_accuracy_2012}.
@@
 	\begin{align}
-		PSNR = 10\log_{10}{\left( \frac{L^2}{MSE} \right)}
+		\mathrm{PSNR} = 10\log_{10}{\left( \frac{L^2}{\mathrm{MSE}} \right)}
 	\end{align}
@@
 	\begin{align}
-		SSIM(X,Y) = \frac{(2\mu_X\mu_Y+c_1)(2\sigma_{XY}+c_2)}{(\mu_X^2+\mu_Y^2+c_1)(\mu_X^2+\mu_Y^2+c_2)}
+		\mathrm{SSIM}(X,Y) = \frac{(2\mu_X\mu_Y+c_1)(2\sigma_{XY}+c_2)}{(\mu_X^2+\mu_Y^2+c_1)(\mu_X^2+\mu_Y^2+c_2)}
 	\end{align}
@@
 	The SSIM is applied to the luminance value of two images to gauge structural similarity between neighboring pixels.
-	For the study, we will compute $SSIM(PDT, CDT)$ for every image operation, under each homomorphic cryptosystem.
+	For the study, we will compute $\mathrm{SSIM}(\mathrm{PDT}, \mathrm{CDT})$ for every image operation, under each homomorphic cryptosystem.
 Higher values of SSIM indicate higher structural similarity, and an SSIM of 1 indicates that the two images are identical\cite{ahmed_benchmark_2016}.
@@
 
-	We will compute $H(CDT)$ for every image operation, under each homomorphic cryptosystem, and compare the effects of each image operation on the entropy of the encrypted image.
+	We will compute $H(\mathrm{CDT})$ for every image operation, under each homomorphic cryptosystem, and compare the effects of each image operation on the entropy of the encrypted image.
 Ideally, performing image operations on encrypted images should still maintain a high level of entropy.
@@
 		\begin{align}
-			CC(X,Y) = \frac{\sigma_{X,Y}}{\sqrt{\sigma_X}\times\sqrt{\sigma_Y}}
+			\mathrm{CC}(X,Y) = \frac{\sigma_{X,Y}}{\sqrt{\sigma_X}\times\sqrt{\sigma_Y}}
 		\end{align}
@@
 
-		For every $CDT$ image, we will compute for the correlation coefficient (for vertical, horizontal and diagonal correlation) for every image operation, under each homomorphic cryptosystem.
+		For every $\mathrm{CDT}$ image, we will compute for the correlation coefficient (for vertical, horizontal and diagonal correlation) for every image operation, under each homomorphic cryptosystem.
 	\item [NPCR and UACI.]
@@
 		\begin{align}
-			NPCR(X,Y) &= \frac{1}{N}\sum_{i = 1}^{N}{D(X_i,Y_i)} \times 100\%\\
-			UACI(X,Y) &= \frac{1}{L_{max} \times N} \sum_{i = 1}^{N}{ |L(X_i) - L(Y_i)| } \times 100\%
+			\mathrm{NPCR}(X,Y) &= \frac{1}{N}\sum_{i = 1}^{N}{D(X_i,Y_i)} \times 100\%\\
+			\mathrm{UACI}(X,Y) &= \frac{1}{L_{\max} \times N} \sum_{i = 1}^{N}{ |L(X_i) - L(Y_i)| } \times 100\%
 		\end{align}
@@
 			\end{align}
-		\item $L_{max}$ is the maximum intensity of a pixel;
+		\item $L_{\max}$ is the maximum intensity of a pixel;
 		\item $L(X_i)$ and $L(Y_i)$ are the intensities of pixels $X_i$ and $Y_i$, respectively.
 		\end{itemize}
-		We will calculate $NPCR(PDT,CDT)$ and $UACI(PDT,CDT)$  for every image operation, under each homomorphic cryptosystem.
+		We will calculate $\mathrm{NPCR}(\mathrm{PDT},\mathrm{CDT})$ and $\mathrm{UACI}(\mathrm{PDT},\mathrm{CDT})$  for every image operation, under each homomorphic cryptosystem.
 A high NPCR and UACI are desired to ensure high dispersion and security against differential attacks \cite{ahmed_benchmark_2016}.

### 2018-06-26 parts/01_introduction_01contextofstudy.tex

@@
 A cryptosystem is a system which operates on plaintexts, ciphertexts and keys.
-a cryptosystem also has an encryption algorithm, which maps a plaintext to a ciphertext, and a decryption algorithm, which maps a ciphertext to a plaintext, given an appropiate key \cite{bauer_cryptosystem_2005}.
+a cryptosystem also has an encryption algorithm, which maps a plaintext to a ciphertext, and a decryption algorithm, which maps a ciphertext to a plaintext, given an appropriate key \cite{bauer_cryptosystem_2005}.
 The encryption and decryption algorithms are chosen such that the plaintext cannot easily be recovered from the ciphertext without knowledge of the key.

### 2018-06-26 parts/03_methodology.tex
Polished methodology summary

--- 2018-06-25 parts/03_methodology.tex
@@
 
-We now recap the research questions and the corresponding methodology.
+In summary, the study will consist of
+\begin{itemize}
+	\item An implementation of an OpenCV library which implements homomorphic cryptosystems by Ziad, et al.
+\cite{ziad_cryptoimg:_2016}, Li, et al.
+\cite{li_elliptic_2012} and Smart and Vercauteren \cite{hutchison_fully_2010}.
+	\item An implementation of image processing operations (intensity transformations, spatial filters) under the above cryptosystems.
+	\item Conducting tests for image quality, processing time, and cryptographic security, using standard test images from \cite{gonzalez_image_nodate}.
+\end{itemize}
+
+These will be conducted over the course of the first semester of AY 2018-2019 to allow for analysis of the results and paper preparation in the second semester.
+Additional cryptosystems, image operations, and cryptographic security tests may be included in the scope of the study, depending on future research.
+
+We now provide a summary of how each of our reserch questions are addressed by the methodology.
 \begin{itemize}

### 2018-06-26 parts/02_relatedliterature.tex
Fixed definition of homomorphic cryptosystem.

@@
 
+Homomorphic cryptosystems are a special type of cryptosystem wherein operations can be securely performed on encrypted data.
+Suppose that for a public-key cryptosystem, $\mathcal{E}_k \left(p \right)$ is the encryption function using the public key $k \in \mathcal{K}$, and $\mathcal{D}_l \left(c \right)$ be the decryption function using the private key $l$.
 A cryptosystem is said to be homomorphic if its encryption function is homomorphic, that is, if it satisfies the relation
@@
 \end{equation}
-where $p_1, p_2 \in \mathcal{P}$ are the plaintexts, $k \in \mathcal{K}$ is the encryption key, and $\boxplus$ and $\oplus$ are operations in $\mathcal{P}$ and $\mathcal{C}$ respectively \cite{fontaine_survey_2007}.
-Furthermore, suppose in a public-key cryptosystem, let $\mathcal{E}_k \left(p \right)$ be the encryption function using the public key $k$, and $\mathcal{D}_l \left(c \right)$ be the decryption function using the private key $l$.
-Then this cryptosystem is homomorphic if it satisfies
+where $p_1, p_2 \in \mathcal{P}$ are the plaintexts, and $\boxplus$ and $\oplus$ are operations in $\mathcal{P}$ and $\mathcal{C}$ respectively \cite{fontaine_survey_2007}.
+Furthermore, a homomorphic cryptosystem also satisfies \cite{li_elliptic_2012}
 \begin{equation}
-    p_1 \boxplus p_2 = \mathcal{D}_l \left( \mathcal{E}_k \left(p_1\right) \oplus \mathcal{E}_k \left(p_2\right) \right)
+    p_1 \boxplus p_2 = \mathcal{D}_l \left( \mathcal{E}_k \left(p_1\right) \oplus \mathcal{E}_k \left(p_2\right) \right).
 \end{equation}
-where $p_1, p_2 \in \mathcal{P}$ are the plaintexts \cite{li_elliptic_2012}.
 In other words, a homomorphic cryptosystem preserves the operations that can be typically done with the plaintext without the intermediary step of decrypting the ciphertext beforehand.
+An important note about the defintion of a homomorphic cryptosystem is that the operations $\boxplus$ and $\oplus$ need not be the same.
+A simple operation in the plaintext space may require a computationally intensive operation in the ciphertext space.
 

### 2018-06-26 parts/02_relatedliterature.tex
Added intro for chapter 2

--- 2018-06-25 parts/02_relatedliterature.tex
@@
 \chapter{REVIEW OF RELATED LITERATURE}
+
+We first present an introduction to the concepts in cryptography, starting from the definition of a cryptosystem up to homomorphic encryption schemes, along with some examples from the literature.
+Then, we present some concepts in image processing, a suitable application of cryptography, specifically the common image operations used.
+Finally, we present related work that attempts to apply image processing operations with homomorphic cryptosystems, as well as their advantages and limitations.
 
@@
 As a consequence, the encryption and decryption functions are inverses of each other.
-Prominent examples of symmetric-key cryptosystems are the Data Encryption Standard (DES), and its replacement, the Advanced Encryption Standard (AES).
+Prominent examples of symmetric-key cryptosystems include the Data Encryption Standard (DES), and its replacement, the Advanced Encryption Standard (AES).
 

### 2018-06-26 parts/02_relatedliterature.tex
Edited RRL

--- 2018-06-26 parts/02_relatedliterature.tex
@@
 
+Homomorphic cryptosystems are classified according to the plaintext and ciphertext operations, $\boxplus$ and $\oplus$.
+If the plaintext operation $\boxplus$ is addition, the cryptosystem is said to be \textit{additively homomorphic}, and the cryptosystem is said to be \textit{multiplicatively homomorphic} if the plaintext operation $\boxplus$ is multiplication.
 Some examples of homomorphic cryptosystems include the Goldwasser-Micali cryptosystem \cite{goldwasser_probabilistic_1984} and the Paillier cryptosystem \cite{stern_public-key_1999}.
-Even the classic public-key cryptosystems are homomorphic, both RSA and ElGamal are multiplicatively homomorphic, while elliptic curve cryptosystems are additively homomorphic \cite{li_elliptic_2012}.
+Even some classic public-key cryptosystems are homomorphic, both RSA and ElGamal are multiplicatively homomorphic, while elliptic curve cryptosystems are additively homomorphic \cite{li_elliptic_2012}.
+These cryptosystems, while relatively efficient, only support a limited set of operations on the encrypted data.
 
-However, there exists a \textit{fully homomorphic} cryptosystem, where instead of being limited to operations like addition or multiplication, it allows any arbitrary operations on the ciphertext.
+However, there exists \textit{fully homomorphic} cryptosystems, where instead of being limited to operations like addition or multiplication, it allows any arbitrary operations on the ciphertext.
 It is only in recent years that a fully homomorphic cryptosystem has been described.
 Gentry's cryptosystem, which uses lattice-based cryptography, allows arbitrary functions that are constructed from various addition and multiplication operations \cite{gentry_fully_2009}.
-
-A recent survey of homomorphic encryption by Sen shows that the open problems in the area deal with fully homomorphic encryption, of which the main concern is the speed of such implementations \cite{sen_homomorphic_2013}.
+Gentry's cryptosystem allows for the computation of arbitrary Boolean circuits on binary data.
+While improvements have been developed for Gentry's original scheme \cite{hutchison_fully_2010 ,sen_homomorphic_2013}, since the homomorphic property of these systems is applied on each bit of the plaintext/ciphertext elementary addition and multiplication operations on the plaintext are compuationally intensive \cite{sen_homomorphic_2013, shortell_secure_2016}.
 
@@
 This shows that it is indeed possible to do various image operations in a homomorphic cryptosystem.
+Ziad, et al.
+also showed experimental results establishing the slow performance of image operations uner a homomorphic cryptosystem.
+For instance, while sharpening and applying a Sobel filter each take less than a second when applied to a $512\times 512$ plaintext image, when applied to an encrypted image, sharpening required at least 238.257 seconds, and applying the Sobel filter required at least 147.567 seconds \cite{ziad_cryptoimg:_2016}.
 
 However, a major limitation of \textit{CryptoImg} is that it does not seem to tackle the problem of security.
-Even though the authors claim that the operations in \textit{CryptoImg} are privacy-preserving, it is not clear whether the modified images are secure as well.
+Even though the authors have established that the Paillier cryptosystem itself cannot be broken \cite{ziad_cryptoimg:_2016}, we believe that a cryptanalysis of the encrypted images after they have been operated is necessary, since image operations may be considered additional information in a known plaintext attack.
+
+Furthermore, Ziad, et al.
+only presented a visual comparison and evaluation to establish the quality of the recovered images.
+We believe that additional image quality benchmarks, such as those presented in \cite{ahmed_benchmark_2016, ahmad_efficiency_2012}, would allow for quantitative comparisons of image quality.
 This study can be further improved by also considering the use of other homomorphic cryptosystems like the elliptic curve-based ElGamal cryptosystem by Li, et al.
-\cite{li_elliptic_2012} and a fully homomorphic cryptosystem introduced by Smart and Vercauteren \cite{hutchison_fully_2010}, which is a variant of Gentry's lattice-based cryptosystem.
+\cite{li_elliptic_2012} and a fully homomorphic cryptosystem introduced by Smart and Vercauteren \cite{hutchison_fully_2010}, which is a variant of Gentry's lattice-based cryptosystem which can be expressed using elementary number theory, without the use of lattices.
 

### 2018-06-26 parts/03_methodology.tex
Made some minor edits

--- 2018-06-25 parts/03_methodology.tex
@@
 For each plaintext image (PT), we will consider each image operation listed above and generate three images: a plaintext domain transformation (PDT), a ciphertext image (CT), and an encrypted domain transformation (EDT).
-The PDT will be generated by running the image operation on the original image.
+The cipherThe PDT will be generated by running the image operation on the original image.
 The CT will be generated by encrypting the image, then applying the operation, and the EDT will be generated by decrypting the CT.
@@
 	According to Ahmed, et al.
-\cite{ahmed_benchmark_2016}, PSNR is ``an estimator for human visual perception of reconstruction quality'' which is based on  It has been used to ascertain image quality in various studies and is a known metric for image and video quality \cite{upmanyu_efficient_2009, jain_image_2016, akramullah_video_2014}.
+\cite{ahmed_benchmark_2016}, PSNR is ``an estimator for human visual perception of reconstruction quality'' which is based on  It has been used to ascertain image quality in various studies and is a known meetric for image and video quality \cite{upmanyu_efficient_2009, jain_image_2016, akramullah_video_2014}.
 Although it may produce results which do not correlate with human visual perception \cite{huynh-thu_accuracy_2012, ahmed_benchmark_2016}, it is a valid indicator of image quality when media containing the same visual content is compared \cite{huynh-thu_accuracy_2012}.

### 2018-06-26 parts/02_relatedliterature.tex

@@
 Gentry's cryptosystem allows for the computation of arbitrary Boolean circuits on binary data.
-While improvements have been developed for Gentry's original scheme \cite{hutchison_fully_2010 ,sen_homomorphic_2013}, since the homomorphic property of these systems is applied on each bit of the plaintext/ciphertext elementary addition and multiplication operations on the plaintext are compuationally intensive \cite{sen_homomorphic_2013, shortell_secure_2016}.
+While improvements have been developed for Gentry's original scheme \cite{hutchison_fully_2010, sen_homomorphic_2013}, since the homomorphic property of these systems is applied on each bit of the plaintext/ciphertext elementary addition and multiplication operations on the plaintext are compuationally intensive \cite{sen_homomorphic_2013, shortell_secure_2016}.
 

### 2018-07-14 parts/01_introduction_01contextofstudy.tex
Revisions to Ch1

--- 2018-06-25 parts/01_introduction_01contextofstudy.tex
@@
 To meet these needs, various cryptosystems have been developed.
-A cryptosystem is a system which operates on plaintexts, ciphertexts and keys.
-a cryptosystem also has an encryption algorithm, which maps a plaintext to a ciphertext, and a decryption algorithm, which maps a ciphertext to a plaintext, given an appropiate key \cite{bauer_cryptosystem_2005}.
+A cryptosystem is a system which operates on plaintexts, ciphertexts and keys, and has an encryption algorithm, which maps a plaintext to a ciphertext, together with a decryption algorithm, which maps a ciphertext to a plaintext, given an appropriate key \cite{bauer_cryptosystem_2005}.
 The encryption and decryption algorithms are chosen such that the plaintext cannot easily be recovered from the ciphertext without knowledge of the key.
-This allows data to be securely transmitted over an insecure channel:  and thus much research has been done on the development and application of various cryptosystems.
+This allows data to be securely transmitted over an insecure channel.
+Much research has been done on the development and application of various cryptosystems.
 
-One such particular application of cryptography is image encryption.
+One particular application of cryptography is image encryption.
 While cryptosystems used to encrypt digital data in general, such as the Advanced Encryption Standard (AES) or elliptic curve cryptography, can also be used to encrypt images \cite{jain_image_2016, singh_image_2015} other algorithms created specifically for image encryption have also been developed \cite{murugan_survey_2018}.
 
-However, research has also considered a type of cryptosystem, homomorphic cryptosystems, where in addition to allowing the secure transmission of data, it is also possible to perform computations with encrypted data, the most basic of which being addition and multiplication.
-Numerous homomorphic cryptosystems exist, which allow for data to be manipulated without compromising data privacy \cite{fontaine_survey_2007, sen_homomorphic_2013}.
-In homomorphic image encryption, there is additional interest in being able to perform image manipulation operations on the encrypted data such as image adjustment, filtering, and morphological/feature extraction operations \cite{ziad_cryptoimg:_2016, gonzalez_digital_2008}.
+However, research has also considered homomorphic cryptosystems, which not only allow the secure transmission of data, but also allow computations with encrypted data.
+In a homomorphic cryptosystem, operations such as addition and multiplication can be performed on encrypted data.
+These operations are then preserved when the data is decrypted.
+In this manner, data is manipulated without compromising data privacy, as the encrypted data being operated on remains secure \cite{fontaine_survey_2007, sen_homomorphic_2013}.
+While numerous homomorphic cryptosystems exist for use with digital data in general, in the area of homomorphic image encryption, there is additional interest in being able to perform image manipulation operations on the encrypted data such as image adjustment, filtering, and morphological/feature extraction operations \cite{ziad_cryptoimg:_2016, gonzalez_digital_2008}.

### 2018-07-14 parts/01_introduction_02researchquestions.tex
Revisions to Ch1

--- 2018-06-24 parts/01_introduction_02researchquestions.tex
@@
 
-In this study, we ask
+By implementing homomorphic cryptosystems and creating an OpenCV library so they can be easily used, we aim to address our main research question: What is the best method for image data to be encrypted and manipulated for practical applications?
 
+More specifically, our research will address the following sub-research questions:
 \begin{enumerate}
-    \item Research questions 1...
-    \item Research questions 2...
-    \item Research questions 3...
+	\item Which homomorphic cryptosystems admit more image processing operations?
+	\item Which homomorphic cryptosystems are the most time-efficient in applying image processing operations?
+	\item Which homomorphic cryptosystems are the most secure under differential and entropy attacks?
 \end{enumerate}

### 2018-07-14 parts/01_introduction_03objectives.tex
Revisions to Ch1

@@
 presents \textit{CryptoImg}, a library for the  Open Source Computer Vision Library (OpenCV) \cite{bradski_opencv_2000} which implements various homomorphic encryption and image processing routines using the Paillier homomorphic cryptosystem \cite{ziad_cryptoimg:_2016}.
-While \textit{CryptoImg} demonstrates that various image manipulation operations are possible in a homomorphic system, we believe this study can be extended by considering other known homomorphic encryption schemes, such as an elliptic curve and ElGamal based cryptosystem presented by Li, et.
-al.
-\cite{li_elliptic_2012}, and the fully homomorphic encryption scheme proposed by Smart and Vercauteren \cite{hutchison_fully_2010}.
-Our study aims to provide an objective comparision of various homomorphic cryptosystems currently in the literature, as they would be used in encrypted image manipulation.
-Furthermore, one of the main problems in homomorphic encryption is the practicality of homomorphic encryption schemes.
-Homomorphic cryptosystems are known to be slower compared to other cryptosystems \cite{sen_homomorphic_2013}.
-Taking the above into account, in this study, we wish to
+While \textit{CryptoImg} demonstrates that various image manipulation operations are possible in a homomorphic cryptosystem, we believe this study can be extended by considering other known homomorphic encryption schemes, such as those found in \cite{li_elliptic_2012, hutchison_fully_2010}.
+Our study aims to provide an objective comparison of various homomorphic cryptosystems currently in the literature, as they would be used in encrypted image manipulation.
+
+Our main research objective is to assess the practicality of various homomorphic cryptosystems in image encryption.
+Homomorphic cryptosystems are known to be slower in terms of encryption, operation, and decryption time \cite{sen_homomorphic_2013}.
+Furthermore, the operations on encrypted data supported by homomorphic cryptosystems are limited, and some schemes require preprocessing to be performed on images, limiting the range of operations which can be performed \cite{li_elliptic_2012}.
+Finally, as data security is the primary purpose of cryptosystems, we want to evaluate the security of homomorphic cryptosystems as image encryption schemes.
+
+In summary, in this study, we wish to
 \begin{enumerate}
-    \item Compare the applicability of known homomorphic encryption schemes to common image processsing operations, in other words, determine which schemes permit more image processing operations;
+    \item Compare the applicability of known homomorphic encryption schemes to common image processing operations, in other words, determine which schemes admit more image processing operations;
 		\item Compare the security of common image processing operations under known homomorphic encryption schemes, using established statistical methods in image encryption;
-    \item Compare the efficiency of common image processsing operations under known homomorphic encryption schemes;
+    \item Compare the time efficiency of common image processing operations under known homomorphic encryption schemes;
     \item Create a library for OpenCV to allow for convenient use and comparison of these homomorphic encryption schemes.

### 2018-07-14 parts/01_introduction_04significanceofstudy.tex
Revisions to Ch1

--- 2018-06-24 parts/01_introduction_04significanceofstudy.tex
@@
 
-The results of the study will provide
+This study aims to directly address one of the current problems in the research of homomorphic cryptosystems: the practicality of homomorphic encryption \cite{sen_homomorphic_2013}.
+The literature shows existing homomorphic cryptosystems and how they support primitive operations (usually addition and multiplicaiton) on encrypted data, however, for homomorphic cryptosystems to be useful for practical image processing applications, support for more complicated operations such as image convolution must be demonstrated as well.
+While implementations of homomorphic encryption algorithms exist \cite{ziad_cryptoimg:_2016, garay_algorithms_2014}, our study targets algorithms for which statistical tests have not been performed for image processing operations.
+
+We wish to contribute to existing models for the secure transmission and modification of image data by developing a library which allows the use and comparison of various homomorphic encryption algorithms.
+Examples include applications in cloud storage \cite{potey_homomorphic_2016} and video surveillance \cite{upmanyu_efficient_2009}.
+This allows service providers to perform image manipulation for clients without compromising data privacy.

### 2018-07-15 parts/01_introduction_04significanceofstudy.tex
Revised 2.1

--- 2018-06-24 parts/01_introduction_04significanceofstudy.tex
@@
 
-The results of the study will provide
+This study aims to directly address one of the current problems in the research of homomorphic cryptosystems: the practicality of homomorphic encryption \cite{sen_homomorphic_2013}.
+The literature shows existing homomorphic cryptosystems and how they support primitive operations (usually addition and multiplication) on encrypted data, however, for homomorphic cryptosystems to be useful for practical use, support for more complicated image processing operations such as image convolution must be demonstrated as well.
+While implementations of image processing operations in a homomorphic cryptosystem exist in the literature \cite{ziad_cryptoimg:_2016, garay_algorithms_2014}, our study targets algorithms for which statistical tests have not been performed for image processing operations.
+
+We wish to contribute to existing models for the secure transmission and modification of image data by developing a software library which allows the use and comparison of various homomorphic encryption algorithms.
+Our software library would allow service providers to perform image manipulation for clients without compromising data privacy.

### 2018-07-15 parts/02_relatedliterature.tex
Revised 2.1

@@
 
-\section{Homomorphic Cryptosystems}
-% [include mention of metrics by which they are compared]
-
-In cryptography, a cryptosystem consists of an encryption function $\mathcal{E}$ and a decryption function $\mathcal{D}$, along with the plaintext space $\mathcal{P}$, ciphertext space $\mathcal{C}$ and the key space $\mathcal{K}$~\cite{bauer_cryptosystem_2005}.
-A \textit{plaintext} is text that can be easily understood by everybody.
-On the other hand, a \textit{ciphertext} is a result from encrypting the plaintext using an encryption key.
-The \textit{plaintext space} is the set of all possible plaintexts, the \textit{ciphertext space} is the set of all possible ciphertexts, while the \textit{keyspace} consists of all possible keys.
-
-There are two kinds of cryptosystems, namely: \textit{symmetric} and \textit{asymmetric}.
-In symmetric-key cryptosystems, the same key is used for both encryption and decryption.
-As a consequence, the encryption and decryption functions are inverses of each other.
-Prominent examples of symmetric-key cryptosystems are the Data Encryption Standard (DES), and its replacement, the Advanced Encryption Standard (AES).
-
-On the other hand, asymmetric-key (or public-key) cryptosystems use separate keys for encryption and decryption.
-The encryption key (also called the \textit{public key}) is shared to everybody, while the decryption key (also called the \textit{private key}) is kept secret.
-Because of this, there is no need to agree upon some secure key sharing protocols.
-Usually, the security of asymmetric-key cryptosystems relies on the intractability of certain computational problems, like how RSA depends on the difficulty of integer factorization \cite{rivest_method_1978}, while ElGamal depends on the difficulty of the discrete logarithm problem \cite{blakley_public_1985}.
-
-Homomorphic cryptosystems are a special type of cryptosystem wherein operations can be securely performed on encrypted data.
-Suppose that for a public-key cryptosystem, $\mathcal{E}_k \left(p \right)$ is the encryption function using the public key $k \in \mathcal{K}$, and $\mathcal{D}_l \left(c \right)$ be the decryption function using the private key $l$.
-A cryptosystem is said to be homomorphic if its encryption function is homomorphic, that is, if it satisfies the relation
-\begin{equation}
-    \mathcal{E}_k \left(p_1 \boxplus p_2\right) = \mathcal{E}_k \left(p_1\right) \oplus \mathcal{E}_k \left(p_2\right)
-\end{equation}
-where $p_1, p_2 \in \mathcal{P}$ are the plaintexts, and $\boxplus$ and $\oplus$ are operations in $\mathcal{P}$ and $\mathcal{C}$ respectively \cite{fontaine_survey_2007}.
-Furthermore, a homomorphic cryptosystem also satisfies \cite{li_elliptic_2012}
-\begin{equation}
-    p_1 \boxplus p_2 = \mathcal{D}_l \left( \mathcal{E}_k \left(p_1\right) \oplus \mathcal{E}_k \left(p_2\right) \right).
-\end{equation}
-In other words, a homomorphic cryptosystem preserves the operations that can be typically done with the plaintext without the intermediary step of decrypting the ciphertext beforehand.
-An important note about the defintion of a homomorphic cryptosystem is that the operations $\boxplus$ and $\oplus$ need not be the same.
-A simple operation in the plaintext space may require a computationally intensive operation in the ciphertext space.
-
-Homomorphic cryptosystems are classified according to the plaintext and ciphertext operations, $\boxplus$ and $\oplus$.
-If the plaintext operation $\boxplus$ is addition, the cryptosystem is said to be \textit{additively homomorphic}, and the cryptosystem is said to be \textit{multiplicatively homomorphic} if the plaintext operation $\boxplus$ is multiplication.
-Some examples of homomorphic cryptosystems include the Goldwasser-Micali cryptosystem \cite{goldwasser_probabilistic_1984} and the Paillier cryptosystem \cite{stern_public-key_1999}.
-Even some classic public-key cryptosystems are homomorphic, both RSA and ElGamal are multiplicatively homomorphic, while elliptic curve cryptosystems are additively homomorphic \cite{li_elliptic_2012}.
-These cryptosystems, while relatively efficient, only support a limited set of operations on the encrypted data.
-
-However, there exists \textit{fully homomorphic} cryptosystems, where instead of being limited to operations like addition or multiplication, it allows any arbitrary operations on the ciphertext.
-It is only in recent years that a fully homomorphic cryptosystem has been described.
-Gentry's cryptosystem, which uses lattice-based cryptography, allows arbitrary functions that are constructed from various addition and multiplication operations \cite{gentry_fully_2009}.
-Gentry's cryptosystem allows for the computation of arbitrary Boolean circuits on binary data.
-While improvements have been developed for Gentry's original scheme \cite{hutchison_fully_2010, sen_homomorphic_2013}, since the homomorphic property of these systems is applied on each bit of the plaintext/ciphertext elementary addition and multiplication operations on the plaintext are compuationally intensive \cite{sen_homomorphic_2013, shortell_secure_2016}.
+\input{parts/02_relatedliterature_01homomorphiccryptosystems}
 

### 2018-07-15 parts/02_relatedliterature_01homomorphiccryptosystems.tex
Revised 2.1

\section{Homomorphic Cryptosystems}
% [include mention of metrics by which they are compared]

In cryptography, a cryptosystem consists of an encryption function $\mathcal{E}$ and a decryption function $\mathcal{D}$, along with the plaintext space $\mathcal{P}$, ciphertext space $\mathcal{C}$ and the key space $\mathcal{K}$~\cite{bauer_cryptosystem_2005}. A \textit{plaintext} is text that can be commonly understood, while a \textit{ciphertext} results from encrypting the plaintext using an encryption key. The \textit{plaintext space} is the set of all possible plaintexts, the \textit{ciphertext space} is the set of all possible ciphertexts, while the \textit{keyspace} is the set of all possible keys.

There are two kinds of cryptosystems, \textit{symmetric} and \textit{asymmetric}. In symmetric-key cryptosystems, the same key is used for both encryption and decryption. As a consequence, symmetric-key cryptosystems must be implemented with a secure key exchange protocol, so that both the sender and receiver have access to the same key. Prominent examples of symmetric-key cryptosystems are the Data Encryption Standard (DES), and its replacement, the Advanced Encryption Standard (AES).

On the other hand, asymmetric-key (or public-key) cryptosystems use separate keys for encryption and decryption. The encryption key (also called the \textit{public key}) is shared to everybody, while the decryption key (also called the \textit{private key}) is kept secret. Since the public key and private keys are different, there is no need to agree upon secure key exchange protocols. Usually, the security of asymmetric-key cryptosystems relies on the intractability of certain computational problems, for example, the RSA cryptosystem depends on the difficulty of big integer factorization \cite{rivest_method_1978}, while the ElGamal cryptosystem depends on the difficulty of the discrete logarithm problem \cite{blakley_public_1985}.

Homomorphic cryptosystems are a special type of cryptosystem wherein operations can be securely performed on encrypted data. Suppose that for a public-key cryptosystem, $\mathcal{E}_k \left(p \right)$ is the encryption function using the public key $k \in \mathcal{K}$, and $\mathcal{D}_l \left(c \right)$ be the decryption function using the private key $l$. A cryptosystem is said to be homomorphic if its encryption function is homomorphic, that is, if it satisfies the relation
\begin{equation}
    \mathcal{E}_k \left(p_1 \boxplus p_2\right) = \mathcal{E}_k \left(p_1\right) \boxdot \mathcal{E}_k \left(p_2\right)
\end{equation}
where $p_1, p_2 \in \mathcal{P}$ are the plaintexts, and $\boxplus$ and $\boxdot$ are operations in $\mathcal{P}$ and $\mathcal{C}$ respectively \cite{fontaine_survey_2007}. Furthermore, a homomorphic cryptosystem also satisfies \cite{li_elliptic_2012}
\begin{equation}
    p_1 \boxplus p_2 = \mathcal{D}_l \left( \mathcal{E}_k \left(p_1\right) \boxdot \mathcal{E}_k \left(p_2\right) \right).
\end{equation}
In other words, a homomorphic cryptosystem preserves the operations that can be done with the plaintext without requiring an intermediary step of decrypting the ciphertext beforehand. It is important to note that the operations $\boxplus$ and $\boxdot$ need not be the same. A simple operation in the plaintext space may require a computationally intensive operation in the ciphertext space.

Homomorphic cryptosystems are classified according to the plaintext and ciphertext operations, $\boxplus$ and $\boxdot$. If the plaintext operation $\boxplus$ is addition, the cryptosystem is said to be \textit{additively homomorphic}, and the cryptosystem is said to be \textit{multiplicatively homomorphic} if the plaintext operation $\boxplus$ is multiplication. Some examples of homomorphic cryptosystems include the Goldwasser-Micali cryptosystem \cite{goldwasser_probabilistic_1984} and the Paillier cryptosystem \cite{stern_public-key_1999}. Even some classic public-key cryptosystems are homomorphic, both RSA and ElGamal are multiplicatively homomorphic, while elliptic curve cryptosystems are additively homomorphic \cite{li_elliptic_2012}. These cryptosystems, while relatively efficient, only support a limited set of operations on the encrypted data.

However, there exists \textit{fully homomorphic} cryptosystems, which are not limited to a fixed set of operations, but allow any arbitrary operations on the ciphertext. The first  fully homomorphic cryptosystem was presented by Gentry in 2009. Gentry's cryptosystem, which uses lattice-based cryptography, allows the computation of computation of arbitrary Boolean circuits on binary data \cite{gentry_fully_2009, shortell_secure_2016}. New algorithms based on Gentry's initial ideas have since been made \cite{ sen_homomorphic_2013}. One notable example is fully homomorphic cryptosystem by Smart and Vercauteren, \cite{hutchison_fully_2010}, later improved by Gentry and Halevi  \cite{hutchison_implementing_2011} which relies on cyclotomic number fields. In 2016, Dasgupta and Pal proposed a fully homomorphic cryptosystem based on polynomial rings \cite{dasgupta_design_2016}. These two cryptosytems are examples of fully homomorphic cryptosystems which have significantly simpler encryption, decryption, addition and multiplication algorithms.

### 2018-07-15 parts/02_relatedliterature.tex
Revised 2.2.1

@@
 \input{parts/02_relatedliterature_01homomorphiccryptosystems}
-
-\section{Common Image Operations}
-% skim chapters 3-4 of the book Digital Image Processing
-
-% we may refer to the classification in the CryptoImg paper
-Knowing that most of the common image operations rely on addition and multiplication operations, adopting a fully homomorphic cryptosystem enables image processing operations on encrypted images without the need of decryption.
-
-In image processing, the typical image operations being done are intensity transformations which maps intensity values to another, and the use of spatial filters to do operations such as edge detection and image blurring.
-
-\subsection{Intensity Transformation}
-Intensity transformations are typically point operations, where a certain operation is applied to each single pixel of the image.
-Usually, there is a function $T$ that maps a pixel value $r$ into a new value $r^\prime$, thus this transformation satisfies the relation $r^\prime = T\left(r\right)$.
-Examples of intensity transformations are image negation, log transformation, and power-law transformation.
-
-Image negation is an example of an intensity transformation, where the resulting image would be similar to a photographic negative~\cite{gonzalez_digital_2008}.
-In this case, suppose the intensity levels of an image are within the range $\left[0, L-1\right]$, then image negation can be expressed by
-\begin{equation}
-    T\left(r\right) = L-1-r
-\end{equation}
-
-The log transformation is used to enhance dark pixels or increase the dark details of an image by mapping low intensity values to a wider range of values~\cite{gonzalez_digital_2008}.
-This has the general form
-\begin{equation}
-    T\left(r\right) = c \log\left(1 + r\right)
-\end{equation}
-where $c$ is a constant and $r \ge 0$.
-
-The power-law transformation is a family of transformations that have the form
-\begin{equation}
-    T\left(r\right) = c r^{\gamma}
-\end{equation}
-where $c>0$ and $\gamma > 0$.
-This is especially useful since many output devices such as printers and display devices follow the power law, and so correcting the power-law response on these devices in a process called \textit{gamma correction} ensures reproducibility and accuracy of images being displayed~\cite{gonzalez_digital_2008}.
-
-\subsection{Edge Detection and Spatial Filtering}
-Edge detection is used to find and determine the boundaries in an image, commonly used in applications such as image segmentation and feature extraction.
-This works by detecting so-called \textit{edges}, areas that have abrupt changes in intensity.
-
-Edge detection is usually done by using gradient operators that detect such abrupt changes.
-These operators are commonly known as \textit{spatial filter}, which are usually of $3 \times 3$ size.
-A common example of spatial filters is the Sobel operator, with two matrices (also called as kernels) $g_x$ and $g_y$ representing the horizontal and vertical components respectively.
-\begin{equation}
-    g_x =
-    \begin{bmatrix}
-        -1 & 0 & 1 \\
-        -2 & 0 & 2 \\
-        -1 & 0 & 1
-    \end{bmatrix}
-    \qquad\text{and}\qquad
-    g_y =
-    \begin{bmatrix}
-        1 & 2 & 1 \\
-        0 & 0 & 0 \\
-        -1 & -2 & -1
-    \end{bmatrix}
-\end{equation}
-To get the resulting image $I^\prime$, a convolution is performed between the original image $I$ of size $M \times N$ and the kernel $k$ of size $m \times n$.
-Now suppose that the pixel value of an image at point $\left(i,j\right)$ is $r_{i,j}$.
-Then, a transformation using spatial filters can be described as follows:
-\begin{align}
-    T\left(r_{i,j}\right) &= \left[k * I\right]\left(\left\lfloor\frac{m}{2}\right\rfloor, \left\lfloor\frac{n}{2}\right\rfloor \right) \\
-                         &= \sum_{u=1}^{m} \sum_{v=1}^{n} \left[k_{i,j} r_{i+u, j+v} \right]
-\end{align}
-
-Spatial filters are not only used for edge detection, but there are also filters that do image smoothing (such as Gaussian blur and box blur, $b_g$ and $b$ respectively in Equation~\ref{eqn:smooth-filters}) and image sharpening, to name a few \cite{gonzalez_digital_2008}.
-\begin{equation}
-    \label{eqn:smooth-filters}
-    b_g = \frac{1}{16}
-    \begin{bmatrix}
-        1 & 2 & 1 \\
-        2 & 4 & 2 \\
-        1 & 2 & 1
-    \end{bmatrix}
-    \qquad
-    b = \frac{1}{9}
-    \begin{bmatrix}
-        1 & 1 & 1 \\
-        1 & 1 & 1 \\
-        1 & 1 & 1
-    \end{bmatrix}
-\end{equation}
-% Should I put a table of other kernels too?
+\input{parts/02_relatedliterature_02commonimageprocessingoperations}
 

### 2018-07-15 parts/02_relatedliterature_02commonimageprocessingoperations.tex
Revised 2.2.1

\section{Common Image Operations}
In this study, we wish to see how the primitive operations of addition and multiplication supported by homomorphic cryptosystems can be applied to image processing operations. These operations are performed on digital images. WE can represent a digital image $A$ as an $M \times N$ matrix of pixel intensity values, each value in the range $\left[0, L-1\right]$, for some positive integer $L$. There are two types of basic operations in image processing, intensity transformations, which map an intensity value to another, spatial filters which assist in operations such as edge detection and image blurring.

\subsection{Intensity Transformation}
To define an intensity transformation on an image $A$, we define a function $T$ which maps a pixel value $r$ to a new value $r^\prime$, which we can write as $r^\prime = T\left(r\right)$. This function is then applied to every pixel in $A$. Examples of intensity transformations are image negation, log transformation, and power-law transformation.

Image negation is an example of an intensity transformation, where the resulting image would be similar to a photographic negative~\cite{gonzalez_digital_2008}. An image negation operation is defined as:
\begin{equation}
    T\left(r\right) = L-1-r
\end{equation}

The log transformation is used to enhance dark pixels or increase the dark details of an image by mapping low intensity values to a wider range of values~\cite{gonzalez_digital_2008}. This has the general form
\begin{equation}
    T\left(r\right) = c \log\left(1 + r\right)
\end{equation}
where $c$ is a constant and $r \ge 0$.

The power-law transformation is a family of transformations that have the form
\begin{equation}
    T\left(r\right) = c r^{\gamma}
\end{equation}
where $c>0$ and $\gamma > 0$. This is especially useful since many image capture and output devices such as cameras, printers and displays follow a similar power law to relate physical percieved light intensity and digital pixel intensity values. A power-law transformation defined by the above equation can calibrate the operation on these devices in a process called \textit{gamma correction}. This ensures reproducibility and accuracy of images being displayed~\cite{gonzalez_digital_2008}.

\subsection{Edge Detection and Spatial Filtering}
Edge detection is used to find and determine the boundaries in an image, commonly used in applications such as image segmentation and feature extraction. This works by detecting so-called \textit{edges}, areas that have abrupt changes in intensity.

Edge detection is usually done by using gradient operators that detect such abrupt changes. These operators are commonly known as \textit{spatial filter}, which are usually of $3 \times 3$ size. A common example of spatial filters is the Sobel operator, with two matrices (also called as kernels) $g_x$ and $g_y$ representing the horizontal and vertical components respectively.
\begin{equation}
    g_x =
    \begin{bmatrix}
        -1 & 0 & 1 \\
        -2 & 0 & 2 \\
        -1 & 0 & 1
    \end{bmatrix}
    \qquad\text{and}\qquad
    g_y =
    \begin{bmatrix}
        1 & 2 & 1 \\
        0 & 0 & 0 \\
        -1 & -2 & -1
    \end{bmatrix}
\end{equation}
To get the resulting image $I^\prime$, a convolution is performed between the original image $I$ of size $M \times N$ and the kernel $k$ of size $m \times n$. Now suppose that the pixel value of an image at point $\left(i,j\right)$ is $r_{i,j}$. Then, a transformation using spatial filters can be described as follows:
\begin{align}
    T\left(r_{i,j}\right) &= \left[k * I\right]\left(\left\lfloor\frac{m}{2}\right\rfloor, \left\lfloor\frac{n}{2}\right\rfloor \right) \\
                         &= \sum_{u=1}^{m} \sum_{v=1}^{n} \left[k_{i,j} r_{i+u, j+v} \right]
\end{align}

Spatial filters are not only used for edge detection, but there are also filters that do image smoothing (such as Gaussian blur and box blur, $b_g$ and $b$ respectively in Equation~\ref{eqn:smooth-filters}) and image sharpening, to name a few \cite{gonzalez_digital_2008}.
\begin{equation}
    \label{eqn:smooth-filters}
    b_g = \frac{1}{16}
    \begin{bmatrix}
        1 & 2 & 1 \\
        2 & 4 & 2 \\
        1 & 2 & 1
    \end{bmatrix}
    \qquad
    b = \frac{1}{9}
    \begin{bmatrix}
        1 & 1 & 1 \\
        1 & 1 & 1 \\
        1 & 1 & 1
    \end{bmatrix}
\end{equation}
% Should I put a table of other kernels too?

### 2018-07-15 parts/02_relatedliterature_02commonimageprocessingoperations.tex
Done revising 2.2

@@
 These operations are performed on digital images.
-WE can represent a digital image $A$ as an $M \times N$ matrix of pixel intensity values, each value in the range $\left[0, L-1\right]$, for some positive integer $L$.
+We can represent a digital image $R$ as an $M \times N$ matrix of pixel intensity values, each value in the range $\left[0, L-1\right]$, for some positive integer $L$.
 There are two types of basic operations in image processing, intensity transformations, which map an intensity value to another, spatial filters which assist in operations such as edge detection and image blurring.
@@
 \subsection{Intensity Transformation}
-To define an intensity transformation on an image $A$, we define a function $T$ which maps a pixel value $r$ to a new value $r^\prime$, which we can write as $r^\prime = T\left(r\right)$.
+To define an intensity transformation on an image $I$, we define a function $T$ which maps a pixel value $r$ to a new value $r^\prime$, which we can write as $r^\prime = T\left(r\right)$.
 This function is then applied to every pixel in $A$.
@@
 
-\subsection{Edge Detection and Spatial Filtering}
+In the CrytoImg software library, of the intensity transformations above, only image negation was implemented under a homomorphic cryptosystem \cite{ziad_cryptoimg}.
+To implement these intensity transformations using addition and multiplication in a homomorphic system, it is necessary to approximate the logarithm and exponential functions, which may result in higher computational overhead.
+In our software library implementation, we aim to investigate the overhead required to approximate these functions.
+
+\subsection{Spatial Filtering}
+Many common image operations are expressed as \textit{spatial filters}.
+Spatial filters are operators which determine output pixels using information from neighboring input pixels.
+To apply a spatial filter to obtain a resulting image $R^\prime$, a convolution is performed between an $m \times n$ matrix $k$, called a kernel, and the original $M\times N$ image $R$.
+A convolution between a kernel $k$ and image $R$ which yields a resulting image $R^\prime$, denoted as $R^\prime = k \ast R$, is defined by
+\begin{align} \label{eq:spatialfilter}
+	R^\prime(x,y) = \sum_{s=1}^m{\sum_{t=1}^n{k(s,t)R(x+s,y+t)}}, \text{ for all } 0\leq x \leq M, 0 \leq y \leq N,
+\end{align}
+where $A(x,y)$ represents the entry at the $x$th row and $y$th column of a matrix $A$.
+
+\begin{figure*}[!ht]
+    \centering
+    \includegraphics[width=\textwidth,\keepaspectratio]{Figures/SpatialFilter.png}
+    \caption{(a) A sample image $R$. (b) A sample kernel $k$.}
+    \label{fig:spatialfilter}
+\end{figure*}
+For example, using the image and kernel given in Figure \ref{fig:spatialfilter}, we can calculate the value in the third row and fourth column of the resulting image $R^\prime$ as follows:
+\begin{align*}
+	R^\prime(3,4) &= \sum_{s=1}^m{\sum_{t=1}^n{k(s,t)R(3+s,4+t)}}\\
+	&= (0.0625\times 200) + (0.1250\times 249) + (0.0625\times 255) +\\
+	&(0.1250\times 143) + (0.2500\times 223) + (0.1250\times 255) +\\
+	&(0.0625\times 196) + (0.1250\times 236) + (0.0625\times 255)\\
+	&= 223.
+\end{align*}
+Since spatial filters take values from a contiguous region of pixels, this presents a difficulty in homomorphic cryptosytems: in order for spatial filters to be performed, the location of each pixel relative to neighboring pixels has to be preserved.
+This was performed in the implementation of spatial filters in the CryptoImg library \cite{ziad_cryptoimg}.
+We wish to implement spatial filters using a similar approach, and assess how preserving spatial correlation between pixels can impact the security of the encrypted image.
+
+\subsection{Common Spatial Filtering Kernels}
 Edge detection is used to find and determine the boundaries in an image, commonly used in applications such as image segmentation and feature extraction.
 This works by detecting so-called \textit{edges}, areas that have abrupt changes in intensity.
-
-Edge detection is usually done by using gradient operators that detect such abrupt changes.
-These operators are commonly known as \textit{spatial filter}, which are usually of $3 \times 3$ size.
-A common example of spatial filters is the Sobel operator, with two matrices (also called as kernels) $g_x$ and $g_y$ representing the horizontal and vertical components respectively.
+One common method of performing edge detection is the Sobel operator, which uses two spatial filters to approximate the gradient in an image. Given an image $R$, and the kernels
 \begin{equation}
@@
         -1 & -2 & -1
-    \end{bmatrix}
+    \end{bmatrix},
 \end{equation}
-To get the resulting image $I^\prime$, a convolution is performed between the original image $I$ of size $M \times N$ and the kernel $k$ of size $m \times n$.
-Now suppose that the pixel value of an image at point $\left(i,j\right)$ is $r_{i,j}$.
-Then, a transformation using spatial filters can be described as follows:
-\begin{align}
-    T\left(r_{i,j}\right) &= \left[k * I\right]\left(\left\lfloor\frac{m}{2}\right\rfloor, \left\lfloor\frac{n}{2}\right\rfloor \right) \\
-                         &= \sum_{u=1}^{m} \sum_{v=1}^{n} \left[k_{i,j} r_{i+u, j+v} \right]
-\end{align}
+$g_x \ast R$ yields the horizontal component of the gradient, while $g_y \ast R$ yields the vertical component of the gradient.
 
-Spatial filters are not only used for edge detection, but there are also filters that do image smoothing (such as Gaussian blur and box blur, $b_g$ and $b$ respectively in Equation~\ref{eqn:smooth-filters}) and image sharpening, to name a few \cite{gonzalez_digital_2008}.
+There are also spatial filters that perform image smoothing (such as Gaussian blur and box blur, which use the kernels $b_g$ and $b$ respectively in Equation~\ref{eqn:smooth-filters}) and image sharpening \cite{gonzalez_digital_2008}.
 \begin{equation}

### 2018-07-15 parts/01_introduction_05scopeandlimitations.tex
Added image quality tests to ch3
Revisions to Ch1
Revised 2.3 and ch3

@@
 	\item A modified version of the Paillier cryptosystem \cite{stern_public-key_1999} which supports floating-point operations, used in \textit{CryptoImg} \cite{ziad_cryptoimg:_2016}.
-	\item An elliptic curve and ElGamal based cryptosystem for homomorphic encryption presented by Li, et. al. \cite{li_elliptic_2012}.
+	\item A fully homomorphic encryption scheme developed by Dasgupta and Pal, which uses polynomial rings \cite{dasgupta_design_2016}.
 	\item A fully homomorphic encryption scheme proposed by Smart and Vercauteren \cite{hutchison_fully_2010}, which is an improvement on the original lattice-based cryptosystem presented by Gentry \cite{gentry_fully_2009}.
@@
 	\item Image adjustment
-	\item Operations based on convolution
-	\item Morphological operations
+	\item Spatial filters/morphological operations
 \end{enumerate}
@@
 		\item Structural Similarity Index (SSIM)
-		\item Noise tolerance
 	\end{enumerate}
@@
 		\item Correlation coefficient analysis
-		\item Differential analysis (number of pixel change rate (NPCR), universeral average change intensity (UACI))
+		\item Differential analysis (number of pixel change rate (NPCR), universal average change intensity (UACI))
 	\end{enumerate}
@@
 
-Our library for OpenCV will be implemented in the C++ programming language.
-
 The study will only consider the operation of the stated algorithms in a single computer. Client-server models for secure data storage and operation will not be considered.

### 2018-07-15 parts/02_relatedliterature.tex
Revised 2.3 and ch3

@@
 
-However, a major limitation of \textit{CryptoImg} is that it does not seem to tackle the problem of security.
+However, a major limitation of \textit{CryptoImg} is that it does not consider image security.
 Even though the authors have established that the Paillier cryptosystem itself cannot be broken \cite{ziad_cryptoimg:_2016}, we believe that a cryptanalysis of the encrypted images after they have been operated is necessary, since image operations may be considered additional information in a known plaintext attack.
@@
 We believe that additional image quality benchmarks, such as those presented in \cite{ahmed_benchmark_2016, ahmad_efficiency_2012}, would allow for quantitative comparisons of image quality.
-This study can be further improved by also considering the use of other homomorphic cryptosystems like the elliptic curve-based ElGamal cryptosystem by Li, et al.
-\cite{li_elliptic_2012} and a fully homomorphic cryptosystem introduced by Smart and Vercauteren \cite{hutchison_fully_2010}, which is a variant of Gentry's lattice-based cryptosystem which can be expressed using elementary number theory, without the use of lattices.
+
+This study can be further improved by also considering the use of fully homomorphic cryptosystems such as the one presented by Dasgupta and Pal \cite{dasgupta_design_2016}, and the fully homomorphic cryptosystem introduced by Smart and Vercauteren \cite{hutchison_fully_2010} and improved by Gentry and Halevi  \cite{hutchison_implementing_2011}.
+These fully homomorphic cryptosytems have yet to be implemented for image processing operations.
 
@@
 
-In particular, we aim to address the shortcoming of \textit{CryptoImg} by developing a library to test various homomorphic encryption schemes with the help of the \textit{HElib} library to be able to implement fully homomorphic encryption schemes.
+In particular, we aim to address the shortcomings of \textit{CryptoImg} by developing a library to test various homomorphic encryption schemes with the help of the \textit{HElib} library to be able to implement fully homomorphic encryption schemes efficiently.
 This helps us determine the practicality of using homomorphic cryptosystems in image processing, especially when dealing with more complex image operations.

### 2018-07-15 parts/02_relatedliterature_02commonimageprocessingoperations.tex
Revised 2.3 and ch3

@@
 
-In the CrytoImg software library, of the intensity transformations above, only image negation was implemented under a homomorphic cryptosystem \cite{ziad_cryptoimg}.
+In the CrytoImg software library, of the intensity transformations above, only image negation was implemented under a homomorphic cryptosystem \cite{ziad_cryptoimg:_2016}.
 To implement these intensity transformations using addition and multiplication in a homomorphic system, it is necessary to approximate the logarithm and exponential functions, which may result in higher computational overhead.
@@
 Since spatial filters take values from a contiguous region of pixels, this presents a difficulty in homomorphic cryptosytems: in order for spatial filters to be performed, the location of each pixel relative to neighboring pixels has to be preserved.
-This was performed in the implementation of spatial filters in the CryptoImg library \cite{ziad_cryptoimg}.
+This was performed in the implementation of spatial filters in the CryptoImg library \cite{ziad_cryptoimg:_2016}.
 We wish to implement spatial filters using a similar approach, and assess how preserving spatial correlation between pixels can impact the security of the encrypted image.

### 2018-07-15 parts/03_methodology.tex
Revised 2.3 and ch3

@@
 
-The study consists of two parts: first, the implementation of the three homomorphic encryption schemes and image processing operations under each scheme as an OpenCV library.
-The second part of the study consists of assessing the robustness and security of image operations under each encryption scheme using benchmarks in \cite{ahmed_benchmark_2016}.
+The study consists of two parts: first, the implementation of the three homomorphic encryption schemes \cite{ziad_cryptoimg:_2016, dasgupta_design_2016, hutchison_fully_2010} and image processing operations under each scheme as an OpenCV library.
+While the scheme in \cite{ziad_cryptoimg:_2016} has been implemented for use in image processing, the fully homomorphic systems \cite{dasgupta_design_2016, hutchison_fully_2010} will have to be adapted for image processing.
+in The second part of the study consists of assessing the robustness and security of image operations under each encryption scheme using benchmarks in \cite{ahmed_benchmark_2016}.
 
@@
 Three homomorphic encryption schemes will be implemented, those presented by Ziad, et al.
-\cite{ziad_cryptoimg:_2016}, Li, et al.
-\cite{li_elliptic_2012} and Smart and Vercauteren \cite{hutchison_fully_2010}.
+\cite{ziad_cryptoimg:_2016}, Dasgupta and Pal \cite{dasgupta_design_2016} and Smart and Vercauteren \cite{hutchison_fully_2010}.
 The encryption and decryption methods will be implemented in C++.
@@
 	According to Ahmed, et al.
-\cite{ahmed_benchmark_2016}, PSNR is ``an estimator for human visual perception of reconstruction quality'' which is based on  It has been used to ascertain image quality in various studies and is a known meetric for image and video quality \cite{upmanyu_efficient_2009, jain_image_2016, akramullah_video_2014}.
+\cite{ahmed_benchmark_2016}, PSNR is ``an estimator for human visual perception of reconstruction quality''.
+It has been used to ascertain image quality in various studies and is a known metric for image and video quality \cite{upmanyu_efficient_2009, jain_image_2016, akramullah_video_2014}.
 Although it may produce results which do not correlate with human visual perception \cite{huynh-thu_accuracy_2012, ahmed_benchmark_2016}, it is a valid indicator of image quality when media containing the same visual content is compared \cite{huynh-thu_accuracy_2012}.
@@
 	\item An implementation of an OpenCV library which implements homomorphic cryptosystems by Ziad, et al.
-\cite{ziad_cryptoimg:_2016}, Li, et al.
-\cite{li_elliptic_2012} and Smart and Vercauteren \cite{hutchison_fully_2010}.
+\cite{ziad_cryptoimg:_2016}, Dasgupta and Pal \cite{dasgupta_design_2016} and Smart and Vercauteren \cite{hutchison_fully_2010}.
 	\item An implementation of image processing operations (intensity transformations, spatial filters) under the above cryptosystems.

### 2018-07-15 parts/01_introduction_01contextofstudy.tex
More revisions

@@
 
-Digital data privacy and security is a growing concern in various fields, such as cloud computing \cite{potey_homomorphic_2016}, health information systems \cite{kester_cryptographic_2015}, and video surveillance \cite{upmanyu_efficient_2009}.
+Digital data privacy and security is a growing concern in various fields, such as cloud computing~\cite{potey_homomorphic_2016}, health information systems~\cite{kester_cryptographic_2015}, and video surveillance~\cite{upmanyu_efficient_2009}.
 To meet these needs, various cryptosystems have been developed.
-A cryptosystem is a system which operates on plaintexts, ciphertexts and keys, and has an encryption algorithm, which maps a plaintext to a ciphertext, together with a decryption algorithm, which maps a ciphertext to a plaintext, given an appropriate key \cite{bauer_cryptosystem_2005}.
+A cryptosystem is a system which operates on plaintexts, ciphertexts and keys, and has an encryption algorithm, which maps a plaintext to a ciphertext, together with a decryption algorithm, which maps a ciphertext to a plaintext, given an appropriate key~\cite{bauer_cryptosystem_2005}.
 The encryption and decryption algorithms are chosen such that the plaintext cannot easily be recovered from the ciphertext without knowledge of the key.
@@
 One particular application of cryptography is image encryption.
-While cryptosystems used to encrypt digital data in general, such as the Advanced Encryption Standard (AES) or elliptic curve cryptography, can also be used to encrypt images \cite{jain_image_2016, singh_image_2015} other algorithms created specifically for image encryption have also been developed \cite{murugan_survey_2018}.
+While cryptosystems used to encrypt digital data in general, such as the Advanced Encryption Standard (AES) or elliptic curve cryptography, can also be used to encrypt images~\cite{jain_image_2016, singh_image_2015} other algorithms created specifically for image encryption have also been developed~\cite{murugan_survey_2018}.
 
@@
 These operations are then preserved when the data is decrypted.
-In this manner, data is manipulated without compromising data privacy, as the encrypted data being operated on remains secure \cite{fontaine_survey_2007, sen_homomorphic_2013}.
-While numerous homomorphic cryptosystems exist for use with digital data in general, in the area of homomorphic image encryption, there is additional interest in being able to perform image manipulation operations on the encrypted data such as image adjustment, filtering, and morphological/feature extraction operations \cite{ziad_cryptoimg:_2016, gonzalez_digital_2008}.
+In this manner, data is manipulated without compromising data privacy, as the encrypted data being operated on remains secure~\cite{fontaine_survey_2007, sen_homomorphic_2013}.
+While numerous homomorphic cryptosystems exist for use with digital data in general, in the area of homomorphic image encryption, there is additional interest in being able to perform image manipulation operations on the encrypted data such as image adjustment, filtering, and morphological/feature extraction operations~\cite{ziad_cryptoimg:_2016, gonzalez_digital_2008}.

### 2018-07-15 parts/01_introduction_03objectives.tex
More revisions

@@
 al.
-presents \textit{CryptoImg}, a library for the  Open Source Computer Vision Library (OpenCV) \cite{bradski_opencv_2000} which implements various homomorphic encryption and image processing routines using the Paillier homomorphic cryptosystem \cite{ziad_cryptoimg:_2016}.
-While \textit{CryptoImg} demonstrates that various image manipulation operations are possible in a homomorphic cryptosystem, we believe this study can be extended by considering other known homomorphic encryption schemes, such as those found in \cite{li_elliptic_2012, hutchison_fully_2010}.
+presents \textit{CryptoImg}, a library for the  Open Source Computer Vision Library (OpenCV)~\cite{bradski_opencv_2000} which implements various homomorphic encryption and image processing routines using the Paillier homomorphic cryptosystem~\cite{ziad_cryptoimg:_2016}.
+While \textit{CryptoImg} demonstrates that various image manipulation operations are possible in a homomorphic cryptosystem, we believe this study can be extended by considering other known homomorphic encryption schemes, such as those found in~\cite{li_elliptic_2012, hutchison_fully_2010}.
 Our study aims to provide an objective comparison of various homomorphic cryptosystems currently in the literature, as they would be used in encrypted image manipulation.
@@
 Our main research objective is to assess the practicality of various homomorphic cryptosystems in image encryption.
-Homomorphic cryptosystems are known to be slower in terms of encryption, operation, and decryption time \cite{sen_homomorphic_2013}.
-Furthermore, the operations on encrypted data supported by homomorphic cryptosystems are limited, and some schemes require preprocessing to be performed on images, limiting the range of operations which can be performed \cite{li_elliptic_2012}.
+Homomorphic cryptosystems are known to be slower in terms of encryption, operation, and decryption time~\cite{sen_homomorphic_2013}.
+Furthermore, the operations on encrypted data supported by homomorphic cryptosystems are limited, and some schemes require preprocessing to be performed on images, limiting the range of operations which can be performed~\cite{li_elliptic_2012}.
 Finally, as data security is the primary purpose of cryptosystems, we want to evaluate the security of homomorphic cryptosystems as image encryption schemes.

### 2018-07-15 parts/01_introduction_05scopeandlimitations.tex
More revisions

@@
 \begin{enumerate}
-	\item A modified version of the Paillier cryptosystem \cite{stern_public-key_1999} which supports floating-point operations, used in \textit{CryptoImg} \cite{ziad_cryptoimg:_2016}.
-	\item A fully homomorphic encryption scheme developed by Dasgupta and Pal, which uses polynomial rings \cite{dasgupta_design_2016}.
-	\item A fully homomorphic encryption scheme proposed by Smart and Vercauteren \cite{hutchison_fully_2010}, which is an improvement on the original lattice-based cryptosystem presented by Gentry \cite{gentry_fully_2009}.
+	\item A modified version of the Paillier cryptosystem~\cite{stern_public-key_1999} which supports floating-point operations, used in \textit{CryptoImg}~\cite{ziad_cryptoimg:_2016}.
+	\item A fully homomorphic encryption scheme developed by Dasgupta and Pal, which uses polynomial rings~\cite{dasgupta_design_2016}.
+	\item A fully homomorphic encryption scheme proposed by Smart and Vercauteren \cite{hutchison_fully_2010}, which is an improvement on the original lattice-based cryptosystem presented by Gentry~\cite{gentry_fully_2009}.
 \end{enumerate}
@@
 We will adopt the benchmark for evaluating the performance and security of image encryption schemes presented by Ahmed, et.
-al \cite{ahmed_benchmark_2016}.
-The presented benchmark reflects many tests used in other literature \cite{ahmad_efficiency_2012, wu_npcr_2011}.
+al~\cite{ahmed_benchmark_2016}.
+The presented benchmark reflects many tests used in other literature~\cite{ahmad_efficiency_2012, wu_npcr_2011}.
 \begin{enumerate}
-	\item Tests for preservation of image quality after encryption and decryption.
+	\item Tests for preservation of image quality after encryption and decryption
 	\begin{enumerate}
@@
 		\item Correlation coefficient analysis
-		\item Differential analysis (number of pixel change rate (NPCR), universal average change intensity (UACI))
+		\item Differential analysis
+        \begin{enumerate}
+            \item Number of Pixel Change Rate (NPCR)
+            \item Universal Average Change Intensity (UACI)
+        \end{enumerate}
 	\end{enumerate}
@@
 A detailed overview of the above will be provided in the methodology.
-Both greyscale and color images will be used in the study.
+Both grayscale and color images will be used in the study.
 

### 2018-07-15 parts/02_relatedliterature_02commonimageprocessingoperations.tex
More revisions

--- 2018-07-15 parts/02_relatedliterature_02commonimageprocessingoperations.tex
@@
 \subsection{Intensity Transformation}
-To define an intensity transformation on an image $I$, we define a function $T$ which maps a pixel value $r$ to a new value $r^\prime$, which we can write as $r^\prime = T\left(r\right)$.
-This function is then applied to every pixel in $A$.
+To define an intensity transformation on an image $R$, we define a function $T$ which maps a pixel value $r$ to a new value $r^\prime$, which we can write as $r^\prime = T\left(r\right)$.
+This function is then applied to every pixel in $R$.
 Examples of intensity transformations are image negation, log transformation, and power-law transformation.
@@
 where $c>0$ and $\gamma > 0$.
-This is especially useful since many image capture and output devices such as cameras, printers and displays follow a similar power law to relate physical percieved light intensity and digital pixel intensity values.
+This is especially useful since many image capture and output devices such as cameras, printers and displays follow a similar power law to relate physical perceived light intensity and digital pixel intensity values.
 A power-law transformation defined by the above equation can calibrate the operation on these devices in a process called \textit{gamma correction}.
@@
 
-In the CrytoImg software library, of the intensity transformations above, only image negation was implemented under a homomorphic cryptosystem \cite{ziad_cryptoimg}.
+In the \textit{CryptoImg} software library, of the intensity transformations above, only image negation was implemented under a homomorphic cryptosystem~\cite{ziad_cryptoimg:_2016}.
 To implement these intensity transformations using addition and multiplication in a homomorphic system, it is necessary to approximate the logarithm and exponential functions, which may result in higher computational overhead.
@@
 	R^\prime(3,4) &= \sum_{s=1}^m{\sum_{t=1}^n{k(s,t)R(3+s,4+t)}}\\
-	&= (0.0625\times 200) + (0.1250\times 249) + (0.0625\times 255) +\\
-	&(0.1250\times 143) + (0.2500\times 223) + (0.1250\times 255) +\\
-	&(0.0625\times 196) + (0.1250\times 236) + (0.0625\times 255)\\
+	&= (0.0625\times 200) + (0.1250\times 249) + (0.0625\times 255) \\
+	&+ (0.1250\times 143) + (0.2500\times 223) + (0.1250\times 255) \\
+	&+ (0.0625\times 196) + (0.1250\times 236) + (0.0625\times 255)\\
 	&= 223.
@@
 Since spatial filters take values from a contiguous region of pixels, this presents a difficulty in homomorphic cryptosytems: in order for spatial filters to be performed, the location of each pixel relative to neighboring pixels has to be preserved.
-This was performed in the implementation of spatial filters in the CryptoImg library \cite{ziad_cryptoimg}.
+This was performed in the implementation of spatial filters in the \textit{CryptoImg} library~\cite{ziad_cryptoimg:_2016}.
 We wish to implement spatial filters using a similar approach, and assess how preserving spatial correlation between pixels can impact the security of the encrypted image.
@@
 
-There are also spatial filters that perform image smoothing (such as Gaussian blur and box blur, which use the kernels $b_g$ and $b$ respectively in Equation~\ref{eqn:smooth-filters}) and image sharpening \cite{gonzalez_digital_2008}.
+There are also spatial filters that perform image smoothing (such as Gaussian blur and box blur, which use the kernels $b_g$ and $b$ respectively in Equation~\ref{eqn:smooth-filters}) and image sharpening~\cite{gonzalez_digital_2008}.
 \begin{equation}

### 2018-07-15 parts/01_introduction_04significanceofstudy.tex

@@
 
-This study aims to directly address one of the current problems in the research of homomorphic cryptosystems: the practicality of homomorphic encryption \cite{sen_homomorphic_2013}.
+This study aims to directly address one of the current problems in the research of homomorphic cryptosystems: the practicality of homomorphic encryption~\cite{sen_homomorphic_2013}.
 The literature shows existing homomorphic cryptosystems and how they support primitive operations (usually addition and multiplication) on encrypted data, however, for homomorphic cryptosystems to be useful for practical use, support for more complicated image processing operations such as image convolution must be demonstrated as well.
-While implementations of image processing operations in a homomorphic cryptosystem exist in the literature \cite{ziad_cryptoimg:_2016, garay_algorithms_2014}, our study targets algorithms for which statistical tests have not been performed for image processing operations.
+While implementations of image processing operations in a homomorphic cryptosystem exist in the literature~\cite{ziad_cryptoimg:_2016, garay_algorithms_2014}, our study targets algorithms for which statistical tests have not been performed for image processing operations.
 

### 2018-07-15 parts/02_relatedliterature.tex

@@
 Another related work would be the implementation of a fully homomorphic encryption.
-Halevi and Shoup \cite{garay_algorithms_2014} introduced \textit{HElib}, a library that implements the Brakerski-Gentry-Vaikuntanathan (BGV) homomorphic cryptosystem.
+Halevi and Shoup \cite{garay_algorithms_2014} introduced \textit{HElib}, a library that implements the Brakerski--Gentry--Vaikuntanathan (BGV) homomorphic cryptosystem.
 This library also makes use of various optimizations to speed up the homomorphic operations, due to homomorphic cryptosystems being slower than other cryptosystems \cite{sen_homomorphic_2013}.

### 2018-07-15 parts/02_relatedliterature_01homomorphiccryptosystems.tex
Revised 2.2.1

@@
 Since the public key and private keys are different, there is no need to agree upon secure key exchange protocols.
-Usually, the security of asymmetric-key cryptosystems relies on the intractability of certain computational problems, for example, the RSA cryptosystem depends on the difficulty of big integer factorization \cite{rivest_method_1978}, while the ElGamal cryptosystem depends on the difficulty of the discrete logarithm problem \cite{blakley_public_1985}.
+Usually, the security of asymmetric-key cryptosystems relies on the intractability of certain computational problems, for example, the RSA cryptosystem depends on the difficulty of big integer factorization~\cite{rivest_method_1978}, while the ElGamal cryptosystem depends on the difficulty of the discrete logarithm problem~\cite{blakley_public_1985}.
 
-Homomorphic cryptosystems are a special type of cryptosystem wherein operations can be securely performed on encrypted data.
+Homomorphic cryptosystems are a special type of cryptosystem in which operations can be securely performed on encrypted data.
 Suppose that for a public-key cryptosystem, $\mathcal{E}_k \left(p \right)$ is the encryption function using the public key $k \in \mathcal{K}$, and $\mathcal{D}_l \left(c \right)$ be the decryption function using the private key $l$.
@@
 \end{equation}
-where $p_1, p_2 \in \mathcal{P}$ are the plaintexts, and $\boxplus$ and $\boxdot$ are operations in $\mathcal{P}$ and $\mathcal{C}$ respectively \cite{fontaine_survey_2007}.
-Furthermore, a homomorphic cryptosystem also satisfies \cite{li_elliptic_2012}
+where $p_1, p_2 \in \mathcal{P}$ are the plaintexts, and $\boxplus$ and $\boxdot$ are operations in $\mathcal{P}$ and $\mathcal{C}$ respectively~\cite{fontaine_survey_2007}.
+Furthermore, a homomorphic cryptosystem also satisfies~\cite{li_elliptic_2012}
 \begin{equation}
@@
 If the plaintext operation $\boxplus$ is addition, the cryptosystem is said to be \textit{additively homomorphic}, and the cryptosystem is said to be \textit{multiplicatively homomorphic} if the plaintext operation $\boxplus$ is multiplication.
-Some examples of homomorphic cryptosystems include the Goldwasser-Micali cryptosystem \cite{goldwasser_probabilistic_1984} and the Paillier cryptosystem \cite{stern_public-key_1999}.
-Even some classic public-key cryptosystems are homomorphic, both RSA and ElGamal are multiplicatively homomorphic, while elliptic curve cryptosystems are additively homomorphic \cite{li_elliptic_2012}.
+Some examples of homomorphic cryptosystems include the Goldwasser--Micali cryptosystem~\cite{goldwasser_probabilistic_1984} and the Paillier cryptosystem~\cite{stern_public-key_1999}.
+Even some classic public-key cryptosystems are homomorphic, both RSA and ElGamal are multiplicatively homomorphic, while elliptic curve cryptosystems are additively homomorphic~\cite{li_elliptic_2012}.
 These cryptosystems, while relatively efficient, only support a limited set of operations on the encrypted data.
@@
 The first  fully homomorphic cryptosystem was presented by Gentry in 2009.
-Gentry's cryptosystem, which uses lattice-based cryptography, allows the computation of computation of arbitrary Boolean circuits on binary data \cite{gentry_fully_2009, shortell_secure_2016}.
-New algorithms based on Gentry's initial ideas have since been made \cite{ sen_homomorphic_2013}.
-One notable example is fully homomorphic cryptosystem by Smart and Vercauteren, \cite{hutchison_fully_2010}, later improved by Gentry and Halevi  \cite{hutchison_implementing_2011} which relies on cyclotomic number fields.
-In 2016, Dasgupta and Pal proposed a fully homomorphic cryptosystem based on polynomial rings \cite{dasgupta_design_2016}.
+Gentry's cryptosystem, which uses lattice-based cryptography, allows the computation of computation of arbitrary Boolean circuits on binary data~\cite{gentry_fully_2009, shortell_secure_2016}.
+New algorithms based on Gentry's initial ideas have since been made~\cite{ sen_homomorphic_2013}.
+One notable example is fully homomorphic cryptosystem by Smart and Vercauteren,~\cite{hutchison_fully_2010}, later improved by Gentry and Halevi ~\cite{hutchison_implementing_2011} which relies on cyclotomic number fields.
+In 2016, Dasgupta and Pal proposed a fully homomorphic cryptosystem based on polynomial rings~\cite{dasgupta_design_2016}.
 These two cryptosytems are examples of fully homomorphic cryptosystems which have significantly simpler encryption, decryption, addition and multiplication algorithms.

### 2018-07-15 parts/03_methodology.tex

--- 2018-06-26 parts/03_methodology.tex
@@
 
-The study consists of two parts: first, the implementation of the three homomorphic encryption schemes and image processing operations under each scheme as an OpenCV library.
-The second part of the study consists of assessing the robustness and security of image operations under each encryption scheme using benchmarks in \cite{ahmed_benchmark_2016}.
+The study consists of two parts: first, the implementation of the three homomorphic encryption schemes~\cite{ziad_cryptoimg:_2016, dasgupta_design_2016, hutchison_fully_2010} and image processing operations under each scheme as an OpenCV library.
+While the scheme in~\cite{ziad_cryptoimg:_2016} has been implemented for use in image processing, the fully homomorphic systems~\cite{dasgupta_design_2016, hutchison_fully_2010} will have to be adapted for image processing.
+The second part of the study consists of assessing the robustness and security of image operations under each encryption scheme using benchmarks in~\cite{ahmed_benchmark_2016}.
 
@@
 
-The current version of the OpenCV library (3.4.1) will be forked from the open-source GitHub repository at \url{https://github.com/opencv/opencv} \cite{bradski_opencv_2000}.
+The current version of the OpenCV library (3.4.2) will be forked from the open-source GitHub repository at \url{https://github.com/opencv/opencv}~\cite{bradski_opencv_2000}.
 
-Three homomorphic encryption schemes will be implemented, those presented by Ziad, et al.
-\cite{ziad_cryptoimg:_2016}, Li, et al.
-\cite{li_elliptic_2012} and Smart and Vercauteren \cite{hutchison_fully_2010}.
-The encryption and decryption methods will be implemented in C++.
+Three homomorphic encryption schemes will be implemented, those presented by Ziad, et al.~\cite{ziad_cryptoimg:_2016}, Dasgupta and Pal~\cite{dasgupta_design_2016} and Smart and Vercauteren~\cite{hutchison_fully_2010}.
+The encryption and decryption methods will be implemented in Python.
+However, these methods will be also implemented in C++ if time permits.
 
-Aside from implementing the homomorphic encryption and decryption algorithms, we will also implement library functions for the following image processing functions, as they are defined in \cite{gonzalez_digital_2008}.
+Aside from implementing the homomorphic encryption and decryption algorithms, we will also implement library functions for the following image processing functions, as they are defined in~\cite{gonzalez_digital_2008}.
 We will also take note of whether or not a candidate operation is impossible to perform under a given cryptosystem.
@@
 
-We will first obtain standard test images from \cite{gonzalez_image_nodate}. Both greyscale and color images will be used.
+We will first obtain standard test images from~\cite{gonzalez_image_nodate}. Both grayscale and color images will be used.
 
 For each plaintext image (PT), we will consider each image operation listed above and generate three images: a plaintext domain transformation (PDT), a ciphertext image (CT), and an encrypted domain transformation (EDT).
-The cipherThe PDT will be generated by running the image operation on the original image.
+The PDT will be generated by running the image operation on the original image.
 The CT will be generated by encrypting the image, then applying the operation, and the EDT will be generated by decrypting the CT.
@@
 
-Lab computers in Faura Hall, Ateneo de Manila University will be used to perform the computations, and processing time will be tracked using C++ timer functions.
+Lab computers in Faura Hall, Ateneo de Manila University will be used to perform the computations, and processing time will be tracked using built-in timing functions.
 The processing time for all cases will be recorded.
@@
 \subsection{Evaluating Image Quality}
-The benchmarks to be used in the study, adopted from \cite{ahmed_benchmark_2016, ahmad_efficiency_2012, wu_npcr_2011} are listed below.
+The benchmarks to be used in the study, adopted from~\cite{ahmed_benchmark_2016, ahmad_efficiency_2012, wu_npcr_2011} are listed below.
 We let $X_i$ denote a value in an image $X$, where $1 \leq i \leq N$.
@@
 \begin{description}
-	\item [Mean Squared Error (MSE).] The MSE is defined in \cite{ahmed_benchmark_2016} as
+	\item [Mean Squared Error (MSE).] The MSE is defined in~\cite{ahmed_benchmark_2016} as
 	\begin{align}
@@
 	The MSE provides a measure of how much data is recovered if an image operation is applied on the encrypted image, which is then decrypted.
-Lower values of MSE indicate higher preservation of image quality \cite{ahmed_benchmark_2016, ahmad_efficiency_2012}.
+Lower values of MSE indicate higher preservation of image quality~\cite{ahmed_benchmark_2016, ahmad_efficiency_2012}.
 	\item [Peak Signal to Noise Ratio (PSNR).]
-	According to Ahmed, et al.
-\cite{ahmed_benchmark_2016}, PSNR is ``an estimator for human visual perception of reconstruction quality'' which is based on  It has been used to ascertain image quality in various studies and is a known meetric for image and video quality \cite{upmanyu_efficient_2009, jain_image_2016, akramullah_video_2014}.
-Although it may produce results which do not correlate with human visual perception \cite{huynh-thu_accuracy_2012, ahmed_benchmark_2016}, it is a valid indicator of image quality when media containing the same visual content is compared \cite{huynh-thu_accuracy_2012}.
+	According to Ahmed, et al.~\cite{ahmed_benchmark_2016}, PSNR is ``an estimator for human visual perception of reconstruction quality.'' It has been used to ascertain image quality in various studies and is a known metric for image and video quality~\cite{upmanyu_efficient_2009, jain_image_2016, akramullah_video_2014}.
+Although it may produce results which do not correlate with human visual perception~\cite{huynh-thu_accuracy_2012, ahmed_benchmark_2016}, it is a valid indicator of image quality when media containing the same visual content is compared~\cite{huynh-thu_accuracy_2012}.
 	PSNR is defined by
@@
 	\item [Structural Similarity Index (SSIM).]
-	The SSIM for two random variables $X$ and $Y$ is defined in \cite{ahmed_benchmark_2016, akramullah_video_2014} as
+	The SSIM for two random variables $X$ and $Y$ is defined in~\cite{ahmed_benchmark_2016, akramullah_video_2014} as
 	\begin{align}
@@
 		\item $\sigma_{XY}$ is the covariance of $X$ and $Y$;
-		\item $c_1 = (k_1L)^2, c_2 = (k_2L)^2$ are two variables used to stabilize the measure when $\mu_X^2+\mu_Y^2$ is close to zero \cite{akramullah_video_2014};
+		\item $c_1 = (k_1L)^2, c_2 = (k_2L)^2$ are two variables used to stabilize the measure when $\mu_X^2+\mu_Y^2$ is close to zero~\cite{akramullah_video_2014};
 		\item $L$ is the the maximum pixel intensity value of an image;
-		\item $k_1 = 0.01, k_2 = 0.03$ by default, given in \cite{ahmed_benchmark_2016}.
+		\item $k_1 = 0.01, k_2 = 0.03$ by default, given in~\cite{ahmed_benchmark_2016}.
 	\end{itemize}
@@
     For the study, we will compute $\mathrm{SSIM}(\mathrm{PDT}, \mathrm{CDT})$ for every image operation, under each homomorphic cryptosystem.
-Higher values of SSIM indicate higher structural similarity, and an SSIM of 1 indicates that the two images are identical\cite{ahmed_benchmark_2016}.
+Higher values of SSIM indicate higher structural similarity, and an SSIM of $1$ indicates that the two images are identical~\cite{ahmed_benchmark_2016}.
 \end{description}
@@
 \subsection{Evaluating Cryptographic Security}
-After performing tests to evaluate image quality, we then perform tests for cryptographic security, as enumerated in \cite{ahmed_benchmark_2016}: entropy analysis, correlation coefficient analysis (CC), NPCR and UACI.
+After performing tests to evaluate image quality, we then perform tests for cryptographic security, as enumerated in~\cite{ahmed_benchmark_2016}: entropy analysis, correlation coefficient analysis (CC), NPCR and UACI.
 \begin{description}
-	\item [Information entropy analysis.] In information theory, the entropy function $H(X)$ is defined in \cite{bauer_information_2005} as
+	\item [Information entropy analysis.] In information theory, the entropy function $H(X)$ is defined in~\cite{bauer_information_2005} as
 	\begin{align}
@@
 	In the analysis of image encryption, $H(X)$ is computed for the values of the ciphertext pixels.
-To ensure security against entropy attacks, $H(X)$ must be as close as possible to $\log_2{N}$, where $N$ is the number of possible pixel values \cite{ahmed_benchmark_2016}.
+To ensure security against entropy attacks, $H(X)$ must be as close as possible to $\log_2{N}$, where $N$ is the number of possible pixel values~\cite{ahmed_benchmark_2016}.
 
@@
 		Images generally have a high degree of similarity between adjacent pixels. This correlation must be hidden in the encrypted image, even after performing image operations.
-		The correlation coefficient of an image can be computed between adjacent pixels either vertically, horizontal, or diagonally, and is defined in \cite{ahmed_benchmark_2016} by:
+		The correlation coefficient of an image can be computed between adjacent pixels either vertically, horizontal, or diagonally, and is defined in~\cite{ahmed_benchmark_2016} by:
 		\begin{align}
@@
 
-		The NPCR and UACI between two images $X$ and $Y$, each containing $N$ pixels indexed from $1$ to $N$ is defined in \cite{wu_npcr_2011} as
+		The NPCR and UACI between two images $X$ and $Y$, each containing $N$ pixels indexed from $1$ to $N$ is defined in~\cite{wu_npcr_2011} as
 		\begin{align}
@@
         We will calculate $\mathrm{NPCR}(\mathrm{PDT},\mathrm{CDT})$ and $\mathrm{UACI}(\mathrm{PDT},\mathrm{CDT})$  for every image operation, under each homomorphic cryptosystem.
-A high NPCR and UACI are desired to ensure high dispersion and security against differential attacks \cite{ahmed_benchmark_2016}.
-Critical values for NPCR and UACI for given image sizes and bit depths are given in  \cite{wu_npcr_2011}.
+A high NPCR and UACI are desired to ensure high dispersion and security against differential attacks~\cite{ahmed_benchmark_2016}.
+Critical values for NPCR and UACI for given image sizes and bit depths are given in~\cite{wu_npcr_2011}.
 \end{description}
@@
 \begin{itemize}
-	\item An implementation of an OpenCV library which implements homomorphic cryptosystems by Ziad, et al.
-\cite{ziad_cryptoimg:_2016}, Li, et al.
-\cite{li_elliptic_2012} and Smart and Vercauteren \cite{hutchison_fully_2010}.
+	\item An implementation of an OpenCV library which implements homomorphic cryptosystems by Ziad, et al.~\cite{ziad_cryptoimg:_2016}, Dasgupta and Pal~\cite{dasgupta_design_2016} and Smart and Vercauteren~\cite{hutchison_fully_2010}.
 	\item An implementation of image processing operations (intensity transformations, spatial filters) under the above cryptosystems.
-	\item Conducting tests for image quality, processing time, and cryptographic security, using standard test images from \cite{gonzalez_image_nodate}.
+	\item Conducting tests for image quality, processing time, and cryptographic security, using standard test images from~\cite{gonzalez_image_nodate}.
 \end{itemize}
 
-These will be conducted over the course of the first semester of AY 2018-2019 to allow for analysis of the results and paper preparation in the second semester.
+These will be conducted over the course of the first semester of AY 2018--2019 to allow for analysis of the results and paper preparation in the second semester.
 Additional cryptosystems, image operations, and cryptographic security tests may be included in the scope of the study, depending on future research.

### 2018-07-16 parts/01_introduction_01contextofstudy.tex
Final edits by Aldrich

@@
 To meet these needs, various cryptosystems have been developed.
-A cryptosystem is a system which operates on plaintexts, ciphertexts and keys, and has an encryption algorithm, which maps a plaintext to a ciphertext, together with a decryption algorithm, which maps a ciphertext to a plaintext, given an appropriate key~\cite{bauer_cryptosystem_2005}.
+A cryptosystem is a system which operates on plaintexts, ciphertexts and keys, using an encryption algorithm, which maps a plaintext to a ciphertext, together with a decryption algorithm, which maps a ciphertext to a plaintext, given an appropriate key~\cite{bauer_cryptosystem_2005}.
 The encryption and decryption algorithms are chosen such that the plaintext cannot easily be recovered from the ciphertext without knowledge of the key.

### 2018-07-16 parts/03_methodology.tex
Final edits by Aldrich
fixed typo, updated spatial filter graphic

@@
 	\end{enumerate}
-	\item[Spatial filters.] Filters implemented by performing a convolution between an $M\times N$ source image and an $m\times n$ filter matrix.
-Let $W$ be a filter matrix.
+	\item[Spatial filters.] Filters implemented by performing a convolution between an $M\times N$ source image and an $m\times n$ kernel.
+Let $k$ be a kernel.
 Then the corresponding spatial filter is given by
 	\begin{align}
-		S(x,y) = \sum_{s=1}^m{\sum_{t=1}^n{W(s,t)R(x+s,y+t)}}.
+		S(x,y) = \sum_{s=1}^m{\sum_{t=1}^n{k(s,t)R(x+s,y+t)}}.
 	\end{align}
@@
 
-We now provide a summary of how each of our reserch questions are addressed by the methodology.
+We now provide a summary of how each of our research questions are addressed by the methodology.
 \begin{itemize}

### 2018-07-16 parts/01_introduction_01contextofstudy.tex

@@
 To meet these needs, various cryptosystems have been developed.
-A cryptosystem is a system which operates on plaintexts, ciphertexts and keys, using an encryption algorithm, which maps a plaintext to a ciphertext, together with a decryption algorithm, which maps a ciphertext to a plaintext, given an appropriate key~\cite{bauer_cryptosystem_2005}.
+A cryptosystem is a system which operates on plaintexts, ciphertexts and keys using an encryption algorithm, which maps a plaintext to a ciphertext, together with a decryption algorithm, which maps a ciphertext to a plaintext, given an appropriate key~\cite{bauer_cryptosystem_2005}.
 The encryption and decryption algorithms are chosen such that the plaintext cannot easily be recovered from the ciphertext without knowledge of the key.

### 2018-07-16 parts/02_relatedliterature_02commonimageprocessingoperations.tex

@@
     \includegraphics[width=\textwidth,\keepaspectratio]{Figures/SpatialFilter.png}
-    \caption{(a) A sample image $R$. (b) A sample kernel $k$.}
+    \caption{A sample image $R$ and sample kernel $k$.}
     \label{fig:spatialfilter}
 \end{figure*}
-For example, using the image and kernel given in Figure \ref{fig:spatialfilter}, we can calculate the value in the third row and fourth column of the resulting image $R^\prime$ as follows:
+For example, using the image and $3 \times 3$ kernel given in Figure \ref{fig:spatialfilter}, we can calculate the value in the third row and fourth column of the resulting image $R^\prime$ by adding the products of entries in $k$ with the corresponding entries in $R$, found in an $3 \times 3$ region around $R(3,4)$.
 \begin{align*}
@@
 This works by detecting so-called \textit{edges}, areas that have abrupt changes in intensity.
-One common method of performing edge detection is the Sobel operator, which uses two spatial filters to approximate the gradient in an image. Given an image $R$, and the kernels
+One common method of performing edge detection is the Sobel operator, which uses two spatial filters to approximate the gradient of an image. Given an image $R$, and the kernels
 \begin{equation}

### 2018-09-18 parts/08_appendices_a_cryptosystems.tex
[WIP] algorithms and approximations
adding algorithm descriptions

%\section{Introduction to the Appendices}

%The Appendices is where you are enabled to present any additional or supplementary information relevant to your study, yet do not require highlighting within the actual paper, either because of its trivial nature or volume. These may in the form of figures, tables, or additional text detailing specific aspects about or related to the study.

%\section{Sample Questions for Different Studies}
%The following table presents three sample studies, as well as the guide questions that may help direct the discussion in each section of the paper. You may use this as another reference in writing your paper.

\section{Description of basic cryptosystems used}
\subsection{Pallier cryptosystem}
\subsection{Key generation}
We choose two large primes $p$ and $q$, and set $n = pq, \lambda = \mathrm\lcm(p-1,q-1)$.

Define the public key as $(g,n)$ and the private key
\begin{align*}
  E(m) = g^m \cdot r^n \mod{n^2}
\end{align*}
\subsection{Homomorphic properties}
For all $m_1,m_2 \in \mathbb{Z}_n$ and $k\in \mathbb{N}$, the following homomorphic properties hold.
\begin{description}
  \item[Additive homomorphism]
  \begin{align*}
    D(E(m_1)g^{m_2}\bmod n^2)=(m_1+m_2)\bmod n & \text{ (used to add a constant)}\\
    D(E(m_1)E(m_2)\bmod n^2)=(m_1+m_2)\bmod n & \text{ (used for binary addition)}
  \end{align*}
  \item[Multiplicative homomorphism]
  \begin{align*}
    D(E(m_1)^k\bmod n^2)= km_1\bmod n & \text{ (used to multiply a constant)}\\
    D(E(m_1)^{m_2}\bmod n^2)= m_1m_2\bmod n & \text{ (used for binary multiplication)}
  \end{align*}
\end{description}

### 2018-09-18 parts/08_appendices_b_numericalapproximations.tex
[WIP] algorithms and approximations
adding algorithm descriptions

%\section{Thesis Formatting Guidelines}

%This thesis template in Word document format was created to ensure that you will spend more time generating content for your paper and less time stressing about formatting issues. To ensure, however, that your document is truly formatted according to specifications, here are some formatting guidelines which you may use to evaluate your own paper’s formatting.

%\begin{enumerate}
%\item There should be NO PAGE NUMBERS on the first page of every chapter/section..
%\item Tables must have NO VERTICAL LINES, as well as NO INNER HORIZONTAL LINES after the table headers.
%\item Figures and tables are numbered ACCORDING TO CHAPTER NUMBER (e.g. Table 3.1 must be located in Chapter 3, and Figure B.2 is in Appendix B).
%\item The sequence of front matter must be as follows:
%    \begin{enumerate}
%    \item Title Page, in the correct formatting (e.g. Titles must be written in an inverted triangle, in ALL CAPS and boldface)
%    \item Abstract
%	\item Table of Contents
%	\item List of Figures
%	\item List of Tables
%	\end{enumerate}
%\item Upon binding, the front cover must contain the EXACT CONTENT AND FORMAT as that of your thesis’ title page.
%\end{enumerate}
\section{Numerical approximations}
In order to calculate a function under a additively and multiplicatively homomorphic cryptosystem, it is necessary to express the function in terms of addition and multiplication operations.
In this section, we discuss approximation for the logarithm ($\log(1+x)$) and power ($x^\gamma$) functions using only addition, subtraction, multiplication, and division operations.
\subsection{Approximation for $\log(1+x)$}

We approximate the function $f(x)=\log(1+x)$ using a similar method to that described in
\cite{khattri_new_2009}.
We consider the integral
\begin{align*}
  \int_{n}^{n+1}{\frac{1}{x}\diff x}=\log{(1+\frac{1}{n})}.
\end{align*}
This integral can be approximated using Legendre-Gauss quadrature.

\subsection{Approximation for $x^r$}
To approximate $x^r$ for any $r \in \mathbb{R}$, we rewrite $x^r$ as follows:
\begin{align*}
  x^\gamma = e^{\log{x^r}} = e^{r\log{x}}.
\end{align*}
This expression can then be approximated using the Taylor series expansion for $e^x$, which converges for all $x$.
\begin{align*}
  e^x &= \sum_{n=0}^{\infty}{\frac{x^n}{n!}}\\
  \Rightarrow e^{r\log{x}} &= \sum_{n=0}^{\infty}{\frac{(r\log{x})^n}{n!}}
\end{align*}
As we already have an approximation for the natural logarithm, we can evaluate partial sums of the above infinite series to arrive at approximations for $x^r$.

### 2018-09-23 parts/01_introduction_05scopeandlimitations.tex
[WIP] Numerical approximation section
Added work on numerical approximation, fixed appendix templates
Cleaned up some wording on Ch1

@@
 \begin{enumerate}
-	\item A modified version of the Paillier cryptosystem~\cite{stern_public-key_1999} which supports floating-point operations, used in \textit{CryptoImg}~\cite{ziad_cryptoimg:_2016}.
-	\item A fully homomorphic encryption scheme developed by Dasgupta and Pal, which uses polynomial rings~\cite{dasgupta_design_2016}.
-	\item A fully homomorphic encryption scheme proposed by Smart and Vercauteren \cite{hutchison_fully_2010}, which is an improvement on the original lattice-based cryptosystem presented by Gentry~\cite{gentry_fully_2009}.
+	\item A variant of the Paillier cryptosystem~\cite{stern_public-key_1999} which supports floating-point operations, used in \textit{CryptoImg}~\cite{ziad_cryptoimg:_2016}.
+	\item A fully homomorphic encryption scheme by Dasgupta and Pal, which uses polynomial rings~\cite{dasgupta_design_2016}.
+	\item A fully homomorphic encryption scheme by Smart and Vercauteren \cite{hutchison_fully_2010}, an improvement on the lattice-based cryptosystem by Gentry~\cite{gentry_fully_2009}.
 \end{enumerate}

### 2018-09-23 parts/08_appendices_a_cryptosystems.tex
[WIP] Numerical approximation section
Added work on numerical approximation, fixed appendix templates
Cleaned up some wording on Ch1

@@
 You may use this as another reference in writing your paper.
-
-\section{Description of basic cryptosystems used}
-\subsection{Pallier cryptosystem}
+\chapter{DESCRIPTION OF CRYPTOSYSTEMS}
+\section{Pallier cryptosystem}
 \subsection{Key generation}
-We choose two large primes $p$ and $q$, and set $n = pq, \lambda = \mathrm\lcm(p-1,q-1)$.
+We choose two large primes $p$ and $q$, and set $n = pq, \lambda = \mathrm{lcm}(p-1,q-1)$.
 
@@
 \end{description}
+\section{Performing real number operations using integer-based cryptosystems}

### 2018-09-23 parts/08_appendices_b_numericalapproximations.tex
[WIP] Numerical approximation section
Added work on numerical approximation, fixed appendix templates
Cleaned up some wording on Ch1

@@
 %\end{enumerate}
-\section{Numerical approximations}
+\chapter{NUMERICAL APPROXIMATIONS}
 In order to calculate a function under a additively and multiplicatively homomorphic cryptosystem, it is necessary to express the function in terms of addition and multiplication operations.
 In this section, we discuss approximation for the logarithm ($\log(1+x)$) and power ($x^\gamma$) functions using only addition, subtraction, multiplication, and division operations.
-\subsection{Approximation for $\log(1+x)$}
-
+%TODO: Explain why standard methods for transcedental function approximation cannot be applied here.
+%TODO: Include citations for this chapter
+\section{Approximation for $\log(1+x)$}
 We approximate the function $f(x)=\log(1+x)$ using a similar method to that described in
 \cite{khattri_new_2009}.
-We consider the integral
+We let $x = 1/n$ and consider the integral
 \begin{align*}
-  \int_{n}^{n+1}{\frac{1}{x}\diff x}=\log{(1+\frac{1}{n})}.
+  \int_{n}^{n+1}{\frac{1}{x}\diff x}=\log{\left(1+\frac{1}{n}\right)}.
 \end{align*}
-This integral can be approximated using Legendre-Gauss quadrature.
+This integral can be approximated using the five-point Gauss-Legendre quadrature rule, yielding the following approximation:
+\begin{equation}\label{eq:standardquadrature}
+  \log(1+x) =
+  \frac{137x^5 + 2310x^4 + 9870x^3 + 15120x^2 + 7560x}
+  {30x^5 + 900x^4 + 6300x^3 + 16800x^2 + 18900x + 7560}.
+\end{equation}
+While this closed form approximation is accurate for values of $x$ near zero, it diverges from $\log{(1+x)}$ significantly for large values of $x$.
+\begin{figure}[!ht]
+    \centering
+    \includegraphics[width=.6\linewidth,\keepaspectratio]{figures/StandardQuadrature.png}
+    \caption{Graph of $\log{(1+x)}$ and the approximation in equation \ref{eq:standardquadrature}}
+    \label{fig:standardquadrature}
+\end{figure}
+As we only need accuracy for $x \in [0, 255]$, we can scale up the approximation by a constant factor $\alpha$ as follows:
+\begin{align*}
+  \log{(1+x)} &= \log{\left(\frac{\alpha + \alpha x}{\alpha}\right)}\\
+  &= \log{(\alpha + \alpha x)} - \log{\alpha}\\
+  &= \log{\left(\alpha+\frac{\alpha}{n}\right)} - \log{\alpha}\\
+  &= \int_{\alpha n}^{\alpha+1}{\frac{1}{x}\diff x} - \log{\alpha}
+\end{align*}
 
-\subsection{Approximation for $x^r$}
+Using the five-point Gauss-Legendre quadrature rule with $\alpha = 1/20$, we arrive at the approximation:
+\begin{align}\label{eq:scaledquadrature}
+  \begin{split}
+    &\log(1+x) \\
+    &=\frac{137x^5 + 33185x^4 + 931370x^3 - 13403630x^2 - 289469315x - 713567363}
+    {30(x^5 + 505x^4 + 42010x^3 + 923010x^2 + 5722005x + 8040501)} + \log{20}
+  \end{split}
+\end{align}
+\section{Approximation for $x^r$}
 To approximate $x^r$ for any $r \in \mathbb{R}$, we rewrite $x^r$ as follows:
@@
 \end{align*}
-This expression can then be approximated using the Taylor series expansion for $e^x$, which converges for all $x$.
+This expression can then be approximated using the Maclaurin series expansion for $e^x$, which converges for all $x$.
 \begin{align*}

### 2018-09-24 parts/08_appendices_a_cryptosystems.tex
Added Pailler cryptosystem description
Added initial description of the Pailler cryptosystem and explained secure homomorphic exponentiation.

@@
 \section{Pallier cryptosystem}
-\subsection{Key generation}
+The Pallier cryptosystem \cite{stern_public-key_1999}, developed by Pascal Pallier, is a probabilistic encryption scheme which is based on the composite residuosity class problem.
+The scheme allows for the encryption and decryption of integer messages, and is known to be additively homomorphic.
+In this section, we state the encryption and decryption algorithms of the Pallier cryptosystem and state its homomorphic properties.
+\subsection{Description}
+We first define a function $L(x)$ as the largest integer $v$ greater than zero such that $x-1 \geq vn$.
 We choose two large primes $p$ and $q$, and set $n = pq, \lambda = \mathrm{lcm}(p-1,q-1)$.
+Then we select an integer $g$, $0\leq g \leq n^2$ such that $\mathrm{gcd}(L(g^\lambda \bmod n^2), n) = 1$.
+Define the public key as $(g,n)$ and the private key $(p,q)$.
+The encryption function to encrypt a plaintext $m \in \mathbb{Z}_n$ is defined as
+\begin{align*}
+  E(m) = g^m \cdot r^n \mod{n^2},
+\end{align*}
+where $r$ is a random non-negative integer less than $n^2$.
 
-Define the public key as $(g,n)$ and the private key
+The decryption function to decrypt a ciphertext $c \in \mathbb{Z}_{n^2}$ is defined as:
 \begin{align*}
-  E(m) = g^m \cdot r^n \mod{n^2}
+  D(c) = L(c^\lambda \bmod n^2) \times (L(g^\lambda \bmod n^2))^{-1} \mod n
 \end{align*}
+
 \subsection{Homomorphic properties}
+The Paillier cryptosystem supports additive homomorphism as well as the multiplication of a plaintext scalar to an encrypted message. These operations are defined as follows.
 For all $m_1,m_2 \in \mathbb{Z}_n$ and $k\in \mathbb{N}$, the following homomorphic properties hold.
@@
   \begin{align*}
-    D(E(m_1)^k\bmod n^2)= km_1\bmod n & \text{ (used to multiply a constant)}\\
-    D(E(m_1)^{m_2}\bmod n^2)= m_1m_2\bmod n & \text{ (used for binary multiplication)}
+    D(E(m_1)^k\bmod n^2)= km_1\bmod n & \text{ (used to multiply a plaintext constant)}
   \end{align*}
 \end{description}
-\section{Performing real number operations using integer-based cryptosystems}
+In order to implement some image operations covered in this study, we require the exponentiation of ciphertexts to integer powers, i.e. we require a function $f$ so that
+\begin{align*}
+	D(f(E(m))) = m^k\bmod n
+\end{align*}
+for any plaintext $m \in \mathbb{Z}_n$, and positive integer $k$.
+
+This is trivially feasible if $m^2 \bmod n$ and $E(m^2 \bmod n)$ are known, since one can use the following equation to raise $m$ to any positive integer power.
+\begin{align*}
+	D(E(m^k)^(m^2 \bmod n)\bmod n^2)= m^{k+2}\bmod n
+\end{align*}
+
+We now show that including $m^2 \bmod n$ and $E(m^2 \bmod n)$ in a transmitted message does not compromise the security of the Paillier cryptosystem.
+Clearly, $E(m^2 \bmod n)$ can be shared without compromising security, as it is an encrypted quantity.
+The quantity $m^2 \bmod n$ does not expose the value of $m$ as finding the value of $m \bmod n$ given $m^2 \bmod n$ is a problem equivalent in hardness to the factorization of large integers \cite{crandall_prime_2005}.

### 2018-09-24 parts/08_appendices_b_numericalapproximations.tex
Numerical approximation integral typo
Fixed a typo in the alpha integral
Added Pailler cryptosystem description
Added initial description of the Pailler cryptosystem and explained secure homomorphic exponentiation.

@@
 \chapter{NUMERICAL APPROXIMATIONS}
-In order to calculate a function under a additively and multiplicatively homomorphic cryptosystem, it is necessary to express the function in terms of addition and multiplication operations.
-In this section, we discuss approximation for the logarithm ($\log(1+x)$) and power ($x^\gamma$) functions using only addition, subtraction, multiplication, and division operations.
+Transcendental functions such as the exponential and logarithmic functions are usually implemented in computer hardware and software libraries using minimax polynomials, which are determined numerically using the Remez algorithm \cite{harrison_computation_1999}.
+However, the Remez algorithm relies on iteratively refining the polynomial coefficients, which requires knowledge of the argument passed to the exponential or logarithmic function.
+
+We cannot directly apply this approach in privacy-preserving image processing as we do not have knowledge of the exact value of the function arguments.
+In order to calculate a function under a  homomorphic cryptosystem, it is necessary to express the function in terms of the homomorphic operations.
+In this section, we discuss approximations for the logarithm ($\log(1+x)$) and power ($x^r$) functions using only addition, subtraction, multiplication, and division operations.
+.
+
 %TODO: Explain why standard methods for transcedental function approximation cannot be applied here.
@@
   &= \log{\left(\alpha+\frac{\alpha}{n}\right)} - \log{\alpha}\\
-  &= \int_{\alpha n}^{\alpha+1}{\frac{1}{x}\diff x} - \log{\alpha}
+  &= \log{\left(\frac{\alpha n + \alpha}{n}\right)} - \log{\alpha}\\
+  &= \int_{n}^{\alpha n + \alpha}{\frac{1}{x}\diff x} - \log{\alpha}
 \end{align*}
@@
 \end{align}
+
 \section{Approximation for $x^r$}

### 2018-09-25 parts/08_appendices_a_cryptosystems.tex
Added Benaloh cryptosystem
Added Benaloh cryptosystem to algorithm descriptions

@@
 \chapter{DESCRIPTION OF CRYPTOSYSTEMS}
-\section{Pallier cryptosystem}
+\section{The Pallier cryptosystem}
 The Pallier cryptosystem \cite{stern_public-key_1999}, developed by Pascal Pallier, is a probabilistic encryption scheme which is based on the composite residuosity class problem.
@@
 In this section, we state the encryption and decryption algorithms of the Pallier cryptosystem and state its homomorphic properties.
-\subsection{Description}
+\subsection{Key generation, encryption and decryption algorithms}
 We first define a function $L(x)$ as the largest integer $v$ greater than zero such that $x-1 \geq vn$.
@@
 Then we select an integer $g$, $0\leq g \leq n^2$ such that $\mathrm{gcd}(L(g^\lambda \bmod n^2), n) = 1$.
-Define the public key as $(g,n)$ and the private key $(p,q)$.
+We denote the public key as $(g,n)$ and the private key $(p,q)$.
 The encryption function to encrypt a plaintext $m \in \mathbb{Z}_n$ is defined as
@@
 The quantity $m^2 \bmod n$ does not expose the value of $m$ as finding the value of $m \bmod n$ given $m^2 \bmod n$ is a problem equivalent in hardness to the factorization of large integers \cite{crandall_prime_2005}.
+
+\section{The Benaloh cryptosystem}
+The Benaloh cryptosystem, initially proposed by Josh Benaloh in \cite{benaloh_dense_1994}, allows for the encryption of integers in $\mathbb{Z}_r$ for some odd integer $r$.
+We present here a corrected version by Fousse, et al.
+\cite{fousse_benalohs_2010} which corrects an error in the key generation algorithm which prevents accurate decryption in some cases.
+
+\subsection{Key generation, encryption and decryption algorithms}
+We choose an integer $r$ and two large primes $p$ and $q$ such that the following conditions hold:
+\begin{itemize}
+  \item $r$ divides $(p-1)$;
+  \item $\mathrm{gcd}(r,(p-1)/r)=1$;
+  \item $\mathrm{gcd}(r,q-1)=1$.
+\end{itemize}
+Next, let $n=pq$ and $\phi = (p-1)(q-1)$, and choose $y\in \mathbb{Z}_n^* = \{ x \in \mathbb{Z}_n | \mathrm{gcd}(x,n)=1 \}$ such that the following conditions hold:
+\begin{itemize}
+  \item $y^{\phi/r}\neq 1 \bmod n$;
+  \item For all prime factors $s$ of $r$, $y^{\phi/s}\neq 1 \bmod n$.
+\end{itemize}
+We denote the public key to be $(y,r,n)$ and the private key to be $(p,q)$.
+
+The encryption function to encrypt a plaintext $m \in \mathbb{Z}_r$ is defined as
+\begin{align*}
+  E(m) = y^m \cdot u^r \mod{n},
+\end{align*}
+where $u$ is a random integer in $\mathbb{Z}_n^*$.
+
+The decryption function to decrypt a ciphertext $c \in \mathbb{Z}_{n}$ is defined as:
+\begin{align*}
+  D(c) = \log_x{c^{\phi/r}} \mod n
+\end{align*}
+where $x = y^{\phi/r}$ and $\log_x{y} = k$ such that $x^k = y \bmod n$.
+
+Decryption requires the computation of the discrete logarithm, which can be done using a linear search when $r$ is small.
+For large values of $r$, the baby-step giant-step algorithm can be used to perform decryption in $O(\sqrt{r})$ time \cite{benaloh_dense_1994}.
+
+\subsection{Homomorphic properties}
+Similar to the Paillier cryptosystem, the Benaloh cryptosystem supports additive homomorphism as well as the multiplication of a plaintext scalar to an encrypted message.
+For all $m_1,m_2 \in \mathbb{Z}_r$ and $k\in \mathbb{N}$, the following homomorphic properties hold.
+\begin{description}
+  \item[Additive homomorphism]
+  \begin{align*}
+    D(E(m_1)y^{m_2}\bmod n^2)=(m_1+m_2)\bmod n & \text{ (used to add a constant)}\\
+    D(E(m_1)E(m_2)\bmod n^2)=(m_1+m_2)\bmod n & \text{ (used for binary addition)}
+  \end{align*}
+  \item[Multiplicative homomorphism]
+  \begin{align*}
+    D(E(m_1)^k\bmod n)= km_1\bmod n & \text{ (used to multiply a plaintext constant)}
+  \end{align*}
+\end{description}
+
+As the multiplicative homomorphism was not presented in the original paper, we provide a short proof here.
+\begin{proof}
+  Let $m \in \mathbb{Z}_r$ and $k\in \mathbb{N}$.
+  We consider $E(m)^k\bmod n = (y^m \cdot u^r \bmod{n})^k\bmod n$.
+  \begin{align*}
+    (y^m \cdot u^r \bmod{n})^k\bmod n
+    &= (y^m \cdot u^r)^k \bmod{n}\\
+    &= (y^m)^k \cdot (u^r)^k \bmod{n}\\
+    &= y^{km} \cdot (u^k)^r \bmod{n}\\
+    &= y^{km} \cdot (u^k \bmod{n})^r \bmod{n}
+  \end{align*}
+  Since $u$ is a random integer in $\mathbb{Z}_n^*$, $\mathrm{gcd}(u,n)=1$.
+  This implies $\mathrm{gcd}(u^k,n)=1$, so $u^k \bmod n$ is a random integer in $\mathbb{Z}_n^*$.
+  Therefore, $y^{km} \cdot (u^k \bmod{n})^r \bmod{n} = E(m)^k\bmod n$ is a valid encryption of the message $km$.
+\end{proof}

### 2018-09-25 parts/02_relatedliterature_03facialrecognition.tex
New section for facial recognition

\section{Facial Recognition}
More complex image processing operations are just made up of simpler image operations such as those mentioned earlier. 
A prominent application of image processing is facial recognition.

### 2018-09-26 parts/08_appendices_a_cryptosystems.tex
Added Dasgupta-Pal cryptosystem to appendix

@@
   \begin{align*}
-    D(E(m_1)g^{m_2}\bmod n^2)=(m_1+m_2)\bmod n & \text{ (used to add a constant)}\\
+    D(E(m_1)g^k\bmod n^2)=(m_1+k)\bmod n & \text{ (used to add a constant)}\\
     D(E(m_1)E(m_2)\bmod n^2)=(m_1+m_2)\bmod n & \text{ (used for binary addition)}
@@
 \begin{align*}
-	D(E(m^k)^(m^2 \bmod n)\bmod n^2)= m^{k+2}\bmod n
+	D(E(m^k)^{m^2 \bmod n}\bmod n^2) &= m^2m^k\bmod n \\
+	&= m^{k+2}\bmod n
 \end{align*}
@@
 The Benaloh cryptosystem, initially proposed by Josh Benaloh in \cite{benaloh_dense_1994}, allows for the encryption of integers in $\mathbb{Z}_r$ for some odd integer $r$.
+It relies on the hardness of the \textit{discrete logarithm problem}.
 We present here a corrected version by Fousse, et al.
@@
 \end{proof}
+
+\section{Dasgupta-Pal cryptosystem}
+The Dasgupta-Pal cryptosystem is a fully homomorphic cryptosystem proposed in 2016 by Smaranika Dasgupta and S.
+K.
+Pal \cite{dasgupta_design_2016}, which encrypts integer plaintexts in $\mathbb{Z}_n$ to polynomial ciphertexts.
+We begin our presentation of the Dasgupta-Pal cryptosystem with the following definition.
+
+Given a message $m \in \mathbb{n}$, we denote
+\begin{align*}
+		m_p(x) = a_0 + a_1x + a_2x^2 + \cdots + a_kx^k
+\end{align*}
+where $a_ka_{k-1}\cdots a_2a_1_0$ is the binary representation of $m$.
+\subsection{Key generation, encryption and decryption algorithms}
+Let $\ell$ denote the security parameter of the cryptosystem.
+Let $S_k$ be a prime number with $\ell$ bits.
+Choose a random even integer $z$ of length $\log_2{\ell}$.
+
+Let the secret key be $S_k$, and let the refresh key be $R_k = z \cdot S_k$. The secret key is kept private to the encrypting/decrypting parties, while the refresh key is made publicly available.
+
+The scheme defines the encryption algorithm for a message $m \in \mathbb{Z}_n$ as follows:
+\begin{align*}
+	E(m) = y(x) + S_k\times d(x)
+\end{align*}
+where
+$y(x)$ is a polynomial of degree $n$ such that $m_p(x) \equiv y(x) \bmod S_k$ and $d(x)$ is a randomly chosen polynomial of degree $n$.
+
+Furthermore, the decryption algorithm to recover $m_p(x)$ from a ciphertext polynomial $c(x)$ as
+\begin{align*}
+	m_p(x) = c(x) \bmod S_k \bmod 2
+\end{align*}
+Thus $D(c(x))$ is defined as the integer recovered from the coefficients of the polynomial $c(x) \bmod S_k \bmod 2$
+
+As a fully homomorphic cryptosystem, homomorphic operations on ciphertext introduce noise which may interfere with decryption.
+To eliminate noise from a polynomial ciphertext, the following refresh function is used.
+\begin{align*}
+	R(c(x)) = c(x) \bmod R_k
+\end{align*}
+
+\subsection{Homomorphic properties}
+It has been shown \cite{dasgupta_design_2016} that the following properties hold for all integer messages $m_1, m_2 \in \mathbb{Z}_n$ in the Dasgupta-Pal cryptosystem.
+\begin{description}
+  \item[Additive homomorphism]
+  \begin{align*}
+    D(E(m_1) + E(m_2))= m_1+m_2 & \text{ (used for binary addition)}
+  \end{align*}
+  \item[Multiplicative homomorphism]
+  \begin{align*}
+    D(E(m_1) \times E(m_2))= m_1 \times m_2 & \text{ (used for binary multiplication)}
+  \end{align*}
+\end{description}

### 2018-09-30 parts/01_introduction_02researchquestions.tex
[WIP] Restructuring RRL for midterms
Currently restructuring the RRL to accomodate algorithms, facial recognition.

@@
 
-More specifically, our research will address the following sub-research questions:
+More specifically, our research will address the following sub-questions:
 \begin{enumerate}
-	\item Which homomorphic cryptosystems admit more image processing operations?
+	\item Which homomorphic cryptosystems admit more image processing operations? How can existing homomorphic cryptosystems be modified to admit more image processing operations?
 	\item Which homomorphic cryptosystems are the most time-efficient in applying image processing operations?
-	\item Which homomorphic cryptosystems are the most secure under differential and entropy attacks?
+	\item Which homomorphic cryptosystems best preserve image quality in applying image processing operations? 
 \end{enumerate}

### 2018-09-30 parts/01_introduction_03objectives.tex
[WIP] Restructuring RRL for midterms
Currently restructuring the RRL to accomodate algorithms, facial recognition.

@@
 \begin{enumerate}
-    \item Compare the applicability of known homomorphic encryption schemes to common image processing operations, in other words, determine which schemes admit more image processing operations;
-		\item Compare the security of common image processing operations under known homomorphic encryption schemes, using established statistical methods in image encryption;
+    \item Compare the applicability of known homomorphic encryption schemes to common image processing operations, in other words, determine which schemes admit more image processing operations and extend known cryptosystems to support more operations, if possible;
     \item Compare the time efficiency of common image processing operations under known homomorphic encryption schemes;

### 2018-09-30 parts/01_introduction_05scopeandlimitations.tex
[WIP] Restructuring RRL for midterms
Currently restructuring the RRL to accomodate algorithms, facial recognition.

@@
 	\item A variant of the Paillier cryptosystem~\cite{stern_public-key_1999} which supports floating-point operations, used in \textit{CryptoImg}~\cite{ziad_cryptoimg:_2016}.
+	\item The Benlano cryptosystem~\cite{benaloh_dense_1994} which is a probabilistic cryptosystem which relies on the hardness of the discrete logarithm.
 	\item A fully homomorphic encryption scheme by Dasgupta and Pal, which uses polynomial rings~\cite{dasgupta_design_2016}.
@@
 \end{enumerate}
-We will adopt the benchmark for evaluating the performance and security of image encryption schemes presented by Ahmed, et.
+We will adopt the benchmark for evaluating image quality of image encryption schemes presented by Ahmed, et.
 al~\cite{ahmed_benchmark_2016}.
@@
 \begin{enumerate}
-	\item Tests for preservation of image quality after encryption and decryption
-	\begin{enumerate}
+	%\item Tests for preservation of image quality after encryption and decryption
+	%\begin{enumerate}
 		\item Mean Squared Error (MSE)
@@
 		\item Structural Similarity Index (SSIM)
-	\end{enumerate}
-	\item Tests for cryptographic security
-	\begin{enumerate}
-		\item Information entropy analysis
-		\item Correlation coefficient analysis
-		\item Differential analysis
-        \begin{enumerate}
-            \item Number of Pixel Change Rate (NPCR)
-            \item Universal Average Change Intensity (UACI)
-        \end{enumerate}
-	\end{enumerate}
+	%\end{enumerate}
+	%\item Tests for cryptographic security
+	%\begin{enumerate}
+	%	\item Information entropy analysis
+	%	\item Correlation coefficient analysis
+	%	\item Differential analysis
+  %      \begin{enumerate}
+  %          \item Number of Pixel Change Rate (NPCR)
+  %          \item Universal Average Change Intensity (UACI)
+  %      \end{enumerate}
+	%\end{enumerate}
 \end{enumerate}

### 2018-09-30 parts/02_relatedliterature.tex
[WIP] Restructuring RRL for midterms
Currently restructuring the RRL to accomodate algorithms, facial recognition.

--- 2018-07-15 parts/02_relatedliterature.tex
@@
 
-We first present an introduction to the concepts in cryptography, starting from the definition of a cryptosystem up to homomorphic encryption schemes, along with some examples from the literature.
-Then, we present some concepts in image processing, a suitable application of cryptography, specifically the common image operations used.
+We begin with an overview of image processing, in which we define the image processing operations we are interested in
+We first introduce concepts in cryptography and define homomorphic cryptosytems.
+along with some examples from the literature.
+Then, we present some concepts in , a suitable application of cryptography, specifically the common image operations used.
 Finally, we present related work that attempts to apply image processing operations with homomorphic cryptosystems, as well as their advantages and limitations.
 
-\input{parts/02_relatedliterature_01homomorphiccryptosystems}
-\input{parts/02_relatedliterature_02commonimageprocessingoperations}
-
-\section{Related Work and Previous Implementations}
-% CryptoImg
-
-% example of homomorphic encryption / image manipulation past work
-
-% minor limitation: improvement on previous work, but not a direct comparison
-
-% major limitation: does not discuss security: are modified images also secure?
-
-There has been work done regarding the application of homomorphic cryptosystems in image processing.
-In particular, Ziad, et al.
-introduced a library called \textit{CryptoImg} that uses the homomorphic properties of the Paillier cryptosystem to apply image operations securely \cite{ziad_cryptoimg:_2016}.
-This shows that it is indeed possible to do various image operations in a homomorphic cryptosystem.
-Ziad, et al.
-also showed experimental results establishing the slow performance of image operations uner a homomorphic cryptosystem.
-For instance, while sharpening and applying a Sobel filter each take less than a second when applied to a $512\times 512$ plaintext image, when applied to an encrypted image, sharpening required at least 238.257 seconds, and applying the Sobel filter required at least 147.567 seconds \cite{ziad_cryptoimg:_2016}.
-
-However, a major limitation of \textit{CryptoImg} is that it does not consider image security.
-Even though the authors have established that the Paillier cryptosystem itself cannot be broken \cite{ziad_cryptoimg:_2016}, we believe that a cryptanalysis of the encrypted images after they have been operated is necessary, since image operations may be considered additional information in a known plaintext attack.
-
-Furthermore, Ziad, et al.
-only presented a visual comparison and evaluation to establish the quality of the recovered images.
-We believe that additional image quality benchmarks, such as those presented in \cite{ahmed_benchmark_2016, ahmad_efficiency_2012}, would allow for quantitative comparisons of image quality.
-
-This study can be further improved by also considering the use of fully homomorphic cryptosystems such as the one presented by Dasgupta and Pal \cite{dasgupta_design_2016}, and the fully homomorphic cryptosystem introduced by Smart and Vercauteren \cite{hutchison_fully_2010} and improved by Gentry and Halevi  \cite{hutchison_implementing_2011}.
-These fully homomorphic cryptosytems have yet to be implemented for image processing operations.
-
-% HElib
-Another related work would be the implementation of a fully homomorphic encryption.
-Halevi and Shoup \cite{garay_algorithms_2014} introduced \textit{HElib}, a library that implements the Brakerski-Gentry-Vaikuntanathan (BGV) homomorphic cryptosystem.
-This library also makes use of various optimizations to speed up the homomorphic operations, due to homomorphic cryptosystems being slower than other cryptosystems \cite{sen_homomorphic_2013}.
+\input{parts/02_relatedliterature_01commonimageprocessingoperations}
+%facial recognition - theory
+\input{parts/02_relatedliterature_02homomorphiccryptosystems}
+\input{parts/02_relatedliterature_03partiallyhomomorphic}
+\input{parts/02_relatedliterature_04fullyhomomorphic}
+%facial recognition - implementation
+\input{parts/02_relatedliterature_05previousimplementations}
 

### 2018-09-30 parts/02_relatedliterature_01commonimageprocessingoperations.tex
[WIP] Restructuring RRL for midterms
Currently restructuring the RRL to accomodate algorithms, facial recognition.

--- 2018-07-16 parts/02_relatedliterature_02commonimageprocessingoperations.tex
@@
 In this study, we wish to see how the primitive operations of addition and multiplication supported by homomorphic cryptosystems can be applied to image processing operations.
-These operations are performed on digital images.
-We can represent a digital image $R$ as an $M \times N$ matrix of pixel intensity values, each value in the range $\left[0, L-1\right]$, for some positive integer $L$.
+We now present a list of basic operations performed on digital images.
+
+We represent a digital image $R$ as an $M \times N$ matrix of pixel intensity values, each value in the range $\left[0, L-1\right]$, for some positive integer $L$.
 There are two types of basic operations in image processing, intensity transformations, which map an intensity value to another, spatial filters which assist in operations such as edge detection and image blurring.
 
-\subsection{Intensity Transformation}
+\subsection{Intensity Transformations}
 To define an intensity transformation on an image $R$, we define a function $T$ which maps a pixel value $r$ to a new value $r^\prime$, which we can write as $r^\prime = T\left(r\right)$.

### 2018-09-30 parts/02_relatedliterature_02homomorphiccryptosystems.tex
[WIP] Restructuring RRL for midterms
Currently restructuring the RRL to accomodate algorithms, facial recognition.

--- 2018-07-15 parts/02_relatedliterature_01homomorphiccryptosystems.tex
@@
 \section{Homomorphic Cryptosystems}
-% [include mention of metrics by which they are compared]
 
@@
 On the other hand, asymmetric-key (or public-key) cryptosystems use separate keys for encryption and decryption.
-The encryption key (also called the \textit{public key}) is shared to everybody, while the decryption key (also called the \textit{private key}) is kept secret.
+The encryption key (also called the \textit{public key}) is shared publicly, while the decryption key (also called the \textit{private key}) is kept secret.
 Since the public key and private keys are different, there is no need to agree upon secure key exchange protocols.
@@
 
-Homomorphic cryptosystems are classified according to the plaintext and ciphertext operations, $\boxplus$ and $\boxdot$.
+Homomorphic cryptosystems can be classified according to the plaintext and ciphertext operations, $\boxplus$ and $\boxdot$.
 If the plaintext operation $\boxplus$ is addition, the cryptosystem is said to be \textit{additively homomorphic}, and the cryptosystem is said to be \textit{multiplicatively homomorphic} if the plaintext operation $\boxplus$ is multiplication.
-Some examples of homomorphic cryptosystems include the Goldwasser--Micali cryptosystem~\cite{goldwasser_probabilistic_1984} and the Paillier cryptosystem~\cite{stern_public-key_1999}.
+
+%Homomorphic cryptosystems
+%Some examples of homomorphic cryptosystems include the Goldwasser--Micali cryptosystem~\cite{goldwasser_probabilistic_1984} and the Paillier cryptosystem~\cite{stern_public-key_1999}.
 Even some classic public-key cryptosystems are homomorphic, both RSA and ElGamal are multiplicatively homomorphic, while elliptic curve cryptosystems are additively homomorphic~\cite{li_elliptic_2012}.
@@
 
-However, there exists \textit{fully homomorphic} cryptosystems, which are not limited to a fixed set of operations, but allow any arbitrary operations on the ciphertext.
+%However, there exists \textit{fully homomorphic} cryptosystems, which are not limited to a fixed set of operations, but allow any arbitrary operations on the ciphertext.
 The first  fully homomorphic cryptosystem was presented by Gentry in 2009.

### 2018-09-30 parts/02_relatedliterature_03partiallyhomomorphic.tex
[WIP] Restructuring RRL for midterms
Currently restructuring the RRL to accomodate algorithms, facial recognition.

--- 2018-09-25 parts/08_appendices_a_cryptosystems.tex
@@
-%\section{Introduction to the Appendices}
+\section{Partially homomorphic cryptosystems}
 
-%The Appendices is where you are enabled to present any additional or supplementary information relevant to your study, yet do not require highlighting within the actual paper, either because of its trivial nature or volume.
-These may in the form of figures, tables, or additional text detailing specific aspects about or related to the study.
+In this section, we will present two classical partially homomorphic cryptosystems which we will be testing in the study: the Pallier cryptosystem and the Benaloh cryptosystem.
+Both of these cryptosystems encrypt integer plaintexts and are additively homomorphic.
 
-%\section{Sample Questions for Different Studies}
-%The following table presents three sample studies, as well as the guide questions that may help direct the discussion in each section of the paper.
-You may use this as another reference in writing your paper.
-\chapter{DESCRIPTION OF CRYPTOSYSTEMS}
-\section{The Pallier cryptosystem}
+We will then show that the cryptosystems can be modified to support limited polynomial evaluation: given an encrypted message $m$, evaluate
+
+These operations
+\subsection{The Pallier cryptosystem}
 The Pallier cryptosystem \cite{stern_public-key_1999}, developed by Pascal Pallier, is a probabilistic encryption scheme which is based on the composite residuosity class problem.
 The scheme allows for the encryption and decryption of integer messages, and is known to be additively homomorphic.
-In this section, we state the encryption and decryption algorithms of the Pallier cryptosystem and state its homomorphic properties.
-\subsection{Key generation, encryption and decryption algorithms}
+We now state the encryption and decryption algorithms of the Pallier cryptosystem and its homomorphic properties.
+
+\subsubsection{Pallier cryptosystem description}
 We first define a function $L(x)$ as the largest integer $v$ greater than zero such that $x-1 \geq vn$.
@@
 We denote the public key as $(g,n)$ and the private key $(p,q)$.
-The encryption function to encrypt a plaintext $m \in \mathbb{Z}_n$ is defined as
+
+The encryption function to encrypt a plaintext $m \in \mathbb{Z}_n$ given a public key $(g,n)$ is defined as
 \begin{align*}
@@
 
-The decryption function to decrypt a ciphertext $c \in \mathbb{Z}_{n^2}$ is defined as:
+The decryption function to decrypt a ciphertext $c \in \mathbb{Z}_{n^2}$ given a private key $(p,q)$ is defined as:
 \begin{align*}
@@
 
-\subsection{Homomorphic properties}
+\subsubsection{Homomorphic Properties}
 The Paillier cryptosystem supports additive homomorphism as well as the multiplication of a plaintext scalar to an encrypted message. These operations are defined as follows.
@@
 
-\section{The Benaloh cryptosystem}
+\subsection{The Benaloh cryptosystem}
 The Benaloh cryptosystem, initially proposed by Josh Benaloh in \cite{benaloh_dense_1994}, allows for the encryption of integers in $\mathbb{Z}_r$ for some odd integer $r$.
+It relies on the hardness of the \textit{discrete logarithm problem}, and is a generalization of the classic Goldwasser--Micali cryptosystem~\cite{goldwasser_probabilistic_1984}.
 We present here a corrected version by Fousse, et al.
@@
 
-\subsection{Key generation, encryption and decryption algorithms}
+\subsubsection{Benaloh cryptosystem description}
 We choose an integer $r$ and two large primes $p$ and $q$ such that the following conditions hold:
@@
 
-\subsection{Homomorphic properties}
+\subsubsection{Homomorphic Properties}
 Similar to the Paillier cryptosystem, the Benaloh cryptosystem supports additive homomorphism as well as the multiplication of a plaintext scalar to an encrypted message.
@@
 \end{proof}
+
+Similar to the Paillier cryptosystem, we can include $m^2$ and $E(m^2)$ in the transmitted message

### 2018-09-30 parts/02_relatedliterature_05previousimplementations.tex
[WIP] Restructuring RRL for midterms
Currently restructuring the RRL to accomodate algorithms, facial recognition.

\section{Related Work and Previous Implementations}
% CryptoImg

% example of homomorphic encryption / image manipulation past work

% minor limitation: improvement on previous work, but not a direct comparison

% major limitation: does not discuss security: are modified images also secure?

There has been work done regarding the application of homomorphic cryptosystems in image processing. In particular, Ziad, et al. introduced a library called \textit{CryptoImg} that uses the homomorphic properties of the Paillier cryptosystem to apply image operations securely \cite{ziad_cryptoimg:_2016}. This shows that it is indeed possible to do various image operations in a homomorphic cryptosystem. Ziad, et al. also showed experimental results establishing the slow performance of image operations uner a homomorphic cryptosystem. For instance, while sharpening and applying a Sobel filter each take less than a second when applied to a $512\times 512$ plaintext image, when applied to an encrypted image, sharpening required at least 238.257 seconds, and applying the Sobel filter required at least 147.567 seconds \cite{ziad_cryptoimg:_2016}.

However, a major limitation of \textit{CryptoImg} is that it does not consider image security. Even though the authors have established that the Paillier cryptosystem itself cannot be broken \cite{ziad_cryptoimg:_2016}, we believe that a cryptanalysis of the encrypted images after they have been operated is necessary, since image operations may be considered additional information in a known plaintext attack.

Furthermore, Ziad, et al. only presented a visual comparison and evaluation to establish the quality of the recovered images. We believe that additional image quality benchmarks, such as those presented in \cite{ahmed_benchmark_2016, ahmad_efficiency_2012}, would allow for quantitative comparisons of image quality.

This study can be further improved by also considering the use of fully homomorphic cryptosystems such as the one presented by Dasgupta and Pal \cite{dasgupta_design_2016}, and the fully homomorphic cryptosystem introduced by Smart and Vercauteren \cite{hutchison_fully_2010} and improved by Gentry and Halevi  \cite{hutchison_implementing_2011}. These fully homomorphic cryptosytems have yet to be implemented for image processing operations.

% HElib
Another related work would be the implementation of a fully homomorphic encryption. Halevi and Shoup \cite{garay_algorithms_2014} introduced \textit{HElib}, a library that implements the Brakerski--Gentry--Vaikuntanathan (BGV) homomorphic cryptosystem. This library also makes use of various optimizations to speed up the homomorphic operations, due to homomorphic cryptosystems being slower than other cryptosystems \cite{sen_homomorphic_2013}.

### 2018-09-30 parts/03_methodology.tex
[WIP] Restructuring RRL for midterms
Currently restructuring the RRL to accomodate algorithms, facial recognition.

@@
 
-\subsection{Evaluating Cryptographic Security}
-After performing tests to evaluate image quality, we then perform tests for cryptographic security, as enumerated in~\cite{ahmed_benchmark_2016}: entropy analysis, correlation coefficient analysis (CC), NPCR and UACI.
-\begin{description}
-	\item [Information entropy analysis.] In information theory, the entropy function $H(X)$ is defined in~\cite{bauer_information_2005} as
-	\begin{align}
-		H(X) = - \sum_{a:p_X(a)>0}{p_X(a)\log_2{p_X(a)}}
-	\end{align}
-	where $p_X(a)$ denotes the probability that the random variable $X$ takes on the value $a$.
-	In the analysis of image encryption, $H(X)$ is computed for the values of the ciphertext pixels.
-To ensure security against entropy attacks, $H(X)$ must be as close as possible to $\log_2{N}$, where $N$ is the number of possible pixel values~\cite{ahmed_benchmark_2016}.
-
-    We will compute $H(\mathrm{CDT})$ for every image operation, under each homomorphic cryptosystem, and compare the effects of each image operation on the entropy of the encrypted image.
-Ideally, performing image operations on encrypted images should still maintain a high level of entropy.
-	\item [Correlation coefficient analysis (CC).]
-		Images generally have a high degree of similarity between adjacent pixels. This correlation must be hidden in the encrypted image, even after performing image operations.
-		The correlation coefficient of an image can be computed between adjacent pixels either vertically, horizontal, or diagonally, and is defined in~\cite{ahmed_benchmark_2016} by:
-		\begin{align}
-            \mathrm{CC}(X,Y) = \frac{\sigma_{X,Y}}{\sqrt{\sigma_X}\times\sqrt{\sigma_Y}}
-		\end{align}
-		where
-		\begin{itemize}
-			\item $\sigma_X, \sigma_Y$ are the variances of $X$ and $Y$, respectively;
-			\item $\sigma_{XY}$ is the covariance of $X$ and $Y$.
-		\end{itemize}
-
-        For every $\mathrm{CDT}$ image, we will compute for the correlation coefficient (for vertical, horizontal and diagonal correlation) for every image operation, under each homomorphic cryptosystem.
-	\item [NPCR and UACI.]
-		The Number of Pixel Change Rate (NPCR) measures the number of pixels which are changed between the a plaintext and a ciphertext to quantify the amount of dispersion which occurs during encryption.
-
-		On the other hand, the Universal Average Change Intensity (UACI) measures the average difference in pixel intensity between two images.
-
-		The NPCR and UACI between two images $X$ and $Y$, each containing $N$ pixels indexed from $1$ to $N$ is defined in~\cite{wu_npcr_2011} as
-		\begin{align}
-            \mathrm{NPCR}(X,Y) &= \frac{1}{N}\sum_{i = 1}^{N}{D(X_i,Y_i)} \times 100\%\\
-            \mathrm{UACI}(X,Y) &= \frac{1}{L_{\max} \times N} \sum_{i = 1}^{N}{ |L(X_i) - L(Y_i)| } \times 100\%
-		\end{align}
-		where
-		\begin{itemize}
-			\item $X_i$ and $Y_i$ are the $i$th pixels of $X$ and $Y$, respectively;
-			\item $D$ is a difference function between pixels $A$ and $B$ defined by
-			\begin{align}
-				D(A,B) =
-				\begin{cases}
-					0 &  \text{if $A = B$},\\
-					1 &  \text{if $A \neq B$};
-				\end{cases}
-			\end{align}
-		\item $L_{\max}$ is the maximum intensity of a pixel;
-		\item $L(X_i)$ and $L(Y_i)$ are the intensities of pixels $X_i$ and $Y_i$, respectively.
-		\end{itemize}
-        We will calculate $\mathrm{NPCR}(\mathrm{PDT},\mathrm{CDT})$ and $\mathrm{UACI}(\mathrm{PDT},\mathrm{CDT})$  for every image operation, under each homomorphic cryptosystem.
-A high NPCR and UACI are desired to ensure high dispersion and security against differential attacks~\cite{ahmed_benchmark_2016}.
-Critical values for NPCR and UACI for given image sizes and bit depths are given in~\cite{wu_npcr_2011}.
-\end{description}
-
 \section{Summary}
@@
 	\item An implementation of image processing operations (intensity transformations, spatial filters) under the above cryptosystems.
-	\item Conducting tests for image quality, processing time, and cryptographic security, using standard test images from~\cite{gonzalez_image_nodate}.
+	\item Conducting tests for image quality, processing time, using standard test images from~\cite{gonzalez_image_nodate}.
 \end{itemize}

### 2018-09-30 parts/08_appendices_a_cryptosystems.tex
[WIP] Restructuring RRL for midterms
Currently restructuring the RRL to accomodate algorithms, facial recognition.

--- 2018-09-24 parts/08_appendices_a_cryptosystems.tex
@@
 \chapter{DESCRIPTION OF CRYPTOSYSTEMS}
-\section{Pallier cryptosystem}
-The Pallier cryptosystem \cite{stern_public-key_1999}, developed by Pascal Pallier, is a probabilistic encryption scheme which is based on the composite residuosity class problem.
-The scheme allows for the encryption and decryption of integer messages, and is known to be additively homomorphic.
-In this section, we state the encryption and decryption algorithms of the Pallier cryptosystem and state its homomorphic properties.
-\subsection{Description}
-We first define a function $L(x)$ as the largest integer $v$ greater than zero such that $x-1 \geq vn$.
-We choose two large primes $p$ and $q$, and set $n = pq, \lambda = \mathrm{lcm}(p-1,q-1)$.
-Then we select an integer $g$, $0\leq g \leq n^2$ such that $\mathrm{gcd}(L(g^\lambda \bmod n^2), n) = 1$.
-Define the public key as $(g,n)$ and the private key $(p,q)$.
-The encryption function to encrypt a plaintext $m \in \mathbb{Z}_n$ is defined as
+
+\section{Dasgupta-Pal cryptosystem}
+The Dasgupta-Pal cryptosystem is a fully homomorphic cryptosystem proposed in 2016 by Smaranika Dasgupta and S.
+K.
+Pal \cite{dasgupta_design_2016}, which encrypts integer plaintexts in $\mathbb{Z}_n$ to polynomial ciphertexts.
+We begin our presentation of the Dasgupta-Pal cryptosystem with the following definition.
+
+Given a message $m \in \mathbb{n}$, we denote
 \begin{align*}
-  E(m) = g^m \cdot r^n \mod{n^2},
+		m_p(x) = a_0 + a_1x + a_2x^2 + \cdots + a_kx^k
 \end{align*}
-where $r$ is a random non-negative integer less than $n^2$.
+where $a_ka_{k-1}\cdots a_2a_1_0$ is the binary representation of $m$.
+\subsection{Key generation, encryption and decryption algorithms}
+Let $\ell$ denote the security parameter of the cryptosystem.
+Let $S_k$ be a prime number with $\ell$ bits.
+Choose a random even integer $z$ of length $\log_2{\ell}$.
 
-The decryption function to decrypt a ciphertext $c \in \mathbb{Z}_{n^2}$ is defined as:
+Let the secret key be $S_k$, and let the refresh key be $R_k = z \cdot S_k$. The secret key is kept private to the encrypting/decrypting parties, while the refresh key is made publicly available.
+
+The scheme defines the encryption algorithm for a message $m \in \mathbb{Z}_n$ as follows:
 \begin{align*}
-  D(c) = L(c^\lambda \bmod n^2) \times (L(g^\lambda \bmod n^2))^{-1} \mod n
+	E(m) = y(x) + S_k\times d(x)
+\end{align*}
+where
+$y(x)$ is a polynomial of degree $n$ such that $m_p(x) \equiv y(x) \bmod S_k$ and $d(x)$ is a randomly chosen polynomial of degree $n$.
+
+Furthermore, the decryption algorithm to recover $m_p(x)$ from a ciphertext polynomial $c(x)$ as
+\begin{align*}
+	m_p(x) = c(x) \bmod S_k \bmod 2
+\end{align*}
+Thus $D(c(x))$ is defined as the integer recovered from the coefficients of the polynomial $c(x) \bmod S_k \bmod 2$
+
+As a fully homomorphic cryptosystem, homomorphic operations on ciphertext introduce noise which may interfere with decryption.
+To eliminate noise from a polynomial ciphertext, the following refresh function is used.
+\begin{align*}
+	R(c(x)) = c(x) \bmod R_k
 \end{align*}
@@
 \subsection{Homomorphic properties}
-The Paillier cryptosystem supports additive homomorphism as well as the multiplication of a plaintext scalar to an encrypted message. These operations are defined as follows.
-For all $m_1,m_2 \in \mathbb{Z}_n$ and $k\in \mathbb{N}$, the following homomorphic properties hold.
+It has been shown \cite{dasgupta_design_2016} that the following properties hold for all integer messages $m_1, m_2 \in \mathbb{Z}_n$ in the Dasgupta-Pal cryptosystem.
 \begin{description}
@@
   \begin{align*}
-    D(E(m_1)g^{m_2}\bmod n^2)=(m_1+m_2)\bmod n & \text{ (used to add a constant)}\\
-    D(E(m_1)E(m_2)\bmod n^2)=(m_1+m_2)\bmod n & \text{ (used for binary addition)}
+    D(E(m_1) + E(m_2))= m_1+m_2 & \text{ (used for binary addition)}
   \end{align*}
@@
   \begin{align*}
-    D(E(m_1)^k\bmod n^2)= km_1\bmod n & \text{ (used to multiply a plaintext constant)}
+    D(E(m_1) \times E(m_2))= m_1 \times m_2 & \text{ (used for binary multiplication)}
   \end{align*}
 \end{description}
-In order to implement some image operations covered in this study, we require the exponentiation of ciphertexts to integer powers, i.e. we require a function $f$ so that
-\begin{align*}
-	D(f(E(m))) = m^k\bmod n
-\end{align*}
-for any plaintext $m \in \mathbb{Z}_n$, and positive integer $k$.
-
-This is trivially feasible if $m^2 \bmod n$ and $E(m^2 \bmod n)$ are known, since one can use the following equation to raise $m$ to any positive integer power.
-\begin{align*}
-	D(E(m^k)^(m^2 \bmod n)\bmod n^2)= m^{k+2}\bmod n
-\end{align*}
-
-We now show that including $m^2 \bmod n$ and $E(m^2 \bmod n)$ in a transmitted message does not compromise the security of the Paillier cryptosystem.
-Clearly, $E(m^2 \bmod n)$ can be shared without compromising security, as it is an encrypted quantity.
-The quantity $m^2 \bmod n$ does not expose the value of $m$ as finding the value of $m \bmod n$ given $m^2 \bmod n$ is a problem equivalent in hardness to the factorization of large integers \cite{crandall_prime_2005}.

### 2018-10-05 parts/02_relatedliterature.tex
Finalized new ordering of RRL
Restructured RRL to accomodate facial recognition

@@
 
-We begin with an overview of image processing, in which we define the image processing operations we are interested in
-We first introduce concepts in cryptography and define homomorphic cryptosytems.
-along with some examples from the literature.
-Then, we present some concepts in , a suitable application of cryptography, specifically the common image operations used.
-Finally, we present related work that attempts to apply image processing operations with homomorphic cryptosystems, as well as their advantages and limitations.
+We will now provide an overview of the \textit{CryptoImg} project, which our study is primarily based on.
+Then, we define the image processing operations we are interested in implementing in this study and
+After establishing our desired image processing operations, introduce concepts in cryptography and define the four homomorphic cryptosystems we will be testing in the study.
 
-\input{parts/02_relatedliterature_01commonimageprocessingoperations}
+\input{parts/02_relatedliterature_01cryptoimg}
+\input{parts/02_relatedliterature_02commonimageprocessingoperations}
 %facial recognition - theory
-\input{parts/02_relatedliterature_02homomorphiccryptosystems}
-\input{parts/02_relatedliterature_03partiallyhomomorphic}
-\input{parts/02_relatedliterature_04fullyhomomorphic}
+\input{parts/02_relatedliterature_03facialrecognition}
+\input{parts/02_relatedliterature_04homomorphiccryptosystems}
+\input{parts/02_relatedliterature_05partiallyhomomorphic}
+\input{parts/02_relatedliterature_06fullyhomomorphic}
 %facial recognition - implementation
-\input{parts/02_relatedliterature_05previousimplementations}
+\input{parts/02_relatedliterature_07previousimplementations}
 

### 2018-10-05 parts/02_relatedliterature_01cryptoimg.tex
Finalized new ordering of RRL
Restructured RRL to accomodate facial recognition

\section{CryptoImg}
A recent attempt in the literature to implement privacy-preserving image processing is the \textit{CryptoImg} software library, presented by Ziad, et al. in 2016 \cite{ziad_cryptoimg:_2016}. The CryptoImg library assumed a client-server model wherein a client requests image processing operations from a server. A client first encrypts a digital image and sends the image securely to a server, which then operates on the encrypted image without revealing its contents. Then the resulting image is sent back to the client, which decrypts the image to recover the desired output.
\begin{figure*}[!ht]
    \centering
    \includegraphics[width=\textwidth,\keepaspectratio]{Figures/ClientServerModel.png}
    \caption{Client-server architecture used by \textit{CryptoImg} \cite{ziad_cryptoimg:_2016}}
    \label{fig:clientserver}
\end{figure*}
The CryptoImg library implemented the following:
\begin{enumerate}
	\item Extending the Paillier homomorphic cryptosystem which operate on integer plaintexts so that they can operate on real number plaintexts;
	\item Developing protocols for and implementing the following image processing operations
	\begin{enumerate}
		\item Image negation and brightness adjustment
		\item Spatial filters (for noise reduction, edge detection and sharpening)
		\item Morphological operations
		\item Histogram equalization
	\end{enumerate}
\end{enumerate}
For image negation and spatial filters, the protocols specified by CryptoImg allow all image processing operations to be performed on the server. However, due to limitations in the Pallier cryptosystem, the protocols presented for morphological operations and histogram equalization require both the client and the server to perform image processing calculations, although the server performs a significant portion of the processing.

Ziad, et al. also showed experimental results establishing the slow performance of image operations under a homomorphic cryptosystem. For instance, while sharpening and applying a Sobel filter each take less than a second when applied to a $512\times 512$ plaintext image, when applied to an encrypted image, sharpening required at least 238.257 seconds, and applying the Sobel filter required at least 147.567 seconds \cite{ziad_cryptoimg:_2016}.

%%limitations = not considering transcendental function evaluation
%%extension to fully homomorphic cryptosystems
%%combined applications in face detection and recognition

We now discuss several limitations in the \textit{CryptoImg} study which we focus on for our research. First, the \textit{CryptoImg} library was limited in the image intensity transformations it implemented. We propose additional protocols to support more computationally intensive intensity transformations.
Second, the \textit{CryptoImg} library only considered the Pallier cryptosystem. We consider testing the performance of other homomorphic cryptosystems, which differ in their processing time and supported operations.

### 2018-10-05 parts/02_relatedliterature_02commonimageprocessingoperations.tex
Finalized new ordering of RRL
Restructured RRL to accomodate facial recognition

@@
-\section{Common Image Operations}
-In this study, we wish to see how the primitive operations of addition and multiplication supported by homomorphic cryptosystems can be applied to image processing operations.
-These operations are performed on digital images.
-We can represent a digital image $R$ as an $M \times N$ matrix of pixel intensity values, each value in the range $\left[0, L-1\right]$, for some positive integer $L$.
-There are two types of basic operations in image processing, intensity transformations, which map an intensity value to another, spatial filters which assist in operations such as edge detection and image blurring.
+\section{Image Processing Operations}
+The \textit{CryptoImg} library implemented several
+We discuss two basic types of image processing operations, \textit{intensity transformations}, which map an intensity value to another, and \textit{spatial filters} which consider intensity values from regions of pixels to perform operations such as edge detection, image blurring and sharpening.
 
-\subsection{Intensity Transformation}
-To define an intensity transformation on an image $R$, we define a function $T$ which maps a pixel value $r$ to a new value $r^\prime$, which we can write as $r^\prime = T\left(r\right)$.
+We represent a digital image $R$ as an $M \times N$ matrix of pixel intensity values, each value in the range $\left[0, L-1\right]$, for some positive integer $L$.
+We use $R(x,y)$ represents the entry at the $x$th row and $y$th column of a matrix $R$.
+
+\subsection{Intensity Transformations}
+An Intensity transformation on an image $R$ can be defined as a function $T$ which maps a pixel value $r$ to a new value $r^\prime$, which we can write as $r^\prime = T\left(r\right)$.
 This function is then applied to every pixel in $R$.
-Examples of intensity transformations are image negation, log transformation, and power-law transformation.
 
-Image negation is an example of an intensity transformation, where the resulting image would be similar to a photographic negative~\cite{gonzalez_digital_2008}.
-An image negation operation is defined as:
+The \textit{CryptoImg} library implemented two types of linear intensity transformations: image negation and brightness control.
+An image negation transformation is defined as:
 \begin{equation}
@@
 \end{equation}
+After applying image negation, the resulting image would be similar to a photographic negative~\cite{gonzalez_digital_2008}.
+
+A brightness control transformation with parameter $v$ is defined as:
+\begin{equation}
+    T\left(r,v\right) = r+v
+\end{equation}
+The above transformations are linear in terms of the input $r$, and are thus simple to implement under a homomorphic cryptosystem.
+
+In this study we extend the range of intensity transformations to non-linear transformations.
+Two common non-linear image transformations are the log transformation and power-law transformation~\cite{gonzalez_digital_2008}.
 
 The log transformation is used to enhance dark pixels or increase the dark details of an image by mapping low intensity values to a wider range of values~\cite{gonzalez_digital_2008}.
-This has the general form
+This has the general formula
 \begin{equation}
@@
 where $c>0$ and $\gamma > 0$.
-This is especially useful since many image capture and output devices such as cameras, printers and displays follow a similar power law to relate physical perceived light intensity and digital pixel intensity values.
-A power-law transformation defined by the above equation can calibrate the operation on these devices in a process called \textit{gamma correction}.
-This ensures reproducibility and accuracy of images being displayed~\cite{gonzalez_digital_2008}.
+A power-law transformation defined by the above equation can calibrate the operation of many image capture and output devices such as cameras, printers and displays in a process called \textit{gamma correction}.
+This ensures reproducibility and accuracy of images being displayed by digital output devices~\cite{gonzalez_digital_2008}.
 
-In the \textit{CryptoImg} software library, of the intensity transformations above, only image negation was implemented under a homomorphic cryptosystem~\cite{ziad_cryptoimg:_2016}.
-To implement these intensity transformations using addition and multiplication in a homomorphic system, it is necessary to approximate the logarithm and exponential functions, which may result in higher computational overhead.
-In our software library implementation, we aim to investigate the overhead required to approximate these functions.
+To implement non-linear intensity transformations using addition and multiplication in a homomorphic system, it is necessary to approximate the logarithm and exponential functions, which may result in higher computational overhead.
+In our software library implementation, we investigate methods required to approximate the logarithm and functions.
 
 \subsection{Spatial Filtering}
-Many common image operations are expressed as \textit{spatial filters}.
+The \textit{CryptoImg} library also implemented \textit{spatial filters}.
 Spatial filters are operators which determine output pixels using information from neighboring input pixels.
@@
 \end{align}
-where $A(x,y)$ represents the entry at the $x$th row and $y$th column of a matrix $A$.
 
@@
 \end{equation}
-% Should I put a table of other kernels too?
+
+%% TODO: specific list of kernels to use for this study

### 2018-10-05 parts/02_relatedliterature_04homomorphiccryptosystems.tex
Completed intensity transformations
Completed RRL, methodology and appendix sections on intensity transformations.
Fixed some typos.

--- 2018-09-30 parts/02_relatedliterature_02homomorphiccryptosystems.tex
@@
 
-In cryptography, a cryptosystem consists of an encryption function $\mathcal{E}$ and a decryption function $\mathcal{D}$, along with the plaintext space $\mathcal{P}$, ciphertext space $\mathcal{C}$ and the key space $\mathcal{K}$~\cite{bauer_cryptosystem_2005}.
+Now that we've established the image processing operations we wish to implement, we now discuss the homomorphic cryptosystems we will be using to implement privacy-preserving image processing.
+
+A cryptosystem consists of an encryption function $\mathcal{E}$ and a decryption function $\mathcal{D}$, along with the plaintext space $\mathcal{P}$, ciphertext space $\mathcal{C}$ and the key space $\mathcal{K}$~\cite{bauer_cryptosystem_2005}.
 A \textit{plaintext} is text that can be commonly understood, while a \textit{ciphertext} results from encrypting the plaintext using an encryption key.
@@
 In 2016, Dasgupta and Pal proposed a fully homomorphic cryptosystem based on polynomial rings~\cite{dasgupta_design_2016}.
-These two cryptosytems are examples of fully homomorphic cryptosystems which have significantly simpler encryption, decryption, addition and multiplication algorithms.
+These two cryptosystems are examples of fully homomorphic cryptosystems which have significantly simpler encryption, decryption, addition and multiplication algorithms.

### 2018-10-05 parts/02_relatedliterature_06fullyhomomorphic.tex
Completed intensity transformations
Completed RRL, methodology and appendix sections on intensity transformations.
Fixed some typos.

--- 2018-09-30 parts/08_appendices_a_cryptosystems.tex
@@
-%\section{Introduction to the Appendices}
-
-%The Appendices is where you are enabled to present any additional or supplementary information relevant to your study, yet do not require highlighting within the actual paper, either because of its trivial nature or volume.
-These may in the form of figures, tables, or additional text detailing specific aspects about or related to the study.
-
-%\section{Sample Questions for Different Studies}
-%The following table presents three sample studies, as well as the guide questions that may help direct the discussion in each section of the paper.
-You may use this as another reference in writing your paper.
-\chapter{DESCRIPTION OF CRYPTOSYSTEMS}
-
-\section{Dasgupta-Pal cryptosystem}
+\section{Fully homomorphic cryptosystems}
+\subsection{Dasgupta-Pal cryptosystem}
 The Dasgupta-Pal cryptosystem is a fully homomorphic cryptosystem proposed in 2016 by Smaranika Dasgupta and S.
@@
 where $a_ka_{k-1}\cdots a_2a_1_0$ is the binary representation of $m$.
-\subsection{Key generation, encryption and decryption algorithms}
+\subsubsection{Dasgupta-Pal cryptosystem description}
 Let $\ell$ denote the security parameter of the cryptosystem.
@@
 
-\subsection{Homomorphic properties}
+\subsubsection{Homomorphic properties}
 It has been shown \cite{dasgupta_design_2016} that the following properties hold for all integer messages $m_1, m_2 \in \mathbb{Z}_n$ in the Dasgupta-Pal cryptosystem.
@@
 \end{description}
+
+\section{}

### 2018-10-05 parts/03_methodology_01nonlinearintensitytransformations.tex
Completed intensity transformations
Completed RRL, methodology and appendix sections on intensity transformations.
Fixed some typos.

\section{Non-Linear Intensity Transformations}
We now describe how we are to implement the logarithm and power-law transformations.
\subsection{Logarithm Transformation}
The logarithm transformation of a pixel intensity value $x$ is defined as
\begin{align}
	T\left(x\right) = c \log\left(1 + x\right)
\end{align}
where $c$ is a constant.

In order to perform this transformation under a homomorphic cryptosystem, we must provide an approximation for $\log\left(1 + x\right)$ in terms of addition and multiplication operations (or their inverses). We have derived a closed form approximation in Appendix \ref{sec:logapproximation}.
\begin{align}
	\label{eq:scaledquadraturech3}
  \begin{split}
    &\log(1+x) \\
    &=\frac{137x^5 + 33185x^4 + 931370x^3 - 13403630x^2 - 289469315x - 713567363}
    {30(x^5 + 505x^4 + 42010x^3 + 923010x^2 + 5722005x + 8040501)} + \log{20}
  \end{split}
\end{align}

\subsection{Power-Law Transformation}
The power-law transformation of a pixel intensity value $x$ is defined as
\begin{equation}
    T\left(x\right) = cx^{\gamma}
\end{equation}
where $c>0$ and $\gamma > 0$.

Similar to the logarithm transformation, we must provide an approximation for $x^\gamma$.
We have derived an infinite series in Appendix \ref{sec:logapproximation}.
\begin{align*}
	x^\gamma &= \sum_{n=0}^{\infty}{\frac{(\gamma\log{x})^n}{n!}}\\
\end{align*}
Partial sums of the above infinite series can be calculated based on the closed form approximation for the logarithm in Equation \ref{eq:scaledquadraturech3}.

### 2018-10-05 parts/08_appendices_a_cryptosystems.tex
Completed intensity transformations
Completed RRL, methodology and appendix sections on intensity transformations.
Fixed some typos.

@@
 
-\section{Dasgupta-Pal cryptosystem}
-The Dasgupta-Pal cryptosystem is a fully homomorphic cryptosystem proposed in 2016 by Smaranika Dasgupta and S.
-K.
-Pal \cite{dasgupta_design_2016}, which encrypts integer plaintexts in $\mathbb{Z}_n$ to polynomial ciphertexts.
-We begin our presentation of the Dasgupta-Pal cryptosystem with the following definition.
-
-Given a message $m \in \mathbb{n}$, we denote
+\section{Proof of the Correction Dasgupta-Pal Cryptosystem}
+The Dasgupta-Pal cryptosystem encrypts each bit in a bit string independently.
+In terms of single-bit encryption, the Dasgupta-Pal cryptosystem can be described as follows:
+\begin{description}
+	\item[Key generation]
+	Let the secret key, $S_k$ be a large prime.
+	Let the public refresh key, $R_k$, be $S_k \times z$, where $z$ is a large even integer.
+	\item[Encryption]
+	Given a message $m$, the encryption function is defined as
 	\begin{align*}
-		m_p(x) = a_0 + a_1x + a_2x^2 + \cdots + a_kx^k
+		E(m) = m + S_kr
 	\end{align*}
-where $a_ka_{k-1}\cdots a_2a_1_0$ is the binary representation of $m$.
-\subsection{Key generation, encryption and decryption algorithms}
-Let $\ell$ denote the security parameter of the cryptosystem.
-Let $S_k$ be a prime number with $\ell$ bits.
-Choose a random even integer $z$ of length $\log_2{\ell}$.
-
-Let the secret key be $S_k$, and let the refresh key be $R_k = z \cdot S_k$. The secret key is kept private to the encrypting/decrypting parties, while the refresh key is made publicly available.
-
-The scheme defines the encryption algorithm for a message $m \in \mathbb{Z}_n$ as follows:
+	where $r$ is a random integer.
+	\item[Decryption]
+	Given a ciphertext $c$, the decryption function is defined as
 	\begin{align*}
-	E(m) = y(x) + S_k\times d(x)
+		D(c) = c \bmod S_k \bmod 2
 	\end{align*}
-where
-$y(x)$ is a polynomial of degree $n$ such that $m_p(x) \equiv y(x) \bmod S_k$ and $d(x)$ is a randomly chosen polynomial of degree $n$.
-
-Furthermore, the decryption algorithm to recover $m_p(x)$ from a ciphertext polynomial $c(x)$ as
+\end{description}
+The homomorphic operations are then defined as
+\begin{description}
+	\item[XOR on ciphertexts]
 	\begin{align*}
-	m_p(x) = c(x) \bmod S_k \bmod 2
+		D(E(a)+E(b)) = a \text{ XOR } b
 	\end{align*}
-Thus $D(c(x))$ is defined as the integer recovered from the coefficients of the polynomial $c(x) \bmod S_k \bmod 2$
-
-As a fully homomorphic cryptosystem, homomorphic operations on ciphertext introduce noise which may interfere with decryption.
-To eliminate noise from a polynomial ciphertext, the following refresh function is used.
+	\item[AND on ciphertexts]
 	\begin{align*}
-	R(c(x)) = c(x) \bmod R_k
+		D(E(a)\times E(b)) = a \text{ AND } b
+	\end{align*}
+\end{description}
+After repeated operations on ciphertexts, the resulting ciphertext can grow in magnitude.
+To prevent storage issues and keep the ciphertext size small, a refresh function is used.
+\begin{description}
+	\item[Refresh function]
+	Given a ciphertext $c$, the refresh function is defined as
+	\begin{align*}
+		R(c) = c \bmod R_k
+	\end{align*}
+\end{description}
+\section{A Case Where Decryption Fails}
+We consider the following quantity:
+\begin{align}
+	\label{eq:cornercase_ciphertext}
+	D(\underbrace{E(1)+E(1)+\cdots+E(1)}_{S_k \text{ times}}).
+\end{align}
+Since $S_k$ is odd, the corresponding operation in the plaintext space is
+\begin{align*}
+	\label{eq:cornercase_plaintext}
+	\underbrace{1 \text{ XOR } 1 \text{ XOR } \cdots \text{ XOR } 1}_{S_k \text{ times}} = 1.
+\end{align*}
+However, evaluating Equation \ref{eq:cornercase_ciphertext} yields:
+\begin{align*}
+	D(\underbrace{E(1)+E(1)+\cdots+E(1)}_{S_k \text{ times}})
+	&= D\left(\sum_{i=1}^{S_k}{(1+S_kr_i)}\right)\\
+	&= D\left(S_k + S_k\sum_{i=1}^{S_k}{r_i}\right)\\
+	&= \left(S_k + S_k\sum_{i=1}^{S_k}{r_i}\right) \bmod S_k \bmod 2\\
+	&= 0 \bmod 2\\
+	&= 0.
+\end{align*}
+Since $1\neq 0$, we have shown an instance where incorrect decryption occurs given a sequence of operations on ciphertexts.
+In general, a ciphertext in the Dasgupta-Pal cryptosystem is composed of a \textit{message-carrying addend} $A_m$ and a \textit{secret key addend} $A_s$ which is divisible by $S_k$.
+The message-carrying addend maintains the parity of the encoded bit, while the secret key addend obfuscates the message.
+This is maintained even when homomorphic operations are applied to ciphertexts:
+\begin{align*}
+	E(a) &= \underbrace{a}_{A_m} + \underbrace{S_kr}_{A_s}\\
+	E(a)+E(b) &= (a + S_kr_1) + (b + S_kr_2)\\
+	&= \underbrace{a+b}_{A_m} + \underbrace{S_k(r_1 + r_2)}_{A_s}\\
+	E(a)\times E(b) &= (a + S_kr_1) \times (b + S_kr_2)\\
+	&= \underbrace{ab}_{A_m} + \underbrace{S_k(br_1 + ar_2 + S_kr_1r_2)}_{A_s}
 \end{align*}
 
-\subsection{Homomorphic properties}
-It has been shown \cite{dasgupta_design_2016} that the following properties hold for all integer messages $m_1, m_2 \in \mathbb{Z}_n$ in the Dasgupta-Pal cryptosystem.
-\begin{description}
-  \item[Additive homomorphism]
-  \begin{align*}
-    D(E(m_1) + E(m_2))= m_1+m_2 & \text{ (used for binary addition)}
-  \end{align*}
-  \item[Multiplicative homomorphism]
-  \begin{align*}
-    D(E(m_1) \times E(m_2))= m_1 \times m_2 & \text{ (used for binary multiplication)}
-  \end{align*}
-\end{description}
+Errors may occur in decryption when the message-carrying addend exceeds $S_k$.
+
+The refresh function does not remedy this error: since $R_k > S_k$, refreshing the ciphertexts
+
+\subsection{Correction to the Dasgupta-Pal Cryptosystem}
+We now show that setting the secret key $S_k$ to $2p$, where $p$ is a prime, fixes the issue in the original cryptosystem.

### 2018-10-05 parts/08_appendices_b_numericalapproximations.tex
Completed intensity transformations
Completed RRL, methodology and appendix sections on intensity transformations.
Fixed some typos.

@@
 \section{Approximation for $\log(1+x)$}
+\label{sec:logapproximation}
 We approximate the function $f(x)=\log(1+x)$ using a similar method to that described in
@@
 \end{align*}
-This integral can be approximated using the five-point Gauss-Legendre quadrature rule, yielding the following approximation:
+This integral can be approximated using the five-point Gauss-Legendre quadrature rule \cite{kythe_quadrature_2002}, which is as follows:
+\begin{align*}
+	\int_a^b{f(x)\diff x}
+	&= \frac{b-a}{2}\int_{-1}^{1}{f\left(\frac{b-a}{2}x+\frac{a+b}{2}\right)\diff x}\\
+	\int_{-1}^{1}{f(x)\diff x} &= \sum_{i=1}^{5}{w_if(x_i)}
+\end{align*}
+where
+\begin{multicols}{2}
+	\noindent
+	\begin{align*}
+		w_1 &= 0\\
+		w_2 &= \frac{1}{21}\sqrt{245-14\sqrt{70}}\\
+		w_3 &= -\frac{1}{21}\sqrt{245-14\sqrt{70}}\\
+		w_4 &= \frac{1}{21}\sqrt{245+14\sqrt{70}}\\
+		w_5 &= -\frac{1}{21}\sqrt{245+14\sqrt{70}}\\
+	\end{align*}
+	\columnbreak
+	\begin{align*}
+		x_1 &= \frac{128}{225}\\
+		x_2 &= \frac{1}{900}\left( 322 + 13\sqrt{70}\right)\\
+		x_3 &= \frac{1}{900}\left( 322 + 13\sqrt{70}\right)\\
+		x_4 &= \frac{1}{900}\left( 322 - 13\sqrt{70}\right)\\
+		x_5 &= \frac{1}{900}\left( 322 - 13\sqrt{70}\right)\\
+	\end{align*}
+\end{multicols}
+This yields the following approximation:
 \begin{equation}\label{eq:standardquadrature}
@@
 \end{figure}
-As we only need accuracy for $x \in [0, 255]$, we can scale up the approximation by a constant factor $\alpha$ as follows:
+As we only need accuracy for $x \in [0, 255]$, we can scale the approximation by a constant factor $\alpha$ as follows:
 \begin{align*}
@@
 \end{align}
-
-\section{Approximation for $x^r$}
-To approximate $x^r$ for any $r \in \mathbb{R}$, we rewrite $x^r$ as follows:
+Below is a graph of the absolute error of the scaled approximation and the exact value of $\log{(1+x)}$.
+\begin{figure}[!ht]
+    \centering
+    \includegraphics[width=.9\linewidth,\keepaspectratio]{figures/ModifiedQuadratureAbsoluteError.png}
+    \caption{Graph of the absolute error of $\log{(1+x)}$ and the approximation in equation \ref{eq:scaledquadrature}}
+    \label{fig:scaledquadrature}
+\end{figure}
+\section{Approximation for $x^\gamma$}
+To approximate $x^\gamma$ for any $\gamma \in \mathbb{R}$, we rewrite $x^\gamma$ as follows:
 \begin{align*}
-  x^\gamma = e^{\log{x^r}} = e^{r\log{x}}.
+  x^\gamma = e^{\log{x^\gamma}} = e^{\gamma\log{x}}.
 \end{align*}
@@
   e^x &= \sum_{n=0}^{\infty}{\frac{x^n}{n!}}\\
-  \Rightarrow e^{r\log{x}} &= \sum_{n=0}^{\infty}{\frac{(r\log{x})^n}{n!}}
+  \Rightarrow e^{\gamma\log{x}} &= \sum_{n=0}^{\infty}{\frac{(\gamma\log{x})^n}{n!}}
 \end{align*}
-As we already have an approximation for the natural logarithm, we can evaluate partial sums of the above infinite series to arrive at approximations for $x^r$.
+As we already have an approximation for the natural logarithm, we can evaluate partial sums of the above infinite series to arrive at approximations for $x^\gamma$.

### 2018-10-05 parts/02_relatedliterature_05partiallyhomomorphic.tex
Completed 3 of 4 cryptosystems
remaining cryptosystem is HeLib

--- 2018-09-30 parts/02_relatedliterature_03partiallyhomomorphic.tex
@@
 
-We will then show that the cryptosystems can be modified to support limited polynomial evaluation: given an encrypted message $m$, evaluate
+We will then show that the cryptosystems can be modified to support privacy-perserving polynomial evaluation in a client-server protocol: given an encrypted message $m$, evaluate $f(m)$ where $f$ is a polynomial function.
 
-These operations
 \subsection{The Pallier cryptosystem}
@@
 
-\subsubsection{Pallier cryptosystem description}
+\subsubsection{Pallier Cryptosystem Description}
 We first define a function $L(x)$ as the largest integer $v$ greater than zero such that $x-1 \geq vn$.
@@
 
-\subsubsection{Homomorphic Properties}
+\subsubsection{Homomorphic Properties of the Pailler Cryptosystem}
 The Paillier cryptosystem supports additive homomorphism as well as the multiplication of a plaintext scalar to an encrypted message. These operations are defined as follows.
@@
 
-This is trivially feasible if $m^2 \bmod n$ and $E(m^2 \bmod n)$ are known, since one can use the following equation to raise $m$ to any positive integer power.
-\begin{align*}
-	D(E(m^k)^{m^2 \bmod n}\bmod n^2) &= m^2m^k\bmod n \\
-	&= m^{k+2}\bmod n
-\end{align*}
+%This is trivially feasible if $m^2 \bmod n$ and $E(m^2 \bmod n)$ are known, since one can use the following equation to raise $m$ to any positive integer power.
+%\begin{align*}
+%	D(E(m^k)^{m^2 \bmod n}\bmod n^2) &= m^2m^k\bmod n \\
+%	&= m^{k+2}\bmod n
+%\end{align*}
 
-We now show that including $m^2 \bmod n$ and $E(m^2 \bmod n)$ in a transmitted message does not compromise the security of the Paillier cryptosystem.
+%We now show that including $m^2 \bmod n$ and $E(m^2 \bmod n)$ in a transmitted message does not compromise the security of the Paillier cryptosystem.
 Clearly, $E(m^2 \bmod n)$ can be shared without compromising security, as it is an encrypted quantity.
@@
 
-\subsubsection{Benaloh cryptosystem description}
+\subsubsection{Benaloh Cryptosystem Description}
 We choose an integer $r$ and two large primes $p$ and $q$ such that the following conditions hold:
@@
 
-\subsubsection{Homomorphic Properties}
+\subsubsection{Homomorphic Properties of the Benaloh Cryptosystem}
 Similar to the Paillier cryptosystem, the Benaloh cryptosystem supports additive homomorphism as well as the multiplication of a plaintext scalar to an encrypted message.
@@
 
-Similar to the Paillier cryptosystem, we can include $m^2$ and $E(m^2)$ in the transmitted message
+\section{General Exponentiation Protocol}
+In order to perform polynomial evaluation, we first present a protocol for privacy-preserving exponentiation to a positive integer power, adapted from the protocol to calculate Euclidean distances used in \cite{hutchison_privacy-preserving_2009}.
+
+The following protocols apply to both the Pailler and Benaloh cryptosystems, as they share similar homomorphisms.
+
+Suppose Alice encrypts an integer $x$ and sends it so Bob has $E(x)$, and wants to obtain $E(x^2)$ without exposing the value of $x$.
+\begin{itemize}
+	\item Bob first selects a random integer $r$ and computes $E(x+r)$. Bob can do this since $r$ is a plaintext constant.
+	\item Bob sends $E(x+r)$ to Alice, who decrypts the ciphertext to obtain $x+r$.
+	\item Alice squares $x+r$ and encrypts the result. She sends $E((x+r)^2)$ to Bob.
+	\item Bob computes $E(-2rx + r^2)$. He then computes $E((x+r)^2)E(-2rx + r^2) = E(x^2)$.
+\end{itemize}

### 2018-10-05 parts/02_relatedliterature_06fullyhomomorphic.tex
Completed 3 of 4 cryptosystems
remaining cryptosystem is HeLib

@@
-\section{Fully homomorphic cryptosystems}
-\subsection{Dasgupta-Pal cryptosystem}
+\section{Fully Homomorphic Cryptosystems}
+\subsection{Dasgupta-Pal Cryptosystem}
 The Dasgupta-Pal cryptosystem is a fully homomorphic cryptosystem proposed in 2016 by Smaranika Dasgupta and S.
@@
 where $a_ka_{k-1}\cdots a_2a_1_0$ is the binary representation of $m$.
-\subsubsection{Dasgupta-Pal cryptosystem description}
+
+In the original scheme presented in \cite{dasgupta_design_2016}, the secret key $S_k$ is set to be a large prime.
+In Appendix \autoref{ch:correction}, we present a case where the Dasgupta-Pal cryptosystem fails and prove that setting the secret key $S_k = 2p$, where $p$ is a large prime, corrects errors in the Dasgupta-Pal cryptosystem.
+We now decribe the correct cryptosystem.
+\subsubsection{Corrected Dasgupta-Pal Cryptosystem Description}
 Let $\ell$ denote the security parameter of the cryptosystem.
-Let $S_k$ be a prime number with $\ell$ bits.
+Let $S_k = 2p$, where $p$ is a prime number with $\ell - 1$ bits.
 Choose a random even integer $z$ of length $\log_2{\ell}$.
@@
 
-The scheme defines the encryption algorithm for a message $m \in \mathbb{Z}_n$ as follows:
+The scheme defines the encryption algorithm for a message $m$ as follows:
 \begin{align*}
@@
 $y(x)$ is a polynomial of degree $n$ such that $m_p(x) \equiv y(x) \bmod S_k$ and $d(x)$ is a randomly chosen polynomial of degree $n$.
+This encrypts each coefficient of of $m_p(x)$ by adding some multiple of $S_k$ to it.
+Through this process, each bit of the message is encrypted separately.
 
@@
 
-As a fully homomorphic cryptosystem, homomorphic operations on ciphertext introduce noise which may interfere with decryption.
+Dasgupta and Pal note that homomorphic operations on ciphertext introduce noise which may interfere with decryption, due to the potential increase in ciphertext values.
 To eliminate noise from a polynomial ciphertext, the following refresh function is used.
@@
 
-\subsubsection{Homomorphic properties}
+\subsubsection{Homomorphic Properties of the Dasgupta-Pal Cryptosystem}
 It has been shown \cite{dasgupta_design_2016} that the following properties hold for all integer messages $m_1, m_2 \in \mathbb{Z}_n$ in the Dasgupta-Pal cryptosystem.
+These properties arise since each coefficient in a ciphertext polynomial is essentially an independently encrypted bit of the original message.
 \begin{description}
-  \item[Additive homomorphism]
+	\item[XOR on ciphertexts]
+	An exclusive or (XOR) operation on integer messages can be achieved by adding the coefficients pairwise between two ciphertexts.
 	\begin{align*}
-    D(E(m_1) + E(m_2))= m_1+m_2 & \text{ (used for binary addition)}
+		D(E(m_1)+E(m_2)) = m_1 \text{ XOR } m_2
 	\end{align*}
-  \item[Multiplicative homomorphism]
+	\item[AND on ciphertexts]
+	Similarly, pair-wise multiplication of
 	\begin{align*}
-    D(E(m_1) \times E(m_2))= m_1 \times m_2 & \text{ (used for binary multiplication)}
+		D(E(a) \otimes E(b)) = a \text{ AND } b = ab \bmod 2
+	\end{align*}
+	where $\otimes$ denotes pairwise multiplication,
+	\begin{align*}
+		\sum_{i=1}^n{a_ix^i} \otimes \sum_{i=1}^n{b_ix^i} = \sum_{i=1}^n{a_ib_ix^i}.
 	\end{align*}
 \end{description}
-
-\section{}

### 2018-10-05 parts/08_appendices_a_cryptosystems.tex
Completed 3 of 4 cryptosystems
remaining cryptosystem is HeLib

@@
 You may use this as another reference in writing your paper.
-\chapter{DESCRIPTION OF CRYPTOSYSTEMS}
-
-\section{Proof of the Correction Dasgupta-Pal Cryptosystem}
-The Dasgupta-Pal cryptosystem encrypts each bit in a bit string independently.
-In terms of single-bit encryption, the Dasgupta-Pal cryptosystem can be described as follows:
+\chapter{CORRECTION TO THE DASGUPTA-PAL CRYPTOSYSTEM}
+\label{ch:correction}
+\section{Bitwise Description of the Dasgupta-Pal Cryptosystem}
+The Dasgupta-Pal cryptosystem \cite{dasgupta_design_2016} encrypts each bit in a bit string independently.
+In terms of the encryption of a single bit, the Dasgupta-Pal cryptosystem can be described as follows:
 \begin{description}
@@
 	\begin{align*}
-		D(E(a)+E(b)) = a \text{ XOR } b
+		D(E(a)+E(b)) = a \text{ XOR } b = (a + b) \bmod 2
 	\end{align*}
@@
 	\begin{align*}
-		D(E(a)\times E(b)) = a \text{ AND } b
+		D(E(a)\times E(b)) = a \text{ AND } b = ab \bmod 2
 	\end{align*}
@@
 \end{description}
-\section{A Case Where Decryption Fails}
+\section{Cases Where Decryption Fails}
 We consider the following quantity:
@@
 \end{align*}
-Since $1\neq 0$, we have shown an instance where incorrect decryption occurs given a sequence of operations on ciphertexts.
-In general, a ciphertext in the Dasgupta-Pal cryptosystem is composed of a \textit{message-carrying addend} $A_m$ and a \textit{secret key addend} $A_s$ which is divisible by $S_k$.
-The message-carrying addend maintains the parity of the encoded bit, while the secret key addend obfuscates the message.
-This is maintained even when homomorphic operations are applied to ciphertexts:
+Since $\underbrace{1 \text{ XOR } 1 \text{ XOR } \cdots \text{ XOR } 1}_{S_k \text{ times}} = 1\neq 0 = D(\underbrace{E(1)+E(1)+\cdots+E(1)}_{S_k \text{ times}})$, we have shown an instance where incorrect decryption occurs given a sequence of operations on ciphertexts.
+
+\subsection{Proposed Correction and Proof of Correctness}
+We now show that setting the secret key $S_k$ to $2p$, where $p$ is a prime, fixes the issue in the original cryptosystem.
+\begin{theorem}
+	Suppose $S_k = 2p$, where $p$ is a prime. Then when addition or multiplication is performed between any two ciphertexts, correct decryption is assured.
+\end{theorem}
+\begin{proof}
+	Suppose $c_1, c_2$ are two ciphertexts such that
 	\begin{align*}
-	E(a) &= \underbrace{a}_{A_m} + \underbrace{S_kr}_{A_s}\\
-	E(a)+E(b) &= (a + S_kr_1) + (b + S_kr_2)\\
-	&= \underbrace{a+b}_{A_m} + \underbrace{S_k(r_1 + r_2)}_{A_s}\\
-	E(a)\times E(b) &= (a + S_kr_1) \times (b + S_kr_2)\\
-	&= \underbrace{ab}_{A_m} + \underbrace{S_k(br_1 + ar_2 + S_kr_1r_2)}_{A_s}
+		c_1 = a + S_kr_1\\
+		c_2 = b + S_kr_2
 	\end{align*}
+	We first consider addition. We want to show that $(c_1+c_2)\bmod S_k$ has the same parity as $a+b$.
+	By the division algorithm, we have $a+b = S_kq + r$, for some $q,r$, $q \geq 0, r > 0$. We can rewrite $c_1+c_2$ as
+	\begin{align*}
+		c_1+c_2 &= (a + S_kr_1) + (b + S_kr_2)\\
+		&= (a+b)+ S_k(r_1 + r_2)\\
+		&= (S_kq + r) + S_k(r_1 + r_2)\\
+		&= r + S_k(q + r_1 + r_2).
+	\end{align*}
+	Therefore $(c_1+c_2)\bmod S_k = r$.
+	It is enough to show that the parity of $a+b$ is the same as the parity of $r$. We consider cases based on the parity of $a+b$.
+	\begin{description}
+		\item[Case 1: $a+b$ is odd.]
+			Since $a+b = S_kq + r$, $S_kq + r$ must also be odd.
+			$S_k$ is even, so $S_kq$ is also even.
+			For $S_kq + r$ to be odd, $r$ must be odd, since $S_k$ is even.
 
-Errors may occur in decryption when the message-carrying addend exceeds $S_k$.
+			Therefore, the parity of $a+b$ is the same as the parity of $r$.
+		\item[Case 2: $a+b$ is even.]
+			Since $a+b = S_kq + r$, $S_kq + r$ must also be even.
+			$S_k$ is even, so $S_kq$ is also even. For $S_kq + r$ to be even, $r$ must be even , since $S_k$ is even.
 
-The refresh function does not remedy this error: since $R_k > S_k$, refreshing the ciphertexts
+			Therefore, the parity of $a+b$ is the same as the parity of $r$.
+	\end{description}
+	Therefore correct decryption is assured for the sum of ciphertexts.
 
-\subsection{Correction to the Dasgupta-Pal Cryptosystem}
-We now show that setting the secret key $S_k$ to $2p$, where $p$ is a prime, fixes the issue in the original cryptosystem.
+	We now consider multiplication.
+We want to show that $c_1c_2 \bmod S_k$ has the same parity as $ab$.
+Similar to the addition case, by the division algorithm, we can write $ab = S_kq + r$, $q > 0, r > 0$ for some $q,r$.
+We can rewrite $c_1c_2$ as
+	\begin{align*}
+		c_1c_2 &= (a + S_kr_1) \times (b + S_kr_2)\\
+		&= ab + S_k(br_1 + ar_2 + S_kr_1r_2)\\
+		&= (S_kq + r) + S_k(br_1 + ar_2 + S_kr_1r_2)\\
+		&= r + S_k(q + br_1 + ar_2 + S_kr_1r_2).
+	\end{align*}
+	Therefore $c_1c_2 \bmod S_k = r$.
+	It is enough to show that the parity of $ab$ is the same as the parity of $r$. We consider cases based on the parity of $ab$.
+	\begin{description}
+		\item[Case 1: $ab$ is odd.]
+			Since $ab = S_kq + r$, $S_kq + r$ must also be odd.
+			$S_k$ is even, so $S_kq$ is also even.
+			For $S_kq + r$ to be odd, $r$ must be odd, since $S_k$ is even.
+
+			Therefore, the parity of $a+b$ is the same as the parity of $r$.
+		\item[Case 2: $ab$ is even.]
+			Since $ab = S_kq + r$, $S_kq + r$ must also be even.
+			$S_k$ is even, so $S_kq$ is also even. For $S_kq + r$ to be even, $r$ must be even , since $S_k$ is even.
+
+			Therefore, the parity of $ab$ is the same as the parity of $r$.
+	\end{description}
+	Therefore, correct decryption is assured for both addition and multiplication of ciphertexts.
+\end{proof}

### 2018-10-06 parts/02_relatedliterature_05partiallyhomomorphic.tex
Replaced Benaloh with DGK in RRL

@@
-\section{Partially homomorphic cryptosystems}
+\section{Partially Homomorphic Cryptosystems}
 
-In this section, we will present two classical partially homomorphic cryptosystems which we will be testing in the study: the Pallier cryptosystem and the Benaloh cryptosystem.
+In this section, we will present two classical partially homomorphic cryptosystems which we will be testing in the study: the Pallier cryptosystem and the DGK cryptosystem.
 Both of these cryptosystems encrypt integer plaintexts and are additively homomorphic.
@@
 
-\subsection{The Pallier cryptosystem}
+\subsection{The Pallier Cryptosystem}
 The Pallier cryptosystem \cite{stern_public-key_1999}, developed by Pascal Pallier, is a probabilistic encryption scheme which is based on the composite residuosity class problem.
@@
 
-\subsubsection{Pallier Cryptosystem Description}
+\subsubsection{Key Generation}
 We first define a function $L(x)$ as the largest integer $v$ greater than zero such that $x-1 \geq vn$.
@@
 
+\subsubsection{Encryption and Decryption}
 The encryption function to encrypt a plaintext $m \in \mathbb{Z}_n$ given a public key $(g,n)$ is defined as
@@
 For all $m_1,m_2 \in \mathbb{Z}_n$ and $k\in \mathbb{N}$, the following homomorphic properties hold.
-\begin{description}
-  \item[Additive homomorphism]
 \begin{align*}
@@
   D(E(m_1)E(m_2)\bmod n^2)=(m_1+m_2)\bmod n & \text{ (used for binary addition)}
-  \end{align*}
-  \item[Multiplicative homomorphism]
-  \begin{align*}
   D(E(m_1)^k\bmod n^2)= km_1\bmod n & \text{ (used to multiply a plaintext constant)}
 \end{align*}
-\end{description}
-In order to implement some image operations covered in this study, we require the exponentiation of ciphertexts to integer powers, i.e. we require a function $f$ so that
-\begin{align*}
-	D(f(E(m))) = m^k\bmod n
-\end{align*}
-for any plaintext $m \in \mathbb{Z}_n$, and positive integer $k$.
+
+%In order to implement some image operations covered in this study, we require the exponentiation %of ciphertexts to integer powers, i.e. we require a function $f$ so that
+%\begin{align*}
+%	D(f(E(m))) = m^k\bmod n
+%\end{align*}
+%for any plaintext $m \in \mathbb{Z}_n$, and positive integer $k$.
 
@@
 
-\subsection{The Benaloh cryptosystem}
-The Benaloh cryptosystem, initially proposed by Josh Benaloh in \cite{benaloh_dense_1994}, allows for the encryption of integers in $\mathbb{Z}_r$ for some odd integer $r$.
+\subsection{The DGK Cryptosystem}
+%insert background
+The DGK cryptosystem was published by Damgard, Geisler, and Krøigaard in an effort to create a secure integer comparison scheme \cite{pieprzyk_efficient_2007, cryptoeprint:2008:321}.
+It encrypts  It is widely used in the literature %insert citations here
+\subsubsection{Key Generation}
+We denote $k,t,\ell$ as security parameters of the scheme, where $k>t>\ell$.
+Let $p,q$ be primes such that
+we can choose two $t$-bit primes $v_p$ and $v_q$ such that $v_p | (p-1)$ and $v_q | (q-1)$, and a small prime $u$ such that $u | (p-1)$ and $u | (q-1)$.
+We denote $n = pq$.
+We choose $g$ to be an integer of order $uv_pv_q$ and $h$ to be of order $v_pv_q$.
+
+The DGK cryptosystem encrypts plaintexts in $\mathbb{Z}_u$ to ciphertexts in $\mathbb{Z}_n^\ast$.
+
+The public key is $(n,g,h,u)$ and the private key is $(p,q,v_p,v_q)$.
+
+\subsubsection{Encryption and Decryption}
+To encrypt a message $m \in \mathbb{Z}_u$, the encryption function is defined as:
+\begin{align*}
+  E(m) = g^m \cdot h^r \mod{n},
+\end{align*}
+where $r$ is a random integer in $\mathbb{Z}_n$ which is longer than $2t$ bits.
+
+To decrypt a ciphertext $c \in \mathbb{Z}_n^\ast$, decryption is achieved by first computing $c^{v_pv_q}$.
+\begin{align*}
+	c^{v_pv_q} \bmod n
+	&= (g^m \cdot h^r)^{v_pv_q} \bmod n\\
+	&= (g^{v_pv_q})^m \bmod n
+\end{align*}
+Since $(g^{v_pv_q})^m$ has order $u$, there is a one-to-one correspondence between plaintexts in $\mathbb{Z}_u$ and  $(g^{v_pv_q})^m$.
+A lookup table can thus be generated privately to successfully recover $m$.
+
+\subsubsection{Homomorphic Properties of the DGK Cryptosystem}
+The DGK cryptosystem supports additive homomorphism as well as the multiplication of a plaintext scalar to an encrypted message. These operations are defined as follows.
+For all $m_1,m_2 \in \mathbb{Z}_u$ and $k\in \mathbb{N}$, the following homomorphic properties hold.
+\begin{align*}
+    D(E(m_1)g^k)=(m_1+k)\bmod u & \text{ (used to add a constant)}\\
+    D(E(m_1)E(m_2))=(m_1+m_2)\bmod u & \text{ (used for binary addition)}
+    D(E(m_1)^k)= km_1\bmod u & \text{ (used to multiply a plaintext constant)}
+\end{align*}
+
+As the multiplicative homomorphism was not presented in the original paper, we provide a short proof here.
+\begin{proof}
+  Let $m \in \mathbb{Z}_u$ and $k\in \mathbb{N}$.
+  We consider $E(m)^k = (g^m \cdot h^r \bmod{n})^k\bmod n$.
+  \begin{align*}
+    (g^m \cdot h^r \bmod{n})^k \bmod n
+    &= (g^m \cdot h^r)^k \bmod{n}\\
+    &= (g^m)^k \cdot (h^r)^k \bmod{n}\\
+    &= g^{km} \cdot (h^kr) \bmod{n}\\
+  \end{align*}
+  Since $r$ is a random integer, $kr$ is also a random integer, Therefore, $g^{km} \cdot (h^kr) \bmod{n} = D(E(m_1)^k)$ is a valid encryption of the message $km$.
+\end{proof}
+
+%\subsection{DGK Comparison Protocol}
+%The DGK system was primarily developed as part of a comparison protocol, a protocol which allows
+%It is known that $E(m)^{v_pv_q} \bmod n = 1$ if and only if $m=0$. This allows
+
+%\subsection{The Benaloh cryptosystem}
+%The Benaloh cryptosystem, initially proposed by Josh Benaloh in \cite{benaloh_dense_1994}, allows for the encryption of integers in $\mathbb{Z}_r$ for some odd integer $r$.
 It relies on the hardness of the \textit{discrete logarithm problem}, and is a generalization of the classic Goldwasser--Micali cryptosystem~\cite{goldwasser_probabilistic_1984}.
@@
 
-\subsubsection{Benaloh Cryptosystem Description}
-We choose an integer $r$ and two large primes $p$ and $q$ such that the following conditions hold:
-\begin{itemize}
-  \item $r$ divides $(p-1)$;
-  \item $\mathrm{gcd}(r,(p-1)/r)=1$;
-  \item $\mathrm{gcd}(r,q-1)=1$.
-\end{itemize}
-Next, let $n=pq$ and $\phi = (p-1)(q-1)$, and choose $y\in \mathbb{Z}_n^* = \{ x \in \mathbb{Z}_n | \mathrm{gcd}(x,n)=1 \}$ such that the following conditions hold:
-\begin{itemize}
-  \item $y^{\phi/r}\neq 1 \bmod n$;
-  \item For all prime factors $s$ of $r$, $y^{\phi/s}\neq 1 \bmod n$.
-\end{itemize}
-We denote the public key to be $(y,r,n)$ and the private key to be $(p,q)$.
+%\subsubsection{Benaloh Cryptosystem Description}
+%We choose an integer $r$ and two large primes $p$ and $q$ such that the following conditions hold:
+%\begin{itemize}
+%  \item $r$ divides $(p-1)$;
+%  \item $\mathrm{gcd}(r,(p-1)/r)=1$;
+%  \item $\mathrm{gcd}(r,q-1)=1$.
+%\end{itemize}
+%Next, let $n=pq$ and $\phi = (p-1)(q-1)$, and choose $y\in \mathbb{Z}_n^* = \{ x \in \mathbb{Z}_n | \mathrm{gcd}(x,n)=1 \}$ such that the following conditions hold:
+%\begin{itemize}
+%  \item $y^{\phi/r}\neq 1 \bmod n$;
+%  \item For all prime factors $s$ of $r$, $y^{\phi/s}\neq 1 \bmod n$.
+%\end{itemize}
+%We denote the public key to be $(y,r,n)$ and the private key to be $(p,q)$.
 
-The encryption function to encrypt a plaintext $m \in \mathbb{Z}_r$ is defined as
-\begin{align*}
-  E(m) = y^m \cdot u^r \mod{n},
-\end{align*}
-where $u$ is a random integer in $\mathbb{Z}_n^*$.
+%The encryption function to encrypt a plaintext $m \in \mathbb{Z}_r$ is defined as
+%\begin{align*}
+%  E(m) = y^m \cdot u^r \mod{n},
+%\end{align*}
+%where $u$ is a random integer in $\mathbb{Z}_n^*$.
 
-The decryption function to decrypt a ciphertext $c \in \mathbb{Z}_{n}$ is defined as:
-\begin{align*}
-  D(c) = \log_x{c^{\phi/r}} \mod n
-\end{align*}
-where $x = y^{\phi/r}$ and $\log_x{y} = k$ such that $x^k = y \bmod n$.
+%The decryption function to decrypt a ciphertext $c \in \mathbb{Z}_{n}$ is defined as:
+%\begin{align*}
+%  D(c) = \log_x{c^{\phi/r}} \mod n
+%\end{align*}
+%where $x = y^{\phi/r}$ and $\log_x{y} = k$ such that $x^k = y \bmod n$.
 
-Decryption requires the computation of the discrete logarithm, which can be done using a linear search when $r$ is small.
+%Decryption requires the computation of the discrete logarithm, which can be done using a linear search when $r$ is small.
 For large values of $r$, the baby-step giant-step algorithm can be used to perform decryption in $O(\sqrt{r})$ time \cite{benaloh_dense_1994}.
 
-\subsubsection{Homomorphic Properties of the Benaloh Cryptosystem}
-Similar to the Paillier cryptosystem, the Benaloh cryptosystem supports additive homomorphism as well as the multiplication of a plaintext scalar to an encrypted message.
-For all $m_1,m_2 \in \mathbb{Z}_r$ and $k\in \mathbb{N}$, the following homomorphic properties hold.
-\begin{description}
-  \item[Additive homomorphism]
-  \begin{align*}
-    D(E(m_1)y^{m_2}\bmod n^2)=(m_1+m_2)\bmod n & \text{ (used to add a constant)}\\
-    D(E(m_1)E(m_2)\bmod n^2)=(m_1+m_2)\bmod n & \text{ (used for binary addition)}
-  \end{align*}
-  \item[Multiplicative homomorphism]
-  \begin{align*}
-    D(E(m_1)^k\bmod n)= km_1\bmod n & \text{ (used to multiply a plaintext constant)}
-  \end{align*}
-\end{description}
+%\subsubsection{Homomorphic Properties of the Benaloh Cryptosystem}
+%Similar to the Paillier cryptosystem, the Benaloh cryptosystem supports additive homomorphism as well as the multiplication of a plaintext scalar to an encrypted message.
+%For all $m_1,m_2 \in \mathbb{Z}_r$ and $k\in \mathbb{N}$, the following homomorphic properties hold.
+%\begin{description}
+%  \item[Additive homomorphism]
+%  \begin{align*}
+%    D(E(m_1)y^{m_2}\bmod n^2)=(m_1+m_2)\bmod n & \text{ (used to add a constant)}\\
+%    D(E(m_1)E(m_2)\bmod n^2)=(m_1+m_2)\bmod n & \text{ (used for binary addition)}
+%  \end{align*}
+%  \item[Multiplicative homomorphism]
+%  \begin{align*}
+%    D(E(m_1)^k\bmod n)= km_1\bmod n & \text{ (used to multiply a plaintext constant)}
+%  \end{align*}
+%\end{description}
 
-As the multiplicative homomorphism was not presented in the original paper, we provide a short proof here.
-\begin{proof}
-  Let $m \in \mathbb{Z}_r$ and $k\in \mathbb{N}$.
-  We consider $E(m)^k\bmod n = (y^m \cdot u^r \bmod{n})^k\bmod n$.
-  \begin{align*}
-    (y^m \cdot u^r \bmod{n})^k\bmod n
-    &= (y^m \cdot u^r)^k \bmod{n}\\
-    &= (y^m)^k \cdot (u^r)^k \bmod{n}\\
-    &= y^{km} \cdot (u^k)^r \bmod{n}\\
-    &= y^{km} \cdot (u^k \bmod{n})^r \bmod{n}
-  \end{align*}
-  Since $u$ is a random integer in $\mathbb{Z}_n^*$, $\mathrm{gcd}(u,n)=1$.
-  This implies $\mathrm{gcd}(u^k,n)=1$, so $u^k \bmod n$ is a random integer in $\mathbb{Z}_n^*$.
-  Therefore, $y^{km} \cdot (u^k \bmod{n})^r \bmod{n} = E(m)^k\bmod n$ is a valid encryption of the message $km$.
-\end{proof}
+%As the multiplicative homomorphism was not presented in the original paper, we provide a short proof here.
+%\begin{proof}
+%  Let $m \in \mathbb{Z}_r$ and $k\in \mathbb{N}$.
+%  We consider $E(m)^k\bmod n = (y^m \cdot u^r \bmod{n})^k\bmod n$.
+%  \begin{align*}
+%    (y^m \cdot u^r \bmod{n})^k\bmod n
+%    &= (y^m \cdot u^r)^k \bmod{n}\\
+%    &= (y^m)^k \cdot (u^r)^k \bmod{n}\\
+%    &= y^{km} \cdot (u^k)^r \bmod{n}\\
+%    &= y^{km} \cdot (u^k \bmod{n})^r \bmod{n}
+%  \end{align*}
+%  Since $u$ is a random integer in $\mathbb{Z}_n^*$, $\mathrm{gcd}(u,n)=1$.
+%  This implies $\mathrm{gcd}(u^k,n)=1$, so $u^k \bmod n$ is a random integer in $\mathbb{Z}_n^*$.
+%  Therefore, $y^{km} \cdot (u^k \bmod{n})^r \bmod{n} = E(m)^k\bmod n$ is a valid encryption of the message $km$.
+%\end{proof}
 
-\section{General Exponentiation Protocol}
+\subsection{General Exponentiation Protocol for Pailler and DGK}
 In order to perform polynomial evaluation, we first present a protocol for privacy-preserving exponentiation to a positive integer power, adapted from the protocol to calculate Euclidean distances used in \cite{hutchison_privacy-preserving_2009}.
 
-The following protocols apply to both the Pailler and Benaloh cryptosystems, as they share similar homomorphisms.
+The following protocols apply to both the Pailler and DGK cryptosystems, as they share similar homomorphisms.
 
@@
 \end{itemize}
+
+This can be extended to arbitrary integer powers.
+Suppose Alice encrypts and integer $x$, and Bob has $E(x), E(x^2), ..., E(x^{n-1})$ and wants to obtain $E(x^n)$.
+\begin{itemize}
+	\item Bob first selects a random integer $r$ and computes $E(x+r)$. Bob can do this since $r$ is a plaintext constant.
+	\item Bob sends $E(x+r)$ to Alice, who decrypts the ciphertext to obtain $x+r$.
+	\item Alice sends $E((x+r)^n)$ to Bob.
+	\item Bob then computes
+	\begin{align*}
+		E((x+r)^n) - E\left(\sum_{i=1}^{n-1}{\binom{n}{i}x^ir^{n-i}}\right),
+	\end{align*}
+	which evaluates to $E(x^n)$ by the binomial theorem.
+\end{itemize}

### 2018-10-06 parts/02_relatedliterature_05partiallyhomomorphic.tex
Updated FHE section of RRL

@@
 \subsection{The DGK Cryptosystem}
-%insert background
-The DGK cryptosystem was published by Damgard, Geisler, and Krøigaard in an effort to create a secure integer comparison scheme \cite{pieprzyk_efficient_2007, cryptoeprint:2008:321}.
-It encrypts  It is widely used in the literature %insert citations here
+The DGK cryptosystem was published by Damgard, Geisler, and Krøigaard in 2007 in an effort to create a secure integer comparison scheme \cite{pieprzyk_efficient_2007, cryptoeprint:2008:321} which is widely used in the literature \cite{veugen_improving_2012}.
+
 \subsubsection{Key Generation}

### 2018-10-06 parts/02_relatedliterature_06fullyhomomorphic.tex
Updated FHE section of RRL

@@
 \section{Fully Homomorphic Cryptosystems}
-\subsection{Dasgupta-Pal Cryptosystem}
+
+We will also be testing fully homomorphic cryptosytems, which allow aribitrary computation on encrypted data.
+While generally being more flexible, fully homomorphic cryptosytems are known to be significantly slower than partially homomorphic cryptosytems; improving the efficiency of fully homomorphic cryptosytems is an active area of research \cite{sen_homomorphic_2013}.
+
+We will present two such cryptosystems, the Dasgupta-Pal cryptosystem, which we present in full to explain a correction we propose to it, and the BGV cryptosystem, which has open source implementations availble primarily used in homomorphic cryptography research.
+
+\subsection{The Dasgupta-Pal Cryptosystem}
 The Dasgupta-Pal cryptosystem is a fully homomorphic cryptosystem proposed in 2016 by Smaranika Dasgupta and S.
@@
 	\item[XOR on ciphertexts]
-	An exclusive or (XOR) operation on integer messages can be achieved by adding the coefficients pairwise between two ciphertexts.
+	A bitwise exclusive or (XOR) operation on integer messages can be achieved by adding the coefficients pairwise between two ciphertexts.
 	\begin{align*}
@@
 	\item[AND on ciphertexts]
-	Similarly, pair-wise multiplication of
+	Similarly, pair-wise multiplication corresponds to bitwise AND of integer messages.
 	\begin{align*}
@@
 \end{description}
+Arbitrary computation on data can thus be achived using these bitwise operations.
+
+\subsection{HElib and the BGV Cryptosystem}
+The BGV (Brakerski-Gentry-Vaikuntanathan) cryptosystem \cite{cryptoeprint:2011:277} is a fully homomorphic cryptosystem created based on the ring-learning with error problem.
+The BGV cryptosystem was constructed to surpass the limitations of prior fully homomorphic cryptosystems, which were based on the first fully homomorphic cryptosystem by Gentry \cite{gentry_fully_2009}.
+
+The details regarding the construction of the BGV cryptosystem are beyond the scope of this paper.
+For this study, we will be using \textit{HElib} \cite{garay_algorithms_2014}, an open-source library which implements the BGV cryptosystem with optimizations to improve efficiency \cite{hutchison_fully_2010,cryptoeprint:2011:566}.
+
+The \textit{HElib} library has been adapted to Python using the Pyfhel library \cite{pyfhel_2018} maintained by Ibarrondo, Laurent (SAP) and Onen (EURECOM), and licensed under the GNU GPL v3 license.
+The Pyfel library is a Python API for the HElib library, which supports the following operations on vectors/scalars of integers or binary ciphertexts:
+\begin{itemize}
+	\item Arithmetic operations: addition, subtraction, multiplication;
+	\item Binary operations: AND, OR, NOT, XOR.
+\end{itemize}

### 2018-10-06 parts/02_relatedliterature_05partiallyhomomorphic.tex
Random fixes

@@
   D(E(m_1)g^k\bmod n^2)=(m_1+k)\bmod n & \text{ (used to add a constant)}\\
-  D(E(m_1)E(m_2)\bmod n^2)=(m_1+m_2)\bmod n & \text{ (used for binary addition)}
+  D(E(m_1)E(m_2)\bmod n^2)=(m_1+m_2)\bmod n & \text{ (used for binary addition)}\\
   D(E(m_1)^k\bmod n^2)= km_1\bmod n & \text{ (used to multiply a plaintext constant)}
@@
     D(E(m_1)g^k)=(m_1+k)\bmod u & \text{ (used to add a constant)}\\
-    D(E(m_1)E(m_2))=(m_1+m_2)\bmod u & \text{ (used for binary addition)}
+    D(E(m_1)E(m_2))=(m_1+m_2)\bmod u & \text{ (used for binary addition)}\\
     D(E(m_1)^k)= km_1\bmod u & \text{ (used to multiply a plaintext constant)}

### 2018-10-06 parts/08_appendices_a_cryptosystems.tex
Random fixes

@@
 You may use this as another reference in writing your paper.
-\chapter{CORRECTION TO THE DASGUPTA-PAL CRYPTOSYSTEM}
+\chapter{CORRECTION FOR DASGUPTA-PAL}
 \label{ch:correction}
@@
 
-\subsection{Proposed Correction and Proof of Correctness}
+\section{Proposed Correction and Proof of Correctness}
 We now show that setting the secret key $S_k$ to $2p$, where $p$ is a prime, fixes the issue in the original cryptosystem.

### 2018-10-06 parts/02_relatedliterature_03facialrecognition.tex
Finalized new ordering of RRL
Restructured RRL to accomodate facial recognition
Added content for facial recognition entry

@@
-\section{Facial Recognition}
-More complex image processing operations are just made up of simpler image operations such as those mentioned earlier. 
-A prominent application of image processing is facial recognition.
+\section{Facial Detection and Recognition}
+%% TODO: Brian dump ur stuff here
+
+Since simple image operations mentioned earlier can be done within a homomorphic cryptosystem, these operations can be assembled together in order to do more complex operations.
+A prominent application of image processing that often uses complex image operations is \textit{facial recognition}.
+
+Traditional facial recognition algorithms rely on detecting salient features in a face image. Two of the popular facial recognition algorithms are \textit{eigenfaces} and \textit{Haar cascades}.
+
+\subsection{Eigenfaces}
+
+Proposed by Matthew Turk and Alex Pentland, the eigenfaces method uses principal component analysis (PCA) in order to express an input image as a linear combination of eigenfaces \cite{turk_eigenfaces_1991}.
+An \textit{eigenface} is a principal component, or more simply an eigenvector that represents a certain variation between the face images which are taken from the initial training set.
+The number of resulting eigenfaces is equal to the number of face images in the training set.
+
+In the enrollment process, $M$ face images $\Theta_1, \ldots, \Theta_M$, each of size $p \times q$, are taken in to comprise the initial training set.
+The training images can be represented as vectors of length $N = pq$, where each row of an image is concatenated together.
+
+The average of the training images, denoted as $\Psi$, is 
+\[ \Psi = \frac{1}{M} \sum_{i=1}^{M} \Theta_i \]
+
+The \textit{difference vectors} are then computed as $\Phi_i = \Theta_i - \Psi$. PCA is applied on the covariance matrix of the vectors
+\[ \mathbf{C} = \frac{1}{M} \sum_{i=1}^M \Phi_i \Phi_i^\top = \frac{1}{M} \mathbf{A}\mathbf{A}^\top,\]
+where $\mathbf{A}$ is an $N \times M$ matrix defined by $\left[\Theta_1 \quad \Theta_2 \quad \cdots \quad \Theta_M\right]$, in order to determine the orthonormal eigenvectors \cite{hutchison_privacy-preserving_2009}.
+
+Directly computing the covariance matrix and then applying PCA will become inefficient for large sizes of $\mathbf{A}$, since computing for $\mathbf{A}\mathbf{A}^\top$ results in an $N \times N$ matrix, which can get drastically large because it is dependent on the size of the image.
+On the other hand, computing for $\mathbf{A}^\top\mathbf{A}$ only results in an $M \times M$ matrix, which is much smaller than the previous one because it is just dependent on the number of face images in the training set.
+Now, we can apply PCA to $\mathbf{A}^\top\mathbf{A}$ along with some post-processing to obtain the eigenvectors \cite{hutchison_privacy-preserving_2009}.
+
+Instead of getting the eigendecomposition of the covariance matrix by explicitly computing the eigenvalues and eigenvectors of $\mathbf{C}$, we can also apply \textit{singular value decomposition} (SVD) on the matrix $\Phi^\top$.
+This is because SVD works through a divide-and-conquer method which results in greater numerical stability, while eigendecomposition simply uses the traditional QR factorization \cite{nakatsukasa_stable_2013, gu_divide-and-conquer_1995}.
+Upon applying SVD, we now get the eigenvectors $\mathbf{u}_1, \ldots, \mathbf{u}_M$ and their corresponding eigenvalues $\lambda_1, \ldots, \lambda_M$.
+
+We choose $K$ eigenvectors $\mathbf{u}_1, \ldots, \mathbf{u}_K$ such that it comprises a set associated with the $K$ largest eigenvalues, where $K$ is much smaller than $M$.
+This set is now the \textit{face space}.
+Then, the images $\Theta_1, \ldots, \Theta_K$ are projected onto the face space spanned by the eigenfaces to determine the weight vectors $\Omega_1, \ldots, \Omega_K$.
+
+To perform the recognition process, the algorithm projects the input image $\Gamma$ onto the face space, and then comparing the projected image $\bar{\Omega} = \mathbf{u}_i\left(\Gamma - \Psi\right)$ with each eigenface in the face space using a metric such as the Euclidean distance.
+Thus it is computed as $d_i = \left\lVert \Omega_i -\bar{\Omega} \right\rVert$ for all $i=1,\ldots,K$, where $\left\lVert \cdot \right\rVert$ denotes the Euclidean norm.
+
+Then, a match can be reported if the smallest possible distance is smaller than the given threshold value $T$. 
+\newcommand{\argmin}{\mathop{\mathrm{arg\,min}}}  
+\[\text{ID} = \begin{cases}\argmin_i d_i & \text{if } \min_i d_i \le T \\\emptyset & \text {otherwise}\end{cases}
+\]
+
+\subsection{Haar Cascades [WIP]}
+A \textit{Haar cascade classifier} is another method for facial recognition by Paul Viola and Michael Jones.
+It uses Haar-like features to detect regularities in a face image.
+A \textit{Haar-like feature} looks at a certain rectangular region of the image through a filter-like window.
+
+\begin{figure}[!h]
+    \centering
+    \includegraphics[width=7cm]{figures/haarfeatures2.png}
+    \caption{Examples of Haar-like features \cite{viola_robust_2004}.}
+\end{figure}
+
+A Haar-like feature is composed of black and white rectangles, and arranged such that it detects a presence or an absence of a particular image feature or regularity of interest.
+For example, a feature may detect the difference in intensities between the eyes and the cheeks, another feature would detect the nose bridge, and another one would detect depending on the location of the eyes.
+The detection is done by summing up the intensities within the black region and the white region, and then calculating the difference.
+
+Getting the sum of pixel intensities within a region na\"{i}vely would become inefficient as the size of the rectangular region increases, so a data structure called an \textit{integral image} is used to allow more efficient detection of Haar-like features.
+In other words, an integral image is essentially a two-dimensional range sum that can compute sums of rectangular regions in constant time, regardless of the size of the regions.
+
+Most of the Haar-like features are irrelevant, because a feature that works in a certain part of the image would not necessarily work in another part.
+The whole process may become needlessly inefficient due to computational time being potentially wasted on a huge number of irrelevant features, even though computing for a feature is said to be efficient.
+That is why we need to select the best features and use those to form a strong classifier in a process called AdaBoost.
+
+In itself, a Haar feature is considered as a \textit{weak classifier}, where the probability of detecting a certain feature is slightly greater than detecting at random.
+Because of this, a large number of Haar features must be used together by forming them into cascade classifiers in order to achieve a sufficient enough accuracy.
+The resulting strong classifier would then be a linear combination of the weak classifiers.
+
+\[h \left(x, f, p, \theta \right) = \begin{cases}1 & \text{if } pf(x) < p\theta\\ 0 & \text{otherwise}\end{cases}
+\]

### 2018-10-07 parts/02_relatedliterature_02commonimageprocessingoperations.tex

@@
 \end{equation}
-where $c$ is a constant and $r \ge 0$.
+where $c$ is a constant.
 
@@
 \end{align*}
-Since spatial filters take values from a contiguous region of pixels, this presents a difficulty in homomorphic cryptosytems: in order for spatial filters to be performed, the location of each pixel relative to neighboring pixels has to be preserved.
+Since spatial filters take values from a contiguous region of pixels, this presents a difficulty in homomorphic cryptosystems: in order for spatial filters to be performed, the location of each pixel relative to neighboring pixels has to be preserved.
 This was performed in the implementation of spatial filters in the \textit{CryptoImg} library~\cite{ziad_cryptoimg:_2016}.

### 2018-10-07 parts/03_methodology.tex

@@
 Aside from implementing the homomorphic encryption and decryption algorithms, we will also implement library functions for the following image processing functions, as they are defined in~\cite{gonzalez_digital_2008}.
-We will also take note of whether or not a candidate operation is impossible to perform under a given cryptosystem.
+%We will also take note of whether or not a candidate operation is impossible to perform under a given cryptosystem.
 We let $R(x,y)$ denote the intensity at coordinate $(x,y)$ in the source image, and $S(x,y)$ denote the intensity at coordinate $(x,y)$ in the resulting image.
 We further suppose that the intensity values of pixels are in the range $[0, L-1]$.
-\begin{description}
-	\item[Intensity transformations.] Transformations on the intensities of each of the pixels on an image. The following definitions hold for all $x,y$.
-	\begin{enumerate}
-		\item Image negation: $S(x,y) = L - 1 - R(x,y)$.
-		\item Log transformation: $S(x,y) = c\log{(1 + R(x,y))}$, $c \geq 0$.
-		\item Power-law transformation: $S(x,y) = c[R(x,y)]^\gamma$, $c > 0, \gamma > 0$.
-	\end{enumerate}
-	\item[Spatial filters.] Filters implemented by performing a convolution between an $M\times N$ source image and an $m\times n$ kernel.
+%\begin{description}
+%	\item[Intensity transformations.] Transformations on the intensities of each of the pixels on an image. The following definitions hold for all $x,y$.
+%	\begin{enumerate}
+%		\item Image negation: $S(x,y) = L - 1 - R(x,y)$.
+%		\item Log transformation: $S(x,y) = c\log{(1 + R(x,y))}$, $c \geq 0$.
+%		\item Power-law transformation: $S(x,y) = c[R(x,y)]^\gamma$, $c > 0, \gamma > 0$.
+%	\end{enumerate}
+%	\item[Spatial filters.] Filters implemented by performing a convolution between an $M\times N$ source image and an $m\times n$ kernel.
 Let $k$ be a kernel.
 Then the corresponding spatial filter is given by
-	\begin{align}
-		S(x,y) = \sum_{s=1}^m{\sum_{t=1}^n{k(s,t)R(x+s,y+t)}}.
-	\end{align}
-	Morphological operations such as erosion and dilation can be achieved using convolution as well.
-\end{description}
+%	\begin{align}
+%		S(x,y) = \sum_{s=1}^m{\sum_{t=1}^n{k(s,t)R(x+s,y+t)}}.
+%	\end{align}
+%	Morphological operations such as erosion and dilation can be achieved using convolution as well.
+%\end{description}
+
+\input{parts/03_methodology_01nonlinearintensitytransformations}
 

### 2018-10-07 parts/02_relatedliterature.tex
RRL summary and fixes
- Commented out spatial filter section
- Updated summary to reflect new research
- Fixed some typesetting errors in D-P section

@@
 \section{Summary}
-We have seen how various image processing operations make use of a series of additions and multiplications.
-Because of this, it is possible to use a homomorphic cryptosystem in order to apply image operations directly on encrypted images, as demonstrated by the \textit{CryptoImg} library.
+We have seen how privacy-preserving image operations have been implemented in the literature using partially homomorphic cryptosystems.
+\textit{CryptoImg} provided a suite of linear image processing operations using the Paillier cryptosystem, while Erkin, et al.
+have implemented a privacy-preserving version of the eigenfaces approach to facial recognition developed by Turk and Pentland.
 
-In particular, we aim to address the shortcomings of \textit{CryptoImg} by developing a library to test various homomorphic encryption schemes with the help of the \textit{HElib} library to be able to implement fully homomorphic encryption schemes efficiently.
-This helps us determine the practicality of using homomorphic cryptosystems in image processing, especially when dealing with more complex image operations.
+We have presented as well several areas in which our study will expand on the research so far.
+\begin{enumerate}
+  \item We have shown two fully homomorphic cryptosystems, the Dasgupta-Pal cryptosystem and the BGV cryptosystem.
+While these cryptosystems are generally less efficient than partially homomorphic cryptosystems, they do not require additional protocols for exponentiation.
+  \item Due to the general limitations of partially homomorphic systems, attempts at applying homomorphic cryptography to applications such as image processing and facial recognition have mainly been restricted to linear operations on ciphertext.
+We have shown that there are basic image processing operations which are non-linear, which we can implement.
+  \item While privacy-preserving facial recognition has been accomplished by Erkin, et al., privacy-preserving facial detection is an area of research which has yet to explored.
+\end{enumerate}

### 2018-10-07 parts/02_relatedliterature_02commonimageprocessingoperations.tex
RRL summary and fixes
- Commented out spatial filter section
- Updated summary to reflect new research
- Fixed some typesetting errors in D-P section

@@
-\section{Image Processing Operations}
-The \textit{CryptoImg} library implemented several
-We discuss two basic types of image processing operations, \textit{intensity transformations}, which map an intensity value to another, and \textit{spatial filters} which consider intensity values from regions of pixels to perform operations such as edge detection, image blurring and sharpening.
+%We discuss two basic types of image processing operations, \textit{intensity transformations}, which map an intensity value to another, and \textit{spatial filters} which consider intensity values from regions of pixels to perform operations such as edge detection, image blurring and sharpening.
 
+\section{Image Intensity Transformations}
 We represent a digital image $R$ as an $M \times N$ matrix of pixel intensity values, each value in the range $\left[0, L-1\right]$, for some positive integer $L$.
 We use $R(x,y)$ represents the entry at the $x$th row and $y$th column of a matrix $R$.
+An intensity transformation on an image $R$ can be defined as a function $T$ which maps a pixel value $r$ to a new value $r^\prime$, which we can write as $r^\prime = T\left(r\right)$.
+This function is then applied to every pixel in $R$.
+The \textit{CryptoImg} library implemented two types of linear intensity transformations: image negation and brightness control.
 
-\subsection{Intensity Transformations}
-An Intensity transformation on an image $R$ can be defined as a function $T$ which maps a pixel value $r$ to a new value $r^\prime$, which we can write as $r^\prime = T\left(r\right)$.
-This function is then applied to every pixel in $R$.
-
-The \textit{CryptoImg} library implemented two types of linear intensity transformations: image negation and brightness control.
 An image negation transformation is defined as:
@@
 To implement non-linear intensity transformations using addition and multiplication in a homomorphic system, it is necessary to approximate the logarithm and exponential functions, which may result in higher computational overhead.
-In our software library implementation, we investigate methods required to approximate the logarithm and functions.
+In our software library implementation, we investigate methods required to approximate the logarithm and power functions.
+Non-linear intensity transformations such as the logarithm transformation have applications in intensity normalization \cite{oravec_illumination_2010}, which is used in some facial recognition algorithms to account for differences in lighting which make facial recognition difficult.
 
+\begin{comment}
 \subsection{Spatial Filtering}
@@
 %% TODO: specific list of kernels to use for this study
+\end{comment}

### 2018-10-07 parts/02_relatedliterature_06fullyhomomorphic.tex
RRL summary and fixes
- Commented out spatial filter section
- Updated summary to reflect new research
- Fixed some typesetting errors in D-P section

@@
 
-Given a message $m \in \mathbb{n}$, we denote
+Given a message $m \in \mathbb{Z}$, we denote
 \begin{align*}
@@
 In the original scheme presented in \cite{dasgupta_design_2016}, the secret key $S_k$ is set to be a large prime.
-In Appendix \autoref{ch:correction}, we present a case where the Dasgupta-Pal cryptosystem fails and prove that setting the secret key $S_k = 2p$, where $p$ is a large prime, corrects errors in the Dasgupta-Pal cryptosystem.
+In Appendix \ref{chap:correction}, we present a case where the Dasgupta-Pal cryptosystem fails and prove that setting the secret key $S_k = 2p$, where $p$ is a large prime, corrects errors in the Dasgupta-Pal cryptosystem.
 We now decribe the correct cryptosystem.
@@
 \begin{align*}
-	m_p(x) = c(x) \bmod S_k \bmod 2
+	m_p(x) = c(x) \bmod S_k \bmod 2.
 \end{align*}
-Thus $D(c(x))$ is defined as the integer recovered from the coefficients of the polynomial $c(x) \bmod S_k \bmod 2$
+Thus $D(c(x))$ is defined as the integer recovered from the coefficients of the polynomial $c(x) \bmod S_k \bmod 2$.
 
 Dasgupta and Pal note that homomorphic operations on ciphertext introduce noise which may interfere with decryption, due to the potential increase in ciphertext values.
-To eliminate noise from a polynomial ciphertext, the following refresh function is used.
+To eliminate noise from a polynomial ciphertext, the following refresh function is used:
 \begin{align*}
-	R(c(x)) = c(x) \bmod R_k
+	R(c(x)) = c(x) \bmod R_k.
 \end{align*}
@@
 \end{description}
+
 Arbitrary computation on data can thus be achived using these bitwise operations.
+While the Dasgupta-Pal cryptosystem requires significant amounts of memory, as each bit of plaintext is encrypted into an integer, this approach provides a flexible method to perform relatively fast arbitrary computation on encrypted data.
+Encryption and decryption in the Dasgupta-Pal cryptosystem are accomplished using few arithmetic operations.
 
@@
 The details regarding the construction of the BGV cryptosystem are beyond the scope of this paper.
-For this study, we will be using \textit{HElib} \cite{garay_algorithms_2014}, an open-source library which implements the BGV cryptosystem with optimizations to improve efficiency \cite{hutchison_fully_2010,cryptoeprint:2011:566}.
+For this study, we will be using \textit{HElib} \cite{garay_algorithms_2014}, an open-source library which implements the BGV cryptosystem with optimizations to improve efficiency.
+Evaluation of operations on 120 inputs in HELib was performed in around 4 minutes, with an average of 2 seconds to process a single input \cite{hutchison_fully_2010,cryptoeprint:2011:566}.
 

### 2018-10-07 parts/02_relatedliterature_05partiallyhomomorphic.tex
Updated Ch 3
- Chapter 3 updated to reflect changes in the thesis scope

@@
 \subsection{General Exponentiation Protocol for Pailler and DGK}
+\label{ssec:exponentiationprotocol}
 In order to perform polynomial evaluation, we first present a protocol for privacy-preserving exponentiation to a positive integer power, adapted from the protocol to calculate Euclidean distances used in \cite{hutchison_privacy-preserving_2009}.

### 2018-10-07 parts/03_methodology.tex
Updated Ch 3
- Chapter 3 updated to reflect changes in the thesis scope

--- 2018-09-30 parts/03_methodology.tex
@@
 
-The study consists of two parts: first, the implementation of the three homomorphic encryption schemes~\cite{ziad_cryptoimg:_2016, dasgupta_design_2016, hutchison_fully_2010} and image processing operations under each scheme as an OpenCV library.
-While the scheme in~\cite{ziad_cryptoimg:_2016} has been implemented for use in image processing, the fully homomorphic systems~\cite{dasgupta_design_2016, hutchison_fully_2010} will have to be adapted for image processing.
-The second part of the study consists of assessing the robustness and security of image operations under each encryption scheme using benchmarks in~\cite{ahmed_benchmark_2016}.
+In this study we apply four homomorphic encryption schemes~\cite{ziad_cryptoimg:_2016, pieprzyk_efficient_2007, dasgupta_design_2016, garay_algorithms_2014} for use in image processing and facial recognition applications.
+While the Pailler and DGK cryptosystems have been implemented for use in image processing in~\cite{ziad_cryptoimg:_2016, hutchison_privacy-preserving_2009}, the other cryptosystems have to be adapted for this study.
 
-\section{Implementation of the OpenCV Library}
+Two experiments will be conducted in this study:
+\begin{enumerate}
+	\item Assessment of non-linear image intensity transformations under each of the four cryptosystems.
+	\item Assessment of efficiency of each of the four cryptosystems when applied for use in privacy-preserving facial recognition and detection using eigenfaces.
+\end{enumerate}
+The results of the image intensity transformations will be tested for image quality using benchmarks in~\cite{ahmed_benchmark_2016}.
 
-The current version of the OpenCV library (3.4.2) will be forked from the open-source GitHub repository at \url{https://github.com/opencv/opencv}~\cite{bradski_opencv_2000}.
+\section{Cryptosystem Implementation}
 
-Three homomorphic encryption schemes will be implemented, those presented by Ziad, et al.~\cite{ziad_cryptoimg:_2016}, Dasgupta and Pal~\cite{dasgupta_design_2016} and Smart and Vercauteren~\cite{hutchison_fully_2010}.
-The encryption and decryption methods will be implemented in Python.
-However, these methods will be also implemented in C++ if time permits.
+The current version of the OpenCV library (3.4.2) will be forked from the open-source GitHub repository at \url{https://github.com/opencv/opencv})~\cite{bradski_opencv_2000}.
 
-Aside from implementing the homomorphic encryption and decryption algorithms, we will also implement library functions for the following image processing functions, as they are defined in~\cite{gonzalez_digital_2008}.
-We will also take note of whether or not a candidate operation is impossible to perform under a given cryptosystem.
-We let $R(x,y)$ denote the intensity at coordinate $(x,y)$ in the source image, and $S(x,y)$ denote the intensity at coordinate $(x,y)$ in the resulting image.
-We further suppose that the intensity values of pixels are in the range $[0, L-1]$.
-\begin{description}
-	\item[Intensity transformations.] Transformations on the intensities of each of the pixels on an image. The following definitions hold for all $x,y$.
-	\begin{enumerate}
-		\item Image negation: $S(x,y) = L - 1 - R(x,y)$.
-		\item Log transformation: $S(x,y) = c\log{(1 + R(x,y))}$, $c \geq 0$.
-		\item Power-law transformation: $S(x,y) = c[R(x,y)]^\gamma$, $c > 0, \gamma > 0$.
-	\end{enumerate}
-	\item[Spatial filters.] Filters implemented by performing a convolution between an $M\times N$ source image and an $m\times n$ kernel.
-Let $k$ be a kernel.
-Then the corresponding spatial filter is given by
-	\begin{align}
-		S(x,y) = \sum_{s=1}^m{\sum_{t=1}^n{k(s,t)R(x+s,y+t)}}.
-	\end{align}
-	Morphological operations such as erosion and dilation can be achieved using convolution as well.
-\end{description}
+Four homomorphic encryption schemes will be investigated.
+For cryptosystems with readily available open-source implementations, such implmentations will be used.
+For the remaining cryptosystems, the encryption and decryption methods will be implemented in Python.
+\begin{itemize}
+	\item The Pailler cryptosystem will be incorporated using the implementation at \url{https://github.com/n1analytics/python-paillier} developed by Data61 - CSIRO.
+	\item The BGV cryptosystem will be implemented using the Pyfhel library (\url{https://github.com/ibarrond/Pyfhel}) using a HElib backend from (\url{https://github.com/shaih/HElib}).
+	\item The DGK and Dasgupta-Pal cryptosystem will be implemented from scratch.
+\end{itemize}
+
+\input{parts/03_methodology_01integertorealnumbers}
+\input{parts/03_methodology_02nonlinearintensitytransformations}
 
@@
 
-We will first obtain standard test images from~\cite{gonzalez_image_nodate}. Both grayscale and color images will be used.
+Lab computers in Faura Hall, Ateneo de Manila University will be used to perform the computations, and processing time will be tracked using built-in timing functions.
+The processing time for all cases will be recorded.
+
+\subsection{Evaluating Image Quality for Intensity Transformations}
+In this section, we discuss the image quality metrics we will use for assessing the performance of non-linear intensity transformations.
+
+We will first obtain standard test images from~\cite{gonzalez_image_nodate}. Grayscale images will be used in the study.
 
@@
 
-Lab computers in Faura Hall, Ateneo de Manila University will be used to perform the computations, and processing time will be tracked using built-in timing functions.
-The processing time for all cases will be recorded.
-
-\subsection{Evaluating Image Quality}
 The benchmarks to be used in the study, adopted from~\cite{ahmed_benchmark_2016, ahmad_efficiency_2012, wu_npcr_2011} are listed below.
@@
 
+\subsection{Facial Recognition Tests}
+%% TODO: Brian, can you fill this part up?
+
 \section{Summary}
-
 In summary, the study will consist of
 \begin{itemize}
-	\item An implementation of an OpenCV library which implements homomorphic cryptosystems by Ziad, et al.~\cite{ziad_cryptoimg:_2016}, Dasgupta and Pal~\cite{dasgupta_design_2016} and Smart and Vercauteren~\cite{hutchison_fully_2010}.
-	\item An implementation of image processing operations (intensity transformations, spatial filters) under the above cryptosystems.
+	\item An implementation of an OpenCV library which implements the Pailler, DGK, Dasgupta-Pal, and BGV homomorphic cryptosystems.
+	\item An implementation of image processing operations (intensity transformations, facial recognition) under the above cryptosystems.
 	\item Conducting tests for image quality, processing time, using standard test images from~\cite{gonzalez_image_nodate}.
@@
 
-These will be conducted over the course of the first semester of AY 2018--2019 to allow for analysis of the results and paper preparation in the second semester.
-Additional cryptosystems, image operations, and cryptographic security tests may be included in the scope of the study, depending on future research.
-
-We now provide a summary of how each of our research questions are addressed by the methodology.
-\begin{itemize}
-	\item \textbf{Applicablity of homomorphic encryption algorithms for the use of image processing operations on encrypted data?} This will be addressed by the implementation of OpenCV library, and the evaluation of image quality (MSE, PSNR, SSIM).
-	\item \textbf{Time efficiency in applying image manipulation operations.} This will be addressed by the implementation of OpenCV library, and the comparison of recorded processing time for image processing operations.
-	\item \textbf{Security under differential and entropy attacks.}
-	This will be addressed by the evaluation of security benchmarks for image encryption schemes (entropy analysis, correlation coefficient analysis, NPCR, UACI).
-\end{itemize}
+%% insert flowchart/diagrams here

### 2018-10-07 parts/03_methodology_01integertorealnumbers.tex
Updated Ch 3
- Chapter 3 updated to reflect changes in the thesis scope

\section{Secure Computation with Real Numbers}
We will briefly discuss a protocol to enable cryptosystems built for integer inputs to handle real number inputs.
The following protocol was also used by \textit{CryptoImg} for image processing \cite{ziad_cryptoimg:_2016}.

We represent a floating-point (FP) number as a pair of two integers $(m,e)$ representing the mantissa and exponent of the FP number with respect to a base $b$. The mantissa $m$ is encrypted, while the exponent $e$ is unencrypted.
Let $a,b,c$ be FP numbers represented by the pairs $(m_a,e_a),(m_b,e_b),(m_c,e_c)$ respectively. Let $\oplus,\otimes$ represent the homomorphic operations which correspond to the addition and multiplication, respectively. We define the secure real number operations as follows:
\begin{description}
  \item[Addition.]
    To compute $E(c)=E(a+b)$ we compute
    \begin{align*}
      E(m_c) &= E(m_1) \oplus (b^{e_b-e_a} \otimes E(m_b)), e_c = e_a & \text{ if } e_a \leq e_b \\
      E(m_c) &= E(m_b) \oplus (b^{e_a-e_b} \otimes E(m_a)), e_c = e_b & \text{ if } e_a > e_b
    \end{align*}
  \item[Scalar multiplication.]
    To compute $E(c) = E(ab)$, where $a$ and $E(b)$ are known (i.e. $m_a$ is not encrypted), we compute
    \begin{align*}
      E(m_c) &= m_a \otimes E(m_b)\\
      e_c &= e_a + e_b
    \end{align*}
\end{description}

### 2018-10-07 parts/03_methodology_02nonlinearintensitytransformations.tex
Updated Ch 3
- Chapter 3 updated to reflect changes in the thesis scope

%We will also take note of whether or not a candidate operation is impossible to perform under a given cryptosystem.  We let $R(x,y)$ denote the intensity at coordinate $(x,y)$ in the source image, and $S(x,y)$ denote the intensity at coordinate $(x,y)$ in the resulting image. We further suppose that the intensity values of pixels are in the range $[0, L-1]$.
%\begin{description}
%	\item[Intensity transformations.] Transformations on the intensities of each of the pixels on an image. The following definitions hold for all $x,y$.
%	\begin{enumerate}
%		\item Image negation: $S(x,y) = L - 1 - R(x,y)$.
%		\item Log transformation: $S(x,y) = c\log{(1 + R(x,y))}$, $c \geq 0$.
%		\item Power-law transformation: $S(x,y) = c[R(x,y)]^\gamma$, $c > 0, \gamma > 0$.
%	\end{enumerate}
%	\item[Spatial filters.] Filters implemented by performing a convolution between an $M\times N$ source image and an $m\times n$ kernel. Let $k$ be a kernel. Then the corresponding spatial filter is given by
%	\begin{align}
%		S(x,y) = \sum_{s=1}^m{\sum_{t=1}^n{k(s,t)R(x+s,y+t)}}.
%	\end{align}
%	Morphological operations such as erosion and dilation can be achieved using convolution as well.
%\end{description}

\section{Non-Linear Intensity Transformations}
Aside from implementing the homomorphic encryption and decryption algorithms, we will also implement library functions for image negation, logarithm transformation and power-law transformation, as they are defined in~\cite{gonzalez_digital_2008}.
We now describe how we implement the logarithm and power-law image intensity transformations. In the case of partially homomorphic cryptosystems (Pailler, DGK), the following considerations will be made regarding required homomorphic operations not supported by the cryptosystems:
\begin{enumerate}
	\item If exponentiation is required, the secure exponentiation protocol in section \ref{ssec:exponentiationprotocol} will be used.
	\item If multiplication of ciphertexts $E(m_1), E(m_2)$ is required, the following protocol will be used:
	\begin{itemize}
		\item Bob calculates $E(m_1+m_2)$ and using the exponentiation protocol, acquires $E(m_1^2),E(m_2^2),E((m_1+m_2)^2)$.
		\item Bob can recover the product of the ciphertexts by computing
		\begin{align*}
			E((m_1+m_2)^2) - E(m_1^2) - E(m_2^2) = E(2m_1m_2),
		\end{align*}
		then carrying out the required constant multiplication to obtain $E(2m_1m_2)$.
	\end{itemize}
\end{enumerate}
\subsection{Logarithm Transformation}
The logarithm transformation of a pixel intensity value $x$ is defined as
\begin{align}
	T\left(x\right) = c \log\left(1 + x\right)
\end{align}
where $c$ is a constant.

In order to perform this transformation under a homomorphic cryptosystem, we must provide an approximation for $\log\left(1 + x\right)$ in terms of addition and multiplication operations (or their inverses). We have derived a closed form approximation in Appendix \ref{sec:logapproximation}.
\begin{align}
	\label{eq:scaledquadraturech3}
  \begin{split}
    &\log(1+x) \\
    &=\frac{137x^5 + 33185x^4 + 931370x^3 - 13403630x^2 - 289469315x - 713567363}
    {30(x^5 + 505x^4 + 42010x^3 + 923010x^2 + 5722005x + 8040501)} + \log{20}
  \end{split}
\end{align}

\subsection{Power-Law Transformation}
The power-law transformation of a pixel intensity value $x$ is defined as
\begin{equation}
    T\left(x\right) = cx^{\gamma}
\end{equation}
where $c>0$ and $\gamma > 0$.

Similar to the logarithm transformation, we must provide an approximation for $x^\gamma$.
We have derived an infinite series in Appendix \ref{sec:logapproximation}.
\begin{align*}
	x^\gamma &= \sum_{n=0}^{\infty}{\frac{(\gamma\log{x})^n}{n!}}
\end{align*}
Partial sums of the above infinite series can be calculated based on the closed form approximation for the logarithm in Equation \ref{eq:scaledquadraturech3}.

### 2018-10-07 parts/01_introduction_03objectives.tex
Updated Chapter 1
updated chapter 1 to have references to facial recognition

@@
 
-A paper published in 2009 by Ziad, et.
-al.
-presents \textit{CryptoImg}, a library for the  Open Source Computer Vision Library (OpenCV)~\cite{bradski_opencv_2000} which implements various homomorphic encryption and image processing routines using the Paillier homomorphic cryptosystem~\cite{ziad_cryptoimg:_2016}.
-While \textit{CryptoImg} demonstrates that various image manipulation operations are possible in a homomorphic cryptosystem, we believe this study can be extended by considering other known homomorphic encryption schemes, such as those found in~\cite{li_elliptic_2012, hutchison_fully_2010}.
-Our study aims to provide an objective comparison of various homomorphic cryptosystems currently in the literature, as they would be used in encrypted image manipulation.
+Previous attempts in the literature to provide image processing tasks such as image manipulation \cite{ziad_cryptoimg:_2016} and  facial recognition \cite{hutchison_privacy-preserving_2009} have primarily used the Paillier and DGK cryptosystems to perform linear operations on encrypted data.
+In this study, we extend this research to provide an objective comparison of various homomorphic cryptosystems currently in the literature in performing non-linear operations, as opposed to just linear operations, and facial detection, as opposed to just facial recognition.
 
@@
 Homomorphic cryptosystems are known to be slower in terms of encryption, operation, and decryption time~\cite{sen_homomorphic_2013}.
-Furthermore, the operations on encrypted data supported by homomorphic cryptosystems are limited, and some schemes require preprocessing to be performed on images, limiting the range of operations which can be performed~\cite{li_elliptic_2012}.
-Finally, as data security is the primary purpose of cryptosystems, we want to evaluate the security of homomorphic cryptosystems as image encryption schemes.
+Furthermore, the operations on encrypted data supported by homomorphic cryptosystems are limited, and some schemes require preprocessing to be performed on images, limiting the range of operations which can be performed efficiently~\cite{li_elliptic_2012}.
 
@@
     \item Compare the time efficiency of common image processing operations under known homomorphic encryption schemes;
-    \item Create a library for OpenCV to allow for convenient use and comparison of these homomorphic encryption schemes.
+    \item Create a library for the Open Source Computer Vision Library (OpenCV) to allow for convenient use and comparison of these homomorphic encryption schemes for image processing and facial recognition.
 \end{enumerate}

### 2018-10-07 parts/01_introduction_04significanceofstudy.tex
Updated Chapter 1
updated chapter 1 to have references to facial recognition

@@
 This study aims to directly address one of the current problems in the research of homomorphic cryptosystems: the practicality of homomorphic encryption~\cite{sen_homomorphic_2013}.
-The literature shows existing homomorphic cryptosystems and how they support primitive operations (usually addition and multiplication) on encrypted data, however, for homomorphic cryptosystems to be useful for practical use, support for more complicated image processing operations such as image convolution must be demonstrated as well.
-While implementations of image processing operations in a homomorphic cryptosystem exist in the literature~\cite{ziad_cryptoimg:_2016, garay_algorithms_2014}, our study targets algorithms for which statistical tests have not been performed for image processing operations.
+The literature shows existing homomorphic cryptosystems and how they support primitive operations (usually addition and multiplication) on encrypted data, however, for homomorphic cryptosystems to be useful for practical use, efficient support for more complicated image processing operation must be demonstrated as well.
+While implementations of image processing operations in a homomorphic cryptosystem exist in the literature~\cite{ziad_cryptoimg:_2016, garay_algorithms_2014}, our study targets the more computationally intensive task of facial detection.
 

### 2018-10-07 parts/01_introduction_05scopeandlimitations.tex
Updated Chapter 1
updated chapter 1 to have references to facial recognition

@@
 	\item A variant of the Paillier cryptosystem~\cite{stern_public-key_1999} which supports floating-point operations, used in \textit{CryptoImg}~\cite{ziad_cryptoimg:_2016}.
-	\item The Benlano cryptosystem~\cite{benaloh_dense_1994} which is a probabilistic cryptosystem which relies on the hardness of the discrete logarithm.
+	\item The Damgård-Geisler-Krøigaard (DGK) cryptosystem~\cite{pieprzyk_efficient_2007, cryptoeprint:2008:321} which is primarily used for secure integer comparison.
 	\item A fully homomorphic encryption scheme by Dasgupta and Pal, which uses polynomial rings~\cite{dasgupta_design_2016}.
-	\item A fully homomorphic encryption scheme by Smart and Vercauteren \cite{hutchison_fully_2010}, an improvement on the lattice-based cryptosystem by Gentry~\cite{gentry_fully_2009}.
+	\item The Brakerski-Gentry-Vaikuntanathan (BGV) cryptosystem \cite{cryptoeprint:2011:277}, an improvement on the lattice-based cryptosystem by Gentry~\cite{gentry_fully_2009}, with optimizations from Smart, Vercauteren and Halevi \cite{hutchison_fully_2010, cryptoeprint:2011:566}.
 \end{enumerate}
@@
 \begin{enumerate}
-	\item Image adjustment
-	\item Spatial filters/morphological operations
+	\item Non-linear image intensity adjustment (logarithm and power-log transformations)
+	\item Facial detection and recognition using the eigenface approach \cite{turk_eigenfaces_1991}.
 \end{enumerate}
@@
 \end{enumerate}
-A detailed overview of the above will be provided in the methodology.
-Both grayscale and color images will be used in the study.
-
-The study will only consider the operation of the stated algorithms in a single computer. Client-server models for secure data storage and operation will not be considered.
+A detailed overview of the above will be provided in the methodology. Grayscale images will be used in the study.
+A client-server model for secure computation will be assumed to allow operations such as secure comparison and exponentiation.

### 2018-10-07 parts/02_relatedliterature_01cryptoimg.tex
Updated Chapter 1
updated chapter 1 to have references to facial recognition

@@
 \section{CryptoImg}
-A recent attempt in the literature to implement privacy-preserving image processing is the \textit{CryptoImg} software library, presented by Ziad, et al.
-in 2016 \cite{ziad_cryptoimg:_2016}.
+A paper published in 2009 by Ziad, et.
+al.
+attempts to implement privacy-preserving image processing using \textit{CryptoImg}, a library for the Open Source Computer Vision Library (OpenCV)~\cite{bradski_opencv_2000} which implements various homomorphic encryption and image processing routines using the Paillier homomorphic cryptosystem~\cite{ziad_cryptoimg:_2016}.
 The CryptoImg library assumed a client-server model wherein a client requests image processing operations from a server.

### 2018-10-07 parts/02_relatedliterature_05partiallyhomomorphic.tex
Updated Chapter 1
updated chapter 1 to have references to facial recognition

@@
 \subsection{The DGK Cryptosystem}
-The DGK cryptosystem was published by Damgard, Geisler, and Krøigaard in 2007 in an effort to create a secure integer comparison scheme \cite{pieprzyk_efficient_2007, cryptoeprint:2008:321} which is widely used in the literature \cite{veugen_improving_2012}.
+The DGK cryptosystem was published by Damgård, Geisler, and Krøigaard in 2007 in an effort to create a secure integer comparison scheme \cite{pieprzyk_efficient_2007, cryptoeprint:2008:321} which is widely used in the literature \cite{veugen_improving_2012}.
 

### 2018-10-07 parts/02_relatedliterature_07previousimplementations.tex
Finalized new ordering of RRL
Restructured RRL to accomodate facial recognition
RRL summary and fixes
- Commented out spatial filter section
- Updated summary to reflect new research
- Fixed some typesetting errors in D-P section
Finished Haar cascades and secure eigenfaces

--- 2018-09-30 parts/02_relatedliterature_05previousimplementations.tex
@@
 \section{Related Work and Previous Implementations}
+
+%% THIS SECTION IS MARKED FOR DELETION / AMPUTATION
 % CryptoImg
@@
 
-There has been work done regarding the application of homomorphic cryptosystems in image processing.
+%There has been work done regarding the application of homomorphic cryptosystems in image processing.
 In particular, Ziad, et al.
@@
 
-However, a major limitation of \textit{CryptoImg} is that it does not consider image security.
+%However, a major limitation of \textit{CryptoImg} is that it does not consider image security.
 Even though the authors have established that the Paillier cryptosystem itself cannot be broken \cite{ziad_cryptoimg:_2016}, we believe that a cryptanalysis of the encrypted images after they have been operated is necessary, since image operations may be considered additional information in a known plaintext attack.
 
-Furthermore, Ziad, et al.
+%Furthermore, Ziad, et al.
 only presented a visual comparison and evaluation to establish the quality of the recovered images.
@@
 
-This study can be further improved by also considering the use of fully homomorphic cryptosystems such as the one presented by Dasgupta and Pal \cite{dasgupta_design_2016}, and the fully homomorphic cryptosystem introduced by Smart and Vercauteren \cite{hutchison_fully_2010} and improved by Gentry and Halevi  \cite{hutchison_implementing_2011}.
+%This study can be further improved by also considering the use of fully homomorphic cryptosystems such as the one presented by Dasgupta and Pal \cite{dasgupta_design_2016}, and the fully homomorphic cryptosystem introduced by Smart and Vercauteren \cite{hutchison_fully_2010} and improved by Gentry and Halevi  \cite{hutchison_implementing_2011}.
 These fully homomorphic cryptosytems have yet to be implemented for image processing operations.
@@
 % HElib
-Another related work would be the implementation of a fully homomorphic encryption.
+%Another related work would be the implementation of a fully homomorphic encryption.
 Halevi and Shoup \cite{garay_algorithms_2014} introduced \textit{HElib}, a library that implements the Brakerski--Gentry--Vaikuntanathan (BGV) homomorphic cryptosystem.
 This library also makes use of various optimizations to speed up the homomorphic operations, due to homomorphic cryptosystems being slower than other cryptosystems \cite{sen_homomorphic_2013}.
+
+Erkin, et al.
+\cite{hutchison_privacy-preserving_2009-2} devised a method to incorporate the use of homomorphic cryptosystems into the eigenfaces method.
+In their study, they proposed a two-party system where Alice holds an encrypted image $\left[\Gamma\right]$, while Bob maintains a database of $K$ eigenfaces $\mathbf{u}_1, \ldots, \mathbf{u}_K$, and feature vectors $\Omega_1, \ldots, \Omega_M$ in the clear.
+
+\begin{figure}[!h]
+    \centering
+    \includegraphics[width=7cm]{figures/secure_eigenfaces.png}
+    \caption{A diagram of the process \cite{hutchison_privacy-preserving_2009-2}.}
+\end{figure}
+
+In order to ensure privacy, the steps in the eigenfaces algorithm, namely: projection, distance computation, and match finding, are done within the encrypted domain, i.e., using the operations in the Paillier cryptosystem.
+
+Projection is similar to that of the original eigenfaces algorithm, except the operations are replaced with their respective operations in the cryptosystem.
+Distance computation in this version is somewhat different from the original eigenfaces method, in that it deals with the square of the Euclidean distance since the relative order of the distances is only important when comparing these during the match finding step \cite{hutchison_privacy-preserving_2009-2}.
+\begin{align*}
+    d_i &= \left\lVert \Omega_i - \bar{\Omega} \right\rVert ^2 = \sum_{j=1}^{K} \left(\omega_{ij} - \bar{\omega}_j\right)^2 \\
+        &= \underbrace{\sum_{j=1}^{K} \omega_{ij}^2}_{\mathcal{S}_1} + \underbrace{\sum_{j=1}^{K} \left(-2 \omega_{ij} \bar{\omega_j}\right)}_{\mathcal{S}_2} + \underbrace{\sum_{j=1}^{K} \bar{\omega}_{j}^2}_{\mathcal{S}_3}
+\end{align*}
+
+Computing for the distances within Paillier would just be multiplying the encrypted sums together.
+\[
+\left[d_i\right] = \left[\mathcal{S}_1\right] \cdot \left[\mathcal{S}_2\right] \cdot \left[\mathcal{S}_3\right]
+\]
+
+The terms $\left[\mathcal{S}_1\right]$ and $\left[\mathcal{S}_2\right]$ can be easily computed by Bob, since he already knows both $\omega_i$ in the clear and $\left[\bar{\omega}_i\right]$ which is in encrypted form.
+Computing for $\left[\mathcal{S}_3\right]$ is trickier because Bob cannot compute for $\left[\bar{\omega}_i^2\right]$ because pairwise multiplication is not supported in Paillier, that is why Bob needs help from Alice to square a number through a protocol described below \cite{hutchison_privacy-preserving_2009-2}.
+
+Before Bob sends $\left[\bar{\omega}_i\right]$ to Alice for squaring, he adds a random number $r_i$ to compute $\left[x_i\right] = \left[\bar{\omega}_i + r_i\right] = \left[\bar{\omega}_i\right] \cdot \left[r_i\right]$, where $r_i$ is obviously distinct for every $i$, then sends $\left[x_i\right]$ to Alice.
+She then decrypts it and computes $x_i^2$, and then computes $\mathcal{S}_3^\prime = \sum_{i=1}^{K} x_i^2$, after which she encrypts the sum and sends $\left[\mathcal{S}_3^\prime\right]$ to Bob.
+Now, he can compute for $\left[\mathcal{S}_3\right]$ as follows:
+\[
+\left[\mathcal{S}_3\right] = \left[\mathcal{S}_3^\prime\right] \cdot \prod_{j=1}^{K} \left(\left[\bar{\omega}_j\right]^{-2r_j} \cdot \left[-r_j^2\right]\right)
+\]
+
+The protocol for squaring a number as described earlier is a workaround for the limitations of Paillier or any other partially homomorphic cryptosystem that only supports addition and scalar multiplication.
+This can be possibly extended so that operations such as pairwise multiplication and exponentiation are also supported, provided that the protocol involves two parties.
+
+The match finding step is done by comparing the distances obtained from the previous step to a specified threshold $T$.
+If the minimum distance is smaller than $T$, then a match is found, and the encrypted identity of the match is returned to Alice \cite{hutchison_privacy-preserving_2009-2}.
+Getting the minimum among the encrypted distances would involve comparing two encrypted numbers, which Paillier does not support.
+Instead, another homomorphic cryptosystem by Damg{\aa}rd, Geisler, and Kr{\o}igaard \cite{pieprzyk_efficient_2007} is used for the comparison protocol.

### 2018-10-07 parts/02_relatedliterature_07previousimplementations.tex
Forgot to uncomment a paragraph

@@
 
-%This study can be further improved by also considering the use of fully homomorphic cryptosystems such as the one presented by Dasgupta and Pal \cite{dasgupta_design_2016}, and the fully homomorphic cryptosystem introduced by Smart and Vercauteren \cite{hutchison_fully_2010} and improved by Gentry and Halevi  \cite{hutchison_implementing_2011}.
+This study can be further improved by also considering the use of fully homomorphic cryptosystems such as the one presented by Dasgupta and Pal \cite{dasgupta_design_2016}, and the fully homomorphic cryptosystem introduced by Smart and Vercauteren \cite{hutchison_fully_2010} and improved by Gentry and Halevi  \cite{hutchison_implementing_2011}.
 These fully homomorphic cryptosytems have yet to be implemented for image processing operations.

### 2018-10-07 parts/02_relatedliterature_05partiallyhomomorphic.tex
Paillier
just paillier.

@@
 
-In this section, we will present two classical partially homomorphic cryptosystems which we will be testing in the study: the Pallier cryptosystem and the DGK cryptosystem.
+In this section, we will present two classical partially homomorphic cryptosystems which we will be testing in the study: the Paillier cryptosystem and the DGK cryptosystem.
 Both of these cryptosystems encrypt integer plaintexts and are additively homomorphic.
@@
 
-\subsection{The Pallier Cryptosystem}
-The Pallier cryptosystem \cite{stern_public-key_1999}, developed by Pascal Pallier, is a probabilistic encryption scheme which is based on the composite residuosity class problem.
+\subsection{The Paillier Cryptosystem}
+The Paillier cryptosystem \cite{stern_public-key_1999}, developed by Pascal Paillier, is a probabilistic encryption scheme which is based on the composite residuosity class problem.
 The scheme allows for the encryption and decryption of integer messages, and is known to be additively homomorphic.
-We now state the encryption and decryption algorithms of the Pallier cryptosystem and its homomorphic properties.
+We now state the encryption and decryption algorithms of the Paillier cryptosystem and its homomorphic properties.
 
@@
 
-\subsubsection{Homomorphic Properties of the Pailler Cryptosystem}
+\subsubsection{Homomorphic Properties of the Paillier Cryptosystem}
 The Paillier cryptosystem supports additive homomorphism as well as the multiplication of a plaintext scalar to an encrypted message. These operations are defined as follows.
@@
 
-\subsection{General Exponentiation Protocol for Pailler and DGK}
+\subsection{General Exponentiation Protocol for Paillier and DGK}
 \label{ssec:exponentiationprotocol}
@@
 
-The following protocols apply to both the Pailler and DGK cryptosystems, as they share similar homomorphisms.
+The following protocols apply to both the Paillier and DGK cryptosystems, as they share similar homomorphisms.
 

### 2018-10-07 parts/02_relatedliterature_07previousimplementations.tex
Paillier
just paillier.

@@
 This study can be further improved by also considering the use of fully homomorphic cryptosystems such as the one presented by Dasgupta and Pal \cite{dasgupta_design_2016}, and the fully homomorphic cryptosystem introduced by Smart and Vercauteren \cite{hutchison_fully_2010} and improved by Gentry and Halevi  \cite{hutchison_implementing_2011}.
-These fully homomorphic cryptosytems have yet to be implemented for image processing operations.
+These fully homomorphic cryptosystems have yet to be implemented for image processing operations.
 
@@
 Getting the minimum among the encrypted distances would involve comparing two encrypted numbers, which Paillier does not support.
-Instead, another homomorphic cryptosystem by Damg{\aa}rd, Geisler, and Kr{\o}igaard \cite{pieprzyk_efficient_2007} is used for the comparison protocol.
+Instead, the DGK cryptosystem \cite{pieprzyk_efficient_2007} is used for the comparison protocol.

### 2018-10-07 parts/03_methodology.tex
Paillier
just paillier.

@@
 In this study we apply four homomorphic encryption schemes~\cite{ziad_cryptoimg:_2016, pieprzyk_efficient_2007, dasgupta_design_2016, garay_algorithms_2014} for use in image processing and facial recognition applications.
-While the Pailler and DGK cryptosystems have been implemented for use in image processing in~\cite{ziad_cryptoimg:_2016, hutchison_privacy-preserving_2009}, the other cryptosystems have to be adapted for this study.
+While the Paillier and DGK cryptosystems have been implemented for use in image processing in~\cite{ziad_cryptoimg:_2016, hutchison_privacy-preserving_2009}, the other cryptosystems have to be adapted for this study.
 
@@
 \begin{itemize}
-	\item The Pailler cryptosystem will be incorporated using the implementation at \url{https://github.com/n1analytics/python-paillier} developed by Data61 - CSIRO.
+	\item The Paillier cryptosystem will be incorporated using the implementation at \url{https://github.com/n1analytics/python-paillier} developed by Data61 - CSIRO.
 	\item The BGV cryptosystem will be implemented using the Pyfhel library (\url{https://github.com/ibarrond/Pyfhel}) using a HElib backend from (\url{https://github.com/shaih/HElib}).
@@
 \begin{itemize}
-	\item An implementation of an OpenCV library which implements the Pailler, DGK, Dasgupta-Pal, and BGV homomorphic cryptosystems.
+	\item An implementation of an OpenCV library which implements the Paillier, DGK, Dasgupta-Pal, and BGV homomorphic cryptosystems.
 	\item An implementation of image processing operations (intensity transformations, facial recognition) under the above cryptosystems.

### 2018-10-07 parts/03_methodology_02nonlinearintensitytransformations.tex
Paillier
just paillier.

@@
 We now describe how we implement the logarithm and power-law image intensity transformations.
-In the case of partially homomorphic cryptosystems (Pailler, DGK), the following considerations will be made regarding required homomorphic operations not supported by the cryptosystems:
+In the case of partially homomorphic cryptosystems (Paillier, DGK), the following considerations will be made regarding required homomorphic operations not supported by the cryptosystems:
 \begin{enumerate}

### 2018-10-07 parts/02_relatedliterature_03facialrecognition.tex

@@
 
-\subsection{Haar Cascades [WIP]}
-A \textit{Haar cascade classifier} is another method for facial recognition by Paul Viola and Michael Jones.
+\subsection{Haar Cascades}
+A \textit{Haar cascade classifier} is another method for facial recognition by Paul Viola and Michael Jones \cite{viola_robust_2004}.
 It uses Haar-like features to detect regularities in a face image.
@@
 A Haar-like feature is composed of black and white rectangles, and arranged such that it detects a presence or an absence of a particular image feature or regularity of interest.
-For example, a feature may detect the difference in intensities between the eyes and the cheeks, another feature would detect the nose bridge, and another one would detect depending on the location of the eyes.
+For example, a feature may detect the difference in intensities between the eyes and the cheeks, another feature would detect the edges of the face, and another one would detect depending on the location of the eyes.
 The detection is done by summing up the intensities within the black region and the white region, and then calculating the difference.
@@
 The whole process may become needlessly inefficient due to computational time being potentially wasted on a huge number of irrelevant features, even though computing for a feature is said to be efficient.
-That is why we need to select the best features and use those to form a strong classifier in a process called AdaBoost.
+That is why we need to select the best features and use those to form a strong classifier in a process called AdaBoost \cite{viola_robust_2004}.
 
-In itself, a Haar feature is considered as a \textit{weak classifier}, where the probability of detecting a certain feature is slightly greater than detecting at random.
-Because of this, a large number of Haar features must be used together by forming them into cascade classifiers in order to achieve a sufficient enough accuracy.
+In itself, a Haar-like feature is considered as a \textit{weak classifier}, the probability of detecting a certain feature is slightly greater than detecting at random \cite{viola_robust_2004}.
+So a large number of Haar-like features must be used together by forming them into cascade classifiers in order to achieve a sufficient enough accuracy.
 The resulting strong classifier would then be a linear combination of the weak classifiers.
 
+Each stage in the cascade classifier consists of weak classifiers that uses decision stumps, so that the weak classifiers can classify many examples correctly.
+A \textit{decision stump} can be defined as
 \[h \left(x, f, p, \theta \right) = \begin{cases}1 & \text{if } pf(x) < p\theta\\ 0 & \text{otherwise}\end{cases}
 \]
+where $x$ is a fixed window of the image, $f$ is the feature, $p$ is the polarity, and $\theta$ is the threshold \cite{viola_robust_2004}.
+
+Each stage also labels the region as positive (meaning that there is a face within the region), and negative (if none).
+If the detector sees the region as negative, it is immediately discarded and not processed anymore.
+Otherwise if the region is labeled as positive, it moves to the next stage for further processing.
+When a region successfully completes all the stages, it can be considered as a face region.

### 2018-10-07 parts/02_relatedliterature_07previousimplementations.tex
Final edits

@@
-\section{Related Work and Previous Implementations}
+\section{Previous Implementations of Secure Facial Recognition}
 
@@
 
-This study can be further improved by also considering the use of fully homomorphic cryptosystems such as the one presented by Dasgupta and Pal \cite{dasgupta_design_2016}, and the fully homomorphic cryptosystem introduced by Smart and Vercauteren \cite{hutchison_fully_2010} and improved by Gentry and Halevi  \cite{hutchison_implementing_2011}.
+%This study can be further improved by also considering the use of fully homomorphic cryptosystems such as the one presented by Dasgupta and Pal \cite{dasgupta_design_2016}, and the fully homomorphic cryptosystem introduced by Smart and Vercauteren \cite{hutchison_fully_2010} and improved by Gentry and Halevi  \cite{hutchison_implementing_2011}.
 These fully homomorphic cryptosystems have yet to be implemented for image processing operations.

### 2018-10-07 parts/03_methodology.tex
Final edits

@@
 
-\subsection{Evaluating Image Quality for Intensity Transformations}
+\subsection{Image Quality of Intensity Transformations}
 In this section, we discuss the image quality metrics we will use for assessing the performance of non-linear intensity transformations.
@@
 %% TODO: Brian, can you fill this part up?
+The method for secure facial recognition using eigenfaces by Erkin, et al. \cite{hutchison_privacy-preserving_2009-2} will be implemented for this study.
+Training data will be secured from The Database of Faces (\url{https://www.cl.cam.ac.uk/research/dtg/attarchive/facedatabase.html}) maintained by AT&T Laboratories Cambridge.
 
+Haar cascades will be implemented using homomorphic operations for facial detection.
+
+Each cryptosystem will be tested on accuracy (compared to unencrypted facial detection and recognition) and processing speed.
 \section{Summary}

### 2018-10-07 parts/02_relatedliterature_01cryptoimg.tex
Final final changes

@@
 \end{figure*}
-The CryptoImg library implemented the following:
+The \textit{CryptoImg} library implemented the following:
 \begin{enumerate}
@@
 \end{enumerate}
-For image negation and spatial filters, the protocols specified by CryptoImg allow all image processing operations to be performed on the server.
-However, due to limitations in the Pallier cryptosystem, the protocols presented for morphological operations and histogram equalization require both the client and the server to perform image processing calculations, although the server performs a significant portion of the processing.
+For image negation and spatial filters, the protocols specified by \textit{CryptoImg} allow all image processing operations to be performed on the server.
+However, due to limitations in the Paillier cryptosystem, the protocols presented for morphological operations and histogram equalization require both the client and the server to perform image processing calculations, although the server performs a significant portion of the processing.
 
@@
 We propose additional protocols to support more computationally intensive intensity transformations.
-Second, the \textit{CryptoImg} library only considered the Pallier cryptosystem.
+Second, the \textit{CryptoImg} library only considered the Paillier cryptosystem.
 We consider testing the performance of other homomorphic cryptosystems, which differ in their processing time and supported operations.

### 2018-10-07 parts/02_relatedliterature_05partiallyhomomorphic.tex
Final final changes

@@
 \subsection{The DGK Cryptosystem}
-The DGK cryptosystem was published by Damgård, Geisler, and Krøigaard in 2007 in an effort to create a secure integer comparison scheme \cite{pieprzyk_efficient_2007, cryptoeprint:2008:321} which is widely used in the literature \cite{veugen_improving_2012}.
+The DGK cryptosystem was published by Damg{\aa}rd, Geisler, and Kr{\o}igaard in 2007 in an effort to create a secure integer comparison scheme \cite{pieprzyk_efficient_2007, cryptoeprint:2008:321} which is widely used in the literature \cite{veugen_improving_2012}.
 

### 2018-10-07 parts/02_relatedliterature_06fullyhomomorphic.tex
Final final changes

@@
 
-We will present two such cryptosystems, the Dasgupta-Pal cryptosystem, which we present in full to explain a correction we propose to it, and the BGV cryptosystem, which has open source implementations availble primarily used in homomorphic cryptography research.
+We will present two such cryptosystems, the Dasgupta--Pal cryptosystem, which we present in full to explain a correction we propose to it, and the BGV cryptosystem, which has open source implementations availble primarily used in homomorphic cryptography research.
 
-\subsection{The Dasgupta-Pal Cryptosystem}
-The Dasgupta-Pal cryptosystem is a fully homomorphic cryptosystem proposed in 2016 by Smaranika Dasgupta and S.
+\subsection{The Dasgupta--Pal Cryptosystem}
+The Dasgupta--Pal cryptosystem is a fully homomorphic cryptosystem proposed in 2016 by Smaranika Dasgupta and S.
 K.
 Pal \cite{dasgupta_design_2016}, which encrypts integer plaintexts in $\mathbb{Z}_n$ to polynomial ciphertexts.
-We begin our presentation of the Dasgupta-Pal cryptosystem with the following definition.
+We begin our presentation of the Dasgupta--Pal cryptosystem with the following definition.
 
@@
 In the original scheme presented in \cite{dasgupta_design_2016}, the secret key $S_k$ is set to be a large prime.
-In Appendix \ref{chap:correction}, we present a case where the Dasgupta-Pal cryptosystem fails and prove that setting the secret key $S_k = 2p$, where $p$ is a large prime, corrects errors in the Dasgupta-Pal cryptosystem.
+In Appendix \ref{chap:correction}, we present a case where the Dasgupta--Pal cryptosystem fails and prove that setting the secret key $S_k = 2p$, where $p$ is a large prime, corrects errors in the Dasgupta--Pal cryptosystem.
 We now decribe the correct cryptosystem.
-\subsubsection{Corrected Dasgupta-Pal Cryptosystem Description}
+\subsubsection{Corrected Dasgupta--Pal Cryptosystem Description}
 Let $\ell$ denote the security parameter of the cryptosystem.
@@
 
-\subsubsection{Homomorphic Properties of the Dasgupta-Pal Cryptosystem}
-It has been shown \cite{dasgupta_design_2016} that the following properties hold for all integer messages $m_1, m_2 \in \mathbb{Z}_n$ in the Dasgupta-Pal cryptosystem.
+\subsubsection{Homomorphic Properties of the Dasgupta--Pal Cryptosystem}
+It has been shown \cite{dasgupta_design_2016} that the following properties hold for all integer messages $m_1, m_2 \in \mathbb{Z}_n$ in the Dasgupta--Pal cryptosystem.
 These properties arise since each coefficient in a ciphertext polynomial is essentially an independently encrypted bit of the original message.
@@
 Arbitrary computation on data can thus be achived using these bitwise operations.
-While the Dasgupta-Pal cryptosystem requires significant amounts of memory, as each bit of plaintext is encrypted into an integer, this approach provides a flexible method to perform relatively fast arbitrary computation on encrypted data.
-Encryption and decryption in the Dasgupta-Pal cryptosystem are accomplished using few arithmetic operations.
+While the Dasgupta--Pal cryptosystem requires significant amounts of memory, as each bit of plaintext is encrypted into an integer, this approach provides a flexible method to perform relatively fast arbitrary computation on encrypted data.
+Encryption and decryption in the Dasgupta--Pal cryptosystem are accomplished using few arithmetic operations.
 
 \subsection{HElib and the BGV Cryptosystem}
-The BGV (Brakerski-Gentry-Vaikuntanathan) cryptosystem \cite{cryptoeprint:2011:277} is a fully homomorphic cryptosystem created based on the ring-learning with error problem.
+The BGV (Brakerski--Gentry--Vaikuntanathan) cryptosystem \cite{cryptoeprint:2011:277} is a fully homomorphic cryptosystem created based on the ring-learning with error problem.
 The BGV cryptosystem was constructed to surpass the limitations of prior fully homomorphic cryptosystems, which were based on the first fully homomorphic cryptosystem by Gentry \cite{gentry_fully_2009}.
@@
 The \textit{HElib} library has been adapted to Python using the Pyfhel library \cite{pyfhel_2018} maintained by Ibarrondo, Laurent (SAP) and Onen (EURECOM), and licensed under the GNU GPL v3 license.
-The Pyfel library is a Python API for the HElib library, which supports the following operations on vectors/scalars of integers or binary ciphertexts:
+The Pyfhel library is a Python API for the HElib library, which supports the following operations on vectors/scalars of integers or binary ciphertexts:
 \begin{itemize}

### 2018-10-07 parts/03_methodology.tex
Final final changes

@@
 	\item The BGV cryptosystem will be implemented using the Pyfhel library (\url{https://github.com/ibarrond/Pyfhel}) using a HElib backend from (\url{https://github.com/shaih/HElib}).
-	\item The DGK and Dasgupta-Pal cryptosystem will be implemented from scratch.
+	\item The DGK and Dasgupta--Pal cryptosystem will be implemented from scratch.
 \end{itemize}
@@
 The method for secure facial recognition using eigenfaces by Erkin, et al. \cite{hutchison_privacy-preserving_2009-2} will be implemented for this study.
-Training data will be secured from The Database of Faces (\url{https://www.cl.cam.ac.uk/research/dtg/attarchive/facedatabase.html}) maintained by AT&T Laboratories Cambridge.
+%Training data will be secured from The Database of Faces (\url{https://www.cl.cam.ac.uk/research/dtg/attarchive/facedatabase.html}) maintained by AT&T Laboratories Cambridge.
+Training data will be secured from the \texttt{faces94} database (\url{https://cswww.essex.ac.uk/mv/allfaces/faces94.html}) maintained by the University of Essex.
 
@@
 Each cryptosystem will be tested on accuracy (compared to unencrypted facial detection and recognition) and processing speed.
+
 \section{Summary}
@@
 \begin{itemize}
-	\item An implementation of an OpenCV library which implements the Paillier, DGK, Dasgupta-Pal, and BGV homomorphic cryptosystems.
+	\item An implementation of an OpenCV library which implements the Paillier, DGK, Dasgupta--Pal, and BGV homomorphic cryptosystems.
 	\item An implementation of image processing operations (intensity transformations, facial recognition) under the above cryptosystems.

### 2018-10-08 parts/02_relatedliterature_05partiallyhomomorphic.tex
final final final
final final final

@@
 
-\subsection{General Exponentiation Protocol for Paillier and DGK}
+\subsection{Secure Exponentiation and Multiplication Protocols}
 \label{ssec:exponentiationprotocol}
@@
 
-The following protocols apply to both the Paillier and DGK cryptosystems, as they share similar homomorphisms.
+The following protocols apply to both the Paillier and DGK cryptosystems, as they share similar homomorphisms. We first present a secure squaring protocol.
 
@@
 
-This can be extended to arbitrary integer powers.
-Suppose Alice encrypts and integer $x$, and Bob has $E(x), E(x^2), ..., E(x^{n-1})$ and wants to obtain $E(x^n)$.
+We can use the secure squaring protocol to arrive at a secure multiplication protocol, which then allows for the evaluation of polynomials.
+Suppose Alice encrypts integers $x$ and $y$, and Bob has $E(x), E(y)$ and wants to obtain $E(xy)$.
 \begin{itemize}
-	\item Bob first selects a random integer $r$ and computes $E(x+r)$. Bob can do this since $r$ is a plaintext constant.
-	\item Bob sends $E(x+r)$ to Alice, who decrypts the ciphertext to obtain $x+r$.
-	\item Alice sends $E((x+r)^n)$ to Bob.
+	\item Bob acquires $E(x^2), E(y^2)$ using the secure squaring protocol.
+	\item Bob sends $E(x+y)$ to Alice, who decrypts the ciphertext to obtain $x+y$.
+	\item Alice sends $E((x+y)^2)$ to Bob.
 	\item Bob then computes
 	\begin{align*}
-		E((x+r)^n) - E\left(\sum_{i=1}^{n-1}{\binom{n}{i}x^ir^{n-i}}\right),
+		E((x+y)^2)E(x^2)^{-1}E(y^2)^{-1} &= E((x+y)^2 - x^2 - y^2)\\
+		&= E(2xy)
 	\end{align*}
-	which evaluates to $E(x^n)$ by the binomial theorem.
+	\item Bob can then recover $E(xy)$ by calcuating for the multiplicative inverse of 2 using the Euclidean algorithm, and calculating $2^{-1}E(xy)$.
+Such an inverse exists since the modulus is either a prime (in the DGK cryptosystem) or a product of primes greater than 2 (in the Paillier cryptosystem).
 \end{itemize}

### 2018-10-08 parts/01_introduction_01contextofstudy.tex
[WIP] Numerical approximation section
Added work on numerical approximation, fixed appendix templates
Cleaned up some wording on Ch1

@@
 
-However, research has also considered homomorphic cryptosystems, which not only allow the secure transmission of data, but also allow computations with encrypted data.
  In a homomorphic cryptosystem, operations such as addition and multiplication can be performed on encrypted data.
@@
 While numerous homomorphic cryptosystems exist for use with digital data in general, in the area of homomorphic image encryption, there is additional interest in being able to perform image manipulation operations on the encrypted data such as image adjustment, filtering, and morphological/feature extraction operations~\cite{ziad_cryptoimg:_2016, gonzalez_digital_2008}.
+More advanced operations have also been implemented using homomorphic cryptosystems, such as facial recognition \cite{hutchison_privacy-preserving_2009} and neural networks \cite{hesamifard_cryptodl:_2017}.

### 2018-10-08 parts/01_introduction_05scopeandlimitations.tex

@@
 	\item A variant of the Paillier cryptosystem~\cite{stern_public-key_1999} which supports floating-point operations, used in \textit{CryptoImg}~\cite{ziad_cryptoimg:_2016}.
-	\item The Damgård-Geisler-Krøigaard (DGK) cryptosystem~\cite{pieprzyk_efficient_2007, cryptoeprint:2008:321} which is primarily used for secure integer comparison.
+    \item The Damg{\aa}rd--Geisler--Kr{\o}igaard (DGK) cryptosystem~\cite{pieprzyk_efficient_2007, cryptoeprint:2008:321} which is primarily used for secure integer comparison.
 	\item A fully homomorphic encryption scheme by Dasgupta and Pal, which uses polynomial rings~\cite{dasgupta_design_2016}.
-	\item The Brakerski-Gentry-Vaikuntanathan (BGV) cryptosystem \cite{cryptoeprint:2011:277}, an improvement on the lattice-based cryptosystem by Gentry~\cite{gentry_fully_2009}, with optimizations from Smart, Vercauteren and Halevi \cite{hutchison_fully_2010, cryptoeprint:2011:566}.
+	\item The Brakerski--Gentry--Vaikuntanathan (BGV) cryptosystem \cite{cryptoeprint:2011:277}, an improvement on the lattice-based cryptosystem by Gentry~\cite{gentry_fully_2009}, with optimizations from Smart, Vercauteren and Halevi \cite{hutchison_fully_2010, cryptoeprint:2011:566}.
 \end{enumerate}

### 2018-10-08 parts/02_relatedliterature.tex

@@
 We will now provide an overview of the \textit{CryptoImg} project, which our study is primarily based on.
-Then, we define the image processing operations we are interested in implementing in this study and
-After establishing our desired image processing operations, introduce concepts in cryptography and define the four homomorphic cryptosystems we will be testing in the study.
+Then, we define the specific image processing operations we are interested in implementing in this study.
+Then we will introduce concepts in cryptography and define the four homomorphic cryptosystems we will be testing in the study.
 

### 2018-10-08 parts/03_methodology_02nonlinearintensitytransformations.tex

--- 2018-10-07 parts/03_methodology_02nonlinearintensitytransformations.tex
@@
 We now describe how we implement the logarithm and power-law image intensity transformations.
-In the case of partially homomorphic cryptosystems (Pailler, DGK), the following considerations will be made regarding required homomorphic operations not supported by the cryptosystems:
-\begin{enumerate}
-	\item If exponentiation is required, the secure exponentiation protocol in section \ref{ssec:exponentiationprotocol} will be used.
-	\item If multiplication of ciphertexts $E(m_1), E(m_2)$ is required, the following protocol will be used:
-	\begin{itemize}
-		\item Bob calculates $E(m_1+m_2)$ and using the exponentiation protocol, acquires $E(m_1^2),E(m_2^2),E((m_1+m_2)^2)$.
-		\item Bob can recover the product of the ciphertexts by computing
-		\begin{align*}
-			E((m_1+m_2)^2) - E(m_1^2) - E(m_2^2) = E(2m_1m_2),
-		\end{align*}
-		then carrying out the required constant multiplication to obtain $E(2m_1m_2)$.
-	\end{itemize}
-\end{enumerate}
+In the case of partially homomorphic cryptosystems (Paillier, DGK), if  exponentiation and multiplication is required, the secure protocols in section \ref{ssec:exponentiationprotocol} will be used.
+
 \subsection{Logarithm Transformation}

### 2018-10-08 parts/08_appendices_a_cryptosystems.tex
RRL summary and fixes
- Commented out spatial filter section
- Updated summary to reflect new research
- Fixed some typesetting errors in D-P section

@@
 You may use this as another reference in writing your paper.
-\chapter{CORRECTION FOR DASGUPTA-PAL}
-\label{ch:correction}
-\section{Bitwise Description of the Dasgupta-Pal Cryptosystem}
-The Dasgupta-Pal cryptosystem \cite{dasgupta_design_2016} encrypts each bit in a bit string independently.
-In terms of the encryption of a single bit, the Dasgupta-Pal cryptosystem can be described as follows:
+\chapter{CORRECTION FOR DASGUPTA--PAL}
+\label{chap:correction}
+\section{Bitwise Description of the Dasgupta--Pal Cryptosystem}
+The Dasgupta--Pal cryptosystem \cite{dasgupta_design_2016} encrypts each bit in a bit string independently.
+In terms of the encryption of a single bit, the Dasgupta--Pal cryptosystem can be described as follows:
 \begin{description}

### 2018-10-08 parts/09_removed.tex

\subsection{Evaluating Cryptographic Security}
After performing tests to evaluate image quality, we then perform tests for cryptographic security, as enumerated in~\cite{ahmed_benchmark_2016}: entropy analysis, correlation coefficient analysis (CC), NPCR and UACI.
\begin{description}
	\item [Information entropy analysis.] In information theory, the entropy function $H(X)$ is defined in~\cite{bauer_information_2005} as
	\begin{align}
		H(X) = - \sum_{a:p_X(a)>0}{p_X(a)\log_2{p_X(a)}}
	\end{align}
	where $p_X(a)$ denotes the probability that the random variable $X$ takes on the value $a$.
	In the analysis of image encryption, $H(X)$ is computed for the values of the ciphertext pixels. To ensure security against entropy attacks, $H(X)$ must be as close as possible to $\log_2{N}$, where $N$ is the number of possible pixel values~\cite{ahmed_benchmark_2016}.

    We will compute $H(\mathrm{CDT})$ for every image operation, under each homomorphic cryptosystem, and compare the effects of each image operation on the entropy of the encrypted image. Ideally, performing image operations on encrypted images should still maintain a high level of entropy.
	\item [Correlation coefficient analysis (CC).]
		Images generally have a high degree of similarity between adjacent pixels. This correlation must be hidden in the encrypted image, even after performing image operations.
		The correlation coefficient of an image can be computed between adjacent pixels either vertically, horizontal, or diagonally, and is defined in~\cite{ahmed_benchmark_2016} by:
		\begin{align}
            \mathrm{CC}(X,Y) = \frac{\sigma_{X,Y}}{\sqrt{\sigma_X}\times\sqrt{\sigma_Y}}
		\end{align}
		where
		\begin{itemize}
			\item $\sigma_X, \sigma_Y$ are the variances of $X$ and $Y$, respectively;
			\item $\sigma_{XY}$ is the covariance of $X$ and $Y$.
		\end{itemize}

        For every $\mathrm{CDT}$ image, we will compute for the correlation coefficient (for vertical, horizontal and diagonal correlation) for every image operation, under each homomorphic cryptosystem.
	\item [NPCR and UACI.]
		The Number of Pixel Change Rate (NPCR) measures the number of pixels which are changed between the a plaintext and a ciphertext to quantify the amount of dispersion which occurs during encryption.

		On the other hand, the Universal Average Change Intensity (UACI) measures the average difference in pixel intensity between two images.

		The NPCR and UACI between two images $X$ and $Y$, each containing $N$ pixels indexed from $1$ to $N$ is defined in~\cite{wu_npcr_2011} as
		\begin{align}
            \mathrm{NPCR}(X,Y) &= \frac{1}{N}\sum_{i = 1}^{N}{D(X_i,Y_i)} \times 100\%\\
            \mathrm{UACI}(X,Y) &= \frac{1}{L_{\max} \times N} \sum_{i = 1}^{N}{ |L(X_i) - L(Y_i)| } \times 100\%
		\end{align}
		where
		\begin{itemize}
			\item $X_i$ and $Y_i$ are the $i$th pixels of $X$ and $Y$, respectively;
			\item $D$ is a difference function between pixels $A$ and $B$ defined by
			\begin{align}
				D(A,B) =
				\begin{cases}
					0 &  \text{if $A = B$},\\
					1 &  \text{if $A \neq B$};
				\end{cases}
			\end{align}
		\item $L_{\max}$ is the maximum intensity of a pixel;
		\item $L(X_i)$ and $L(Y_i)$ are the intensities of pixels $X_i$ and $Y_i$, respectively.
		\end{itemize}
        We will calculate $\mathrm{NPCR}(\mathrm{PDT},\mathrm{CDT})$ and $\mathrm{UACI}(\mathrm{PDT},\mathrm{CDT})$  for every image operation, under each homomorphic cryptosystem. A high NPCR and UACI are desired to ensure high dispersion and security against differential attacks~\cite{ahmed_benchmark_2016}. Critical values for NPCR and UACI for given image sizes and bit depths are given in~\cite{wu_npcr_2011}.
\end{description}

### 2018-12-12 parts/02_relatedliterature_03facialrecognition.tex
Various edits

--- 2018-10-06 parts/02_relatedliterature_03facialrecognition.tex
@@
 
-\subsection{Haar Cascades [WIP]}
-A \textit{Haar cascade classifier} is another method for facial recognition by Paul Viola and Michael Jones.
+% \subsection{Haar Cascades}
+% A \textit{Haar cascade classifier} is another method for facial recognition by Paul Viola and Michael Jones \cite{viola_robust_2004}.
 It uses Haar-like features to detect regularities in a face image.
@@
 
-\begin{figure}[!h]
-    \centering
-    \includegraphics[width=7cm]{figures/haarfeatures2.png}
-    \caption{Examples of Haar-like features \cite{viola_robust_2004}.}
-\end{figure}
+% \begin{figure}[!h]
+%     \centering
+%     \includegraphics[width=7cm]{figures/haarfeatures2.png}
+%     \caption{Examples of Haar-like features \cite{viola_robust_2004}.}
+% \end{figure}
 
-A Haar-like feature is composed of black and white rectangles, and arranged such that it detects a presence or an absence of a particular image feature or regularity of interest.
-For example, a feature may detect the difference in intensities between the eyes and the cheeks, another feature would detect the nose bridge, and another one would detect depending on the location of the eyes.
+% A Haar-like feature is composed of black and white rectangles, and arranged such that it detects a presence or an absence of a particular image feature or regularity of interest.
+For example, a feature may detect the difference in intensities between the eyes and the cheeks, another feature would detect the edges of the face, and another one would detect depending on the location of the eyes.
 The detection is done by summing up the intensities within the black region and the white region, and then calculating the difference.
 
-Getting the sum of pixel intensities within a region na\"{i}vely would become inefficient as the size of the rectangular region increases, so a data structure called an \textit{integral image} is used to allow more efficient detection of Haar-like features.
+% Getting the sum of pixel intensities within a region na\"{i}vely would become inefficient as the size of the rectangular region increases, so a data structure called an \textit{integral image} is used to allow more efficient detection of Haar-like features.
 In other words, an integral image is essentially a two-dimensional range sum that can compute sums of rectangular regions in constant time, regardless of the size of the regions.
 
-Most of the Haar-like features are irrelevant, because a feature that works in a certain part of the image would not necessarily work in another part.
+% Most of the Haar-like features are irrelevant, because a feature that works in a certain part of the image would not necessarily work in another part.
 The whole process may become needlessly inefficient due to computational time being potentially wasted on a huge number of irrelevant features, even though computing for a feature is said to be efficient.
-That is why we need to select the best features and use those to form a strong classifier in a process called AdaBoost.
+That is why we need to select the best features and use those to form a strong classifier in a process called AdaBoost \cite{viola_robust_2004}.
 
-In itself, a Haar feature is considered as a \textit{weak classifier}, where the probability of detecting a certain feature is slightly greater than detecting at random.
-Because of this, a large number of Haar features must be used together by forming them into cascade classifiers in order to achieve a sufficient enough accuracy.
+% In itself, a Haar-like feature is considered as a \textit{weak classifier}, the probability of detecting a certain feature is slightly greater than detecting at random \cite{viola_robust_2004}.
+So a large number of Haar-like features must be used together by forming them into cascade classifiers in order to achieve a sufficient enough accuracy.
 The resulting strong classifier would then be a linear combination of the weak classifiers.
 
-\[h \left(x, f, p, \theta \right) = \begin{cases}1 & \text{if } pf(x) < p\theta\\ 0 & \text{otherwise}\end{cases}
-\]
+% Each stage in the cascade classifier consists of weak classifiers that uses decision stumps, so that the weak classifiers can classify many examples correctly.
+A \textit{decision stump} can be defined as
+% \[h \left(x, f, p, \theta \right) = \begin{cases}1 & \text{if } pf(x) < p\theta\\ 0 & \text{otherwise}\end{cases}
+% \]
+% where $x$ is a fixed window of the image, $f$ is the feature, $p$ is the polarity, and $\theta$ is the threshold \cite{viola_robust_2004}.
+
+% Each stage also labels the region as positive (meaning that there is a face within the region), and negative (if none).
+If the detector sees the region as negative, it is immediately discarded and not processed anymore.
+Otherwise if the region is labeled as positive, it moves to the next stage for further processing.
+When a region successfully completes all the stages, it can be considered as a face region.

### 2018-12-12 parts/03_methodology.tex
Various edits

@@
 While the Paillier and DGK cryptosystems have been implemented for use in image processing in~\cite{ziad_cryptoimg:_2016, hutchison_privacy-preserving_2009}, the other cryptosystems have to be adapted for this study.
-
 Two experiments will be conducted in this study:
@@
 
-The current version of the OpenCV library (3.4.2) will be forked from the open-source GitHub repository at \url{https://github.com/opencv/opencv})~\cite{bradski_opencv_2000}.
+% The current version of the OpenCV library (3.4.2) will be forked from the open-source GitHub repository at \url{https://github.com/opencv/opencv})~\cite{bradski_opencv_2000}.
 
 Four homomorphic encryption schemes will be investigated.
-For cryptosystems with readily available open-source implementations, such implmentations will be used.
+For cryptosystems with readily available open-source implementations, such implementations will be used.
 For the remaining cryptosystems, the encryption and decryption methods will be implemented in Python.
@@
 \end{itemize}
+
+For convenience, a wrapper library will be created that integrates the four cryptosystems into a unified interface.
 
@@
 The CT will be generated by encrypting the image, then applying the operation, and the EDT will be generated by decrypting the CT.
-The four images (PT, PDT, CT, CDT) will then be compared using various benchmarks to evaluate the quality and security of each homomorphic encryption scheme.
+The four images (PT, PDT, CT, EDT) will then be compared using various benchmarks to evaluate the quality and security of each homomorphic encryption scheme.
 
@@
 \subsection{Facial Recognition Tests}
-%% TODO: Brian, can you fill this part up?
+%% TODO: Brian, can you fill this part up? Yes
 The method for secure facial recognition using eigenfaces by Erkin, et al. \cite{hutchison_privacy-preserving_2009-2} will be implemented for this study.
 %Training data will be secured from The Database of Faces (\url{https://www.cl.cam.ac.uk/research/dtg/attarchive/facedatabase.html}) maintained by AT&T Laboratories Cambridge.
-Training data will be secured from the \texttt{faces94} database (\url{https://cswww.essex.ac.uk/mv/allfaces/faces94.html}) maintained by the University of Essex.
+Training and test data will be secured from the \texttt{faces94} dataset (\url{https://cswww.essex.ac.uk/mv/allfaces/faces94.html}) maintained by the University of Essex.
 
-Haar cascades will be implemented using homomorphic operations for facial detection.
+% Haar cascades will be implemented using homomorphic operations for facial detection.
 
-Each cryptosystem will be tested on accuracy (compared to unencrypted facial detection and recognition) and processing speed.
+% Each cryptosystem will be tested on accuracy (compared to unencrypted facial detection and recognition) and processing speed.
+
+The facial recognition tests will be done using ten-fold cross-validation for each cryptosystem, where the number of principal components used by the algorithm is fixed at $K=5$.
+
+Prior to splitting the dataset, the images within each set are shuffled.
+Since there are twenty (20) images per set, two images are taken at a time for each round of cross-validation.
+The first round would take the first two images from each set as part of the test set, and the rest of the images will be part of the training set.
+Then, the succeeding round would take the next two images from each set as part of the test set.
+and so on until ten rounds have been done.
+After every cross-validation round, the accuracy score, confusion matrix, and total processing time will be obtained.
 
 \section{Summary}
-In summary, the study will consist of
+In summary, the study will consist of:
 \begin{itemize}
-	\item An implementation of an OpenCV library which implements the Paillier, DGK, Dasgupta--Pal, and BGV homomorphic cryptosystems.
+	\item Creating a wrapper library that acts as a unified interface which implements the Paillier, DGK, Dasgupta--Pal, and BGV homomorphic cryptosystems.
 	\item An implementation of image processing operations (intensity transformations, facial recognition) under the above cryptosystems.

### 2018-12-12 parts/03_methodology.tex
Change chapter 3 to past tense

@@
 While the Paillier and DGK cryptosystems have been implemented for use in image processing in~\cite{ziad_cryptoimg:_2016, hutchison_privacy-preserving_2009}, the other cryptosystems have to be adapted for this study.
-Two experiments will be conducted in this study:
+Two experiments were conducted in this study:
 \begin{enumerate}
@@
 \end{enumerate}
-The results of the image intensity transformations will be tested for image quality using benchmarks in~\cite{ahmed_benchmark_2016}.
+The results of the image intensity transformations were tested for image quality using benchmarks in~\cite{ahmed_benchmark_2016}.
 
@@
 
-Four homomorphic encryption schemes will be investigated.
-For cryptosystems with readily available open-source implementations, such implementations will be used.
-For the remaining cryptosystems, the encryption and decryption methods will be implemented in Python.
+Four homomorphic encryption schemes were investigated.
+For cryptosystems with readily available open-source implementations, such implementations were used.
+For the remaining cryptosystems, the encryption and decryption methods were implemented in Python.
 \begin{itemize}
-	\item The Paillier cryptosystem will be incorporated using the implementation at \url{https://github.com/n1analytics/python-paillier} developed by Data61 - CSIRO.
-	\item The BGV cryptosystem will be implemented using the Pyfhel library (\url{https://github.com/ibarrond/Pyfhel}) using a HElib backend from (\url{https://github.com/shaih/HElib}).
-	\item The DGK and Dasgupta--Pal cryptosystem will be implemented from scratch.
+	\item The Paillier cryptosystem was incorporated using the implementation at \url{https://github.com/n1analytics/python-paillier} developed by Data61 - CSIRO.
+	\item The BGV cryptosystem was implemented using the Pyfhel library (\url{https://github.com/ibarrond/Pyfhel}) using a HElib backend from (\url{https://github.com/shaih/HElib}).
+	\item The DGK and Dasgupta--Pal cryptosystem were implemented from scratch.
 \end{itemize}
 
-For convenience, a wrapper library will be created that integrates the four cryptosystems into a unified interface.
+For convenience, a wrapper library was created that integrates the four cryptosystems into a unified interface.
 
@@
 
-Lab computers in Faura Hall, Ateneo de Manila University will be used to perform the computations, and processing time will be tracked using built-in timing functions.
-The processing time for all cases will be recorded.
+Lab computers in Faura Hall, Ateneo de Manila University were used to perform the computations, and processing time was tracked using built-in timing functions.
+The processing time for all cases were recorded.
 
 \subsection{Image Quality of Intensity Transformations}
-In this section, we discuss the image quality metrics we will use for assessing the performance of non-linear intensity transformations.
+In this section, we discuss the image quality metrics we used for assessing the performance of non-linear intensity transformations.
 
-We will first obtain standard test images from~\cite{gonzalez_image_nodate}. Grayscale images will be used in the study.
+We first obtained standard test images from~\cite{gonzalez_image_nodate}. Grayscale images were used in the study.
 
-For each plaintext image (PT), we will consider each image operation listed above and generate three images: a plaintext domain transformation (PDT), a ciphertext image (CT), and an encrypted domain transformation (EDT).
-The PDT will be generated by running the image operation on the original image.
-The CT will be generated by encrypting the image, then applying the operation, and the EDT will be generated by decrypting the CT.
-The four images (PT, PDT, CT, EDT) will then be compared using various benchmarks to evaluate the quality and security of each homomorphic encryption scheme.
+For each plaintext image (PT), we considered each image operation listed above and generate three images: a plaintext domain transformation (PDT), a ciphertext image (CT), and an encrypted domain transformation (EDT).
+The PDT was generated by running the image operation on the original image.
+The CT was generated by encrypting the image, then applying the operation, and the EDT was generated by decrypting the CT.
+The four images (PT, PDT, CT, EDT) were then compared using various benchmarks to evaluate the quality and security of each homomorphic encryption scheme.
 
@@
 	The SSIM is applied to the luminance value of two images to gauge structural similarity between neighboring pixels.
-    For the study, we will compute $\mathrm{SSIM}(\mathrm{PDT}, \mathrm{CDT})$ for every image operation, under each homomorphic cryptosystem.
+    For the study, we computed $\mathrm{SSIM}(\mathrm{PDT}, \mathrm{CDT})$ for every image operation, under each homomorphic cryptosystem.
 Higher values of SSIM indicate higher structural similarity, and an SSIM of $1$ indicates that the two images are identical~\cite{ahmed_benchmark_2016}.
@@
 %% TODO: Brian, can you fill this part up? Yes
-The method for secure facial recognition using eigenfaces by Erkin, et al. \cite{hutchison_privacy-preserving_2009-2} will be implemented for this study.
+The method for secure facial recognition using eigenfaces by Erkin, et al. \cite{hutchison_privacy-preserving_2009-2} was implemented for this study.
 %Training data will be secured from The Database of Faces (\url{https://www.cl.cam.ac.uk/research/dtg/attarchive/facedatabase.html}) maintained by AT&T Laboratories Cambridge.
-Training and test data will be secured from the \texttt{faces94} dataset (\url{https://cswww.essex.ac.uk/mv/allfaces/faces94.html}) maintained by the University of Essex.
+Training and test data were secured from the \texttt{faces94} dataset (\url{https://cswww.essex.ac.uk/mv/allfaces/faces94.html}) maintained by the University of Essex.
 
@@
 
-The facial recognition tests will be done using ten-fold cross-validation for each cryptosystem, where the number of principal components used by the algorithm is fixed at $K=5$.
+The facial recognition tests were done using ten-fold cross-validation for each cryptosystem, where the number of principal components used by the algorithm is fixed at $K=5$.
 
@@
 and so on until ten rounds have been done.
-After every cross-validation round, the accuracy score, confusion matrix, and total processing time will be obtained.
+After every cross-validation round, the accuracy score, confusion matrix, and total processing time were obtained.
 
 \section{Summary}
-In summary, the study will consist of:
+In summary, the study consisted of:
 \begin{itemize}

### 2018-12-13 parts/03_methodology.tex
Applied comments for chapter 1

@@
 The first round would take the first two images from each set as part of the test set, and the rest of the images will be part of the training set.
-Then, the succeeding round would take the next two images from each set as part of the test set.
-and so on until ten rounds have been done.
-After every cross-validation round, the accuracy score, confusion matrix, and total processing time were obtained.
+Then, the succeeding round would take the next two images from each set as part of the test set, and so on until ten rounds have been done.
+After every round of cross-validation, the accuracy score, confusion matrix, and total processing time were obtained.
 
 \section{Summary}
-In summary, the study consisted of:
+In summary, the study consists of:
 \begin{itemize}

### 2019-01-08 parts/01_introduction_03objectives.tex

@@
 
-Previous attempts in the literature to provide image processing tasks such as image manipulation \cite{ziad_cryptoimg:_2016} and  facial recognition \cite{hutchison_privacy-preserving_2009} have primarily used the Paillier and DGK cryptosystems to perform linear operations on encrypted data.
+Previous attempts in the literature to provide image processing tasks such as image manipulation \cite{ziad_cryptoimg:_2016} and  facial recognition \cite{hutchison_privacy-preserving_2009} have primarily used the Paillier and  Damg{\aa}rd--Geisler--Kr{\o}igaard (DGK) cryptosystems to perform linear operations on encrypted data.
 In this study, we extend this research to provide an objective comparison of various homomorphic cryptosystems currently in the literature in performing non-linear operations, as opposed to just linear operations, and facial detection, as opposed to just facial recognition.
 
-Our main research objective is to assess the practicality of various homomorphic cryptosystems in image encryption.
+Our main research objective is to assess the practicality of various homomorphic cryptosystems with regard to image processing on faces.
 Homomorphic cryptosystems are known to be slower in terms of encryption, operation, and decryption time~\cite{sen_homomorphic_2013}.
@@
 \begin{enumerate}
-    \item Compare the applicability of known homomorphic encryption schemes to common image processing operations, in other words, determine which schemes admit more image processing operations and extend known cryptosystems to support more operations, if possible;
-    \item Compare the time efficiency of common image processing operations under known homomorphic encryption schemes;
+    \item Implement common image processing operations using known homomorphic encryption schemes, then determine which schemes admit more image processing operations and extend known cryptosystems to support more operations, if possible;
+    \item Compare the time efficiency and accuracy of common image processing operations under known homomorphic encryption schemes, and of common image processing operations without using homomorphic encryption;
     \item Create a library for the Open Source Computer Vision Library (OpenCV) to allow for convenient use and comparison of these homomorphic encryption schemes for image processing and facial recognition.

### 2019-01-08 parts/04_results.tex

@@
 \chapter{RESULTS AND DISCUSSION}
-After implementing your methodology and gathering all pertinent data, in this section, you will now present the gathered data to your reader.
+% After implementing your methodology and gathering all pertinent data, in this section, you will now present the gathered data to your reader.
 By the end of this section, your reader should have an idea of what exactlty happened during the experiment.
-A good way to organize your results is to group them is to present them in the same order which your methodology was presented.
+% A good way to organize your results is to group them is to present them in the same order which your methodology was presented.
 For instance, if your methodology included the analysis of user logs, the implementation of an application, and the testing of this application, your results should flow in the same way.
@@
 Note the table caption and headers, as mentioned in our framework.
+
+% \begin{table}[t]
+% \centering
+% \caption {Preliminary Test Result, organized by Problem Type}
+% \label{tab:acc_lit} 
+% \begin{tabular}{ c  c  c  c  c  c  c  c  c  c  c }
+% \hline
+% Problem	&Average 	&Standard 	&Average 		&Standard		&Dominant\\
+% Type  &Steps   &Deviation   &Duration   &Deviation   &Affective\\
+%   &   &(Steps)   &(s)   &(Duration)   &State\\ \hline
+
+% A1  &14   &2.30   &23.04   &3.50   &CONF\\
+% A2  &2   &5.36   &32.10   &2.01   &FLOW\\
+% A3  &31   &1.01   &28.55   &4.03   &FLOW\\
+% B1  &24   &4.40   &45.30   &3.30   &BOR\\
+% B2  &33   &2.12   &20.56   &2.21   &FLOW\\
+% B3  &36   &1.05   &LOSE   &1.15   &CONF\\
+% C1  &22   &1.33   &LOSE   &1.40   &FLOW\\
+% C2  &23   &3.03   &LOSE   &1.30   &FLOW\\
+% D1  &30   &1.79   &LOSE   &1.45   &FLOW\\
+% D2  &15   &1.30   &LOSE   &1.05   &FLOW\\ \hline
+% \end{tabular}
+% \end{table}
+
+% There are, however, some additional notes that must be clarified.
+First, given that you will be gathering a huge volume of data, you must be able to classify which of these were critical in determining the outcome of your study, and which ones need not be presented.
+The critical data must be presented in this section, while the minor ones may be placed in the Appendices of your paper, which will be described later in this template.
+
+% Another clarification to be noted is that the presentation of results in this section must be objective, or `as-is'.
+This means that you must describe your results in a way understandable to your reader without putting any form of interpretation.
+In effect, this section’s intent is to provide answers to ``what happened'' questions, not ``what does it mean'' questions.
+The interpretation of results is the subject of a later section.
+
+% Finally, because this is a presentation of what happened in the past, all tenses used in this section must be in the past form, be it active or passive.
+This will also be true for the preceeding sections after the study’s implementation, especially when stating the methodology.
 
@@
 \end{table}
-
-There are, however, some additional notes that must be clarified.
-First, given that you will be gathering a huge volume of data, you must be able to classify which of these were critical in determining the outcome of your study, and which ones need not be presented.
-The critical data must be presented in this section, while the minor ones may be placed in the Appendices of your paper, which will be described later in this template.
-
-Another clarification to be noted is that the presentation of results in this section must be objective, or `as-is'.
-This means that you must describe your results in a way understandable to your reader without putting any form of interpretation.
-In effect, this section’s intent is to provide answers to ``what happened'' questions, not ``what does it mean'' questions.
-The interpretation of results is the subject of a later section.
-
-Finally, because this is a presentation of what happened in the past, all tenses used in this section must be in the past form, be it active or passive.
-This will also be true for the preceeding sections after the study’s implementation, especially when stating the methodology.

### 2019-01-09 paper/PCSC2019-sigconf.tex
Prepare thesis for PCSC

\documentclass[sigconf]{acmart}
\usepackage[utf8]{inputenc}
\usepackage{multicol}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs} % For formal tables

\setcopyright{rightsretained}

% DOI
\acmDOI{}

% ISBN
\acmISBN{}

%Conference
\acmConference[PCSC2019]{Philippine Computing Science Congress}{March 2019}{City of Manila, Philippines}
\acmYear{2019}
\copyrightyear{2019}

\acmArticle{}
\acmPrice{}

% These commands are optional
%\acmBooktitle{Transactions of the ACM Woodstock conference}
\editor{}
\editor{}
\editor{}

\begin{document}
\title{Implementation and Analysis of Homomorphic Facial Image Encryption and Manipulation}

\author{Me 1}
\affiliation{%
  \institution{Institute for Clarity in Documentation}
  \streetaddress{P.O. Box 1212}
  \city{Dublin}
  \state{Ohio}
  \postcode{43017-6221}
}
\email{webmaster@marysville-ohio.com}

\author{Me 2}
\affiliation{%
  \institution{The Th{\o}rv{\"a}ld Group}
  \streetaddress{1 Th{\o}rv{\"a}ld Circle}
  \city{Hekla}
  \country{Iceland}}
\email{larst@affiliation.org}

% The default list of authors is too long for headers.
\renewcommand{\shorttitle}{Implementation and Analysis}
% \renewcommand{\shortauthors}{B. Trovato et al.}

\begin{abstract}
This paper provides a sample of a \LaTeX\ document which conforms,
somewhat loosely, to the formatting guidelines for
ACM SIG Proceedings.\footnote{This is an abstract footnote}
\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below.
%
\begin{CCSXML}
  <ccs2012>
  <concept>
  <concept_id>10002978.10002979.10002981.10011745</concept_id>
  <concept_desc>Security and privacy~Public key encryption</concept_desc>
  <concept_significance>500</concept_significance>
  </concept>
  <concept>
  <concept_id>10002978.10003018.10003020</concept_id>
  <concept_desc>Security and privacy~Management and querying of encrypted data</concept_desc>
  <concept_significance>300</concept_significance>
  </concept>
  <concept>
  <concept_id>10010147.10010371.10010382.10010383</concept_id>
  <concept_desc>Computing methodologies~Image processing</concept_desc>
  <concept_significance>500</concept_significance>
  </concept>
  <concept>
  <concept_id>10002950.10003714.10003740</concept_id>
  <concept_desc>Mathematics of computing~Quadrature</concept_desc>
  <concept_significance>100</concept_significance>
  </concept>
  </ccs2012>
\end{CCSXML}

\ccsdesc[500]{Security and privacy~Public key encryption}
\ccsdesc[300]{Security and privacy~Management and querying of encrypted data}
\ccsdesc[500]{Computing methodologies~Image processing}
\ccsdesc[100]{Mathematics of computing~Quadrature}

\keywords{ACM proceedings, \LaTeX, text tagging}

\maketitle

\input{paper-conf}

\appendix
\input{appendix}

\begin{acks}
  The authors would like to thank Dr. Yuhua Li for providing the
  MATLAB code of the \textit{BEPS} method.

  The authors would also like to thank the anonymous referees for
  their valuable comments and helpful suggestions. The work is
  supported by the \grantsponsor{GS501100001809}{National Natural
    Science Foundation of
    China}{http://dx.doi.org/10.13039/501100001809} under Grant
  No.:~\grantnum{GS501100001809}{61273304}
  and~\grantnum[http://www.nnsf.cn/youngscientists]{GS501100001809}{Young
    Scientists' Support Program}.

\end{acks}

\bibliographystyle{ACM-Reference-Format}
\bibliography{thesis_refs}

\end{document}

### 2019-01-09 paper/appendix.tex
Prepare thesis for PCSC

--- 2018-10-05 parts/08_appendices_a_cryptosystems.tex
@@
-%\section{Introduction to the Appendices}
-
-%The Appendices is where you are enabled to present any additional or supplementary information relevant to your study, yet do not require highlighting within the actual paper, either because of its trivial nature or volume.
-These may in the form of figures, tables, or additional text detailing specific aspects about or related to the study.
-
-%\section{Sample Questions for Different Studies}
-%The following table presents three sample studies, as well as the guide questions that may help direct the discussion in each section of the paper.
-You may use this as another reference in writing your paper.
-\chapter{CORRECTION TO THE DASGUPTA-PAL CRYPTOSYSTEM}
-\label{ch:correction}
-\section{Bitwise Description of the Dasgupta-Pal Cryptosystem}
-The Dasgupta-Pal cryptosystem \cite{dasgupta_design_2016} encrypts each bit in a bit string independently.
-In terms of the encryption of a single bit, the Dasgupta-Pal cryptosystem can be described as follows:
+\section{Correction for Dasgupta--Pal}
+\label{chap:correction}
+\subsection{Bitwise Description of the Dasgupta--Pal Cryptosystem}
+The Dasgupta--Pal cryptosystem \cite{dasgupta_design_2016} encrypts each bit in a bit string independently.
+In terms of the encryption of a single bit, the Dasgupta--Pal cryptosystem can be described as follows:
 \begin{description}
@@
 	\begin{align*}
-		D(E(a)+E(b)) = a \text{ XOR } b = (a + b) \bmod 2
+		D(E(a)+E(b)) = a \textsc{ xor } b = (a + b) \bmod 2
 	\end{align*}
@@
 	\begin{align*}
-		D(E(a)\times E(b)) = a \text{ AND } b = ab \bmod 2
+		D(E(a)\times E(b)) = a \textsc{ and } b = ab \bmod 2
 	\end{align*}
@@
 \end{description}
-\section{Cases Where Decryption Fails}
+\subsection{Cases Where Decryption Fails}
 We consider the following quantity:
@@
 	\label{eq:cornercase_plaintext}
-	\underbrace{1 \text{ XOR } 1 \text{ XOR } \cdots \text{ XOR } 1}_{S_k \text{ times}} = 1.
+	\underbrace{1 \textsc{ xor } 1 \textsc{ xor } \cdots \textsc{ xor } 1}_{S_k \text{ times}} = 1.
 \end{align*}
@@
 \end{align*}
-Since $\underbrace{1 \text{ XOR } 1 \text{ XOR } \cdots \text{ XOR } 1}_{S_k \text{ times}} = 1\neq 0 = D(\underbrace{E(1)+E(1)+\cdots+E(1)}_{S_k \text{ times}})$, we have shown an instance where incorrect decryption occurs given a sequence of operations on ciphertexts.
+Since $\underbrace{1 \textsc{ xor } 1 \textsc{ xor } \cdots \textsc{ xor } 1}_{S_k \text{ times}} = 1\neq 0 = D(\underbrace{E(1)+E(1)+\cdots+E(1)}_{S_k \text{ times}})$, we have shown an instance where incorrect decryption occurs given a sequence of operations on ciphertexts.
 
@@
 \end{proof}
+
+\section{Numerical Approximations}
+\newcommand*\diff{\mathop{}\!\mathrm{d}}
+
+Transcendental functions such as the exponential and logarithmic functions are usually implemented in computer hardware and software libraries using minimax polynomials, which are determined numerically using the Remez algorithm \cite{harrison_computation_1999}.
+However, the Remez algorithm relies on iteratively refining the polynomial coefficients, which requires knowledge of the argument passed to the exponential or logarithmic function.
+
+We cannot directly apply this approach in privacy-preserving image processing as we do not have knowledge of the exact value of the function arguments.
+In order to calculate a function under a  homomorphic cryptosystem, it is necessary to express the function in terms of the homomorphic operations.
+In this section, we discuss approximations for the logarithm ($\log(1+x)$) and power ($x^r$) functions using only addition, subtraction, multiplication, and division operations.
+
+%TODO: Explain why standard methods for transcedental function approximation cannot be applied here.
+%TODO: Include citations for this chapter
+\subsection{Approximation for $\log(1+x)$}
+\label{sec:logapproximation}
+We approximate the function $f(x)=\log(1+x)$ using a similar method to that described in
+\cite{khattri_new_2009}.
+We let $x = 1/n$ and consider the integral
+\begin{align*}
+  \int_{n}^{n+1}{\frac{1}{x}\diff x}=\log{\left(1+\frac{1}{n}\right)}.
+\end{align*}
+
+This integral can be approximated using the five-point Gauss-Legendre quadrature rule \cite{kythe_quadrature_2002}, which is as follows:
+\begin{align*}
+	\int_a^b{f(x)\diff x}
+	&= \frac{b-a}{2}\int_{-1}^{1}{f\left(\frac{b-a}{2}x+\frac{a+b}{2}\right)\diff x}\\
+	\int_{-1}^{1}{f(x)\diff x} &= \sum_{i=1}^{5}{w_if(x_i)}
+\end{align*}
+where
+\begin{multicols}{2}
+	\noindent
+	\begin{align*}
+		w_1 &= 0\\
+		w_2 &= \frac{1}{21}\sqrt{245-14\sqrt{70}}\\
+		w_3 &= -\frac{1}{21}\sqrt{245-14\sqrt{70}}\\
+		w_4 &= \frac{1}{21}\sqrt{245+14\sqrt{70}}\\
+		w_5 &= -\frac{1}{21}\sqrt{245+14\sqrt{70}}\\
+	\end{align*}
+	\columnbreak
+	\begin{align*}
+		x_1 &= \frac{128}{225}\\
+		x_2 &= \frac{1}{900}\left( 322 + 13\sqrt{70}\right)\\
+		x_3 &= \frac{1}{900}\left( 322 + 13\sqrt{70}\right)\\
+		x_4 &= \frac{1}{900}\left( 322 - 13\sqrt{70}\right)\\
+		x_5 &= \frac{1}{900}\left( 322 - 13\sqrt{70}\right)\\
+	\end{align*}
+\end{multicols}
+This yields the following approximation:
+\begin{equation}\label{eq:standardquadrature}
+  \log(1+x) \approx
+  \frac{137x^5 + 2310x^4 + 9870x^3 + 15120x^2 + 7560x}
+  {30x^5 + 900x^4 + 6300x^3 + 16800x^2 + 18900x + 7560}.
+\end{equation}
+While this closed form approximation is accurate for values of $x$ near zero, it diverges from $\log{(1+x)}$ significantly for large values of $x$.
+\begin{figure}[!ht]
+    \centering
+    \includegraphics[width=.8\linewidth]{figures/StandardQuadrature.png}
+    \caption{Graph of $\log{(1+x)}$ and the approximation in equation \ref{eq:standardquadrature}}
+    \label{fig:standardquadrature}
+\end{figure}
+As we only need accuracy for $x \in [0, 255]$, we can scale the approximation by a constant factor $\alpha$ as follows:
+\begin{align*}
+  \log{(1+x)} &= \log{\left(\frac{\alpha + \alpha x}{\alpha}\right)}\\
+  &= \log{(\alpha + \alpha x)} - \log{\alpha}\\
+  &= \log{\left(\alpha+\frac{\alpha}{n}\right)} - \log{\alpha}\\
+  &= \log{\left(\frac{\alpha n + \alpha}{n}\right)} - \log{\alpha}\\
+  &= \int_{n}^{\alpha n + \alpha}{\frac{1}{x}\diff x} - \log{\alpha}
+\end{align*}
+
+Using the five-point Gauss-Legendre quadrature rule with $\alpha = 1/20$, we arrive at the approximation:
+\begin{align}\label{eq:scaledquadrature}
+  \begin{split}
+    &\log(1+x) \\
+    &\approx \frac{137x^5 + 33185x^4 + 931370x^3 - 13403630x^2 - 289469315x - 713567363}
+    {30(x^5 + 505x^4 + 42010x^3 + 923010x^2 + 5722005x + 8040501)} \\
+    &+ \log{20}
+  \end{split}
+\end{align}
+Below is a graph of the absolute error of the scaled approximation and the exact value of $\log{(1+x)}$.
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=.9\linewidth]{figures/ModifiedQuadratureAbsoluteError.png}
+    \caption{Graph of the absolute error of $\log{(1+x)}$ and the approximation in equation \ref{eq:scaledquadrature}}
+    \label{fig:scaledquadrature}
+\end{figure}
+
+\subsection{Approximation for $x^\gamma$}
+To approximate $x^\gamma$ for any $\gamma \in \mathbb{R}$, we rewrite $x^\gamma$ as follows:
+\begin{align*}
+  x^\gamma = e^{\log{x^\gamma}} = e^{\gamma\log{x}}.
+\end{align*}
+This expression can then be approximated using the Maclaurin series expansion for $e^x$, which converges for all $x$.
+\begin{align*}
+  e^x &= \sum_{n=0}^{\infty}{\frac{x^n}{n!}}\\
+  \Rightarrow e^{\gamma\log{x}} &= \sum_{n=0}^{\infty}{\frac{(\gamma\log{x})^n}{n!}}
+\end{align*}
+As we already have an approximation for the natural logarithm, we can evaluate partial sums of the above infinite series to arrive at approximations for $x^\gamma$.

### 2019-01-09 paper/paper-conf.tex
Prepare thesis for PCSC

\section{Introduction}
\subsection{Context of the Study}
Digital data privacy and security is a growing concern in various fields, such as cloud computing~\cite{potey_homomorphic_2016}, health information systems~\cite{kester_cryptographic_2015}, and video surveillance~\cite{upmanyu_efficient_2009}. To meet these needs, various cryptosystems have been developed. A cryptosystem is a system which operates on plaintexts, ciphertexts and keys using an encryption algorithm, which maps a plaintext to a ciphertext, together with a decryption algorithm, which maps a ciphertext to a plaintext, given an appropriate key~\cite{bauer_cryptosystem_2005}. The encryption and decryption algorithms are chosen such that the plaintext cannot easily be recovered from the ciphertext without knowledge of the key. This allows data to be securely transmitted over an insecure channel. Much research has been done on the development and application of various cryptosystems.

One particular application of cryptography is image encryption. While cryptosystems used to encrypt digital data in general, such as the Advanced Encryption Standard (AES) or elliptic curve cryptography, can also be used to encrypt images~\cite{jain_image_2016, singh_image_2015} other algorithms created specifically for image encryption have also been developed~\cite{murugan_survey_2018}.

In a homomorphic cryptosystem, operations such as addition and multiplication can be performed on encrypted data. These operations are then preserved when the data is decrypted. In this manner, data is manipulated without compromising data privacy, as the encrypted data being operated on remains secure~\cite{fontaine_survey_2007, sen_homomorphic_2013}. While numerous homomorphic cryptosystems exist for use with digital data in general, in the area of homomorphic image encryption, there is additional interest in being able to perform image manipulation operations on the encrypted data such as image adjustment, filtering, and morphological/feature extraction operations~\cite{ziad_cryptoimg:_2016, gonzalez_digital_2008}. More advanced operations have also been implemented using homomorphic cryptosystems, such as facial recognition \cite{hutchison_privacy-preserving_2009} and neural networks \cite{hesamifard_cryptodl:_2017}. This study in particular focuses on facial recognition.

\subsection{Research Questions}
By implementing homomorphic cryptosystems and creating a library so they can be easily used, we aim to address our main research question: What is the best method for facial image data to be encrypted and manipulated for practical applications?

More specifically, our research will address the following sub-questions:
\begin{enumerate}
	\item Which homomorphic cryptosystems admit more image processing operations? How can existing homomorphic cryptosystems be modified to admit more image processing operations?
	\item Which homomorphic cryptosystems are the most time-efficient and the most accurate in applying image processing operations?
	\item Which homomorphic cryptosystems best preserve image quality in applying image processing operations?
\end{enumerate}

\subsection{Research Objectives}
Previous attempts in the literature to provide image processing tasks such as image manipulation \cite{ziad_cryptoimg:_2016} and  facial recognition \cite{hutchison_privacy-preserving_2009} have primarily used the Paillier and  Damg{\aa}rd--Geisler--Kr{\o}igaard (DGK) cryptosystems to perform linear operations on encrypted data. In this study, we extend this research to provide an objective comparison of various homomorphic cryptosystems currently in the literature in performing non-linear operations, as opposed to just linear operations, and facial detection, as opposed to just facial recognition.

Our main research objective is to assess the practicality of various homomorphic cryptosystems with regard to image processing on faces. Homomorphic cryptosystems are known to be slower in terms of encryption, operation, and decryption time~\cite{sen_homomorphic_2013}. Furthermore, the operations on encrypted data supported by homomorphic cryptosystems are limited, and some schemes require preprocessing to be performed on images, limiting the range of operations which can be performed efficiently~\cite{li_elliptic_2012}.

In summary, in this study, we wish to
\begin{enumerate}
    \item Implement common image processing operations using known homomorphic encryption schemes, then determine which schemes admit more image processing operations and extend known cryptosystems to support more operations, if possible;
    \item Compare the time efficiency and accuracy of common image processing operations under known homomorphic encryption schemes, and of common image processing operations without using homomorphic encryption;
    \item Create a library to allow for convenient use and comparison of these homomorphic encryption schemes for image processing and facial recognition.
\end{enumerate}

\subsection{Significance of the Study}
This study aims to directly address one of the current problems in the research of homomorphic cryptosystems: the practicality of homomorphic encryption~\cite{sen_homomorphic_2013}. The literature shows existing homomorphic cryptosystems and how they support primitive operations (usually addition and multiplication) on encrypted data, however, for homomorphic cryptosystems to be useful for practical use, efficient support for more complicated image processing operation must be demonstrated as well. While implementations of image processing operations in a homomorphic cryptosystem exist in the literature~\cite{ziad_cryptoimg:_2016, garay_algorithms_2014}, our study targets the more computationally intensive task of facial detection.

We wish to contribute to existing models for the secure transmission and modification of image data by developing a software library which allows the use and comparison of various homomorphic encryption algorithms. Our software library would allow service providers to perform image manipulation for clients without compromising data privacy.

\subsection{Scope and Limitations}
Our study will be limited in terms of the cryptosystems to be tested, the image processing operations we will implement, and the statistical tests we will use to gauge the security of the cryptosystems. Below is a listing of the scope of the study.

We will implement and test the following algorithms:
\begin{enumerate}
	\item A variant of the Paillier cryptosystem~\cite{stern_public-key_1999} which supports floating-point operations, used in \textit{CryptoImg}~\cite{ziad_cryptoimg:_2016}.
    \item The Damg{\aa}rd--Geisler--Kr{\o}igaard (DGK) cryptosystem~\cite{pieprzyk_efficient_2007, cryptoeprint:2008:321} which is primarily used for secure integer comparison.
	\item A fully homomorphic encryption scheme by Dasgupta and Pal, which uses polynomial rings~\cite{dasgupta_design_2016}.
	\item The Brakerski--Gentry--Vaikuntanathan (BGV) cryptosystem \cite{cryptoeprint:2011:277}, an improvement on the lattice-based cryptosystem by Gentry~\cite{gentry_fully_2009}, with optimizations from Smart, Vercauteren, and Halevi \cite{hutchison_fully_2010, cryptoeprint:2011:566}.
\end{enumerate}
We will implement and test the following categories of image manipulation operations:
\begin{enumerate}
	\item Non-linear image intensity adjustment (logarithm and power-log transformations)
	\item Facial detection and recognition using the eigenface approach \cite{turk_eigenfaces_1991}.
\end{enumerate}
We will adopt the benchmark for evaluating image quality of image encryption schemes presented by Ahmed, et. al~\cite{ahmed_benchmark_2016}. The presented benchmark reflects many tests used in other literature~\cite{ahmad_efficiency_2012, wu_npcr_2011}.
\begin{enumerate}
    \item Mean Squared Error (MSE)
    \item Peak Signal to Noise Ratio (PSNR)
    \item Structural Similarity Index (SSIM)
\end{enumerate}
A detailed overview of the above will be provided in the methodology. Grayscale images will be used in the study.
A client-server model for secure computation will be assumed to allow operations such as secure comparison and exponentiation.
Training and test data are taken from the publicly available \texttt{faces94} dataset (\url{https://cswww.essex.ac.uk/mv/allfaces/faces94.html}) maintained by the University of Essex.

\section{Review of Related Literature}
\subsection{Homomorphic Cryptosystems}
A cryptosystem consists of an encryption function $\mathcal{E}$ and a decryption function $\mathcal{D}$, along with the plaintext space $\mathcal{P}$, ciphertext space $\mathcal{C}$ and the key space $\mathcal{K}$~\cite{bauer_cryptosystem_2005}. A \textit{plaintext} is text that can be commonly understood, while a \textit{ciphertext} results from encrypting the plaintext using an encryption key. The \textit{plaintext space} is the set of all possible plaintexts, the \textit{ciphertext space} is the set of all possible ciphertexts, while the \textit{keyspace} is the set of all possible keys.

There are two kinds of cryptosystems, \textit{symmetric} and \textit{asymmetric}. In symmetric-key cryptosystems, the same key is used for both encryption and decryption. As a consequence, symmetric-key cryptosystems must be implemented with a secure key exchange protocol, so that both the sender and receiver have access to the same key. Prominent examples of symmetric-key cryptosystems are the Data Encryption Standard (DES), and its replacement, the Advanced Encryption Standard (AES).

On the other hand, asymmetric-key (or public-key) cryptosystems use separate keys for encryption and decryption. The encryption key (also called the \textit{public key}) is shared publicly, while the decryption key (also called the \textit{private key}) is kept secret. Since the public key and private keys are different, there is no need to agree upon secure key exchange protocols. Usually, the security of asymmetric-key cryptosystems relies on the intractability of certain computational problems, for example, the RSA cryptosystem depends on the difficulty of big integer factorization~\cite{rivest_method_1978}, while the ElGamal cryptosystem depends on the difficulty of the discrete logarithm problem~\cite{blakley_public_1985}.

Homomorphic cryptosystems are a special type of cryptosystem in which operations can be securely performed on encrypted data. Suppose that for a public-key cryptosystem, $\mathcal{E}_k \left(p \right)$ is the encryption function using the public key $k \in \mathcal{K}$, and $\mathcal{D}_l \left(c \right)$ be the decryption function using the private key $l$. A cryptosystem is said to be homomorphic if its encryption function is homomorphic, that is, if it satisfies the relation
\begin{equation}
    \mathcal{E}_k \left(p_1 \boxplus p_2\right) = \mathcal{E}_k \left(p_1\right) \boxdot \mathcal{E}_k \left(p_2\right)
\end{equation}
where $p_1, p_2 \in \mathcal{P}$ are the plaintexts, and $\boxplus$ and $\boxdot$ are operations in $\mathcal{P}$ and $\mathcal{C}$ respectively~\cite{fontaine_survey_2007}. Furthermore, a homomorphic cryptosystem also satisfies~\cite{li_elliptic_2012}
\begin{equation}
    p_1 \boxplus p_2 = \mathcal{D}_l \left( \mathcal{E}_k \left(p_1\right) \boxdot \mathcal{E}_k \left(p_2\right) \right).
\end{equation}
In other words, a homomorphic cryptosystem preserves the operations that can be done with the plaintext without requiring an intermediary step of decrypting the ciphertext beforehand. It is important to note that the operations $\boxplus$ and $\boxdot$ need not be the same. A simple operation in the plaintext space may require a computationally intensive operation in the ciphertext space.

Homomorphic cryptosystems can be classified according to the plaintext and ciphertext operations, $\boxplus$ and $\boxdot$. If the plaintext operation $\boxplus$ is addition, the cryptosystem is said to be \textit{additively homomorphic}, and the cryptosystem is said to be \textit{multiplicatively homomorphic} if the plaintext operation $\boxplus$ is multiplication.

\subsection{Partially Homomorphic Cryptosystems}

In this section, we will present two classical partially homomorphic cryptosystems which we will be testing in the study: the Paillier cryptosystem and the DGK cryptosystem. Both of these cryptosystems encrypt integer plaintexts and are additively homomorphic.

We will then show that the cryptosystems can be modified to support privacy-perserving polynomial evaluation in a client-server protocol: given an encrypted message $m$, evaluate $f(m)$ where $f$ is a polynomial function.

\subsubsection{The Paillier Cryptosystem}
The Paillier cryptosystem \cite{stern_public-key_1999}, developed by Pascal Paillier, is a probabilistic encryption scheme which is based on the composite residuosity class problem. The scheme allows for the encryption and decryption of integer messages, and is known to be additively homomorphic. We now state the encryption and decryption algorithms of the Paillier cryptosystem and its homomorphic properties.

\paragraph{Key Generation}
We first define a function $L(x)$ as the largest integer $v$ greater than zero such that $x-1 \geq vn$.
We choose two large primes $p$ and $q$, and set $n = pq, \lambda = \mathrm{lcm}(p-1,q-1)$.
Then we select an integer $g$, $0\leq g \leq n^2$ such that $\mathrm{gcd}(L(g^\lambda \bmod n^2), n) = 1$.
We denote the public key as $(g,n)$ and the private key $(p,q)$.

\paragraph{Encryption and Decryption}
The encryption function to encrypt a plaintext $m \in \mathbb{Z}_n$ given a public key $(g,n)$ is defined as
\begin{align*}
  E(m) = g^m \cdot r^n \mod{n^2},
\end{align*}
where $r$ is a random non-negative integer less than $n^2$.

The decryption function to decrypt a ciphertext $c \in \mathbb{Z}_{n^2}$ given a private key $(p,q)$ is defined as:
\begin{align*}
  D(c) = L(c^\lambda \bmod n^2) \times (L(g^\lambda \bmod n^2))^{-1} \mod n
\end{align*}

\paragraph{Homomorphic Properties of the Paillier Cryptosystem}
The Paillier cryptosystem supports additive homomorphism as well as the multiplication of a plaintext scalar to an encrypted message. These operations are defined as follows.
For all $m_1,m_2 \in \mathbb{Z}_n$ and $k\in \mathbb{N}$, the following homomorphic properties hold.
\begin{align*}
  D(E(m_1)g^k\bmod n^2)=(m_1+k)\bmod n & \text{ (used to add a constant)}\\
  D(E(m_1)E(m_2)\bmod n^2)=(m_1+m_2)\bmod n & \text{ (used for binary addition)}\\
  D(E(m_1)^k\bmod n^2)= km_1\bmod n & \text{ (used to multiply a plaintext constant)}
\end{align*}

\subsubsection{The DGK Cryptosystem}
The DGK cryptosystem was published by Damg{\aa}rd, Geisler, and Kr{\o}igaard in 2007 in an effort to create a secure integer comparison scheme \cite{pieprzyk_efficient_2007, cryptoeprint:2008:321} which is widely used in the literature \cite{veugen_improving_2012}.

\paragraph{Key Generation}
We denote $k,t,\ell$ as security parameters of the scheme, where $k>t>\ell$.
Let $p,q$ be primes such that
we can choose two $t$-bit primes $v_p$ and $v_q$ such that $v_p | (p-1)$ and $v_q | (q-1)$, and a small prime $u$ such that $u | (p-1)$ and $u | (q-1)$.
We denote $n = pq$.
We choose $g$ to be an integer of order $uv_pv_q$ and $h$ to be of order $v_pv_q$.

The DGK cryptosystem encrypts plaintexts in $\mathbb{Z}_u$ to ciphertexts in $\mathbb{Z}_n^\ast$.

The public key is $(n,g,h,u)$ and the private key is $(p,q,v_p,v_q)$.

\paragraph{Encryption and Decryption}
To encrypt a message $m \in \mathbb{Z}_u$, the encryption function is defined as:
\begin{align*}
  E(m) = g^m \cdot h^r \mod{n},
\end{align*}
where $r$ is a random integer in $\mathbb{Z}_n$ which is longer than $2t$ bits.

To decrypt a ciphertext $c \in \mathbb{Z}_n^\ast$, decryption is achieved by first computing $c^{v_pv_q}$.
\begin{align*}
	c^{v_pv_q} \bmod n
	&= (g^m \cdot h^r)^{v_pv_q} \bmod n\\
	&= (g^{v_pv_q})^m \bmod n
\end{align*}
Since $(g^{v_pv_q})^m$ has order $u$, there is a one-to-one correspondence between plaintexts in $\mathbb{Z}_u$ and  $(g^{v_pv_q})^m$. A lookup table can thus be generated privately to successfully recover $m$.

\paragraph{Homomorphic Properties of the DGK Cryptosystem}
The DGK cryptosystem supports additive homomorphism as well as the multiplication of a plaintext scalar to an encrypted message. These operations are defined as follows.
For all $m_1,m_2 \in \mathbb{Z}_u$ and $k\in \mathbb{N}$, the following homomorphic properties hold.
\begin{align*}
    D(E(m_1)g^k)=(m_1+k)\bmod u & \text{ (used to add a constant)}\\
    D(E(m_1)E(m_2))=(m_1+m_2)\bmod u & \text{ (used for binary addition)}\\
    D(E(m_1)^k)= km_1\bmod u & \text{ (used to multiply a plaintext constant)}
\end{align*}

As the multiplicative homomorphism was not presented in the original paper, we provide a short proof here.
\begin{proof}
  Let $m \in \mathbb{Z}_u$ and $k\in \mathbb{N}$.
  We consider $E(m)^k = (g^m \cdot h^r \bmod{n})^k\bmod n$.
  \begin{align*}
    (g^m \cdot h^r \bmod{n})^k \bmod n
    &= (g^m \cdot h^r)^k \bmod{n}\\
    &= (g^m)^k \cdot (h^r)^k \bmod{n}\\
    &= g^{km} \cdot (h^kr) \bmod{n}\\
  \end{align*}
  Since $r$ is a random integer, $kr$ is also a random integer, Therefore, $g^{km} \cdot (h^kr) \bmod{n} = D(E(m_1)^k)$ is a valid encryption of the message $km$.
\end{proof}

\subsubsection{Secure Exponentiation and Multiplication Protocols}
\label{ssec:exponentiationprotocol}
In order to perform polynomial evaluation, we first present a protocol for privacy-preserving exponentiation to a positive integer power, adapted from the protocol to calculate Euclidean distances used in \cite{hutchison_privacy-preserving_2009}.

The following protocols apply to both the Paillier and DGK cryptosystems, as they share similar homomorphisms. We first present a secure squaring protocol.

Suppose Alice encrypts an integer $x$ and sends it so Bob has $E(x)$, and wants to obtain $E(x^2)$ without exposing the value of $x$.
\begin{itemize}
	\item Bob first selects a random integer $r$ and computes $E(x+r)$. Bob can do this since $r$ is a plaintext constant.
	\item Bob sends $E(x+r)$ to Alice, who decrypts the ciphertext to obtain $x+r$.
	\item Alice squares $x+r$ and encrypts the result. She sends $E((x+r)^2)$ to Bob.
	\item Bob computes $E(-2rx + r^2)$. He then computes $E((x+r)^2)E(-2rx + r^2) = E(x^2)$.
\end{itemize}

We can use the secure squaring protocol to arrive at a secure multiplication protocol, which then allows for the evaluation of polynomials.
Suppose Alice encrypts integers $x$ and $y$, and Bob has $E(x), E(y)$ and wants to obtain $E(xy)$.
\begin{itemize}
	\item Bob acquires $E(x^2), E(y^2)$ using the secure squaring protocol.
	\item Bob sends $E(x+y)$ to Alice, who decrypts the ciphertext to obtain $x+y$.
	\item Alice sends $E((x+y)^2)$ to Bob.
	\item Bob then computes
	\begin{align*}
		E((x+y)^2)E(x^2)^{-1}E(y^2)^{-1} &= E((x+y)^2 - x^2 - y^2)\\
		&= E(2xy)
	\end{align*}
	\item Bob can then recover $E(xy)$ by calcuating for the multiplicative inverse of 2 using the Euclidean algorithm, and calculating $2^{-1}E(xy)$. Such an inverse exists since the modulus is either a prime (in the DGK cryptosystem) or a product of primes greater than 2 (in the Paillier cryptosystem).
\end{itemize}

\subsection{Fully Homomorphic Cryptosystems}
We will also be testing fully homomorphic cryptosytems, which allow aribitrary computation on encrypted data.
While generally being more flexible, fully homomorphic cryptosytems are known to be significantly slower than partially homomorphic cryptosytems; improving the efficiency of fully homomorphic cryptosytems is an active area of research \cite{sen_homomorphic_2013}.

We will present two such cryptosystems, the Dasgupta--Pal cryptosystem, which we present in full to explain a correction we propose to it, and the BGV cryptosystem, which has open source implementations availble primarily used in homomorphic cryptography research.

\subsubsection{The Dasgupta--Pal Cryptosystem}
The Dasgupta--Pal cryptosystem is a fully homomorphic cryptosystem proposed in 2016 by Smaranika Dasgupta and S. K. Pal \cite{dasgupta_design_2016}, which encrypts integer plaintexts in $\mathbb{Z}_n$ to polynomial ciphertexts. We begin our presentation of the Dasgupta--Pal cryptosystem with the following definition.

Given a message $m \in \mathbb{Z}$, we denote
\begin{align*}
		m_p(x) = a_0 + a_1 x + a_2 x^2 + \cdots + a_k x^k
\end{align*}
where $a_k a_{k-1}\cdots a_2 a_1 a_0$ is the binary representation of $m$.

In the original scheme presented in \cite{dasgupta_design_2016}, the secret key $S_k$ is set to be a large prime. In Appendix \ref{chap:correction}, we present a case where the Dasgupta--Pal cryptosystem fails and prove that setting the secret key $S_k = 2p$, where $p$ is a large prime, corrects errors in the Dasgupta--Pal cryptosystem.
We now decribe the correct cryptosystem.
\paragraph{Corrected Dasgupta--Pal Cryptosystem Description}
Let $\ell$ denote the security parameter of the cryptosystem.
Let $S_k = 2p$, where $p$ is a prime number with $\ell - 1$ bits.
Choose a random even integer $z$ of length $\log_2{\ell}$.

Let the secret key be $S_k$, and let the refresh key be $R_k = z \cdot S_k$. The secret key is kept private to the encrypting/decrypting parties, while the refresh key is made publicly available.

The scheme defines the encryption algorithm for a message $m$ as follows:
\begin{align*}
	E(m) = y(x) + S_k\times d(x)
\end{align*}
where
$y(x)$ is a polynomial of degree $n$ such that $m_p(x) \equiv y(x) \bmod S_k$ and $d(x)$ is a randomly chosen polynomial of degree $n$. This encrypts each coefficient of of $m_p(x)$ by adding some multiple of $S_k$ to it. Through this process, each bit of the message is encrypted separately.

Furthermore, the decryption algorithm to recover $m_p(x)$ from a ciphertext polynomial $c(x)$ as
\begin{align*}
	m_p(x) = c(x) \bmod S_k \bmod 2.
\end{align*}
Thus $D(c(x))$ is defined as the integer recovered from the coefficients of the polynomial $c(x) \bmod S_k \bmod 2$.

Dasgupta and Pal note that homomorphic operations on ciphertext introduce noise which may interfere with decryption, due to the potential increase in ciphertext values.
To eliminate noise from a polynomial ciphertext, the following refresh function is used:
\begin{align*}
	R(c(x)) = c(x) \bmod R_k.
\end{align*}

\paragraph{Homomorphic Properties of the Dasgupta--Pal Cryptosystem}
It has been shown \cite{dasgupta_design_2016} that the following properties hold for all integer messages $m_1, m_2 \in \mathbb{Z}_n$ in the Dasgupta--Pal cryptosystem. These properties arise since each coefficient in a ciphertext polynomial is essentially an independently encrypted bit of the original message.
\begin{description}
	\item[XOR on ciphertexts]
	A bitwise exclusive or (XOR) operation on integer messages can be achieved by adding the coefficients pairwise between two ciphertexts.
	\begin{align*}
		D(E(m_1)+E(m_2)) = m_1 \textsc{ xor } m_2
	\end{align*}
	\item[AND on ciphertexts]
	Similarly, pair-wise multiplication corresponds to bitwise AND of integer messages.
	\begin{align*}
		D(E(a) \otimes E(b)) = a \textsc{ and } b = ab \bmod 2
	\end{align*}
	where $\otimes$ denotes pairwise multiplication,
	\begin{align*}
		\sum_{i=1}^n{a_ix^i} \otimes \sum_{i=1}^n{b_ix^i} = \sum_{i=1}^n{a_ib_ix^i}.
	\end{align*}
\end{description}

Arbitrary computation on data can thus be achived using these bitwise operations. While the Dasgupta--Pal cryptosystem requires significant amounts of memory, as each bit of plaintext is encrypted into an integer, this approach provides a flexible method to perform relatively fast arbitrary computation on encrypted data. Encryption and decryption in the Dasgupta--Pal cryptosystem are accomplished using few arithmetic operations.

\subsubsection{HElib and the BGV Cryptosystem}
The BGV (Brakerski--Gentry--Vaikuntanathan) cryptosystem \cite{cryptoeprint:2011:277} is a fully homomorphic cryptosystem created based on the ring-learning with error problem. The BGV cryptosystem was constructed to surpass the limitations of prior fully homomorphic cryptosystems, which were based on the first fully homomorphic cryptosystem by Gentry \cite{gentry_fully_2009}.

The details regarding the construction of the BGV cryptosystem are beyond the scope of this paper. For this study, we will be using \textit{HElib} \cite{garay_algorithms_2014}, an open-source library which implements the BGV cryptosystem with optimizations to improve efficiency. Evaluation of operations on 120 inputs in HELib was performed in around 4 minutes, with an average of 2 seconds to process a single input \cite{hutchison_fully_2010,cryptoeprint:2011:566}.

The \textit{HElib} library has been adapted to Python using the Pyfhel library \cite{pyfhel_2018} maintained by Ibarrondo, Laurent (SAP) and Onen (EURECOM), and licensed under the GNU GPL v3 license. The Pyfhel library is a Python API for the \textit{HElib} library, which supports the following operations on vectors/scalars of integers or binary ciphertexts:
\begin{itemize}
	\item Arithmetic operations: addition, subtraction, multiplication;
	\item Binary operations: AND, OR, NOT, XOR.
\end{itemize}

\subsection{CryptoImg}
A paper published in 2009 by Ziad, et al. attempts to implement privacy-preserving image processing using \textit{CryptoImg}, a library for the Open Source Computer Vision Library (OpenCV)~\cite{bradski_opencv_2000} which implements various homomorphic encryption and image processing routines using the Paillier homomorphic cryptosystem~\cite{ziad_cryptoimg:_2016}. The CryptoImg library assumed a client-server model wherein a client requests image processing operations from a server. A client first encrypts a digital image and sends the image securely to a server, which then operates on the encrypted image without revealing its contents. Then the resulting image is sent back to the client, which decrypts the image to recover the desired output.
\begin{figure}[!ht]
    \centering
    \includegraphics[width=0.4\textwidth]{figures/ClientServerModel.png}
    \caption{Client-server architecture used by \textit{CryptoImg} \cite{ziad_cryptoimg:_2016}}
    \label{fig:clientserver}
\end{figure}

The \textit{CryptoImg} library implemented the following:
\begin{enumerate}
	\item Extending the Paillier homomorphic cryptosystem which operate on integer plaintexts so that they can operate on real number plaintexts;
	\item Developing protocols for and implementing the following image processing operations
	\begin{enumerate}
		\item Image negation and brightness adjustment
		\item Spatial filters (for noise reduction, edge detection and sharpening)
		\item Morphological operations
		\item Histogram equalization
	\end{enumerate}
\end{enumerate}
For image negation and spatial filters, the protocols specified by \textit{CryptoImg} allow all image processing operations to be performed on the server. However, due to limitations in the Paillier cryptosystem, the protocols presented for morphological operations and histogram equalization require both the client and the server to perform image processing calculations, although the server performs a significant portion of the processing.

Ziad, et al. also showed experimental results establishing the slow performance of image operations under a homomorphic cryptosystem. For instance, while sharpening and applying a Sobel filter each take less than a second when applied to a $512\times 512$ plaintext image, when applied to an encrypted image, sharpening required at least 238.257 seconds, and applying the Sobel filter required at least 147.567 seconds \cite{ziad_cryptoimg:_2016}.

We now discuss several limitations in the \textit{CryptoImg} study which we focus on for our research. First, the \textit{CryptoImg} library was limited in the image intensity transformations it implemented. We propose additional protocols to support more computationally intensive intensity transformations.
Second, the \textit{CryptoImg} library only considered the Paillier cryptosystem. We consider testing the performance of other homomorphic cryptosystems, which differ in their processing time and supported operations.

\subsection{Image Intensity Transformations}
We represent a digital image $R$ as an $M \times N$ matrix of pixel intensity values, each value in the range $\left[0, L-1\right]$, for some positive integer $L$. We use $R(x,y)$ to represent the entry at the $x$th row and $y$th column of a matrix $R$.
An intensity transformation on an image $R$ can be defined as a function $T$ which maps a pixel value $r$ to a new value $r^\prime$, which we can write as $r^\prime = T\left(r\right)$. This function is then applied to every pixel in $R$.
The \textit{CryptoImg} library implemented two types of linear intensity transformations: image negation and brightness control.

An image negation transformation is defined as:
\begin{equation}
    T\left(r\right) = L-1-r
\end{equation}
After applying image negation, the resulting image would be similar to a photographic negative~\cite{gonzalez_digital_2008}.

A brightness control transformation with parameter $v$ is defined as:
\begin{equation}
    T\left(r,v\right) = r+v
\end{equation}
The above transformations are linear in terms of the input $r$, and are thus simple to implement under a homomorphic cryptosystem.

In this study we extend the range of intensity transformations to non-linear transformations. Two common non-linear image transformations are the log transformation and power-law transformation~\cite{gonzalez_digital_2008}.

The log transformation is used to enhance dark pixels or increase the dark details of an image by mapping low intensity values to a wider range of values~\cite{gonzalez_digital_2008}. This has the general formula
\begin{equation}
    T\left(r\right) = c \log\left(1 + r\right)
\end{equation}
where $c$ is a constant.

The power-law transformation is a family of transformations that have the form
\begin{equation}
    T\left(r\right) = c r^{\gamma}
\end{equation}
where $c>0$ and $\gamma > 0$.
A power-law transformation defined by the above equation can calibrate the operation of many image capture and output devices such as cameras, printers and displays in a process called \textit{gamma correction}. This ensures reproducibility and accuracy of images being displayed by digital output devices~\cite{gonzalez_digital_2008}.

To implement non-linear intensity transformations using addition and multiplication in a homomorphic system, it is necessary to approximate the logarithm and exponential functions, which may result in higher computational overhead. In our software library implementation, we investigate methods required to approximate the logarithm and power functions. Non-linear intensity transformations such as the logarithm transformation have applications in intensity normalization \cite{oravec_illumination_2010}, which is used in some facial recognition algorithms to account for differences in lighting which make facial recognition difficult.

\subsection{Facial Detection and Recognition}
%% TODO: Brian dump ur stuff here

Since simple image operations mentioned earlier can be done within a homomorphic cryptosystem, these operations can be assembled together in order to do more complex operations. A prominent application of image processing that often uses complex image operations is \textit{facial recognition}.

Traditional facial recognition algorithms rely on detecting salient features in a face image. One of the popular facial recognition algorithms is \textit{eigenfaces}.
% Traditional facial recognition algorithms rely on detecting salient features in a face image. Two of the popular facial recognition algorithms are \textit{eigenfaces} and \textit{Haar cascades}.

\subsubsection{Eigenfaces}

Proposed by Matthew Turk and Alex Pentland, the eigenfaces method uses principal component analysis (PCA) in order to express an input image as a linear combination of eigenfaces \cite{turk_eigenfaces_1991}. An \textit{eigenface} is a principal component, or more simply an eigenvector that represents a certain variation between the face images which are taken from the initial training set. The number of resulting eigenfaces is equal to the number of face images in the training set.

In the enrollment process, $M$ face images $\Theta_1, \ldots, \Theta_M$, each of size $p \times q$, are taken in to comprise the initial training set. The training images can be represented as vectors of length $N = pq$, where each row of an image is concatenated together.

The average of the training images, denoted as $\Psi$, is 
\begin{equation}
	\Psi = \frac{1}{M} \sum_{i=1}^{M} \Theta_i
\end{equation}

The \textit{difference vectors} are then computed as $\Phi_i = \Theta_i - \Psi$. PCA is applied on the covariance matrix of the vectors
\begin{equation}
	\mathbf{C} = \frac{1}{M} \sum_{i=1}^M \Phi_i \Phi_i^\top = \frac{1}{M} \mathbf{A}\mathbf{A}^\top,
\end{equation}
where $\mathbf{A}$ is an $N \times M$ matrix defined by $\left[\Theta_1 \quad \Theta_2 \quad \cdots \quad \Theta_M\right]$, in order to determine the orthonormal eigenvectors \cite{hutchison_privacy-preserving_2009}.

Directly computing the covariance matrix and then applying PCA will become inefficient for large sizes of $\mathbf{A}$, since computing for $\mathbf{A}\mathbf{A}^\top$ results in an $N \times N$ matrix, which can get drastically large because it is dependent on the size of the image. On the other hand, computing for $\mathbf{A}^\top\mathbf{A}$ only results in an $M \times M$ matrix, which is much smaller than the previous one because it is just dependent on the number of face images in the training set. Now, we can apply PCA to $\mathbf{A}^\top\mathbf{A}$ along with some post-processing to obtain the eigenvectors \cite{hutchison_privacy-preserving_2009}.

Instead of getting the eigendecomposition of the covariance matrix by explicitly computing the eigenvalues and eigenvectors of $\mathbf{C}$, we can also apply \textit{singular value decomposition} (SVD) on the matrix $\Phi^\top$. This is because SVD works through a divide-and-conquer method which results in greater numerical stability, while eigendecomposition simply uses the traditional QR factorization \cite{nakatsukasa_stable_2013, gu_divide-and-conquer_1995}. Upon applying SVD, we now get the eigenvectors $\mathbf{u}_1, \ldots, \mathbf{u}_M$ and their corresponding eigenvalues $\lambda_1, \ldots, \lambda_M$.

We choose $K$ eigenvectors $\mathbf{u}_1, \ldots, \mathbf{u}_K$ such that it comprises a set associated with the $K$ largest eigenvalues, where $K$ is much smaller than $M$. This set is now the \textit{face space}. Then, the images $\Theta_1, \ldots, \Theta_K$ are projected onto the face space spanned by the eigenfaces to determine the weight vectors $\Omega_1, \ldots, \Omega_K$.

To perform the recognition process, the algorithm projects the input image $\Gamma$ onto the face space, and then comparing the projected image $\bar{\Omega} = \mathbf{u}_i\left(\Gamma - \Psi\right)$ with each eigenface in the face space using a metric such as the Euclidean distance. Thus it is computed as $d_i = \left\lVert \Omega_i -\bar{\Omega} \right\rVert$ for all $i=1,\ldots,K$, where $\left\lVert \cdot \right\rVert$ denotes the Euclidean norm.

Then, a match can be reported if the smallest possible distance is smaller than the given threshold value $T$. 
\newcommand{\argmin}{\mathop{\mathrm{arg\,min}}}  
\begin{equation}
	\text{ID} = \begin{cases}\argmin_i d_i & \text{if } \min_i d_i \le T \\\emptyset & \text {otherwise}\end{cases}
\end{equation}

\subsection{Previous Implementations of Secure Facial Recognition}
Erkin, et al. \cite{hutchison_privacy-preserving_2009} devised a method to incorporate the use of homomorphic cryptosystems into the eigenfaces method. In their study, they proposed a two-party system where Alice holds an encrypted image $\left[\Gamma\right]$, while Bob maintains a database of $K$ eigenfaces $\mathbf{u}_1, \ldots, \mathbf{u}_K$, and feature vectors $\Omega_1, \ldots, \Omega_M$ in the clear.

\begin{figure}[!h]
    \centering
    \includegraphics[width=0.3\textwidth]{figures/secure_eigenfaces.png}
    \caption{Diagram of the privacy-preserving facial recognition process \cite{hutchison_privacy-preserving_2009}.}
\end{figure}

In order to ensure privacy, the steps in the eigenfaces algorithm, namely: projection, distance computation, and match finding, are done within the encrypted domain, i.e., using the operations in the Paillier cryptosystem.

Projection is similar to that of the original eigenfaces algorithm, except the operations are replaced with their respective operations in the cryptosystem. Distance computation in this version is somewhat different from the original eigenfaces method, in that it deals with the square of the Euclidean distance since the relative order of the distances is only important when comparing these during the match finding step \cite{hutchison_privacy-preserving_2009}.
\begin{align}
    d_i &= \left\lVert \Omega_i - \bar{\Omega} \right\rVert ^2 = \sum_{j=1}^{K} \left(\omega_{ij} - \bar{\omega}_j\right)^2 \\
        &= \underbrace{\sum_{j=1}^{K} \omega_{ij}^2}_{\mathcal{S}_1} + \underbrace{\sum_{j=1}^{K} \left(-2 \omega_{ij} \bar{\omega_j}\right)}_{\mathcal{S}_2} + \underbrace{\sum_{j=1}^{K} \bar{\omega}_{j}^2}_{\mathcal{S}_3}
\end{align}

Computing for the distances within Paillier would just be multiplying the encrypted sums together.
\begin{equation}
	\left[d_i\right] = \left[\mathcal{S}_1\right] \cdot \left[\mathcal{S}_2\right] \cdot \left[\mathcal{S}_3\right]
\end{equation}

The terms $\left[\mathcal{S}_1\right]$ and $\left[\mathcal{S}_2\right]$ can be easily computed by Bob, since he already knows both $\omega_i$ in the clear and $\left[\bar{\omega}_i\right]$ which is in encrypted form. Computing for $\left[\mathcal{S}_3\right]$ is trickier because Bob cannot compute for $\left[\bar{\omega}_i^2\right]$ because pairwise multiplication is not supported in Paillier, that is why Bob needs help from Alice to square a number through a protocol described below \cite{hutchison_privacy-preserving_2009}.

Before Bob sends $\left[\bar{\omega}_i\right]$ to Alice for squaring, he adds a random number $r_i$ to compute $\left[x_i\right] = \left[\bar{\omega}_i + r_i\right] = \left[\bar{\omega}_i\right] \cdot \left[r_i\right]$, where $r_i$ is obviously distinct for every $i$, then sends $\left[x_i\right]$ to Alice. She then decrypts it and computes $x_i^2$, and then computes $\mathcal{S}_3^\prime = \sum_{i=1}^{K} x_i^2$, after which she encrypts the sum and sends $\left[\mathcal{S}_3^\prime\right]$ to Bob. Now, he can compute for $\left[\mathcal{S}_3\right]$ as follows:
\begin{equation}
	\left[\mathcal{S}_3\right] = \left[\mathcal{S}_3^\prime\right] \cdot \prod_{j=1}^{K} \left(\left[\bar{\omega}_j\right]^{-2r_j} \cdot \left[-r_j^2\right]\right)
\end{equation}

The protocol for squaring a number as described earlier is a workaround for the limitations of Paillier or any other partially homomorphic cryptosystem that only supports addition and scalar multiplication. This can be possibly extended so that operations such as pairwise multiplication and exponentiation are also supported, provided that the protocol involves two parties.

The match finding step is done by comparing the distances obtained from the previous step to a specified threshold $T$. If the minimum distance is smaller than $T$, then a match is found, and the encrypted identity of the match is returned to Alice \cite{hutchison_privacy-preserving_2009}. Getting the minimum among the encrypted distances would involve comparing two encrypted numbers, which Paillier does not support. Instead, the DGK cryptosystem \cite{pieprzyk_efficient_2007} is used for the comparison protocol.

\section{Methodology}
In this study we apply four homomorphic encryption schemes~\cite{ziad_cryptoimg:_2016, pieprzyk_efficient_2007, dasgupta_design_2016, garay_algorithms_2014} for use in image processing and facial recognition applications.
While the Paillier and DGK cryptosystems have been implemented for use in image processing in~\cite{ziad_cryptoimg:_2016, hutchison_privacy-preserving_2009}, the other cryptosystems have to be adapted for this study.
Two experiments are conducted in this study:
\begin{enumerate}
	\item Assessment of non-linear image intensity transformations under each of the four cryptosystems.
	\item Assessment of efficiency of each of the four cryptosystems when applied for use in privacy-preserving facial recognition and detection using eigenfaces.
\end{enumerate}
The results of the image intensity transformations are tested for image quality using benchmarks in~\cite{ahmed_benchmark_2016}.

\subsection{Cryptosystem Implementation}

Four homomorphic encryption schemes are investigated. For cryptosystems with readily available open-source implementations, such implementations are used. For the remaining cryptosystems, the encryption and decryption methods were implemented in Python.
\begin{itemize}
	\item The Paillier cryptosystem is incorporated using the implementation at \url{https://github.com/n1analytics/python-paillier} developed by Data61 - CSIRO.
	\item The BGV cryptosystem is implemented using the Pyfhel library (\url{https://github.com/ibarrond/Pyfhel}) using a HElib backend from (\url{https://github.com/shaih/HElib}).
	\item The DGK and Dasgupta--Pal cryptosystem are implemented from scratch.
\end{itemize}

For convenience, a wrapper library is created that integrates the four cryptosystems into a unified interface.

\subsection{Secure Computation with Real Numbers}
We will briefly discuss a protocol to enable cryptosystems built for integer inputs to handle real number inputs.
The following protocol was also used by \textit{CryptoImg} for image processing \cite{ziad_cryptoimg:_2016}.

We represent a floating-point (FP) number as a pair of two integers $(m,e)$ representing the mantissa and exponent of the FP number with respect to a base $b$. The mantissa $m$ is encrypted, while the exponent $e$ is unencrypted.
Let $a,b,c$ be FP numbers represented by the pairs $(m_a,e_a),(m_b,e_b),(m_c,e_c)$ respectively. Let $\oplus,\otimes$ represent the homomorphic operations which correspond to the addition and multiplication, respectively. We define the secure real number operations as follows:
\begin{description}
  \item[Addition.]
    To compute $E(c)=E(a+b)$ we compute
    \begin{align*}
      E(m_c) &= E(m_1) \oplus (b^{e_b-e_a} \otimes E(m_b)), e_c = e_a & \text{ if } e_a \leq e_b \\
      E(m_c) &= E(m_b) \oplus (b^{e_a-e_b} \otimes E(m_a)), e_c = e_b & \text{ if } e_a > e_b
    \end{align*}
  \item[Scalar multiplication.]
    To compute $E(c) = E(ab)$, where $a$ and $E(b)$ are known (i.e. $m_a$ is not encrypted), we compute
    \begin{align*}
      E(m_c) &= m_a \otimes E(m_b)\\
      e_c &= e_a + e_b
    \end{align*}
\end{description}

\subsection{Non-Linear Intensity Transformations}
Aside from implementing the homomorphic encryption and decryption algorithms, we will also implement library functions for image negation, logarithm transformation and power-law transformation, as they are defined in~\cite{gonzalez_digital_2008}.
We now describe how we implement the logarithm and power-law image intensity transformations. In the case of partially homomorphic cryptosystems (Paillier, DGK), if  exponentiation and multiplication is required, the secure protocols in section \ref{ssec:exponentiationprotocol} will be used.

\subsubsection{Logarithm Transformation}
The logarithm transformation of a pixel intensity value $x$ is defined as
\begin{align}
	T\left(x\right) = c \log\left(1 + x\right)
\end{align}
where $c$ is a constant.

In order to perform this transformation under a homomorphic cryptosystem, we must provide an approximation for $\log\left(1 + x\right)$ in terms of addition and multiplication operations (or their inverses). We have derived a closed form approximation in Appendix \ref{sec:logapproximation}.
\begin{align}
	\label{eq:scaledquadraturech3}
  \begin{split}
    &\log(1+x) \\
    &\approx \frac{137x^5 + 33185x^4 + 931370x^3 - 13403630x^2 - 289469315x - 713567363}
	{30(x^5 + 505x^4 + 42010x^3 + 923010x^2 + 5722005x + 8040501)} \\
	&+ \log{20}
  \end{split}
\end{align}

\subsubsection{Power-Law Transformation}
The power-law transformation of a pixel intensity value $x$ is defined as
\begin{equation}
    T\left(x\right) = cx^{\gamma}
\end{equation}
where $c>0$ and $\gamma > 0$.

Similar to the logarithm transformation, we must provide an approximation for $x^\gamma$.
We have derived an infinite series in Appendix \ref{sec:logapproximation}.
\begin{align*}
	x^\gamma &= \sum_{n=0}^{\infty}{\frac{(\gamma\log{x})^n}{n!}}
\end{align*}
Partial sums of the above infinite series can be calculated based on the closed form approximation for the logarithm in Equation \ref{eq:scaledquadraturech3}. For the implementation of the power-law transformation, the first six terms of the infinite series were used.

\subsection{Assessment of Homomorphic Encryption Schemes}

Lab computers in Faura Hall, Ateneo de Manila University were used to perform the computations, and processing time was tracked using built-in timing functions. The processing time for all cases were recorded.

\subsubsection{Image Quality of Intensity Transformations}
In this section, we discuss the image quality metrics we used for assessing the performance of non-linear intensity transformations.

We first obtained standard test images from~\cite{gonzalez_image_nodate}. Grayscale images were used in the study.

For each plaintext image (PT), we considered each image operation listed above and generate three images: a plaintext domain transformation (PDT), a ciphertext image (CT), and an ciphertext domain transformation (CDT). The PDT was generated by running the image operation on the original image. The CT was generated by encrypting the image, then applying the operation, and the CDT was generated by decrypting the CT. The four images (PT, PDT, CT, CDT) were then compared using various benchmarks to evaluate the quality and security of each homomorphic encryption scheme.

The benchmarks to be used in the study, adopted from~\cite{ahmed_benchmark_2016, ahmad_efficiency_2012, wu_npcr_2011} are listed below. We let $X_i$ denote a value in an image $X$, where $1 \leq i \leq N$.
We first perform three tests to ascertain the preservation of image quality after encryption and decryption: MSE, PSNR, and SSIM.
\begin{description}
	\item [Mean Squared Error (MSE).] The MSE is defined in~\cite{ahmed_benchmark_2016} as
	\begin{align}
        \mathrm{MSE} = \frac{1}{N}\sum_{i=1}^{N}{(\mathrm{CDT}_i - \mathrm{PDT}_i)^2}.
	\end{align}
	The MSE provides a measure of how much data is recovered if an image operation is applied on the encrypted image, which is then decrypted. Lower values of MSE indicate higher preservation of image quality~\cite{ahmed_benchmark_2016, ahmad_efficiency_2012}.
	\item [Peak Signal to Noise Ratio (PSNR).]
	According to Ahmed, et al.~\cite{ahmed_benchmark_2016}, PSNR is ``an estimator for human visual perception of reconstruction quality.'' It has been used to ascertain image quality in various studies and is a known metric for image and video quality~\cite{upmanyu_efficient_2009, jain_image_2016, akramullah_video_2014}. Although it may produce results which do not correlate with human visual perception~\cite{huynh-thu_accuracy_2012, ahmed_benchmark_2016}, it is a valid indicator of image quality when media containing the same visual content is compared~\cite{huynh-thu_accuracy_2012}.
	PSNR is defined by
	\begin{align}
        \mathrm{PSNR} = 10\log_{10}{\left( \frac{L^2}{\mathrm{MSE}} \right)}
	\end{align}
	where $L$ is the maximum pixel intensity value of an image.
	Despite the known limitations of PSNR, since we are going to compare the effect of each encryption scheme on recovered image quality, given a fixed library of images, it is a valid measure of image quality for the study. A higher PSNR indicates higher image quality preservation.
	\item [Structural Similarity Index (SSIM).]
	The SSIM for two random variables $X$ and $Y$ is defined in~\cite{ahmed_benchmark_2016, akramullah_video_2014} as
	\begin{align}
        \mathrm{SSIM}(X,Y) = \frac{(2\mu_X\mu_Y+c_1)(2\sigma_{XY}+c_2)}{(\mu_X^2+\mu_Y^2+c_1)(\mu_X^2+\mu_Y^2+c_2)}
	\end{align}
	where
	\begin{itemize}
		\item $\mu_X, \mu_Y$ are the averages of $X$ and $Y$, respectively;
		\item $\sigma_X, \sigma_Y$ are the variances of $X$ and $Y$, respectively;
		\item $\sigma_{XY}$ is the covariance of $X$ and $Y$;
		\item $c_1 = (k_1L)^2, c_2 = (k_2L)^2$ are two variables used to stabilize the measure when $\mu_X^2+\mu_Y^2$ is close to zero~\cite{akramullah_video_2014};
		\item $L$ is the the maximum pixel intensity value of an image;
		\item $k_1 = 0.01, k_2 = 0.03$ by default, given in~\cite{ahmed_benchmark_2016}.
	\end{itemize}
	The SSIM is applied to the luminance value of two images to gauge structural similarity between neighboring pixels.
	For the study, we computed $\mathrm{SSIM}(\mathrm{PDT}, \mathrm{CDT})$ for every image operation, under each homomorphic cryptosystem. Higher values of SSIM indicate higher structural similarity, and an SSIM of $1$ indicates that the two images are identical~\cite{ahmed_benchmark_2016}.
\end{description}

Computing for MSE, PSNR, and SSIM was done using the corresponding built-in functions from the scikit-image Python library \cite{scikit-image}.

\subsubsection{Facial Recognition Tests}
The method for secure facial recognition using eigenfaces by Erkin, et al. \cite{hutchison_privacy-preserving_2009} was implemented for this study.

Training and test data were secured from the \texttt{faces94} dataset (\url{https://cswww.essex.ac.uk/mv/allfaces/faces94.html}) maintained by the University of Essex.

The facial recognition tests were done using ten-fold cross-validation for each cryptosystem, where the number of principal components used by the algorithm is fixed at $K=5$.

Prior to splitting the dataset, the images within each set are shuffled. Since there are twenty (20) images per set, two images are taken at a time for each round of cross-validation. The first round would take the first two images from each set as part of the test set, and the rest of the images will be part of the training set. Then, the succeeding round would take the next two images from each set as part of the test set, and so on until ten rounds have been done. After every round of cross-validation, the accuracy score, confusion matrix, and total processing time were obtained.

\subsection{Summary}
In summary, the study consists of:
\begin{itemize}
	\item Creating a wrapper library that acts as a unified interface which implements the Paillier, DGK, Dasgupta--Pal, and BGV homomorphic cryptosystems.
	\item An implementation of image processing operations (intensity transformations, facial recognition) under the above cryptosystems.
	\item Conducting tests for image quality, processing time, using standard test images from~\cite{gonzalez_image_nodate}.
\end{itemize}

\section{Preliminary Results and Discussion}
The results shown here are gathered from the tests for intensity transformations under Paillier and Dasgupta--Pal cryptosystems. During testing, the Pyfhel library being used for the BGV cryptosystem is still

\subsection{Intensity Transformations}
\begin{table}[h]
    \caption{Image negation under Paillier}
    \begin{tabular}{lcccccc}
        \toprule
        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
        \texttt{anpage} & 0.000 & $\infty$ & 1.00000 & 0.084 & 0.010 & 0.016 \\
		\texttt{bplyce} & 0.000 & $\infty$ & 1.00000 & 0.063 & 0.008 & 0.016 \\
		\texttt{drbost} & 0.000 & $\infty$ & 1.00000 & 0.062 & 0.008 & 0.016 \\
		\texttt{ksunth} & 0.000 & $\infty$ & 1.00000 & 0.077 & 0.010 & 0.017 \\
		\texttt{martin} & 0.000 & $\infty$ & 1.00000 & 0.067 & 0.008 & 0.023 \\
		\texttt{pmives} & 0.000 & $\infty$ & 1.00000 & 0.060 & 0.008 & 0.016 \\
		\texttt{rnpwil} & 0.000 & $\infty$ & 1.00000 & 0.061 & 0.008 & 0.030 \\
		\texttt{sbains} & 0.000 & $\infty$ & 1.00000 & 0.061 & 0.008 & 0.033 \\
		\texttt{swewin} & 0.000 & $\infty$ & 1.00000 & 0.072 & 0.008 & 0.016 \\
		\texttt{yfhsie} & 0.000 & $\infty$ & 1.00000 & 0.062 & 0.008 & 0.016 \\
		\bottomrule
        \end{tabular}
\end{table}
\begin{table}[h]
    \caption{Logarithm transformation under Paillier}
    \begin{tabular}{lcccccc}
        \toprule
        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
        \texttt{anpage} & 13.143 & 36.944 & 0.99311 & 0.073 & 1.238 & 0.016 \\
		\texttt{bplyce} & 6.870 & 39.761 & 0.99038 & 0.061 & 1.324 & 0.016 \\
		\texttt{drbost} & 8.019 & 39.089 & 0.98642 & 0.061 & 1.284 & 0.016 \\
		\texttt{ksunth} & 25.194 & 34.118 & 0.98944 & 0.065 & 1.318 & 0.042 \\
		\texttt{martin} & 10.148 & 38.067 & 0.98744 & 0.078 & 1.271 & 0.023 \\
		\texttt{pmives} & 2.404 & 44.322 & 0.99420 & 0.056 & 1.384 & 0.021 \\
		\texttt{rnpwil} & 5.087 & 41.067 & 0.98968 & 0.071 & 1.322 & 0.016 \\
		\texttt{sbains} & 16.762 & 35.888 & 0.98512 & 0.058 & 1.338 & 0.016 \\
		\texttt{swewin} & 5.686 & 40.583 & 0.99360 & 0.067 & 1.360 & 0.016 \\
		\texttt{yfhsie} & 12.135 & 37.290 & 0.99383 & 0.057 & 1.293 & 0.017 \\
		\bottomrule
        \end{tabular}
\end{table}
\begin{table}[h]
    \caption{Power-law transformation under Paillier}
    \begin{tabular}{lcccccc}
        \toprule
        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
        \texttt{anpage} & 4264.991 & 11.832 & 0.35971 & 0.058 & 12.800 & 0.016 \\
		\texttt{bplyce} & 881.611 & 18.678 & 0.87174 & 0.056 & 13.017 & 0.021 \\
		\texttt{drbost} & 1166.789 & 17.461 & 0.83118 & 0.072 & 12.462 & 0.018 \\
		\texttt{ksunth} & 648.512 & 20.012 & 0.91254 & 0.071 & 12.667 & 0.037 \\
		\texttt{martin} & 541.318 & 20.796 & 0.90277 & 0.069 & 12.515 & 0.018 \\
		\texttt{pmives} & 1933.216 & 15.268 & 0.65838 & 0.060 & 12.957 & 0.016 \\
		\texttt{rnpwil} & 728.828 & 19.505 & 0.87270 & 0.064 & 13.752 & 0.016 \\
		\texttt{sbains} & 617.591 & 20.224 & 0.91169 & 0.079 & 12.578 & 0.016 \\
		\texttt{swewin} & 7985.854 & 9.108 & 0.45367 & 0.074 & 12.884 & 0.016 \\
		\texttt{yfhsie} & 2114.705 & 14.878 & 0.60351 & 0.076 & 13.625 & 0.016 \\
		\bottomrule
        \end{tabular}
\end{table}
\begin{table}[h]
    \caption{Image negation under Dasgupta--Pal}
    \begin{tabular}{lcccccc}
        \toprule
        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
		\texttt{anpage} & 0.000 & $\infty$ & 1.00000 & 0.150 & 22.523 & 0.152 \\
		\texttt{bplyce} & 0.000 & $\infty$ & 1.00000 & 0.258 & 21.940 & 0.265 \\
		\texttt{drbost} & 0.000 & $\infty$ & 1.00000 & 0.172 & 22.164 & 0.207 \\
		\texttt{ksunth} & 0.000 & $\infty$ & 1.00000 & 0.222 & 20.952 & 0.156 \\
		\texttt{martin} & 0.000 & $\infty$ & 1.00000 & 0.145 & 28.285 & 0.181 \\
		\texttt{pmives} & 0.000 & $\infty$ & 1.00000 & 0.181 & 21.873 & 0.169 \\
		\texttt{rnpwil} & 0.000 & $\infty$ & 1.00000 & 0.175 & 22.408 & 0.235 \\
		\texttt{sbains} & 0.000 & $\infty$ & 1.00000 & 0.158 & 22.312 & 0.273 \\
		\texttt{swewin} & 0.000 & $\infty$ & 1.00000 & 0.255 & 27.705 & 0.225 \\
		\texttt{yfhsie} & 0.000 & $\infty$ & 1.00000 & 0.289 & 26.008 & 0.185 \\		
		\bottomrule
        \end{tabular}
\end{table}

\section{Conclusion}

\subsection{Ongoing and Future Work}

### 2019-01-09 paper/paper-conf.tex
Results!

@@
 \subsection{Cryptosystem Implementation}
-
 Four homomorphic encryption schemes are investigated.
@@
 	\item The BGV cryptosystem is implemented using the Pyfhel library (\url{https://github.com/ibarrond/Pyfhel}) using a HElib backend from (\url{https://github.com/shaih/HElib}).
-	\item The DGK and Dasgupta--Pal cryptosystem are implemented from scratch.
+	\item The DGK and Dasgupta--Pal cryptosystems are implemented from scratch with Python.
 \end{itemize}
@@
 Partial sums of the above infinite series can be calculated based on the closed form approximation for the logarithm in Equation \ref{eq:scaledquadraturech3}.
-For the implementation of the power-law transformation, the first six terms of the infinite series were used.
+For the implementation of the power-law transformation, a partial sum consisting of the first five terms of the infinite series were used.
 
 \subsection{Assessment of Homomorphic Encryption Schemes}
-
-Lab computers in Faura Hall, Ateneo de Manila University were used to perform the computations, and processing time was tracked using built-in timing functions.
+A laptop computer with a 2.5 GHz Intel Core i7 quad-core processor and 8 GB of RAM is used to perform the computations, and processing time was tracked using built-in timing functions.
 The processing time for all cases were recorded.
+All of the tests are done using Python 3.7.1 running under Linux.
 
@@
 
-We first obtained standard test images from~\cite{gonzalez_image_nodate}. Grayscale images were used in the study.
+We first obtained test images from the \texttt{faces94} dataset (\url{https://cswww.essex.ac.uk/mv/allfaces/faces94.html}) maintained by the University of Essex.
+However, only ten distinct facial images from the dataset were selected for the purposes of this test.
+Since only grayscale images are used in the study, the images were converted to grayscale and then downsampled to $40 \times 36$ pixels.
 
@@
 
-Training and test data were secured from the \texttt{faces94} dataset (\url{https://cswww.essex.ac.uk/mv/allfaces/faces94.html}) maintained by the University of Essex.
+As before, training and test data were also secured from the \texttt{faces94} dataset. The images were first converted to grayscale but it is not downsampled, unlike in the previous test.
 
-The facial recognition tests were done using ten-fold cross-validation for each cryptosystem, where the number of principal components used by the algorithm is fixed at $K=5$.
+The facial recognition tests are done using ten-fold cross-validation for each cryptosystem, where the number of principal components used by the algorithm is fixed at $K=5$.
 
@@
 Then, the succeeding round would take the next two images from each set as part of the test set, and so on until ten rounds have been done.
-After every round of cross-validation, the accuracy score, confusion matrix, and total processing time were obtained.
+After every round of cross-validation, the accuracy score, confusion matrix, and total processing time are obtained.
 
@@
 \section{Preliminary Results and Discussion}
-The results shown here are gathered from the tests for intensity transformations under Paillier and Dasgupta--Pal cryptosystems.
-During testing, the Pyfhel library being used for the BGV cryptosystem is still
+The results shown in this section are gathered from the tests for intensity transformations under Paillier and Dasgupta--Pal cryptosystems.
+During testing, initial results obtained from BGV, particularly with image operations involving floating-point numbers like the logarithmic transformation, were unstable (i.e.
+the results vary drastically every time the same tests were done).
+This is because the Pyfhel library being used for the BGV cryptosystem is still in alpha development stage \cite{pyfhel_2018}.
+
+% One of the authors has already informed the maintainers of the library about a bug involving exponentiation of two real numbers.
 
 \subsection{Intensity Transformations}
-\begin{table}[h]
+The following tables show the resulting metric scores for mean squared error (MSE), peak signal to noise ratio (PSNR), and structural similarity index (SSIM), as well as time taken for encrypting the input image ($t_\text{enc}$), applying an operation to the encrypted image ($t_\text{apply}$), and decrypting the resulting encrypted image ($t_\text{dec}$), for each image in the test set.
+
+\subsubsection{Image Negation}
+Both the Paillier and Dasgupta--Pal cryptosystems were able to perform image negation under the encrypted domain without introducing noise in the resulting image.
+In other words, the resulting image from doing image negation on an image on the clear and doing image negation under the encrypted domain are identical, as evidenced by the mean squared errors being exactly equal to zero and the SSIM being exactly equal to one.
+
+The Paillier cryptosystem performed better in terms of time, only taking about 0.01 seconds to apply image negation.
+On the other hand, the Dasgupta--Pal cryptosystem took about 22 seconds each to apply the same operation, which is expected since the implementation for Dasgupta--Pal was done in Python without using any external libraries.
+
+\begin{table}[!h]
     \caption{Image negation under Paillier}
@@
         Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
-        \texttt{anpage} & 0.000 & $\infty$ & 1.00000 & 0.084 & 0.010 & 0.016 \\
-		\texttt{bplyce} & 0.000 & $\infty$ & 1.00000 & 0.063 & 0.008 & 0.016 \\
-		\texttt{drbost} & 0.000 & $\infty$ & 1.00000 & 0.062 & 0.008 & 0.016 \\
-		\texttt{ksunth} & 0.000 & $\infty$ & 1.00000 & 0.077 & 0.010 & 0.017 \\
-		\texttt{martin} & 0.000 & $\infty$ & 1.00000 & 0.067 & 0.008 & 0.023 \\
-		\texttt{pmives} & 0.000 & $\infty$ & 1.00000 & 0.060 & 0.008 & 0.016 \\
-		\texttt{rnpwil} & 0.000 & $\infty$ & 1.00000 & 0.061 & 0.008 & 0.030 \\
-		\texttt{sbains} & 0.000 & $\infty$ & 1.00000 & 0.061 & 0.008 & 0.033 \\
-		\texttt{swewin} & 0.000 & $\infty$ & 1.00000 & 0.072 & 0.008 & 0.016 \\
-		\texttt{yfhsie} & 0.000 & $\infty$ & 1.00000 & 0.062 & 0.008 & 0.016 \\
+        \texttt{anpage} & 0.000 & inf & 1.00000 & 0.128 & 0.013 & 0.041 \\
+		\texttt{bplyce} & 0.000 & inf & 1.00000 & 0.084 & 0.013 & 0.024 \\
+		\texttt{drbost} & 0.000 & inf & 1.00000 & 0.099 & 0.012 & 0.031 \\
+		\texttt{ksunth} & 0.000 & inf & 1.00000 & 0.109 & 0.012 & 0.048 \\
+		\texttt{martin} & 0.000 & inf & 1.00000 & 0.117 & 0.015 & 0.043 \\
+		\texttt{pmives} & 0.000 & inf & 1.00000 & 0.111 & 0.012 & 0.025 \\
+		\texttt{rnpwil} & 0.000 & inf & 1.00000 & 0.099 & 0.012 & 0.023 \\
+		\texttt{sbains} & 0.000 & inf & 1.00000 & 0.084 & 0.012 & 0.024 \\
+		\texttt{swewin} & 0.000 & inf & 1.00000 & 0.089 & 0.012 & 0.023 \\
+		\texttt{yfhsie} & 0.000 & inf & 1.00000 & 0.081 & 0.012 & 0.029 \\
 		\bottomrule
@@
 \end{table}
-\begin{table}[h]
+\begin{table}[!h]
+    \caption{Image negation under Dasgupta--Pal}
+    \begin{tabular}{lcccccc}
+        \toprule
+        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
+		\texttt{anpage} & 0.000 & inf & 1.00000 & 0.221 & 30.217 & 0.239 \\
+		\texttt{bplyce} & 0.000 & inf & 1.00000 & 0.190 & 30.919 & 0.216 \\
+		\texttt{drbost} & 0.000 & inf & 1.00000 & 0.284 & 31.182 & 0.268 \\
+		\texttt{ksunth} & 0.000 & inf & 1.00000 & 0.225 & 32.581 & 0.223 \\
+		\texttt{martin} & 0.000 & inf & 1.00000 & 0.220 & 32.220 & 0.271 \\
+		\texttt{pmives} & 0.000 & inf & 1.00000 & 0.287 & 31.224 & 0.294 \\
+		\texttt{rnpwil} & 0.000 & inf & 1.00000 & 0.285 & 29.478 & 0.284 \\
+		\texttt{sbains} & 0.000 & inf & 1.00000 & 0.186 & 29.784 & 0.362 \\
+		\texttt{swewin} & 0.000 & inf & 1.00000 & 0.243 & 38.407 & 0.220 \\
+		\texttt{yfhsie} & 0.000 & inf & 1.00000 & 0.285 & 29.488 & 0.449 \\		
+		\bottomrule
+        \end{tabular}
+\end{table}
+
+\subsubsection{Logarithm Transformation}
+\begin{table}[!h]
     \caption{Logarithm transformation under Paillier}
@@
         Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
-        \texttt{anpage} & 13.143 & 36.944 & 0.99311 & 0.073 & 1.238 & 0.016 \\
-		\texttt{bplyce} & 6.870 & 39.761 & 0.99038 & 0.061 & 1.324 & 0.016 \\
-		\texttt{drbost} & 8.019 & 39.089 & 0.98642 & 0.061 & 1.284 & 0.016 \\
-		\texttt{ksunth} & 25.194 & 34.118 & 0.98944 & 0.065 & 1.318 & 0.042 \\
-		\texttt{martin} & 10.148 & 38.067 & 0.98744 & 0.078 & 1.271 & 0.023 \\
-		\texttt{pmives} & 2.404 & 44.322 & 0.99420 & 0.056 & 1.384 & 0.021 \\
-		\texttt{rnpwil} & 5.087 & 41.067 & 0.98968 & 0.071 & 1.322 & 0.016 \\
-		\texttt{sbains} & 16.762 & 35.888 & 0.98512 & 0.058 & 1.338 & 0.016 \\
-		\texttt{swewin} & 5.686 & 40.583 & 0.99360 & 0.067 & 1.360 & 0.016 \\
-		\texttt{yfhsie} & 12.135 & 37.290 & 0.99383 & 0.057 & 1.293 & 0.017 \\
+		\texttt{anpage} & 13.369 & 36.870 & 0.99263 & 0.085 & 1.813 & 0.023 \\
+		\texttt{bplyce} & 7.072 & 39.635 & 0.99017 & 0.089 & 2.073 & 0.023 \\
+		\texttt{drbost} & 8.151 & 39.019 & 0.98688 & 0.091 & 1.913 & 0.023 \\
+		\texttt{ksunth} & 25.253 & 34.108 & 0.98927 & 0.089 & 1.919 & 0.023 \\
+		\texttt{martin} & 10.374 & 37.971 & 0.98695 & 0.106 & 1.829 & 0.023 \\
+		\texttt{pmives} & 2.426 & 44.283 & 0.99401 & 0.127 & 1.900 & 0.023 \\
+		\texttt{rnpwil} & 5.184 & 40.985 & 0.98971 & 0.096 & 1.853 & 0.023 \\
+		\texttt{sbains} & 16.772 & 35.885 & 0.98492 & 0.081 & 1.746 & 0.024 \\
+		\texttt{swewin} & 5.803 & 40.494 & 0.99241 & 0.091 & 1.827 & 0.027 \\
+		\texttt{yfhsie} & 12.192 & 37.270 & 0.99354 & 0.081 & 1.815 & 0.023 \\
 		\bottomrule
@@
 \end{table}
-\begin{table}[h]
+\begin{table}[!h]
+    \caption{Logarithm transformation under Dasgupta--Pal}
+    \begin{tabular}{lcccccc}
+        \toprule
+        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
+		\texttt{anpage} & 0.004 & 71.624 & 0.99999 & 0.287 & 802.957 & 0.036 \\
+		\texttt{bplyce} & 0.000 & 82.043 & 1.00000 & 0.190 & 815.384 & 0.048 \\
+		\texttt{drbost} & 0.004 & 72.480 & 1.00000 & 0.270 & 813.640 & 0.036 \\
+		\texttt{ksunth} & 0.000 & 87.372 & 1.00000 & 0.204 & 804.629 & 0.047 \\
+		\texttt{martin} & 0.001 & 77.421 & 1.00000 & 0.245 & 822.940 & 0.036 \\
+		\texttt{pmives} & 0.001 & 76.934 & 1.00000 & 0.194 & 814.132 & 0.036 \\
+		\texttt{rnpwil} & 0.000 & 83.135 & 1.00000 & 0.197 & 808.503 & 0.047 \\
+		\texttt{sbains} & 0.001 & 77.301 & 1.00000 & 0.270 & 809.406 & 0.047 \\
+		\texttt{swewin} & 0.006 & 70.004 & 0.99999 & 0.268 & 813.217 & 0.051 \\
+		\texttt{yfhsie} & 0.001 & 78.576 & 1.00000 & 0.243 & 830.640 & 0.039 \\
+		\bottomrule
+        \end{tabular}
+\end{table}
+
+\subsubsection{Power-Law Transformation}
+\begin{table}[!h]
     \caption{Power-law transformation under Paillier}
@@
         Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
-        \texttt{anpage} & 4264.991 & 11.832 & 0.35971 & 0.058 & 12.800 & 0.016 \\
-		\texttt{bplyce} & 881.611 & 18.678 & 0.87174 & 0.056 & 13.017 & 0.021 \\
-		\texttt{drbost} & 1166.789 & 17.461 & 0.83118 & 0.072 & 12.462 & 0.018 \\
-		\texttt{ksunth} & 648.512 & 20.012 & 0.91254 & 0.071 & 12.667 & 0.037 \\
-		\texttt{martin} & 541.318 & 20.796 & 0.90277 & 0.069 & 12.515 & 0.018 \\
-		\texttt{pmives} & 1933.216 & 15.268 & 0.65838 & 0.060 & 12.957 & 0.016 \\
-		\texttt{rnpwil} & 728.828 & 19.505 & 0.87270 & 0.064 & 13.752 & 0.016 \\
-		\texttt{sbains} & 617.591 & 20.224 & 0.91169 & 0.079 & 12.578 & 0.016 \\
-		\texttt{swewin} & 7985.854 & 9.108 & 0.45367 & 0.074 & 12.884 & 0.016 \\
-		\texttt{yfhsie} & 2114.705 & 14.878 & 0.60351 & 0.076 & 13.625 & 0.016 \\
-		\bottomrule
-        \end{tabular}
-\end{table}
-\begin{table}[h]
-    \caption{Image negation under Dasgupta--Pal}
-    \begin{tabular}{lcccccc}
-        \toprule
-        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
-		\texttt{anpage} & 0.000 & $\infty$ & 1.00000 & 0.150 & 22.523 & 0.152 \\
-		\texttt{bplyce} & 0.000 & $\infty$ & 1.00000 & 0.258 & 21.940 & 0.265 \\
-		\texttt{drbost} & 0.000 & $\infty$ & 1.00000 & 0.172 & 22.164 & 0.207 \\
-		\texttt{ksunth} & 0.000 & $\infty$ & 1.00000 & 0.222 & 20.952 & 0.156 \\
-		\texttt{martin} & 0.000 & $\infty$ & 1.00000 & 0.145 & 28.285 & 0.181 \\
-		\texttt{pmives} & 0.000 & $\infty$ & 1.00000 & 0.181 & 21.873 & 0.169 \\
-		\texttt{rnpwil} & 0.000 & $\infty$ & 1.00000 & 0.175 & 22.408 & 0.235 \\
-		\texttt{sbains} & 0.000 & $\infty$ & 1.00000 & 0.158 & 22.312 & 0.273 \\
-		\texttt{swewin} & 0.000 & $\infty$ & 1.00000 & 0.255 & 27.705 & 0.225 \\
-		\texttt{yfhsie} & 0.000 & $\infty$ & 1.00000 & 0.289 & 26.008 & 0.185 \\		
+        \texttt{anpage} & 3910.678 & 12.208 & 0.46712 & 0.099 & 14.695 & 0.024 \\
+		\texttt{bplyce} & 873.064 & 18.720 & 0.84379 & 0.139 & 16.190 & 0.023 \\
+		\texttt{drbost} & 1261.059 & 17.123 & 0.77229 & 0.082 & 13.866 & 0.023 \\
+		\texttt{ksunth} & 653.049 & 19.981 & 0.90673 & 0.083 & 15.507 & 0.023 \\
+		\texttt{martin} & 646.310 & 20.026 & 0.88157 & 0.108 & 15.727 & 0.045 \\
+		\texttt{pmives} & 2047.933 & 15.018 & 0.69408 & 0.113 & 14.728 & 0.034 \\
+		\texttt{rnpwil} & 806.473 & 19.065 & 0.85346 & 0.082 & 14.253 & 0.024 \\
+		\texttt{sbains} & 616.419 & 20.232 & 0.92334 & 0.121 & 14.415 & 0.023 \\
+		\texttt{swewin} & 8270.696 & 8.955 & 0.43185 & 0.112 & 14.362 & 0.065 \\
+		\texttt{yfhsie} & 1715.478 & 15.787 & 0.73857 & 0.145 & 20.239 & 0.023 \\
 		\bottomrule

### 2019-01-10 paper/PCSC2019-sigconf.tex
New results

@@
 \usepackage{multicol}
+\usepackage{multirow}
 \usepackage{amsmath}
 \usepackage{amssymb}
+\usepackage{xinttools}
+\usepackage{array}
 \usepackage{booktabs} % For formal tables
@@
 % The default list of authors is too long for headers.
-\renewcommand{\shorttitle}{Implementation and Analysis}
+\renewcommand{\shorttitle}{Impl. and Analysis of Homomorphic Facial Image Encryption and Manipulation}
 % \renewcommand{\shortauthors}{B. Trovato et al.}
@@
 \begin{abstract}
-This paper provides a sample of a \LaTeX\ document which conforms,
-somewhat loosely, to the formatting guidelines for
-ACM SIG Proceedings.\footnote{This is an abstract footnote}
+Homomorphic cryptography allows for encrypted data to be modified and operated on without requiring decryption, although current homomorphic cryptosystems are either limited in their permitted operations or are significantly more time-intensive than standard non-homomorphic cryptosystems.
+Regardless, homomorphic cryptography has been targeted for use in secure image processing and facial recognition, due to their ability to maintain data privacy, In this paper, we compared the viability of the Paillier, Damg{\aa}rd--Geisler--Kr{\o}igaard (DGK), Dasgupta--Pal, and Brakerski--Gentry--Vaikuntanathan (BGV) cryptosystems for facial image processing applications, by implementing a software library equipped with these cryptosystems, and comparing their time efficiency and accuracy.
+Furthermore, as an extension to previous research, we attempt to support non-linear image processing operations.
+Preliminary results have shown that the Pailler and Dasgupta--Pal cryptosystems are comparable in accuracy and may be used to approximate a logarithm transformation, but the Dasgupta--Pal cryptosystem is significantly slower.
 \end{abstract}
@@
 
-\keywords{ACM proceedings, \LaTeX, text tagging}
+\keywords{homomorphic encryption, image operations, facial recognition, numerical approximations}
 
@@
   The authors would like to thank Dr. Yuhua Li for providing the
-  MATLAB code of the \textit{BEPS} method.
+  MATLAB code of the \textit{BEPS} method. Testing testing.
 

### 2019-01-10 paper/appendix.tex
New results

@@
 \begin{description}
-	\item[XOR on ciphertexts]
+	\item[\textsc{xor} on ciphertexts]
 	\begin{align*}
@@
 	\end{align*}
-	\item[AND on ciphertexts]
+	\item[\textsc{and} on ciphertexts]
 	\begin{align*}
@@
 			Since $ab = S_kq + r$, $S_kq + r$ must also be even.
-			$S_k$ is even, so $S_kq$ is also even. For $S_kq + r$ to be even, $r$ must be even , since $S_k$ is even.
+			$S_k$ is even, so $S_kq$ is also even. For $S_kq + r$ to be even, $r$ must be even, since $S_k$ is even.
 
@@
 Transcendental functions such as the exponential and logarithmic functions are usually implemented in computer hardware and software libraries using minimax polynomials, which are determined numerically using the Remez algorithm \cite{harrison_computation_1999}.
-However, the Remez algorithm relies on iteratively refining the polynomial coefficients, which requires knowledge of the argument passed to the exponential or logarithmic function.
+However, the Remez algorithm relies on iteratively refining the polynomial coefficients, which requires knowledge of the argument passed to the transcendental function.
 
@@
 
-%TODO: Explain why standard methods for transcedental function approximation cannot be applied here.
-%TODO: Include citations for this chapter
 \subsection{Approximation for $\log(1+x)$}
@@
 We let $x = 1/n$ and consider the integral
-\begin{align*}
+\begin{equation}
+	\label{eq:log_integral}
   	\int_{n}^{n+1}{\frac{1}{x}\diff x}=\log{\left(1+\frac{1}{n}\right)}.
-\end{align*}
+\end{equation}
 
-This integral can be approximated using the five-point Gauss-Legendre quadrature rule \cite{kythe_quadrature_2002}, which is as follows:
+This integral can be approximated using the five-point Gauss-Legendre quadrature rule \cite{kythe_quadrature_2002}.
+We first convert the integral to an integral over the interval $[-1,1]$ using the following transformation:
 \begin{align*}
 	\int_a^b{f(x)\diff x}
-	&= \frac{b-a}{2}\int_{-1}^{1}{f\left(\frac{b-a}{2}x+\frac{a+b}{2}\right)\diff x}\\
-	\int_{-1}^{1}{f(x)\diff x} &= \sum_{i=1}^{5}{w_if(x_i)}
+	&= \frac{b-a}{2}\int_{-1}^{1}{f\left(\frac{b-a}{2}x+\frac{a+b}{2}\right)\diff x}.
+\end{align*}
+Then, we approximate the integral using the following summation:
+\begin{align*}
+  \int_{-1}^{1}{f(x)\diff x} &= \sum_{i=1}^{5}{w_if(x_i)},
 \end{align*}
@@
 		w_4 &= \frac{1}{21}\sqrt{245+14\sqrt{70}}\\
-		w_5 &= -\frac{1}{21}\sqrt{245+14\sqrt{70}}\\
+		w_5 &= -\frac{1}{21}\sqrt{245+14\sqrt{70}}
 	\end{align*}
@@
 		x_4 &= \frac{1}{900}\left( 322 - 13\sqrt{70}\right)\\
-		x_5 &= \frac{1}{900}\left( 322 - 13\sqrt{70}\right)\\
+		x_5 &= \frac{1}{900}\left( 322 - 13\sqrt{70}\right)
 	\end{align*}
 \end{multicols}
-This yields the following approximation:
+Applying this procedure to the integral in equation \ref{eq:log_integral} using SageMath 8.3 yields the following approximation:
 \begin{equation}\label{eq:standardquadrature}
@@
 \end{equation}
-While this closed form approximation is accurate for values of $x$ near zero, it diverges from $\log{(1+x)}$ significantly for large values of $x$.
+
+While the closed form approximation in equation \ref{eq:standardquadrature} is accurate for values of $x$ near zero, it diverges from $\log{(1+x)}$ significantly for large values of $x$, as shown in figure \ref{fig:standardquadrature}.
 \begin{figure}[!ht]
@@
 \end{figure}
-As we only need accuracy for $x \in [0, 255]$, we can scale the approximation by a constant factor $\alpha$ as follows:
+
+As we only need accuracy for arguments $x \in [0, 255]$, we can scale the approximation by a constant factor $\alpha$ as follows:
 \begin{align*}
@@
 
-Using the five-point Gauss-Legendre quadrature rule with $\alpha = 1/20$, we arrive at the approximation:
+Applying the five-point Gauss-Legendre quadrature rule with $\alpha = 1/20$ using SageMath 8.3, we arrive at the approximation:
 \begin{align}\label{eq:scaledquadrature}
@@
 \end{align}
-Below is a graph of the absolute error of the scaled approximation and the exact value of $\log{(1+x)}$.
+
+Figure \ref{fig:scaledquadrature} is a graph of the absolute error of the scaled approximation and the exact value of $\log{(1+x)}$.
+Using SageMath 8.3, it was numerically determined that the maximum absolute error of this approximation in the range $x\in[0,255]$ is approximately $0.0103315865985758$, occurring at $x=255$.
+This is an improvement from the approximation in equation \ref{eq:standardquadrature}, which has a maximum absolute error of $1.19717868468392$, similarly occurring at $x=255$.
+
 \begin{figure}[h]
@@
 \end{align*}
+
 This expression can then be approximated using the Maclaurin series expansion for $e^x$, which converges for all $x$.
@@
 \end{align*}
+
 As we already have an approximation for the natural logarithm, we can evaluate partial sums of the above infinite series to arrive at approximations for $x^\gamma$.

### 2019-01-10 paper/paper-conf.tex
New results

@@
 
-\subsection{Significance of the Study}
-This study aims to directly address one of the current problems in the research of homomorphic cryptosystems: the practicality of homomorphic encryption~\cite{sen_homomorphic_2013}.
-The literature shows existing homomorphic cryptosystems and how they support primitive operations (usually addition and multiplication) on encrypted data, however, for homomorphic cryptosystems to be useful for practical use, efficient support for more complicated image processing operation must be demonstrated as well.
-While implementations of image processing operations in a homomorphic cryptosystem exist in the literature~\cite{ziad_cryptoimg:_2016, garay_algorithms_2014}, our study targets the more computationally intensive task of facial detection.
-
-We wish to contribute to existing models for the secure transmission and modification of image data by developing a software library which allows the use and comparison of various homomorphic encryption algorithms.
-Our software library would allow service providers to perform image manipulation for clients without compromising data privacy.
-
 \subsection{Scope and Limitations}
@@
 Training and test data are taken from the publicly available \texttt{faces94} dataset (\url{https://cswww.essex.ac.uk/mv/allfaces/faces94.html}) maintained by the University of Essex.
+
+\subsection{Significance of the Study}
+This study aims to directly address one of the current problems in the research of homomorphic cryptosystems: the practicality of homomorphic encryption~\cite{sen_homomorphic_2013}.
+The literature shows existing homomorphic cryptosystems and how they support primitive operations (usually addition and multiplication) on encrypted data, however, for homomorphic cryptosystems to be useful for practical use, efficient support for more complicated image processing operation must be demonstrated as well.
+While implementations of image processing operations in a homomorphic cryptosystem exist in the literature~\cite{ziad_cryptoimg:_2016, garay_algorithms_2014}, our study targets the more computationally intensive task of facial detection.
+
+We wish to contribute to existing models for the secure transmission and modification of image data by developing a software library which allows the use and comparison of various homomorphic encryption algorithms.
+Our software library would allow service providers to perform image manipulation for clients without compromising data privacy.
 
@@
 \subsection{Partially Homomorphic Cryptosystems}
-
 In this section, we will present two classical partially homomorphic cryptosystems which we will be testing in the study: the Paillier cryptosystem and the DGK cryptosystem.
@@
 
-The decryption function to decrypt a ciphertext $c \in \mathbb{Z}_{n^2}$ given a private key $(p,q)$ is defined as:
+The decryption function to decrypt a ciphertext $c \in \mathbb{Z}^\ast_{n^2}$ given a private key $(p,q)$ is defined as:
 \begin{align*}
@@
 \paragraph{Homomorphic Properties of the Paillier Cryptosystem}
-The Paillier cryptosystem supports additive homomorphism as well as the multiplication of a plaintext scalar to an encrypted message. These operations are defined as follows.
+The Paillier cryptosystem supports additive homomorphism as well as the multiplication of a plaintext scalar to an encrypted message.
+These homomorphic properties are used to add a plaintext scalar to a ciphertext, add two ciphertexts, and multiply a ciphertext by a plaintext scalar, respectively.
+They are defined as follows.
+
 For all $m_1,m_2 \in \mathbb{Z}_n$ and $k\in \mathbb{N}$, the following homomorphic properties hold.
 \begin{align*}
-  D(E(m_1)g^k\bmod n^2)=(m_1+k)\bmod n & \text{ (used to add a constant)}\\
-  D(E(m_1)E(m_2)\bmod n^2)=(m_1+m_2)\bmod n & \text{ (used for binary addition)}\\
-  D(E(m_1)^k\bmod n^2)= km_1\bmod n & \text{ (used to multiply a plaintext constant)}
+  D(E(m_1)g^k\bmod n^2) &=(m_1+k)\bmod n\\
+  D(E(m_1)E(m_2)\bmod n^2) &=(m_1+m_2)\bmod n\\
+  D(E(m_1)^k\bmod n^2) &= km_1\bmod n
 \end{align*}
@@
 \paragraph{Homomorphic Properties of the DGK Cryptosystem}
-The DGK cryptosystem supports additive homomorphism as well as the multiplication of a plaintext scalar to an encrypted message. These operations are defined as follows.
+The DGK cryptosystem supports additive homomorphism as well as the multiplication of a plaintext scalar to an encrypted message.
+These homomorphic properties are used to add a plaintext scalar to a ciphertext, add two ciphertexts, and multiply a ciphertext by a plaintext scalar, respectively.
+They are defined as follows.
+
 For all $m_1,m_2 \in \mathbb{Z}_u$ and $k\in \mathbb{N}$, the following homomorphic properties hold.
 \begin{align*}
-    D(E(m_1)g^k)=(m_1+k)\bmod u & \text{ (used to add a constant)}\\
-    D(E(m_1)E(m_2))=(m_1+m_2)\bmod u & \text{ (used for binary addition)}\\
-    D(E(m_1)^k)= km_1\bmod u & \text{ (used to multiply a plaintext constant)}
+    D(E(m_1)g^k) &=(m_1+k)\bmod u\\
+    D(E(m_1)E(m_2)) &=(m_1+m_2)\bmod u\\
+    D(E(m_1)^k) &= km_1\bmod u
 \end{align*}
@@
 \begin{description}
-	\item[XOR on ciphertexts]
-	A bitwise exclusive or (XOR) operation on integer messages can be achieved by adding the coefficients pairwise between two ciphertexts.
+	\item[\textsc{xor} on ciphertexts]
+	A bitwise exclusive or (\textsc{xor}) operation on integer messages can be achieved by adding the coefficients pairwise between two ciphertexts.
 	\begin{align*}
@@
 	\end{align*}
-	\item[AND on ciphertexts]
-	Similarly, pair-wise multiplication corresponds to bitwise AND of integer messages.
+	\item[\textsc{and} on ciphertexts]
+	Similarly, pair-wise multiplication corresponds to bitwise \textsc{and} of integer messages.
 	\begin{align*}
@@
 	\item Arithmetic operations: addition, subtraction, multiplication;
-	\item Binary operations: AND, OR, NOT, XOR.
+	\item Binary operations: \textsc{and}, \textsc{or}, \textsc{not}, \textsc{xor}.
 \end{itemize}
@@
 \subsubsection{Eigenfaces}
-
 Proposed by Matthew Turk and Alex Pentland, the eigenfaces method uses principal component analysis (PCA) in order to express an input image as a linear combination of eigenfaces \cite{turk_eigenfaces_1991}.
@@
     \centering
-    \includegraphics[width=0.3\textwidth]{figures/secure_eigenfaces.png}
-    \caption{Diagram of the privacy-preserving facial recognition process \cite{hutchison_privacy-preserving_2009}.}
+    \includegraphics[width=0.4\textwidth]{figures/secure_eigenfaces.png}
+    \caption{Diagram of the privacy-preserving facial recognition process \cite{hutchison_privacy-preserving_2009}}
 \end{figure}
@@
 The following protocol was also used by \textit{CryptoImg} for image processing \cite{ziad_cryptoimg:_2016}.
+This is also used for our own implementation of the Dasgupta--Pal cryptosystem in order to handle real numbers.
 
@@
 We have derived an infinite series in Appendix \ref{sec:logapproximation}.
-\begin{align*}
+\begin{align}
 	x^\gamma &= \sum_{n=0}^{\infty}{\frac{(\gamma\log{x})^n}{n!}}
-\end{align*}
+\end{align}
 Partial sums of the above infinite series can be calculated based on the closed form approximation for the logarithm in Equation \ref{eq:scaledquadraturech3}.
@@
 The processing time for all cases were recorded.
-All of the tests are done using Python 3.7.1 running under Linux.
+All of the tests are done using Python 3.7.1 running on Linux.
 
@@
 Since only grayscale images are used in the study, the images were converted to grayscale and then downsampled to $40 \times 36$ pixels.
+
+For each cryptosystem, three image operations are tested:
+\begin{enumerate}
+	\item Image negation
+	\item Logarithm transformation, with $c = 30$
+	\item Power-law transformation, with $c = 1$ and $\gamma = 0.4$
+\end{enumerate}
 
@@
 	\item An implementation of image processing operations (intensity transformations, facial recognition) under the above cryptosystems.
-	\item Conducting tests for image quality, processing time, using standard test images from~\cite{gonzalez_image_nodate}.
+	\item Conducting tests for image quality, processing time, using images from the \texttt{faces94} dataset.
 \end{itemize}
@@
 \subsection{Intensity Transformations}
-The following tables show the resulting metric scores for mean squared error (MSE), peak signal to noise ratio (PSNR), and structural similarity index (SSIM), as well as time taken for encrypting the input image ($t_\text{enc}$), applying an operation to the encrypted image ($t_\text{apply}$), and decrypting the resulting encrypted image ($t_\text{dec}$), for each image in the test set.
+
+\begin{table*}
+	\caption{Comparison of intensity transformations under Paillier}
+	\label{tbl:it-pal}
+	\begin{tabular}{m{1cm}*{7}{>{\centering\arraybackslash}m{1.75cm}}}
+		\toprule
+		\multirow{2}{*}{Image} & \multirow{2}{*}{Original} & \multicolumn{2}{c}{Image negation} & \multicolumn{2}{c}{Logarithm transformation} & \multicolumn{2}{c}{Power-law transformation} \\
+							   &                           & PDT           & CDT          & PDT            & CDT           & PDT               & CDT           \\ 
+		\midrule
+		\xintFor #1 in {anpage, bplyce, drbost, ksunth, martin, pmives, rnpwil, sbains, swewin, yfhsie} \do {%
+		\texttt{#1} & \includegraphics[width=1.75cm]{out_faces/paillier_negate_#1_original.png} & \includegraphics[width=1.75cm]{out_faces/paillier_negate_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/paillier_negate_#1_decrypted.png} & \includegraphics[width=1.75cm]{out_faces/paillier_logtransform_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/paillier_logtransform_#1_decrypted.png} & \includegraphics[width=1.75cm]{out_faces/paillier_pwrtransform_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/paillier_pwrtransform_#1_decrypted.png} \\ }%
+		\bottomrule         
+	\end{tabular}
+\end{table*}
+
+\begin{table*}
+	\caption{Comparison of intensity transformations under Dasgupta--Pal}
+	\label{tbl:it-dp}
+	\begin{tabular}{m{1cm}*{7}{>{\centering\arraybackslash}m{1.75cm}}}
+		\toprule
+		\multirow{2}{*}{Image} & \multirow{2}{*}{Original} & \multicolumn{2}{c}{Image negation} & \multicolumn{2}{c}{Logarithm transformation} & \multicolumn{2}{c}{Power-law transformation} \\
+							   &                           & PDT           & CDT          & PDT            & CDT           & PDT               & CDT           \\ 
+		\midrule
+		\xintFor #1 in {anpage, bplyce, drbost, ksunth, martin, pmives, rnpwil, sbains, swewin, yfhsie} \do {%
+		\texttt{#1} & \includegraphics[width=1.75cm]{out_faces/dp_negate_#1_original.png} & \includegraphics[width=1.75cm]{out_faces/dp_negate_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/dp_negate_#1_decrypted.png} & \includegraphics[width=1.75cm]{out_faces/dp_logtransform_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/dp_logtransform_#1_decrypted.png} & \includegraphics[width=1.75cm]{out_faces/paillier_pwrtransform_#1_reference.png} &  \\ }%
+		\bottomrule         
+	\end{tabular}
+\end{table*}
+
+Table~\ref{tbl:it-pal} shows the images obtained from the intensity transformation tests under the Paillier cryptosystem, while Table~\ref{tbl:it-pal} shows the resulting images from the same tests under the Dasgupta--Pal cryptosystem.
+Shown for each image is the original unecrypted image, and for each intensity transformation the \textit{plaintext domain transformation} (PDT) is given which is the resulting image after applying the transformation to the unencrypted image and the \textit{ciphertext domain transformation} (CDT) is the decrypted image of the processed encrypted image.
+
+The following tables show the resulting metric scores for mean squared error (MSE), peak signal to noise ratio (PSNR), and structural similarity index (SSIM), as well as time taken (in seconds) for encrypting the input image ($t_\text{enc}$), applying an operation to the encrypted image ($t_\text{apply}$), and decrypting the resulting encrypted image ($t_\text{dec}$), for each image in the test set.
+Tables~\ref{tbl:neg-pal} and~\ref{tbl:neg-dp} show the results obtained from applying image negation, Tables~\ref{tbl:log-pal} and~\ref{tbl:log-dp} from applying logarithm transformation, and Tables~\ref{tbl:pwr-pal} and~\ref{tbl:pwr-dp} from applying power-law transformation.
 
@@
 Both the Paillier and Dasgupta--Pal cryptosystems were able to perform image negation under the encrypted domain without introducing noise in the resulting image.
-In other words, the resulting image from doing image negation on an image on the clear and doing image negation under the encrypted domain are identical, as evidenced by the mean squared errors being exactly equal to zero and the SSIM being exactly equal to one.
+In other words, the resulting image from doing image negation on an image on the clear and doing image negation under the encrypted domain are identical, as evidenced by the mean squared errors being exactly equal to zero, the PSNR being infinite, and the SSIM being exactly equal to one.
 
@@
 
-\begin{table}[!h]
+\begin{table}[h]
 	\caption{Image negation under Paillier}
+	\label{tbl:neg-pal}
     \begin{tabular}{lcccccc}
@@
         Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
-        \texttt{anpage} & 0.000 & inf & 1.00000 & 0.128 & 0.013 & 0.041 \\
-		\texttt{bplyce} & 0.000 & inf & 1.00000 & 0.084 & 0.013 & 0.024 \\
-		\texttt{drbost} & 0.000 & inf & 1.00000 & 0.099 & 0.012 & 0.031 \\
-		\texttt{ksunth} & 0.000 & inf & 1.00000 & 0.109 & 0.012 & 0.048 \\
-		\texttt{martin} & 0.000 & inf & 1.00000 & 0.117 & 0.015 & 0.043 \\
-		\texttt{pmives} & 0.000 & inf & 1.00000 & 0.111 & 0.012 & 0.025 \\
-		\texttt{rnpwil} & 0.000 & inf & 1.00000 & 0.099 & 0.012 & 0.023 \\
-		\texttt{sbains} & 0.000 & inf & 1.00000 & 0.084 & 0.012 & 0.024 \\
-		\texttt{swewin} & 0.000 & inf & 1.00000 & 0.089 & 0.012 & 0.023 \\
-		\texttt{yfhsie} & 0.000 & inf & 1.00000 & 0.081 & 0.012 & 0.029 \\
+        \texttt{anpage} & 0.000 & $\infty$ & 1.00000 & 0.128 & 0.013 & 0.041 \\
+		\texttt{bplyce} & 0.000 & $\infty$ & 1.00000 & 0.084 & 0.013 & 0.024 \\
+		\texttt{drbost} & 0.000 & $\infty$ & 1.00000 & 0.099 & 0.012 & 0.031 \\
+		\texttt{ksunth} & 0.000 & $\infty$ & 1.00000 & 0.109 & 0.012 & 0.048 \\
+		\texttt{martin} & 0.000 & $\infty$ & 1.00000 & 0.117 & 0.015 & 0.043 \\
+		\texttt{pmives} & 0.000 & $\infty$ & 1.00000 & 0.111 & 0.012 & 0.025 \\
+		\texttt{rnpwil} & 0.000 & $\infty$ & 1.00000 & 0.099 & 0.012 & 0.023 \\
+		\texttt{sbains} & 0.000 & $\infty$ & 1.00000 & 0.084 & 0.012 & 0.024 \\
+		\texttt{swewin} & 0.000 & $\infty$ & 1.00000 & 0.089 & 0.012 & 0.023 \\
+		\texttt{yfhsie} & 0.000 & $\infty$ & 1.00000 & 0.081 & 0.012 & 0.029 \\
 		\bottomrule
@@
 \end{table}
-\begin{table}[!h]
+\begin{table}[h]
 	\caption{Image negation under Dasgupta--Pal}
+	\label{tbl:neg-dp}
     \begin{tabular}{lcccccc}
@@
         Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
-		\texttt{anpage} & 0.000 & inf & 1.00000 & 0.221 & 30.217 & 0.239 \\
-		\texttt{bplyce} & 0.000 & inf & 1.00000 & 0.190 & 30.919 & 0.216 \\
-		\texttt{drbost} & 0.000 & inf & 1.00000 & 0.284 & 31.182 & 0.268 \\
-		\texttt{ksunth} & 0.000 & inf & 1.00000 & 0.225 & 32.581 & 0.223 \\
-		\texttt{martin} & 0.000 & inf & 1.00000 & 0.220 & 32.220 & 0.271 \\
-		\texttt{pmives} & 0.000 & inf & 1.00000 & 0.287 & 31.224 & 0.294 \\
-		\texttt{rnpwil} & 0.000 & inf & 1.00000 & 0.285 & 29.478 & 0.284 \\
-		\texttt{sbains} & 0.000 & inf & 1.00000 & 0.186 & 29.784 & 0.362 \\
-		\texttt{swewin} & 0.000 & inf & 1.00000 & 0.243 & 38.407 & 0.220 \\
-		\texttt{yfhsie} & 0.000 & inf & 1.00000 & 0.285 & 29.488 & 0.449 \\		
+		\texttt{anpage} & 0.000 & $\infty$ & 1.00000 & 0.221 & 30.217 & 0.239 \\
+		\texttt{bplyce} & 0.000 & $\infty$ & 1.00000 & 0.190 & 30.919 & 0.216 \\
+		\texttt{drbost} & 0.000 & $\infty$ & 1.00000 & 0.284 & 31.182 & 0.268 \\
+		\texttt{ksunth} & 0.000 & $\infty$ & 1.00000 & 0.225 & 32.581 & 0.223 \\
+		\texttt{martin} & 0.000 & $\infty$ & 1.00000 & 0.220 & 32.220 & 0.271 \\
+		\texttt{pmives} & 0.000 & $\infty$ & 1.00000 & 0.287 & 31.224 & 0.294 \\
+		\texttt{rnpwil} & 0.000 & $\infty$ & 1.00000 & 0.285 & 29.478 & 0.284 \\
+		\texttt{sbains} & 0.000 & $\infty$ & 1.00000 & 0.186 & 29.784 & 0.362 \\
+		\texttt{swewin} & 0.000 & $\infty$ & 1.00000 & 0.243 & 38.407 & 0.220 \\
+		\texttt{yfhsie} & 0.000 & $\infty$ & 1.00000 & 0.285 & 29.488 & 0.449 \\		
 		\bottomrule
@@
 \subsubsection{Logarithm Transformation}
-\begin{table}[!h]
+Unlike image negation, logarithm transformation involves more operations, so the increase in processing time for both cryptosystems are expected.
+Applying the logarithm transformation under Paillier took about 2 seconds per image, while it took about 13.5 minutes each under Dasgupta--Pal.
+
+The logarithm transformation under Dasgupta--Pal turned out to be more accurate than Paillier, whose mean squared errors approach zero and the SSIM values approach one for every image as shown in Table~\ref{tbl:log-dp}.
+Although the results from using Paillier show that it is also accurate enough with the mean squared errors being less than 30 and the SSIM values average to 0.99, Dasgupta--Pal has been able to produce an almost identical result to that of the plaintext domain transformation counterparts.
+This observation is rather unexpected, considering that the implementation used for Paillier is more robust (due to its use of external C/C++ libraries which makes computations faster).
+
+\begin{table}[h]
 	\caption{Logarithm transformation under Paillier}
+	\label{tbl:log-pal}
     \begin{tabular}{lcccccc}
@@
 \end{table}
-\begin{table}[!h]
+\begin{table}[h]
 	\caption{Logarithm transformation under Dasgupta--Pal}
+	\label{tbl:log-dp}
     \begin{tabular}{lcccccc}
@@
 \subsubsection{Power-Law Transformation}
-\begin{table}[!h]
+Unlike in the previous intensity transformations, applying the power-law transformation under both cryptosystems produced less than accurate images.
+The accuracy varies greatly across all the images as in the case of Paillier, with mean squared errors as high as 8270.696 and as low as 616.419, and SSIM scores ranging from 0.43185 to 0.92334.
+As expected, the total processing time now takes about 20 seconds per image since the power-law transformation is more computationally intensive due to its approximation of an infinite series consisting of terms using the logarithm function, which is also approximated using a combination of addition and multiplication operations.
+
+\begin{table}[h]
 	\caption{Power-law transformation under Paillier}
+	\label{tbl:pwr-pal}
     \begin{tabular}{lcccccc}
@@
 \end{table}
+\begin{table}[h]
+	\caption{Power-law transformation under Dasgupta--Pal}
+	\label{tbl:pwr-dp}
+    \begin{tabular}{lcccccc}
+        \toprule
+        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
+		% \texttt{anpage} & 25115.891 & 4.131 & 0.00000 & 0.016 & 741.872 & 0.031 \\ 10x10
+		\texttt{anpage} & 25008.723 & 4.150 & 0.00000 & 0.376 & 9700.926 & 1.269 \\
+		% \texttt{bplyce} & 22777.187 & 4.556 & 0.00000 & 0.017 & 730.873 & 0.003 \\ 10x10
+		\texttt{bplyce} & 22700.522 & 4.570 & 0.00000 & 0.230 & 9196.609 & 0.043 \\
+		% \texttt{drbost} & 18899.906 & 5.366 & 0.00000 & 0.014 & 733.409 & 0.003 \\
+		\texttt{drbost} & 18902.214 & 5.366 & 0.00000 & 0.064 & 2261.407 & 0.110 \\ % 20x18
+		\texttt{ksunth} & 12585.729 & 7.132 & 0.00000 & 0.044 & 2259.010 & 0.011 \\ % 20x18
+		\texttt{martin} & 17012.423 & 5.823 & 0.00000 & 0.066 & 2440.351 & 0.011 \\
+		\texttt{pmives} & 31124.615 & 3.200 & 0.00000 & 0.072 & 2492.149 & 0.012 \\
+		\texttt{rnpwil} & 22982.917 & 4.517 & 0.00000 & 0.076 & 2321.928 & 0.008 \\
+		\texttt{sbains} & 13469.155 & 6.837 & 0.00000 & 0.044 & 2233.818 & 0.008 \\
+		\texttt{swewin} & 37453.834 & 2.396 & 0.00000 & 0.049 & 2203.045 & 0.008 \\
+		\texttt{yfhsie} & 23037.762 & 4.506 & 0.00000 & 0.045 & 2210.393 & 0.008 \\
+		\bottomrule
+        \end{tabular}
+\end{table}
 
 \section{Conclusion}
+In this paper, we have assessed the feasibility and practicality of various homomorphic cryptosystems with regard to secure processing and manipulation of facial image data through creation of a software library that facilitates image processing operations within the encrypted domain, as well as our own implementation of some homomorphic cryptosystems like Dasgupta--Pal for which existing third-party library dedicated for this purpose is not yet available.
+
+This paper also proposes a correction to the Dasgupta--Pal cryptosystem which is further explained in Appendix~\ref{chap:correction}.
+
+Even though an operation in a partially homomorphic cryptosystem is not theoretically possible, like multiplication of two ciphertexts under Paillier, it has been shown that such operations are indeed possible in a two-party system.
+Protocols for secure multiplication and exponentiation have been proposed and also applied to more complex image operations such as facial recognition.
+Thus, a partially homomorphic cryptosystem can be modified to admit more image processing operations by assuming a two-party system.
+
+Preliminary results have shown that both Paillier and Dasgupta--Pal apply image negation accurately and efficiently, as evidenced by the perfect zero MSE and infinite PSNR.
+For the logarithm transformation, Paillier was faster and accurate enough (with $\text{MSE} \le 30$ and $\text{SSIM} \approx 0.99$), but Dasgupta--Pal was slower but more accurate (with $\text{MSE} \le 0.01$ and $\text{SSIM} \approx 0.99999$) which was rather unexpected.
+However both Paillier and Dasgupta--Pal fail to produce accurate results in applying the power-law transformation.
+Based from these results, the Paillier cryptosystem is consistent enough to produce reasonable to accurate results.
+
+A wrapper library has been made which implements the various functions and methods of the cryptosystems into a single interface.
+This allowed us to express various image operations with a unified syntax, thus facilitating easier testing.
 
 \subsection{Ongoing and Future Work}
+Testing intensity transformations under the BGV cryptosystem will be started once the Pyfhel library is deemed stable enough to use, or another Python library that implements BGV becomes available. 
+One of the authors has already informed the developers of the Pyfhel library about a bug involving exponentiation of two real numbers.
+
+Efforts are ongoing with regard to the facial recognition tests.
+Our own implementation of the privacy-preserving  eigenfaces by Erkin, et al.
+does not yet use the DGK cryptosystem for secure integer comparison in the match finding step, thus we are working on implementing DGK from scratch.
+
+Another promising image operation to consider is \textit{facial detection} under a homomorphic cryptosystem.
+Work has been started in order to assess the feasibility of using Haar cascades in a privacy-preserving manner.
+
+Future work would involve improving and optimizing our implementation of the Dasgupta--Pal cryptosystem so that it performs faster.
+A suggestion would be to port the existing implementation to C/C++ and then create a Python library that acts as a wrapper to the C/C++ methods.
+For future studies, an implementation of a client-server framework or system dealing with secure image processing can be considered.

### 2019-01-11 paper/PCSC2019-sigconf.tex
Final paper done

@@
 
-\author{Me 1}
+\author{Aldrich Ellis C. Asuncion}
 \affiliation{%
-  \institution{Institute for Clarity in Documentation}
-  \streetaddress{P.O. Box 1212}
-  \city{Dublin}
-  \state{Ohio}
-  \postcode{43017-6221}
+  \institution{Ateneo de Manila University}
+  \streetaddress{Katipunan Avenue, Loyola Heights}
+  \city{Quezon City}
+  \country{Philippines}
+  \postcode{1108}
 }
-\email{webmaster@marysville-ohio.com}
+\email{aldrich.asuncion@obf.ateneo.edu}
 
-\author{Me 2}
+\author{Brian Christopher T. Guadalupe}
 \affiliation{%
-  \institution{The Th{\o}rv{\"a}ld Group}
-  \streetaddress{1 Th{\o}rv{\"a}ld Circle}
-  \city{Hekla}
-  \country{Iceland}}
-\email{larst@affiliation.org}
+  \institution{Ateneo de Manila University}
+  \streetaddress{Katipunan Avenue, Loyola Heights}
+  \city{Quezon City}
+  \country{Philippines}
+  \postcode{1108}
+}
+\email{brian.guadalupe@obf.ateneo.edu}
 
@@
 \renewcommand{\shorttitle}{Impl. and Analysis of Homomorphic Facial Image Encryption and Manipulation}
-% \renewcommand{\shortauthors}{B. Trovato et al.}
+\renewcommand{\shortauthors}{A. Asuncion and B. Guadalupe}
 
@@
 
-\keywords{homomorphic encryption, image operations, facial recognition, numerical approximations}
+\keywords{cryptography, homomorphic encryption, data privacy, image processing, intensity transformation, facial recognition, numerical approximations}
 
@@
 \begin{acks}
-  The authors would like to thank Dr. Yuhua Li for providing the
-  MATLAB code of the \textit{BEPS} method. Testing testing.
-
-  The authors would also like to thank the anonymous referees for
-  their valuable comments and helpful suggestions. The work is
-  supported by the \grantsponsor{GS501100001809}{National Natural
-    Science Foundation of
-    China}{http://dx.doi.org/10.13039/501100001809} under Grant
-  No.:~\grantnum{GS501100001809}{61273304}
-  and~\grantnum[http://www.nnsf.cn/youngscientists]{GS501100001809}{Young
-    Scientists' Support Program}.
-
+We would like to thank our adviser Dr.
+William Emmanuel S.
+Yu for his guidance and constant feedback, and our panelists Dr.
+Andrei D.
+Coronel and Dr.
+Mari-jo P.
+Ruiz for lending their expertise and for giving their invaluable comments and insights.
+Due acknowlegement is also given to the University of Essex for making the \texttt{faces94} dataset publicly available for research purposes.
 \end{acks}

### 2019-01-11 paper/appendix.tex
Final paper done

@@
 \end{description}
+
 The homomorphic operations are then defined as
@@
 \end{description}
+
 After repeated operations on ciphertexts, the resulting ciphertext can grow in magnitude.
@@
 \end{align}
+
 Since $S_k$ is odd, the corresponding operation in the plaintext space is
@@
 \end{align*}
+
 However, evaluating Equation \ref{eq:cornercase_ciphertext} yields:
@@
 
-This integral can be approximated using the five-point Gauss-Legendre quadrature rule \cite{kythe_quadrature_2002}.
+This integral can be approximated using the five-point Gauss--Legendre quadrature rule \cite{kythe_quadrature_2002}.
 We first convert the integral to an integral over the interval $[-1,1]$ using the following transformation:
@@
 
-Applying the five-point Gauss-Legendre quadrature rule with $\alpha = 1/20$ using SageMath 8.3, we arrive at the approximation:
+Applying the five-point Gauss--Legendre quadrature rule with $\alpha = 1/20$ using SageMath 8.3, we arrive at the approximation:
 \begin{align}\label{eq:scaledquadrature}

### 2019-01-11 paper/paper-conf.tex
Final paper done

@@
 		\xintFor #1 in {anpage, bplyce, drbost, ksunth, martin, pmives, rnpwil, sbains, swewin, yfhsie} \do {%
-		\texttt{#1} & \includegraphics[width=1.75cm]{out_faces/dp_negate_#1_original.png} & \includegraphics[width=1.75cm]{out_faces/dp_negate_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/dp_negate_#1_decrypted.png} & \includegraphics[width=1.75cm]{out_faces/dp_logtransform_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/dp_logtransform_#1_decrypted.png} & \includegraphics[width=1.75cm]{out_faces/paillier_pwrtransform_#1_reference.png} &  \\ }%
+		\texttt{#1} & \includegraphics[width=1.75cm]{out_faces/dp_negate_#1_original.png} & \includegraphics[width=1.75cm]{out_faces/dp_negate_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/dp_negate_#1_decrypted.png} & \includegraphics[width=1.75cm]{out_faces/dp_logtransform_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/dp_logtransform_#1_decrypted.png} & \includegraphics[width=1.75cm]{out_faces/paillier_pwrtransform_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/dp_pwrtransform_#1_decrypted.png} \\ }%
 		\bottomrule         
@@
 \subsubsection{Power-Law Transformation}
-Unlike in the previous intensity transformations, applying the power-law transformation under both cryptosystems produced less than accurate images.
-The accuracy varies greatly across all the images as in the case of Paillier, with mean squared errors as high as 8270.696 and as low as 616.419, and SSIM scores ranging from 0.43185 to 0.92334.
-As expected, the total processing time now takes about 20 seconds per image since the power-law transformation is more computationally intensive due to its approximation of an infinite series consisting of terms using the logarithm function, which is also approximated using a combination of addition and multiplication operations.
+Applying the power-law transformation under both cryptosystems produced less than accurate images.
+The accuracy varies greatly across all the images as in the case of Paillier, with mean squared errors as high as 8270.696 and as low as 616.419, and SSIM scores ranging from 0.43185 to 0.92334, as seen in Table~\ref{tbl:pwr-pal}.
+As expected, the total processing time now takes about 15 to 20 seconds per image since the power-law transformation is more computationally intensive due to its approximation of an infinite series consisting of terms using the logarithm function, which is also approximated using a combination of addition and multiplication operations.
 
@@
 \end{table}
+
+When Dasgupta--Pal was used in the power-law transformation, it completely failed to produce a discernible image and only resulted in a blank image.
+The mean squared errors for this case is an order of magnitude higher than the results from using Paillier.
+Furthermore, doing a power-law transformation under Dasgupta--Pal is not only impractical in terms of accuracy, but also it is impractical in terms of time efficiency because it took about 2 hours and 40 minutes on average to process each image.
+
 \begin{table}[h]
@@
         Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
+		\texttt{anpage} & 25008.723 & 4.150 & 0.00000 & 0.376 & 9700.926 & 1.269 \\
+		\texttt{bplyce} & 22700.522 & 4.570 & 0.00000 & 0.230 & 9196.609 & 0.043 \\
 		% \texttt{anpage} & 25115.891 & 4.131 & 0.00000 & 0.016 & 741.872 & 0.031 \\ 10x10
-		\texttt{anpage} & 25008.723 & 4.150 & 0.00000 & 0.376 & 9700.926 & 1.269 \\
 		% \texttt{bplyce} & 22777.187 & 4.556 & 0.00000 & 0.017 & 730.873 & 0.003 \\ 10x10
-		\texttt{bplyce} & 22700.522 & 4.570 & 0.00000 & 0.230 & 9196.609 & 0.043 \\
 		% \texttt{drbost} & 18899.906 & 5.366 & 0.00000 & 0.014 & 733.409 & 0.003 \\
-		\texttt{drbost} & 18902.214 & 5.366 & 0.00000 & 0.064 & 2261.407 & 0.110 \\ % 20x18
-		\texttt{ksunth} & 12585.729 & 7.132 & 0.00000 & 0.044 & 2259.010 & 0.011 \\ % 20x18
-		\texttt{martin} & 17012.423 & 5.823 & 0.00000 & 0.066 & 2440.351 & 0.011 \\
-		\texttt{pmives} & 31124.615 & 3.200 & 0.00000 & 0.072 & 2492.149 & 0.012 \\
-		\texttt{rnpwil} & 22982.917 & 4.517 & 0.00000 & 0.076 & 2321.928 & 0.008 \\
-		\texttt{sbains} & 13469.155 & 6.837 & 0.00000 & 0.044 & 2233.818 & 0.008 \\
-		\texttt{swewin} & 37453.834 & 2.396 & 0.00000 & 0.049 & 2203.045 & 0.008 \\
-		\texttt{yfhsie} & 23037.762 & 4.506 & 0.00000 & 0.045 & 2210.393 & 0.008 \\
+		\texttt{drbost} & 18902.214 & 5.366 & 0.00000 & 0.277 & 9261.407 & 0.150 \\
+		\texttt{ksunth} & 12585.729 & 7.132 & 0.00000 & 0.257 & 9259.010 & 0.051 \\
+		\texttt{martin} & 17012.423 & 5.823 & 0.00000 & 0.279 & 9440.351 & 0.051 \\
+		\texttt{pmives} & 31124.615 & 3.200 & 0.00000 & 0.285 & 9492.149 & 0.052 \\
+		\texttt{rnpwil} & 22982.917 & 4.517 & 0.00000 & 0.289 & 9321.928 & 0.048 \\
+		\texttt{sbains} & 13469.155 & 6.837 & 0.00000 & 0.257 & 9233.818 & 0.048 \\
+		\texttt{swewin} & 37453.834 & 2.396 & 0.00000 & 0.262 & 9203.045 & 0.048 \\
+		\texttt{yfhsie} & 23037.762 & 4.506 & 0.00000 & 0.258 & 9210.393 & 0.048 \\
+		% \texttt{drbost} & 18902.214 & 5.366 & 0.00000 & 0.064 & 2261.407 & 0.110 \\ % 20x18
+		% \texttt{ksunth} & 12585.729 & 7.132 & 0.00000 & 0.044 & 2259.010 & 0.011 \\ % 20x18
+		% \texttt{martin} & 17012.423 & 5.823 & 0.00000 & 0.066 & 2440.351 & 0.011 \\
+		% \texttt{pmives} & 31124.615 & 3.200 & 0.00000 & 0.072 & 2492.149 & 0.012 \\
+		% \texttt{rnpwil} & 22982.917 & 4.517 & 0.00000 & 0.076 & 2321.928 & 0.008 \\
+		% \texttt{sbains} & 13469.155 & 6.837 & 0.00000 & 0.044 & 2233.818 & 0.008 \\
+		% \texttt{swewin} & 37453.834 & 2.396 & 0.00000 & 0.049 & 2203.045 & 0.008 \\
+		% \texttt{yfhsie} & 23037.762 & 4.506 & 0.00000 & 0.045 & 2210.393 & 0.008 \\
 		\bottomrule
@@
 \section{Conclusion}
-In this paper, we have assessed the feasibility and practicality of various homomorphic cryptosystems with regard to secure processing and manipulation of facial image data through creation of a software library that facilitates image processing operations within the encrypted domain, as well as our own implementation of some homomorphic cryptosystems like Dasgupta--Pal for which existing third-party library dedicated for this purpose is not yet available.
+In this paper, we have assessed the feasibility and practicality of various homomorphic cryptosystems with regard to secure processing and manipulation of facial image data through creation of a software library that facilitates image processing operations within the encrypted domain, as well as our own implementation of some homomorphic cryptosystems like Dasgupta--Pal for which existing third-party libraries dedicated for this purpose are not yet available.
 
-This paper also proposes a correction to the Dasgupta--Pal cryptosystem which is further explained in Appendix~\ref{chap:correction}.
+% This paper also proposes a correction to the Dasgupta--Pal cryptosystem which is further explained in Appendix~\ref{chap:correction}.
 
@@
 For the logarithm transformation, Paillier was faster and accurate enough (with $\text{MSE} \le 30$ and $\text{SSIM} \approx 0.99$), but Dasgupta--Pal was slower but more accurate (with $\text{MSE} \le 0.01$ and $\text{SSIM} \approx 0.99999$) which was rather unexpected.
-However both Paillier and Dasgupta--Pal fail to produce accurate results in applying the power-law transformation.
+However both Paillier and Dasgupta--Pal fail to produce accurate results in applying the power-law transformation, with the latter completely failing to produce discernible results.
 Based from these results, the Paillier cryptosystem is consistent enough to produce reasonable to accurate results.
@@
 Testing intensity transformations under the BGV cryptosystem will be started once the Pyfhel library is deemed stable enough to use, or another Python library that implements BGV becomes available. 
-One of the authors has already informed the developers of the Pyfhel library about a bug involving exponentiation of two real numbers.
+One of the authors of this paper has already informed the developers of the Pyfhel library about a bug involving exponentiation of two real numbers.
 

### 2019-01-13 paper/PCSC2019-sigconf.tex
Recreated graphs with pgfplots (and more)

@@
-\documentclass[sigconf]{acmart}
+% \documentclass[sigconf]{acmart}
+\documentclass{sig-alternate-05-2015}
+\usepackage{natbib}
+% \usepackage[LGR,T1]{fontenc}‎
 \usepackage[utf8]{inputenc}
+\usepackage[hidelinks]{hyperref}
+\usepackage{newtxtext}
+\usepackage{zi4}
+\usepackage{newtxmath}
 \usepackage{multicol}
@@
 \usepackage{booktabs} % For formal tables
+\usepackage{pgf, tikz}
+\usepackage{pgfplots}
+\usetikzlibrary{calc}
 
-\setcopyright{rightsretained}
+\setcopyright{acmlicensed}
+\newtheorem{theorem}{Theorem}
 
 % DOI
-\acmDOI{}
+% \acmDOI{}
 
 % ISBN
-\acmISBN{}
+% \acmISBN{}
 
 %Conference
-\acmConference[PCSC2019]{Philippine Computing Science Congress}{March 2019}{City of Manila, Philippines}
-\acmYear{2019}
-\copyrightyear{2019}
+% \acmConference[PCSC2019]{Philippine Computing Science Congress}{March 2019}{City of Manila, Philippines}
+% \acmYear{2019}
+\CopyrightYear{2019}
 
-\acmArticle{}
-\acmPrice{}
+% \acmArticle{}
+% \acmPrice{}
 
@@
 %\acmBooktitle{Transactions of the ACM Woodstock conference}
-\editor{}
-\editor{}
-\editor{}
+% \editor{}
+% \editor{}
+% \editor{}
 
 \begin{document}
+\setcitestyle{numbers,square,comma,sort}
 \title{Implementation and Analysis of Homomorphic Facial Image Encryption and Manipulation}
 
-\author{Aldrich Ellis C. Asuncion}
-\affiliation{%
-  \institution{Ateneo de Manila University}
-  \streetaddress{Katipunan Avenue, Loyola Heights}
-  \city{Quezon City}
-  \country{Philippines}
-  \postcode{1108}
+% \author{Aldrich Ellis C. Asuncion}
+% \affiliation{%
+%   \institution{Ateneo de Manila University}
+%   \streetaddress{Katipunan Avenue, Loyola Heights}
+%   \city{Quezon City}
+%   \country{Philippines}
+%   \postcode{1108}
+% }
+% \email{aldrich.asuncion@obf.ateneo.edu}
+
+% \author{Brian Christopher T. Guadalupe}
+% \affiliation{%
+%   \institution{Ateneo de Manila University}
+%   \streetaddress{Katipunan Avenue, Loyola Heights}
+%   \city{Quezon City}
+%   \country{Philippines}
+%   \postcode{1108}
+% }
+% \email{brian.guadalupe@obf.ateneo.edu}
+
+\numberofauthors{2}
+\author{
+\alignauthor Aldrich Ellis C. Asuncion\\
+\affaddr{Ateneo de Manila University}\\
+\affaddr{Katipunan Ave., Loyola Heights}\\
+\affaddr{Quezon City, Philippines 1108}\\
+\email{aldrich.asuncion@obf.ateneo.edu}
+\alignauthor Brian Christopher T. Guadalupe\\
+\affaddr{Ateneo de Manila University}\\
+\affaddr{Katipunan Ave., Loyola Heights}\\
+\affaddr{Quezon City, Philippines 1108}\\
+\email{brian.guadalupe@obf.ateneo.edu}
 }
-\email{aldrich.asuncion@obf.ateneo.edu}
 
-\author{Brian Christopher T. Guadalupe}
-\affiliation{%
-  \institution{Ateneo de Manila University}
-  \streetaddress{Katipunan Avenue, Loyola Heights}
-  \city{Quezon City}
-  \country{Philippines}
-  \postcode{1108}
-}
-\email{brian.guadalupe@obf.ateneo.edu}
-
+\maketitle
 % The default list of authors is too long for headers.
-\renewcommand{\shorttitle}{Impl. and Analysis of Homomorphic Facial Image Encryption and Manipulation}
-\renewcommand{\shortauthors}{A. Asuncion and B. Guadalupe}
+% \renewcommand{\shorttitle}{Impl. and Analysis of Homomorphic Facial Image Encryption and Manipulation}
+% \renewcommand{\shortauthors}{A. Asuncion and B. Guadalupe}
 
@@
 Furthermore, as an extension to previous research, we attempt to support non-linear image processing operations.
-Preliminary results have shown that the Pailler and Dasgupta--Pal cryptosystems are comparable in accuracy and may be used to approximate a logarithm transformation, but the Dasgupta--Pal cryptosystem is significantly slower.
+Preliminary results have shown that the Paillier and Dasgupta--Pal cryptosystems are comparable in accuracy and may be used to approximate a logarithm transformation, but the Dasgupta--Pal cryptosystem is significantly slower.
 \end{abstract}
@@
   <concept>
+  <concept_id>10002978.10003029.10011150</concept_id>
+  <concept_desc>Security and privacy~Privacy protections</concept_desc>
+  <concept_significance>300</concept_significance>
+  </concept>
+  <concept>
   <concept_id>10010147.10010371.10010382.10010383</concept_id>
@@
   <concept_significance>500</concept_significance>
+  </concept>
+  <concept>
+  <concept_id>10002950.10003714.10003736.10003737</concept_id>
+  <concept_desc>Mathematics of computing~Approximation</concept_desc>
+  <concept_significance>300</concept_significance>
   </concept>
@@
 \ccsdesc[300]{Security and privacy~Management and querying of encrypted data}
+\ccsdesc[300]{Security and privacy~Privacy protections}
 \ccsdesc[500]{Computing methodologies~Image processing}
+\ccsdesc[300]{Mathematics of computing~Approximation}
 \ccsdesc[100]{Mathematics of computing~Quadrature}
 
-\keywords{cryptography, homomorphic encryption, data privacy, image processing, intensity transformation, facial recognition, numerical approximations}
+\printccsdesc
+\keywords{cryptography; homomorphic encryption; data privacy; image processing; intensity transformation; facial recognition; numerical approximations}
 
-\maketitle
+% \maketitle
 
@@
 
-\appendix
-\input{appendix}
-
-\begin{acks}
+% \begin{acks}
+\section{Acknowledgments}
 We would like to thank our adviser Dr.
@@
 Due acknowlegement is also given to the University of Essex for making the \texttt{faces94} dataset publicly available for research purposes.
-\end{acks}
+% \end{acks}
 
 \bibliographystyle{ACM-Reference-Format}
+% \citestyle{acmnumeric}
+% \bibliographystyle{acm}
 \bibliography{thesis_refs}
+\balancecolumns
+
+\appendix
+\input{appendix}
+\balancecolumns
 

### 2019-01-13 paper/paper-conf.tex
Recreated graphs with pgfplots (and more)

@@
 $y(x)$ is a polynomial of degree $n$ such that $m_p(x) \equiv y(x) \bmod S_k$ and $d(x)$ is a randomly chosen polynomial of degree $n$.
-This encrypts each coefficient of of $m_p(x)$ by adding some multiple of $S_k$ to it.
+This encrypts each coefficient of $m_p(x)$ by adding some multiple of $S_k$ to it.
 Through this process, each bit of the message is encrypted separately.
@@
 Similar to the logarithm transformation, we must provide an approximation for $x^\gamma$.
-We have derived an infinite series in Appendix \ref{sec:logapproximation}.
+We have derived an infinite series in Appendix~\ref{sec:approx-pwr}.
 \begin{align}
@@
 \begin{table*}
+	\centering
 	\caption{Comparison of intensity transformations under Paillier}
@@
 \begin{table*}
+	\centering
 	\caption{Comparison of intensity transformations under Dasgupta--Pal}
@@
 
-Table~\ref{tbl:it-pal} shows the images obtained from the intensity transformation tests under the Paillier cryptosystem, while Table~\ref{tbl:it-pal} shows the resulting images from the same tests under the Dasgupta--Pal cryptosystem.
+Table~\ref{tbl:it-pal} shows the images obtained from the intensity transformation tests under the Paillier cryptosystem, while Table~\ref{tbl:it-dp} shows the resulting images from the same tests under the Dasgupta--Pal cryptosystem.
 Shown for each image is the original unecrypted image, and for each intensity transformation the \textit{plaintext domain transformation} (PDT) is given which is the resulting image after applying the transformation to the unencrypted image and the \textit{ciphertext domain transformation} (CDT) is the decrypted image of the processed encrypted image.
@@
 \begin{table}[h]
+	\centering
 	\caption{Image negation under Paillier}
@@
 \begin{table}[h]
+	\centering
 	\caption{Image negation under Dasgupta--Pal}
@@
 \begin{table}[h]
+	\centering
 	\caption{Logarithm transformation under Paillier}
@@
 \begin{table}[h]
+	\centering
 	\caption{Power-law transformation under Paillier}
@@
 \begin{table}[h]
+	\centering
 	\caption{Power-law transformation under Dasgupta--Pal}
@@
         Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
-		\texttt{anpage} & 25008.723 & 4.150 & 0.00000 & 0.376 & 9700.926 & 1.269 \\
-		\texttt{bplyce} & 22700.522 & 4.570 & 0.00000 & 0.230 & 9196.609 & 0.043 \\
+		\texttt{anpage} & 25008.723 & 4.150 & 0.000 & 0.376 & 9700.926 & 1.269 \\
+		\texttt{bplyce} & 22700.522 & 4.570 & 0.000 & 0.230 & 9196.609 & 0.043 \\
 		% \texttt{anpage} & 25115.891 & 4.131 & 0.00000 & 0.016 & 741.872 & 0.031 \\ 10x10
@@
 		% \texttt{drbost} & 18899.906 & 5.366 & 0.00000 & 0.014 & 733.409 & 0.003 \\
-		\texttt{drbost} & 18902.214 & 5.366 & 0.00000 & 0.277 & 9261.407 & 0.150 \\
-		\texttt{ksunth} & 12585.729 & 7.132 & 0.00000 & 0.257 & 9259.010 & 0.051 \\
-		\texttt{martin} & 17012.423 & 5.823 & 0.00000 & 0.279 & 9440.351 & 0.051 \\
-		\texttt{pmives} & 31124.615 & 3.200 & 0.00000 & 0.285 & 9492.149 & 0.052 \\
-		\texttt{rnpwil} & 22982.917 & 4.517 & 0.00000 & 0.289 & 9321.928 & 0.048 \\
-		\texttt{sbains} & 13469.155 & 6.837 & 0.00000 & 0.257 & 9233.818 & 0.048 \\
-		\texttt{swewin} & 37453.834 & 2.396 & 0.00000 & 0.262 & 9203.045 & 0.048 \\
-		\texttt{yfhsie} & 23037.762 & 4.506 & 0.00000 & 0.258 & 9210.393 & 0.048 \\
+		\texttt{drbost} & 18902.214 & 5.366 & 0.000 & 0.277 & 9261.407 & 0.150 \\
+		\texttt{ksunth} & 12585.729 & 7.132 & 0.000 & 0.257 & 9259.010 & 0.051 \\
+		\texttt{martin} & 17012.423 & 5.823 & 0.000 & 0.279 & 9440.351 & 0.051 \\
+		\texttt{pmives} & 31124.615 & 3.200 & 0.000 & 0.285 & 9492.149 & 0.052 \\
+		\texttt{rnpwil} & 22982.917 & 4.517 & 0.000 & 0.289 & 9321.928 & 0.048 \\
+		\texttt{sbains} & 13469.155 & 6.837 & 0.000 & 0.257 & 9233.818 & 0.048 \\
+		\texttt{swewin} & 37453.834 & 2.396 & 0.000 & 0.262 & 9203.045 & 0.048 \\
+		\texttt{yfhsie} & 23037.762 & 4.506 & 0.000 & 0.258 & 9210.393 & 0.048 \\
 		% \texttt{drbost} & 18902.214 & 5.366 & 0.00000 & 0.064 & 2261.407 & 0.110 \\ % 20x18

### 2019-01-15 paper/paper-conf.tex
New branch for paper 2

--- 2019-01-10 paper/paper-conf.tex
@@
 \section{Introduction}
-\subsection{Context of the Study}
-Digital data privacy and security is a growing concern in various fields, such as cloud computing~\cite{potey_homomorphic_2016}, health information systems~\cite{kester_cryptographic_2015}, and video surveillance~\cite{upmanyu_efficient_2009}.
-To meet these needs, various cryptosystems have been developed.
-A cryptosystem is a system which operates on plaintexts, ciphertexts and keys using an encryption algorithm, which maps a plaintext to a ciphertext, together with a decryption algorithm, which maps a ciphertext to a plaintext, given an appropriate key~\cite{bauer_cryptosystem_2005}.
-The encryption and decryption algorithms are chosen such that the plaintext cannot easily be recovered from the ciphertext without knowledge of the key.
-This allows data to be securely transmitted over an insecure channel.
-Much research has been done on the development and application of various cryptosystems.
+\newcommand*\diff{\mathop{}\!\mathrm{d}}
 
-One particular application of cryptography is image encryption.
-While cryptosystems used to encrypt digital data in general, such as the Advanced Encryption Standard (AES) or elliptic curve cryptography, can also be used to encrypt images~\cite{jain_image_2016, singh_image_2015} other algorithms created specifically for image encryption have also been developed~\cite{murugan_survey_2018}.
+Transcendental functions such as the exponential and logarithmic functions are usually implemented in computer hardware and software libraries using minimax polynomials, which are determined numerically using the Remez algorithm \cite{harrison_computation_1999}.
+However, the Remez algorithm relies on iteratively refining the polynomial coefficients, which requires knowledge of the argument passed to the transcendental function.
 
-In a homomorphic cryptosystem, operations such as addition and multiplication can be performed on encrypted data.
-These operations are then preserved when the data is decrypted.
-In this manner, data is manipulated without compromising data privacy, as the encrypted data being operated on remains secure~\cite{fontaine_survey_2007, sen_homomorphic_2013}.
-While numerous homomorphic cryptosystems exist for use with digital data in general, in the area of homomorphic image encryption, there is additional interest in being able to perform image manipulation operations on the encrypted data such as image adjustment, filtering, and morphological/feature extraction operations~\cite{ziad_cryptoimg:_2016, gonzalez_digital_2008}.
-More advanced operations have also been implemented using homomorphic cryptosystems, such as facial recognition \cite{hutchison_privacy-preserving_2009} and neural networks \cite{hesamifard_cryptodl:_2017}.
-This study in particular focuses on facial recognition.
+We cannot directly apply this approach in privacy-preserving image processing as we do not have knowledge of the exact value of the function arguments.
+In order to calculate a function under a  homomorphic cryptosystem, it is necessary to express the function in terms of the homomorphic operations.
+In this section, we discuss approximations for the logarithm ($\log(1+x)$) and power ($x^r$) functions using only addition, subtraction, multiplication, and division operations.
 
-\subsection{Research Questions}
-By implementing homomorphic cryptosystems and creating a library so they can be easily used, we aim to address our main research question: What is the best method for facial image data to be encrypted and manipulated for practical applications?
+\section{Approximation for $\log(1+x)$}
+\label{sec:logapproximation}
+We approximate the function $f(x)=\log(1+x)$ using a similar method to that described in
+\cite{khattri_new_2009}.
+We let $x = 1/n$ and consider the integral
+\begin{equation}
+	\label{eq:log_integral}
+  	\int_{n}^{n+1}{\frac{1}{x}\diff x}=\log{\left(1+\frac{1}{n}\right)}.
+\end{equation}
 
-More specifically, our research will address the following sub-questions:
-\begin{enumerate}
-	\item Which homomorphic cryptosystems admit more image processing operations? How can existing homomorphic cryptosystems be modified to admit more image processing operations?
-	\item Which homomorphic cryptosystems are the most time-efficient and the most accurate in applying image processing operations?
-	\item Which homomorphic cryptosystems best preserve image quality in applying image processing operations?
-\end{enumerate}
+This integral can be approximated using the five-point Gauss--Legendre quadrature rule \cite{kythe_quadrature_2002}.
+We first convert the integral to an integral over the interval $[-1,1]$ using the following transformation:
+\begin{align*}
+	\int_a^b{f(x)\diff x}
+	&= \frac{b-a}{2}\int_{-1}^{1}{f\left(\frac{b-a}{2}x+\frac{a+b}{2}\right)\diff x}.
+\end{align*}
+Then, we approximate the integral using the following summation:
+\begin{align*}
+  \int_{-1}^{1}{f(x)\diff x} &= \sum_{i=1}^{5}{w_if(x_i)},
+\end{align*}
+where
+\begin{multicols}{2}
+	\noindent
+	\begin{align*}
+		w_1 &= 0\\
+		w_2 &= \frac{1}{21}\sqrt{245-14\sqrt{70}}\\
+		w_3 &= -\frac{1}{21}\sqrt{245-14\sqrt{70}}\\
+		w_4 &= \frac{1}{21}\sqrt{245+14\sqrt{70}}\\
+		w_5 &= -\frac{1}{21}\sqrt{245+14\sqrt{70}}
+	\end{align*}
+	% \columnbreak
+	\begin{align*}
+		x_1 &= \frac{128}{225}\\
+		x_2 &= \frac{1}{900}\left( 322 + 13\sqrt{70}\right)\\
+		x_3 &= \frac{1}{900}\left( 322 + 13\sqrt{70}\right)\\
+		x_4 &= \frac{1}{900}\left( 322 - 13\sqrt{70}\right)\\
+		x_5 &= \frac{1}{900}\left( 322 - 13\sqrt{70}\right)
+	\end{align*}
+\end{multicols}
 
-\subsection{Research Objectives}
-Previous attempts in the literature to provide image processing tasks such as image manipulation \cite{ziad_cryptoimg:_2016} and  facial recognition \cite{hutchison_privacy-preserving_2009} have primarily used the Paillier and  Damg{\aa}rd--Geisler--Kr{\o}igaard (DGK) cryptosystems to perform linear operations on encrypted data.
-In this study, we extend this research to provide an objective comparison of various homomorphic cryptosystems currently in the literature in performing non-linear operations, as opposed to just linear operations, and facial detection, as opposed to just facial recognition.
+Applying this procedure to the integral in Equation~\ref{eq:log_integral} using SageMath 8.3 yields the following approximation:
+\begin{equation}\label{eq:standardquadrature}
+  \log(1+x) \approx
+  \frac{137x^5 + 2310x^4 + 9870x^3 + 15120x^2 + 7560x}
+  {30x^5 + 900x^4 + 6300x^3 + 16800x^2 + 18900x + 7560}.
+\end{equation}
 
-Our main research objective is to assess the practicality of various homomorphic cryptosystems with regard to image processing on faces.
-Homomorphic cryptosystems are known to be slower in terms of encryption, operation, and decryption time~\cite{sen_homomorphic_2013}.
-Furthermore, the operations on encrypted data supported by homomorphic cryptosystems are limited, and some schemes require preprocessing to be performed on images, limiting the range of operations which can be performed efficiently~\cite{li_elliptic_2012}.
+% \pgfplotsset{
+% 	every axis legend/.append style={anchor=south east},
+% }
 
-In summary, in this study, we wish to
-\begin{enumerate}
-    \item Implement common image processing operations using known homomorphic encryption schemes, then determine which schemes admit more image processing operations and extend known cryptosystems to support more operations, if possible;
-    \item Compare the time efficiency and accuracy of common image processing operations under known homomorphic encryption schemes, and of common image processing operations without using homomorphic encryption;
-    \item Create a library to allow for convenient use and comparison of these homomorphic encryption schemes for image processing and facial recognition.
-\end{enumerate}
+While the closed form approximation in Equation~\ref{eq:standardquadrature} is accurate for values of $x$ near zero, it diverges from $\log{(1+x)}$ significantly for large values of $x$, as shown in Figure~\ref{fig:standardquadrature}.
+% \begin{figure}[!ht]
+%     \centering
+%     \includegraphics[width=.8\linewidth]{figures/StandardQuadrature.png}
+%     \caption{Graph of $\log{(1+x)}$ and the approximation in equation \ref{eq:standardquadrature}}
+%     \label{fig:standardquadrature}
+% \end{figure}
+\begin{figure}[!ht]
+    \centering
+	\begin{tikzpicture}
+		\begin{axis}[
+			% height=6cm, width=9cm,
+			xmin=0, xmax=300,
+			ymin=0, ymax=5.5, ytick={0,...,6},
+			xlabel={$x$}, ylabel={$y$},
+			grid=major,
+			legend pos=south east,
+			legend cell align=left,
+		]
+		\addplot[very thick, domain=0:300, samples=100]{1/30*(137*x^5 + 2310*x^4 + 9870*x^3 + 15120*x^2 + 7560*x)/(x^5 + 30*x^4 + 210*x^3 + 560*x^2 + 630*x + 252)};
+		\addplot[densely dashed, domain=0:300, samples=100]{ln(x)};
+		\legend{5-point quadrature approximation, Actual value of $\log(1+x)$}
+		\end{axis}
+	\end{tikzpicture}%
+    \caption{Graph of $\log{(1+x)}$ and the approximation in Equation~\ref{eq:standardquadrature}}
+    \label{fig:standardquadrature}
+\end{figure}
 
-\subsection{Scope and Limitations}
-Our study will be limited in terms of the cryptosystems to be tested, the image processing operations we will implement, and the statistical tests we will use to gauge the security of the cryptosystems.
-Below is a listing of the scope of the study.
-
-We will implement and test the following algorithms:
-\begin{enumerate}
-	\item A variant of the Paillier cryptosystem~\cite{stern_public-key_1999} which supports floating-point operations, used in \textit{CryptoImg}~\cite{ziad_cryptoimg:_2016}.
-    \item The Damg{\aa}rd--Geisler--Kr{\o}igaard (DGK) cryptosystem~\cite{pieprzyk_efficient_2007, cryptoeprint:2008:321} which is primarily used for secure integer comparison.
-	\item A fully homomorphic encryption scheme by Dasgupta and Pal, which uses polynomial rings~\cite{dasgupta_design_2016}.
-	\item The Brakerski--Gentry--Vaikuntanathan (BGV) cryptosystem \cite{cryptoeprint:2011:277}, an improvement on the lattice-based cryptosystem by Gentry~\cite{gentry_fully_2009}, with optimizations from Smart, Vercauteren, and Halevi \cite{hutchison_fully_2010, cryptoeprint:2011:566}.
-\end{enumerate}
-We will implement and test the following categories of image manipulation operations:
-\begin{enumerate}
-	\item Non-linear image intensity adjustment (logarithm and power-log transformations)
-	\item Facial detection and recognition using the eigenface approach \cite{turk_eigenfaces_1991}.
-\end{enumerate}
-We will adopt the benchmark for evaluating image quality of image encryption schemes presented by Ahmed, et.
-al~\cite{ahmed_benchmark_2016}.
-The presented benchmark reflects many tests used in other literature~\cite{ahmad_efficiency_2012, wu_npcr_2011}.
-\begin{enumerate}
-    \item Mean Squared Error (MSE)
-    \item Peak Signal to Noise Ratio (PSNR)
-    \item Structural Similarity Index (SSIM)
-\end{enumerate}
-A detailed overview of the above will be provided in the methodology. Grayscale images will be used in the study.
-A client-server model for secure computation will be assumed to allow operations such as secure comparison and exponentiation.
-Training and test data are taken from the publicly available \texttt{faces94} dataset (\url{https://cswww.essex.ac.uk/mv/allfaces/faces94.html}) maintained by the University of Essex.
-
-\subsection{Significance of the Study}
-This study aims to directly address one of the current problems in the research of homomorphic cryptosystems: the practicality of homomorphic encryption~\cite{sen_homomorphic_2013}.
-The literature shows existing homomorphic cryptosystems and how they support primitive operations (usually addition and multiplication) on encrypted data, however, for homomorphic cryptosystems to be useful for practical use, efficient support for more complicated image processing operation must be demonstrated as well.
-While implementations of image processing operations in a homomorphic cryptosystem exist in the literature~\cite{ziad_cryptoimg:_2016, garay_algorithms_2014}, our study targets the more computationally intensive task of facial detection.
-
-We wish to contribute to existing models for the secure transmission and modification of image data by developing a software library which allows the use and comparison of various homomorphic encryption algorithms.
-Our software library would allow service providers to perform image manipulation for clients without compromising data privacy.
-
-\section{Review of Related Literature}
-\subsection{Homomorphic Cryptosystems}
-A cryptosystem consists of an encryption function $\mathcal{E}$ and a decryption function $\mathcal{D}$, along with the plaintext space $\mathcal{P}$, ciphertext space $\mathcal{C}$ and the key space $\mathcal{K}$~\cite{bauer_cryptosystem_2005}.
-A \textit{plaintext} is text that can be commonly understood, while a \textit{ciphertext} results from encrypting the plaintext using an encryption key.
-The \textit{plaintext space} is the set of all possible plaintexts, the \textit{ciphertext space} is the set of all possible ciphertexts, while the \textit{keyspace} is the set of all possible keys.
-
-There are two kinds of cryptosystems, \textit{symmetric} and \textit{asymmetric}.
-In symmetric-key cryptosystems, the same key is used for both encryption and decryption.
-As a consequence, symmetric-key cryptosystems must be implemented with a secure key exchange protocol, so that both the sender and receiver have access to the same key.
-Prominent examples of symmetric-key cryptosystems are the Data Encryption Standard (DES), and its replacement, the Advanced Encryption Standard (AES).
-
-On the other hand, asymmetric-key (or public-key) cryptosystems use separate keys for encryption and decryption.
-The encryption key (also called the \textit{public key}) is shared publicly, while the decryption key (also called the \textit{private key}) is kept secret.
-Since the public key and private keys are different, there is no need to agree upon secure key exchange protocols.
-Usually, the security of asymmetric-key cryptosystems relies on the intractability of certain computational problems, for example, the RSA cryptosystem depends on the difficulty of big integer factorization~\cite{rivest_method_1978}, while the ElGamal cryptosystem depends on the difficulty of the discrete logarithm problem~\cite{blakley_public_1985}.
-
-Homomorphic cryptosystems are a special type of cryptosystem in which operations can be securely performed on encrypted data.
-Suppose that for a public-key cryptosystem, $\mathcal{E}_k \left(p \right)$ is the encryption function using the public key $k \in \mathcal{K}$, and $\mathcal{D}_l \left(c \right)$ be the decryption function using the private key $l$.
-A cryptosystem is said to be homomorphic if its encryption function is homomorphic, that is, if it satisfies the relation
-\begin{equation}
-    \mathcal{E}_k \left(p_1 \boxplus p_2\right) = \mathcal{E}_k \left(p_1\right) \boxdot \mathcal{E}_k \left(p_2\right)
-\end{equation}
-where $p_1, p_2 \in \mathcal{P}$ are the plaintexts, and $\boxplus$ and $\boxdot$ are operations in $\mathcal{P}$ and $\mathcal{C}$ respectively~\cite{fontaine_survey_2007}.
-Furthermore, a homomorphic cryptosystem also satisfies~\cite{li_elliptic_2012}
-\begin{equation}
-    p_1 \boxplus p_2 = \mathcal{D}_l \left( \mathcal{E}_k \left(p_1\right) \boxdot \mathcal{E}_k \left(p_2\right) \right).
-\end{equation}
-In other words, a homomorphic cryptosystem preserves the operations that can be done with the plaintext without requiring an intermediary step of decrypting the ciphertext beforehand.
-It is important to note that the operations $\boxplus$ and $\boxdot$ need not be the same.
-A simple operation in the plaintext space may require a computationally intensive operation in the ciphertext space.
-
-Homomorphic cryptosystems can be classified according to the plaintext and ciphertext operations, $\boxplus$ and $\boxdot$.
-If the plaintext operation $\boxplus$ is addition, the cryptosystem is said to be \textit{additively homomorphic}, and the cryptosystem is said to be \textit{multiplicatively homomorphic} if the plaintext operation $\boxplus$ is multiplication.
-
-\subsection{Partially Homomorphic Cryptosystems}
-In this section, we will present two classical partially homomorphic cryptosystems which we will be testing in the study: the Paillier cryptosystem and the DGK cryptosystem.
-Both of these cryptosystems encrypt integer plaintexts and are additively homomorphic.
-
-We will then show that the cryptosystems can be modified to support privacy-perserving polynomial evaluation in a client-server protocol: given an encrypted message $m$, evaluate $f(m)$ where $f$ is a polynomial function.
-
-\subsubsection{The Paillier Cryptosystem}
-The Paillier cryptosystem \cite{stern_public-key_1999}, developed by Pascal Paillier, is a probabilistic encryption scheme which is based on the composite residuosity class problem.
-The scheme allows for the encryption and decryption of integer messages, and is known to be additively homomorphic.
-We now state the encryption and decryption algorithms of the Paillier cryptosystem and its homomorphic properties.
-
-\paragraph{Key Generation}
-We first define a function $L(x)$ as the largest integer $v$ greater than zero such that $x-1 \geq vn$.
-We choose two large primes $p$ and $q$, and set $n = pq, \lambda = \mathrm{lcm}(p-1,q-1)$.
-Then we select an integer $g$, $0\leq g \leq n^2$ such that $\mathrm{gcd}(L(g^\lambda \bmod n^2), n) = 1$.
-We denote the public key as $(g,n)$ and the private key $(p,q)$.
-
-\paragraph{Encryption and Decryption}
-The encryption function to encrypt a plaintext $m \in \mathbb{Z}_n$ given a public key $(g,n)$ is defined as
+As we only need accuracy for arguments $x \in [0, 255]$, we can scale the approximation by a constant factor $\alpha$ as follows:
 \begin{align*}
-  E(m) = g^m \cdot r^n \mod{n^2},
-\end{align*}
-where $r$ is a random non-negative integer less than $n^2$.
-
-The decryption function to decrypt a ciphertext $c \in \mathbb{Z}^\ast_{n^2}$ given a private key $(p,q)$ is defined as:
-\begin{align*}
-  D(c) = L(c^\lambda \bmod n^2) \times (L(g^\lambda \bmod n^2))^{-1} \mod n
+  \log{(1+x)} &= \log{\left(\frac{\alpha + \alpha x}{\alpha}\right)}\\
+  &= \log{(\alpha + \alpha x)} - \log{\alpha}\\
+  &= \log{\left(\alpha+\frac{\alpha}{n}\right)} - \log{\alpha}\\
+  &= \log{\left(\frac{\alpha n + \alpha}{n}\right)} - \log{\alpha}\\
+  &= \int_{n}^{\alpha n + \alpha}{\frac{1}{x}\diff x} - \log{\alpha}
 \end{align*}
 
-\paragraph{Homomorphic Properties of the Paillier Cryptosystem}
-The Paillier cryptosystem supports additive homomorphism as well as the multiplication of a plaintext scalar to an encrypted message.
-These homomorphic properties are used to add a plaintext scalar to a ciphertext, add two ciphertexts, and multiply a ciphertext by a plaintext scalar, respectively.
-They are defined as follows.
-
-For all $m_1,m_2 \in \mathbb{Z}_n$ and $k\in \mathbb{N}$, the following homomorphic properties hold.
-\begin{align*}
-  D(E(m_1)g^k\bmod n^2) &=(m_1+k)\bmod n\\
-  D(E(m_1)E(m_2)\bmod n^2) &=(m_1+m_2)\bmod n\\
-  D(E(m_1)^k\bmod n^2) &= km_1\bmod n
-\end{align*}
-
-\subsubsection{The DGK Cryptosystem}
-The DGK cryptosystem was published by Damg{\aa}rd, Geisler, and Kr{\o}igaard in 2007 in an effort to create a secure integer comparison scheme \cite{pieprzyk_efficient_2007, cryptoeprint:2008:321} which is widely used in the literature \cite{veugen_improving_2012}.
-
-\paragraph{Key Generation}
-We denote $k,t,\ell$ as security parameters of the scheme, where $k>t>\ell$.
-Let $p,q$ be primes such that
-we can choose two $t$-bit primes $v_p$ and $v_q$ such that $v_p | (p-1)$ and $v_q | (q-1)$, and a small prime $u$ such that $u | (p-1)$ and $u | (q-1)$.
-We denote $n = pq$.
-We choose $g$ to be an integer of order $uv_pv_q$ and $h$ to be of order $v_pv_q$.
-
-The DGK cryptosystem encrypts plaintexts in $\mathbb{Z}_u$ to ciphertexts in $\mathbb{Z}_n^\ast$.
-
-The public key is $(n,g,h,u)$ and the private key is $(p,q,v_p,v_q)$.
-
-\paragraph{Encryption and Decryption}
-To encrypt a message $m \in \mathbb{Z}_u$, the encryption function is defined as:
-\begin{align*}
-  E(m) = g^m \cdot h^r \mod{n},
-\end{align*}
-where $r$ is a random integer in $\mathbb{Z}_n$ which is longer than $2t$ bits.
-
-To decrypt a ciphertext $c \in \mathbb{Z}_n^\ast$, decryption is achieved by first computing $c^{v_pv_q}$.
-\begin{align*}
-	c^{v_pv_q} \bmod n
-	&= (g^m \cdot h^r)^{v_pv_q} \bmod n\\
-	&= (g^{v_pv_q})^m \bmod n
-\end{align*}
-Since $(g^{v_pv_q})^m$ has order $u$, there is a one-to-one correspondence between plaintexts in $\mathbb{Z}_u$ and  $(g^{v_pv_q})^m$.
-A lookup table can thus be generated privately to successfully recover $m$.
-
-\paragraph{Homomorphic Properties of the DGK Cryptosystem}
-The DGK cryptosystem supports additive homomorphism as well as the multiplication of a plaintext scalar to an encrypted message.
-These homomorphic properties are used to add a plaintext scalar to a ciphertext, add two ciphertexts, and multiply a ciphertext by a plaintext scalar, respectively.
-They are defined as follows.
-
-For all $m_1,m_2 \in \mathbb{Z}_u$ and $k\in \mathbb{N}$, the following homomorphic properties hold.
-\begin{align*}
-    D(E(m_1)g^k) &=(m_1+k)\bmod u\\
-    D(E(m_1)E(m_2)) &=(m_1+m_2)\bmod u\\
-    D(E(m_1)^k) &= km_1\bmod u
-\end{align*}
-
-As the multiplicative homomorphism was not presented in the original paper, we provide a short proof here.
-\begin{proof}
-  Let $m \in \mathbb{Z}_u$ and $k\in \mathbb{N}$.
-  We consider $E(m)^k = (g^m \cdot h^r \bmod{n})^k\bmod n$.
-  \begin{align*}
-    (g^m \cdot h^r \bmod{n})^k \bmod n
-    &= (g^m \cdot h^r)^k \bmod{n}\\
-    &= (g^m)^k \cdot (h^r)^k \bmod{n}\\
-    &= g^{km} \cdot (h^kr) \bmod{n}\\
-  \end{align*}
-  Since $r$ is a random integer, $kr$ is also a random integer, Therefore, $g^{km} \cdot (h^kr) \bmod{n} = D(E(m_1)^k)$ is a valid encryption of the message $km$.
-\end{proof}
-
-\subsubsection{Secure Exponentiation and Multiplication Protocols}
-\label{ssec:exponentiationprotocol}
-In order to perform polynomial evaluation, we first present a protocol for privacy-preserving exponentiation to a positive integer power, adapted from the protocol to calculate Euclidean distances used in \cite{hutchison_privacy-preserving_2009}.
-
-The following protocols apply to both the Paillier and DGK cryptosystems, as they share similar homomorphisms. We first present a secure squaring protocol.
-
-Suppose Alice encrypts an integer $x$ and sends it so Bob has $E(x)$, and wants to obtain $E(x^2)$ without exposing the value of $x$.
-\begin{itemize}
-	\item Bob first selects a random integer $r$ and computes $E(x+r)$. Bob can do this since $r$ is a plaintext constant.
-	\item Bob sends $E(x+r)$ to Alice, who decrypts the ciphertext to obtain $x+r$.
-	\item Alice squares $x+r$ and encrypts the result. She sends $E((x+r)^2)$ to Bob.
-	\item Bob computes $E(-2rx + r^2)$. He then computes $E((x+r)^2)E(-2rx + r^2) = E(x^2)$.
-\end{itemize}
-
-We can use the secure squaring protocol to arrive at a secure multiplication protocol, which then allows for the evaluation of polynomials.
-Suppose Alice encrypts integers $x$ and $y$, and Bob has $E(x), E(y)$ and wants to obtain $E(xy)$.
-\begin{itemize}
-	\item Bob acquires $E(x^2), E(y^2)$ using the secure squaring protocol.
-	\item Bob sends $E(x+y)$ to Alice, who decrypts the ciphertext to obtain $x+y$.
-	\item Alice sends $E((x+y)^2)$ to Bob.
-	\item Bob then computes
-	\begin{align*}
-		E((x+y)^2)E(x^2)^{-1}E(y^2)^{-1} &= E((x+y)^2 - x^2 - y^2)\\
-		&= E(2xy)
-	\end{align*}
-	\item Bob can then recover $E(xy)$ by calcuating for the multiplicative inverse of 2 using the Euclidean algorithm, and calculating $2^{-1}E(xy)$.
-Such an inverse exists since the modulus is either a prime (in the DGK cryptosystem) or a product of primes greater than 2 (in the Paillier cryptosystem).
-\end{itemize}
-
-\subsection{Fully Homomorphic Cryptosystems}
-We will also be testing fully homomorphic cryptosytems, which allow aribitrary computation on encrypted data.
-While generally being more flexible, fully homomorphic cryptosytems are known to be significantly slower than partially homomorphic cryptosytems; improving the efficiency of fully homomorphic cryptosytems is an active area of research \cite{sen_homomorphic_2013}.
-
-We will present two such cryptosystems, the Dasgupta--Pal cryptosystem, which we present in full to explain a correction we propose to it, and the BGV cryptosystem, which has open source implementations availble primarily used in homomorphic cryptography research.
-
-\subsubsection{The Dasgupta--Pal Cryptosystem}
-The Dasgupta--Pal cryptosystem is a fully homomorphic cryptosystem proposed in 2016 by Smaranika Dasgupta and S.
-K.
-Pal \cite{dasgupta_design_2016}, which encrypts integer plaintexts in $\mathbb{Z}_n$ to polynomial ciphertexts.
-We begin our presentation of the Dasgupta--Pal cryptosystem with the following definition.
-
-Given a message $m \in \mathbb{Z}$, we denote
-\begin{align*}
-		m_p(x) = a_0 + a_1 x + a_2 x^2 + \cdots + a_k x^k
-\end{align*}
-where $a_k a_{k-1}\cdots a_2 a_1 a_0$ is the binary representation of $m$.
-
-In the original scheme presented in \cite{dasgupta_design_2016}, the secret key $S_k$ is set to be a large prime.
-In Appendix \ref{chap:correction}, we present a case where the Dasgupta--Pal cryptosystem fails and prove that setting the secret key $S_k = 2p$, where $p$ is a large prime, corrects errors in the Dasgupta--Pal cryptosystem.
-We now decribe the correct cryptosystem.
-\paragraph{Corrected Dasgupta--Pal Cryptosystem Description}
-Let $\ell$ denote the security parameter of the cryptosystem.
-Let $S_k = 2p$, where $p$ is a prime number with $\ell - 1$ bits.
-Choose a random even integer $z$ of length $\log_2{\ell}$.
-
-Let the secret key be $S_k$, and let the refresh key be $R_k = z \cdot S_k$. The secret key is kept private to the encrypting/decrypting parties, while the refresh key is made publicly available.
-
-The scheme defines the encryption algorithm for a message $m$ as follows:
-\begin{align*}
-	E(m) = y(x) + S_k\times d(x)
-\end{align*}
-where
-$y(x)$ is a polynomial of degree $n$ such that $m_p(x) \equiv y(x) \bmod S_k$ and $d(x)$ is a randomly chosen polynomial of degree $n$.
-This encrypts each coefficient of of $m_p(x)$ by adding some multiple of $S_k$ to it.
-Through this process, each bit of the message is encrypted separately.
-
-Furthermore, the decryption algorithm to recover $m_p(x)$ from a ciphertext polynomial $c(x)$ as
-\begin{align*}
-	m_p(x) = c(x) \bmod S_k \bmod 2.
-\end{align*}
-Thus $D(c(x))$ is defined as the integer recovered from the coefficients of the polynomial $c(x) \bmod S_k \bmod 2$.
-
-Dasgupta and Pal note that homomorphic operations on ciphertext introduce noise which may interfere with decryption, due to the potential increase in ciphertext values.
-To eliminate noise from a polynomial ciphertext, the following refresh function is used:
-\begin{align*}
-	R(c(x)) = c(x) \bmod R_k.
-\end{align*}
-
-\paragraph{Homomorphic Properties of the Dasgupta--Pal Cryptosystem}
-It has been shown \cite{dasgupta_design_2016} that the following properties hold for all integer messages $m_1, m_2 \in \mathbb{Z}_n$ in the Dasgupta--Pal cryptosystem.
-These properties arise since each coefficient in a ciphertext polynomial is essentially an independently encrypted bit of the original message.
-\begin{description}
-	\item[\textsc{xor} on ciphertexts]
-	A bitwise exclusive or (\textsc{xor}) operation on integer messages can be achieved by adding the coefficients pairwise between two ciphertexts.
-	\begin{align*}
-		D(E(m_1)+E(m_2)) = m_1 \textsc{ xor } m_2
-	\end{align*}
-	\item[\textsc{and} on ciphertexts]
-	Similarly, pair-wise multiplication corresponds to bitwise \textsc{and} of integer messages.
-	\begin{align*}
-		D(E(a) \otimes E(b)) = a \textsc{ and } b = ab \bmod 2
-	\end{align*}
-	where $\otimes$ denotes pairwise multiplication,
-	\begin{align*}
-		\sum_{i=1}^n{a_ix^i} \otimes \sum_{i=1}^n{b_ix^i} = \sum_{i=1}^n{a_ib_ix^i}.
-	\end{align*}
-\end{description}
-
-Arbitrary computation on data can thus be achived using these bitwise operations.
-While the Dasgupta--Pal cryptosystem requires significant amounts of memory, as each bit of plaintext is encrypted into an integer, this approach provides a flexible method to perform relatively fast arbitrary computation on encrypted data.
-Encryption and decryption in the Dasgupta--Pal cryptosystem are accomplished using few arithmetic operations.
-
-\subsubsection{HElib and the BGV Cryptosystem}
-The BGV (Brakerski--Gentry--Vaikuntanathan) cryptosystem \cite{cryptoeprint:2011:277} is a fully homomorphic cryptosystem created based on the ring-learning with error problem.
-The BGV cryptosystem was constructed to surpass the limitations of prior fully homomorphic cryptosystems, which were based on the first fully homomorphic cryptosystem by Gentry \cite{gentry_fully_2009}.
-
-The details regarding the construction of the BGV cryptosystem are beyond the scope of this paper.
-For this study, we will be using \textit{HElib} \cite{garay_algorithms_2014}, an open-source library which implements the BGV cryptosystem with optimizations to improve efficiency.
-Evaluation of operations on 120 inputs in HELib was performed in around 4 minutes, with an average of 2 seconds to process a single input \cite{hutchison_fully_2010,cryptoeprint:2011:566}.
-
-The \textit{HElib} library has been adapted to Python using the Pyfhel library \cite{pyfhel_2018} maintained by Ibarrondo, Laurent (SAP) and Onen (EURECOM), and licensed under the GNU GPL v3 license.
-The Pyfhel library is a Python API for the \textit{HElib} library, which supports the following operations on vectors/scalars of integers or binary ciphertexts:
-\begin{itemize}
-	\item Arithmetic operations: addition, subtraction, multiplication;
-	\item Binary operations: \textsc{and}, \textsc{or}, \textsc{not}, \textsc{xor}.
-\end{itemize}
-
-\subsection{CryptoImg}
-A paper published in 2009 by Ziad, et al.
-attempts to implement privacy-preserving image processing using \textit{CryptoImg}, a library for the Open Source Computer Vision Library (OpenCV)~\cite{bradski_opencv_2000} which implements various homomorphic encryption and image processing routines using the Paillier homomorphic cryptosystem~\cite{ziad_cryptoimg:_2016}.
-The CryptoImg library assumed a client-server model wherein a client requests image processing operations from a server.
-A client first encrypts a digital image and sends the image securely to a server, which then operates on the encrypted image without revealing its contents.
-Then the resulting image is sent back to the client, which decrypts the image to recover the desired output.
-\begin{figure}[!ht]
-    \centering
-    \includegraphics[width=0.4\textwidth]{figures/ClientServerModel.png}
-    \caption{Client-server architecture used by \textit{CryptoImg} \cite{ziad_cryptoimg:_2016}}
-    \label{fig:clientserver}
-\end{figure}
-
-The \textit{CryptoImg} library implemented the following:
-\begin{enumerate}
-	\item Extending the Paillier homomorphic cryptosystem which operate on integer plaintexts so that they can operate on real number plaintexts;
-	\item Developing protocols for and implementing the following image processing operations
-	\begin{enumerate}
-		\item Image negation and brightness adjustment
-		\item Spatial filters (for noise reduction, edge detection and sharpening)
-		\item Morphological operations
-		\item Histogram equalization
-	\end{enumerate}
-\end{enumerate}
-For image negation and spatial filters, the protocols specified by \textit{CryptoImg} allow all image processing operations to be performed on the server.
-However, due to limitations in the Paillier cryptosystem, the protocols presented for morphological operations and histogram equalization require both the client and the server to perform image processing calculations, although the server performs a significant portion of the processing.
-
-Ziad, et al.
-also showed experimental results establishing the slow performance of image operations under a homomorphic cryptosystem.
-For instance, while sharpening and applying a Sobel filter each take less than a second when applied to a $512\times 512$ plaintext image, when applied to an encrypted image, sharpening required at least 238.257 seconds, and applying the Sobel filter required at least 147.567 seconds \cite{ziad_cryptoimg:_2016}.
-
-We now discuss several limitations in the \textit{CryptoImg} study which we focus on for our research.
-First, the \textit{CryptoImg} library was limited in the image intensity transformations it implemented.
-We propose additional protocols to support more computationally intensive intensity transformations.
-Second, the \textit{CryptoImg} library only considered the Paillier cryptosystem.
-We consider testing the performance of other homomorphic cryptosystems, which differ in their processing time and supported operations.
-
-\subsection{Image Intensity Transformations}
-We represent a digital image $R$ as an $M \times N$ matrix of pixel intensity values, each value in the range $\left[0, L-1\right]$, for some positive integer $L$.
-We use $R(x,y)$ to represent the entry at the $x$th row and $y$th column of a matrix $R$.
-An intensity transformation on an image $R$ can be defined as a function $T$ which maps a pixel value $r$ to a new value $r^\prime$, which we can write as $r^\prime = T\left(r\right)$.
-This function is then applied to every pixel in $R$.
-The \textit{CryptoImg} library implemented two types of linear intensity transformations: image negation and brightness control.
-
-An image negation transformation is defined as:
-\begin{equation}
-    T\left(r\right) = L-1-r
-\end{equation}
-After applying image negation, the resulting image would be similar to a photographic negative~\cite{gonzalez_digital_2008}.
-
-A brightness control transformation with parameter $v$ is defined as:
-\begin{equation}
-    T\left(r,v\right) = r+v
-\end{equation}
-The above transformations are linear in terms of the input $r$, and are thus simple to implement under a homomorphic cryptosystem.
-
-In this study we extend the range of intensity transformations to non-linear transformations.
-Two common non-linear image transformations are the log transformation and power-law transformation~\cite{gonzalez_digital_2008}.
-
-The log transformation is used to enhance dark pixels or increase the dark details of an image by mapping low intensity values to a wider range of values~\cite{gonzalez_digital_2008}.
-This has the general formula
-\begin{equation}
-    T\left(r\right) = c \log\left(1 + r\right)
-\end{equation}
-where $c$ is a constant.
-
-The power-law transformation is a family of transformations that have the form
-\begin{equation}
-    T\left(r\right) = c r^{\gamma}
-\end{equation}
-where $c>0$ and $\gamma > 0$.
-A power-law transformation defined by the above equation can calibrate the operation of many image capture and output devices such as cameras, printers and displays in a process called \textit{gamma correction}.
-This ensures reproducibility and accuracy of images being displayed by digital output devices~\cite{gonzalez_digital_2008}.
-
-To implement non-linear intensity transformations using addition and multiplication in a homomorphic system, it is necessary to approximate the logarithm and exponential functions, which may result in higher computational overhead.
-In our software library implementation, we investigate methods required to approximate the logarithm and power functions.
-Non-linear intensity transformations such as the logarithm transformation have applications in intensity normalization \cite{oravec_illumination_2010}, which is used in some facial recognition algorithms to account for differences in lighting which make facial recognition difficult.
-
-\subsection{Facial Detection and Recognition}
-%% TODO: Brian dump ur stuff here
-
-Since simple image operations mentioned earlier can be done within a homomorphic cryptosystem, these operations can be assembled together in order to do more complex operations.
-A prominent application of image processing that often uses complex image operations is \textit{facial recognition}.
-
-Traditional facial recognition algorithms rely on detecting salient features in a face image. One of the popular facial recognition algorithms is \textit{eigenfaces}.
-% Traditional facial recognition algorithms rely on detecting salient features in a face image. Two of the popular facial recognition algorithms are \textit{eigenfaces} and \textit{Haar cascades}.
-
-\subsubsection{Eigenfaces}
-Proposed by Matthew Turk and Alex Pentland, the eigenfaces method uses principal component analysis (PCA) in order to express an input image as a linear combination of eigenfaces \cite{turk_eigenfaces_1991}.
-An \textit{eigenface} is a principal component, or more simply an eigenvector that represents a certain variation between the face images which are taken from the initial training set.
-The number of resulting eigenfaces is equal to the number of face images in the training set.
-
-In the enrollment process, $M$ face images $\Theta_1, \ldots, \Theta_M$, each of size $p \times q$, are taken in to comprise the initial training set.
-The training images can be represented as vectors of length $N = pq$, where each row of an image is concatenated together.
-
-The average of the training images, denoted as $\Psi$, is 
-\begin{equation}
-	\Psi = \frac{1}{M} \sum_{i=1}^{M} \Theta_i
-\end{equation}
-
-The \textit{difference vectors} are then computed as $\Phi_i = \Theta_i - \Psi$. PCA is applied on the covariance matrix of the vectors
-\begin{equation}
-	\mathbf{C} = \frac{1}{M} \sum_{i=1}^M \Phi_i \Phi_i^\top = \frac{1}{M} \mathbf{A}\mathbf{A}^\top,
-\end{equation}
-where $\mathbf{A}$ is an $N \times M$ matrix defined by $\left[\Theta_1 \quad \Theta_2 \quad \cdots \quad \Theta_M\right]$, in order to determine the orthonormal eigenvectors \cite{hutchison_privacy-preserving_2009}.
-
-Directly computing the covariance matrix and then applying PCA will become inefficient for large sizes of $\mathbf{A}$, since computing for $\mathbf{A}\mathbf{A}^\top$ results in an $N \times N$ matrix, which can get drastically large because it is dependent on the size of the image.
-On the other hand, computing for $\mathbf{A}^\top\mathbf{A}$ only results in an $M \times M$ matrix, which is much smaller than the previous one because it is just dependent on the number of face images in the training set.
-Now, we can apply PCA to $\mathbf{A}^\top\mathbf{A}$ along with some post-processing to obtain the eigenvectors \cite{hutchison_privacy-preserving_2009}.
-
-Instead of getting the eigendecomposition of the covariance matrix by explicitly computing the eigenvalues and eigenvectors of $\mathbf{C}$, we can also apply \textit{singular value decomposition} (SVD) on the matrix $\Phi^\top$.
-This is because SVD works through a divide-and-conquer method which results in greater numerical stability, while eigendecomposition simply uses the traditional QR factorization \cite{nakatsukasa_stable_2013, gu_divide-and-conquer_1995}.
-Upon applying SVD, we now get the eigenvectors $\mathbf{u}_1, \ldots, \mathbf{u}_M$ and their corresponding eigenvalues $\lambda_1, \ldots, \lambda_M$.
-
-We choose $K$ eigenvectors $\mathbf{u}_1, \ldots, \mathbf{u}_K$ such that it comprises a set associated with the $K$ largest eigenvalues, where $K$ is much smaller than $M$.
-This set is now the \textit{face space}.
-Then, the images $\Theta_1, \ldots, \Theta_K$ are projected onto the face space spanned by the eigenfaces to determine the weight vectors $\Omega_1, \ldots, \Omega_K$.
-
-To perform the recognition process, the algorithm projects the input image $\Gamma$ onto the face space, and then comparing the projected image $\bar{\Omega} = \mathbf{u}_i\left(\Gamma - \Psi\right)$ with each eigenface in the face space using a metric such as the Euclidean distance.
-Thus it is computed as $d_i = \left\lVert \Omega_i -\bar{\Omega} \right\rVert$ for all $i=1,\ldots,K$, where $\left\lVert \cdot \right\rVert$ denotes the Euclidean norm.
-
-Then, a match can be reported if the smallest possible distance is smaller than the given threshold value $T$. 
-\newcommand{\argmin}{\mathop{\mathrm{arg\,min}}}  
-\begin{equation}
-	\text{ID} = \begin{cases}\argmin_i d_i & \text{if } \min_i d_i \le T \\\emptyset & \text {otherwise}\end{cases}
-\end{equation}
-
-\subsection{Previous Implementations of Secure Facial Recognition}
-Erkin, et al.
-\cite{hutchison_privacy-preserving_2009} devised a method to incorporate the use of homomorphic cryptosystems into the eigenfaces method.
-In their study, they proposed a two-party system where Alice holds an encrypted image $\left[\Gamma\right]$, while Bob maintains a database of $K$ eigenfaces $\mathbf{u}_1, \ldots, \mathbf{u}_K$, and feature vectors $\Omega_1, \ldots, \Omega_M$ in the clear.
-
-\begin{figure}[!h]
-    \centering
-    \includegraphics[width=0.4\textwidth]{figures/secure_eigenfaces.png}
-    \caption{Diagram of the privacy-preserving facial recognition process \cite{hutchison_privacy-preserving_2009}}
-\end{figure}
-
-In order to ensure privacy, the steps in the eigenfaces algorithm, namely: projection, distance computation, and match finding, are done within the encrypted domain, i.e., using the operations in the Paillier cryptosystem.
-
-Projection is similar to that of the original eigenfaces algorithm, except the operations are replaced with their respective operations in the cryptosystem.
-Distance computation in this version is somewhat different from the original eigenfaces method, in that it deals with the square of the Euclidean distance since the relative order of the distances is only important when comparing these during the match finding step \cite{hutchison_privacy-preserving_2009}.
-\begin{align}
-    d_i &= \left\lVert \Omega_i - \bar{\Omega} \right\rVert ^2 = \sum_{j=1}^{K} \left(\omega_{ij} - \bar{\omega}_j\right)^2 \\
-        &= \underbrace{\sum_{j=1}^{K} \omega_{ij}^2}_{\mathcal{S}_1} + \underbrace{\sum_{j=1}^{K} \left(-2 \omega_{ij} \bar{\omega_j}\right)}_{\mathcal{S}_2} + \underbrace{\sum_{j=1}^{K} \bar{\omega}_{j}^2}_{\mathcal{S}_3}
-\end{align}
-
-Computing for the distances within Paillier would just be multiplying the encrypted sums together.
-\begin{equation}
-	\left[d_i\right] = \left[\mathcal{S}_1\right] \cdot \left[\mathcal{S}_2\right] \cdot \left[\mathcal{S}_3\right]
-\end{equation}
-
-The terms $\left[\mathcal{S}_1\right]$ and $\left[\mathcal{S}_2\right]$ can be easily computed by Bob, since he already knows both $\omega_i$ in the clear and $\left[\bar{\omega}_i\right]$ which is in encrypted form.
-Computing for $\left[\mathcal{S}_3\right]$ is trickier because Bob cannot compute for $\left[\bar{\omega}_i^2\right]$ because pairwise multiplication is not supported in Paillier, that is why Bob needs help from Alice to square a number through a protocol described below \cite{hutchison_privacy-preserving_2009}.
-
-Before Bob sends $\left[\bar{\omega}_i\right]$ to Alice for squaring, he adds a random number $r_i$ to compute $\left[x_i\right] = \left[\bar{\omega}_i + r_i\right] = \left[\bar{\omega}_i\right] \cdot \left[r_i\right]$, where $r_i$ is obviously distinct for every $i$, then sends $\left[x_i\right]$ to Alice.
-She then decrypts it and computes $x_i^2$, and then computes $\mathcal{S}_3^\prime = \sum_{i=1}^{K} x_i^2$, after which she encrypts the sum and sends $\left[\mathcal{S}_3^\prime\right]$ to Bob.
-Now, he can compute for $\left[\mathcal{S}_3\right]$ as follows:
-\begin{equation}
-	\left[\mathcal{S}_3\right] = \left[\mathcal{S}_3^\prime\right] \cdot \prod_{j=1}^{K} \left(\left[\bar{\omega}_j\right]^{-2r_j} \cdot \left[-r_j^2\right]\right)
-\end{equation}
-
-The protocol for squaring a number as described earlier is a workaround for the limitations of Paillier or any other partially homomorphic cryptosystem that only supports addition and scalar multiplication.
-This can be possibly extended so that operations such as pairwise multiplication and exponentiation are also supported, provided that the protocol involves two parties.
-
-The match finding step is done by comparing the distances obtained from the previous step to a specified threshold $T$.
-If the minimum distance is smaller than $T$, then a match is found, and the encrypted identity of the match is returned to Alice \cite{hutchison_privacy-preserving_2009}.
-Getting the minimum among the encrypted distances would involve comparing two encrypted numbers, which Paillier does not support.
-Instead, the DGK cryptosystem \cite{pieprzyk_efficient_2007} is used for the comparison protocol.
-
-\section{Methodology}
-In this study we apply four homomorphic encryption schemes~\cite{ziad_cryptoimg:_2016, pieprzyk_efficient_2007, dasgupta_design_2016, garay_algorithms_2014} for use in image processing and facial recognition applications.
-While the Paillier and DGK cryptosystems have been implemented for use in image processing in~\cite{ziad_cryptoimg:_2016, hutchison_privacy-preserving_2009}, the other cryptosystems have to be adapted for this study.
-Two experiments are conducted in this study:
-\begin{enumerate}
-	\item Assessment of non-linear image intensity transformations under each of the four cryptosystems.
-	\item Assessment of efficiency of each of the four cryptosystems when applied for use in privacy-preserving facial recognition and detection using eigenfaces.
-\end{enumerate}
-The results of the image intensity transformations are tested for image quality using benchmarks in~\cite{ahmed_benchmark_2016}.
-
-\subsection{Cryptosystem Implementation}
-Four homomorphic encryption schemes are investigated.
-For cryptosystems with readily available open-source implementations, such implementations are used.
-For the remaining cryptosystems, the encryption and decryption methods were implemented in Python.
-\begin{itemize}
-	\item The Paillier cryptosystem is incorporated using the implementation at \url{https://github.com/n1analytics/python-paillier} developed by Data61 - CSIRO.
-	\item The BGV cryptosystem is implemented using the Pyfhel library (\url{https://github.com/ibarrond/Pyfhel}) using a HElib backend from (\url{https://github.com/shaih/HElib}).
-	\item The DGK and Dasgupta--Pal cryptosystems are implemented from scratch with Python.
-\end{itemize}
-
-For convenience, a wrapper library is created that integrates the four cryptosystems into a unified interface.
-
-\subsection{Secure Computation with Real Numbers}
-We will briefly discuss a protocol to enable cryptosystems built for integer inputs to handle real number inputs.
-The following protocol was also used by \textit{CryptoImg} for image processing \cite{ziad_cryptoimg:_2016}.
-This is also used for our own implementation of the Dasgupta--Pal cryptosystem in order to handle real numbers.
-
-We represent a floating-point (FP) number as a pair of two integers $(m,e)$ representing the mantissa and exponent of the FP number with respect to a base $b$.
-The mantissa $m$ is encrypted, while the exponent $e$ is unencrypted.
-Let $a,b,c$ be FP numbers represented by the pairs $(m_a,e_a),(m_b,e_b),(m_c,e_c)$ respectively.
-Let $\oplus,\otimes$ represent the homomorphic operations which correspond to the addition and multiplication, respectively.
-We define the secure real number operations as follows:
-\begin{description}
-  \item[Addition.]
-    To compute $E(c)=E(a+b)$ we compute
-    \begin{align*}
-      E(m_c) &= E(m_1) \oplus (b^{e_b-e_a} \otimes E(m_b)), e_c = e_a & \text{ if } e_a \leq e_b \\
-      E(m_c) &= E(m_b) \oplus (b^{e_a-e_b} \otimes E(m_a)), e_c = e_b & \text{ if } e_a > e_b
-    \end{align*}
-  \item[Scalar multiplication.]
-    To compute $E(c) = E(ab)$, where $a$ and $E(b)$ are known (i.e. $m_a$ is not encrypted), we compute
-    \begin{align*}
-      E(m_c) &= m_a \otimes E(m_b)\\
-      e_c &= e_a + e_b
-    \end{align*}
-\end{description}
-
-\subsection{Non-Linear Intensity Transformations}
-Aside from implementing the homomorphic encryption and decryption algorithms, we will also implement library functions for image negation, logarithm transformation and power-law transformation, as they are defined in~\cite{gonzalez_digital_2008}.
-We now describe how we implement the logarithm and power-law image intensity transformations.
-In the case of partially homomorphic cryptosystems (Paillier, DGK), if  exponentiation and multiplication is required, the secure protocols in section \ref{ssec:exponentiationprotocol} will be used.
-
-\subsubsection{Logarithm Transformation}
-The logarithm transformation of a pixel intensity value $x$ is defined as
-\begin{align}
-	T\left(x\right) = c \log\left(1 + x\right)
-\end{align}
-where $c$ is a constant.
-
-In order to perform this transformation under a homomorphic cryptosystem, we must provide an approximation for $\log\left(1 + x\right)$ in terms of addition and multiplication operations (or their inverses).
-We have derived a closed form approximation in Appendix \ref{sec:logapproximation}.
-\begin{align}
-	\label{eq:scaledquadraturech3}
+Applying the five-point Gauss--Legendre quadrature rule with $\alpha = 1/20$ using SageMath 8.3, we arrive at the approximation:
+\begin{align}\label{eq:scaledquadrature}
   \begin{split}
@@
 
-\subsubsection{Power-Law Transformation}
-The power-law transformation of a pixel intensity value $x$ is defined as
-\begin{equation}
-    T\left(x\right) = cx^{\gamma}
-\end{equation}
-where $c>0$ and $\gamma > 0$.
+Figure~\ref{fig:scaledquadrature} is a graph of the absolute error of the scaled approximation and the exact value of $\log{(1+x)}$.
+Using SageMath 8.3, it was numerically determined that the maximum absolute error of this approximation in the range $x\in[0,255]$ is approximately $0.0103315865985758$, occurring at $x=255$.
+This is an improvement from the approximation in Equation~\ref{eq:standardquadrature}, which has a maximum absolute error of $1.19717868468392$, similarly occurring at $x=255$.
 
-Similar to the logarithm transformation, we must provide an approximation for $x^\gamma$.
-We have derived an infinite series in Appendix \ref{sec:logapproximation}.
-\begin{align}
-	x^\gamma &= \sum_{n=0}^{\infty}{\frac{(\gamma\log{x})^n}{n!}}
-\end{align}
-Partial sums of the above infinite series can be calculated based on the closed form approximation for the logarithm in Equation \ref{eq:scaledquadraturech3}.
-For the implementation of the power-law transformation, a partial sum consisting of the first five terms of the infinite series were used.
+% \begin{figure}[h]
+%     \centering
+%     \includegraphics[width=.9\linewidth]{figures/ModifiedQuadratureAbsoluteError.png}
+%     \caption{Graph of the absolute error of $\log{(1+x)}$ and the approximation in equation \ref{eq:scaledquadrature}}
+%     \label{fig:scaledquadrature}
+% \end{figure}
+\begin{figure}[h]
+    \centering
+    \begin{tikzpicture}
+		\begin{axis}[
+			% height=6cm, width=9cm,
+			xmin=0, xmax=300,
+			ymin=0, ymax=0.04,
+			xlabel={$x$}, ylabel={Absolute error},
+			grid=major,
+			legend pos=south east,
+			legend cell align=left,
+			tick scale binop=\times,
+		]
+		\addplot[thick, domain=0:300, samples=100]{abs((1/30*(137*x^5 + 33185*x^4 + 931370*x^3 - 13403630*x^2 - 289469315*x - 713567363)/(x^5 + 505*x^4 + 42010*x^3 + 923010*x^2 + 5722005*x + 8040501))-ln((1/20)+(1/20)*x))};
+		\end{axis}
+	\end{tikzpicture}%
+    \caption{Graph of the absolute error of $\log{(1+x)}$ and the approximation in Equation~\ref{eq:scaledquadrature}}
+    \label{fig:scaledquadrature}
+\end{figure}
 
-\subsection{Assessment of Homomorphic Encryption Schemes}
-A laptop computer with a 2.5 GHz Intel Core i7 quad-core processor and 8 GB of RAM is used to perform the computations, and processing time was tracked using built-in timing functions.
-The processing time for all cases were recorded.
-All of the tests are done using Python 3.7.1 running on Linux.
+\section{Approximation for $x^\gamma$}
+\label{sec:approx-pwr}
+To approximate $x^\gamma$ for any $\gamma \in \mathbb{R}$, we rewrite $x^\gamma$ as follows:
+\begin{align*}
+  x^\gamma = e^{\log{x^\gamma}} = e^{\gamma\log{x}}.
+\end{align*}
 
-\subsubsection{Image Quality of Intensity Transformations}
-In this section, we discuss the image quality metrics we used for assessing the performance of non-linear intensity transformations.
+This expression can then be approximated using the Maclaurin series expansion for $e^x$, which converges for all $x$.
+\begin{align*}
+  e^x &= \sum_{n=0}^{\infty}{\frac{x^n}{n!}}\\
+  \Rightarrow \quad e^{\gamma\log{x}} &= \sum_{n=0}^{\infty}{\frac{(\gamma\log{x})^n}{n!}}
+\end{align*}
 
-We first obtained test images from the \texttt{faces94} dataset (\url{https://cswww.essex.ac.uk/mv/allfaces/faces94.html}) maintained by the University of Essex.
-However, only ten distinct facial images from the dataset were selected for the purposes of this test.
-Since only grayscale images are used in the study, the images were converted to grayscale and then downsampled to $40 \times 36$ pixels.
-
-For each cryptosystem, three image operations are tested:
-\begin{enumerate}
-	\item Image negation
-	\item Logarithm transformation, with $c = 30$
-	\item Power-law transformation, with $c = 1$ and $\gamma = 0.4$
-\end{enumerate}
-
-For each plaintext image (PT), we considered each image operation listed above and generate three images: a plaintext domain transformation (PDT), a ciphertext image (CT), and an ciphertext domain transformation (CDT).
-The PDT was generated by running the image operation on the original image.
-The CT was generated by encrypting the image, then applying the operation, and the CDT was generated by decrypting the CT.
-The four images (PT, PDT, CT, CDT) were then compared using various benchmarks to evaluate the quality and security of each homomorphic encryption scheme.
-
-The benchmarks to be used in the study, adopted from~\cite{ahmed_benchmark_2016, ahmad_efficiency_2012, wu_npcr_2011} are listed below.
-We let $X_i$ denote a value in an image $X$, where $1 \leq i \leq N$.
-We first perform three tests to ascertain the preservation of image quality after encryption and decryption: MSE, PSNR, and SSIM.
-\begin{description}
-	\item [Mean Squared Error (MSE).] The MSE is defined in~\cite{ahmed_benchmark_2016} as
-	\begin{align}
-        \mathrm{MSE} = \frac{1}{N}\sum_{i=1}^{N}{(\mathrm{CDT}_i - \mathrm{PDT}_i)^2}.
-	\end{align}
-	The MSE provides a measure of how much data is recovered if an image operation is applied on the encrypted image, which is then decrypted.
-Lower values of MSE indicate higher preservation of image quality~\cite{ahmed_benchmark_2016, ahmad_efficiency_2012}.
-	\item [Peak Signal to Noise Ratio (PSNR).]
-	According to Ahmed, et al.~\cite{ahmed_benchmark_2016}, PSNR is ``an estimator for human visual perception of reconstruction quality.'' It has been used to ascertain image quality in various studies and is a known metric for image and video quality~\cite{upmanyu_efficient_2009, jain_image_2016, akramullah_video_2014}.
-Although it may produce results which do not correlate with human visual perception~\cite{huynh-thu_accuracy_2012, ahmed_benchmark_2016}, it is a valid indicator of image quality when media containing the same visual content is compared~\cite{huynh-thu_accuracy_2012}.
-	PSNR is defined by
-	\begin{align}
-        \mathrm{PSNR} = 10\log_{10}{\left( \frac{L^2}{\mathrm{MSE}} \right)}
-	\end{align}
-	where $L$ is the maximum pixel intensity value of an image.
-	Despite the known limitations of PSNR, since we are going to compare the effect of each encryption scheme on recovered image quality, given a fixed library of images, it is a valid measure of image quality for the study.
-A higher PSNR indicates higher image quality preservation.
-	\item [Structural Similarity Index (SSIM).]
-	The SSIM for two random variables $X$ and $Y$ is defined in~\cite{ahmed_benchmark_2016, akramullah_video_2014} as
-	\begin{align}
-        \mathrm{SSIM}(X,Y) = \frac{(2\mu_X\mu_Y+c_1)(2\sigma_{XY}+c_2)}{(\mu_X^2+\mu_Y^2+c_1)(\mu_X^2+\mu_Y^2+c_2)}
-	\end{align}
-	where
-	\begin{itemize}
-		\item $\mu_X, \mu_Y$ are the averages of $X$ and $Y$, respectively;
-		\item $\sigma_X, \sigma_Y$ are the variances of $X$ and $Y$, respectively;
-		\item $\sigma_{XY}$ is the covariance of $X$ and $Y$;
-		\item $c_1 = (k_1L)^2, c_2 = (k_2L)^2$ are two variables used to stabilize the measure when $\mu_X^2+\mu_Y^2$ is close to zero~\cite{akramullah_video_2014};
-		\item $L$ is the the maximum pixel intensity value of an image;
-		\item $k_1 = 0.01, k_2 = 0.03$ by default, given in~\cite{ahmed_benchmark_2016}.
-	\end{itemize}
-	The SSIM is applied to the luminance value of two images to gauge structural similarity between neighboring pixels.
-	For the study, we computed $\mathrm{SSIM}(\mathrm{PDT}, \mathrm{CDT})$ for every image operation, under each homomorphic cryptosystem.
-Higher values of SSIM indicate higher structural similarity, and an SSIM of $1$ indicates that the two images are identical~\cite{ahmed_benchmark_2016}.
-\end{description}
-
-Computing for MSE, PSNR, and SSIM was done using the corresponding built-in functions from the scikit-image Python library \cite{scikit-image}.
-
-\subsubsection{Facial Recognition Tests}
-The method for secure facial recognition using eigenfaces by Erkin, et al. \cite{hutchison_privacy-preserving_2009} was implemented for this study.
-
-As before, training and test data were also secured from the \texttt{faces94} dataset. The images were first converted to grayscale but it is not downsampled, unlike in the previous test.
-
-The facial recognition tests are done using ten-fold cross-validation for each cryptosystem, where the number of principal components used by the algorithm is fixed at $K=5$.
-
-Prior to splitting the dataset, the images within each set are shuffled.
-Since there are twenty (20) images per set, two images are taken at a time for each round of cross-validation.
-The first round would take the first two images from each set as part of the test set, and the rest of the images will be part of the training set.
-Then, the succeeding round would take the next two images from each set as part of the test set, and so on until ten rounds have been done.
-After every round of cross-validation, the accuracy score, confusion matrix, and total processing time are obtained.
-
-\subsection{Summary}
-In summary, the study consists of:
-\begin{itemize}
-	\item Creating a wrapper library that acts as a unified interface which implements the Paillier, DGK, Dasgupta--Pal, and BGV homomorphic cryptosystems.
-	\item An implementation of image processing operations (intensity transformations, facial recognition) under the above cryptosystems.
-	\item Conducting tests for image quality, processing time, using images from the \texttt{faces94} dataset.
-\end{itemize}
-
-\section{Preliminary Results and Discussion}
-The results shown in this section are gathered from the tests for intensity transformations under Paillier and Dasgupta--Pal cryptosystems.
-During testing, initial results obtained from BGV, particularly with image operations involving floating-point numbers like the logarithmic transformation, were unstable (i.e.
-the results vary drastically every time the same tests were done).
-This is because the Pyfhel library being used for the BGV cryptosystem is still in alpha development stage \cite{pyfhel_2018}.
-
-% One of the authors has already informed the maintainers of the library about a bug involving exponentiation of two real numbers.
-
-\subsection{Intensity Transformations}
-
-\begin{table*}
-	\caption{Comparison of intensity transformations under Paillier}
-	\label{tbl:it-pal}
-	\begin{tabular}{m{1cm}*{7}{>{\centering\arraybackslash}m{1.75cm}}}
-		\toprule
-		\multirow{2}{*}{Image} & \multirow{2}{*}{Original} & \multicolumn{2}{c}{Image negation} & \multicolumn{2}{c}{Logarithm transformation} & \multicolumn{2}{c}{Power-law transformation} \\
-							   &                           & PDT           & CDT          & PDT            & CDT           & PDT               & CDT           \\ 
-		\midrule
-		\xintFor #1 in {anpage, bplyce, drbost, ksunth, martin, pmives, rnpwil, sbains, swewin, yfhsie} \do {%
-		\texttt{#1} & \includegraphics[width=1.75cm]{out_faces/paillier_negate_#1_original.png} & \includegraphics[width=1.75cm]{out_faces/paillier_negate_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/paillier_negate_#1_decrypted.png} & \includegraphics[width=1.75cm]{out_faces/paillier_logtransform_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/paillier_logtransform_#1_decrypted.png} & \includegraphics[width=1.75cm]{out_faces/paillier_pwrtransform_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/paillier_pwrtransform_#1_decrypted.png} \\ }%
-		\bottomrule         
-	\end{tabular}
-\end{table*}
-
-\begin{table*}
-	\caption{Comparison of intensity transformations under Dasgupta--Pal}
-	\label{tbl:it-dp}
-	\begin{tabular}{m{1cm}*{7}{>{\centering\arraybackslash}m{1.75cm}}}
-		\toprule
-		\multirow{2}{*}{Image} & \multirow{2}{*}{Original} & \multicolumn{2}{c}{Image negation} & \multicolumn{2}{c}{Logarithm transformation} & \multicolumn{2}{c}{Power-law transformation} \\
-							   &                           & PDT           & CDT          & PDT            & CDT           & PDT               & CDT           \\ 
-		\midrule
-		\xintFor #1 in {anpage, bplyce, drbost, ksunth, martin, pmives, rnpwil, sbains, swewin, yfhsie} \do {%
-		\texttt{#1} & \includegraphics[width=1.75cm]{out_faces/dp_negate_#1_original.png} & \includegraphics[width=1.75cm]{out_faces/dp_negate_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/dp_negate_#1_decrypted.png} & \includegraphics[width=1.75cm]{out_faces/dp_logtransform_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/dp_logtransform_#1_decrypted.png} & \includegraphics[width=1.75cm]{out_faces/paillier_pwrtransform_#1_reference.png} &  \\ }%
-		\bottomrule         
-	\end{tabular}
-\end{table*}
-
-Table~\ref{tbl:it-pal} shows the images obtained from the intensity transformation tests under the Paillier cryptosystem, while Table~\ref{tbl:it-pal} shows the resulting images from the same tests under the Dasgupta--Pal cryptosystem.
-Shown for each image is the original unecrypted image, and for each intensity transformation the \textit{plaintext domain transformation} (PDT) is given which is the resulting image after applying the transformation to the unencrypted image and the \textit{ciphertext domain transformation} (CDT) is the decrypted image of the processed encrypted image.
-
-The following tables show the resulting metric scores for mean squared error (MSE), peak signal to noise ratio (PSNR), and structural similarity index (SSIM), as well as time taken (in seconds) for encrypting the input image ($t_\text{enc}$), applying an operation to the encrypted image ($t_\text{apply}$), and decrypting the resulting encrypted image ($t_\text{dec}$), for each image in the test set.
-Tables~\ref{tbl:neg-pal} and~\ref{tbl:neg-dp} show the results obtained from applying image negation, Tables~\ref{tbl:log-pal} and~\ref{tbl:log-dp} from applying logarithm transformation, and Tables~\ref{tbl:pwr-pal} and~\ref{tbl:pwr-dp} from applying power-law transformation.
-
-\subsubsection{Image Negation}
-Both the Paillier and Dasgupta--Pal cryptosystems were able to perform image negation under the encrypted domain without introducing noise in the resulting image.
-In other words, the resulting image from doing image negation on an image on the clear and doing image negation under the encrypted domain are identical, as evidenced by the mean squared errors being exactly equal to zero, the PSNR being infinite, and the SSIM being exactly equal to one.
-
-The Paillier cryptosystem performed better in terms of time, only taking about 0.01 seconds to apply image negation.
-On the other hand, the Dasgupta--Pal cryptosystem took about 22 seconds each to apply the same operation, which is expected since the implementation for Dasgupta--Pal was done in Python without using any external libraries.
-
-\begin{table}[h]
-	\caption{Image negation under Paillier}
-	\label{tbl:neg-pal}
-    \begin{tabular}{lcccccc}
-        \toprule
-        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
-        \texttt{anpage} & 0.000 & $\infty$ & 1.00000 & 0.128 & 0.013 & 0.041 \\
-		\texttt{bplyce} & 0.000 & $\infty$ & 1.00000 & 0.084 & 0.013 & 0.024 \\
-		\texttt{drbost} & 0.000 & $\infty$ & 1.00000 & 0.099 & 0.012 & 0.031 \\
-		\texttt{ksunth} & 0.000 & $\infty$ & 1.00000 & 0.109 & 0.012 & 0.048 \\
-		\texttt{martin} & 0.000 & $\infty$ & 1.00000 & 0.117 & 0.015 & 0.043 \\
-		\texttt{pmives} & 0.000 & $\infty$ & 1.00000 & 0.111 & 0.012 & 0.025 \\
-		\texttt{rnpwil} & 0.000 & $\infty$ & 1.00000 & 0.099 & 0.012 & 0.023 \\
-		\texttt{sbains} & 0.000 & $\infty$ & 1.00000 & 0.084 & 0.012 & 0.024 \\
-		\texttt{swewin} & 0.000 & $\infty$ & 1.00000 & 0.089 & 0.012 & 0.023 \\
-		\texttt{yfhsie} & 0.000 & $\infty$ & 1.00000 & 0.081 & 0.012 & 0.029 \\
-		\bottomrule
-    \end{tabular}
-\end{table}
-\begin{table}[h]
-	\caption{Image negation under Dasgupta--Pal}
-	\label{tbl:neg-dp}
-    \begin{tabular}{lcccccc}
-        \toprule
-        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
-		\texttt{anpage} & 0.000 & $\infty$ & 1.00000 & 0.221 & 30.217 & 0.239 \\
-		\texttt{bplyce} & 0.000 & $\infty$ & 1.00000 & 0.190 & 30.919 & 0.216 \\
-		\texttt{drbost} & 0.000 & $\infty$ & 1.00000 & 0.284 & 31.182 & 0.268 \\
-		\texttt{ksunth} & 0.000 & $\infty$ & 1.00000 & 0.225 & 32.581 & 0.223 \\
-		\texttt{martin} & 0.000 & $\infty$ & 1.00000 & 0.220 & 32.220 & 0.271 \\
-		\texttt{pmives} & 0.000 & $\infty$ & 1.00000 & 0.287 & 31.224 & 0.294 \\
-		\texttt{rnpwil} & 0.000 & $\infty$ & 1.00000 & 0.285 & 29.478 & 0.284 \\
-		\texttt{sbains} & 0.000 & $\infty$ & 1.00000 & 0.186 & 29.784 & 0.362 \\
-		\texttt{swewin} & 0.000 & $\infty$ & 1.00000 & 0.243 & 38.407 & 0.220 \\
-		\texttt{yfhsie} & 0.000 & $\infty$ & 1.00000 & 0.285 & 29.488 & 0.449 \\		
-		\bottomrule
-        \end{tabular}
-\end{table}
-
-\subsubsection{Logarithm Transformation}
-Unlike image negation, logarithm transformation involves more operations, so the increase in processing time for both cryptosystems are expected.
-Applying the logarithm transformation under Paillier took about 2 seconds per image, while it took about 13.5 minutes each under Dasgupta--Pal.
-
-The logarithm transformation under Dasgupta--Pal turned out to be more accurate than Paillier, whose mean squared errors approach zero and the SSIM values approach one for every image as shown in Table~\ref{tbl:log-dp}.
-Although the results from using Paillier show that it is also accurate enough with the mean squared errors being less than 30 and the SSIM values average to 0.99, Dasgupta--Pal has been able to produce an almost identical result to that of the plaintext domain transformation counterparts.
-This observation is rather unexpected, considering that the implementation used for Paillier is more robust (due to its use of external C/C++ libraries which makes computations faster).
-
-\begin{table}[h]
-	\caption{Logarithm transformation under Paillier}
-	\label{tbl:log-pal}
-    \begin{tabular}{lcccccc}
-        \toprule
-        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
-		\texttt{anpage} & 13.369 & 36.870 & 0.99263 & 0.085 & 1.813 & 0.023 \\
-		\texttt{bplyce} & 7.072 & 39.635 & 0.99017 & 0.089 & 2.073 & 0.023 \\
-		\texttt{drbost} & 8.151 & 39.019 & 0.98688 & 0.091 & 1.913 & 0.023 \\
-		\texttt{ksunth} & 25.253 & 34.108 & 0.98927 & 0.089 & 1.919 & 0.023 \\
-		\texttt{martin} & 10.374 & 37.971 & 0.98695 & 0.106 & 1.829 & 0.023 \\
-		\texttt{pmives} & 2.426 & 44.283 & 0.99401 & 0.127 & 1.900 & 0.023 \\
-		\texttt{rnpwil} & 5.184 & 40.985 & 0.98971 & 0.096 & 1.853 & 0.023 \\
-		\texttt{sbains} & 16.772 & 35.885 & 0.98492 & 0.081 & 1.746 & 0.024 \\
-		\texttt{swewin} & 5.803 & 40.494 & 0.99241 & 0.091 & 1.827 & 0.027 \\
-		\texttt{yfhsie} & 12.192 & 37.270 & 0.99354 & 0.081 & 1.815 & 0.023 \\
-		\bottomrule
-        \end{tabular}
-\end{table}
-\begin{table}[h]
-	\caption{Logarithm transformation under Dasgupta--Pal}
-	\label{tbl:log-dp}
-    \begin{tabular}{lcccccc}
-        \toprule
-        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
-		\texttt{anpage} & 0.004 & 71.624 & 0.99999 & 0.287 & 802.957 & 0.036 \\
-		\texttt{bplyce} & 0.000 & 82.043 & 1.00000 & 0.190 & 815.384 & 0.048 \\
-		\texttt{drbost} & 0.004 & 72.480 & 1.00000 & 0.270 & 813.640 & 0.036 \\
-		\texttt{ksunth} & 0.000 & 87.372 & 1.00000 & 0.204 & 804.629 & 0.047 \\
-		\texttt{martin} & 0.001 & 77.421 & 1.00000 & 0.245 & 822.940 & 0.036 \\
-		\texttt{pmives} & 0.001 & 76.934 & 1.00000 & 0.194 & 814.132 & 0.036 \\
-		\texttt{rnpwil} & 0.000 & 83.135 & 1.00000 & 0.197 & 808.503 & 0.047 \\
-		\texttt{sbains} & 0.001 & 77.301 & 1.00000 & 0.270 & 809.406 & 0.047 \\
-		\texttt{swewin} & 0.006 & 70.004 & 0.99999 & 0.268 & 813.217 & 0.051 \\
-		\texttt{yfhsie} & 0.001 & 78.576 & 1.00000 & 0.243 & 830.640 & 0.039 \\
-		\bottomrule
-        \end{tabular}
-\end{table}
-
-\subsubsection{Power-Law Transformation}
-Unlike in the previous intensity transformations, applying the power-law transformation under both cryptosystems produced less than accurate images.
-The accuracy varies greatly across all the images as in the case of Paillier, with mean squared errors as high as 8270.696 and as low as 616.419, and SSIM scores ranging from 0.43185 to 0.92334.
-As expected, the total processing time now takes about 20 seconds per image since the power-law transformation is more computationally intensive due to its approximation of an infinite series consisting of terms using the logarithm function, which is also approximated using a combination of addition and multiplication operations.
-
-\begin{table}[h]
-	\caption{Power-law transformation under Paillier}
-	\label{tbl:pwr-pal}
-    \begin{tabular}{lcccccc}
-        \toprule
-        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
-        \texttt{anpage} & 3910.678 & 12.208 & 0.46712 & 0.099 & 14.695 & 0.024 \\
-		\texttt{bplyce} & 873.064 & 18.720 & 0.84379 & 0.139 & 16.190 & 0.023 \\
-		\texttt{drbost} & 1261.059 & 17.123 & 0.77229 & 0.082 & 13.866 & 0.023 \\
-		\texttt{ksunth} & 653.049 & 19.981 & 0.90673 & 0.083 & 15.507 & 0.023 \\
-		\texttt{martin} & 646.310 & 20.026 & 0.88157 & 0.108 & 15.727 & 0.045 \\
-		\texttt{pmives} & 2047.933 & 15.018 & 0.69408 & 0.113 & 14.728 & 0.034 \\
-		\texttt{rnpwil} & 806.473 & 19.065 & 0.85346 & 0.082 & 14.253 & 0.024 \\
-		\texttt{sbains} & 616.419 & 20.232 & 0.92334 & 0.121 & 14.415 & 0.023 \\
-		\texttt{swewin} & 8270.696 & 8.955 & 0.43185 & 0.112 & 14.362 & 0.065 \\
-		\texttt{yfhsie} & 1715.478 & 15.787 & 0.73857 & 0.145 & 20.239 & 0.023 \\
-		\bottomrule
-        \end{tabular}
-\end{table}
-\begin{table}[h]
-	\caption{Power-law transformation under Dasgupta--Pal}
-	\label{tbl:pwr-dp}
-    \begin{tabular}{lcccccc}
-        \toprule
-        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
-		% \texttt{anpage} & 25115.891 & 4.131 & 0.00000 & 0.016 & 741.872 & 0.031 \\ 10x10
-		\texttt{anpage} & 25008.723 & 4.150 & 0.00000 & 0.376 & 9700.926 & 1.269 \\
-		% \texttt{bplyce} & 22777.187 & 4.556 & 0.00000 & 0.017 & 730.873 & 0.003 \\ 10x10
-		\texttt{bplyce} & 22700.522 & 4.570 & 0.00000 & 0.230 & 9196.609 & 0.043 \\
-		% \texttt{drbost} & 18899.906 & 5.366 & 0.00000 & 0.014 & 733.409 & 0.003 \\
-		\texttt{drbost} & 18902.214 & 5.366 & 0.00000 & 0.064 & 2261.407 & 0.110 \\ % 20x18
-		\texttt{ksunth} & 12585.729 & 7.132 & 0.00000 & 0.044 & 2259.010 & 0.011 \\ % 20x18
-		\texttt{martin} & 17012.423 & 5.823 & 0.00000 & 0.066 & 2440.351 & 0.011 \\
-		\texttt{pmives} & 31124.615 & 3.200 & 0.00000 & 0.072 & 2492.149 & 0.012 \\
-		\texttt{rnpwil} & 22982.917 & 4.517 & 0.00000 & 0.076 & 2321.928 & 0.008 \\
-		\texttt{sbains} & 13469.155 & 6.837 & 0.00000 & 0.044 & 2233.818 & 0.008 \\
-		\texttt{swewin} & 37453.834 & 2.396 & 0.00000 & 0.049 & 2203.045 & 0.008 \\
-		\texttt{yfhsie} & 23037.762 & 4.506 & 0.00000 & 0.045 & 2210.393 & 0.008 \\
-		\bottomrule
-        \end{tabular}
-\end{table}
-
-\section{Conclusion}
-In this paper, we have assessed the feasibility and practicality of various homomorphic cryptosystems with regard to secure processing and manipulation of facial image data through creation of a software library that facilitates image processing operations within the encrypted domain, as well as our own implementation of some homomorphic cryptosystems like Dasgupta--Pal for which existing third-party library dedicated for this purpose is not yet available.
-
-This paper also proposes a correction to the Dasgupta--Pal cryptosystem which is further explained in Appendix~\ref{chap:correction}.
-
-Even though an operation in a partially homomorphic cryptosystem is not theoretically possible, like multiplication of two ciphertexts under Paillier, it has been shown that such operations are indeed possible in a two-party system.
-Protocols for secure multiplication and exponentiation have been proposed and also applied to more complex image operations such as facial recognition.
-Thus, a partially homomorphic cryptosystem can be modified to admit more image processing operations by assuming a two-party system.
-
-Preliminary results have shown that both Paillier and Dasgupta--Pal apply image negation accurately and efficiently, as evidenced by the perfect zero MSE and infinite PSNR.
-For the logarithm transformation, Paillier was faster and accurate enough (with $\text{MSE} \le 30$ and $\text{SSIM} \approx 0.99$), but Dasgupta--Pal was slower but more accurate (with $\text{MSE} \le 0.01$ and $\text{SSIM} \approx 0.99999$) which was rather unexpected.
-However both Paillier and Dasgupta--Pal fail to produce accurate results in applying the power-law transformation.
-Based from these results, the Paillier cryptosystem is consistent enough to produce reasonable to accurate results.
-
-A wrapper library has been made which implements the various functions and methods of the cryptosystems into a single interface.
-This allowed us to express various image operations with a unified syntax, thus facilitating easier testing.
-
-\subsection{Ongoing and Future Work}
-Testing intensity transformations under the BGV cryptosystem will be started once the Pyfhel library is deemed stable enough to use, or another Python library that implements BGV becomes available. 
-One of the authors has already informed the developers of the Pyfhel library about a bug involving exponentiation of two real numbers.
-
-Efforts are ongoing with regard to the facial recognition tests.
-Our own implementation of the privacy-preserving  eigenfaces by Erkin, et al.
-does not yet use the DGK cryptosystem for secure integer comparison in the match finding step, thus we are working on implementing DGK from scratch.
-
-Another promising image operation to consider is \textit{facial detection} under a homomorphic cryptosystem.
-Work has been started in order to assess the feasibility of using Haar cascades in a privacy-preserving manner.
-
-Future work would involve improving and optimizing our implementation of the Dasgupta--Pal cryptosystem so that it performs faster.
-A suggestion would be to port the existing implementation to C/C++ and then create a Python library that acts as a wrapper to the C/C++ methods.
-For future studies, an implementation of a client-server framework or system dealing with secure image processing can be considered.
+As we already have an approximation for the natural logarithm, we can evaluate partial sums of the above infinite series to arrive at approximations for $x^\gamma$.

### 2019-01-16 pcsc-paper/parts/01_introduction.tex
Drafted the wordy part
Drafted the intro and RRL for the mini-thesis.

\section{Introduction}
Research in digital privacy has involved the use of homomorphic cryptosystems, cryptosystems which allow for operations to be performed on encrypted data without leaking information about the operands.
Previous research has highlighted the use of the Paillier cryptosystem, a partially homomorphic cryptosystem which allows two basic operations to be performed on encrypted integers: two encrypted integers can be added to obtain an encryption of their sum, and an encrypted integer can be multiplied to an unencrypted plaintext integer to obtain an encryption of their product.

Applications of the Paillier cryptosystem have included such as use in linear digital image transformations \cite{ziad_cryptoimg:_2016}, and linear algebra applications \cite{hutchison_privacy-preserving_2009}. However, many extensions to the Paillier cryptosystem have also been published, allowing floating-point arithmetic. In this paper, we will summarize these extensions and concern ourselves with the approximation of the transcendental functions using the Paillier cryptosystem given input constraints shown in table \ref{tab:inputconstraints}. By demonstrating how the Paillier cryptosystem can be applied to approximate common non-linear functions, we hope to extend its usability as a tool for privacy-preserving computation.
\begin{table}
	\caption{Summary of Functions [WIP]}
	\label{tab:inputconstraints}
	\begin{tabular}{ccl}
		\toprule
		Functions & Input Constraints\\
		\midrule
		$e^x$ & $x\in[0,255]$\\
		$\log(1+x)$ & $x\in[0,255]$\\
		$\sin x$ & $x\in[-2\pi,2\pi]$ \\
		$\arctan x$ & $x\in[-255,255]$\\
	\bottomrule
\end{tabular}
\end{table}

### 2019-01-16 pcsc-paper/parts/02_01_paillier.tex
Drafted the wordy part
Drafted the intro and RRL for the mini-thesis.

\subsection{The Paillier Cryptosystem}
The Paillier cryptosystem \cite{stern_public-key_1999}, developed by Pascal Paillier, is a probabilistic encryption scheme which is based on the composite residuosity class problem. The scheme allows for the encryption and decryption of integer messages, and is known to be additively homomorphic. We now state the encryption and decryption algorithms of the Paillier cryptosystem and its homomorphic properties.

\subsubsection{Key Generation}
We first define a function $L(x)$ as the largest integer $v$ greater than zero such that $x-1 \geq vn$.
We choose two large primes $p$ and $q$, and set $n = pq, \lambda = \mathrm{lcm}(p-1,q-1)$.
Then we select an integer $g$, $0\leq g \leq n^2$ such that $\mathrm{gcd}(L(g^\lambda \bmod n^2), n) = 1$.
We denote the public key as $(g,n)$ and the private key $(p,q)$.
\subsubsection{Encryption and Decryption}
The encryption function to encrypt a plaintext $m \in \mathbb{Z}_n$ given a public key $(g,n)$ is defined as
\begin{align*}
	E(m) = g^m \cdot r^n \mod{n^2},
\end{align*}
where $r$ is a random non-negative integer less than $n^2$.
The decryption function to decrypt a ciphertext $c \in \mathbb{Z}^*_{n^2}$ given a private key $(p,q)$ is defined as:
\begin{align*}
	D(c) = L(c^\lambda \bmod n^2) \times (L(g^\lambda \bmod n^2))^{-1} \mod n.
\end{align*}
\subsubsection{Homomorphic Properties of the Paillier Cryptosystem}
The Paillier cryptosystem supports additive homomorphism as well as the multiplication of a plaintext scalar to an encrypted message. These operations are defined as follows. These properties are used
For all $m_1,m_2 \in \mathbb{Z}_n$ and $k\in \mathbb{N}$, the following homomorphic properties hold.
\begin{align*}
	D(E(m_1)g^k\bmod n^2)=(m_1+k)\bmod n\\
	D(E(m_1)E(m_2)\bmod n^2)=(m_1+m_2)\bmod n\\
	D(E(m_1)^k\bmod n^2)= km_1\bmod n
\end{align*}

\subsection{Floating-Point Arithmetic}
The Paillier cryptosystem encrypts integers and allows operations on these integers. We now briefly go over several extensions to the Paillier cryptosystem discussed in the literature, which allow us to perform privacy-preserving floating-point arithmetic.

\subsubsection{Extending to Floating-Point Numbers}
We can use the following protocol described in \cite{ziad_cryptoimg:_2016}, in order to extend the privacy-preserving integer addition and integer scalar multiplication of Paillier cryptosystem to floating-point numbers.

We represent a floating-point (FP) number as a pair of two integers $(m,e)$ representing the mantissa and exponent of the FP number with respect to a base $b$. The mantissa $m$ is encrypted, while the exponent $e$ is unencrypted.
Let $a,b,c$ be FP numbers represented by the pairs $(m_a,e_a),(m_b,e_b),(m_c,e_c)$ respectively. Let $\oplus,\otimes$ represent the homomorphic operations which correspond to the addition and multiplication of integers in the Paillier cryptosystem, respectively. We define the corresponding FP number operations as follows:
\begin{description}
  \item[Addition.]
    To compute $E(c)=E(a+b)$ we compute
    \begin{align*}
      E(m_c) &= E(m_1) \oplus (b^{e_b-e_a} \otimes E(m_b)), e_c = e_a & \text{ if } e_a \leq e_b \\
      E(m_c) &= E(m_b) \oplus (b^{e_a-e_b} \otimes E(m_a)), e_c = e_b & \text{ if } e_a > e_b
    \end{align*}
  \item[Scalar multiplication.]
    To compute $E(c) = E(ab)$, where $a$ and $E(b)$ are known (i.e. $m_a$ is not encrypted), we compute
    \begin{align*}
      E(m_c) &= m_a \otimes E(m_b)\\
      e_c &= e_a + e_b
    \end{align*}
\end{description}
\subsubsection{Secure Division}
We can use the following two-party scheme defined in \cite{boukoros_lightweight_2017} to perform privacy-preserving division.
Suppose Bob has $E(x)$ and $E(y)$ and wants to obtain $E(x/y)$ without exposing the value of either integer.
\begin{itemize}
	\item Bob first selects a random number $r$ and computes $E(rx)$ and $E(ry)$. Bob can do this since $r$ is a plaintext constant.
	\item Bob sends $E(rx)$ and $E(ry)$ to Alice, who decrypts both values and computes $x/y$ in the plaintext domain.
	\item Alice encrypts and sends $E(x/y)$ to Bob.
\end{itemize}

\subsubsection{Secure Exponentiation}
\label{ssec:exponentiationprotocol}
To extend the available privacy-preserving arithmetic operations beyond those already supported by the system, we can use the following two-party scheme, adapted from the protocol to calculate Euclidean distances used in \cite{hutchison_privacy-preserving_2009}.

Suppose Alice encrypts an integer $x$ and sends it so Bob has $E(x)$, and wants to obtain $E(x^2)$ without exposing the value of $x$.
\begin{itemize}
	\item Bob first selects a random integer $r$ and computes $E(x+r)$. Bob can do this since $r$ is a plaintext constant.
	\item Bob sends $E(x+r)$ to Alice, who decrypts the ciphertext to obtain $x+r$.
	\item Alice squares $x+r$ and encrypts the result. She sends $E((x+r)^2)$ to Bob.
	\item Bob computes $E(-2rx + r^2)$. He then computes
	\begin{align*}
		E((x+r)^2)E(-2rx + r^2) = E(x^2).
	\end{align*}
\end{itemize}

\subsubsection{Secure Multiplication}
We can use the secure squaring protocol to arrive at a secure multiplication protocol, which then allows for the evaluation of polynomials.
Suppose Alice encrypts integers $x$ and $y$, and Bob has $E(x), E(y)$ and wants to obtain $E(xy)$.
\begin{itemize}
	\item Bob acquires $E(x^2), E(y^2)$ using the secure squaring protocol.
	\item Bob sends $E(x+y)$ to Alice, who decrypts the ciphertext to obtain $x+y$.
	\item Alice sends $E((x+y)^2)$ to Bob.
	\item Bob then computes
	\begin{align*}
		\frac{1}{2}E((x+y)^2)E(x^2)^{-1}E(y^2)^{-1} &= \frac{1}{2}E((x+y)^2 - x^2 - y^2)\\
		&= \frac{1}{2}E(2xy)\\
		&= E(xy)
	\end{align*}
\end{itemize}

Using these extensions to the Paillier cryptosystem, privacy-preserving floating-point arithmetic can be acheived.

### 2019-01-16 pcsc-paper/parts/02_02_approximation.tex
Drafted the wordy part
Drafted the intro and RRL for the mini-thesis.

\subsection{Known Approximations for Transcendental Functions}
Many methods to compute transcendental functions implemented in computer hardware and software libraries rely on direct knowledge of the function arguments. Several such approaches include using the CORDIC (coordinate rotation digital computer), pseudo-division and pseudo-multiplication algorithms \cite{walther_cordic_2000}, as well as using minimax polynomials, which are determined numerically using the Remez algorithm \cite{harrison_computation_1999}. These algorithms, while efficient, rely on table lookups, which cannot be done in a privacy-preserving system where the function arguments cannot be directly determined.

We must therefore rely on other methods, such as using the Taylor series expansions of these functions. While also in common use, not all Taylor series expansions have a convenient radius of convergence. To circumvent this, we can rely on an approach presented by Khattri in \cite{khattri_new_2009} to obtain closed form approximations to functions by approximating related integrals.

Khattri presents the following method to approximate the function $f(x)=\log(1+x)$.
Let $x = 1/n$ and consider the integral
\begin{align}
	\label{eq:log_integral}
	\int_{n}^{n+1}{\frac{1}{x}\diff x}=\log{\left(1+\frac{1}{n}\right)}.
\end{align}

This integral can be approximated using the five-point Gauss-Legendre quadrature rule \cite{kythe_quadrature_2002}. We first convert the integral to an integral over the interval $[-1,1]$ using the following transformation:
\begin{align*}
	\int_a^b{f(x)\diff x}
	&= \frac{b-a}{2}\int_{-1}^{1}{f\left(\frac{b-a}{2}x+\frac{a+b}{2}\right)\diff x}.
\end{align*}
Then, we approximate the integral using the following summation:
\begin{align*}
	\int_{-1}^{1}{f(x)\diff x} &= \sum_{i=1}^{5}{w_if(x_i)},
\end{align*}
where
\begin{multicols}{2}
	\noindent
	\begin{align*}
		w_1 &= 0\\
		w_2 &= \frac{1}{21}\sqrt{245-14\sqrt{70}}\\
		w_3 &= -\frac{1}{21}\sqrt{245-14\sqrt{70}}\\
		w_4 &= \frac{1}{21}\sqrt{245+14\sqrt{70}}\\
		w_5 &= -\frac{1}{21}\sqrt{245+14\sqrt{70}}
	\end{align*}
	\columnbreak
	\begin{align*}
		x_1 &= \frac{128}{225}\\
		x_2 &= \frac{1}{900}\left( 322 + 13\sqrt{70}\right)\\
		x_3 &= \frac{1}{900}\left( 322 + 13\sqrt{70}\right)\\
		x_4 &= \frac{1}{900}\left( 322 - 13\sqrt{70}\right)\\
		x_5 &= \frac{1}{900}\left( 322 - 13\sqrt{70}\right)
	\end{align*}
\end{multicols}
Applying this procedure to the integral in equation \ref{eq:log_integral} yields the following approximation:
\begin{equation}\label{eq:standard_logarithm_quadrature}
	\log(1+x) =
	\frac{137x^5 + 2310x^4 + 9870x^3 + 15120x^2 + 7560x}
	{30x^5 + 900x^4 + 6300x^3 + 16800x^2 + 18900x + 7560}.
\end{equation}
While the closed form approximation presented by Khattri (equation \ref{eq:standard_logarithm_quadrature}) is accurate for values of $x$ near zero, it diverges from $\log{(1+x)}$ significantly for large values of $x$, as shown in figure \ref{fig:standard_logarithm_quadrature}.
\begin{figure}[!ht]
		\centering
		\includegraphics[width=.8\linewidth]{figures/StandardQuadrature.png}
		\caption{Graph of $\log{(1+x)}$ and the approximation in equation \ref{eq:standard_logarithm_quadrature}}
		\label{fig:standard_logarithm_quadrature}
\end{figure}

### 2019-01-16 pcsc-paper/parts/03_exponentialandlogarithmic.tex
Drafted the wordy part
Drafted the intro and RRL for the mini-thesis.

--- 2018-09-24 parts/08_appendices_b_numericalapproximations.tex
@@
-%\section{Thesis Formatting Guidelines}
+\section{Exponential and Logarithmic Functions [WIP]}
 
-%This thesis template in Word document format was created to ensure that you will spend more time generating content for your paper and less time stressing about formatting issues.
-To ensure, however, that your document is truly formatted according to specifications, here are some formatting guidelines which you may use to evaluate your own paper’s formatting.
+% THIS SECTION IS
 
-%\begin{enumerate}
-%\item There should be NO PAGE NUMBERS on the first page of every chapter/section..
-%\item Tables must have NO VERTICAL LINES, as well as NO INNER HORIZONTAL LINES after the table headers.
-%\item Figures and tables are numbered ACCORDING TO CHAPTER NUMBER (e.g. Table 3.1 must be located in Chapter 3, and Figure B.2 is in Appendix B).
-%\item The sequence of front matter must be as follows:
-%    \begin{enumerate}
-%    \item Title Page, in the correct formatting (e.g. Titles must be written in an inverted triangle, in ALL CAPS and boldface)
-%    \item Abstract
-%	\item Table of Contents
-%	\item List of Figures
-%	\item List of Tables
-%	\end{enumerate}
-%\item Upon binding, the front cover must contain the EXACT CONTENT AND FORMAT as that of your thesis’ title page.
-%\end{enumerate}
-\chapter{NUMERICAL APPROXIMATIONS}
-Transcendental functions such as the exponential and logarithmic functions are usually implemented in computer hardware and software libraries using minimax polynomials, which are determined numerically using the Remez algorithm \cite{harrison_computation_1999}.
-However, the Remez algorithm relies on iteratively refining the polynomial coefficients, which requires knowledge of the argument passed to the exponential or logarithmic function.
-
-We cannot directly apply this approach in privacy-preserving image processing as we do not have knowledge of the exact value of the function arguments.
-In order to calculate a function under a  homomorphic cryptosystem, it is necessary to express the function in terms of the homomorphic operations.
-In this section, we discuss approximations for the logarithm ($\log(1+x)$) and power ($x^r$) functions using only addition, subtraction, multiplication, and division operations.
-.
-
-%TODO: Explain why standard methods for transcedental function approximation cannot be applied here.
-%TODO: Include citations for this chapter
-\section{Approximation for $\log(1+x)$}
-We approximate the function $f(x)=\log(1+x)$ using a similar method to that described in
-\cite{khattri_new_2009}.
-We let $x = 1/n$ and consider the integral
-\begin{align*}
-  \int_{n}^{n+1}{\frac{1}{x}\diff x}=\log{\left(1+\frac{1}{n}\right)}.
-\end{align*}
-This integral can be approximated using the five-point Gauss-Legendre quadrature rule, yielding the following approximation:
-\begin{equation}\label{eq:standardquadrature}
-  \log(1+x) =
-  \frac{137x^5 + 2310x^4 + 9870x^3 + 15120x^2 + 7560x}
-  {30x^5 + 900x^4 + 6300x^3 + 16800x^2 + 18900x + 7560}.
-\end{equation}
-While this closed form approximation is accurate for values of $x$ near zero, it diverges from $\log{(1+x)}$ significantly for large values of $x$.
-\begin{figure}[!ht]
-    \centering
-    \includegraphics[width=.6\linewidth,\keepaspectratio]{figures/StandardQuadrature.png}
-    \caption{Graph of $\log{(1+x)}$ and the approximation in equation \ref{eq:standardquadrature}}
-    \label{fig:standardquadrature}
-\end{figure}
-As we only need accuracy for $x \in [0, 255]$, we can scale up the approximation by a constant factor $\alpha$ as follows:
+As we only need accuracy for arguments $x \in [0, 255]$, we can scale the approximation by a constant factor $\alpha$ as follows:
 \begin{align*}
@@
 \end{align}
+Figure \ref{fig:scaledquadrature} is a graph of the absolute error of the scaled approximation and the exact value of $\log{(1+x)}$.
+Using SageMath 8.3, it was numerically determined that the maximum absolute error of this approximation in the range $x\in[0,255]$ is approximately 0.0103315865985758, occurring at $x=255$.
+This is an improvement from the approximation in equation \ref{eq:standardquadrature}, which has a maximum absolute error of 1.19717868468392, similarly occurring at $x=255$.
 
-\section{Approximation for $x^r$}
-To approximate $x^r$ for any $r \in \mathbb{R}$, we rewrite $x^r$ as follows:
+\begin{figure}[!ht]
+    \centering
+    \includegraphics[width=.9\linewidth]{figures/ModifiedQuadratureAbsoluteError.png}
+    \caption{Graph of the absolute error of $\log{(1+x)}$ and the approximation in equation \ref{eq:scaledquadrature}.}
+    \label{fig:scaledquadrature}
+\end{figure}
+
+\subsection{Approximation for $x^\gamma$}
+To approximate $x^\gamma$ for any $\gamma \in \mathbb{R}$, we rewrite $x^\gamma$ as follows:
 \begin{align*}
-  x^\gamma = e^{\log{x^r}} = e^{r\log{x}}.
+  x^\gamma = e^{\log{x^\gamma}} = e^{\gamma\log{x}}.
 \end{align*}

### 2019-01-16 pcsc-paper/parts/06_conclusionreccomendations.tex
Drafted the wordy part
Drafted the intro and RRL for the mini-thesis.

\section{Conclusion [WIP]}
\section{Recommendations [WIP]}

### 2019-01-17 pcsc-paper/parts/02_01_paillier.tex
Added log approximation proof
Log approximation prooooooooof

@@
 \subsubsection{Extending to Floating-Point Numbers}
+\label{sec:fp_operations}
 We can use the following protocol described in \cite{ziad_cryptoimg:_2016}, in order to extend the privacy-preserving integer addition and integer scalar multiplication of Paillier cryptosystem to floating-point numbers.

### 2019-01-17 pcsc-paper/parts/03_exponentialandlogarithmic.tex
Added log approximation proof
Log approximation prooooooooof

@@
-\section{Exponential and Logarithmic Functions [WIP]}
+\section{Exponential and Logarithmic Functions}
+We now present our main contribution in this paper: a general method to improve the general accuracy of the logarithm approximation given by Khattri in \cite{khattri_new_2009} for use in privacy-preserving calculation, provided that accuracy is only required for a specific range.
 
-% THIS SECTION IS
+For this approximation, we assume we only require accurate results in the input range $x \in [0, 255]$.
+This reflects some potential applications such as in logarithm intensity transformations in image processing \cite{gonzalez_digital_2008}.
 
-As we only need accuracy for arguments $x \in [0, 255]$, we can scale the approximation by a constant factor $\alpha$ as follows:
+Since the approximation by Khattri is accurate for values of $x$ near zero, we can scale the approximation by a constant factor $\alpha$ by expressing $\log(1+x)$ as follows:
 \begin{align*}
@@
 	&= \log{\left(\frac{\alpha n + \alpha}{n}\right)} - \log{\alpha}\\
-  &= \int_{n}^{\alpha n + \alpha}{\frac{1}{x}\diff x} - \log{\alpha}
+	&= \int_{n}^{\alpha n + \alpha}{\frac{1}{x}\diff x} - \log{\alpha}.
 \end{align*}
 
-Applying the five-point Gauss-Legendre quadrature rule with $\alpha = 1/20$ using SageMath 8.3, we arrive at the approximation:
-\begin{align}\label{eq:scaledquadrature}
+Applying the five-point Gauss-Legendre quadrature rule to approximate $\int_{n}^{\alpha n + \alpha}{\frac{1}{x}\diff x}$ with $\alpha = 1/16$ using SageMath 8.3, we arrive at the approximation:
+\begin{align}\label{eq:optimal_log_approximation}
 	\begin{split}
 		&\log(1+x) \\
-    &=\frac{137x^5 + 33185x^4 + 931370x^3 - 13403630x^2 - 289469315x - 713567363}
-    {30(x^5 + 505x^4 + 42010x^3 + 923010x^2 + 5722005x + 8040501)} + \log{20}
+		&=\frac{137x^5 + 26685x^4 + 617370x^3 - 6498630x^2 - 121239315x - 257804775}
+		{30(x^5 + 405x^4 + 27210x^3 + 488810x^2 + 2536005x + 3122577)}\\
+		&+ \log{16}
 	\end{split}
 \end{align}
-Figure \ref{fig:scaledquadrature} is a graph of the absolute error of the scaled approximation and the exact value of $\log{(1+x)}$.
-Using SageMath 8.3, it was numerically determined that the maximum absolute error of this approximation in the range $x\in[0,255]$ is approximately 0.0103315865985758, occurring at $x=255$.
-This is an improvement from the approximation in equation \ref{eq:standardquadrature}, which has a maximum absolute error of 1.19717868468392, similarly occurring at $x=255$.
+
+We note that the approximation in equation \ref{eq:optimal_log_approximation} requires the value of $\log{16}$.
+This can be computed in the plaintext domain and added to an encrypted value using the properties of the Paillier cryptosystem.
+The remaining arithmetic operations in the approximation can be computed in the encrypted domain, using the protocols described in section \ref{sec:fp_operations}.
+Therefore, this approximation can be calculated in a privacy-preserving manner.
+
+Figure \ref{fig:log_error_comparison} is a graph comparing the absolute error of the scaled approximation and the original approximation by Khattri given an input $x$.
+We can see that scaling the input by some constant factor $\alpha$ improves the accuracy of the closed-form approximation, although it requires that $\log \alpha$ be known.
 
@@
 		\centering
-    \includegraphics[width=.9\linewidth]{figures/ModifiedQuadratureAbsoluteError.png}
-    \caption{Graph of the absolute error of $\log{(1+x)}$ and the approximation in equation \ref{eq:scaledquadrature}.}
-    \label{fig:scaledquadrature}
+		\includegraphics[width=.9\linewidth]{figures/log_error_comparison.png}
+		\caption{Comparison of the absolute error between the original approximation in equation \ref{eq:standard_logarithm_quadrature} and the scaled approximation in equation \ref{eq:optimal_log_approximation}.}
+		\label{fig:log_error_comparison}
 \end{figure}
 
-\subsection{Approximation for $x^\gamma$}
-To approximate $x^\gamma$ for any $\gamma \in \mathbb{R}$, we rewrite $x^\gamma$ as follows:
+We now show how we used numerical methods to determine that a scaling factor of $\alpha = 1/16$ minimizes the maximum absolute error of the scaled approximation for $\log{(1+x)}$, within the range $x \in [0, 255]$.
+Let the function $I(x,\alpha)$ be the function obtained by approximating $\int_{n}^{\alpha n + \alpha}{\frac{1}{x}\diff x}$ with five-point Gauss-Legendre quadrature.
+The absolute error of the approximation compared to  $\log{(1+x)}$ at a given $x$ and $\alpha$ is given by the following function.
 \begin{align*}
-  x^\gamma = e^{\log{x^\gamma}} = e^{\gamma\log{x}}.
+	A(x,\alpha) = \left| I(x,\alpha) - \log\alpha - \log{(1+x)}\right|.
 \end{align*}
-This expression can then be approximated using the Maclaurin series expansion for $e^x$, which converges for all $x$.
+We want to show that the function
 \begin{align*}
-  e^x &= \sum_{n=0}^{\infty}{\frac{x^n}{n!}}\\
-  \Rightarrow e^{\gamma\log{x}} &= \sum_{n=0}^{\infty}{\frac{(\gamma\log{x})^n}{n!}}
+	f(\alpha) = \max_{0\leq x \leq 255}{A(x,\alpha)}
 \end{align*}
-As we already have an approximation for the natural logarithm, we can evaluate partial sums of the above infinite series to arrive at approximations for $x^\gamma$.
+is minimized at $\alpha = 1/16$.
+We consider the functions $A(0,\alpha)$ and $A(255,\alpha)$. These are graphed in figure \ref{fig:endpoint_plot}.
+
+It can be determined numerically using SageMath 8.3 that a local minimum of $\max(A(0,\alpha),A(255,\alpha))$ on the interval $[0,1]$ is at $\alpha = 1/16$, which is found at the intersection of the two graphs.
+\begin{figure}[!ht]
+		\centering
+		\includegraphics[width=.9\linewidth]{figures/endpoint_plot.png}
+		\caption{Graphs of $A(x,\alpha)$ at $x=0$ and $x=255$.}
+		\label{fig:endpoint_plot}
+\end{figure}
+We then consider the function $A(x,1/16)$, shown in figure \ref{fig:single_alpha_plot}.
+It was determined numerically using SageMath 8.3 that the local maxima of $A(x,1/16)$ on the interval occur at $x=0$ and $x=255$.
+Since a scaling factor other than $alpha=1/16$ yields a higher absolute error at either $x=0$ or $x=255$, as seen in figure \ref{fig:endpoint_plot}, it follows that a scaling factor of $\alpha = 1/16$ minimizes the maximum absolute error of the scaled approximation for $\log{(1+x)}$, within the range $x \in [0, 255]$.
+\begin{figure}[!ht]
+		\centering
+		\includegraphics[width=.9\linewidth]{figures/single_alpha_plot.png}
+		\caption{Graph of $A(x,1/16)$, the absolute error of the approximation in equation \ref{eq:optimal_log_approximation} given a scaling factor of $\alpha=1/16$.}
+		\label{fig:single_alpha_plot}
+\end{figure}
+
+We have shown how we can adapt Khattri's approximation to allow for privacy-preserving logarithm computation over a larger interval.
+We note we only require the quadrature approach if series representations of the desired function are not suitable for privacy-preserving calculation using the floating-point arithmetic supported by the Paillier cryptosystem.
+
+As a concrete example, evaluating partial sums of the series representation for the exponential function
+\begin{align*}
+	e^x = \sum_{n=0}^{\infty}{\frac{x^n}{n!}}
+\end{align*}
+is a valid approach for privacy-preserving computation, as this series converges for all $x$.

### 2019-01-17 pcsc-paper/parts/03_exponentialandlogarithmic.tex
Make integrals in terms of t to avoid confusion
see commit title

@@
 
-Since the approximation by Khattri is accurate for values of $x$ near zero, we can scale the approximation by a constant factor $\alpha$ by expressing $\log(1+x)$ as follows:
+Since the approximation by Khattri is accurate for values of $x$ near zero, we can scale the approximation by a constant factor $\alpha$ by expressing $\log(1+x)$ as follows, similarly using the substitution $x=1/n$:
 \begin{align*}
@@
 	&= \log{\left(\frac{\alpha n + \alpha}{n}\right)} - \log{\alpha}\\
-	&= \int_{n}^{\alpha n + \alpha}{\frac{1}{x}\diff x} - \log{\alpha}.
+	&= \int_{n}^{\alpha n + \alpha}{\frac{1}{t}\diff t} - \log{\alpha}.
 \end{align*}

### 2019-01-17 pcsc-paper/parts/04_inversetrig.tex
Added trig section
Added section about arctan approximation

\section{Inverse Trigonometric Functions}
We will now show how a Gauss-Legendre quadrature approach can also be used for efficient privacy-preserving approximation of the inverse tangent function. Two well-known series representations of the arctangent function exist. The Maclaurin series expansion,
\begin{align} \label{eq:arctan_maclaurin}
	\arctan x = \sum_{n=0}^{\infty}{\frac{(-1)^nx^{2n+1}}{2n+1}}, |x|\leq 1
\end{align}
and the following series expansion discovered by Euler in 1755, which converges more rapidly for all $x$ \cite{chien-lih_89.67_2005}.
\begin{align} \label{eq:arctan_euler}
	\arctan x = \sum_{n=0}^{\infty}
	{
	\frac
		{2^{2n}(n!)^2}
		{(2n+1)!}
	\frac
		{x^{2n+1}}
		{(1+x^2)^{n+1}}
	}
\end{align}
We will compare the quadrature approach with the method of computing partial sums from each of these series.

To obtain a Gauss-Legendre quadrature-based approximation, we take the following integral,
\begin{align*}
	\arctan x = \int_0^x{\frac{1}{1+x^2}\diff x},
\end{align*}
and perform five-point Gauss-Legendre quadrature to obtain the following closed-form approximation:
\begin{align} \label{eq:arctan_quadrature}
	\begin{split}
		&\arctan x \\
		&= \frac
		{4(225x^9 + 15925x^7 + 144753x^5 + 350595x^3 + 238140x)}
		{15(x^{10} + 480x^8 + 11760x^6 + 64120x^4 + 114660x^2 + 63504)}
	\end{split}
\end{align}

We note that in order to evaluate the quadrature approximation in equation \ref{eq:arctan_quadrature}, we must compute the value of $x^{10}$, which requires several rounds of the squaring and multiplication protocols to compute. We now compare the quadrature approximation to the partial sum composed of the first 4 terms of Euler's series expansion in equation \ref{eq:arctan_euler}, which requires a similar number of floating-point operations to compute:
\begin{align} \label{eq:arctan_euler_partial}
	\begin{split}
		&\sum_{n=0}^{3}
		{
		\frac
			{2^{2n}(n!)^2}
			{(2n+1)!}
		\frac
			{x^{2n+1}}
			{(1+x^2)^{n+1}}
		}\\
		&= \frac
		{965x^9 + 2370x^7 + 2688x^5 + 1470x^3 + 315x}
		{315(x^10 + 5x^8 + 10x^6 + 10x^4 + 5x^2 + 1)}
	\end{split}
\end{align}
Figure \ref{fig:arctan_error} shows that despite requiring a similar number of floating-point operations, the quadrature based approximation in equation \ref{eq:arctan_quadrature} gives accurate approximations over a larger interval, making it a more viable candidate for efficient computation.
\begin{figure}[!ht]
		\centering
		\includegraphics[width=.9\linewidth]{figures/single_alpha_plot.png}
		\caption{Comparison of the absolute error of the approximations for $\arctan x$ using quadrature approximation (equation \ref{eq:arctan_quadrature}) and the first 4 terms of Euler's series (equation \ref{eq:arctan_euler_partial})}
		\label{fig:arctan_error}
\end{figure}
Figure \ref{fig:arctan_error_2} shows the absolute error of the quadrature approximation over the interval $[-1,1]$. Since the quadrature approximation yields results with high accuracy over this interval, potential implmentations may use the following trigonometric identities to calculate values of the inverse tangent at larger arguments.
\begin{align*}
	\arctan x =
	\begin{cases}
		\frac{\pi}{2}-\arctan{\frac{1}{x}} & \text{if } x > 0, \\
		-\frac{\pi}{2}-\arctan{\frac{1}{x}} & \text{if } x < 0.
	\end{cases}
\end{align*}
To carry out the conditional check required to use these identities, a privacy-preserving comparison protocol may be used, such as in \cite{veugen_improving_2012}.
\begin{figure}[!ht]
		\centering
		\includegraphics[width=.9\linewidth]{figures/arctan_error_2.png}
		\caption{Absolute error of the approximation for $\arctan x$ using quadrature approximation (equation \ref{eq:arctan_quadrature}) over the interval $[-1,1]$}
		\label{fig:arctan_error_2}
\end{figure}

### 2019-01-18 pcsc-paper/parts/01_introduction.tex
Recreated graphs with pgfplots

@@
 
-Applications of the Paillier cryptosystem have included such as use in linear digital image transformations \cite{ziad_cryptoimg:_2016}, and linear algebra applications \cite{hutchison_privacy-preserving_2009}.
+Applications of the Paillier cryptosystem have included such as use in linear digital image transformations~\cite{ziad_cryptoimg:_2016}, and linear algebra applications~\cite{hutchison_privacy-preserving_2009}.
 However, many extensions to the Paillier cryptosystem have also been published, allowing floating-point arithmetic.
-In this paper, we will summarize these extensions and concern ourselves with the approximation of the transcendental functions using the Paillier cryptosystem given input constraints shown in table \ref{tab:inputconstraints}.
+In this paper, we will summarize these extensions and concern ourselves with the approximation of the transcendental functions using the Paillier cryptosystem given input constraints shown in Table~\ref{tab:inputconstraints}.
 By demonstrating how the Paillier cryptosystem can be applied to approximate common non-linear functions, we hope to extend its usability as a tool for privacy-preserving computation.
 \begin{table}
-	\caption{Summary of Functions [WIP]}
+	\caption{Summary of functions [WIP]}
 	\label{tab:inputconstraints}
@@
 		\toprule
-		Functions & Input Constraints\\
+		Functions & Input constraints\\
 		\midrule

### 2019-01-18 pcsc-paper/parts/02_01_paillier.tex
Recreated graphs with pgfplots

--- 2019-01-16 pcsc-paper/parts/02_01_paillier.tex
@@
 \subsection{The Paillier Cryptosystem}
-The Paillier cryptosystem \cite{stern_public-key_1999}, developed by Pascal Paillier, is a probabilistic encryption scheme which is based on the composite residuosity class problem.
+The Paillier cryptosystem~\cite{stern_public-key_1999}, developed by Pascal Paillier, is a probabilistic encryption scheme which is based on the composite residuosity class problem.
 The scheme allows for the encryption and decryption of integer messages, and is known to be additively homomorphic.
@@
 
-\subsubsection{Extending to Floating-Point Numbers}
-We can use the following protocol described in \cite{ziad_cryptoimg:_2016}, in order to extend the privacy-preserving integer addition and integer scalar multiplication of Paillier cryptosystem to floating-point numbers.
+\subsubsection{Extension to Floating-Point Numbers}
+\label{sec:fp_operations}
+We can use the following protocol described in~\cite{ziad_cryptoimg:_2016}, in order to extend the privacy-preserving integer addition and integer scalar multiplication of Paillier cryptosystem to floating-point numbers.
 
@@
 \subsubsection{Secure Division}
-We can use the following two-party scheme defined in \cite{boukoros_lightweight_2017} to perform privacy-preserving division.
+We can use the following two-party scheme defined in~\cite{boukoros_lightweight_2017} to perform privacy-preserving division.
 Suppose Bob has $E(x)$ and $E(y)$ and wants to obtain $E(x/y)$ without exposing the value of either integer.

### 2019-01-18 pcsc-paper/parts/03_exponentialandlogarithmic.tex
Recreated graphs with pgfplots

@@
 \section{Exponential and Logarithmic Functions}
-We now present our main contribution in this paper: a general method to improve the general accuracy of the logarithm approximation given by Khattri in \cite{khattri_new_2009} for use in privacy-preserving calculation, provided that accuracy is only required for a specific range.
+We now present our main contribution in this paper: a general method to improve the general accuracy of the logarithm approximation given by Khattri in~\cite{khattri_new_2009} for use in privacy-preserving calculation, provided that accuracy is only required for a specific range.
 
 For this approximation, we assume we only require accurate results in the input range $x \in [0, 255]$.
-This reflects some potential applications such as in logarithm intensity transformations in image processing \cite{gonzalez_digital_2008}.
+This reflects some potential applications such as in logarithm intensity transformations in image processing~\cite{gonzalez_digital_2008}.
 
@@
 
-Applying the five-point Gauss-Legendre quadrature rule to approximate $\int_{n}^{\alpha n + \alpha}{\frac{1}{x}\diff x}$ with $\alpha = 1/16$ using SageMath 8.3, we arrive at the approximation:
+Applying the five-point Gauss--Legendre quadrature rule to approximate $\int_{n}^{\alpha n + \alpha}{\frac{1}{x}\diff x}$ with $\alpha = 1/16$ using SageMath 8.3, we arrive at the approximation:
 \begin{align}\label{eq:optimal_log_approximation}
@@
 
-We note that the approximation in equation \ref{eq:optimal_log_approximation} requires the value of $\log{16}$.
+We note that the approximation in Equation~\ref{eq:optimal_log_approximation} requires the value of $\log{16}$.
 This can be computed in the plaintext domain and added to an encrypted value using the properties of the Paillier cryptosystem.
-The remaining arithmetic operations in the approximation can be computed in the encrypted domain, using the protocols described in section \ref{sec:fp_operations}.
+The remaining arithmetic operations in the approximation can be computed in the encrypted domain, using the protocols described in Section~\ref{sec:fp_operations}.
 Therefore, this approximation can be calculated in a privacy-preserving manner.
 
-Figure \ref{fig:log_error_comparison} is a graph comparing the absolute error of the scaled approximation and the original approximation by Khattri given an input $x$.
+Figure~\ref{fig:log_error_comparison} is a graph comparing the absolute error of the scaled approximation and the original approximation by Khattri given an input $x$.
 We can see that scaling the input by some constant factor $\alpha$ improves the accuracy of the closed-form approximation, although it requires that $\log \alpha$ be known.
 
-\begin{figure}[!ht]
+\begin{figure}[ht]
 	\centering
-		\includegraphics[width=.9\linewidth]{figures/log_error_comparison.png}
-		\caption{Comparison of the absolute error between the original approximation in equation \ref{eq:standard_logarithm_quadrature} and the scaled approximation in equation \ref{eq:optimal_log_approximation}.}
+    \begin{tikzpicture}
+		\begin{semilogyaxis}[
+			% height=6cm, width=9cm,
+			xmin=0, xmax=300,
+			ymin=1e-10, ymax=1.4,
+			xlabel={$x$}, ylabel={Absolute error},
+			grid=major,
+			legend pos=south east,
+			legend cell align=left,
+			tick scale binop=\times,
+		]
+		% \addplot[very thick, domain=0:300, samples=500]{abs(-1/30*(x^5*(30*ln(1/16) - 137) + 45*x^4*(270*ln(1/16) - 593) + 30*x^3*(27210*ln(1/16) - 20579) + 30*x^2*(488810*ln(1/16) + 216621) + 45*x*(1690670*ln(1/16) + 2694207) + 93677310*ln(1/16) + 257804775)/(x^5 + 405*x^4 + 27210*x^3 + 488810*x^2 + 2536005*x + 3122577) - ln(x + 1))};
+		% \addplot[very thick, domain=0:300, samples=300]{abs(1/30*(137*x^5 + 26685*x^4 + 617370*x^3 - 6498630*x^2 - 121239315*x - 257804775)/(x^5 + 405*x^4 + 27210*x^3 + 488810*x^2 + 2536005*x + 3122577) - ln(1/16) - ln(x + 1))};
+		\addplot[very thick] table[x=x, y=error] {plots/abs_err_scaledlog.txt};
+		\addplot[densely dashed, domain=0:300, samples=100]{abs(1/30*(137*x^5 + 2310*x^4 + 9870*x^3 + 15120*x^2 + 7560*x)/(x^5 + 30*x^4 + 210*x^3 + 560*x^2 + 630*x + 252) - ln(x + 1))};
+		\legend{scaled ($\alpha = 1/16$), original ($\alpha = 1$)}
+	\end{semilogyaxis}
+	\end{tikzpicture}%
+	\caption{Comparison of the absolute error between the original approximation in Equation~\ref{eq:standard_logarithm_quadrature} and the scaled approximation in Equation~\ref{eq:optimal_log_approximation}}
 	\label{fig:log_error_comparison}
@@
 We now show how we used numerical methods to determine that a scaling factor of $\alpha = 1/16$ minimizes the maximum absolute error of the scaled approximation for $\log{(1+x)}$, within the range $x \in [0, 255]$.
-Let the function $I(x,\alpha)$ be the function obtained by approximating $\int_{n}^{\alpha n + \alpha}{\frac{1}{x}\diff x}$ with five-point Gauss-Legendre quadrature.
+Let $I(x,\alpha)$ be the function obtained by approximating $\int_{n}^{\alpha n + \alpha}{\frac{1}{x}\diff x}$ with five-point Gauss--Legendre quadrature.
 The absolute error of the approximation compared to  $\log{(1+x)}$ at a given $x$ and $\alpha$ is given by the following function.
@@
 \end{align*}
+
 We want to show that the function
@@
 is minimized at $\alpha = 1/16$.
-We consider the functions $A(0,\alpha)$ and $A(255,\alpha)$. These are graphed in figure \ref{fig:endpoint_plot}.
+We consider the functions $A(0,\alpha)$ and $A(255,\alpha)$. These are plotted in Figure~\ref{fig:endpoint_plot}.
 
@@
 	\centering
-		\includegraphics[width=.9\linewidth]{figures/endpoint_plot.png}
-		\caption{Graphs of $A(x,\alpha)$ at $x=0$ and $x=255$.}
+    \begin{tikzpicture}
+		\begin{axis}[
+			% height=6cm, width=9cm,
+			xmin=0, xmax=1,
+			ymin=0, ymax=1.3,
+			xlabel={$\alpha$}, ylabel={Absolute error},
+			grid=major,
+			legend pos=south east,
+			legend cell align=left,
+			tick scale binop=\times,
+		]
+		\addplot[ACMDarkBlue, domain=0:1, samples=200]{1/30*abs((137*x^5 + 1625*x^4 + 2000*x^3 - 2000*x^2 - 30*(x^5 + 25*x^4 + 100*x^3 + 100*x^2 + 25*x + 1)*ln(x) - 1625*x - 137)/(x^5 + 25*x^4 + 100*x^3 + 100*x^2 + 25*x + 1))};
+		\addplot[ACMOrange, domain=0:1, samples=200]{abs(-1/30*(32346117281250*x^5*ln(x) - 150633093005312*x^5 - 6979321856000*x^4 - 33554432000*x^3 + 131072000*x^2 + 30*(x^5 + 25*x^4 + 100*x^3 + 100*x^2 + 25*x + 1)*ln(x) + 38250*(x^5 + 20*x^4 + 60*x^3 + 40*x^2 + 5*x)*ln(x) + 19507500*(x^5 + 15*x^4 + 30*x^3 + 10*x^2)*ln(x) + 4974412500*(x^5 + 10*x^4 + 10*x^3)*ln(x) + 634237593750*(x^5 + 5*x^4)*ln(x) + 416000*x + 137)/(1099511627776*x^5 + 107374182400*x^4 + 1677721600*x^3 + 6553600*x^2 + 6400*x + 1) - 8*ln(2))};
+		\legend{$x=0$, $x=255$}
+	\end{axis}
+	\end{tikzpicture}%
+	\caption{Graphs of $A(x,\alpha)$ at $x=0$ and $x=255$}
 	\label{fig:endpoint_plot}
 \end{figure}
-We then consider the function $A(x,1/16)$, shown in figure \ref{fig:single_alpha_plot}.
+We then consider the function $A(x,1/16)$, shown in Figure~\ref{fig:single_alpha_plot}.
 It was determined numerically using SageMath 8.3 that the local maxima of $A(x,1/16)$ on the interval occur at $x=0$ and $x=255$.
-Since a scaling factor other than $alpha=1/16$ yields a higher absolute error at either $x=0$ or $x=255$, as seen in figure \ref{fig:endpoint_plot}, it follows that a scaling factor of $\alpha = 1/16$ minimizes the maximum absolute error of the scaled approximation for $\log{(1+x)}$, within the range $x \in [0, 255]$.
-\begin{figure}[!ht]
+Since a scaling factor other than $\alpha=1/16$ yields a higher absolute error at either $x=0$ or $x=255$, as seen in Figure~\ref{fig:endpoint_plot}, it follows that a scaling factor of $\alpha = 1/16$ minimizes the maximum absolute error of the scaled approximation for $\log{(1+x)}$, within the range $x \in [0, 255]$.
+\begin{figure}[ht]
 	\centering
-		\includegraphics[width=.9\linewidth]{figures/single_alpha_plot.png}
-		\caption{Graph of $A(x,1/16)$, the absolute error of the approximation in equation \ref{eq:optimal_log_approximation} given a scaling factor of $\alpha=1/16$.}
+	\begin{tikzpicture}
+		\begin{axis}[
+			xmin=0, xmax=300,
+			ymin=0, ymax=0.035,
+			xlabel={$x$}, ylabel={Absolute error},
+			grid=major,
+			legend pos=south east,
+			legend cell align=left,
+			tick scale binop=\times,
+		]
+		% \addplot[very thick, domain=0:300, samples=300]{abs(1/30*(137*x^5 + 26685*x^4 + 617370*x^3 - 6498630*x^2 - 121239315*x - 257804775)/(x^5 + 405*x^4 + 27210*x^3 + 488810*x^2 + 2536005*x + 3122577) - ln(1/16) - ln(x + 1))};
+		\addplot[very thick] table[x=x, y=error] {plots/abs_err_scaledlog.txt};
+	\end{axis}
+	\end{tikzpicture}%
+	\caption{Graph of $A(x,1/16)$, the absolute error of the approximation in Equation~\ref{eq:optimal_log_approximation} given a scaling factor of $\alpha=1/16$}
 	\label{fig:single_alpha_plot}

### 2019-01-18 pcsc-paper/parts/04_inversetrig.tex
Recreated graphs with pgfplots

@@
 \section{Inverse Trigonometric Functions}
-We will now show how a Gauss-Legendre quadrature approach can also be used for efficient privacy-preserving approximation of the inverse tangent function.
-Two well-known series representations of the arctangent function exist.
-The Maclaurin series expansion,
+We will now show how a Gauss--Legendre quadrature approach can also be used for efficient privacy-preserving approximation of the inverse tangent function.
+Two well-known series representations of the arctangent function exist: the Maclaurin series expansion,
 \begin{align} \label{eq:arctan_maclaurin}
-	\arctan x = \sum_{n=0}^{\infty}{\frac{(-1)^nx^{2n+1}}{2n+1}}, |x|\leq 1
+	\arctan x = \sum_{n=0}^{\infty}{\frac{(-1)^nx^{2n+1}}{2n+1}}, \text{ for }|x|\leq 1
 \end{align}
-and the following series expansion discovered by Euler in 1755, which converges more rapidly for all $x$ \cite{chien-lih_89.67_2005}.
+and the following series expansion discovered by Euler in 1755, which converges more rapidly for all $x$~\cite{chien-lih_89.67_2005}.
 \begin{align} \label{eq:arctan_euler}
@@
 
-To obtain a Gauss-Legendre quadrature-based approximation, we take the following integral,
+To obtain a Gauss--Legendre quadrature-based approximation, we take the following integral,
 \begin{align*}
@@
 \end{align*}
-and perform five-point Gauss-Legendre quadrature to obtain the following closed-form approximation:
+and perform five-point Gauss--Legendre quadrature to obtain the following closed-form approximation:
 \begin{align} \label{eq:arctan_quadrature}
@@
 		&= \frac
-		{4(225x^9 + 15925x^7 + 144753x^5 + 350595x^3 + 238140x)}
-		{15(x^{10} + 480x^8 + 11760x^6 + 64120x^4 + 114660x^2 + 63504)}
+		{4\left(225x^9 + 15925x^7 + 144753x^5 + 350595x^3 + 238140x\right)}
+		{15\left(x^{10} + 480x^8 + 11760x^6 + 64120x^4 + 114660x^2 + 63504\right)}
 	\end{split}
@@
 
-We note that in order to evaluate the quadrature approximation in equation \ref{eq:arctan_quadrature}, we must compute the value of $x^{10}$, which requires several rounds of the squaring and multiplication protocols to compute.
-We now compare the quadrature approximation to the partial sum composed of the first 4 terms of Euler's series expansion in equation \ref{eq:arctan_euler}, which requires a similar number of floating-point operations to compute:
+We note that in order to evaluate the quadrature approximation in Equation~\ref{eq:arctan_quadrature}, we must compute the value of $x^{10}$, which requires several rounds of the squaring and multiplication protocols to compute.
+We now compare the quadrature approximation to the partial sum composed of the first 4 terms of Euler's series expansion in Equation~\ref{eq:arctan_euler}, which requires a similar number of floating-point operations to compute:
 \begin{align} \label{eq:arctan_euler_partial}
@@
 		{965x^9 + 2370x^7 + 2688x^5 + 1470x^3 + 315x}
-		{315(x^10 + 5x^8 + 10x^6 + 10x^4 + 5x^2 + 1)}
+		{315\left(x^{10} + 5x^8 + 10x^6 + 10x^4 + 5x^2 + 1\right)}
 	\end{split}
 \end{align}
-Figure \ref{fig:arctan_error} shows that despite requiring a similar number of floating-point operations, the quadrature based approximation in equation \ref{eq:arctan_quadrature} gives accurate approximations over a larger interval, making it a more viable candidate for efficient computation.
+
+Figure~\ref{fig:arctan_error} shows that despite requiring a similar number of floating-point operations, the quadrature based approximation in Equation~\ref{eq:arctan_quadrature} gives accurate approximations over a larger interval, making it a more viable candidate for efficient computation.
 \begin{figure}[!ht]
@@
 		\includegraphics[width=.9\linewidth]{figures/single_alpha_plot.png}
-		\caption{Comparison of the absolute error of the approximations for $\arctan x$ using quadrature approximation (equation \ref{eq:arctan_quadrature}) and the first 4 terms of Euler's series (equation \ref{eq:arctan_euler_partial})}
+		\caption{Comparison of the absolute error of the approximations for $\arctan x$ using quadrature approximation (Equation~\ref{eq:arctan_quadrature}) and the first 4 terms of Euler's series (Equation~\ref{eq:arctan_euler_partial})}
 		\label{fig:arctan_error}
 \end{figure}
-Figure \ref{fig:arctan_error_2} shows the absolute error of the quadrature approximation over the interval $[-1,1]$.
+
+Figure~\ref{fig:arctan_error_2} shows the absolute error of the quadrature approximation over the interval $[-1,1]$.
 Since the quadrature approximation yields results with high accuracy over this interval, potential implmentations may use the following trigonometric identities to calculate values of the inverse tangent at larger arguments.
@@
 	\begin{cases}
-		\frac{\pi}{2}-\arctan{\frac{1}{x}} & \text{if } x > 0, \\
-		-\frac{\pi}{2}-\arctan{\frac{1}{x}} & \text{if } x < 0.
+		\frac{\pi}{2}-\arctan{\frac{1}{x}} & \text{if } x > 0 \\
+		-\frac{\pi}{2}-\arctan{\frac{1}{x}} & \text{if } x < 0 
 	\end{cases}
 \end{align*}
-To carry out the conditional check required to use these identities, a privacy-preserving comparison protocol may be used, such as in \cite{veugen_improving_2012}.
+
+To carry out the conditional check required to use these identities, a privacy-preserving comparison protocol may be used, such as in~\cite{veugen_improving_2012}.
 \begin{figure}[!ht]
@@
 		\includegraphics[width=.9\linewidth]{figures/arctan_error_2.png}
-		\caption{Absolute error of the approximation for $\arctan x$ using quadrature approximation (equation \ref{eq:arctan_quadrature}) over the interval $[-1,1]$}
+		\caption{Absolute error of the approximation for $\arctan x$ using quadrature approximation (Equation~\ref{eq:arctan_quadrature}) over the interval $[-1,1]$}
 		\label{fig:arctan_error_2}

### 2019-01-18 pcsc-paper/parts/05_testsforaccuracy.tex

\section{Experiments on Accuracy}
We implemented privacy-preserving floating-point arithmetic using the system described in section \ref{sec:fp_operations}, using the python-paillier library (\url{https://github.com/n1analytics/python-paillier}) on Python 3.

\subsection{Logarithm approximation}
We then computed $\log(1+x)$ for various encrypted inputs using both the original quadrature formula by Khattri (equation \ref{eq:standard_logarithm_quadrature}) and our scaled approximation (equation \ref{eq:optimal_log_approximation}). These were compared with the values returned by the built-in logarithm function in Python 3. Several data points are shown in table \ref{tab:log_approximation}.

We note that the privacy-preserving floating-point arithmetic resulted in some degree of floating-point error, as the observed floating point error in table \ref{tab:log_approximation} is greater than the raw absolute error observed in figure \ref{fig:log_error_comparison}. However, it can still be seen that the error of the scaled approximation is less than that of the original approximation for large inputs.
\begin{table}
	\caption{Comparison of Logarithm Approximation Error under Paillier}
	\label{tab:log_approximation}
	\begin{tabular}{ccc}
		\toprule
		Input & Original quadrature & Scaled quadrature\\
		\midrule
		$\log(1)$ & $0$ & $2.053729 \times 10^{-2}$\\
		$\log(10)$ & $2.833179 \times 10^{-2} $ & $2.280124 \times 10^{-1}$\\
		$\log(50)$ & $2.170779 \times 10^{-2}$ & $2.437148 \times 10^{-2}$\\
		$\log(100)$ & $3.524916 \times 10^{-1}$ & $2.122159 \times 10^{-2}$\\
		$\log(200)$ & $8.859869 \times 10^{-1}$ & $1.441611 \times 10^{-1}$\\
		$\log(256)$ & $1.098463 \times 10^{0}$ & $1.993136 \times 10^{-1}$\\
	\bottomrule
\end{tabular}
\end{table}

\subsection{Inverse tangent approximation}
We also computed $\arctan x$ using for various encrypted inputs using both the first four terms of Euler's series for the arctangent (equation \ref{eq:arctan_euler_partial}) and our quadrature approximation (equation \ref{eq:arctan_quadrature}). These were compared with the values returned by the built-in arctangent function in Python 3.We show several data points in table \ref{tab:arctan_approximation}. Similar to the logarithm approximations, we note that there is a degree of floating-point error compared to that predicted by figure \ref{fig:arctan_error}, but the quadrature approach obtains higher accuracy despite requiring a similar number of floating-point operations to execute.

\begin{table}
	\caption{Comparison of Inverse Tangent Approximation Error under Paillier}
	\label{tab:arctan_approximation}
	\begin{tabular}{ccc}
		\toprule
		Input & Partial sum of infinite series & Quadrature\\
		\midrule
		$\arctan -1$ & $6.564089 \times 10^{-1}$ & $4.629557 \times 10^{-1}$\\
		$\arctan -0.1$ & $4.523405 \times 10^{-3}$ & $1.451929 \times 10^{-3}$\\
		$\arctan -0.01$ & $4.665260 \times 10^{-6}$ & $1.472027 \times 10^{-6}$\\
		$\arctan 0$ & $0$ & $0$\\
		$\arctan 0.01$ & $4.665228 \times 10^{-6}$ & $1.472020 \times 10^{-6}$\\
		$\arctan 0.1$ & $4.523405 \times 10^{-3} $ & $1.451929 \times 10^{-3}$\\
		$\arctan 1$ & $6.564089 \times 10^{-1} $ & $4.629557 \times 10^{-1}$\\
	\bottomrule
\end{tabular}
\end{table}

### 2019-01-18 pcsc-paper/parts/06_conclusionreccomendations.tex

@@
-\section{Conclusion [WIP]}
-\section{Recommendations [WIP]}
+\section{Conclusion}
+We have shown new closed-form approximations to the logarithm and arctangent functions and showed how they can be implemented together with the Paillier cryptosystem to allow for privacy-preserving function calculation.
+We have compared our approach to other closed-form approximations which require a similar number of secure arithmetic operations to evaluate, and have shown our new approximation procedures can yield more accurate results over larger ranges of inputs.
+
+\section{Recommendations}
+Further research can be done regarding implementation of other transcendental functions, either by using known infinite series, or by using identities with the quadrature-based approximations we have presented in this paper.
+Furthermore, testing with other types of homomorphic cryptosystems can be done, to potentially reduce noise encountered in secure floating-point operations.

### 2019-01-18 pcsc-paper/parts/02_02_approximation.tex
Added log approximation proof
Log approximation prooooooooof
Make integrals in terms of t to avoid confusion
see commit title

@@
 Many methods to compute transcendental functions implemented in computer hardware and software libraries rely on direct knowledge of the function arguments.
-Several such approaches include using the CORDIC (coordinate rotation digital computer), pseudo-division and pseudo-multiplication algorithms \cite{walther_cordic_2000}, as well as using minimax polynomials, which are determined numerically using the Remez algorithm \cite{harrison_computation_1999}.
+Several such approaches include using CORDIC (coordinate rotation digital computer), pseudo-division and pseudo-multiplication algorithms~\cite{walther_cordic_2000}, as well as using minimax polynomials, which are determined numerically using the Remez algorithm~\cite{harrison_computation_1999}.
 These algorithms, while efficient, rely on table lookups, which cannot be done in a privacy-preserving system where the function arguments cannot be directly determined.
@@
 While also in common use, not all Taylor series expansions have a convenient radius of convergence.
-To circumvent this, we can rely on an approach presented by Khattri in \cite{khattri_new_2009} to obtain closed form approximations to functions by approximating related integrals.
+To circumvent this, we can rely on an approach presented by Khattri in~\cite{khattri_new_2009} to obtain closed form approximations to functions by approximating related integrals.
 
@@
 	\label{eq:log_integral}
-	\int_{n}^{n+1}{\frac{1}{x}\diff x}=\log{\left(1+\frac{1}{n}\right)}.
+	\int_{n}^{n+1}{\frac{1}{t}\diff t}=\log{\left(1+\frac{1}{n}\right)}.
 \end{align}
 
-This integral can be approximated using the five-point Gauss-Legendre quadrature rule \cite{kythe_quadrature_2002}.
+This integral can be approximated using the five-point Gauss--Legendre quadrature rule~\cite{kythe_quadrature_2002}.
 We first convert the integral to an integral over the interval $[-1,1]$ using the following transformation:
@@
 \end{multicols}
-Applying this procedure to the integral in equation \ref{eq:log_integral} yields the following approximation:
+Applying this procedure to the integral in Equation~\ref{eq:log_integral} yields the following approximation:
 \begin{equation}\label{eq:standard_logarithm_quadrature}
@@
 \end{equation}
-While the closed form approximation presented by Khattri (equation \ref{eq:standard_logarithm_quadrature}) is accurate for values of $x$ near zero, it diverges from $\log{(1+x)}$ significantly for large values of $x$, as shown in figure \ref{fig:standard_logarithm_quadrature}.
+
+While the closed form approximation presented by Khattri (Equation~\ref{eq:standard_logarithm_quadrature}) is accurate for values of $x$ near zero, it diverges from $\log{(1+x)}$ significantly for large values of $x$, as shown in Figure~\ref{fig:standard_logarithm_quadrature}.
 \begin{figure}[!ht]
 	\centering
-		\includegraphics[width=.8\linewidth]{figures/StandardQuadrature.png}
-		\caption{Graph of $\log{(1+x)}$ and the approximation in equation \ref{eq:standard_logarithm_quadrature}}
+	\begin{tikzpicture}
+		\begin{axis}[
+			% height=6cm, width=9cm,
+			xmin=0, xmax=300,
+			ymin=0, ymax=5.5, ytick={0,...,6},
+			xlabel={$x$}, ylabel={$y$},
+			grid=major,
+			legend pos=south east,
+			legend cell align=left,
+		]
+		\addplot[very thick, domain=0:300, samples=100]{1/30*(137*x^5 + 2310*x^4 + 9870*x^3 + 15120*x^2 + 7560*x)/(x^5 + 30*x^4 + 210*x^3 + 560*x^2 + 630*x + 252)};
+		\addplot[densely dashed, domain=0:300, samples=100]{ln(x)};
+		\legend{5-point quadrature approximation, Actual value of $\log(1+x)$}
+		\end{axis}
+	\end{tikzpicture}%
+	\caption{Graph of $\log{(1+x)}$ and the approximation in Equation~\ref{eq:standard_logarithm_quadrature}}
 	\label{fig:standard_logarithm_quadrature}
 \end{figure}
+
+However, the quadrature approach presented by Khattri allows us to approximate the logarithm in a larger range than is possible with the Taylor series, as the Taylor series of $\log(1+x)$ has an interval of convergence of $[-1,1]$.

### 2019-01-18 pcsc-paper/parts/00_abstract.tex
Paper almost finished

This paper presents methods to securely compute transcendental functions such as the natural logarithm and the inverse tangent function within a homomorphic cryptosystem.
First, an extension to the Paillier cryptosystem that allows operations on floating-point numbers is presented. 
Second, protocols using a two-party scheme are described for secure multiplication, division, and exponentiation, in order for such operations to be supported by a partially homomorphic cryptosystem such as the Paillier cryptosystem, where these operations are theoretically infeasible to do under a single-party system.
Finally, new closed-form approximations to the logarithm and the inverse tangent functions are derived using the Gauss--Legendre quadrature, which yield more accurate results than other closed-form approximations that involve a similar number of secure operations.

### 2019-01-18 pcsc-paper/parts/02_01_paillier.tex
Added experiments
We have a mini-thesis na
Paper almost finished

@@
 \begin{align*}
-	D(c) = L(c^\lambda \bmod n^2) \times (L(g^\lambda \bmod n^2))^{-1} \mod n.
+	D(c) = L\left(c^\lambda \bmod n^2\right) \cdot \left(L\left(g^\lambda \bmod n^2\right)\right)^{-1} \mod n.
 \end{align*}
 \subsubsection{Homomorphic Properties of the Paillier Cryptosystem}
-The Paillier cryptosystem supports additive homomorphism as well as the multiplication of a plaintext scalar to an encrypted message. These operations are defined as follows. These properties are used
+The Paillier cryptosystem supports additive homomorphism as well as the multiplication of a plaintext scalar to an encrypted message.
+age.
+These homomorphic properties are used to add a plaintex scalar to a ciphertext, add two ciphertexts, and multiply a ciphertext by a plaintext scalar, respectively.
+They are defined as follows.
+
 For all $m_1,m_2 \in \mathbb{Z}_n$ and $k\in \mathbb{N}$, the following homomorphic properties hold.
@@
 \subsection{Floating-Point Arithmetic}
+\label{sec:fp_operations}
 The Paillier cryptosystem encrypts integers and allows operations on these integers.

### 2019-01-18 pcsc-paper/parts/02_02_approximation.tex
Paper almost finished

@@
 Many methods to compute transcendental functions implemented in computer hardware and software libraries rely on direct knowledge of the function arguments.
-Several such approaches include using CORDIC (coordinate rotation digital computer), pseudo-division and pseudo-multiplication algorithms~\cite{walther_cordic_2000}, as well as using minimax polynomials, which are determined numerically using the Remez algorithm~\cite{harrison_computation_1999}.
+Several such approaches include CORDIC (coordinate rotation digital computer), pseudo-division and pseudo-multiplication algorithms~\cite{walther_cordic_2000}, as well as minimax polynomials, which are determined numerically using the Remez algorithm~\cite{harrison_computation_1999}.
 These algorithms, while efficient, rely on table lookups, which cannot be done in a privacy-preserving system where the function arguments cannot be directly determined.
@@
 While also in common use, not all Taylor series expansions have a convenient radius of convergence.
-To circumvent this, we can rely on an approach presented by Khattri in~\cite{khattri_new_2009} to obtain closed form approximations to functions by approximating related integrals.
+To circumvent this, we can rely on an approach presented by Khattri in~\cite{khattri_new_2009} to obtain closed-form approximations to functions by approximating related integrals.
 
-Khattri presents the following method to approximate the function $f(x)=\log(1+x)$.
+Khattri presents the following method to approximate the function $f(x)=\log\left(1+x\right)$.
 Let $x = 1/n$ and consider the integral
@@
 \begin{align*}
-	\int_{-1}^{1}{f(x)\diff x} &= \sum_{i=1}^{5}{w_if(x_i)},
+	\int_{-1}^{1}{f\left(x\right)\diff x} &= \sum_{i=1}^{5}{w_i f\left(x_i\right)},
 \end{align*}
@@
 \begin{equation}\label{eq:standard_logarithm_quadrature}
-	\log(1+x) =
+	\log\left(1+x\right) \approx
 	\frac{137x^5 + 2310x^4 + 9870x^3 + 15120x^2 + 7560x}
@@
 
-While the closed form approximation presented by Khattri (Equation~\ref{eq:standard_logarithm_quadrature}) is accurate for values of $x$ near zero, it diverges from $\log{(1+x)}$ significantly for large values of $x$, as shown in Figure~\ref{fig:standard_logarithm_quadrature}.
+While the closed-form approximation presented by Khattri (Equation~\ref{eq:standard_logarithm_quadrature}) is accurate for values of $x$ near zero, it diverges from $\log{\left(1+x\right)}$ significantly for large values of $x$, as shown in Figure~\ref{fig:standard_logarithm_quadrature}.
 \begin{figure}[!ht]
@@
 		]
-		\addplot[very thick, domain=0:300, samples=100]{1/30*(137*x^5 + 2310*x^4 + 9870*x^3 + 15120*x^2 + 7560*x)/(x^5 + 30*x^4 + 210*x^3 + 560*x^2 + 630*x + 252)};
+		\addplot[very thick, ACMDarkBlue, domain=0:300, samples=100]{1/30*(137*x^5 + 2310*x^4 + 9870*x^3 + 15120*x^2 + 7560*x)/(x^5 + 30*x^4 + 210*x^3 + 560*x^2 + 630*x + 252)};
 		\addplot[densely dashed, domain=0:300, samples=100]{ln(x)};
@@
 	\end{tikzpicture}%
-	\caption{Graph of $\log{(1+x)}$ and the approximation in Equation~\ref{eq:standard_logarithm_quadrature}}
+	\caption{Graph of $\log{\left(1+x\right)}$ and the approximation in Equation~\ref{eq:standard_logarithm_quadrature}}
 	\label{fig:standard_logarithm_quadrature}
@@
 
-However, the quadrature approach presented by Khattri allows us to approximate the logarithm in a larger range than is possible with the Taylor series, as the Taylor series of $\log(1+x)$ has an interval of convergence of $[-1,1]$.
+However, the quadrature approach presented by Khattri allows us to approximate the logarithm in a larger range than is possible with the Taylor series, as the Taylor series of $\log\left(1+x\right)$ has an interval of convergence of $[-1,1]$.

### 2019-01-18 pcsc-paper/parts/03_exponentialandlogarithmic.tex
Paper almost finished

@@
 		&\log(1+x) \\
-		&=\frac{137x^5 + 26685x^4 + 617370x^3 - 6498630x^2 - 121239315x - 257804775}
+		&\approx \frac{137x^5 + 26685x^4 + 617370x^3 - 6498630x^2 - 121239315x - 257804775}
 		{30(x^5 + 405x^4 + 27210x^3 + 488810x^2 + 2536005x + 3122577)}\\
@@
 		% \addplot[very thick, domain=0:300, samples=300]{abs(1/30*(137*x^5 + 26685*x^4 + 617370*x^3 - 6498630*x^2 - 121239315*x - 257804775)/(x^5 + 405*x^4 + 27210*x^3 + 488810*x^2 + 2536005*x + 3122577) - ln(1/16) - ln(x + 1))};
-		\addplot[very thick] table[x=x, y=error] {plots/abs_err_scaledlog.txt};
+		\addplot[very thick, ACMDarkBlue] table[x=x, y=error] {plots/abs_err_scaledlog.txt};
 		\addplot[densely dashed, domain=0:300, samples=100]{abs(1/30*(137*x^5 + 2310*x^4 + 9870*x^3 + 15120*x^2 + 7560*x)/(x^5 + 30*x^4 + 210*x^3 + 560*x^2 + 630*x + 252) - ln(x + 1))};
-		\legend{scaled ($\alpha = 1/16$), original ($\alpha = 1$)}
+		\legend{Scaled quadrature ($\alpha = 1/16$), Original quadrature ($\alpha = 1$)}
 	\end{semilogyaxis}
@@
     \begin{tikzpicture}
-		\begin{axis}[
+		\begin{semilogyaxis}[
 			% height=6cm, width=9cm,
 			xmin=0, xmax=1,
-			ymin=0, ymax=1.3,
+			ymin=5e-7, ymax=1.3,
 			xlabel={$\alpha$}, ylabel={Absolute error},
 			grid=major,
+			extra x ticks={1/16},
+			extra x tick labels={$\frac{1}{16}$},
 			legend pos=south east,
@@
 		]
-		\addplot[ACMDarkBlue, domain=0:1, samples=200]{1/30*abs((137*x^5 + 1625*x^4 + 2000*x^3 - 2000*x^2 - 30*(x^5 + 25*x^4 + 100*x^3 + 100*x^2 + 25*x + 1)*ln(x) - 1625*x - 137)/(x^5 + 25*x^4 + 100*x^3 + 100*x^2 + 25*x + 1))};
-		\addplot[ACMOrange, domain=0:1, samples=200]{abs(-1/30*(32346117281250*x^5*ln(x) - 150633093005312*x^5 - 6979321856000*x^4 - 33554432000*x^3 + 131072000*x^2 + 30*(x^5 + 25*x^4 + 100*x^3 + 100*x^2 + 25*x + 1)*ln(x) + 38250*(x^5 + 20*x^4 + 60*x^3 + 40*x^2 + 5*x)*ln(x) + 19507500*(x^5 + 15*x^4 + 30*x^3 + 10*x^2)*ln(x) + 4974412500*(x^5 + 10*x^4 + 10*x^3)*ln(x) + 634237593750*(x^5 + 5*x^4)*ln(x) + 416000*x + 137)/(1099511627776*x^5 + 107374182400*x^4 + 1677721600*x^3 + 6553600*x^2 + 6400*x + 1) - 8*ln(2))};
+		% \addplot[thick, ACMDarkBlue, domain=0:1, samples=200]{1/30*abs((137*x^5 + 1625*x^4 + 2000*x^3 - 2000*x^2 - 30*(x^5 + 25*x^4 + 100*x^3 + 100*x^2 + 25*x + 1)*ln(x) - 1625*x - 137)/(x^5 + 25*x^4 + 100*x^3 + 100*x^2 + 25*x + 1))};
+		% \addplot[thick, ACMOrange, domain=0:1, samples=200]{abs(-1/30*(32346117281250*x^5*ln(x) - 150633093005312*x^5 - 6979321856000*x^4 - 33554432000*x^3 + 131072000*x^2 + 30*(x^5 + 25*x^4 + 100*x^3 + 100*x^2 + 25*x + 1)*ln(x) + 38250*(x^5 + 20*x^4 + 60*x^3 + 40*x^2 + 5*x)*ln(x) + 19507500*(x^5 + 15*x^4 + 30*x^3 + 10*x^2)*ln(x) + 4974412500*(x^5 + 10*x^4 + 10*x^3)*ln(x) + 634237593750*(x^5 + 5*x^4)*ln(x) + 416000*x + 137)/(1099511627776*x^5 + 107374182400*x^4 + 1677721600*x^3 + 6553600*x^2 + 6400*x + 1) - 8*ln(2))};
+		\addplot[thick, ACMDarkBlue, domain=0:1] table[x=alpha, y=x0] {plots/abs_err_sl_0_255.txt};
+		\addplot[thick, ACMOrange, domain=0:1] table[x=alpha, y=x255] {plots/abs_err_sl_0_255.txt};
 		\legend{$x=0$, $x=255$}
-	\end{axis}
+	\end{semilogyaxis}
 	\end{tikzpicture}%
@@
 We then consider the function $A(x,1/16)$, shown in Figure~\ref{fig:single_alpha_plot}.
-It was determined numerically using SageMath 8.3 that the local maxima of $A(x,1/16)$ on the interval occur at $x=0$ and $x=255$.
+It was determined numerically that the local maxima of $A(x,1/16)$ on the interval occur at $x=0$ and $x=255$.
 Since a scaling factor other than $\alpha=1/16$ yields a higher absolute error at either $x=0$ or $x=255$, as seen in Figure~\ref{fig:endpoint_plot}, it follows that a scaling factor of $\alpha = 1/16$ minimizes the maximum absolute error of the scaled approximation for $\log{(1+x)}$, within the range $x \in [0, 255]$.
@@
 	\begin{tikzpicture}
-		\begin{axis}[
+		\begin{semilogyaxis}[
 			xmin=0, xmax=300,
-			ymin=0, ymax=0.035,
+			ymin=1e-15, ymax=0.035,
 			xlabel={$x$}, ylabel={Absolute error},
@@
 		% \addplot[very thick, domain=0:300, samples=300]{abs(1/30*(137*x^5 + 26685*x^4 + 617370*x^3 - 6498630*x^2 - 121239315*x - 257804775)/(x^5 + 405*x^4 + 27210*x^3 + 488810*x^2 + 2536005*x + 3122577) - ln(1/16) - ln(x + 1))};
-		\addplot[very thick] table[x=x, y=error] {plots/abs_err_scaledlog.txt};
-	\end{axis}
+		\addplot[thick, ACMDarkBlue] table[x=x, y=error] {plots/abs_err_scaledlog.txt};
+	\end{semilogyaxis}
 	\end{tikzpicture}%

### 2019-01-18 pcsc-paper/parts/04_inversetrig.tex
Paper almost finished

@@
 \begin{align*}
-	\arctan x = \int_0^x{\frac{1}{1+x^2}\diff x},
+	\arctan x = \int_0^x{\frac{1}{1+t^2}\diff t},
 \end{align*}
@@
 		&\arctan x \\
-		&= \frac
+		&\approx \frac
 		{4\left(225x^9 + 15925x^7 + 144753x^5 + 350595x^3 + 238140x\right)}
@@
 We note that in order to evaluate the quadrature approximation in Equation~\ref{eq:arctan_quadrature}, we must compute the value of $x^{10}$, which requires several rounds of the squaring and multiplication protocols to compute.
-We now compare the quadrature approximation to the partial sum composed of the first 4 terms of Euler's series expansion in Equation~\ref{eq:arctan_euler}, which requires a similar number of floating-point operations to compute:
+We now compare the quadrature approximation to the partial sum composed of the first five terms of Euler's series expansion in Equation~\ref{eq:arctan_euler}, which requires a similar number of floating-point operations to compute:
 \begin{align} \label{eq:arctan_euler_partial}
 	\begin{split}
-		&\sum_{n=0}^{3}
+		&\sum_{n=0}^{4}
 		{
@@
 
-Figure~\ref{fig:arctan_error} shows that despite requiring a similar number of floating-point operations, the quadrature based approximation in Equation~\ref{eq:arctan_quadrature} gives accurate approximations over a larger interval, making it a more viable candidate for efficient computation.
+Figure~\ref{fig:arctan_error} shows that despite requiring a similar number of floating-point operations, the quadrature-based approximation in Equation~\ref{eq:arctan_quadrature} gives accurate approximations over a larger interval, making it a more viable candidate for efficient computation as seen in Figure~\ref{fig:arctan_comparison}.
 \begin{figure}[!ht]
 	\centering
-		\includegraphics[width=.9\linewidth]{figures/single_alpha_plot.png}
-		\caption{Comparison of the absolute error of the approximations for $\arctan x$ using quadrature approximation (Equation~\ref{eq:arctan_quadrature}) and the first 4 terms of Euler's series (Equation~\ref{eq:arctan_euler_partial})}
+	\begin{tikzpicture}
+		\begin{semilogyaxis}[
+			xmin=-40, xmax=40,
+			ymin=1e-11, ymax=2,
+			xlabel={$x$}, ylabel={Absolute error},
+			grid=major,
+			legend pos=south east,
+			legend cell align=left,
+			tick scale binop=\times,
+		]
+		\addplot[thick, ACMDarkBlue] table[x=x, y=gl] {plots/abs_err_arctan.txt};
+		\addplot[thick, ACMOrange] table[x=x, y=euler] {plots/abs_err_arctan.txt};
+		\legend{Gauss--Legendre quadrature, Euler's series}
+		\end{semilogyaxis}
+	\end{tikzpicture}%
+	\caption{Comparison of the absolute error of the approximations for $\arctan x$ using quadrature approximation (Equation~\ref{eq:arctan_quadrature}) and the first five terms of Euler's series (Equation~\ref{eq:arctan_euler_partial})}
 	\label{fig:arctan_error}
+\end{figure}
+
+\begin{figure}[ht]
+	\centering
+    \begin{tikzpicture}
+		\begin{axis}[
+			xmin=-12, xmax=12,
+			ymin=-2.6, ymax=2.6,
+			xlabel={$x$}, ylabel={$y$},
+			grid=major,
+			legend pos=south east,
+			legend cell align=left,
+			tick scale binop=\times,
+		]
+		\addplot[very thick, ACMDarkBlue] table[x=x, y=yhat] {plots/plot_arctan.txt};
+		\addplot[densely dashed] table[x=x, y=y] {plots/plot_arctan.txt};
+		\legend{5-point quadrature approximation, Actual value of $\arctan x$}
+	\end{axis}
+	\end{tikzpicture}%
+	\caption{Graph of $\arctan x$ and the approximation in Equation~\ref{eq:arctan_quadrature}}
+	\label{fig:arctan_comparison}
 \end{figure}
@@
 	\centering
-		\includegraphics[width=.9\linewidth]{figures/arctan_error_2.png}
+	\begin{tikzpicture}
+		\begin{semilogyaxis}[
+			xmin=-1.25, xmax=1.25,
+			ymin=1e-18, ymax=5e-5, ytickten={-18,-16,...,0},
+			xlabel={$x$}, ylabel={Absolute error},
+			grid=major,
+			legend pos=south east,
+			legend cell align=left,
+			tick scale binop=\times,
+		]
+		\addplot[thick, ACMDarkBlue] table[x=x, y=gl] {plots/abs_err_arctan.txt};
+		\end{semilogyaxis}
+	\end{tikzpicture}%
 	\caption{Absolute error of the approximation for $\arctan x$ using quadrature approximation (Equation~\ref{eq:arctan_quadrature}) over the interval $[-1,1]$}

### 2019-01-18 pcsc-paper/parts/05_testsforaccuracy.tex
Paper almost finished

@@
 \section{Experiments on Accuracy}
-We implemented privacy-preserving floating-point arithmetic using the system described in section \ref{sec:fp_operations}, using the python-paillier library (\url{https://github.com/n1analytics/python-paillier}) on Python 3.
+We implemented privacy-preserving floating-point arithmetic using the system described in Section~\ref{sec:fp_operations}, through the \texttt{python-paillier} library (\url{https://github.com/n1analytics/python-paillier}) running on Python~3.6.5.
 
-\subsection{Logarithm approximation}
-We then computed $\log(1+x)$ for various encrypted inputs using both the original quadrature formula by Khattri (equation \ref{eq:standard_logarithm_quadrature}) and our scaled approximation (equation \ref{eq:optimal_log_approximation}).
-These were compared with the values returned by the built-in logarithm function in Python 3.
-Several data points are shown in table \ref{tab:log_approximation}.
+\subsection{Logarithm Approximation}
+We then computed $\log(1+x)$ for various encrypted inputs using both the original quadrature formula by Khattri (Equation~\ref{eq:standard_logarithm_quadrature}) and our scaled approximation (Equation~\ref{eq:optimal_log_approximation}).
+These were compared with the values returned by the built-in logarithm function in Python.
+Several data points are shown in Table~\ref{tab:log_approximation}.
 
-We note that the privacy-preserving floating-point arithmetic resulted in some degree of floating-point error, as the observed floating point error in table \ref{tab:log_approximation} is greater than the raw absolute error observed in figure \ref{fig:log_error_comparison}.
+We note that the privacy-preserving floating-point arithmetic resulted in some degree of floating-point error, as the observed floating point error in Table~\ref{tab:log_approximation} is greater than the raw absolute error observed in Figure~\ref{fig:log_error_comparison}.
 However, it can still be seen that the error of the scaled approximation is less than that of the original approximation for large inputs.
-\begin{table}
-	\caption{Comparison of Logarithm Approximation Error under Paillier}
+\begin{table}[h]
+	\caption{Comparison of logarithm approximation errors under Paillier}
 	\label{tab:log_approximation}
-	\begin{tabular}{ccc}
+	\begin{tabular}{lcc}
 		\toprule
@@
 		\midrule
-		$\log(1)$ & $0$ & $2.053729 \times 10^{-2}$\\
-		$\log(10)$ & $2.833179 \times 10^{-2} $ & $2.280124 \times 10^{-1}$\\
-		$\log(50)$ & $2.170779 \times 10^{-2}$ & $2.437148 \times 10^{-2}$\\
-		$\log(100)$ & $3.524916 \times 10^{-1}$ & $2.122159 \times 10^{-2}$\\
-		$\log(200)$ & $8.859869 \times 10^{-1}$ & $1.441611 \times 10^{-1}$\\
-		$\log(256)$ & $1.098463 \times 10^{0}$ & $1.993136 \times 10^{-1}$\\
+		$\log 1$ & $0$ & $2.053729 \times 10^{-2}$\\
+		$\log 10$ & $2.833179 \times 10^{-2} $ & $2.280124 \times 10^{-1}$\\
+		$\log 50$ & $2.170779 \times 10^{-2}$ & $2.437148 \times 10^{-2}$\\
+		$\log 100$ & $3.524916 \times 10^{-1}$ & $2.122159 \times 10^{-2}$\\
+		$\log 200$ & $8.859869 \times 10^{-1}$ & $1.441611 \times 10^{-1}$\\
+		$\log 256$ & $1.098463 \times 10^{0}$ & $1.993136 \times 10^{-1}$\\
 	\bottomrule
@@
 
-\subsection{Inverse tangent approximation}
-We also computed $\arctan x$ using for various encrypted inputs using both the first four terms of Euler's series for the arctangent (equation \ref{eq:arctan_euler_partial}) and our quadrature approximation (equation \ref{eq:arctan_quadrature}).
-These were compared with the values returned by the built-in arctangent function in Python 3.We show several data points in table \ref{tab:arctan_approximation}.
-Similar to the logarithm approximations, we note that there is a degree of floating-point error compared to that predicted by figure \ref{fig:arctan_error}, but the quadrature approach obtains higher accuracy despite requiring a similar number of floating-point operations to execute.
+\subsection{Inverse Tangent Approximation}
+We also computed $\arctan x$ using for various encrypted inputs using both the first five terms of Euler's series for the inverse tangent function (Equation~\ref{eq:arctan_euler_partial}) and our quadrature approximation (Equation~\ref{eq:arctan_quadrature}).
+These were compared with the values returned by the built-in inverse tangent function in Python.
+We show several data points in Table~\ref{tab:arctan_approximation}.
+Similar to the logarithm approximations, we note that there is a degree of floating-point error compared to that predicted by Figure~\ref{fig:arctan_error}, but the quadrature approach obtains higher accuracy despite requiring a similar number of floating-point operations to execute.
 
-\begin{table}
-	\caption{Comparison of Inverse Tangent Approximation Error under Paillier}
+\begin{table}[h]
+	\caption{Comparison of inverse tangent approximation errors under Paillier}
 	\label{tab:arctan_approximation}
-	\begin{tabular}{ccc}
+	\begin{tabular}{lcc}
 		\toprule

### 2019-01-18 pcsc-paper/parts/02_01_paillier.tex
Periods and commas everywhere
added periods to equations
also some minor wording changes

@@
 The Paillier cryptosystem supports additive homomorphism as well as the multiplication of a plaintext scalar to an encrypted message.
-age.
-These homomorphic properties are used to add a plaintex scalar to a ciphertext, add two ciphertexts, and multiply a ciphertext by a plaintext scalar, respectively.
+These homomorphic properties are used to add a plaintext scalar to a ciphertext, add two ciphertexts, and multiply a ciphertext by a plaintext scalar, respectively.
 They are defined as follows.
 
-For all $m_1,m_2 \in \mathbb{Z}_n$ and $k\in \mathbb{N}$, the following homomorphic properties hold.
+For all $m_1,m_2 \in \mathbb{Z}_n$ and $k\in \mathbb{N}$, the following homomorphic properties hold:
 \begin{align*}
-	D(E(m_1)g^k\bmod n^2)=(m_1+k)\bmod n\\
-	D(E(m_1)E(m_2)\bmod n^2)=(m_1+m_2)\bmod n\\
-	D(E(m_1)^k\bmod n^2)= km_1\bmod n
+	D(E(m_1)g^k\bmod n^2)=(m_1+k)\bmod n,\\
+	D(E(m_1)E(m_2)\bmod n^2)=(m_1+m_2)\bmod n,\\
+	D(E(m_1)^k\bmod n^2)= km_1\bmod n.
 \end{align*}
@@
 \label{sec:fp_operations}
-The Paillier cryptosystem encrypts integers and allows operations on these integers.
-We now briefly go over several extensions to the Paillier cryptosystem discussed in the literature, which allow us to perform privacy-preserving floating-point arithmetic.
+The Paillier cryptosystem encrypts and allows operations on integers.
+We now describe several extensions to the Paillier cryptosystem discussed in the literature which allow us to perform privacy-preserving floating-point arithmetic.
 
@@
 \label{sec:fp_operations}
-We can use the following protocol described in~\cite{ziad_cryptoimg:_2016}, in order to extend the privacy-preserving integer addition and integer scalar multiplication of Paillier cryptosystem to floating-point numbers.
+We can use the following protocol described in~\cite{ziad_cryptoimg:_2016} in order to extend the privacy-preserving integer addition and integer scalar multiplication of Paillier cryptosystem to floating-point numbers.
 
@@
     \begin{align*}
-      E(m_c) &= E(m_1) \oplus (b^{e_b-e_a} \otimes E(m_b)), e_c = e_a & \text{ if } e_a \leq e_b \\
-      E(m_c) &= E(m_b) \oplus (b^{e_a-e_b} \otimes E(m_a)), e_c = e_b & \text{ if } e_a > e_b
+      E(m_c) &= E(m_1) \oplus (b^{e_b-e_a} \otimes E(m_b)), e_c = e_a & \text{ if } e_a \leq e_b, \\
+      E(m_c) &= E(m_b) \oplus (b^{e_a-e_b} \otimes E(m_a)), e_c = e_b & \text{ if } e_a > e_b.
     \end{align*}
@@
     \begin{align*}
-      E(m_c) &= m_a \otimes E(m_b)\\
-      e_c &= e_a + e_b
+      E(m_c) &= m_a \otimes E(m_b),\\
+      e_c &= e_a + e_b.
     \end{align*}
@@
 We can use the following two-party scheme defined in~\cite{boukoros_lightweight_2017} to perform privacy-preserving division.
-Suppose Bob has $E(x)$ and $E(y)$ and wants to obtain $E(x/y)$ without exposing the value of either integer.
+
+Suppose Bob has $E(x)$ and $E(y)$ and wants to obtain $E(x/y)$ without exposing the value of either variable.
 \begin{itemize}
-	\item Bob first selects a random number $r$ and computes $E(rx)$ and $E(ry)$. Bob can do this since $r$ is a plaintext constant.
+	\item Bob first selects a random non-zero number $r$ and computes $E(rx)$ and $E(ry)$. Bob can do this since $r$ is a plaintext constant.
 	\item Bob sends $E(rx)$ and $E(ry)$ to Alice, who decrypts both values and computes $x/y$ in the plaintext domain.
@@
 \label{ssec:exponentiationprotocol}
-To extend the available privacy-preserving arithmetic operations beyond those already supported by the system, we can use the following two-party scheme, adapted from the protocol to calculate Euclidean distances used in \cite{hutchison_privacy-preserving_2009}.
+ We can use the following two-party scheme, adapted from the protocol to calculate Euclidean distances used in \cite{hutchison_privacy-preserving_2009}, in order to perform secure exponentiation.
 
@@
 \begin{itemize}
-	\item Bob acquires $E(x^2), E(y^2)$ using the secure squaring protocol.
+	\item Bob acquires $E(x^2)$ and $E(y^2)$ using the secure squaring protocol.
 	\item Bob sends $E(x+y)$ to Alice, who decrypts the ciphertext to obtain $x+y$.
@@
 		&= \frac{1}{2}E(2xy)\\
-		&= E(xy)
+		&= E(xy).
 	\end{align*}
@@
 
-Using these extensions to the Paillier cryptosystem, privacy-preserving floating-point arithmetic can be acheived.
+By applying these extensions to the Paillier cryptosystem, privacy-preserving floating-point arithmetic can be acheived.

### 2019-01-18 pcsc-paper/parts/05_testsforaccuracy.tex
Periods and commas everywhere
added periods to equations
also some minor wording changes

@@
 We note that the privacy-preserving floating-point arithmetic resulted in some degree of floating-point error, as the observed floating point error in Table~\ref{tab:log_approximation} is greater than the raw absolute error observed in Figure~\ref{fig:log_error_comparison}.
-However, it can still be seen that the error of the scaled approximation is less than that of the original approximation for large inputs.
+However, it can still be seen that the error of the scaled approximation is less than that of the original approximation for large inputs, although this approximation loses accuracy for smaller inputs.
 \begin{table}[h]

### 2019-01-19 pcsc-paper/parts/02_01_paillier.tex
Fixed typo in FP extension
Fixed in both pcsc paper and thesis manuscript
Minor fixes

@@
 \subsubsection{Key Generation}
-We first define a function $L(x)$ as the largest integer $v$ greater than zero such that $x-1 \geq vn$.
-We choose two large primes $p$ and $q$, and set $n = pq, \lambda = \mathrm{lcm}(p-1,q-1)$.
-Then we select an integer $g$, $0\leq g \leq n^2$ such that $\mathrm{gcd}(L(g^\lambda \bmod n^2), n) = 1$.
+We first define a function $L\left(x\right)$ as the largest integer $v$ greater than zero such that $x-1 \geq vn$.
+We choose two large primes $p$ and $q$, and set $n = pq, \lambda = \mathrm{lcm}\left(p-1,q-1\right)$.
+Then we select an integer $g$ such that $\gcd\left(L\left(g^\lambda \bmod n^2\right), n\right) = 1$ and $0\leq g \leq n^2$.
 We denote the public key as $(g,n)$ and the private key $(p,q)$.
@@
 The encryption function to encrypt a plaintext $m \in \mathbb{Z}_n$ given a public key $(g,n)$ is defined as
-\begin{align*}
-	E(m) = g^m \cdot r^n \mod{n^2},
-\end{align*}
+\begin{equation*}
+	E\left(m\right) = g^m \cdot r^n \mod{n^2},
+\end{equation*}
 where $r$ is a random non-negative integer less than $n^2$.
 The decryption function to decrypt a ciphertext $c \in \mathbb{Z}^*_{n^2}$ given a private key $(p,q)$ is defined as:
-\begin{align*}
-	D(c) = L\left(c^\lambda \bmod n^2\right) \cdot \left(L\left(g^\lambda \bmod n^2\right)\right)^{-1} \mod n.
-\end{align*}
+\begin{equation*}
+	D\left(c\right) = L\left(c^\lambda \bmod n^2\right) \cdot \left(L\left(g^\lambda \bmod n^2\right)\right)^{-1} \mod n.
+\end{equation*}
 \subsubsection{Homomorphic Properties of the Paillier Cryptosystem}
@@
 \begin{align*}
-	D(E(m_1)g^k\bmod n^2)=(m_1+k)\bmod n,\\
-	D(E(m_1)E(m_2)\bmod n^2)=(m_1+m_2)\bmod n,\\
-	D(E(m_1)^k\bmod n^2)= km_1\bmod n.
+	D\left(E\left(m_1\right) g^k\bmod n^2\right) &= \left(m_1+k\right)\bmod n,\\
+	D\left(E\left(m_1\right) E\left(m_2\right)\bmod n^2\right) &= \left(m_1+m_2\right)\bmod n,\\
+	D\left(E\left(m_1\right)^k\bmod n^2\right) &= km_1\bmod n.
 \end{align*}
@@
 \subsection{Floating-Point Arithmetic}
-\label{sec:fp_operations}
+\label{sec:fp_arithmetic}
 The Paillier cryptosystem encrypts and allows operations on integers.
@@
   \item[Addition.]
-    To compute $E(c)=E(a+b)$ we compute
+    To compute $E\left(c\right)=E\left(a+b\right)$ we compute
     \begin{align*}
-      E(m_c) &= E(m_1) \oplus (b^{e_b-e_a} \otimes E(m_b)), e_c = e_a & \text{ if } e_a \leq e_b, \\
-      E(m_c) &= E(m_b) \oplus (b^{e_a-e_b} \otimes E(m_a)), e_c = e_b & \text{ if } e_a > e_b.
+		E\left(m_c\right) &= E\left(m_a\right) \oplus \left(b^{e_b-e_a} \otimes E\left(m_b\right)\right) \text{and } e_c = e_a & \text{ if } e_a \leq e_b, \\
+		E\left(m_c\right) &= E\left(m_b\right) \oplus \left(b^{e_a-e_b} \otimes E\left(m_a\right)\right) \text{and } e_c = e_b & \text{ if } e_a > e_b.
 	\end{align*}
+	% \begin{align*}
+	% 	E\left(m_c\right) &= 
+	% 	\begin{cases}
+	% 		E\left(m_a\right) \oplus \left(b^{e_b-e_a} \otimes E\left(m_b\right)\right) & \text{if } e_a \leq e_b \\
+	% 		E\left(m_b\right) \oplus \left(b^{e_a-e_b} \otimes E\left(m_a\right)\right) & \text{if } e_a > e_b
+	% 	\end{cases} \\
+	% 	% \text{ and }
+	% 	e_c &= \min\left(e_a, e_b \right).	
+	% 	% \begin{cases}
+	% 	% 	e_a & \text{if } e_a \leq e_b \\
+	% 	% 	e_b & \text{if } e_a > e_b
+	% 	% \end{cases}.
+	% \end{align*}
   \item[Scalar multiplication.]
-    To compute $E(c) = E(ab)$, where $a$ and $E(b)$ are known (i.e. $m_a$ is not encrypted), we compute
+    To compute $E\left(c\right) = E\left(ab\right)$, where $a$ and $E\left(b\right)$ are known (i.e., $m_a$ is not encrypted), we compute
     \begin{align*}
-      E(m_c) &= m_a \otimes E(m_b),\\
+      E\left(m_c\right) &= m_a \otimes E\left(m_b\right),\\
       e_c &= e_a + e_b.
@@
 \end{description}
+
 \subsubsection{Secure Division}
@@
 
-Suppose Bob has $E(x)$ and $E(y)$ and wants to obtain $E(x/y)$ without exposing the value of either variable.
+Suppose Bob has $E\left(x\right)$ and $E\left(y\right)$ and wants to obtain $E\left(x/y\right)$ without exposing the value of either variable.
 \begin{itemize}
-	\item Bob first selects a random non-zero number $r$ and computes $E(rx)$ and $E(ry)$. Bob can do this since $r$ is a plaintext constant.
-	\item Bob sends $E(rx)$ and $E(ry)$ to Alice, who decrypts both values and computes $x/y$ in the plaintext domain.
-	\item Alice encrypts and sends $E(x/y)$ to Bob.
+	\item Bob first selects a random non-zero number $r$ and computes $E\left(rx\right)$ and $E\left(ry\right)$. Bob can do this since $r$ is a plaintext constant.
+	\item Bob sends $E\left(rx\right)$ and $E\left(ry\right)$ to Alice, who decrypts both values and computes $x/y$ in the plaintext domain.
+	\item Alice encrypts and sends $E\left(x/y\right)$ to Bob.
 \end{itemize}
@@
 
-Suppose Alice encrypts an integer $x$ and sends it so Bob has $E(x)$, and wants to obtain $E(x^2)$ without exposing the value of $x$.
+Suppose Alice encrypts an integer $x$ and sends it so Bob has $E\left(x\right)$, and wants to obtain $E\left(x^2\right)$ without exposing the value of $x$.
 \begin{itemize}
-	\item Bob first selects a random integer $r$ and computes $E(x+r)$. Bob can do this since $r$ is a plaintext constant.
-	\item Bob sends $E(x+r)$ to Alice, who decrypts the ciphertext to obtain $x+r$.
-	\item Alice squares $x+r$ and encrypts the result. She sends $E((x+r)^2)$ to Bob.
-	\item Bob computes $E(-2rx + r^2)$. He then computes
+	\item Bob first selects a random integer $r$ and computes $E\left(x+r\right)$. Bob can do this since $r$ is a plaintext constant.
+	\item Bob sends $E\left(x+r\right)$ to Alice, who decrypts the ciphertext to obtain $x+r$.
+	\item Alice squares $x+r$ and encrypts the result. She sends $E\left(\left(x+r\right)^2\right)$ to Bob.
+	\item Bob computes $E\left(-2rx + r^2\right)$. He then computes
 	\begin{align*}
-		E((x+r)^2)E(-2rx + r^2) = E(x^2).
+		E\left(\left(x+r\right)^2\right)E\left(-2rx + r^2\right) = E\left(x^2\right).
 	\end{align*}
@@
 We can use the secure squaring protocol to arrive at a secure multiplication protocol, which then allows for the evaluation of polynomials.
-Suppose Alice encrypts integers $x$ and $y$, and Bob has $E(x), E(y)$ and wants to obtain $E(xy)$.
+Suppose Alice encrypts integers $x$ and $y$, and Bob has $E\left(x\right), E\left(y\right)$ and wants to obtain $E\left(xy\right)$.
 \begin{itemize}
-	\item Bob acquires $E(x^2)$ and $E(y^2)$ using the secure squaring protocol.
-	\item Bob sends $E(x+y)$ to Alice, who decrypts the ciphertext to obtain $x+y$.
-	\item Alice sends $E((x+y)^2)$ to Bob.
+	\item Bob acquires $E\left(x^2\right)$ and $E\left(y^2\right)$ using the secure squaring protocol.
+	\item Bob sends $E\left(x+y\right)$ to Alice, who decrypts the ciphertext to obtain $x+y$.
+	\item Alice sends $E\left(\left(x+y\right)^2\right)$ to Bob.
 	\item Bob then computes
 	\begin{align*}
-		\frac{1}{2}E((x+y)^2)E(x^2)^{-1}E(y^2)^{-1} &= \frac{1}{2}E((x+y)^2 - x^2 - y^2)\\
-		&= \frac{1}{2}E(2xy)\\
-		&= E(xy).
+		\frac{1}{2}E\left(\left(x+y\right)^2\right)E\left(x^2\right)^{-1}E\left(y^2\right)^{-1} &= \frac{1}{2}E\left(\left(x+y\right)^2 - x^2 - y^2\right)\\
+		&= \frac{1}{2}E\left(2xy\right)\\
+		&= E\left(xy\right).
 	\end{align*}

### 2019-01-19 pcsc-paper/parts/03_exponentialandlogarithmic.tex
Periods and commas everywhere
added periods to equations
also some minor wording changes
Minor fixes

@@
 \begin{align*}
-	\log{(1+x)} &= \log{\left(\frac{\alpha + \alpha x}{\alpha}\right)}\\
+	\log{\left(1+x\right)} &= \log{\left(\frac{\alpha + \alpha x}{\alpha}\right)}\\
 	&= \log{(\alpha + \alpha x)} - \log{\alpha}\\
@@
 	\begin{split}
-		&\log(1+x) \\
+		&\log\left(1+x\right) \\
 		&\approx \frac{137x^5 + 26685x^4 + 617370x^3 - 6498630x^2 - 121239315x - 257804775}
 		{30(x^5 + 405x^4 + 27210x^3 + 488810x^2 + 2536005x + 3122577)}\\
-		&+ \log{16}
+		&+ \log{16}.
 	\end{split}
@@
 This can be computed in the plaintext domain and added to an encrypted value using the properties of the Paillier cryptosystem.
-The remaining arithmetic operations in the approximation can be computed in the encrypted domain, using the protocols described in Section~\ref{sec:fp_operations}.
+The remaining arithmetic operations in the approximation can be computed in the encrypted domain, using the protocols described in Section~\ref{sec:fp_arithmetic}.
 Therefore, this approximation can be calculated in a privacy-preserving manner.
@@
 
-We now show how we used numerical methods to determine that a scaling factor of $\alpha = 1/16$ minimizes the maximum absolute error of the scaled approximation for $\log{(1+x)}$, within the range $x \in [0, 255]$.
-Let $I(x,\alpha)$ be the function obtained by approximating $\int_{n}^{\alpha n + \alpha}{\frac{1}{x}\diff x}$ with five-point Gauss--Legendre quadrature.
-The absolute error of the approximation compared to  $\log{(1+x)}$ at a given $x$ and $\alpha$ is given by the following function.
+We now show how we used numerical methods to determine that a scaling factor of $\alpha = 1/16$ minimizes the maximum absolute error of the scaled approximation for $\log{\left(1+x\right)}$, within the range $x \in [0, 255]$.
+
+Let $I\left(x,\alpha\right)$ be the function obtained by approximating $\int_{n}^{\alpha n + \alpha}{\frac{1}{x}\diff x}$ with five-point Gauss--Legendre quadrature.
+The absolute error of the approximation compared to $\log{\left(1+x\right)}$ at a given $x$ and $\alpha$ is given by the following function.
 \begin{align*}
-	A(x,\alpha) = \left| I(x,\alpha) - \log\alpha - \log{(1+x)}\right|.
+	A\left(x,\alpha\right) = \left| I\left(x,\alpha\right) - \log\alpha - \log{\left(1+x\right)}\right|.
 \end{align*}
-
 We want to show that the function
 \begin{align*}
-	f(\alpha) = \max_{0\leq x \leq 255}{A(x,\alpha)}
+	f\left(\alpha\right) = \max_{0\leq x \leq 255}{A\left(x,\alpha\right)}
 \end{align*}
 is minimized at $\alpha = 1/16$.
-We consider the functions $A(0,\alpha)$ and $A(255,\alpha)$. These are plotted in Figure~\ref{fig:endpoint_plot}.
-
-It can be determined numerically using SageMath 8.3 that a local minimum of $\max(A(0,\alpha),A(255,\alpha))$ on the interval $[0,1]$ is at $\alpha = 1/16$, which is found at the intersection of the two graphs.
+We consider the functions $A\left(0,\alpha\right)$ and $A\left(255,\alpha\right)$. These are plotted in Figure~\ref{fig:endpoint_plot}.
 \begin{figure}[!ht]
@@
 		]
-		% \addplot[thick, ACMDarkBlue, domain=0:1, samples=200]{1/30*abs((137*x^5 + 1625*x^4 + 2000*x^3 - 2000*x^2 - 30*(x^5 + 25*x^4 + 100*x^3 + 100*x^2 + 25*x + 1)*ln(x) - 1625*x - 137)/(x^5 + 25*x^4 + 100*x^3 + 100*x^2 + 25*x + 1))};
-		% \addplot[thick, ACMOrange, domain=0:1, samples=200]{abs(-1/30*(32346117281250*x^5*ln(x) - 150633093005312*x^5 - 6979321856000*x^4 - 33554432000*x^3 + 131072000*x^2 + 30*(x^5 + 25*x^4 + 100*x^3 + 100*x^2 + 25*x + 1)*ln(x) + 38250*(x^5 + 20*x^4 + 60*x^3 + 40*x^2 + 5*x)*ln(x) + 19507500*(x^5 + 15*x^4 + 30*x^3 + 10*x^2)*ln(x) + 4974412500*(x^5 + 10*x^4 + 10*x^3)*ln(x) + 634237593750*(x^5 + 5*x^4)*ln(x) + 416000*x + 137)/(1099511627776*x^5 + 107374182400*x^4 + 1677721600*x^3 + 6553600*x^2 + 6400*x + 1) - 8*ln(2))};
 		\addplot[thick, ACMDarkBlue, domain=0:1] table[x=alpha, y=x0] {plots/abs_err_sl_0_255.txt};
@@
 		\legend{$x=0$, $x=255$}
+		% \legend{$A\left(0,\alpha \right)$, $A\left(255,\alpha \right)$}
 	\end{semilogyaxis}
 	\end{tikzpicture}%
-	\caption{Graphs of $A(x,\alpha)$ at $x=0$ and $x=255$}
+	\caption{Graphs of $A\left(x,\alpha\right)$ at $x=0$ and $x=255$}
 	\label{fig:endpoint_plot}
 \end{figure}
-We then consider the function $A(x,1/16)$, shown in Figure~\ref{fig:single_alpha_plot}.
-It was determined numerically that the local maxima of $A(x,1/16)$ on the interval occur at $x=0$ and $x=255$.
-Since a scaling factor other than $\alpha=1/16$ yields a higher absolute error at either $x=0$ or $x=255$, as seen in Figure~\ref{fig:endpoint_plot}, it follows that a scaling factor of $\alpha = 1/16$ minimizes the maximum absolute error of the scaled approximation for $\log{(1+x)}$, within the range $x \in [0, 255]$.
+
+It can be determined numerically using SageMath 8.3 that a local minimum of $\max\left(A\left(0,\alpha\right),A\left(255,\alpha\right)\right)$ on the interval $[0,1]$ is at $\alpha = 1/16$, which is found at the intersection of the two graphs.
+
+We then consider the function $A\left(x,1/16\right)$, shown in Figure~\ref{fig:single_alpha_plot}.
+It was determined numerically that the local maxima of $A\left(x,1/16\right)$ on the interval occur at $x=0$ and $x=255$.
+Since a scaling factor other than $\alpha=1/16$ yields a higher absolute error at either $x=0$ or $x=255$, as seen in Figure~\ref{fig:endpoint_plot}, it follows that a scaling factor of $\alpha = 1/16$ minimizes the maximum absolute error of the scaled approximation for $\log{\left(1+x\right)}$, within the range $x \in [0, 255]$.
 \begin{figure}[ht]
@@
 	\end{tikzpicture}%
-	\caption{Graph of $A(x,1/16)$, the absolute error of the approximation in Equation~\ref{eq:optimal_log_approximation} given a scaling factor of $\alpha=1/16$}
+	\caption{Graph of $A\left(x,1/16\right)$, the absolute error of the approximation in Equation~\ref{eq:optimal_log_approximation} given a scaling factor of $\alpha=1/16$}
 	\label{fig:single_alpha_plot}
@@
 
-As a concrete example, evaluating partial sums of the series representation for the exponential function
+As a concrete example, evaluating partial sums of the series representation for the exponential function,
 \begin{align*}
-	e^x = \sum_{n=0}^{\infty}{\frac{x^n}{n!}}
+	e^x = \sum_{n=0}^{\infty}{\frac{x^n}{n!}},
 \end{align*}

### 2019-01-19 pcsc-paper/parts/05_testsforaccuracy.tex
Minor fixes

@@
 \section{Experiments on Accuracy}
-We implemented privacy-preserving floating-point arithmetic using the system described in Section~\ref{sec:fp_operations}, through the \texttt{python-paillier} library (\url{https://github.com/n1analytics/python-paillier}) running on Python~3.6.5.
+We implemented privacy-preserving floating-point arithmetic using the system described in Section~\ref{sec:fp_arithmetic}, through the \texttt{python-paillier} library (\url{https://github.com/n1analytics/python-paillier}) running on Python~3.6.5.
 
 \subsection{Logarithm Approximation}
-We then computed $\log(1+x)$ for various encrypted inputs using both the original quadrature formula by Khattri (Equation~\ref{eq:standard_logarithm_quadrature}) and our scaled approximation (Equation~\ref{eq:optimal_log_approximation}).
+We then computed $\log\left(1+x\right)$ for various encrypted inputs using both the original quadrature formula by Khattri (Equation~\ref{eq:standard_logarithm_quadrature}) and our scaled approximation (Equation~\ref{eq:optimal_log_approximation}).
 These were compared with the values returned by the built-in logarithm function in Python.
@@
 However, it can still be seen that the error of the scaled approximation is less than that of the original approximation for large inputs, although this approximation loses accuracy for smaller inputs.
-\begin{table}[h]
+\begin{table}[ht]
 	\caption{Comparison of logarithm approximation errors under Paillier}
@@
 
-\begin{table}[h]
+\begin{table}[ht]
 	\caption{Comparison of inverse tangent approximation errors under Paillier}

### 2019-01-20 pcsc-paper/parts/06_conclusionreccomendations.tex
Comments to intro/conclusion
Attempt to take into account sir's comments

--- 2019-01-16 pcsc-paper/parts/06_conclusionreccomendations.tex
@@
-\section{Conclusion [WIP]}
-\section{Recommendations [WIP]}
+\section{Conclusion}
+We have shown new closed-form approximations to the logarithm and inverse tangent functions and showed how they can be implemented together with the Paillier cryptosystem to allow for privacy-preserving function calculation.
+We have compared our approach to other closed-form approximations which require a similar number of secure arithmetic operations to evaluate, and have shown our new approximation procedures can generally yield more accurate results over larger ranges of inputs.
+
+While other approximation procedures for the logarithm and inverse tangent functions may yield better accuracy, the rational approximations shown in this paper are suitable enough for privacy-preserving protocols where the precise input values are not exposed, and arithmetic operations are limited and more computationally expensive.
+
+\section{Recommendations}
+Further research can be done regarding implementation of other transcendental functions, either by using known infinite series, or by using identities with the quadrature-based approximations we have presented in this paper.
+Furthermore, testing with other types of homomorphic cryptosystems can be done, to potentially reduce noise encountered in secure floating-point operations.

### 2019-01-20 pcsc-paper/parts/04_inversetrig.tex
Periods and commas everywhere
added periods to equations
also some minor wording changes
Minor fixes
Plots for experiment data

@@
 We will now show how a Gauss--Legendre quadrature approach can also be used for efficient privacy-preserving approximation of the inverse tangent function.
-Two well-known series representations of the arctangent function exist: the Maclaurin series expansion,
+Two well-known series representations of the inverse tangent function exist: the Maclaurin series expansion,
 \begin{align} \label{eq:arctan_maclaurin}
-	\arctan x = \sum_{n=0}^{\infty}{\frac{(-1)^nx^{2n+1}}{2n+1}}, \text{ for }|x|\leq 1
+	\arctan x = \sum_{n=0}^{\infty}{\frac{(-1)^nx^{2n+1}}{2n+1}}, \text{ for }|x|\leq 1,
 \end{align}
@@
 		{(1+x^2)^{n+1}}
-	}
+	}.
 \end{align}
@@
 		{4\left(225x^9 + 15925x^7 + 144753x^5 + 350595x^3 + 238140x\right)}
-		{15\left(x^{10} + 480x^8 + 11760x^6 + 64120x^4 + 114660x^2 + 63504\right)}
+		{15\left(x^{10} + 480x^8 + 11760x^6 + 64120x^4 + 114660x^2 + 63504\right)}.
 	\end{split}
@@
 		{965x^9 + 2370x^7 + 2688x^5 + 1470x^3 + 315x}
-		{315\left(x^{10} + 5x^8 + 10x^6 + 10x^4 + 5x^2 + 1\right)}
+		{315\left(x^{10} + 5x^8 + 10x^6 + 10x^4 + 5x^2 + 1\right)}.
 	\end{split}
@@
 		\begin{semilogyaxis}[
-			xmin=-1.25, xmax=1.25,
+			xmin=-1, xmax=1,
 			ymin=1e-18, ymax=5e-5, ytickten={-18,-16,...,0},

### 2019-01-20 pcsc-paper/parts/05_testsforaccuracy.tex
Plots for experiment data

@@
 
+\begin{figure}[!ht]
+	\centering
+	\begin{tikzpicture}
+		\begin{semilogyaxis}[
+			xmin=0, xmax=255,
+			ymin=1e-3, ymax=1.5,
+			xlabel={$x$}, ylabel={Absolute error},
+			grid=major,
+			legend pos=south east,
+			legend cell align=left,
+			tick scale binop=\times,
+		]
+		\addplot[very thick, ACMDarkBlue] table[x=x, y=newerr] {plots/comp_log_errs.txt};
+		\addplot[thick, ACMOrange] table[x=x, y=olderr] {plots/comp_log_errs.txt};
+		\legend{Scaled quadrature, Original quadrature}
+		\end{semilogyaxis}
+	\end{tikzpicture}%
+	\caption{Comparison of logarithm approximation errors under Paillier}
+	\label{fig:comp_log}
+\end{figure}
+
 \subsection{Inverse Tangent Approximation}
@@
 \end{table}
+
+\begin{figure}[!ht]
+	\centering
+	\begin{tikzpicture}
+		\begin{semilogyaxis}[
+			xmin=-1, xmax=1,
+			ymin=1e-7, ymax=1,
+			xlabel={$x$}, ylabel={Absolute error},
+			grid=major,
+			legend pos=south east,
+			legend cell align=left,
+			tick scale binop=\times,
+		]
+		\addplot[very thick, ACMDarkBlue] table[x=x, y=newerr] {plots/comp_arctan_errs.txt};
+		\addplot[thick, ACMOrange] table[x=x, y=olderr] {plots/comp_arctan_errs.txt};
+		\legend{Gauss--Legendre quadrature, Partial sum of Euler's series}
+		\end{semilogyaxis}
+	\end{tikzpicture}%
+	\caption{Comparison of inverse tangent approximation errors under Paillier}
+	\label{fig:comp_arctan}
+\end{figure}

### 2019-01-21 pcsc-paper/parts/03_exponentialandlogarithmic.tex
Briefly referenced new graphs
Briefly referenced new graphs

@@
-\section{Exponential and Logarithmic Functions}
+\section{Logarithmic Function Approximation}
 We now present our main contribution in this paper: a general method to improve the general accuracy of the logarithm approximation given by Khattri in~\cite{khattri_new_2009} for use in privacy-preserving calculation, provided that accuracy is only required for a specific range.

### 2019-01-21 pcsc-paper/parts/04_inversetrig.tex
Briefly referenced new graphs
Briefly referenced new graphs

@@
-\section{Inverse Trigonometric Functions}
+\section{Inverse Tangent Function Approximation}
 We will now show how a Gauss--Legendre quadrature approach can also be used for efficient privacy-preserving approximation of the inverse tangent function.

### 2019-01-21 pcsc-paper/parts/05_testsforaccuracy.tex
Briefly referenced new graphs
Briefly referenced new graphs

@@
 We note that the privacy-preserving floating-point arithmetic resulted in some degree of floating-point error, as the observed floating point error in Table~\ref{tab:log_approximation} is greater than the raw absolute error observed in Figure~\ref{fig:log_error_comparison}.
-However, it can still be seen that the error of the scaled approximation is less than that of the original approximation for large inputs, although this approximation loses accuracy for smaller inputs.
+Figure~\ref{fig:comp_log} shows a plot of the observed absolute error of the original quadrature approximation and scaled quadrature approximation to the logarithm, when computed using privacy-preserving arithmetic through the Paillier cryptosystem.
+While there are intervals where the original quadrature approximation is more accurate than the scaled quadrature approximation, we can see that the scaled quadrature is more accurate for larger inputs.
+
 \begin{table}[ht]
@@
 These were compared with the values returned by the built-in inverse tangent function in Python.
-We show several data points in Table~\ref{tab:arctan_approximation}.
+We show several data points in Table~\ref{tab:arctan_approximation}, and show graphs of the observed error in Figure~\ref{fig:comp_arctan}.
 Similar to the logarithm approximations, we note that there is a degree of floating-point error compared to that predicted by Figure~\ref{fig:arctan_error}, but the quadrature approach obtains higher accuracy despite requiring a similar number of floating-point operations to execute.

### 2019-01-21 pcsc-paper/parts/01_introduction.tex
Added experiments
We have a mini-thesis na
Done!
conclusion and reccomendations
Minor fixes
Comments to intro/conclusion
Attempt to take into account sir's comments
3rd draft
apply 2nd round of comments

@@
 \section{Introduction}
-Research in digital privacy has involved the use of homomorphic cryptosystems, cryptosystems which allow for operations to be performed on encrypted data without leaking information about the operands.
+Research in digital privacy has involved the use of homomorphic cryptosystems that allow for operations to be performed on encrypted data without leaking information about the operands.
 Previous research has highlighted the use of the Paillier cryptosystem, a partially homomorphic cryptosystem which allows two basic operations to be performed on encrypted integers: two encrypted integers can be added to obtain an encryption of their sum, and an encrypted integer can be multiplied to an unencrypted plaintext integer to obtain an encryption of their product.
@@
 By demonstrating how the Paillier cryptosystem can be applied to approximate common non-linear functions, we hope to extend its usability as a tool for privacy-preserving computation.
+
+The functions in Table~\ref{tab:inputconstraints} were chosen since current approximations of these functions which can easily be computed through privacy-preserving artihmetic are limited in their range of accuracy.
 \begin{table}
-	\caption{Summary of functions [WIP]}
+	\caption{Summary of functions}
 	\label{tab:inputconstraints}
@@
 		\midrule
-		$e^x$ & $x\in[0,255]$\\
-		$\log(1+x)$ & $x\in[0,255]$\\
-		$\sin x$ & $x\in[-2\pi,2\pi]$ \\
-		$\arctan x$ & $x\in[-255,255]$\\
+		$\log\left(1+x\right)$ & $x\in[0,255]$\\
+		$\arctan x$ & $x\in[-1,1]$\\
 	    \bottomrule

### 2019-01-21 pcsc-paper/parts/06_conclusionreccomendations.tex
Additional recommendation
Additional recommendation
3rd draft
apply 2nd round of comments

@@
 We have compared our approach to other closed-form approximations which require a similar number of secure arithmetic operations to evaluate, and have shown our new approximation procedures can generally yield more accurate results over larger ranges of inputs.
+In particular, the error in the original approximation for $\log{\left(1+x\right)}$ increases quickly over inputs greater than 52, while the error in our new logarithm approximation increases slower, allowing our new approximation to be used for applications where accuracy is desired over a larger range of inputs.
+Futhermore, as seen in Table~\ref{tab:arctan_approximation}, our new inverse tangent approximation is an order of magnitude better than the sum of the first five terms of the series by Euler in Equation~\ref{eq:arctan_euler}, despite requiring a similar number of floating-point operations.
 
@@
 Further research can be done regarding implementation of other transcendental functions, either by using known infinite series, or by using identities with the quadrature-based approximations we have presented in this paper.
+Different methods for numerical integration can also be explored and applied for use in deriving formulas for privacy-preserving computation.
 Furthermore, testing with other types of homomorphic cryptosystems can be done, to potentially reduce noise encountered in secure floating-point operations.

### 2019-02-06 dghv/dghv_utils.py
Initial port complete

@@ -74,4 +74,77 @@ def mpz_mod_modified(op1, op2)
         rop = gmpy2.sub(rop, op2)
     return rop
 
-def generate_random(x, bitsize, include_negative_range, seeded, full_range):
+def generate_random(bit_size, include_negative_range, seeded, full_range):
+    if not seeded:
+        gmpy2.random_state()
+    x = zero
+    if full_range:
+        x = gmpy2.mul_2exp(one, bit_size - 1)
+    tmp = 0
+    if bit_size < 33:
+        tmp = gmpy2.get_random()
+        temp = (1 << bit_size)
+        x = gmpy2.f_mod(tmp, temp)
+        if include_negative_range:
+            tmp = gmpy2.mul_2exp(one, bit_size - 1)
+            x = gmpy2.sub(x, tmp)
+        return x
+    for i in range(bit_size-32, 0-1, -32):
+        tmp = gmpy2.get_random()
+        tmp = gmpy2.mul_2exp(tmp, i)
+        x = gmpy2.add(x, tmp)
+    x = gmpy2.add(x, gmpy2.get_random())
+    if include_negative_range:
+        tmp = gmpy2.mul_2exp(one, bit_size - 1)
+        x = gmpy2.sub(x, tmp)
+    return x
+        
+def generate_x(sk):
+    gmpy2.random_state()
+    q, r = 0, 0
+    q = generate_random(gamma - eta, False, False, False)
+    r = generate_random(rho, True, False, False)
+    x = gmpy2.mul(q, sk)
+    x = gmpy2.add(r, x)
+    return x
+
+def generate_x_i(sk, length):
+    tmp, q, r = 0, 0, 0
+    q = gmpy2.mul_2exp(one, length - 1)
+    gmpy2.random_state()
+    for i in range(length-32, 0-1, -32):
+        tmp = gmpy2.get_random()
+        tmp = gmpy2.mul_2exp(tmp, i)
+        q = gmpy2.add(tmp, q)
+    q = gmpy2.add(q, gmpy2.get_random())
+    r = generate_random(rho, True, False, False)
+    x_i = gmpy2.mul(q, sk)
+    x_i = gmpy2.add(r, x_i)
+    return x_i
+    
+def generate_sparse_matrix(u_1, modified_secret_key, x_p):
+    gmpy2.random_state()
+    Theta_vector = [0 for _ in range(Theta)]
+    for i in range(1, Theta):
[…]

### 2019-02-06 dghv/dghv_shorter_public_key.py
pushing WIPs

@@ -1,12 +1,9 @@
 import gmpy2
-from gmpy2 import mpz,mpq,mpfr,mpc
+from gmpy2 import mpz
 from pathlib import Path
-import dghv_utils
+from dghv_utils import *
 
 class binary_real:
-    def __init__(self):
-        return
-
     def __init__(self, num, den, Precision):
         self.initialize(num, den, Precision)
 
@@ -14,12 +11,12 @@ class binary_real:
         num = mpz(num)
         den = mpz(den)
         self.precision = Precision
-        quotient = gmpy2.f_div(num,den)
+        quotient = gmpy2.f_div(num, den)
         if gmpy2.is_odd(quotient):
             self.decimal = 1
         else:
             self.decimal = 0
-        remainder = gmpy2.fmod(num,den)
+        remainder = gmpy2.fmod(num, den)
 
         self.value = []
         remainder *= 2
@@ -27,16 +24,16 @@ class binary_real:
         while i < self.precision:
             if remainder < den:
                 remainder *= 2
-                value.append(False)
-            elif remainer > den:
-                value.append(True)
+                self.value.append(False)
+            elif remainder > den:
+                self.value.append(True)
                 remainder -= den
                 remainder *= 2
             elif remainder == den:
-                value.append(True)
+                self.value.append(True)
                 remainder -= den
             elif remainder == 0:
-                value.append(False)
+                self.value.append(False)
             i += 1
 
     def custom_setup(self, dec, prec, val):
@@ -51,29 +48,30 @@ class binary_real:
 
         carry = False
         for i in range(prec):
-            if int(self.value[prec - i - 1]) + int(x.value[prec - i - i]) + int(carry) == 3:
+            if int(self.value[prec - i - 1]) + int(other.value[prec - i - i]) + int(carry) == 3:
                 bits.append(True)
                 carry = True
-            elif int(self.value[prec - i - 1]) + int(x.value[prec - i - i]) + int(carry) == 2:
+            elif int(self.value[prec - i - 1]) + int(other.value[prec - i - i]) + int(carry) == 2:
                 bits.append(False)
                 carry = True
             else:
-                bits.append( self.value[prec - i - 1] or x.value[prec - i - i] or carry)
[…]

### 2019-02-06 dghv/dghv_utils.py

@@ -32,7 +32,7 @@ def sort_utility(array, l, m, r):
             array[k] = L[i]
             k += 1
             i += 1
-        else
+        else:
             array[k] = R[j]
             k += 1
             j += 1
@@ -67,7 +67,7 @@ def bit_size(x):
     
     return temp
 
-def mpz_mod_modified(op1, op2)
+def mpz_mod_modified(op1, op2):
     rop = gmpy2.f_mod(op1,op2)
     temp = gmpy2.f_div(op2, two)
     if rop > temp:
@@ -75,3 +75,4 @@ def mpz_mod_modified(op1, op2)
     return rop
 
 def generate_random(x, bitsize, include_negative_range, seeded, full_range):
+    return

### 2019-02-07 dghv/dghv_shorter_public_key.py
Almost done translating

@@ -108,9 +108,9 @@ class cryptosystem:
             seed = generate_sparse_matrix(u_1, self.modified_secret_key, x_p)
             for i in range(Theta):
                 if self.modified_secret_key[i] is True:
-                    symmetric_encryption(self.encrypted_sk[i], 1)
+                    self.encrypted_sk[i] = symmetric_encryption(1)
                 else:
-                    symmetric_encryption(self.encrypted_sk[i], 0)
+                    self.encrypted_sk[i] = symmetric_encryption(0)
             enc_sk_file = open('short_public_key.txt', 'w')
             enc_sk_file.write(seed)
             enc_sk_file.write(u_1)
@@ -149,15 +149,15 @@ class cryptosystem:
             while self.pk[i] >= self.pk[0]:
                 generate_x(pk[i], sk)
 
-    def encrypt_bit(ct, bit):
+    def encrypt_bit(self, bit):
         tmp, temp, test = mpz(), mpz(), mpz()
         ct = mpz(bit)
-        generate_random(tmp, sigma, True, False, False)
+        tmp = generate_random(sigma, True, False, False)
         tmp *= 2
         ct += tmp
         for i in range(1, beta + 1):
             for j in range(1, beta + 1):
-                generate_random(tmp, alpha, False, False, False)
+                tmp = generate_random(alpha, False, False, False)
                 temp = self.pk[2 * j] * self.pk[2 * i - 1]
                 temp %= self.pk[0]
                 tmp *= temp
@@ -166,13 +166,118 @@ class cryptosystem:
                 tmp %= self.pk[0]
                 ct += tmp
                 ct += pk[0]
+        return ct
 
-    def symmetric_encryption(ct, m):
-        generate_x(ct, self.sk)
+    def symmetric_encryption(self, m):
+        ct = generate_x(self.sk)
         ct *= 2
         ct += m
+        return ct
 
-    def decrypt_bit(m, ct):
+    def decrypt_bit(self, m, ct):
         m = mpz_mod_modified(ct, self.sk)
         m %= 2
+        return m
+
+    def AND_GATE(self, ct_1, ct_2):
+        return (ct_1 * ct_2) % self.pk[0]
+    
+    def XOR_GATE(self, ct_1, ct_2):
+        return (ct_1 + ct_2) % self.pk[0]
+    
+    def NOT_GATE(self, ct_1):
+        return XOR_GATE(ct_1, 1)
+
[…]

### 2019-02-07 dghv/dghv_utils.py

@@ -1,5 +1,5 @@
 import gmpy2
-from gmpy2 import mpz,mpq,mpfr,mpc
+from gmpy2 import mpz
 zero = mpz(0)
 one = mpz(1)
 two = mpz(2)
@@ -22,7 +22,7 @@ def sort_utility(array, l, m, r):
     n_1 = m - l + 1
     n_2 = r - m
     L = [mpz(array[l + i]) for i in range(n_1)]
-    R = [mpz(array[m + 1 + j]) for i in range(n_2)]
+    R = [mpz(array[m + 1 + j]) for j in range(n_2)]
 
     i = 0
     j = 0
@@ -49,7 +49,7 @@ def sort_utility(array, l, m, r):
 
 def sort_huge_numbers(array, l, r):
     if l < r:
-        m = (l + r)//2
+        m = (l + r) // 2
         sort_huge_numbers(array, l, m)
         sort_huge_numbers(array, m + 1, r)
         sort_utility(array, l, m, r)
@@ -68,7 +68,7 @@ def bit_size(x):
     return temp
 
 def mpz_mod_modified(op1, op2):
-    rop = gmpy2.f_mod(op1,op2)
+    rop = gmpy2.f_mod(op1, op2)
     temp = gmpy2.f_div(op2, two)
     if rop > temp:
         rop = gmpy2.sub(rop, op2)
@@ -89,7 +89,7 @@ def generate_random(bit_size, include_negative_range, seeded, full_range):
             tmp = gmpy2.mul_2exp(one, bit_size - 1)
             x = gmpy2.sub(x, tmp)
         return x
-    for i in range(bit_size-32, 0-1, -32):
+    for i in range(bit_size - 32, 0 - 1, -32):
         tmp = gmpy2.get_random()
         tmp = gmpy2.mul_2exp(tmp, i)
         x = gmpy2.add(x, tmp)
@@ -112,7 +112,7 @@ def generate_x_i(sk, length):
     tmp, q, r = 0, 0, 0
     q = gmpy2.mul_2exp(one, length - 1)
     gmpy2.random_state()
-    for i in range(length-32, 0-1, -32):
+    for i in range(length - 32, 0 - 1, -32):
         tmp = gmpy2.get_random()
         tmp = gmpy2.mul_2exp(tmp, i)
         q = gmpy2.add(tmp, q)

### 2019-02-08 dghv/dghv_shorter_public_key.py
Fully translated, debugging WIP

@@ -81,7 +81,8 @@ class cryptosystem:
         if not sk_file_check.is_file():
             sk_file = open('secret_key.txt', 'w')
             self.generate_secret_key()
-            sk_file.write(self.sk)
+            print('secret key:', self.sk)
+            sk_file.write(self.sk.digits())
             sk_file.close()
         else:
             sk_file = open('secret_key.txt', 'r')
@@ -92,8 +93,10 @@ class cryptosystem:
         if not pk_file_check.is_file():
             pk_file = open('short_public_key.txt', 'w')
             self.generate_public_key()
+            print('public key')
             for pk_i in self.pk:
-                pk_file.write(pk_i)
+                pk_file.write(pk_i.digits())
+                print(pk_i.digits())
             pk_file.close()
         else:
             pk_file = open('short_public_key.txt', 'r')
@@ -121,27 +124,36 @@ class cryptosystem:
             enc_sk_file = open('short_public_key.txt', 'r')
             seed = enc_sk_file.read()
             self.u_1 = enc_sk_file.read()
-
-        # continue from line 222
+            temp = mpz()
+            for i in range(Theta):
+                Input = enc_sk_file.read()
+                self.encrypted_sk[i] = Input
+                temp = self.decrypt_bit(encrypted_sk[i])
+                if temp == 1:
+                    self.modified_secret_key[i] = True
+                else:
+                    self.modified_secret_key[i] = False
+            enc_sk_file.close()
 
     def generate_secret_key(self):
         tmp = mpz()
         self.sk = mpz(2)**(eta - mpz(1))
-        gmpy2.random_state()
+        random_state = gmpy2.random_state()
         i = eta - 32
         while i >= 0:
-            tmp = gmpy2.mpz_random()
-            tmp = tmp * (2**i)
+            tmp = gmpy2.mpz_random(random_state, 2 ** 64)
+            tmp = tmp * (mpz(2)**i)
             self.sk += tmp
-        self.sk += gmpy2.mpz_random()
+            i -= 32
+        self.sk += gmpy2.mpz_random(random_state, 2 ** 64)
         self.sk = self.sk * 2 + 1
 
     def generate_public_key(self):
[…]

### 2019-02-08 dghv/dghv_utils.py

@@ -76,13 +76,13 @@ def mpz_mod_modified(op1, op2):
 
 def generate_random(bit_size, include_negative_range, seeded, full_range):
     if not seeded:
-        gmpy2.random_state()
+        seeded = gmpy2.random_state()
     x = zero
     if full_range:
         x = gmpy2.mul_2exp(one, bit_size - 1)
     tmp = 0
     if bit_size < 33:
-        tmp = gmpy2.get_random()
+        tmp = gmpy2.mpz_random(seeded, 2 ** 64)
         temp = (1 << bit_size)
         x = gmpy2.f_mod(tmp, temp)
         if include_negative_range:
@@ -90,14 +90,14 @@ def generate_random(bit_size, include_negative_range, seeded, full_range):
             x = gmpy2.sub(x, tmp)
         return x
     for i in range(bit_size - 32, 0 - 1, -32):
-        tmp = gmpy2.get_random()
+        tmp = gmpy2.mpz_random(seeded, 2 ** 64)
         tmp = gmpy2.mul_2exp(tmp, i)
         x = gmpy2.add(x, tmp)
-    x = gmpy2.add(x, gmpy2.get_random())
+    x = gmpy2.add(x, gmpy2.mpz_random(seeded, 2 ** 64))
     if include_negative_range:
         tmp = gmpy2.mul_2exp(one, bit_size - 1)
         x = gmpy2.sub(x, tmp)
-    return x
+    return mpz(x)
         
 def generate_x(sk):
     gmpy2.random_state()

### 2019-02-08 dghv/dghv_shorter_public_key.py
Fixed compilation errors; logic debugging wip

@@ -79,56 +79,57 @@ class cryptosystem:
 
         sk_file_check = Path('secret_key.txt')
         if not sk_file_check.is_file():
+            print('generating secret key')
             sk_file = open('secret_key.txt', 'w')
             self.generate_secret_key()
-            print('secret key:', self.sk)
             sk_file.write(self.sk.digits())
             sk_file.close()
         else:
+            print('loading secret key')
             sk_file = open('secret_key.txt', 'r')
             self.sk = mpz(sk_file.read())
             sk_file.close()
+        print('secret key:', self.sk)
 
         pk_file_check = Path('short_public_key.txt')
         if not pk_file_check.is_file():
             pk_file = open('short_public_key.txt', 'w')
             self.generate_public_key()
-            print('public key')
-            for pk_i in self.pk:
-                pk_file.write(pk_i.digits())
-                print(pk_i.digits())
+            pk_file.writelines("%s\n" % str(pk_i.digits()) for pk_i in self.pk)
+            print('public key generated,', len(self.pk), 'elements')
+            #print([str(pk_i) for pk_i in self.pk])
             pk_file.close()
         else:
             pk_file = open('short_public_key.txt', 'r')
-            for i in range(2 * beta + 1):
-                self.pk[i] = mpz(pk_file.read())
+            self.pk = [mpz(element.rstrip()) for element in pk_file.readlines()]
+            print('public key loaded,', len(self.pk), 'elements')
             pk_file.close()
 
         enc_sk_file_check = Path('encrypted_sk_and_seed.txt')
         if not enc_sk_file_check.is_file():
             x_p = mpz(2) ** kappa
-            x_p = gmpy2.f_div(x_p, sk)
-            seed = generate_sparse_matrix(u_1, self.modified_secret_key, x_p)
+            x_p = gmpy2.f_div(x_p, self.sk)
+            self.seed = generate_sparse_matrix(self.u_1, self.modified_secret_key, x_p)
             for i in range(Theta):
                 if self.modified_secret_key[i] is True:
-                    self.encrypted_sk[i] = symmetric_encryption(1)
+                    self.encrypted_sk[i] = self.symmetric_encryption(self.encrypted_sk[i], 1)
                 else:
-                    self.encrypted_sk[i] = symmetric_encryption(0)
[…]

### 2019-02-08 dghv/dghv_utils.py

@@ -1,9 +1,10 @@
+import time
 import gmpy2
 from gmpy2 import mpz
 zero = mpz(0)
 one = mpz(1)
 two = mpz(2)
-
+global_random_state = None
 Lambda = 42
 alpha = 42
 rho = 16
@@ -68,21 +69,24 @@ def bit_size(x):
     return temp
 
 def mpz_mod_modified(op1, op2):
-    rop = gmpy2.f_mod(op1, op2)
-    temp = gmpy2.f_div(op2, two)
+    print(op1)
+    print(op2)
+    rop = gmpy2.f_mod(mpz(op1), mpz(op2))
+    temp = gmpy2.f_div(mpz(op2), two)
     if rop > temp:
-        rop = gmpy2.sub(rop, op2)
+        rop = gmpy2.sub(rop, mpz(op2))
     return rop
 
 def generate_random(bit_size, include_negative_range, seeded, full_range):
-    if not seeded:
-        seeded = gmpy2.random_state()
+    global global_random_state
+    if not seeded or global_random_state is None:
+        global_random_state = gmpy2.random_state()
     x = zero
     if full_range:
         x = gmpy2.mul_2exp(one, bit_size - 1)
     tmp = 0
     if bit_size < 33:
-        tmp = gmpy2.mpz_random(seeded, 2 ** 64)
+        tmp = gmpy2.mpz_random(global_random_state, 2 ** 64)
         temp = (1 << bit_size)
         x = gmpy2.f_mod(tmp, temp)
         if include_negative_range:
@@ -90,23 +94,23 @@ def generate_random(bit_size, include_negative_range, seeded, full_range):
             x = gmpy2.sub(x, tmp)
         return x
     for i in range(bit_size - 32, 0 - 1, -32):
-        tmp = gmpy2.mpz_random(seeded, 2 ** 64)
+        tmp = gmpy2.mpz_random(global_random_state, 2 ** 64)
         tmp = gmpy2.mul_2exp(tmp, i)
         x = gmpy2.add(x, tmp)
-    x = gmpy2.add(x, gmpy2.mpz_random(seeded, 2 ** 64))
+    x = gmpy2.add(x, gmpy2.mpz_random(global_random_state, 2 ** 64))
     if include_negative_range:
         tmp = gmpy2.mul_2exp(one, bit_size - 1)
         x = gmpy2.sub(x, tmp)
     return mpz(x)
         
-def generate_x(sk):
+def generate_x(x, sk):
     gmpy2.random_state()
     q, r = 0, 0
[…]

### 2019-02-08 dghv/dghv_shorter_public_key.py
Addition functional
Addition works but multiplication is bugged

@@ -139,14 +139,14 @@ class cryptosystem:
     def generate_secret_key(self):
         tmp = mpz()
         self.sk = mpz(2)**(eta - mpz(1))
-        random_state = gmpy2.random_state()
+        random_state = gmpy2.random_state(mpz(time.time()))
         i = eta - 32
         while i >= 0:
-            tmp = gmpy2.mpz_random(random_state, 2 ** 64)
+            tmp = gmpy2.mpz_random(random_state, RAND_MAX)
             tmp = tmp * (mpz(2)**i)
             self.sk += tmp
             i -= 32
-        self.sk += gmpy2.mpz_random(random_state, 2 ** 64)
+        self.sk += gmpy2.mpz_random(random_state, RAND_MAX)
         self.sk = self.sk * 2 + 1
 
     def generate_public_key(self):
@@ -155,13 +155,13 @@ class cryptosystem:
         temp = (gamma - eta) // (Lambda**2) + 1
 
         for i in range(temp):
-            print('public key generation phase 1/2: iteration', i+1, 'of', temp)
+            print('public key generation phase 1/2: iteration', i + 1, 'of', temp)
             tmp = generate_random( Lambda**2, False, False, True)
             tmp = gmpy2.next_prime(tmp)
             self.pk[0] *= tmp
 
         for i in range(1, 2 * beta + 1):
-            print('public key generation phase 2/2: iteration', i+1, 'of', 2 * beta + 1)
+            print('public key generation phase 2/2: iteration', i + 1, 'of', 2 * beta + 1)
             self.pk[i] = generate_x(self.pk[i], self.sk)
             while self.pk[i] >= self.pk[0]:
                 self.pk[i] = generate_x(self.pk[i], self.sk)
@@ -245,7 +245,7 @@ def two_for_three_trick(a, b, c, pkc):
     temp_3 = pkc.XOR_GATE(a, b)
     temp_3 = pkc.AND_GATE(temp_3, c)
     temp_1 = pkc.XOR_GATE(temp_1, temp_3)
-    return temp_1, temp2
+    return temp_1, temp_2
 
 class ciphertext:
     def __init__(self, pkc=None, m=None):
@@ -276,7 +276,7 @@ class ciphertext:
         result.degree = max(self.degree, other.degree)
         return result
 
-    def __mult__(self, other):
[…]

### 2019-02-08 dghv/dghv_utils.py

@@ -18,6 +18,7 @@ theta = 15
 n = 4
 kappa = 161569 + 2 + n
 e = 0
+RAND_MAX = 1 << rho + 1
 
 def sort_utility(array, l, m, r):
     n_1 = m - l + 1
@@ -69,8 +70,6 @@ def bit_size(x):
     return temp
 
 def mpz_mod_modified(op1, op2):
-    print(op1)
-    print(op2)
     rop = gmpy2.f_mod(mpz(op1), mpz(op2))
     temp = gmpy2.f_div(mpz(op2), two)
     if rop > temp:
@@ -86,7 +85,7 @@ def generate_random(bit_size, include_negative_range, seeded, full_range):
         x = gmpy2.mul_2exp(one, bit_size - 1)
     tmp = 0
     if bit_size < 33:
-        tmp = gmpy2.mpz_random(global_random_state, 2 ** 64)
+        tmp = gmpy2.mpz_random(global_random_state, RAND_MAX)
         temp = (1 << bit_size)
         x = gmpy2.f_mod(tmp, temp)
         if include_negative_range:
@@ -94,10 +93,10 @@ def generate_random(bit_size, include_negative_range, seeded, full_range):
             x = gmpy2.sub(x, tmp)
         return x
     for i in range(bit_size - 32, 0 - 1, -32):
-        tmp = gmpy2.mpz_random(global_random_state, 2 ** 64)
+        tmp = gmpy2.mpz_random(global_random_state, RAND_MAX)
         tmp = gmpy2.mul_2exp(tmp, i)
         x = gmpy2.add(x, tmp)
-    x = gmpy2.add(x, gmpy2.mpz_random(global_random_state, 2 ** 64))
+    x = gmpy2.add(x, gmpy2.mpz_random(global_random_state, RAND_MAX))
     if include_negative_range:
         tmp = gmpy2.mul_2exp(one, bit_size - 1)
         x = gmpy2.sub(x, tmp)
@@ -139,7 +138,7 @@ def generate_sparse_matrix(u_1, modified_secret_key, x_p):
     count = theta - 1
     gmpy2.random_state()
     while count > 0:
-        index = gmpy2.mpz_random(global_random_state, 2 ** 64) % Theta
+        index = gmpy2.mpz_random(global_random_state, RAND_MAX) % Theta
         if not modified_secret_key[index]:
             modified_secret_key[index] = True
             count -= 1

### 2019-02-08 dghv/dghv_shorter_public_key.py
Some bugfixes

@@ -48,10 +48,10 @@ class binary_real:
 
         carry = False
         for i in range(prec):
-            if int(self.value[prec - i - 1]) + int(other.value[prec - i - i]) + int(carry) == 3:
+            if int(self.value[prec - i - 1]) + int(other.value[prec - i - 1]) + int(carry) == 3:
                 bits.append(True)
                 carry = True
-            elif int(self.value[prec - i - 1]) + int(other.value[prec - i - i]) + int(carry) == 2:
+            elif int(self.value[prec - i - 1]) + int(other.value[prec - i - 1]) + int(carry) == 2:
                 bits.append(False)
                 carry = True
             else:
@@ -107,9 +107,9 @@ class cryptosystem:
 
         enc_sk_file_check = Path('encrypted_sk_and_seed.txt')
         if not enc_sk_file_check.is_file():
-            x_p = mpz(2) ** kappa
+            x_p = gmpy2.mul_2exp(1, kappa)
             x_p = gmpy2.f_div(x_p, self.sk)
-            self.seed = generate_sparse_matrix(self.u_1, self.modified_secret_key, x_p)
+            self.seed, self.u_1 = generate_sparse_matrix(self.u_1, self.modified_secret_key, x_p)
             for i in range(Theta):
                 if self.modified_secret_key[i] is True:
                     self.encrypted_sk[i] = self.symmetric_encryption(self.encrypted_sk[i], 1)
@@ -138,12 +138,12 @@ class cryptosystem:
 
     def generate_secret_key(self):
         tmp = mpz()
-        self.sk = mpz(2)**(eta - mpz(1))
+        self.sk = gmpy2.mul_2exp(1, eta - 1)
         random_state = gmpy2.random_state(mpz(time.time()))
         i = eta - 32
         while i >= 0:
             tmp = gmpy2.mpz_random(random_state, RAND_MAX)
-            tmp = tmp * (mpz(2)**i)
+            tmp = gmpy2.mul_2exp(tmp, i)
             self.sk += tmp
             i -= 32
         self.sk += gmpy2.mpz_random(random_state, RAND_MAX)
@@ -203,22 +203,23 @@ class cryptosystem:
         return (ct_1 + ct_2) % self.pk[0]
 
     def NOT_GATE(self, ct_1):
-        return XOR_GATE(ct_1, 1)
[…]

### 2019-02-08 dghv/dghv_utils.py

@@ -151,5 +151,5 @@ def generate_sparse_matrix(u_1, modified_secret_key, x_p):
     u_1 = gmpy2.sub(x_p, sum_)
     if u_1 < zero:
         u_1 = gmpy2.add(temp, u_1)
-    return seed
+    return mpz(seed), mpz(u_1)
 

### 2019-02-08 dghv/dghv_shorter_public_key.py
Generated keys for dghv

@@ -107,8 +107,8 @@ class cryptosystem:
 
         enc_sk_file_check = Path('encrypted_sk_and_seed.txt')
         if not enc_sk_file_check.is_file():
-            x_p = gmpy2.mul_2exp(1, kappa)
-            x_p = gmpy2.f_div(x_p, self.sk)
+            x_p = mpz(gmpy2.mul_2exp(1, kappa))
+            x_p = mpz(gmpy2.f_div(x_p, self.sk))
             self.seed, self.u_1 = generate_sparse_matrix(self.u_1, self.modified_secret_key, x_p)
             for i in range(Theta):
                 if self.modified_secret_key[i] is True:
@@ -147,7 +147,7 @@ class cryptosystem:
             self.sk += tmp
             i -= 32
         self.sk += gmpy2.mpz_random(random_state, RAND_MAX)
-        self.sk = self.sk * 2 + 1
+        self.sk = mpz(self.sk * 2 + 1)
 
     def generate_public_key(self):
         tmp = mpz()
@@ -376,9 +376,9 @@ print('0 * 1:', (a*b).decrypt())
 print('1 * 1:', (b*b).decrypt())
 c = ciphertext(pkc, 1)
 for i in range(10):
-    c = c + ciphertext(pkc, 1)
+    print('+',i%2,'=')
+    c = c + ciphertext(pkc, i%2)
     #c.recrypt(pkc)
     print(c.decrypt())
-    if i % 3 == 0:
-        c.recrypt(pkc)
+    #c.recrypt(pkc)
 

### 2019-02-08 dghv/dghv_adapter.py
Adapted to integers

@@ -1,0 +1,176 @@
+import math
+import random
+import sys
+import bitstring
+from dghv_shorter_public_key import cryptosystem as dghv_system
+from dghv_shorter_public_key import ciphertext as  dghv_text
+""" class DGHV_FP(object):
+    
+    def __init__(self):
+        self.dp = DasguptaPalInteger()
+        self.R_k = self.dp.R_k
+        self.BASE = 16
+        self.LOG2_BASE = math.log(self.BASE, 2)
+        self.FLOAT_MANTISSA_BITS = sys.float_info.mant_dig
+
+    def fp2pair(self,scalar):
+        if isinstance(scalar, int):
+            exponent = 0
+        elif isinstance(scalar, float):
+            bin_flt_exponent = math.frexp(scalar)[1]
+            bin_lsb_exponent = bin_flt_exponent - self.FLOAT_MANTISSA_BITS
+            exponent = math.floor(bin_lsb_exponent / self.LOG2_BASE)
+        neg = False
+        if scalar < 0:
+            neg = True
+            scalar = -scalar
+        int_rep = int(round(scalar * pow(self.BASE, -exponent)))
+        if neg:
+            int_rep = -int_rep
+        return {'mantissa':int_rep, 'exponent':exponent}
+
+    def pair2fp(self,pair):
+        neg = False
+        if pair['mantissa'] < 0:
+            neg = True
+            pair['mantissa'] = -pair['mantissa']
+        result = pair['mantissa'] * pow(self.BASE, pair['exponent'])
+        if neg:
+            result = -result
+        return result
+
+    def encrypt(self,fp):
+        pair = self.fp2pair(fp)
+        pair['mantissa'] = self.dp.encrypt(pair['mantissa'])
+        return pair
+
+    def decrypt(self,pair):
+        pair['mantissa'] = self.dp.decrypt(pair['mantissa'])
+        return self.pair2fp(pair)
+
+    def add(self,a,b):
+        if a['exponent'] <= b['exponent']:
+            mantissa = self.dp.add(a['mantissa'],self.dp.multiplyc(b['mantissa'], int(self.BASE**(b['exponent']-a['exponent']))))
+            exponent = a['exponent']
+        else:
+            mantissa = self.dp.add(b['mantissa'],self.dp.multiplyc(a['mantissa'], int(self.BASE**(a['exponent']-b['exponent']))))
+            exponent = b['exponent']
[…]

### 2019-02-08 dghv/dghv_shorter_public_key.py

@@ -257,6 +257,7 @@ class ciphertext:
             self.degree = 1
             self.pkc = pkc
             self.value = mpz(pkc.encrypt_bit(m))
+            print('encrypting bit', m)
 
     def decrypt(self):
         return self.pkc.decrypt_bit(self.value)
@@ -363,22 +364,22 @@ class ciphertext:
 
 
 # driver
-pkc = cryptosystem()
-a = ciphertext(pkc, 0)
-b = ciphertext(pkc, 1)
-print('0 + 0:', (a+a).decrypt())
-print('1 + 0:', (b+a).decrypt())
-print('0 + 1:', (a+b).decrypt())
-print('1 + 1:', (b+b).decrypt())
-print('0 * 0:', (a*a).decrypt())
-print('1 * 0:', (b*a).decrypt())
-print('0 * 1:', (a*b).decrypt())
-print('1 * 1:', (b*b).decrypt())
-c = ciphertext(pkc, 1)
-for i in range(10):
-    print('+',i%2,'=')
-    c = c + ciphertext(pkc, i%2)
-    #c.recrypt(pkc)
-    print(c.decrypt())
-    #c.recrypt(pkc)
+# pkc = cryptosystem()
+# a = ciphertext(pkc, 0)
+# b = ciphertext(pkc, 1)
+# print('0 + 0:', (a+a).decrypt())
+# print('1 + 0:', (b+a).decrypt())
+# print('0 + 1:', (a+b).decrypt())
+# print('1 + 1:', (b+b).decrypt())
+# print('0 * 0:', (a*a).decrypt())
+# print('1 * 0:', (b*a).decrypt())
+# print('0 * 1:', (a*b).decrypt())
+# print('1 * 1:', (b*b).decrypt())
+# c = ciphertext(pkc, 1)
+# for i in range(10):
+#     print('+',i%2,'=')
+#     c = c + ciphertext(pkc, i%2)
+#     #c.recrypt(pkc)
+#     print(c.decrypt())
+#     #c.recrypt(pkc)
 

### 2019-02-08 dghv/dghv_adapter.py
Disabled refresh for now

@@ -108,9 +108,10 @@ class DGHV_Integer(object):
         return bitstring.BitArray(num).int
 
     def refresh(self, c):
-        for ci in c:
-            ci.recrypt(self.system)
-    
+        #for ci in c:
+        #    ci.recrypt(self.system)
+        return
+
     # binary operation primitives
     def xor_bits(self, x, y):
         return x + y
@@ -127,7 +128,7 @@ class DGHV_Integer(object):
     def shift_poly(self, p, x):
         return ([dghv_text(self.system, 0) for i in range(x)] + p)[:self.n]
     def nby1_poly(self, p, x):
-        return [and_bits(a,x) for a in p]
+        return [self.and_bits(a,x) for a in p]
     
     def add(self, A,B):
         result = []
@@ -150,11 +151,12 @@ class DGHV_Integer(object):
         return self.add(p1, self.encrypt(k))
     
     def multiply(self,p1,p2):
-        product = [0]*self.n
+        product = [dghv_text(self.system, 0) for i in range(self.n)]
         for i in range(len(p2)):
             partial_sum = self.shift_poly(self.nby1_poly(p1,p2[i]),i)
             product = self.add(product, partial_sum)
-        product = self.refresh(product)[:self.n]
+        product = product[:self.n]
+        self.refresh(product)
         return product
     
     def multiplyc(self,p1,k):
@@ -167,7 +169,7 @@ class DGHV_Integer(object):
 
 dghvcs = DGHV_Integer()
 a = dghvcs.encrypt(5)
-b = dghvcs.encrypt(7)
+b = dghvcs.encrypt(-7)
 c = dghvcs.add(a,b)
 d = dghvcs.multiply(a,b)
 print(dghvcs.decrypt(a))

### 2019-02-08 paper/icmssp2019-sigconf.tex
Renamed main tex file
Started edits

--- 2019-01-13 paper/PCSC2019-sigconf.tex
@@
 \affaddr{Ateneo de Manila University}\\
-\affaddr{Katipunan Ave., Loyola Heights}\\
-\affaddr{Quezon City, Philippines 1108}\\
+\affaddr{Katipunan Avenue, Loyola Heights}\\
+\affaddr{Quezon City, Philippines}\\
 \email{aldrich.asuncion@obf.ateneo.edu}
@@
 \affaddr{Ateneo de Manila University}\\
-\affaddr{Katipunan Ave., Loyola Heights}\\
-\affaddr{Quezon City, Philippines 1108}\\
+\affaddr{Katipunan Avenue, Loyola Heights}\\
+\affaddr{Quezon City, Philippines}\\
 \email{brian.guadalupe@obf.ateneo.edu}
@@
 \maketitle
-% The default list of authors is too long for headers.
-% \renewcommand{\shorttitle}{Impl. and Analysis of Homomorphic Facial Image Encryption and Manipulation}
-% \renewcommand{\shortauthors}{A. Asuncion and B. Guadalupe}
 
@@
 Homomorphic cryptography allows for encrypted data to be modified and operated on without requiring decryption, although current homomorphic cryptosystems are either limited in their permitted operations or are significantly more time-intensive than standard non-homomorphic cryptosystems.
-Regardless, homomorphic cryptography has been targeted for use in secure image processing and facial recognition, due to their ability to maintain data privacy, In this paper, we compared the viability of the Paillier, Damg{\aa}rd--Geisler--Kr{\o}igaard (DGK), Dasgupta--Pal, and Brakerski--Gentry--Vaikuntanathan (BGV) cryptosystems for facial image processing applications, by implementing a software library equipped with these cryptosystems, and comparing their time efficiency and accuracy.
+Regardless, homomorphic cryptography has been targeted for use in secure image processing and facial recognition, due to their ability to maintain data privacy.
+In this paper, we compared the viability of the Paillier, Damg{\aa}rd--Geisler--Kr{\o}igaard (DGK), Dasgupta--Pal, and Brakerski--Gentry--Vaikuntanathan (BGV) cryptosystems for facial image processing applications, by implementing a software library equipped with these cryptosystems, and comparing their time efficiency and accuracy.
 Furthermore, as an extension to previous research, we attempt to support non-linear image processing operations.
@@
   <concept>
-  <concept_id>10002950.10003714.10003736.10003737</concept_id>
-  <concept_desc>Mathematics of computing~Approximation</concept_desc>
-  <concept_significance>300</concept_significance>
-  </concept>
-  <concept>
-  <concept_id>10002950.10003714.10003740</concept_id>
-  <concept_desc>Mathematics of computing~Quadrature</concept_desc>
-  <concept_significance>100</concept_significance>
-  </concept>
   </ccs2012>
@@
 \ccsdesc[500]{Computing methodologies~Image processing}
-\ccsdesc[300]{Mathematics of computing~Approximation}
-\ccsdesc[100]{Mathematics of computing~Quadrature}
 
 \printccsdesc
-\keywords{cryptography; homomorphic encryption; data privacy; image processing; intensity transformation; facial recognition; numerical approximations}
+\keywords{cryptography; homomorphic encryption; data privacy; image processing; intensity transformation; facial recognition}
 
@@
 \section{Acknowledgments}
-We would like to thank our adviser Dr.
-William Emmanuel S.
-Yu for his guidance and constant feedback, and our panelists Dr.
-Andrei D.
-Coronel and Dr.
-Mari-jo P.
-Ruiz for lending their expertise and for giving their invaluable comments and insights.
+% We would like to thank our adviser Dr. William Emmanuel S. Yu for his guidance and constant feedback, and 
+We would like to thank our panelists Dr. Andrei D. Coronel and Dr. Mari-Jo P. Ruiz for lending their expertise and for giving their invaluable comments and insights.
 Due acknowlegement is also given to the University of Essex for making the \texttt{faces94} dataset publicly available for research purposes.
@@
 
-\appendix
-\input{appendix}
-\balancecolumns
+% \appendix
+% \input{appendix}
+% \balancecolumns
 

### 2019-02-08 paper/paper-conf.tex
Started edits

--- 2019-01-13 paper/paper-conf.tex
@@
 
-\subsection{Research Questions}
-By implementing homomorphic cryptosystems and creating a library so they can be easily used, we aim to address our main research question: What is the best method for facial image data to be encrypted and manipulated for practical applications?
+% \subsection{Research Questions}
+% By implementing homomorphic cryptosystems and creating a library so they can be easily used, we aim to address our main research question: What is the best method for facial image data to be encrypted and manipulated for practical applications?
 
-More specifically, our research will address the following sub-questions:
-\begin{enumerate}
-	\item Which homomorphic cryptosystems admit more image processing operations? How can existing homomorphic cryptosystems be modified to admit more image processing operations?
-	\item Which homomorphic cryptosystems are the most time-efficient and the most accurate in applying image processing operations?
-	\item Which homomorphic cryptosystems best preserve image quality in applying image processing operations?
-\end{enumerate}
+% More specifically, our research will address the following sub-questions:
+% \begin{enumerate}
+% 	\item Which homomorphic cryptosystems admit more image processing operations? How can existing homomorphic cryptosystems be modified to admit more image processing operations?
+% 	\item Which homomorphic cryptosystems are the most time-efficient and the most accurate in applying image processing operations?
+% 	\item Which homomorphic cryptosystems best preserve image quality in applying image processing operations?
+% \end{enumerate}
 
@@
 
-There are two kinds of cryptosystems, \textit{symmetric} and \textit{asymmetric}.
+% There are two kinds of cryptosystems, \textit{symmetric} and \textit{asymmetric}.
 In symmetric-key cryptosystems, the same key is used for both encryption and decryption.
@@
 
-On the other hand, asymmetric-key (or public-key) cryptosystems use separate keys for encryption and decryption.
+% On the other hand, asymmetric-key (or public-key) cryptosystems use separate keys for encryption and decryption.
 The encryption key (also called the \textit{public key}) is shared publicly, while the decryption key (also called the \textit{private key}) is kept secret.
@@
 \end{equation}
+
 In other words, a homomorphic cryptosystem preserves the operations that can be done with the plaintext without requiring an intermediary step of decrypting the ciphertext beforehand.
@@
 The scheme allows for the encryption and decryption of integer messages, and is known to be additively homomorphic.
-We now state the encryption and decryption algorithms of the Paillier cryptosystem and its homomorphic properties.
+% We now state the encryption and decryption algorithms of the Paillier cryptosystem and its homomorphic properties.
 
-\paragraph{Key Generation}
-We first define a function $L(x)$ as the largest integer $v$ greater than zero such that $x-1 \geq vn$.
-We choose two large primes $p$ and $q$, and set $n = pq, \lambda = \mathrm{lcm}(p-1,q-1)$.
-Then we select an integer $g$, $0\leq g \leq n^2$ such that $\mathrm{gcd}(L(g^\lambda \bmod n^2), n) = 1$.
-We denote the public key as $(g,n)$ and the private key $(p,q)$.
+% \paragraph{Key Generation}
+% We first define a function $L(x)$ as the largest integer $v$ greater than zero such that $x-1 \geq vn$.
+% We choose two large primes $p$ and $q$, and set $n = pq, \lambda = \mathrm{lcm}(p-1,q-1)$.
+% Then we select an integer $g$, $0\leq g \leq n^2$ such that $\mathrm{gcd}(L(g^\lambda \bmod n^2), n) = 1$.
+% We denote the public key as $(g,n)$ and the private key $(p,q)$.
 
-\paragraph{Encryption and Decryption}
-The encryption function to encrypt a plaintext $m \in \mathbb{Z}_n$ given a public key $(g,n)$ is defined as
-\begin{align*}
-  E(m) = g^m \cdot r^n \mod{n^2},
-\end{align*}
-where $r$ is a random non-negative integer less than $n^2$.
+% \paragraph{Encryption and Decryption}
+% The encryption function to encrypt a plaintext $m \in \mathbb{Z}_n$ given a public key $(g,n)$ is defined as
+% \begin{align*}
+%   E(m) = g^m \cdot r^n \mod{n^2},
+% \end{align*}
+% where $r$ is a random non-negative integer less than $n^2$.
 
-The decryption function to decrypt a ciphertext $c \in \mathbb{Z}^\ast_{n^2}$ given a private key $(p,q)$ is defined as:
-\begin{align*}
-  D(c) = L(c^\lambda \bmod n^2) \times (L(g^\lambda \bmod n^2))^{-1} \mod n
-\end{align*}
+% The decryption function to decrypt a ciphertext $c \in \mathbb{Z}^\ast_{n^2}$ given a private key $(p,q)$ is defined as:
+% \begin{align*}
+%   D(c) = L(c^\lambda \bmod n^2) \times (L(g^\lambda \bmod n^2))^{-1} \mod n
+% \end{align*}
 
@@
 
-\paragraph{Key Generation}
-We denote $k,t,\ell$ as security parameters of the scheme, where $k>t>\ell$.
-Let $p,q$ be primes such that
-we can choose two $t$-bit primes $v_p$ and $v_q$ such that $v_p | (p-1)$ and $v_q | (q-1)$, and a small prime $u$ such that $u | (p-1)$ and $u | (q-1)$.
-We denote $n = pq$.
-We choose $g$ to be an integer of order $uv_pv_q$ and $h$ to be of order $v_pv_q$.
+% \paragraph{Key Generation}
+% We denote $k,t,\ell$ as security parameters of the scheme, where $k>t>\ell$.
+% Let $p,q$ be primes such that
+% we can choose two $t$-bit primes $v_p$ and $v_q$ such that $v_p | (p-1)$ and $v_q | (q-1)$, and a small prime $u$ such that $u | (p-1)$ and $u | (q-1)$.
+% We denote $n = pq$.
+% We choose $g$ to be an integer of order $uv_pv_q$ and $h$ to be of order $v_pv_q$.
 
-The DGK cryptosystem encrypts plaintexts in $\mathbb{Z}_u$ to ciphertexts in $\mathbb{Z}_n^\ast$.
+% The DGK cryptosystem encrypts plaintexts in $\mathbb{Z}_u$ to ciphertexts in $\mathbb{Z}_n^\ast$.
 
-The public key is $(n,g,h,u)$ and the private key is $(p,q,v_p,v_q)$.
+% The public key is $(n,g,h,u)$ and the private key is $(p,q,v_p,v_q)$.
 
-\paragraph{Encryption and Decryption}
-To encrypt a message $m \in \mathbb{Z}_u$, the encryption function is defined as:
-\begin{align*}
-  E(m) = g^m \cdot h^r \mod{n},
-\end{align*}
-where $r$ is a random integer in $\mathbb{Z}_n$ which is longer than $2t$ bits.
+% \paragraph{Encryption and Decryption}
+% To encrypt a message $m \in \mathbb{Z}_u$, the encryption function is defined as:
+% \begin{align*}
+%   E(m) = g^m \cdot h^r \mod{n},
+% \end{align*}
+% where $r$ is a random integer in $\mathbb{Z}_n$ which is longer than $2t$ bits.
 
-To decrypt a ciphertext $c \in \mathbb{Z}_n^\ast$, decryption is achieved by first computing $c^{v_pv_q}$.
-\begin{align*}
-	c^{v_pv_q} \bmod n
-	&= (g^m \cdot h^r)^{v_pv_q} \bmod n\\
-	&= (g^{v_pv_q})^m \bmod n
-\end{align*}
-Since $(g^{v_pv_q})^m$ has order $u$, there is a one-to-one correspondence between plaintexts in $\mathbb{Z}_u$ and  $(g^{v_pv_q})^m$.
+% To decrypt a ciphertext $c \in \mathbb{Z}_n^\ast$, decryption is achieved by first computing $c^{v_pv_q}$.
+% \begin{align*}
+% 	c^{v_pv_q} \bmod n
+% 	&= (g^m \cdot h^r)^{v_pv_q} \bmod n\\
+% 	&= (g^{v_pv_q})^m \bmod n
+% \end{align*}
+% Since $(g^{v_pv_q})^m$ has order $u$, there is a one-to-one correspondence between plaintexts in $\mathbb{Z}_u$ and  $(g^{v_pv_q})^m$.
 A lookup table can thus be generated privately to successfully recover $m$.
@@
 \label{ssec:exponentiationprotocol}
-In order to perform polynomial evaluation, we first present a protocol for privacy-preserving exponentiation to a positive integer power, adapted from the protocol to calculate Euclidean distances used in \cite{hutchison_privacy-preserving_2009}.
+[TO-DO: This is further explained in another paper.]
+% In order to perform polynomial evaluation, we first present a protocol for privacy-preserving exponentiation to a positive integer power, adapted from the protocol to calculate Euclidean distances used in \cite{hutchison_privacy-preserving_2009}.
 
-The following protocols apply to both the Paillier and DGK cryptosystems, as they share similar homomorphisms. We first present a secure squaring protocol.
+% The following protocols apply to both the Paillier and DGK cryptosystems, as they share similar homomorphisms. We first present a secure squaring protocol.
 
-Suppose Alice encrypts an integer $x$ and sends it so Bob has $E(x)$, and wants to obtain $E(x^2)$ without exposing the value of $x$.
-\begin{itemize}
-	\item Bob first selects a random integer $r$ and computes $E(x+r)$. Bob can do this since $r$ is a plaintext constant.
-	\item Bob sends $E(x+r)$ to Alice, who decrypts the ciphertext to obtain $x+r$.
-	\item Alice squares $x+r$ and encrypts the result. She sends $E((x+r)^2)$ to Bob.
-	\item Bob computes $E(-2rx + r^2)$. He then computes $E((x+r)^2)E(-2rx + r^2) = E(x^2)$.
-\end{itemize}
+% Suppose Alice encrypts an integer $x$ and sends it so Bob has $E(x)$, and wants to obtain $E(x^2)$ without exposing the value of $x$.
+% \begin{itemize}
+% 	\item Bob first selects a random integer $r$ and computes $E(x+r)$. Bob can do this since $r$ is a plaintext constant.
+% 	\item Bob sends $E(x+r)$ to Alice, who decrypts the ciphertext to obtain $x+r$.
+% 	\item Alice squares $x+r$ and encrypts the result. She sends $E((x+r)^2)$ to Bob.
+% 	\item Bob computes $E(-2rx + r^2)$. He then computes $E((x+r)^2)E(-2rx + r^2) = E(x^2)$.
+% \end{itemize}
 
-We can use the secure squaring protocol to arrive at a secure multiplication protocol, which then allows for the evaluation of polynomials.
-Suppose Alice encrypts integers $x$ and $y$, and Bob has $E(x), E(y)$ and wants to obtain $E(xy)$.
-\begin{itemize}
-	\item Bob acquires $E(x^2), E(y^2)$ using the secure squaring protocol.
-	\item Bob sends $E(x+y)$ to Alice, who decrypts the ciphertext to obtain $x+y$.
-	\item Alice sends $E((x+y)^2)$ to Bob.
-	\item Bob then computes
-	\begin{align*}
-		E((x+y)^2)E(x^2)^{-1}E(y^2)^{-1} &= E((x+y)^2 - x^2 - y^2)\\
-		&= E(2xy)
-	\end{align*}
-	\item Bob can then recover $E(xy)$ by calcuating for the multiplicative inverse of 2 using the Euclidean algorithm, and calculating $2^{-1}E(xy)$.
+% We can use the secure squaring protocol to arrive at a secure multiplication protocol, which then allows for the evaluation of polynomials.
+% Suppose Alice encrypts integers $x$ and $y$, and Bob has $E(x), E(y)$ and wants to obtain $E(xy)$.
+% \begin{itemize}
+% 	\item Bob acquires $E(x^2), E(y^2)$ using the secure squaring protocol.
+% 	\item Bob sends $E(x+y)$ to Alice, who decrypts the ciphertext to obtain $x+y$.
+% 	\item Alice sends $E((x+y)^2)$ to Bob.
+% 	\item Bob then computes
+% 	\begin{align*}
+% 		E((x+y)^2)E(x^2)^{-1}E(y^2)^{-1} &= E((x+y)^2 - x^2 - y^2)\\
+% 		&= E(2xy)
+% 	\end{align*}
+% 	\item Bob can then recover $E(xy)$ by calcuating for the multiplicative inverse of 2 using the Euclidean algorithm, and calculating $2^{-1}E(xy)$.
 Such an inverse exists since the modulus is either a prime (in the DGK cryptosystem) or a product of primes greater than 2 (in the Paillier cryptosystem).
-\end{itemize}
+% \end{itemize}
 
@@
 
-In the enrollment process, $M$ face images $\Theta_1, \ldots, \Theta_M$, each of size $p \times q$, are taken in to comprise the initial training set.
+% In the enrollment process, $M$ face images $\Theta_1, \ldots, \Theta_M$, each of size $p \times q$, are taken in to comprise the initial training set.
 The training images can be represented as vectors of length $N = pq$, where each row of an image is concatenated together.
 
-The average of the training images, denoted as $\Psi$, is 
-\begin{equation}
-	\Psi = \frac{1}{M} \sum_{i=1}^{M} \Theta_i
-\end{equation}
+% The average of the training images, denoted as $\Psi$, is 
+% \begin{equation}
+% 	\Psi = \frac{1}{M} \sum_{i=1}^{M} \Theta_i
+% \end{equation}
 
-The \textit{difference vectors} are then computed as $\Phi_i = \Theta_i - \Psi$. PCA is applied on the covariance matrix of the vectors
-\begin{equation}
-	\mathbf{C} = \frac{1}{M} \sum_{i=1}^M \Phi_i \Phi_i^\top = \frac{1}{M} \mathbf{A}\mathbf{A}^\top,
-\end{equation}
-where $\mathbf{A}$ is an $N \times M$ matrix defined by $\left[\Theta_1 \quad \Theta_2 \quad \cdots \quad \Theta_M\right]$, in order to determine the orthonormal eigenvectors \cite{hutchison_privacy-preserving_2009}.
+% The \textit{difference vectors} are then computed as $\Phi_i = \Theta_i - \Psi$. PCA is applied on the covariance matrix of the vectors
+% \begin{equation}
+% 	\mathbf{C} = \frac{1}{M} \sum_{i=1}^M \Phi_i \Phi_i^\top = \frac{1}{M} \mathbf{A}\mathbf{A}^\top,
+% \end{equation}
+% where $\mathbf{A}$ is an $N \times M$ matrix defined by $\left[\Theta_1 \quad \Theta_2 \quad \cdots \quad \Theta_M\right]$, in order to determine the orthonormal eigenvectors \cite{hutchison_privacy-preserving_2009}.
 
-Directly computing the covariance matrix and then applying PCA will become inefficient for large sizes of $\mathbf{A}$, since computing for $\mathbf{A}\mathbf{A}^\top$ results in an $N \times N$ matrix, which can get drastically large because it is dependent on the size of the image.
+% Directly computing the covariance matrix and then applying PCA will become inefficient for large sizes of $\mathbf{A}$, since computing for $\mathbf{A}\mathbf{A}^\top$ results in an $N \times N$ matrix, which can get drastically large because it is dependent on the size of the image.
 On the other hand, computing for $\mathbf{A}^\top\mathbf{A}$ only results in an $M \times M$ matrix, which is much smaller than the previous one because it is just dependent on the number of face images in the training set.
@@
 
-Instead of getting the eigendecomposition of the covariance matrix by explicitly computing the eigenvalues and eigenvectors of $\mathbf{C}$, we can also apply \textit{singular value decomposition} (SVD) on the matrix $\Phi^\top$.
+% Instead of getting the eigendecomposition of the covariance matrix by explicitly computing the eigenvalues and eigenvectors of $\mathbf{C}$, we can also apply \textit{singular value decomposition} (SVD) on the matrix $\Phi^\top$.
 This is because SVD works through a divide-and-conquer method which results in greater numerical stability, while eigendecomposition simply uses the traditional QR factorization \cite{nakatsukasa_stable_2013, gu_divide-and-conquer_1995}.
@@
 
-We choose $K$ eigenvectors $\mathbf{u}_1, \ldots, \mathbf{u}_K$ such that it comprises a set associated with the $K$ largest eigenvalues, where $K$ is much smaller than $M$.
+% We choose $K$ eigenvectors $\mathbf{u}_1, \ldots, \mathbf{u}_K$ such that it comprises a set associated with the $K$ largest eigenvalues, where $K$ is much smaller than $M$.
 This set is now the \textit{face space}.
@@
 
-To perform the recognition process, the algorithm projects the input image $\Gamma$ onto the face space, and then comparing the projected image $\bar{\Omega} = \mathbf{u}_i\left(\Gamma - \Psi\right)$ with each eigenface in the face space using a metric such as the Euclidean distance.
+% To perform the recognition process, the algorithm projects the input image $\Gamma$ onto the face space, and then comparing the projected image $\bar{\Omega} = \mathbf{u}_i\left(\Gamma - \Psi\right)$ with each eigenface in the face space using a metric such as the Euclidean distance.
 Thus it is computed as $d_i = \left\lVert \Omega_i -\bar{\Omega} \right\rVert$ for all $i=1,\ldots,K$, where $\left\lVert \cdot \right\rVert$ denotes the Euclidean norm.
 
-Then, a match can be reported if the smallest possible distance is smaller than the given threshold value $T$. 
-\newcommand{\argmin}{\mathop{\mathrm{arg\,min}}}  
-\begin{equation}
-	\text{ID} = \begin{cases}\argmin_i d_i & \text{if } \min_i d_i \le T \\\emptyset & \text {otherwise}\end{cases}
-\end{equation}
+% Then, a match can be reported if the smallest possible distance is smaller than the given threshold value $T$. 
+% \newcommand{\argmin}{\mathop{\mathrm{arg\,min}}}  
+% \begin{equation}
+% 	\text{ID} = \begin{cases}\argmin_i d_i & \text{if } \min_i d_i \le T \\\emptyset & \text {otherwise}\end{cases}
+% \end{equation}
 
@@
 \subsection{Secure Computation with Real Numbers}
-We will briefly discuss a protocol to enable cryptosystems built for integer inputs to handle real number inputs.
-The following protocol was also used by \textit{CryptoImg} for image processing \cite{ziad_cryptoimg:_2016}.
-This is also used for our own implementation of the Dasgupta--Pal cryptosystem in order to handle real numbers.
+[TO-DO: This is further explained in another paper.]
+% We will briefly discuss a protocol to enable cryptosystems built for integer inputs to handle real number inputs.
+% The following protocol was also used by \textit{CryptoImg} for image processing \cite{ziad_cryptoimg:_2016}.
+% This is also used for our own implementation of the Dasgupta--Pal cryptosystem in order to handle real numbers.
 
-We represent a floating-point (FP) number as a pair of two integers $(m,e)$ representing the mantissa and exponent of the FP number with respect to a base $b$.
+% We represent a floating-point (FP) number as a pair of two integers $(m,e)$ representing the mantissa and exponent of the FP number with respect to a base $b$.
 The mantissa $m$ is encrypted, while the exponent $e$ is unencrypted.
-Let $a,b,c$ be FP numbers represented by the pairs $(m_a,e_a),(m_b,e_b),(m_c,e_c)$ respectively.
+% Let $a,b,c$ be FP numbers represented by the pairs $(m_a,e_a),(m_b,e_b),(m_c,e_c)$ respectively.
 Let $\oplus,\otimes$ represent the homomorphic operations which correspond to the addition and multiplication, respectively.
 We define the secure real number operations as follows:
-\begin{description}
-  \item[Addition.]
-    To compute $E(c)=E(a+b)$ we compute
-    \begin{align*}
-      E(m_c) &= E(m_1) \oplus (b^{e_b-e_a} \otimes E(m_b)), e_c = e_a & \text{ if } e_a \leq e_b \\
-      E(m_c) &= E(m_b) \oplus (b^{e_a-e_b} \otimes E(m_a)), e_c = e_b & \text{ if } e_a > e_b
-    \end{align*}
-  \item[Scalar multiplication.]
-    To compute $E(c) = E(ab)$, where $a$ and $E(b)$ are known (i.e. $m_a$ is not encrypted), we compute
-    \begin{align*}
-      E(m_c) &= m_a \otimes E(m_b)\\
-      e_c &= e_a + e_b
-    \end{align*}
-\end{description}
+% \begin{description}
+%   \item[Addition.]
+%     To compute $E(c)=E(a+b)$ we compute
+%     \begin{align*}
+%       E(m_c) &= E(m_1) \oplus (b^{e_b-e_a} \otimes E(m_b)), e_c = e_a & \text{ if } e_a \leq e_b \\
+%       E(m_c) &= E(m_b) \oplus (b^{e_a-e_b} \otimes E(m_a)), e_c = e_b & \text{ if } e_a > e_b
+%     \end{align*}
+%   \item[Scalar multiplication.]
+%     To compute $E(c) = E(ab)$, where $a$ and $E(b)$ are known (i.e. $m_a$ is not encrypted), we compute
+%     \begin{align*}
+%       E(m_c) &= m_a \otimes E(m_b)\\
+%       e_c &= e_a + e_b
+%     \end{align*}
+% \end{description}
 

### 2019-02-09 dghv/dghv_shorter_public_key.py
Attempt to fix recrypt

@@ -211,14 +211,14 @@ class cryptosystem:
     def recrypt_util(self, encrypted_z, ct, PKC):
         global global_random_state
         u_i = [mpz() for i in range(Theta)]
-        u_i[0] = self.u_1
+        u_i[0] = mpz(self.u_1)
         global_random_state = gmpy2.random_state(self.seed)
 
         for i in range(1, Theta):
             u_i[i] = generate_random(kappa + 1, False, True, False)
 
         z_i = []
-        den = gmpy2.mul_2exp(1, kappa)
+        den = mpz(gmpy2.mul_2exp(1, kappa))
         Sum = binary_real(zero, one, n + e)
 
         for i in range(Theta):
@@ -308,7 +308,7 @@ class ciphertext:
 
         dp = [[ciphertext() for j in range(Theta + 1)] for i in range(2**(n - 1) + 1)]
         W = [[ciphertext() for j in range(n + 1)] for i in range(n + 1 + e)]
-        for i in range(2**(n - 1) + 1):
+        for i in range(1, 2**(n - 1) + 1):
             dp[i][0].custom_setup(0, 1, pkc)
         for i in range(Theta + 1):
             dp[0][i].custom_setup(1, 1, pkc)
@@ -318,12 +318,12 @@ class ciphertext:
                     dp[i][j] = a[j - 1][k] * dp[i - 1][j - 1]
                     dp[i][j] = dp[i][j] + dp[i][j - 1]
 
-        if k < n:
-            for i in range(k + 1):
-                W[k][i].custom_setup(dp[2**(k - i)][Theta].value, dp[2**(k - i)][Theta].degree, pkc)
-        else:
-            for i in range(k + 1 - n, n + 1):
-                W[k][i].custom_setup(dp[2**(k - i)][Theta].value, dp[2**(k - i)][Theta].degree, pkc)
+            if k < n:
+                for i in range(k + 1):
+                    W[k][i].custom_setup(dp[2**(k - i)][Theta].value, dp[2**(k - i)][Theta].degree, pkc)
+            else:
+                for i in range(k + 1 - n, n + 1):
+                    W[k][i].custom_setup(dp[2**(k - i)][Theta].value, dp[2**(k - i)][Theta].degree, pkc)
 
[…]

### 2019-02-09 dghv/dghv_adapter.py
Adapt to flops

@@ -4,11 +4,11 @@ import sys
 import bitstring
 from dghv_shorter_public_key import cryptosystem as dghv_system
 from dghv_shorter_public_key import ciphertext as  dghv_text
-""" class DGHV_FP(object):
+class DGHV_FP(object):
     
     def __init__(self):
-        self.dp = DasguptaPalInteger()
-        self.R_k = self.dp.R_k
+        self.dp = DGHV_Integer()
+        self.n = self.dp.n
         self.BASE = 16
         self.LOG2_BASE = math.log(self.BASE, 2)
         self.FLOAT_MANTISSA_BITS = sys.float_info.mant_dig
@@ -79,11 +79,12 @@ from dghv_shorter_public_key import ciphertext as  dghv_text
         return {'mantissa':mantissa, 'exponent':exponent}
     
     def negate(self,a):
-        return {'mantissa':self.dp.negate(a['mantissa']), 'exponent':a['exponent']} """
+        return {'mantissa':self.dp.negate(a['mantissa']), 'exponent':a['exponent']}
+
 class DGHV_Integer(object):
     def __init__(self):
         self.system = dghv_system()
-        self.n = 8
+        self.n = 70
         print('dghv initialized')
 
     # pairwise add poly
@@ -134,7 +135,6 @@ class DGHV_Integer(object):
         result = []
         carry = dghv_text(self.system, 0)
         for i in range(len(A)):
-            print('addition round', i)
             a = A[i]
             b = B[i]
             c = carry
@@ -167,8 +167,9 @@ class DGHV_Integer(object):
         p = self.add(p,self.encrypt(1))
         return self.refresh(p)
 
-dghvcs = DGHV_Integer()
-a = dghvcs.encrypt(5)
+
+dghvcs = DGHV_FP()
+a = dghvcs.encrypt(5.5)
 b = dghvcs.encrypt(-7)
 c = dghvcs.add(a,b)
 d = dghvcs.multiply(a,b)

### 2019-02-09 dghv/dghv_shorter_public_key.py

@@ -257,7 +257,7 @@ class ciphertext:
             self.degree = 1
             self.pkc = pkc
             self.value = mpz(pkc.encrypt_bit(m))
-            print('encrypting bit', m)
+            #print('encrypting bit', m)
 
     def decrypt(self):
         return self.pkc.decrypt_bit(self.value)
@@ -363,22 +363,22 @@ class ciphertext:
 
 
 # driver
-pkc = cryptosystem()
-a = ciphertext(pkc, 0)
-b = ciphertext(pkc, 1)
-print('0 + 0:', (a+a).decrypt())
-print('1 + 0:', (b+a).decrypt())
-print('0 + 1:', (a+b).decrypt())
-print('1 + 1:', (b+b).decrypt())
-print('0 * 0:', (a*a).decrypt())
-print('1 * 0:', (b*a).decrypt())
-print('0 * 1:', (a*b).decrypt())
-print('1 * 1:', (b*b).decrypt())
-c = ciphertext(pkc, 1)
-for i in range(10):
-    print('+',i%2,'=')
-    c = c + ciphertext(pkc, i%2)
-    c.recrypt(pkc)
-    print(c.decrypt())
+# pkc = cryptosystem()
+# a = ciphertext(pkc, 0)
+# b = ciphertext(pkc, 1)
+# print('0 + 0:', (a+a).decrypt())
+# print('1 + 0:', (b+a).decrypt())
+# print('0 + 1:', (a+b).decrypt())
+# print('1 + 1:', (b+b).decrypt())
+# print('0 * 0:', (a*a).decrypt())
+# print('1 * 0:', (b*a).decrypt())
+# print('0 * 1:', (a*b).decrypt())
+# print('1 * 1:', (b*b).decrypt())
+# c = ciphertext(pkc, 1)
+# for i in range(10):
+    #print('+',i%2,'=')
+    # c = c + ciphertext(pkc, i%2)
     #c.recrypt(pkc)
+    # print(c.decrypt())
+    # c.recrypt(pkc)
 

### 2019-02-09 dgk/dgk.py
Translated DGK from repo
Translated to python from

https://github.com/encryptogroup/ENCRYPTO_utils/blob/master/src/ENCRYPTO_utils/crypto/dgk.cpp

@@ -1,0 +1,223 @@
+import gmpy2
+from gmpy2 import mpz
+import time
+
+global_random_state = None
+
+# utils.cpp
+def aby_prng(Len):
+    """Generates a random mpz with bitlength Len."""
+    global global_random_state
+    if global_random_state is None:
+        global_random_state = gmpy2.random_state(int(time.time()))
+    result = mpz(0)
+    for i in range(Len):
+        if gmpy2.mpz_random(global_random_state, 2) == 1:
+            result += gmpy2.exp2(i)
+    return mpz(result)
+
+
+# new in python 3.7 - "structs"
+from dataclasses import dataclass
+
+# dgk.h
+
+# This represents a DGK public key.
+@dataclass
+class dgk_pubkey:
+    bits: int   # key bits e.g., 1024
+    lbits: int  # share (message) length e.g., 32
+    n: mpz      # public modulus n = pq
+    u: mpz
+    g: mpz
+    h: mpz
+
+@dataclass
+class dgk_prvkey:
+    vp: mpz
+    vq: mpz
+    p: mpz
+    q: mpz
+    p_minusone: mpz
+    q_minusone: mpz
+    pinv: mpz
+    qinv: mpz
+
+# dgk.cpp
+
+DGK_CHECKSIZE = 0
+
+# number of test encryptions and decryptions that are performed to verify a generated key. This will take time, but more are better.
+KEYTEST_ITERATIONS = 1000
+
+powtwo = []
+gvpvqp = []
+
+# Return public key
+def dgk_complete_pubkey(modulusbits, lbits, n, g, h):
+    return dgk_pubkey(modulusbits, 2 * lbits + 2, mpz(n), mpz(1 << (2 * lbits + 2)), mpz(g), mpz(h))
+
+def dgk_keygen(modulusbits, lbits):
+    pub = dgk_pubkey(0,0,0,0,0,0)
+    prv = dgk_prvkey(0,0,0,0,0,0,0,0)
+
+    lbits = lbits * 2 + 2
+
+    pub.bits = modulusbits
+    pub.lbits = lbits
+
+    # vp and vq are primes
+    prv.vp = aby_prng(160)
+    prv.vp = gmpy2.next_prime(prv.vp)
+
+    prv.vq = aby_prng(160)
[…]

### 2019-02-09 dgk/powmod.py

@@ -1,0 +1,2 @@
+import gmpy2
+from gmpy2 import mpz

### 2019-02-09 dgk/utils.py

@@ -1,0 +1,20 @@
+import gmpy2
+from gmpy2 import mpz
+import time
+
+global_random_state = None
+
+def ceil_divide(x, y):
+    return ((((x) + (y) - 1) / (y)))
+
+
+def aby_prng(Len):
+    """Generates a random mpz with bitlength Len."""
+    global global_random_state
+    if global_random_state is None:
+        global_random_state = gmpy2.random_state(int(time.time()))
+    result = mpz(0)
+    for i in range(Len):
+        if gmpy2.mpz_random(global_random_state, 2) == 1:
+            result += gmpy2.exp2(i)
+    return mpz(result)

### 2019-02-09 dgk/dgk.py
extend DGK to positive FP

@@ -211,13 +211,22 @@ def dgk_decrypt(pub, prv, ciphertext):
     
     return res
 
+def add_dgk_ct(pub, x, y):
+    return (x * y) % pub.n
 
-pubkey, privatekey = dgk_keygen(1024, 32)
-a = dgk_encrypt_plain(pubkey, 74)
-b = dgk_encrypt_plain(pubkey, 56)
-c = dgk_decrypt(pubkey,privatekey,a*b)
-d = dgk_decrypt(pubkey,privatekey,a ** 3)
-print('a:',a)
-print('b:',b)
-print('c:',c, 74+56)
-print('d:',d, 74*3)
+def scalar_add_dgk(pub, x, k):
+    return (x * gmpy2.powmod(pub.g,k,pub.n)) % pub.n
+
+def scalar_mul_dgk(pub, x, k):
+    return gmpy2.powmod(x,k,pub.n)
+
+# pubkey, privatekey = dgk_keygen(1024, 32)
+# a = dgk_encrypt_plain(pubkey, 74)
+# b = dgk_encrypt_plain(pubkey, 56)
+# c = dgk_decrypt(pubkey,privatekey,a*b*b*b*b%pubkey.n)
+# d = dgk_decrypt(pubkey,privatekey,a ** 3)
+# print('a:',a)
+# print('b:',b)
+# print('c:',c, 74+56+56+56+56)
+# print('d:',d, 74*3)
+# print(dgk_decrypt(pubkey,privatekey, scalar_add_dgk(pubkey,a,8)))

### 2019-02-09 dgk/dgk_adapter.py

@@ -1,0 +1,83 @@
+import math
+import sys
+import bitstring
+from dgk import *
+
+class DGK_FP(object):
+    
+    def __init__(self):
+        self.pubkey, self.privatekey = dgk_keygen(1024, 32)
+        self.BASE = 16
+        self.LOG2_BASE = math.log(self.BASE, 2)
+        self.FLOAT_MANTISSA_BITS = sys.float_info.mant_dig
+        self.boundary = (self.pubkey.n)
+
+    def fp2pair(self,scalar):
+        if isinstance(scalar, int):
+            exponent = 0
+        elif isinstance(scalar, float):
+            bin_flt_exponent = math.frexp(scalar)[1]
+            bin_lsb_exponent = bin_flt_exponent - self.FLOAT_MANTISSA_BITS
+            exponent = math.floor(bin_lsb_exponent / self.LOG2_BASE)
+        neg = False
+        if scalar < 0:
+            neg = True
+            scalar = -scalar
+        int_rep = int(round(scalar * pow(self.BASE, -exponent)))
+        if neg:
+            int_rep = int_rep + self.boundary
+        return {'mantissa':int_rep, 'exponent':exponent}
+
+    def pair2fp(self,pair):
+        neg = False
+        if pair['mantissa'] >= self.boundary:
+            neg = True
+            pair['mantissa'] -= self.boundary
+        result = pair['mantissa'] * pow(self.BASE, pair['exponent'])
+        if neg:
+            result = -result
+        return result
+
+    def encrypt(self,fp):
+        pair = self.fp2pair(fp)
+        pair['mantissa'] = dgk_encrypt_plain(self.pubkey, pair['mantissa'])
+        return pair
+
+    def decrypt(self,pair):
+        pair['mantissa'] = dgk_decrypt(self.pubkey, self.privatekey, pair['mantissa'])
+        return self.pair2fp(pair)
+
+    def add(self,a,b):
+        if a['exponent'] <= b['exponent']:
+            mantissa = add_dgk_ct(self.pubkey, a['mantissa'],scalar_mul_dgk(self.pubkey, b['mantissa'], int(self.BASE**(b['exponent']-a['exponent']))))
+            exponent = a['exponent']
+        else:
[…]

### 2019-02-09 dgk/powmod.cpp

@@ -1,175 +1,0 @@
-/**
- \file 		powmod.cpp
- \author 	daniel.demmler@ec-spride.de
- \copyright	ABY - A Framework for Efficient Mixed-protocol Secure Two-party Computation
-			Copyright (C) 2015 Engineering Cryptographic Protocols Group, TU Darmstadt
-			This program is free software: you can redistribute it and/or modify
-			it under the terms of the GNU Affero General Public License as published
-			by the Free Software Foundation, either version 3 of the License, or
-			(at your option) any later version.
-			This program is distributed in the hope that it will be useful,
-			but WITHOUT ANY WARRANTY; without even the implied warranty of
-			MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE. See the
-			GNU Affero General Public License for more details.
-			You should have received a copy of the GNU Affero General Public License
-			along with this program. If not, see <http://www.gnu.org/licenses/>.
- \brief		PowMod Implementation
- */
-
-#include "powmod.h"
-#include <cstdlib>
-
-#define POWMOD_DEBUG 0
-
-#if POWMOD_DEBUG
-#include <cstdio>
-#endif
-
-mpz_t* m_table_g;
-mpz_t* m_table_h;
-mpz_t* m_prod;
-mpz_t m_mod;
-size_t m_numberOfElements_g, m_numberOfElements_h;
-
-void fbpowmod_init_g(const mpz_t base, const mpz_t mod, size_t bitsize) {
-	m_numberOfElements_g = bitsize;
-	mpz_init(m_mod);
-	mpz_set(m_mod, mod);
-	m_table_g = (mpz_t*) malloc(sizeof(mpz_t) * bitsize);
-	for (size_t i = 0; i < bitsize; i++) {
-		mpz_init(m_table_g[i]);
-	}
-
-	mpz_set(m_table_g[0], base);
-	for (size_t u = 1; u < bitsize; u++) {
-		mpz_mul(m_table_g[u], m_table_g[u - 1], m_table_g[u - 1]);
[…]

### 2019-02-09 dgk/powmod.h

@@ -1,57 +1,0 @@
-/**
- \file 		powmod.h
- \author 	daniel.demmler@ec-spride.de
- \copyright	ABY - A Framework for Efficient Mixed-protocol Secure Two-party Computation
-			Copyright (C) 2015 Engineering Cryptographic Protocols Group, TU Darmstadt
-			This program is free software: you can redistribute it and/or modify
-			it under the terms of the GNU Affero General Public License as published
-			by the Free Software Foundation, either version 3 of the License, or
-			(at your option) any later version.
-			This program is distributed in the hope that it will be useful,
-			but WITHOUT ANY WARRANTY; without even the implied warranty of
-			MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE. See the
-			GNU Affero General Public License for more details.
-			You should have received a copy of the GNU Affero General Public License
-			along with this program. If not, see <http://www.gnu.org/licenses/>.
- \brief		Powmod Implementation
- */
-
-#ifndef _POWMOD_H_
-#define _POWMOD_H_
-
-#include <gmp.h>
-
-extern mpz_t* m_table_g;
-extern mpz_t* m_table_h;
-extern mpz_t* m_prod;
-extern mpz_t m_mod;
-extern size_t m_numberOfElements_g;
-extern size_t m_numberOfElements_h;
-
-/**
- * initialize fixed base multiplication for a given base and a desired exponent bit size
- * identical functionality for either g or h
- */
-void fbpowmod_init_g(const mpz_t base, const mpz_t mod, size_t bitsize);
-void fbpowmod_init_h(const mpz_t base, const mpz_t mod, size_t bitsize);
-
-/**
- * fixed-base multiplication
- * requires pre-computed table, created with fbpowmod_init_*
- */
-void fbpowmod_g(mpz_t result, const mpz_t exp);
-void fbpowmod_h(mpz_t result, const mpz_t exp);
-
-/**
- * fixed-base double base encryption
- * requires pre-computed product with fbdbpowmod_init
- */
-void fbdbpowmod(mpz_t ret, const mpz_t e1, const mpz_t e2);
-void fbdbpowmod_init(const mpz_t b1, const mpz_t b2, const mpz_t mod, size_t bitsize);
-
-/**
- * double-base exponentiation ret = b1^e1*b2^e2
- */
-void dbpowmod(mpz_t ret, const mpz_t b1, const mpz_t e1, const mpz_t b2, const mpz_t e2, const mpz_t mod);
-
-#endif

### 2019-02-09 dgk/powmod.py

@@ -1,2 +1,0 @@
-import gmpy2
-from gmpy2 import mpz

### 2019-02-09 dgk/utils.cpp

@@ -1,99 +1,0 @@
-#include "utils.h"
-
-#include <cstdint>
-#include <fcntl.h>
-#include <gmp.h>
-#include <iostream>
-#include <unistd.h>
-
-
-//TODO: this is bad, fix occurrences of ceil_log2 and replace by ceil_log2_min1 where log(1) = 1 is necessary. For all else use ceil_log2_real
-uint32_t ceil_log2(int bits) {
-	if (bits == 1)
-		return 1;
-	int targetlevel = 0, bitstemp = bits;
-	while (bitstemp >>= 1)
-		++targetlevel;
-	return targetlevel + ((1 << targetlevel) < bits);
-}
-
-uint32_t ceil_log2_min1(int bits) {
-	if (bits <= 1)
-		return 1;
-	int targetlevel = 0, bitstemp = bits;
-	while (bitstemp >>= 1)
-		++targetlevel;
-	return targetlevel + ((1 << targetlevel) < bits);
-}
-
-uint32_t ceil_log2_real(int bits) {
-	if (bits == 1)
-		return 0;
-	int targetlevel = 0, bitstemp = bits;
-	while (bitstemp >>= 1)
-		++targetlevel;
-	return targetlevel + ((1 << targetlevel) < bits);
-}
-
-uint32_t floor_log2(int bits) {
-	if (bits == 1)
-		return 1;
-	int targetlevel = 0;
-	while (bits >>= 1)
-		++targetlevel;
-	return targetlevel;
-}
-
-/**
- * returns a 4-byte value from dev/random
- */
-uint32_t aby_rand() {
-	int frandom = open("/dev/random", O_RDONLY);
-	if (frandom < 0) {
-		std::cerr << "Error in opening /dev/random: utils.h:aby_rand()" << std::endl;
-		exit(1);
-	} else {
-		char data[4];
-		size_t len = 0;
-		while (len < sizeof data) {
-			ssize_t result = read(frandom, data + len, (sizeof data) - len);
-			if (result < 0) {
-				std::cerr << "Error in generating random number: utils.h:aby_rand()" << std::endl;
-				exit(1);
-			}
-			len += result;
-		}
-		close(frandom);
-		return *((uint32_t*) data);
-	}
-	return 0;
-}
-
-/**
- * returns a random mpz_t with bitlen len generated from dev/urandom
- */
-void aby_prng(mpz_t rnd, mp_bitcnt_t len) {
-	size_t byte_count = ceil_divide(len, 8);
[…]

### 2019-02-09 dgk/utils.h

@@ -1,48 +1,0 @@
-#ifndef _UTILS_H__
-#define _UTILS_H__
-
-#include <cstdint>
-#include <gmp.h>
-#include <unistd.h>
-
-#ifdef WIN32
-#define SleepMiliSec(x)	Sleep(x)
-#else
-#define SleepMiliSec(x)			usleep((x)<<10)
-#endif
-
-#define two_pow(e) (((uint64_t) 1) << (e))
-
-#define pad_to_power_of_two(e) ( ((uint64_t) 1) << (ceil_log2(e)) )
-
-/*compute (a-b) mod (m+1) as: b > a ? (m) - (b-1) + a : a - b	*/
-#define MOD_SUB(a, b, m) (( ((b) > (a))? (m) - ((b) -1 ) + a : a - b))
-
-#define ceil_divide(x, y)			(( ((x) + (y)-1)/(y)))
-#define bits_in_bytes(bits) (ceil_divide((bits), 8))
-#define pad_to_multiple(x, y) 		( ceil_divide(x, y) * (y))
-
-#define PadToRegisterSize(x) 		(PadToMultiple(x, OTEXT_BLOCK_SIZE_BITS))
-#define PadToMultiple(x, y) 		( ceil_divide(x, y) * (y))
-
-//TODO: this is bad, fix occurrences of ceil_log2 and replace by ceil_log2_min1 where log(1) = 1 is necessary. For all else use ceil_log2_real
-uint32_t ceil_log2(int bits);
-
-uint32_t ceil_log2_min1(int bits);
-
-uint32_t ceil_log2_real(int bits);
-
-uint32_t floor_log2(int bits);
-
-/**
- * returns a 4-byte value from dev/random
- */
-uint32_t aby_rand();
-
-/**
- * returns a random mpz_t with bitlen len generated from dev/urandom
- */
-void aby_prng(mpz_t rnd, mp_bitcnt_t len);
-
-
-#endif // _UTILS_H__

### 2019-02-09 dgk/utils.py

@@ -1,20 +1,0 @@
-import gmpy2
-from gmpy2 import mpz
-import time
-
-global_random_state = None
-
-def ceil_divide(x, y):
-    return ((((x) + (y) - 1) / (y)))
-
-
-def aby_prng(Len):
-    """Generates a random mpz with bitlength Len."""
-    global global_random_state
-    if global_random_state is None:
-        global_random_state = gmpy2.random_state(int(time.time()))
-    result = mpz(0)
-    for i in range(Len):
-        if gmpy2.mpz_random(global_random_state, 2) == 1:
-            result += gmpy2.exp2(i)
-    return mpz(result)

### 2019-02-09 paper/paper-conf.tex
Removed identifiers from sample images

@@
 		\midrule
-		\xintFor #1 in {anpage, bplyce, drbost, ksunth, martin, pmives, rnpwil, sbains, swewin, yfhsie} \do {%
-		\texttt{#1} & \includegraphics[width=1.75cm]{out_faces/paillier_negate_#1_original.png} & \includegraphics[width=1.75cm]{out_faces/paillier_negate_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/paillier_negate_#1_decrypted.png} & \includegraphics[width=1.75cm]{out_faces/paillier_logtransform_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/paillier_logtransform_#1_decrypted.png} & \includegraphics[width=1.75cm]{out_faces/paillier_pwrtransform_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/paillier_pwrtransform_#1_decrypted.png} \\ }%
+		\xintForpair #1#2 in {(anpage,a), (bplyce,b), (drbost,c), (ksunth,d), (martin,e), (pmives,f), (rnpwil,g), (sbains,h), (swewin,i), (yfhsie,j)} \do {%
+		(#2) & \includegraphics[width=1.75cm]{out_faces/paillier_negate_#1_original.png} & \includegraphics[width=1.75cm]{out_faces/paillier_negate_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/paillier_negate_#1_decrypted.png} & \includegraphics[width=1.75cm]{out_faces/paillier_logtransform_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/paillier_logtransform_#1_decrypted.png} & \includegraphics[width=1.75cm]{out_faces/paillier_pwrtransform_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/paillier_pwrtransform_#1_decrypted.png} \\ }%
 		\bottomrule         
@@
 		\midrule
-		\xintFor #1 in {anpage, bplyce, drbost, ksunth, martin, pmives, rnpwil, sbains, swewin, yfhsie} \do {%
-		\texttt{#1} & \includegraphics[width=1.75cm]{out_faces/dp_negate_#1_original.png} & \includegraphics[width=1.75cm]{out_faces/dp_negate_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/dp_negate_#1_decrypted.png} & \includegraphics[width=1.75cm]{out_faces/dp_logtransform_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/dp_logtransform_#1_decrypted.png} & \includegraphics[width=1.75cm]{out_faces/paillier_pwrtransform_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/dp_pwrtransform_#1_decrypted.png} \\ }%
+		\xintForpair #1#2 in {(anpage,a), (bplyce,b), (drbost,c), (ksunth,d), (martin,e), (pmives,f), (rnpwil,g), (sbains,h), (swewin,i), (yfhsie,j)} \do {%
+		(#2) & \includegraphics[width=1.75cm]{out_faces/dp_negate_#1_original.png} & \includegraphics[width=1.75cm]{out_faces/dp_negate_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/dp_negate_#1_decrypted.png} & \includegraphics[width=1.75cm]{out_faces/dp_logtransform_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/dp_logtransform_#1_decrypted.png} & \includegraphics[width=1.75cm]{out_faces/paillier_pwrtransform_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/dp_pwrtransform_#1_decrypted.png} \\ }%
 		\bottomrule
@@
         Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
-        \texttt{anpage} & 0.000 & $\infty$ & 1.00000 & 0.128 & 0.013 & 0.041 \\
-		\texttt{bplyce} & 0.000 & $\infty$ & 1.00000 & 0.084 & 0.013 & 0.024 \\
-		\texttt{drbost} & 0.000 & $\infty$ & 1.00000 & 0.099 & 0.012 & 0.031 \\
-		\texttt{ksunth} & 0.000 & $\infty$ & 1.00000 & 0.109 & 0.012 & 0.048 \\
-		\texttt{martin} & 0.000 & $\infty$ & 1.00000 & 0.117 & 0.015 & 0.043 \\
-		\texttt{pmives} & 0.000 & $\infty$ & 1.00000 & 0.111 & 0.012 & 0.025 \\
-		\texttt{rnpwil} & 0.000 & $\infty$ & 1.00000 & 0.099 & 0.012 & 0.023 \\
-		\texttt{sbains} & 0.000 & $\infty$ & 1.00000 & 0.084 & 0.012 & 0.024 \\
-		\texttt{swewin} & 0.000 & $\infty$ & 1.00000 & 0.089 & 0.012 & 0.023 \\
-		\texttt{yfhsie} & 0.000 & $\infty$ & 1.00000 & 0.081 & 0.012 & 0.029 \\
+        (a) & 0.000 & $\infty$ & 1.00000 & 0.128 & 0.013 & 0.041 \\
+		(b) & 0.000 & $\infty$ & 1.00000 & 0.084 & 0.013 & 0.024 \\
+		(c) & 0.000 & $\infty$ & 1.00000 & 0.099 & 0.012 & 0.031 \\
+		(d) & 0.000 & $\infty$ & 1.00000 & 0.109 & 0.012 & 0.048 \\
+		(e) & 0.000 & $\infty$ & 1.00000 & 0.117 & 0.015 & 0.043 \\
+		(f) & 0.000 & $\infty$ & 1.00000 & 0.111 & 0.012 & 0.025 \\
+		(g) & 0.000 & $\infty$ & 1.00000 & 0.099 & 0.012 & 0.023 \\
+		(h) & 0.000 & $\infty$ & 1.00000 & 0.084 & 0.012 & 0.024 \\
+		(i) & 0.000 & $\infty$ & 1.00000 & 0.089 & 0.012 & 0.023 \\
+		(j) & 0.000 & $\infty$ & 1.00000 & 0.081 & 0.012 & 0.029 \\
 		\bottomrule
@@
         Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
-		\texttt{anpage} & 0.000 & $\infty$ & 1.00000 & 0.221 & 30.217 & 0.239 \\
-		\texttt{bplyce} & 0.000 & $\infty$ & 1.00000 & 0.190 & 30.919 & 0.216 \\
-		\texttt{drbost} & 0.000 & $\infty$ & 1.00000 & 0.284 & 31.182 & 0.268 \\
-		\texttt{ksunth} & 0.000 & $\infty$ & 1.00000 & 0.225 & 32.581 & 0.223 \\
-		\texttt{martin} & 0.000 & $\infty$ & 1.00000 & 0.220 & 32.220 & 0.271 \\
-		\texttt{pmives} & 0.000 & $\infty$ & 1.00000 & 0.287 & 31.224 & 0.294 \\
-		\texttt{rnpwil} & 0.000 & $\infty$ & 1.00000 & 0.285 & 29.478 & 0.284 \\
-		\texttt{sbains} & 0.000 & $\infty$ & 1.00000 & 0.186 & 29.784 & 0.362 \\
-		\texttt{swewin} & 0.000 & $\infty$ & 1.00000 & 0.243 & 38.407 & 0.220 \\
-		\texttt{yfhsie} & 0.000 & $\infty$ & 1.00000 & 0.285 & 29.488 & 0.449 \\		
+		(a) & 0.000 & $\infty$ & 1.00000 & 0.221 & 30.217 & 0.239 \\
+		(b) & 0.000 & $\infty$ & 1.00000 & 0.190 & 30.919 & 0.216 \\
+		(c) & 0.000 & $\infty$ & 1.00000 & 0.284 & 31.182 & 0.268 \\
+		(d) & 0.000 & $\infty$ & 1.00000 & 0.225 & 32.581 & 0.223 \\
+		(e) & 0.000 & $\infty$ & 1.00000 & 0.220 & 32.220 & 0.271 \\
+		(f) & 0.000 & $\infty$ & 1.00000 & 0.287 & 31.224 & 0.294 \\
+		(g) & 0.000 & $\infty$ & 1.00000 & 0.285 & 29.478 & 0.284 \\
+		(h) & 0.000 & $\infty$ & 1.00000 & 0.186 & 29.784 & 0.362 \\
+		(i) & 0.000 & $\infty$ & 1.00000 & 0.243 & 38.407 & 0.220 \\
+		(j) & 0.000 & $\infty$ & 1.00000 & 0.285 & 29.488 & 0.449 \\		
 		\bottomrule
@@
         Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
-		\texttt{anpage} & 13.369 & 36.870 & 0.99263 & 0.085 & 1.813 & 0.023 \\
-		\texttt{bplyce} & 7.072 & 39.635 & 0.99017 & 0.089 & 2.073 & 0.023 \\
-		\texttt{drbost} & 8.151 & 39.019 & 0.98688 & 0.091 & 1.913 & 0.023 \\
-		\texttt{ksunth} & 25.253 & 34.108 & 0.98927 & 0.089 & 1.919 & 0.023 \\
-		\texttt{martin} & 10.374 & 37.971 & 0.98695 & 0.106 & 1.829 & 0.023 \\
-		\texttt{pmives} & 2.426 & 44.283 & 0.99401 & 0.127 & 1.900 & 0.023 \\
-		\texttt{rnpwil} & 5.184 & 40.985 & 0.98971 & 0.096 & 1.853 & 0.023 \\
-		\texttt{sbains} & 16.772 & 35.885 & 0.98492 & 0.081 & 1.746 & 0.024 \\
-		\texttt{swewin} & 5.803 & 40.494 & 0.99241 & 0.091 & 1.827 & 0.027 \\
-		\texttt{yfhsie} & 12.192 & 37.270 & 0.99354 & 0.081 & 1.815 & 0.023 \\
+		(a) & 13.369 & 36.870 & 0.99263 & 0.085 & 1.813 & 0.023 \\
+		(b) & 7.072 & 39.635 & 0.99017 & 0.089 & 2.073 & 0.023 \\
+		(c) & 8.151 & 39.019 & 0.98688 & 0.091 & 1.913 & 0.023 \\
+		(d) & 25.253 & 34.108 & 0.98927 & 0.089 & 1.919 & 0.023 \\
+		(e) & 10.374 & 37.971 & 0.98695 & 0.106 & 1.829 & 0.023 \\
+		(f) & 2.426 & 44.283 & 0.99401 & 0.127 & 1.900 & 0.023 \\
+		(g) & 5.184 & 40.985 & 0.98971 & 0.096 & 1.853 & 0.023 \\
+		(h) & 16.772 & 35.885 & 0.98492 & 0.081 & 1.746 & 0.024 \\
+		(i) & 5.803 & 40.494 & 0.99241 & 0.091 & 1.827 & 0.027 \\
+		(j) & 12.192 & 37.270 & 0.99354 & 0.081 & 1.815 & 0.023 \\
 		\bottomrule
@@
         Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
-		\texttt{anpage} & 0.004 & 71.624 & 0.99999 & 0.287 & 802.957 & 0.036 \\
-		\texttt{bplyce} & 0.000 & 82.043 & 1.00000 & 0.190 & 815.384 & 0.048 \\
-		\texttt{drbost} & 0.004 & 72.480 & 1.00000 & 0.270 & 813.640 & 0.036 \\
-		\texttt{ksunth} & 0.000 & 87.372 & 1.00000 & 0.204 & 804.629 & 0.047 \\
-		\texttt{martin} & 0.001 & 77.421 & 1.00000 & 0.245 & 822.940 & 0.036 \\
-		\texttt{pmives} & 0.001 & 76.934 & 1.00000 & 0.194 & 814.132 & 0.036 \\
-		\texttt{rnpwil} & 0.000 & 83.135 & 1.00000 & 0.197 & 808.503 & 0.047 \\
-		\texttt{sbains} & 0.001 & 77.301 & 1.00000 & 0.270 & 809.406 & 0.047 \\
-		\texttt{swewin} & 0.006 & 70.004 & 0.99999 & 0.268 & 813.217 & 0.051 \\
-		\texttt{yfhsie} & 0.001 & 78.576 & 1.00000 & 0.243 & 830.640 & 0.039 \\
+		(a) & 0.004 & 71.624 & 0.99999 & 0.287 & 802.957 & 0.036 \\
+		(b) & 0.000 & 82.043 & 1.00000 & 0.190 & 815.384 & 0.048 \\
+		(c) & 0.004 & 72.480 & 1.00000 & 0.270 & 813.640 & 0.036 \\
+		(d) & 0.000 & 87.372 & 1.00000 & 0.204 & 804.629 & 0.047 \\
+		(e) & 0.001 & 77.421 & 1.00000 & 0.245 & 822.940 & 0.036 \\
+		(f) & 0.001 & 76.934 & 1.00000 & 0.194 & 814.132 & 0.036 \\
+		(g) & 0.000 & 83.135 & 1.00000 & 0.197 & 808.503 & 0.047 \\
+		(h) & 0.001 & 77.301 & 1.00000 & 0.270 & 809.406 & 0.047 \\
+		(i) & 0.006 & 70.004 & 0.99999 & 0.268 & 813.217 & 0.051 \\
+		(j) & 0.001 & 78.576 & 1.00000 & 0.243 & 830.640 & 0.039 \\
 		\bottomrule
@@
         Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
-        \texttt{anpage} & 3910.678 & 12.208 & 0.46712 & 0.099 & 14.695 & 0.024 \\
-		\texttt{bplyce} & 873.064 & 18.720 & 0.84379 & 0.139 & 16.190 & 0.023 \\
-		\texttt{drbost} & 1261.059 & 17.123 & 0.77229 & 0.082 & 13.866 & 0.023 \\
-		\texttt{ksunth} & 653.049 & 19.981 & 0.90673 & 0.083 & 15.507 & 0.023 \\
-		\texttt{martin} & 646.310 & 20.026 & 0.88157 & 0.108 & 15.727 & 0.045 \\
-		\texttt{pmives} & 2047.933 & 15.018 & 0.69408 & 0.113 & 14.728 & 0.034 \\
-		\texttt{rnpwil} & 806.473 & 19.065 & 0.85346 & 0.082 & 14.253 & 0.024 \\
-		\texttt{sbains} & 616.419 & 20.232 & 0.92334 & 0.121 & 14.415 & 0.023 \\
-		\texttt{swewin} & 8270.696 & 8.955 & 0.43185 & 0.112 & 14.362 & 0.065 \\
-		\texttt{yfhsie} & 1715.478 & 15.787 & 0.73857 & 0.145 & 20.239 & 0.023 \\
+        (a) & 3910.678 & 12.208 & 0.46712 & 0.099 & 14.695 & 0.024 \\
+		(b) & 873.064 & 18.720 & 0.84379 & 0.139 & 16.190 & 0.023 \\
+		(c) & 1261.059 & 17.123 & 0.77229 & 0.082 & 13.866 & 0.023 \\
+		(d) & 653.049 & 19.981 & 0.90673 & 0.083 & 15.507 & 0.023 \\
+		(e) & 646.310 & 20.026 & 0.88157 & 0.108 & 15.727 & 0.045 \\
+		(f) & 2047.933 & 15.018 & 0.69408 & 0.113 & 14.728 & 0.034 \\
+		(g) & 806.473 & 19.065 & 0.85346 & 0.082 & 14.253 & 0.024 \\
+		(h) & 616.419 & 20.232 & 0.92334 & 0.121 & 14.415 & 0.023 \\
+		(i) & 8270.696 & 8.955 & 0.43185 & 0.112 & 14.362 & 0.065 \\
+		(j) & 1715.478 & 15.787 & 0.73857 & 0.145 & 20.239 & 0.023 \\
 		\bottomrule
@@
         Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
-		\texttt{anpage} & 25008.723 & 4.150 & 0.000 & 0.376 & 9700.926 & 1.269 \\
-		\texttt{bplyce} & 22700.522 & 4.570 & 0.000 & 0.230 & 9196.609 & 0.043 \\
 		% \texttt{anpage} & 25115.891 & 4.131 & 0.00000 & 0.016 & 741.872 & 0.031 \\ 10x10
@@
 		% \texttt{drbost} & 18899.906 & 5.366 & 0.00000 & 0.014 & 733.409 & 0.003 \\
-		\texttt{drbost} & 18902.214 & 5.366 & 0.000 & 0.277 & 9261.407 & 0.150 \\
-		\texttt{ksunth} & 12585.729 & 7.132 & 0.000 & 0.257 & 9259.010 & 0.051 \\
-		\texttt{martin} & 17012.423 & 5.823 & 0.000 & 0.279 & 9440.351 & 0.051 \\
-		\texttt{pmives} & 31124.615 & 3.200 & 0.000 & 0.285 & 9492.149 & 0.052 \\
-		\texttt{rnpwil} & 22982.917 & 4.517 & 0.000 & 0.289 & 9321.928 & 0.048 \\
-		\texttt{sbains} & 13469.155 & 6.837 & 0.000 & 0.257 & 9233.818 & 0.048 \\
-		\texttt{swewin} & 37453.834 & 2.396 & 0.000 & 0.262 & 9203.045 & 0.048 \\
-		\texttt{yfhsie} & 23037.762 & 4.506 & 0.000 & 0.258 & 9210.393 & 0.048 \\
+		(a) & 25008.723 & 4.150 & 0.000 & 0.376 & 9700.926 & 1.269 \\
+		(b) & 22700.522 & 4.570 & 0.000 & 0.230 & 9196.609 & 0.043 \\
+		(c) & 18902.214 & 5.366 & 0.000 & 0.277 & 9261.407 & 0.150 \\
+		(d) & 12585.729 & 7.132 & 0.000 & 0.257 & 9259.010 & 0.051 \\
+		(e) & 17012.423 & 5.823 & 0.000 & 0.279 & 9440.351 & 0.051 \\
+		(f) & 31124.615 & 3.200 & 0.000 & 0.285 & 9492.149 & 0.052 \\
+		(g) & 22982.917 & 4.517 & 0.000 & 0.289 & 9321.928 & 0.048 \\
+		(h) & 13469.155 & 6.837 & 0.000 & 0.257 & 9233.818 & 0.048 \\
+		(i) & 37453.834 & 2.396 & 0.000 & 0.262 & 9203.045 & 0.048 \\
+		(j) & 23037.762 & 4.506 & 0.000 & 0.258 & 9210.393 & 0.048 \\
 		% \texttt{drbost} & 18902.214 & 5.366 & 0.00000 & 0.064 & 2261.407 & 0.110 \\ % 20x18

### 2019-02-10 paper/paper-conf.tex
RRL edits

@@
 
-Homomorphic cryptosystems are a special type of cryptosystem in which operations can be securely performed on encrypted data.
+% Homomorphic cryptosystems are a special type of cryptosystem in which operations can be securely performed on encrypted data.
 Suppose that for a public-key cryptosystem, $\mathcal{E}_k \left(p \right)$ is the encryption function using the public key $k \in \mathcal{K}$, and $\mathcal{D}_l \left(c \right)$ be the decryption function using the private key $l$.
 A cryptosystem is said to be homomorphic if its encryption function is homomorphic, that is, if it satisfies the relation
-\begin{equation}
-    \mathcal{E}_k \left(p_1 \boxplus p_2\right) = \mathcal{E}_k \left(p_1\right) \boxdot \mathcal{E}_k \left(p_2\right)
-\end{equation}
-where $p_1, p_2 \in \mathcal{P}$ are the plaintexts, and $\boxplus$ and $\boxdot$ are operations in $\mathcal{P}$ and $\mathcal{C}$ respectively~\cite{fontaine_survey_2007}.
+% \begin{equation}
+%     \mathcal{E}_k \left(p_1 \boxplus p_2\right) = \mathcal{E}_k \left(p_1\right) \boxdot \mathcal{E}_k \left(p_2\right)
+% \end{equation}
+% where $p_1, p_2 \in \mathcal{P}$ are the plaintexts, and $\boxplus$ and $\boxdot$ are operations in $\mathcal{P}$ and $\mathcal{C}$ respectively~\cite{fontaine_survey_2007}.
 Furthermore, a homomorphic cryptosystem also satisfies~\cite{li_elliptic_2012}
-\begin{equation}
-    p_1 \boxplus p_2 = \mathcal{D}_l \left( \mathcal{E}_k \left(p_1\right) \boxdot \mathcal{E}_k \left(p_2\right) \right).
-\end{equation}
+% \begin{equation}
+%     p_1 \boxplus p_2 = \mathcal{D}_l \left( \mathcal{E}_k \left(p_1\right) \boxdot \mathcal{E}_k \left(p_2\right) \right).
+% \end{equation}
 
-In other words, a homomorphic cryptosystem preserves the operations that can be done with the plaintext without requiring an intermediary step of decrypting the ciphertext beforehand.
+% In other words, 
+A homomorphic cryptosystem preserves the operations that can be done with the plaintext without requiring an intermediary step of decrypting the ciphertext beforehand.
 It is important to note that the operations $\boxplus$ and $\boxdot$ need not be the same.
@@
 
-Homomorphic cryptosystems can be classified according to the plaintext and ciphertext operations, $\boxplus$ and $\boxdot$.
+% Homomorphic cryptosystems can be classified according to the plaintext and ciphertext operations, $\boxplus$ and $\boxdot$.
 If the plaintext operation $\boxplus$ is addition, the cryptosystem is said to be \textit{additively homomorphic}, and the cryptosystem is said to be \textit{multiplicatively homomorphic} if the plaintext operation $\boxplus$ is multiplication.
@@
 
-We will present two such cryptosystems, the Dasgupta--Pal cryptosystem, which we present in full to explain a correction we propose to it, and the BGV cryptosystem, which has open source implementations availble primarily used in homomorphic cryptography research.
+% We will present two such cryptosystems, the Dasgupta--Pal cryptosystem, which we present in full to explain a correction we propose to it, and the BGV cryptosystem, which has open source implementations availble primarily used in homomorphic cryptography research.
+We will present the BGV cryptosystem, which has open source implementations availble primarily used in homomorphic cryptography research.
 
-\subsubsection{The Dasgupta--Pal Cryptosystem}
-The Dasgupta--Pal cryptosystem is a fully homomorphic cryptosystem proposed in 2016 by Smaranika Dasgupta and S.
+% \subsubsection{The Dasgupta--Pal Cryptosystem}
+% The Dasgupta--Pal cryptosystem is a fully homomorphic cryptosystem proposed in 2016 by Smaranika Dasgupta and S.
 K.
@@
 
-Given a message $m \in \mathbb{Z}$, we denote
-\begin{align*}
-		m_p(x) = a_0 + a_1 x + a_2 x^2 + \cdots + a_k x^k
-\end{align*}
-where $a_k a_{k-1}\cdots a_2 a_1 a_0$ is the binary representation of $m$.
+% Given a message $m \in \mathbb{Z}$, we denote
+% \begin{align*}
+% 		m_p(x) = a_0 + a_1 x + a_2 x^2 + \cdots + a_k x^k
+% \end{align*}
+% where $a_k a_{k-1}\cdots a_2 a_1 a_0$ is the binary representation of $m$.
 
-In the original scheme presented in \cite{dasgupta_design_2016}, the secret key $S_k$ is set to be a large prime.
+% In the original scheme presented in \cite{dasgupta_design_2016}, the secret key $S_k$ is set to be a large prime.
 In Appendix \ref{chap:correction}, we present a case where the Dasgupta--Pal cryptosystem fails and prove that setting the secret key $S_k = 2p$, where $p$ is a large prime, corrects errors in the Dasgupta--Pal cryptosystem.
-We now decribe the correct cryptosystem.
-\paragraph{Corrected Dasgupta--Pal Cryptosystem Description}
-Let $\ell$ denote the security parameter of the cryptosystem.
-Let $S_k = 2p$, where $p$ is a prime number with $\ell - 1$ bits.
-Choose a random even integer $z$ of length $\log_2{\ell}$.
+% We now decribe the correct cryptosystem.
+% \paragraph{Corrected Dasgupta--Pal Cryptosystem Description}
+% Let $\ell$ denote the security parameter of the cryptosystem.
+% Let $S_k = 2p$, where $p$ is a prime number with $\ell - 1$ bits.
+% Choose a random even integer $z$ of length $\log_2{\ell}$.
 
-Let the secret key be $S_k$, and let the refresh key be $R_k = z \cdot S_k$. The secret key is kept private to the encrypting/decrypting parties, while the refresh key is made publicly available.
+% Let the secret key be $S_k$, and let the refresh key be $R_k = z \cdot S_k$. The secret key is kept private to the encrypting/decrypting parties, while the refresh key is made publicly available.
 
-The scheme defines the encryption algorithm for a message $m$ as follows:
-\begin{align*}
-	E(m) = y(x) + S_k\times d(x)
-\end{align*}
-where
-$y(x)$ is a polynomial of degree $n$ such that $m_p(x) \equiv y(x) \bmod S_k$ and $d(x)$ is a randomly chosen polynomial of degree $n$.
+% The scheme defines the encryption algorithm for a message $m$ as follows:
+% \begin{align*}
+% 	E(m) = y(x) + S_k\times d(x)
+% \end{align*}
+% where
+% $y(x)$ is a polynomial of degree $n$ such that $m_p(x) \equiv y(x) \bmod S_k$ and $d(x)$ is a randomly chosen polynomial of degree $n$.
 This encrypts each coefficient of $m_p(x)$ by adding some multiple of $S_k$ to it.
@@
 
-Furthermore, the decryption algorithm to recover $m_p(x)$ from a ciphertext polynomial $c(x)$ as
-\begin{align*}
-	m_p(x) = c(x) \bmod S_k \bmod 2.
-\end{align*}
-Thus $D(c(x))$ is defined as the integer recovered from the coefficients of the polynomial $c(x) \bmod S_k \bmod 2$.
+% Furthermore, the decryption algorithm to recover $m_p(x)$ from a ciphertext polynomial $c(x)$ as
+% \begin{align*}
+% 	m_p(x) = c(x) \bmod S_k \bmod 2.
+% \end{align*}
+% Thus $D(c(x))$ is defined as the integer recovered from the coefficients of the polynomial $c(x) \bmod S_k \bmod 2$.
 
-Dasgupta and Pal note that homomorphic operations on ciphertext introduce noise which may interfere with decryption, due to the potential increase in ciphertext values.
-To eliminate noise from a polynomial ciphertext, the following refresh function is used:
-\begin{align*}
-	R(c(x)) = c(x) \bmod R_k.
-\end{align*}
+% Dasgupta and Pal note that homomorphic operations on ciphertext introduce noise which may interfere with decryption, due to the potential increase in ciphertext values.
+% To eliminate noise from a polynomial ciphertext, the following refresh function is used:
+% \begin{align*}
+% 	R(c(x)) = c(x) \bmod R_k.
+% \end{align*}
 
-\paragraph{Homomorphic Properties of the Dasgupta--Pal Cryptosystem}
-It has been shown \cite{dasgupta_design_2016} that the following properties hold for all integer messages $m_1, m_2 \in \mathbb{Z}_n$ in the Dasgupta--Pal cryptosystem.
+% \paragraph{Homomorphic Properties of the Dasgupta--Pal Cryptosystem}
+% It has been shown \cite{dasgupta_design_2016} that the following properties hold for all integer messages $m_1, m_2 \in \mathbb{Z}_n$ in the Dasgupta--Pal cryptosystem.
 These properties arise since each coefficient in a ciphertext polynomial is essentially an independently encrypted bit of the original message.
-\begin{description}
-	\item[\textsc{xor} on ciphertexts]
-	A bitwise exclusive or (\textsc{xor}) operation on integer messages can be achieved by adding the coefficients pairwise between two ciphertexts.
-	\begin{align*}
-		D(E(m_1)+E(m_2)) = m_1 \textsc{ xor } m_2
-	\end{align*}
-	\item[\textsc{and} on ciphertexts]
-	Similarly, pair-wise multiplication corresponds to bitwise \textsc{and} of integer messages.
-	\begin{align*}
-		D(E(a) \otimes E(b)) = a \textsc{ and } b = ab \bmod 2
-	\end{align*}
-	where $\otimes$ denotes pairwise multiplication,
-	\begin{align*}
-		\sum_{i=1}^n{a_ix^i} \otimes \sum_{i=1}^n{b_ix^i} = \sum_{i=1}^n{a_ib_ix^i}.
-	\end{align*}
-\end{description}
+% \begin{description}
+% 	\item[\textsc{xor} on ciphertexts]
+% 	A bitwise exclusive or (\textsc{xor}) operation on integer messages can be achieved by adding the coefficients pairwise between two ciphertexts.
+% 	\begin{align*}
+% 		D(E(m_1)+E(m_2)) = m_1 \textsc{ xor } m_2
+% 	\end{align*}
+% 	\item[\textsc{and} on ciphertexts]
+% 	Similarly, pair-wise multiplication corresponds to bitwise \textsc{and} of integer messages.
+% 	\begin{align*}
+% 		D(E(a) \otimes E(b)) = a \textsc{ and } b = ab \bmod 2
+% 	\end{align*}
+% 	where $\otimes$ denotes pairwise multiplication,
+% 	\begin{align*}
+% 		\sum_{i=1}^n{a_ix^i} \otimes \sum_{i=1}^n{b_ix^i} = \sum_{i=1}^n{a_ib_ix^i}.
+% 	\end{align*}
+% \end{description}
 
-Arbitrary computation on data can thus be achived using these bitwise operations.
+% Arbitrary computation on data can thus be achived using these bitwise operations.
 While the Dasgupta--Pal cryptosystem requires significant amounts of memory, as each bit of plaintext is encrypted into an integer, this approach provides a flexible method to perform relatively fast arbitrary computation on encrypted data.
@@
 In this study we extend the range of intensity transformations to non-linear transformations.
-Two common non-linear image transformations are the log transformation and power-law transformation~\cite{gonzalez_digital_2008}.
+Two common non-linear image transformations are the logarithm transformation and power-law transformation~\cite{gonzalez_digital_2008}.
 
-The log transformation is used to enhance dark pixels or increase the dark details of an image by mapping low intensity values to a wider range of values~\cite{gonzalez_digital_2008}.
+The logarithm transformation is used to enhance dark pixels or increase the dark details of an image by mapping low intensity values to a wider range of values~\cite{gonzalez_digital_2008}.
 This has the general formula
@@
 A power-law transformation defined by the above equation can calibrate the operation of many image capture and output devices such as cameras, printers and displays in a process called \textit{gamma correction}.
-This ensures reproducibility and accuracy of images being displayed by digital output devices~\cite{gonzalez_digital_2008}.
+% This ensures reproducibility and accuracy of images being displayed by digital output devices~\cite{gonzalez_digital_2008}.
 

### 2019-02-10 paper/paper-conf.tex
Cleaned up and shortened Ch1,2

@@
 This allows data to be securely transmitted over an insecure channel.
-Much research has been done on the development and application of various cryptosystems.
 
@@
 In this manner, data is manipulated without compromising data privacy, as the encrypted data being operated on remains secure~\cite{fontaine_survey_2007, sen_homomorphic_2013}.
-While numerous homomorphic cryptosystems exist for use with digital data in general, in the area of homomorphic image encryption, there is additional interest in being able to perform image manipulation operations on the encrypted data such as image adjustment, filtering, and morphological/feature extraction operations~\cite{ziad_cryptoimg:_2016, gonzalez_digital_2008}.
+In the area of homomorphic image encryption, there is interest in being able to perform image manipulation operations on the encrypted data such as image adjustment, filtering, and morphological/feature extraction operations~\cite{ziad_cryptoimg:_2016, gonzalez_digital_2008}.
 More advanced operations have also been implemented using homomorphic cryptosystems, such as facial recognition \cite{hutchison_privacy-preserving_2009} and neural networks \cite{hesamifard_cryptodl:_2017}.
@@
 \subsection{Research Objectives}
-Previous attempts in the literature to provide image processing tasks such as image manipulation \cite{ziad_cryptoimg:_2016} and  facial recognition \cite{hutchison_privacy-preserving_2009} have primarily used the Paillier and  Damg{\aa}rd--Geisler--Kr{\o}igaard (DGK) cryptosystems to perform linear operations on encrypted data.
-In this study, we extend this research to provide an objective comparison of various homomorphic cryptosystems currently in the literature in performing non-linear operations, as opposed to just linear operations, and facial detection, as opposed to just facial recognition.
+% Previous attempts in the literature to provide image processing tasks such as image manipulation \cite{ziad_cryptoimg:_2016} and  facial recognition \cite{hutchison_privacy-preserving_2009} have primarily used the Paillier and  Damg{\aa}rd--Geisler--Kr{\o}igaard (DGK) cryptosystems to perform linear operations on encrypted data.
+% In this study, we extend this research to provide an objective comparison of various homomorphic cryptosystems currently in the literature in performing non-linear operations, and facial detection, as opposed to just linear operations and facial recognition.
 
 Our main research objective is to assess the practicality of various homomorphic cryptosystems with regard to image processing on faces. 
-Homomorphic cryptosystems are known to be slower in terms of encryption, operation, and decryption time~\cite{sen_homomorphic_2013}.
+% Homomorphic cryptosystems are known to be slower in terms of encryption, operation, and decryption time~\cite{sen_homomorphic_2013}.
 Furthermore, the operations on encrypted data supported by homomorphic cryptosystems are limited, and some schemes require preprocessing to be performed on images, limiting the range of operations which can be performed efficiently~\cite{li_elliptic_2012}.
 
-In summary, in this study, we wish to
+% In summary, in this study, we wish to
+More specifically, we wish to do the following:
 \begin{enumerate}
-    \item Implement common image processing operations using known homomorphic encryption schemes, then determine which schemes admit more image processing operations and extend known cryptosystems to support more operations, if possible;
+    \item Implement common linear and non-linear image processing operations using known homomorphic encryption schemes, then determine which schemes admit more image processing operations and extend known cryptosystems to support more operations, if possible;
     \item Compare the time efficiency and accuracy of common image processing operations under known homomorphic encryption schemes, and of common image processing operations without using homomorphic encryption;
@@
 \subsection{Scope and Limitations}
-Our study will be limited in terms of the cryptosystems to be tested, the image processing operations we will implement, and the statistical tests we will use to gauge the security of the cryptosystems.
+% Our study will be limited in terms of the cryptosystems to be tested, the image processing operations we will implement, and the statistical tests we will use to gauge the security of the cryptosystems.
 Below is a listing of the scope of the study.
 
-We will implement and test the following algorithms:
+% We will implement and test the following algorithms:
+In this study, we will implement and test the following cryptosystems:
 \begin{enumerate}
@@
     \item The Damg{\aa}rd--Geisler--Kr{\o}igaard (DGK) cryptosystem~\cite{pieprzyk_efficient_2007, cryptoeprint:2008:321} which is primarily used for secure integer comparison.
-	\item A fully homomorphic encryption scheme by Dasgupta and Pal, which uses polynomial rings~\cite{dasgupta_design_2016}.
+	% \item A fully homomorphic encryption scheme by Dasgupta and Pal, which uses polynomial rings~\cite{dasgupta_design_2016}.
 	\item The Brakerski--Gentry--Vaikuntanathan (BGV) cryptosystem \cite{cryptoeprint:2011:277}, an improvement on the lattice-based cryptosystem by Gentry~\cite{gentry_fully_2009}, with optimizations from Smart, Vercauteren, and Halevi \cite{hutchison_fully_2010, cryptoeprint:2011:566}.
@@
 A homomorphic cryptosystem preserves the operations that can be done with the plaintext without requiring an intermediary step of decrypting the ciphertext beforehand.
-It is important to note that the operations $\boxplus$ and $\boxdot$ need not be the same.
+It is important to note that the operations in the plaintext space and ciphertext space need not be the same.
 A simple operation in the plaintext space may require a computationally intensive operation in the ciphertext space.
@@
 In this section, we will present two classical partially homomorphic cryptosystems which we will be testing in the study: the Paillier cryptosystem and the DGK cryptosystem.
-Both of these cryptosystems encrypt integer plaintexts and are additively homomorphic.
+Both of these cryptosystems encrypt integer plaintexts as integer ciphertexts.
+In our description of each cryptosystem, we use $E(m)$ to denote the encryption of a plaintext $m$, and $D(c)$ to denote the decryption of a ciphertext $c$.
 
-We will then show that the cryptosystems can be modified to support privacy-perserving polynomial evaluation in a client-server protocol: given an encrypted message $m$, evaluate $f(m)$ where $f$ is a polynomial function.
+% We will then show that the cryptosystems can be modified to support privacy-perserving polynomial evaluation in a client-server protocol: given an encrypted message $m$, evaluate $f(m)$ where $f$ is a polynomial function.
 
@@
 The Paillier cryptosystem \cite{stern_public-key_1999}, developed by Pascal Paillier, is a probabilistic encryption scheme which is based on the composite residuosity class problem.
-The scheme allows for the encryption and decryption of integer messages, and is known to be additively homomorphic.
+The scheme has several well--known homomorphic properties.
+% The scheme allows for the encryption and decryption of integer messages, and is known to be additively homomorphic.
 % We now state the encryption and decryption algorithms of the Paillier cryptosystem and its homomorphic properties.
@@
 
-\paragraph{Homomorphic Properties of the Paillier Cryptosystem}
-The Paillier cryptosystem supports additive homomorphism as well as the multiplication of a plaintext scalar to an encrypted message.
+% \paragraph{Homomorphic Properties of the Paillier Cryptosystem}
+% The Paillier cryptosystem supports additive homomorphism as well as the multiplication of a plaintext scalar to an encrypted message.
 These homomorphic properties are used to add a plaintext scalar to a ciphertext, add two ciphertexts, and multiply a ciphertext by a plaintext scalar, respectively.
@@
 
-For all $m_1,m_2 \in \mathbb{Z}_n$ and $k\in \mathbb{N}$, the following homomorphic properties hold.
+For all $m_1,m_2 \in \mathbb{Z}_n$ and $k\in \mathbb{N}$, the following homomorphic properties hold for the Paillier cryptosystem with public key $(g,n)$.
 \begin{align*}
@@
 
+These homomorphic properties are used to add a plaintext scalar to a ciphertext, add two ciphertexts, and multiply a ciphertext by a plaintext scalar, respectively.
+
 \subsubsection{The DGK Cryptosystem}
 The DGK cryptosystem was published by Damg{\aa}rd, Geisler, and Kr{\o}igaard in 2007 in an effort to create a secure integer comparison scheme \cite{pieprzyk_efficient_2007, cryptoeprint:2008:321} which is widely used in the literature \cite{veugen_improving_2012}.
+The DGK cryptosystem has homomorphic properties similar to the Paillier cryptosystem.
 
@@
 
-\paragraph{Homomorphic Properties of the DGK Cryptosystem}
-The DGK cryptosystem supports additive homomorphism as well as the multiplication of a plaintext scalar to an encrypted message.
+% \paragraph{Homomorphic Properties of the DGK Cryptosystem}
+% The DGK cryptosystem supports additive homomorphism as well as the multiplication of a plaintext scalar to an encrypted message.
 These homomorphic properties are used to add a plaintext scalar to a ciphertext, add two ciphertexts, and multiply a ciphertext by a plaintext scalar, respectively.
@@
 
-For all $m_1,m_2 \in \mathbb{Z}_u$ and $k\in \mathbb{N}$, the following homomorphic properties hold.
+For all $m_1,m_2 \in \mathbb{Z}_u$ and $k\in \mathbb{N}$, the following homomorphic properties hold for the DGK cryptosystem with public key $(n,g,h,u)$.
 \begin{align*}
@@
     &= (g^m)^k \cdot (h^r)^k \bmod{n}\\
-    &= g^{km} \cdot (h^kr) \bmod{n}\\
+    &= g^{km} \cdot (h^kr) \bmod{n}
   \end{align*}
@@
 
-\subsubsection{Secure Exponentiation and Multiplication Protocols}
-\label{ssec:exponentiationprotocol}
-[TO-DO: This is further explained in another paper.]
+% \subsubsection{Secure Exponentiation and Multiplication Protocols}
+% \label{ssec:exponentiationprotocol}
+% [TO-DO: This is further explained in another paper.]
 % In order to perform polynomial evaluation, we first present a protocol for privacy-preserving exponentiation to a positive integer power, adapted from the protocol to calculate Euclidean distances used in \cite{hutchison_privacy-preserving_2009}.
@@
 % We will present two such cryptosystems, the Dasgupta--Pal cryptosystem, which we present in full to explain a correction we propose to it, and the BGV cryptosystem, which has open source implementations availble primarily used in homomorphic cryptography research.
-We will present the BGV cryptosystem, which has open source implementations availble primarily used in homomorphic cryptography research.
 
@@
 
-\subsubsection{HElib and the BGV Cryptosystem}
+% \subsubsection{HElib and the BGV Cryptosystem}
 The BGV (Brakerski--Gentry--Vaikuntanathan) cryptosystem \cite{cryptoeprint:2011:277} is a fully homomorphic cryptosystem created based on the ring-learning with error problem.
@@
 We represent a digital image $R$ as an $M \times N$ matrix of pixel intensity values, each value in the range $\left[0, L-1\right]$, for some positive integer $L$.
-We use $R(x,y)$ to represent the entry at the $x$th row and $y$th column of a matrix $R$.
+We denote with $R(x,y)$ the entry at the $x$th row and $y$th column of a matrix $R$.
 An intensity transformation on an image $R$ can be defined as a function $T$ which maps a pixel value $r$ to a new value $r^\prime$, which we can write as $r^\prime = T\left(r\right)$.
@@
 \subsection{Facial Detection and Recognition}
-%% TODO: Brian dump ur stuff here
 
@@
 The protocol for squaring a number as described earlier is a workaround for the limitations of Paillier or any other partially homomorphic cryptosystem that only supports addition and scalar multiplication.
-This can be possibly extended so that operations such as pairwise multiplication and exponentiation are also supported, provided that the protocol involves two parties.
+% This can be possibly extended so that operations such as pairwise multiplication and exponentiation are also supported, provided that the protocol involves two parties.
 
@@
 \section{Methodology}
-In this study we apply four homomorphic encryption schemes~\cite{ziad_cryptoimg:_2016, pieprzyk_efficient_2007, dasgupta_design_2016, garay_algorithms_2014} for use in image processing and facial recognition applications.
+In this study we apply three homomorphic encryption schemes~\cite{ziad_cryptoimg:_2016, pieprzyk_efficient_2007, garay_algorithms_2014} for use in image processing and facial recognition applications.
 While the Paillier and DGK cryptosystems have been implemented for use in image processing in~\cite{ziad_cryptoimg:_2016, hutchison_privacy-preserving_2009}, the other cryptosystems have to be adapted for this study.
@@
 
-For convenience, a wrapper library is created that integrates the four cryptosystems into a unified interface.
+For convenience, a wrapper library is created that integrates the three cryptosystems into a unified interface.
 
-\subsection{Secure Computation with Real Numbers}
+\subsection{Extension of Partially Homomorphic Cryptosystems}
+\label{sse:pheextension}
 [TO-DO: This is further explained in another paper.]
@@
 \subsection{Non-Linear Intensity Transformations}
-Aside from implementing the homomorphic encryption and decryption algorithms, we will also implement library functions for image negation, logarithm transformation and power-law transformation, as they are defined in~\cite{gonzalez_digital_2008}.
+We will implement library functions for image negation, logarithm transformation and power-law transformation, as they are defined in~\cite{gonzalez_digital_2008}.
 We now describe how we implement the logarithm and power-law image intensity transformations.
-In the case of partially homomorphic cryptosystems (Paillier, DGK), if  exponentiation and multiplication is required, the secure protocols in section \ref{ssec:exponentiationprotocol} will be used.
+In the case of partially homomorphic cryptosystems (Paillier, DGK), if exponentiation and multiplication is required, the secure protocols in section \ref{ssec:pheextension} will be used.
 

### 2019-02-10 paper/paper-conf.tex
Updated log equation to alpha = 16, made ch3 more concise

@@
 In this study we apply three homomorphic encryption schemes~\cite{ziad_cryptoimg:_2016, pieprzyk_efficient_2007, garay_algorithms_2014} for use in image processing and facial recognition applications.
-While the Paillier and DGK cryptosystems have been implemented for use in image processing in~\cite{ziad_cryptoimg:_2016, hutchison_privacy-preserving_2009}, the other cryptosystems have to be adapted for this study.
-Two experiments are conducted in this study:
-\begin{enumerate}
-	\item Assessment of non-linear image intensity transformations under each of the four cryptosystems.
-	\item Assessment of efficiency of each of the four cryptosystems when applied for use in privacy-preserving facial recognition and detection using eigenfaces.
-\end{enumerate}
-The results of the image intensity transformations are tested for image quality using benchmarks in~\cite{ahmed_benchmark_2016}.
+In particular, the study consists of the following:
+\begin{itemize}
+	\item Creating a wrapper library that acts as a unified interface which implements the Paillier, DGK, and BGV homomorphic cryptosystems.
+	\item An implementation of image processing operations (intensity transformations, facial recognition) under the above cryptosystems.
+	\item Conducting tests for image quality, processing time, using images from the \texttt{faces94} dataset.
+\end{itemize}
+
+% While the Paillier and DGK cryptosystems have been implemented for use in image processing in~\cite{ziad_cryptoimg:_2016, hutchison_privacy-preserving_2009}, the other cryptosystems have to be adapted for this study.
+% Two experiments are conducted in this study:
+% \begin{enumerate}
+% 	\item Assessment of non-linear image intensity transformations under each of the three cryptosystems.
+% 	\item Assessment of efficiency of each of the four cryptosystems when applied for use in privacy-preserving facial recognition and detection using eigenfaces.
+% \end{enumerate}
+% The results of the image intensity transformations are tested for image quality using benchmarks in~\cite{ahmed_benchmark_2016}.
 
 \subsection{Cryptosystem Implementation}
-Four homomorphic encryption schemes are investigated.
-For cryptosystems with readily available open-source implementations, such implementations are used.
-For the remaining cryptosystems, the encryption and decryption methods were implemented in Python.
+Three homomorphic encryption schemes are investigated, and a wrapper library was created in Python that integrates these cryptosystems into a unified interface.
 \begin{itemize}
 	\item The Paillier cryptosystem is incorporated using the implementation at \url{https://github.com/n1analytics/python-paillier} developed by Data61 - CSIRO.
+	\item The DGK cryptosystem is ported from the C++ implementation at \url{https://github.com/encryptogroup/ENCRYPTO_utils}, developed by Daniel Demmler from EC-SPRIDE.
 	\item The BGV cryptosystem is implemented using the Pyfhel library (\url{https://github.com/ibarrond/Pyfhel}) using a HElib backend from (\url{https://github.com/shaih/HElib}).
-	\item The DGK and Dasgupta--Pal cryptosystems are implemented from scratch with Python.
 \end{itemize}
 
-For convenience, a wrapper library is created that integrates the three cryptosystems into a unified interface.
-
-\subsection{Extension of Partially Homomorphic Cryptosystems}
+\subsubsection{Extension of Partially Homomorphic Cryptosystems}
 \label{sse:pheextension}
-[TO-DO: This is further explained in another paper.]
+% [TO-DO: This is further explained in another paper.]
 % We will briefly discuss a protocol to enable cryptosystems built for integer inputs to handle real number inputs.
@@
 
-In order to perform this transformation under a homomorphic cryptosystem, we must provide an approximation for $\log\left(1 + x\right)$ in terms of addition and multiplication operations (or their inverses).
-We have derived a closed form approximation in Appendix \ref{sec:logapproximation}.
-\begin{align}
-	\label{eq:scaledquadraturech3}
+In order to perform this transformation under Paillier and DGK, we provide the following closed-form approximation for $\log\left(1 + x\right)$.
+% TODO: IDK HOW TO CITE OUR PCSC PAPER
+\begin{align}\label{eq:optimal_log_approximation}
 	\begin{split}
-    &\log(1+x) \\
-    &\approx \frac{137x^5 + 33185x^4 + 931370x^3 - 13403630x^2 - 289469315x - 713567363}
-	{30(x^5 + 505x^4 + 42010x^3 + 923010x^2 + 5722005x + 8040501)} \\
-	&+ \log{20}
+		&\log\left(1+x\right) \approx \frac{a(x)}{b(x)} + \log{16}
 	\end{split}
 \end{align}
+where
+\begin{align*}
+	\begin{split}
+	a(x) &= 137x^5 + 26685x^4 + 617370x^3 - 6498630x^2 \\
+	&- 121239315x - 257804775\\
+	b(x) &= 30(x^5 + 405x^4 + 27210x^3 + 488810x^2 + 2536005x \\
+	&+ 3122577)
+	\end{split}
+\end{align*}
+% \begin{align}\label{eq:optimal_log_approximation}
+% 	\begin{split}
+% 		&\log\left(1+x\right) \\
+% 		&\approx \frac{137x^5 + 26685x^4 + 617370x^3 - 6498630x^2 - 121239315x - 257804775}
+% 		{30(x^5 + 405x^4 + 27210x^3 + 488810x^2 + 2536005x + 3122577)}\\
+% 		&+ \log{16}.
+% 	\end{split}
+% \end{align}
 
@@
 
-Similar to the logarithm transformation, we must provide an approximation for $x^\gamma$.
-We have derived an infinite series in Appendix~\ref{sec:approx-pwr}.
+Similar to the logarithm transformation, to apply this transformation using Paillier and DGK, we must provide an approximation for $x^\gamma$.
+We can use partial sums of the following series, which relies on the logarithm function.
 \begin{align}
@@
 \end{align}
-Partial sums of the above infinite series can be calculated based on the closed form approximation for the logarithm in Equation \ref{eq:scaledquadraturech3}.
-For the implementation of the power-law transformation, a partial sum consisting of the first five terms of the infinite series were used.
+% Partial sums of the above infinite series can be calculated based on the closed form approximation for the logarithm in Equation \ref{eq:scaledquadraturech3}. 
+For the implementation of the power-law transformation for this paper, a partial sum consisting of the first five terms of the infinite series were used.
 
@@
 
-\subsection{Summary}
-In summary, the study consists of:
-\begin{itemize}
-	\item Creating a wrapper library that acts as a unified interface which implements the Paillier, DGK, Dasgupta--Pal, and BGV homomorphic cryptosystems.
-	\item An implementation of image processing operations (intensity transformations, facial recognition) under the above cryptosystems.
-	\item Conducting tests for image quality, processing time, using images from the \texttt{faces94} dataset.
-\end{itemize}
+%% Summary not needed, this was only important for the thesis proposal - Aldrich
+% \subsection{Summary}
+% In summary, the study consists of:
+% \begin{itemize}
+% 	\item Creating a wrapper library that acts as a unified interface which implements the Paillier, DGK, Dasgupta--Pal, and BGV homomorphic cryptosystems.
+% 	\item An implementation of image processing operations (intensity transformations, facial recognition) under the above cryptosystems.
+% 	\item Conducting tests for image quality, processing time, using images from the \texttt{faces94} dataset.
+% \end{itemize}
 

### 2019-02-10 paper/paper-conf.tex
Added summary of FP arithmetic extensions to PHE
summarized the relevant part ofthe PCSC paper

@@
 \begin{itemize}
-	\item The Paillier cryptosystem is incorporated using the implementation at \url{https://github.com/n1analytics/python-paillier} developed by Data61 - CSIRO.
+	\item The Paillier cryptosystem is incorporated using the python-paillier library at \url{https://github.com/n1analytics/python-paillier} developed by Data61 - CSIRO.
 	\item The DGK cryptosystem is ported from the C++ implementation at \url{https://github.com/encryptogroup/ENCRYPTO_utils}, developed by Daniel Demmler from EC-SPRIDE.
@@
 \subsubsection{Extension of Partially Homomorphic Cryptosystems}
-\label{sse:pheextension}
+\label{sssec:pheextension}
+In order to use Paillier and DGK for secure image processing, we require the two schemes to support the encryption of floating-point (FP)numbers, as well as multiplication and division of arbitrary ciphertexts.
+We extend the two cryptosystems to FP operations by using an approach shown in~\cite{ziad_cryptoimg:_2016}.
+This approach represents FP numbers using a pair $(m,e)$, where $m$ represents the mantissa (which is encrypted), and $e$ represents the exponent (which is not encrypted).
+This approach is also used by the python-paillier library.
+This represntation allows us to extend the addition and plaintext multiplication homomorphisms of the Paillier and DGK cryptosystems to floating-point numbers.
+
+Various two-party protocols can be used to facilitate ciphertext multiplication and division.
+These allow a server armed with only knowledge of the public key, to obtain the product and quotient of ciphertexts, by communicating with the client, who has the private key.
+For division, we use the protocol defined in~\cite{boukoros_lightweight_2017}: to obtain $E(x/y)$ from $E(x)$ and $E(y)$, the server sends $E(rx)$ and $E(ry)$ to the client, (where $r$ is a random non-zero number), allowing the client to compute $E(rx/ry)$ and give the result back to the server.
+
+For multiplication, we adapt the protocol to calculate Euclidean distances used in \cite{hutchison_privacy-preserving_2009}, which provides a two-party protocol which yields $E(x^2)$ given $E(x)$.
+We use this protocol together with the additive homomorphism of the partially homomorphic cryptosystems to instead compute $E((x + y)^2 - x^2 - y^2) = E(2xy)$, from which we can easily obtain $E(xy)$ through plaintext multiplication.
+
 % [TO-DO: This is further explained in another paper.]
@@
 We now describe how we implement the logarithm and power-law image intensity transformations.
-In the case of partially homomorphic cryptosystems (Paillier, DGK), if exponentiation and multiplication is required, the secure protocols in section \ref{ssec:pheextension} will be used.
+In the case of partially homomorphic cryptosystems (Paillier, DGK), if ciphertext multiplication or division is required, the secure protocols in section \ref{sssec:pheextension} will be used.
 
@@
 	b(x) &= 30(x^5 + 405x^4 + 27210x^3 + 488810x^2 + 2536005x \\
-	&+ 3122577)
+	&+ 3122577).
 	\end{split}

### 2019-02-11 paper/paper-conf.tex
Final paper

@@
 To meet these needs, various cryptosystems have been developed.
-A cryptosystem is a system which operates on plaintexts, ciphertexts and keys using an encryption algorithm, which maps a plaintext to a ciphertext, together with a decryption algorithm, which maps a ciphertext to a plaintext, given an appropriate key~\cite{bauer_cryptosystem_2005}.
+% A cryptosystem is a system which operates on plaintexts, ciphertexts and keys using an encryption algorithm, which maps a plaintext to a ciphertext, together with a decryption algorithm, which maps a ciphertext to a plaintext, given an appropriate key~\cite{bauer_cryptosystem_2005}.
 The encryption and decryption algorithms are chosen such that the plaintext cannot easily be recovered from the ciphertext without knowledge of the key.
@@
 A client-server model for secure computation will be assumed to allow operations such as secure comparison and exponentiation.
-Training and test data are taken from the publicly available \texttt{faces94} dataset (\url{https://cswww.essex.ac.uk/mv/allfaces/faces94.html}) maintained by the University of Essex.
+% Training and test data are taken from the publicly available \texttt{faces94} dataset (\url{https://cswww.essex.ac.uk/mv/allfaces/faces94.html}) maintained by the University of Essex.
 
@@
 The literature shows existing homomorphic cryptosystems and how they support primitive operations (usually addition and multiplication) on encrypted data, however, for homomorphic cryptosystems to be useful for practical use, efficient support for more complicated image processing operation must be demonstrated as well.
-While implementations of image processing operations in a homomorphic cryptosystem exist in the literature~\cite{ziad_cryptoimg:_2016, garay_algorithms_2014}, our study targets the more computationally intensive task of facial detection.
+While implementations of image processing operations in a homomorphic cryptosystem exist in the literature~\cite{ziad_cryptoimg:_2016, garay_algorithms_2014}, our study targets the more computationally intensive task of facial recognition and detection.
+
+In the Philippine setting, preservation of data privacy is of utmost importance when it comes to outsourcing work involving sensitive data to local companies with the ratification of the Data Privacy Act of 2012.
+Thus recent developments in applications of homomorphic encryption on non-text-based data (such as images) are becoming relevant today.
 
@@
     &= (g^m)^k \cdot (h^r)^k \bmod{n}\\
-    &= g^{km} \cdot (h^kr) \bmod{n}
+    &= g^{km} \cdot (h^{kr}) \bmod{n}
   \end{align*}
-  Since $r$ is a random integer, $kr$ is also a random integer, Therefore, $g^{km} \cdot (h^kr) \bmod{n} = D(E(m_1)^k)$ is a valid encryption of the message $km$.
+  Since $r$ is a random integer, $kr$ is also a random integer, Therefore, $g^{km} \cdot (h^{kr}) \bmod{n} = D(E(m)^k)$ is a valid encryption of the message $km$.
 \end{proof}
@@
 For this study, we will be using \textit{HElib} \cite{garay_algorithms_2014}, an open-source library which implements the BGV cryptosystem with optimizations to improve efficiency.
-Evaluation of operations on 120 inputs in HELib was performed in around 4 minutes, with an average of 2 seconds to process a single input \cite{hutchison_fully_2010,cryptoeprint:2011:566}.
+Evaluation of operations on 120 inputs in \textit{HELib} was performed in around 4 minutes, with an average of 2 seconds to process a single input \cite{hutchison_fully_2010,cryptoeprint:2011:566}.
 
@@
 attempts to implement privacy-preserving image processing using \textit{CryptoImg}, a library for the Open Source Computer Vision Library (OpenCV)~\cite{bradski_opencv_2000} which implements various homomorphic encryption and image processing routines using the Paillier homomorphic cryptosystem~\cite{ziad_cryptoimg:_2016}.
-The CryptoImg library assumed a client-server model wherein a client requests image processing operations from a server.
+The \textit{CryptoImg} library assumed a client-server model wherein a client requests image processing operations from a server.
 A client first encrypts a digital image and sends the image securely to a server, which then operates on the encrypted image without revealing its contents.
@@
 
-\begin{figure}[!h]
+\begin{figure}[h]
     \centering
@@
 
-The match finding step is done by comparing the distances obtained from the previous step to a specified threshold $T$.
+The match-finding step is done by comparing the distances obtained from the previous step to a specified threshold $T$.
 If the minimum distance is smaller than $T$, then a match is found, and the encrypted identity of the match is returned to Alice \cite{hutchison_privacy-preserving_2009}.
@@
 \label{sssec:pheextension}
-In order to use Paillier and DGK for secure image processing, we require the two schemes to support the encryption of floating-point (FP)numbers, as well as multiplication and division of arbitrary ciphertexts.
+In order to use Paillier and DGK for secure image processing, we require the two schemes to support the encryption of floating-point (FP) numbers, as well as multiplication and division of arbitrary ciphertexts.
 We extend the two cryptosystems to FP operations by using an approach shown in~\cite{ziad_cryptoimg:_2016}.
@@
 We now describe how we implement the logarithm and power-law image intensity transformations.
-In the case of partially homomorphic cryptosystems (Paillier, DGK), if ciphertext multiplication or division is required, the secure protocols in section \ref{sssec:pheextension} will be used.
+In the case of partially homomorphic cryptosystems (Paillier and DGK), if ciphertext multiplication or division is required, the secure protocols in section~\ref{sssec:pheextension} will be used.
 
@@
 The CT was generated by encrypting the image, then applying the operation, and the CDT was generated by decrypting the CT.
-The four images (PT, PDT, CT, CDT) were then compared using various benchmarks to evaluate the quality and security of each homomorphic encryption scheme.
+The three images (PT, PDT, CDT) were then compared using various benchmarks to evaluate the quality and security of each homomorphic encryption scheme.
 
@@
 
-As before, training and test data were also secured from the \texttt{faces94} dataset. The images were first converted to grayscale but it is not downsampled, unlike in the previous test.
+As before, training and test data were also secured from the \texttt{faces94} dataset. The images were first converted to grayscale and then downsampled to $40 \times 36$ pixels.
 
@@
 \section{Preliminary Results and Discussion}
-The results shown in this section are gathered from the tests for intensity transformations under Paillier and Dasgupta--Pal cryptosystems.
+The results shown in this section are gathered from the tests for intensity transformations under Paillier and DGK cryptosystems.
 During testing, initial results obtained from BGV, particularly with image operations involving floating-point numbers like the logarithmic transformation, were unstable (i.e.
@@
 
+% \begin{table*}
+% 	\centering
+% 	\caption{Comparison of intensity transformations under Dasgupta--Pal}
+% 	\label{tbl:it-dp}
+% 	\begin{tabular}{m{1cm}*{7}{>{\centering\arraybackslash}m{1.75cm}}}
+% 		\toprule
+% 		\multirow{2}{*}{Image} & \multirow{2}{*}{Original} & \multicolumn{2}{c}{Image negation} & \multicolumn{2}{c}{Logarithm transformation} & \multicolumn{2}{c}{Power-law transformation} \\
+% 							   &                           & PDT           & CDT          & PDT            & CDT           & PDT               & CDT           \\ 
+% 		\midrule
+% 		\xintForpair #1#2 in {(anpage,a), (bplyce,b), (drbost,c), (ksunth,d), (martin,e), (pmives,f), (rnpwil,g), (sbains,h), (swewin,i), (yfhsie,j)} \do {%
+% 		(#2) & \includegraphics[width=1.75cm]{out_faces/dp_negate_#1_original.png} & \includegraphics[width=1.75cm]{out_faces/dp_negate_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/dp_negate_#1_decrypted.png} & \includegraphics[width=1.75cm]{out_faces/dp_logtransform_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/dp_logtransform_#1_decrypted.png} & \includegraphics[width=1.75cm]{out_faces/paillier_pwrtransform_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/dp_pwrtransform_#1_decrypted.png} \\ }%
+% 		\bottomrule
+% 	\end{tabular}
+% \end{table*}
+
 \begin{table*}
 	\centering
-	\caption{Comparison of intensity transformations under Dasgupta--Pal}
-	\label{tbl:it-dp}
+	\caption{Comparison of intensity transformations under DGK}
+	\label{tbl:it-dgk}
 	\begin{tabular}{m{1cm}*{7}{>{\centering\arraybackslash}m{1.75cm}}}
@@
 		\xintForpair #1#2 in {(anpage,a), (bplyce,b), (drbost,c), (ksunth,d), (martin,e), (pmives,f), (rnpwil,g), (sbains,h), (swewin,i), (yfhsie,j)} \do {%
-		(#2) & \includegraphics[width=1.75cm]{out_faces/dp_negate_#1_original.png} & \includegraphics[width=1.75cm]{out_faces/dp_negate_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/dp_negate_#1_decrypted.png} & \includegraphics[width=1.75cm]{out_faces/dp_logtransform_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/dp_logtransform_#1_decrypted.png} & \includegraphics[width=1.75cm]{out_faces/paillier_pwrtransform_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/dp_pwrtransform_#1_decrypted.png} \\ }%
+		(#2) & \includegraphics[width=1.75cm]{out_faces/dgk_negate_#1_original.png} & \includegraphics[width=1.75cm]{out_faces/dgk_negate_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/dgk_negate_#1_decrypted.png} & \includegraphics[width=1.75cm]{out_faces/dgk_logtransform_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/dgk_logtransform_#1_decrypted.png} & \includegraphics[width=1.75cm]{out_faces/dgk_pwrtransform_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/dgk_pwrtransform_#1_decrypted.png} \\ }%
 		\bottomrule
@@
 
-Table~\ref{tbl:it-pal} shows the images obtained from the intensity transformation tests under the Paillier cryptosystem, while Table~\ref{tbl:it-dp} shows the resulting images from the same tests under the Dasgupta--Pal cryptosystem.
+Table~\ref{tbl:it-pal} shows the images obtained from the intensity transformation tests under the Paillier cryptosystem, while Table~\ref{tbl:it-dgk} shows the resulting images from the same tests under the DGK cryptosystem.
 Shown for each image is the original unecrypted image, and for each intensity transformation the \textit{plaintext domain transformation} (PDT) is given which is the resulting image after applying the transformation to the unencrypted image and the \textit{ciphertext domain transformation} (CDT) is the decrypted image of the processed encrypted image.
@@
 The following tables show the resulting metric scores for mean squared error (MSE), peak signal to noise ratio (PSNR), and structural similarity index (SSIM), as well as time taken (in seconds) for encrypting the input image ($t_\text{enc}$), applying an operation to the encrypted image ($t_\text{apply}$), and decrypting the resulting encrypted image ($t_\text{dec}$), for each image in the test set.
-Tables~\ref{tbl:neg-pal} and~\ref{tbl:neg-dp} show the results obtained from applying image negation, Tables~\ref{tbl:log-pal} and~\ref{tbl:log-dp} from applying logarithm transformation, and Tables~\ref{tbl:pwr-pal} and~\ref{tbl:pwr-dp} from applying power-law transformation.
+Tables~\ref{tbl:neg-pal} and~\ref{tbl:neg-dgk} show the results obtained from applying image negation, Tables~\ref{tbl:log-pal} and~\ref{tbl:log-dgk} from applying logarithm transformation, and Tables~\ref{tbl:pwr-pal} and~\ref{tbl:pwr-dgk} from applying power-law transformation.
 
 \subsubsection{Image Negation}
-Both the Paillier and Dasgupta--Pal cryptosystems were able to perform image negation under the encrypted domain without introducing noise in the resulting image.
+Both the Paillier and DGK cryptosystems were able to perform image negation under the encrypted domain without introducing noise in the resulting image.
 In other words, the resulting image from doing image negation on an image on the clear and doing image negation under the encrypted domain are identical, as evidenced by the mean squared errors being exactly equal to zero, the PSNR being infinite, and the SSIM being exactly equal to one.
-
-The Paillier cryptosystem performed better in terms of time, only taking about 0.01 seconds to apply image negation.
-On the other hand, the Dasgupta--Pal cryptosystem took about 22 seconds each to apply the same operation, which is expected since the implementation for Dasgupta--Pal was done in Python without using any external libraries.
+While the time taken to apply image negation is comparable to that of DGK, the Paillier cryptosystem performed better in terms of encryption and decryption time.
 
@@
 \end{table}
+% \begin{table}[h]
+% 	\centering
+% 	\caption{Image negation under Dasgupta--Pal}
+% 	\label{tbl:neg-dp}
+%     \begin{tabular}{lcccccc}
+%         \toprule
+%         Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
+% 		(a) & 0.000 & $\infty$ & 1.00000 & 0.221 & 30.217 & 0.239 \\
+% 		(b) & 0.000 & $\infty$ & 1.00000 & 0.190 & 30.919 & 0.216 \\
+% 		(c) & 0.000 & $\infty$ & 1.00000 & 0.284 & 31.182 & 0.268 \\
+% 		(d) & 0.000 & $\infty$ & 1.00000 & 0.225 & 32.581 & 0.223 \\
+% 		(e) & 0.000 & $\infty$ & 1.00000 & 0.220 & 32.220 & 0.271 \\
+% 		(f) & 0.000 & $\infty$ & 1.00000 & 0.287 & 31.224 & 0.294 \\
+% 		(g) & 0.000 & $\infty$ & 1.00000 & 0.285 & 29.478 & 0.284 \\
+% 		(h) & 0.000 & $\infty$ & 1.00000 & 0.186 & 29.784 & 0.362 \\
+% 		(i) & 0.000 & $\infty$ & 1.00000 & 0.243 & 38.407 & 0.220 \\
+% 		(j) & 0.000 & $\infty$ & 1.00000 & 0.285 & 29.488 & 0.449 \\		
+% 		\bottomrule
+%         \end{tabular}
+% \end{table}
 \begin{table}[h]
 	\centering
-	\caption{Image negation under Dasgupta--Pal}
-	\label{tbl:neg-dp}
+	\caption{Image negation under DGK}
+	\label{tbl:neg-dgk}
     \begin{tabular}{lcccccc}
@@
         Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
-		(a) & 0.000 & $\infty$ & 1.00000 & 0.221 & 30.217 & 0.239 \\
-		(b) & 0.000 & $\infty$ & 1.00000 & 0.190 & 30.919 & 0.216 \\
-		(c) & 0.000 & $\infty$ & 1.00000 & 0.284 & 31.182 & 0.268 \\
-		(d) & 0.000 & $\infty$ & 1.00000 & 0.225 & 32.581 & 0.223 \\
-		(e) & 0.000 & $\infty$ & 1.00000 & 0.220 & 32.220 & 0.271 \\
-		(f) & 0.000 & $\infty$ & 1.00000 & 0.287 & 31.224 & 0.294 \\
-		(g) & 0.000 & $\infty$ & 1.00000 & 0.285 & 29.478 & 0.284 \\
-		(h) & 0.000 & $\infty$ & 1.00000 & 0.186 & 29.784 & 0.362 \\
-		(i) & 0.000 & $\infty$ & 1.00000 & 0.243 & 38.407 & 0.220 \\
-		(j) & 0.000 & $\infty$ & 1.00000 & 0.285 & 29.488 & 0.449 \\		
+		(a) & 0.000 & $\infty$ & 1.00000 & 0.509 & 0.011 & 0.450 \\
+		(b) & 0.000 & $\infty$ & 1.00000 & 0.512 & 0.009 & 0.462 \\
+		(c) & 0.000 & $\infty$ & 1.00000 & 0.732 & 0.018 & 0.519 \\
+		(d) & 0.000 & $\infty$ & 1.00000 & 0.593 & 0.017 & 0.677 \\
+		(e) & 0.000 & $\infty$ & 1.00000 & 0.607 & 0.010 & 0.454 \\
+		(f) & 0.000 & $\infty$ & 1.00000 & 0.550 & 0.010 & 0.507 \\
+		(g) & 0.000 & $\infty$ & 1.00000 & 0.532 & 0.010 & 0.471 \\
+		(h) & 0.000 & $\infty$ & 1.00000 & 0.538 & 0.010 & 0.513 \\
+		(i) & 0.000 & $\infty$ & 1.00000 & 0.606 & 0.010 & 0.519 \\
+		(j) & 0.000 & $\infty$ & 1.00000 & 0.608 & 0.012 & 0.496 \\		
 		\bottomrule
@@
 \subsubsection{Logarithm Transformation}
-Unlike image negation, logarithm transformation involves more operations, so the increase in processing time for both cryptosystems are expected.
-Applying the logarithm transformation under Paillier took about 2 seconds per image, while it took about 13.5 minutes each under Dasgupta--Pal.
-
-The logarithm transformation under Dasgupta--Pal turned out to be more accurate than Paillier, whose mean squared errors approach zero and the SSIM values approach one for every image as shown in Table~\ref{tbl:log-dp}.
-Although the results from using Paillier show that it is also accurate enough with the mean squared errors being less than 30 and the SSIM values average to 0.99, Dasgupta--Pal has been able to produce an almost identical result to that of the plaintext domain transformation counterparts.
-This observation is rather unexpected, considering that the implementation used for Paillier is more robust (due to its use of external C/C++ libraries which makes computations faster).
+Unlike image negation, logarithm transformation involves more operations, so the increase in processing times for both cryptosystems are expected.
+Applying the logarithm transformation under Paillier took about 2 seconds per image, while it took about 25 seconds each under DGK.
+Applying the logarithm transformation under Paillier results in faster and more accurate output images (with $\text{MSE} \le 30$ and $\text{SSIM} \approx 0.99$) than under DGK (with $\text{MSE} \le 300$ and $0.61 \le \text{SSIM} \le 0.87$).
 
@@
 \end{table}
+% \begin{table}[h]
+% 	\caption{Logarithm transformation under Dasgupta--Pal}
+% 	\label{tbl:log-dp}
+%     \begin{tabular}{lcccccc}
+%         \toprule
+%         Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
+% 		(a) & 0.004 & 71.624 & 0.99999 & 0.287 & 802.957 & 0.036 \\
+% 		(b) & 0.000 & 82.043 & 1.00000 & 0.190 & 815.384 & 0.048 \\
+% 		(c) & 0.004 & 72.480 & 1.00000 & 0.270 & 813.640 & 0.036 \\
+% 		(d) & 0.000 & 87.372 & 1.00000 & 0.204 & 804.629 & 0.047 \\
+% 		(e) & 0.001 & 77.421 & 1.00000 & 0.245 & 822.940 & 0.036 \\
+% 		(f) & 0.001 & 76.934 & 1.00000 & 0.194 & 814.132 & 0.036 \\
+% 		(g) & 0.000 & 83.135 & 1.00000 & 0.197 & 808.503 & 0.047 \\
+% 		(h) & 0.001 & 77.301 & 1.00000 & 0.270 & 809.406 & 0.047 \\
+% 		(i) & 0.006 & 70.004 & 0.99999 & 0.268 & 813.217 & 0.051 \\
+% 		(j) & 0.001 & 78.576 & 1.00000 & 0.243 & 830.640 & 0.039 \\
+% 		\bottomrule
+%         \end{tabular}
+% \end{table}
 \begin{table}[h]
-	\caption{Logarithm transformation under Dasgupta--Pal}
-	\label{tbl:log-dp}
+	\caption{Logarithm transformation under DGK}
+	\label{tbl:log-dgk}
     \begin{tabular}{lcccccc}
@@
         Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
-		(a) & 0.004 & 71.624 & 0.99999 & 0.287 & 802.957 & 0.036 \\
-		(b) & 0.000 & 82.043 & 1.00000 & 0.190 & 815.384 & 0.048 \\
-		(c) & 0.004 & 72.480 & 1.00000 & 0.270 & 813.640 & 0.036 \\
-		(d) & 0.000 & 87.372 & 1.00000 & 0.204 & 804.629 & 0.047 \\
-		(e) & 0.001 & 77.421 & 1.00000 & 0.245 & 822.940 & 0.036 \\
-		(f) & 0.001 & 76.934 & 1.00000 & 0.194 & 814.132 & 0.036 \\
-		(g) & 0.000 & 83.135 & 1.00000 & 0.197 & 808.503 & 0.047 \\
-		(h) & 0.001 & 77.301 & 1.00000 & 0.270 & 809.406 & 0.047 \\
-		(i) & 0.006 & 70.004 & 0.99999 & 0.268 & 813.217 & 0.051 \\
-		(j) & 0.001 & 78.576 & 1.00000 & 0.243 & 830.640 & 0.039 \\
+		(a) & 222.196 & 24.663 & 0.83568 & 0.635 & 25.556 & 0.488 \\
+		(b) & 180.941 & 25.555 & 0.75159 & 0.542 & 27.102 & 0.460 \\
+		(c) & 295.227 & 23.429 & 0.61360 & 0.534 & 25.720 & 0.486 \\
+		(d) & 286.799 & 23.555 & 0.76514 & 0.622 & 25.118 & 0.467 \\
+		(e) & 215.389 & 24.799 & 0.66924 & 0.557 & 25.500 & 0.452 \\
+		(f) & 65.621 & 29.960 & 0.83973 & 0.561 & 25.014 & 0.458 \\
+		(g) & 133.007 & 26.892 & 0.74749 & 0.572 & 25.605 & 0.497 \\
+		(h) & 225.269 & 24.604 & 0.70342 & 0.548 & 25.088 & 0.468 \\
+		(i) & 171.073 & 25.799 & 0.83257 & 0.538 & 25.410 & 0.494 \\
+		(j) & 203.214 & 25.051 & 0.86675 & 0.528 & 25.383 & 0.516 \\
 		\bottomrule
@@
 
-When Dasgupta--Pal was used in the power-law transformation, it completely failed to produce a discernible image and only resulted in a blank image.
+When DGK was used in the power-law transformation, it failed to produce a discernible image and only resulted in an almost black image with a faint shape of a face.
 The mean squared errors for this case is an order of magnitude higher than the results from using Paillier.
-Furthermore, doing a power-law transformation under Dasgupta--Pal is not only impractical in terms of accuracy, but also it is impractical in terms of time efficiency because it took about 2 hours and 40 minutes on average to process each image.
+Furthermore, doing a power-law transformation under DGK is not only impractical in terms of accuracy, but also it is somewhat impractical in terms of time efficiency because it took at most 4 minutes to process each image.
 
+% \begin{table}[h]
+% 	\centering
+% 	\caption{Power-law transformation under Dasgupta--Pal}
+% 	\label{tbl:pwr-dp}
+%     \begin{tabular}{lcccccc}
+%         \toprule
+%         Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
+% 		% \texttt{anpage} & 25115.891 & 4.131 & 0.00000 & 0.016 & 741.872 & 0.031 \\ 10x10
+% 		% \texttt{bplyce} & 22777.187 & 4.556 & 0.00000 & 0.017 & 730.873 & 0.003 \\ 10x10
+% 		% \texttt{drbost} & 18899.906 & 5.366 & 0.00000 & 0.014 & 733.409 & 0.003 \\
+% 		(a) & 25008.723 & 4.150 & 0.000 & 0.376 & 9700.926 & 1.269 \\
+% 		(b) & 22700.522 & 4.570 & 0.000 & 0.230 & 9196.609 & 0.043 \\
+% 		(c) & 18902.214 & 5.366 & 0.000 & 0.277 & 9261.407 & 0.150 \\
+% 		(d) & 12585.729 & 7.132 & 0.000 & 0.257 & 9259.010 & 0.051 \\
+% 		(e) & 17012.423 & 5.823 & 0.000 & 0.279 & 9440.351 & 0.051 \\
+% 		(f) & 31124.615 & 3.200 & 0.000 & 0.285 & 9492.149 & 0.052 \\
+% 		(g) & 22982.917 & 4.517 & 0.000 & 0.289 & 9321.928 & 0.048 \\
+% 		(h) & 13469.155 & 6.837 & 0.000 & 0.257 & 9233.818 & 0.048 \\
+% 		(i) & 37453.834 & 2.396 & 0.000 & 0.262 & 9203.045 & 0.048 \\
+% 		(j) & 23037.762 & 4.506 & 0.000 & 0.258 & 9210.393 & 0.048 \\
+% 		% \texttt{drbost} & 18902.214 & 5.366 & 0.00000 & 0.064 & 2261.407 & 0.110 \\ % 20x18
+% 		% \texttt{ksunth} & 12585.729 & 7.132 & 0.00000 & 0.044 & 2259.010 & 0.011 \\ % 20x18
+% 		% \texttt{martin} & 17012.423 & 5.823 & 0.00000 & 0.066 & 2440.351 & 0.011 \\
+% 		% \texttt{pmives} & 31124.615 & 3.200 & 0.00000 & 0.072 & 2492.149 & 0.012 \\
+% 		% \texttt{rnpwil} & 22982.917 & 4.517 & 0.00000 & 0.076 & 2321.928 & 0.008 \\
+% 		% \texttt{sbains} & 13469.155 & 6.837 & 0.00000 & 0.044 & 2233.818 & 0.008 \\
+% 		% \texttt{swewin} & 37453.834 & 2.396 & 0.00000 & 0.049 & 2203.045 & 0.008 \\
+% 		% \texttt{yfhsie} & 23037.762 & 4.506 & 0.00000 & 0.045 & 2210.393 & 0.008 \\
+% 		\bottomrule
+%         \end{tabular}
+% \end{table}
 \begin{table}[h]
 	\centering
-	\caption{Power-law transformation under Dasgupta--Pal}
-	\label{tbl:pwr-dp}
+	\caption{Power-law transformation under DGK}
+	\label{tbl:pwr-dgk}
     \begin{tabular}{lcccccc}
@@
         Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
-		% \texttt{anpage} & 25115.891 & 4.131 & 0.00000 & 0.016 & 741.872 & 0.031 \\ 10x10
-		% \texttt{bplyce} & 22777.187 & 4.556 & 0.00000 & 0.017 & 730.873 & 0.003 \\ 10x10
-		% \texttt{drbost} & 18899.906 & 5.366 & 0.00000 & 0.014 & 733.409 & 0.003 \\
-		(a) & 25008.723 & 4.150 & 0.000 & 0.376 & 9700.926 & 1.269 \\
-		(b) & 22700.522 & 4.570 & 0.000 & 0.230 & 9196.609 & 0.043 \\
-		(c) & 18902.214 & 5.366 & 0.000 & 0.277 & 9261.407 & 0.150 \\
-		(d) & 12585.729 & 7.132 & 0.000 & 0.257 & 9259.010 & 0.051 \\
-		(e) & 17012.423 & 5.823 & 0.000 & 0.279 & 9440.351 & 0.051 \\
-		(f) & 31124.615 & 3.200 & 0.000 & 0.285 & 9492.149 & 0.052 \\
-		(g) & 22982.917 & 4.517 & 0.000 & 0.289 & 9321.928 & 0.048 \\
-		(h) & 13469.155 & 6.837 & 0.000 & 0.257 & 9233.818 & 0.048 \\
-		(i) & 37453.834 & 2.396 & 0.000 & 0.262 & 9203.045 & 0.048 \\
-		(j) & 23037.762 & 4.506 & 0.000 & 0.258 & 9210.393 & 0.048 \\
-		% \texttt{drbost} & 18902.214 & 5.366 & 0.00000 & 0.064 & 2261.407 & 0.110 \\ % 20x18
-		% \texttt{ksunth} & 12585.729 & 7.132 & 0.00000 & 0.044 & 2259.010 & 0.011 \\ % 20x18
-		% \texttt{martin} & 17012.423 & 5.823 & 0.00000 & 0.066 & 2440.351 & 0.011 \\
-		% \texttt{pmives} & 31124.615 & 3.200 & 0.00000 & 0.072 & 2492.149 & 0.012 \\
-		% \texttt{rnpwil} & 22982.917 & 4.517 & 0.00000 & 0.076 & 2321.928 & 0.008 \\
-		% \texttt{sbains} & 13469.155 & 6.837 & 0.00000 & 0.044 & 2233.818 & 0.008 \\
-		% \texttt{swewin} & 37453.834 & 2.396 & 0.00000 & 0.049 & 2203.045 & 0.008 \\
-		% \texttt{yfhsie} & 23037.762 & 4.506 & 0.00000 & 0.045 & 2210.393 & 0.008 \\
+		(a) & 14777.466 & 6.435 & 0.12778 & 0.677 & 204.491 & 0.978 \\
+		(b) & 13343.854 & 6.878 & 0.07894 & 0.913 & 232.692 & 0.663 \\
+		(c) & 10885.568 & 7.762 & 0.09146 & 0.696 & 198.959 & 0.590 \\
+		(d) & 7218.081 & 9.547 & 0.10182 & 0.658 & 160.924 & 0.461 \\
+		(e) & 9994.237 & 8.133 & 0.09100 & 0.518 & 166.274 & 0.507 \\
+		(f) & 19141.793 & 5.311 & 0.08388 & 0.531 & 193.571 & 0.606 \\
+		(g) & 13213.915 & 6.920 & 0.09794 & 0.656 & 163.594 & 0.455 \\
+		(h) & 7444.691 & 9.412 & 0.09291 & 0.522 & 160.426 & 0.463 \\
+		(i) & 21349.488 & 4.837 & 0.17239 & 0.526 & 160.191 & 0.446 \\
+		(j) & 13776.770 & 6.739 & 0.10769 & 0.489 & 156.763 & 0.460 \\
 		\bottomrule
@@
 \section{Conclusion}
-In this paper, we have assessed the feasibility and practicality of various homomorphic cryptosystems with regard to secure processing and manipulation of facial image data through creation of a software library that facilitates image processing operations within the encrypted domain, as well as our own implementation of some homomorphic cryptosystems like Dasgupta--Pal for which existing third-party libraries dedicated for this purpose are not yet available.
+In this paper, we have assessed the feasibility and practicality of various homomorphic cryptosystems with regard to secure processing and manipulation of facial image data through creation of a software library that facilitates image processing operations within the encrypted domain, as well as our own implementation of some homomorphic cryptosystems like DGK.
 
@@
 
-Preliminary results have shown that both Paillier and Dasgupta--Pal apply image negation accurately and efficiently, as evidenced by the perfect zero MSE and infinite PSNR.
-For the logarithm transformation, Paillier was faster and accurate enough (with $\text{MSE} \le 30$ and $\text{SSIM} \approx 0.99$), but Dasgupta--Pal was slower but more accurate (with $\text{MSE} \le 0.01$ and $\text{SSIM} \approx 0.99999$) which was rather unexpected.
-However both Paillier and Dasgupta--Pal fail to produce accurate results in applying the power-law transformation, with the latter completely failing to produce discernible results.
+Preliminary results have shown that both Paillier and DGK apply image negation accurately and efficiently, as evidenced by the perfect zero MSE and infinite PSNR.
+For the logarithm transformation, Paillier was faster and accurate enough (with $\text{MSE} \le 30$ and $\text{SSIM} \approx 0.99$) which was rather unexpected.
+However both Paillier and DGK fail to produce accurate results in applying the power-law transformation, with the latter failing to produce discernible results.
 Based from these results, the Paillier cryptosystem is consistent enough to produce reasonable to accurate results.
@@
 
-Future work would involve improving and optimizing our implementation of the Dasgupta--Pal cryptosystem so that it performs faster.
-A suggestion would be to port the existing implementation to C/C++ and then create a Python library that acts as a wrapper to the C/C++ methods.
+Future work would involve improving and optimizing our implementation of non-linear intensity transformations in terms of number of operations, numerical accuracy and stability, and time efficiency.
+% Future work would involve improving and optimizing our implementation of the DGK cryptosystem so that it performs faster. 
+% A suggestion would be to port the existing implementation to C/C++ and then create a Python library that acts as a wrapper to the C/C++ methods. 
 For future studies, an implementation of a client-server framework or system dealing with secure image processing can be considered.

### 2019-02-14 pcsc-paper/parts/02_01_paillier.tex
Plots for experiment data
Applied most of the reviewer comments
Still missing time benchmarking

@@
 \subsubsection{Key Generation}
-We first define a function $L\left(x\right)$ as the largest integer $v$ greater than zero such that $x-1 \geq vn$.
 We choose two large primes $p$ and $q$, and set $n = pq, \lambda = \mathrm{lcm}\left(p-1,q-1\right)$.
+We then define $L\left(x\right)$ to be the largest integer $v$ greater than zero such that $x-1 \geq vn$.
 Then we select an integer $g$ such that $\gcd\left(L\left(g^\lambda \bmod n^2\right), n\right) = 1$ and $0\leq g \leq n^2$.
@@
     To compute $E\left(c\right)=E\left(a+b\right)$ we compute
+    % \begin{align*}
+	% 	E\left(m_c\right) &= E\left(m_a\right) \oplus \left(b^{e_b-e_a} \otimes E\left(m_b\right)\right) \text{and } e_c = e_a & \text{ if } e_a \leq e_b, \\
+	% 	E\left(m_c\right) &= E\left(m_b\right) \oplus \left(b^{e_a-e_b} \otimes E\left(m_a\right)\right) \text{and } e_c = e_b & \text{ if } e_a > e_b.
+	% \end{align*}
 	\begin{align*}
-		E\left(m_c\right) &= E\left(m_a\right) \oplus \left(b^{e_b-e_a} \otimes E\left(m_b\right)\right) \text{and } e_c = e_a & \text{ if } e_a \leq e_b, \\
-		E\left(m_c\right) &= E\left(m_b\right) \oplus \left(b^{e_a-e_b} \otimes E\left(m_a\right)\right) \text{and } e_c = e_b & \text{ if } e_a > e_b.
+		E\left(m_c\right) &= 
+		\begin{cases}
+			E\left(m_a\right) \oplus \left(b^{e_b-e_a} \otimes E\left(m_b\right)\right) & \text{if } e_a \leq e_b \\
+			E\left(m_b\right) \oplus \left(b^{e_a-e_b} \otimes E\left(m_a\right)\right) & \text{if } e_a > e_b
+		\end{cases}, \\
+		% \text{ and }
+		e_c &= %\min\left(e_a, e_b \right).	
+		\begin{cases}
+			e_a & \text{if } e_a \leq e_b \\
+			e_b & \text{if } e_a > e_b
+		\end{cases}.
 	\end{align*}
-	% \begin{align*}
-	% 	E\left(m_c\right) &= 
-	% 	\begin{cases}
-	% 		E\left(m_a\right) \oplus \left(b^{e_b-e_a} \otimes E\left(m_b\right)\right) & \text{if } e_a \leq e_b \\
-	% 		E\left(m_b\right) \oplus \left(b^{e_a-e_b} \otimes E\left(m_a\right)\right) & \text{if } e_a > e_b
-	% 	\end{cases} \\
-	% 	% \text{ and }
-	% 	e_c &= \min\left(e_a, e_b \right).	
-	% 	% \begin{cases}
-	% 	% 	e_a & \text{if } e_a \leq e_b \\
-	% 	% 	e_b & \text{if } e_a > e_b
-	% 	% \end{cases}.
-	% \end{align*}
   \item[Scalar multiplication.]

### 2019-02-14 pcsc-paper/parts/03_exponentialandlogarithmic.tex
Applied most of the reviewer comments
Still missing time benchmarking

@@
 \section{Logarithmic Function Approximation}
+\label{sec:logarithm_approximation}
 We now present our main contribution in this paper: a general method to improve the general accuracy of the logarithm approximation given by Khattri in~\cite{khattri_new_2009} for use in privacy-preserving calculation, provided that accuracy is only required for a specific range.
@@
 
-Applying the five-point Gauss--Legendre quadrature rule to approximate $\int_{n}^{\alpha n + \alpha}{\frac{1}{x}\diff x}$ with $\alpha = 1/16$ using SageMath 8.3, we arrive at the approximation:
+Applying the five-point Gauss--Legendre quadrature rule to approximate $\int_{n}^{\alpha n + \alpha}{\frac{1}{t}\diff t}$ with $\alpha = 1/16$ using SageMath 8.3, we arrive at the approximation:
 \begin{align}\label{eq:optimal_log_approximation}

### 2019-02-14 pcsc-paper/parts/04_inversetrig.tex
3rd draft
apply 2nd round of comments
Applied most of the reviewer comments
Still missing time benchmarking

--- 2019-01-20 pcsc-paper/parts/04_inversetrig.tex
@@
-\section{Inverse Trigonometric Functions}
+\section{Inverse Tangent Function Approximation}
+\label{sec:arctan_approximation}
 We will now show how a Gauss--Legendre quadrature approach can also be used for efficient privacy-preserving approximation of the inverse tangent function.
@@
 		\addplot[thick, ACMOrange] table[x=x, y=euler] {plots/abs_err_arctan.txt};
-		\legend{Gauss--Legendre quadrature, Euler's series}
+		\legend{Gauss--Legendre quadrature, Partial sum of Euler's series}
 		\end{semilogyaxis}

### 2019-02-14 pcsc-paper/parts/05__00_experiments.tex
Applied most of the reviewer comments
Still missing time benchmarking

\section{Experiments}
We implemented privacy-preserving floating-point arithmetic using the system described in Section~\ref{sec:fp_arithmetic}, through the \texttt{python-paillier} library (\url{https://github.com/n1analytics/python-paillier}) running on Python~3.6.5.

We first summarize the approximations discussed in sections \ref{sec:logarithm_approximation} and \ref{sec:arctan_approximation}. % in Table \ref{tab:approximation_summary}.

\begin{table*}[ht]
	\caption{Summary of approximations for logarithm and inverse tangent}
	\label{tab:approximation_summary}
    \begin{tabular}{
        p{\dimexpr 0.4\linewidth-2\tabcolsep}
        p{\dimexpr 0.6\linewidth-2\tabcolsep}}
		\toprule
		Approximation & Derivation and formula\\
		\midrule
            Original quadrature for $\log\left(1+x\right)$ (equation \ref{eq:standard_logarithm_quadrature})
            & Let $x=1/n$. Perform 5-point Gauss--Legendre quadrature to approximate $\int_{n}^{n+1}{\frac{1}{t}\diff t} = \log\left(1+x\right)$ This yields the approximation:
            \begin{center}
                $\displaystyle 
            \frac{137x^5 + 2310x^4 + 9870x^3 + 15120x^2 + 7560x}
            {30x^5 + 900x^4 + 6300x^3 + 16800x^2 + 18900x + 7560}$.
            \end{center}
            \\[10pt]

            Scaled quadrature for $\log\left(1+x\right)$ (equation \ref{eq:optimal_log_approximation})
            & Let $x=1/n$ and $\alpha= 1/16$. Perform 5-point Gauss--Legendre quadrature to approximate $\int_{n}^{\alpha n + \alpha}{\frac{1}{t}\diff t} = \log\left(1+x\right) + \log\alpha$. 
            Then subtract $\log\alpha$, which can be computed in the plaintext domain. This yields the approximation:
            \begin{center}
            $\displaystyle 
            \frac{137x^5 + 26685x^4 + 617370x^3 - 6498630x^2 - 121239315x - 257804775}
            {30(x^5 + 405x^4 + 27210x^3 + 488810x^2 + 2536005x + 3122577)}
            + \log{16}$.
            \end{center}
            \\[10pt]

            Partial sum of Euler's series for $\arctan{x}$ (equation \ref{eq:arctan_euler_partial})
            & Compute the partial sum consisting of first five terms of Euler's series for the inverse tangent:
            $\sum_{n=0}^{4}
            {
            \frac
                {2^{2n}(n!)^2}
                {(2n+1)!}
            \frac
                {x^{2n+1}}
                {(1+x^2)^{n+1}}
            }$. This yields the approximation:
            \begin{center}
                $\displaystyle 
                \frac
                {965x^9 + 2370x^7 + 2688x^5 + 1470x^3 + 315x}
                {315\left(x^{10} + 5x^8 + 10x^6 + 10x^4 + 5x^2 + 1\right)}$.
            \end{center}
            \\[10pt]

            Quadrature approximation for $\arctan{x}$ (equation \ref{eq:arctan_quadrature})
            & Perform 5-point Gauss--Legendre quadrature to approximate $\int_0^x{\frac{1}{1+t^2}\diff t} = \arctan{x}$. This yields the approximation:
            \begin{center}
                $\displaystyle
            \frac
            {4\left(225x^9 + 15925x^7 + 144753x^5 + 350595x^3 + 238140x\right)}
            {15\left(x^{10} + 480x^8 + 11760x^6 + 64120x^4 + 114660x^2 + 63504\right)}$.
            \end{center}
            \\
	    \bottomrule
    \end{tabular}
\end{table*}

### 2019-02-14 pcsc-paper/parts/05_testsforaccuracy.tex
3rd draft
apply 2nd round of comments
Applied most of the reviewer comments
Still missing time benchmarking

@@
-\section{Experiments on Accuracy}
-We implemented privacy-preserving floating-point arithmetic using the system described in Section~\ref{sec:fp_arithmetic}, through the \texttt{python-paillier} library (\url{https://github.com/n1analytics/python-paillier}) running on Python~3.6.5.
-
 \subsection{Logarithm Approximation}
@@
 		\toprule
-		Input & Partial sum of infinite series & Quadrature\\
+		Input & Partial sum of Euler's series & Quadrature\\
 		\midrule

### 2019-02-14 pcsc-paper/parts/05__00_experiments.tex
Fix 5-point to five-point

@@
 
-We first summarize the approximations discussed in sections \ref{sec:logarithm_approximation} and \ref{sec:arctan_approximation}. % in Table \ref{tab:approximation_summary}.
+We first summarize the approximations discussed in Sections \ref{sec:logarithm_approximation} and \ref{sec:arctan_approximation} in Table \ref{tab:approximation_summary}.
 
@@
             Original quadrature for $\log\left(1+x\right)$ (equation \ref{eq:standard_logarithm_quadrature})
-            & Let $x=1/n$. Perform 5-point Gauss--Legendre quadrature to approximate $\int_{n}^{n+1}{\frac{1}{t}\diff t} = \log\left(1+x\right)$ This yields the approximation:
+            & Let $x=1/n$. Perform five-point Gauss--Legendre quadrature to approximate $\int_{n}^{n+1}{\frac{1}{t}\diff t} = \log\left(1+x\right)$ This yields the approximation:
             \begin{center}
@@
             Scaled quadrature for $\log\left(1+x\right)$ (equation \ref{eq:optimal_log_approximation})
-            & Let $x=1/n$ and $\alpha= 1/16$. Perform 5-point Gauss--Legendre quadrature to approximate $\int_{n}^{\alpha n + \alpha}{\frac{1}{t}\diff t} = \log\left(1+x\right) + \log\alpha$. 
+            & Let $x=1/n$ and $\alpha= 1/16$. Perform five-point Gauss--Legendre quadrature to approximate $\int_{n}^{\alpha n + \alpha}{\frac{1}{t}\diff t} = \log\left(1+x\right) + \log\alpha$. 
             Then subtract $\log\alpha$, which can be computed in the plaintext domain. This yields the approximation:
@@
             Quadrature approximation for $\arctan{x}$ (equation \ref{eq:arctan_quadrature})
-            & Perform 5-point Gauss--Legendre quadrature to approximate $\int_0^x{\frac{1}{1+t^2}\diff t} = \arctan{x}$. This yields the approximation:
+            & Perform five-point Gauss--Legendre quadrature to approximate $\int_0^x{\frac{1}{1+t^2}\diff t} = \arctan{x}$. This yields the approximation:
             \begin{center}

### 2019-02-17 pcsc-paper/parts/04_inversetrig.tex
Added short remark on flops

@@
 We note that in order to evaluate the quadrature approximation in Equation~\ref{eq:arctan_quadrature}, we must compute the value of $x^{10}$, which requires several rounds of the squaring and multiplication protocols to compute.
-We now compare the quadrature approximation to the partial sum composed of the first five terms of Euler's series expansion in Equation~\ref{eq:arctan_euler}, which requires a similar number of floating-point operations to compute:
+We now compare the quadrature approximation to the partial sum composed of the first five terms of Euler's series expansion in Equation~\ref{eq:arctan_euler}:
 \begin{align} \label{eq:arctan_euler_partial}
@@
 \end{align}
+
+We note that the quadrature approximation in Equation~\ref{eq:arctan_quadrature} and the partial sum approximation in Equation~\ref{eq:arctan_euler_partial} are both rational expressions, which differ only in the coefficients of each term.
+For both approximations, the numerator is a ninth-degree polynomial containing only odd powers of $x$ and the denominator is a tenth-degree polynomial containing only even powers of $x$ and a constant term.
+As such, these two approximations require a similar number of floating-point operations.
 

### 2019-02-18 pcsc-paper/parts/05__00_experiments.tex
Time graphs

@@
 
-We first summarize the approximations discussed in Sections \ref{sec:logarithm_approximation} and \ref{sec:arctan_approximation} in Table \ref{tab:approximation_summary}.
+We first summarize the approximations discussed in Sections~\ref{sec:logarithm_approximation} and~\ref{sec:arctan_approximation} in Table~\ref{tab:approximation_summary}.
 

### 2019-02-18 pcsc-paper/parts/05_testsforaccuracy.tex
Time graphs

@@
 \end{figure}
+
+\subsection{Timing Results}
+
+\begin{figure}[!ht]
+	\centering
+	\begin{tikzpicture}
+		\begin{axis}[
+			% xmin=0, xmax=255,
+			ytick={1,2},
+			yticklabels={Scaled quadrature, Original quadrature},
+			xlabel={Time (seconds)},
+			grid=major,
+			legend pos=north east,
+			legend cell align=left,
+		]
+		\addplot+[boxplot, thick, ACMDarkBlue] table[x=x, y=newt] {plots/comp_log_errs.txt};
+		\addplot+[boxplot, thick, ACMOrange] table[x=x, y=oldt] {plots/comp_log_errs.txt};
+		\end{axis}
+	\end{tikzpicture}%
+	\caption{Comparison of logarithm computation times under Paillier}
+	\label{fig:times_log}
+\end{figure}
+
+\begin{figure}[!ht]
+	\centering
+	\begin{tikzpicture}
+		\begin{axis}[
+			% xmin=0, xmax=255,
+			ytick={1,2},
+			yticklabels={Gauss--Legendre quadrature, Euler's series},
+			xlabel={Time (seconds)},
+			grid=major,
+			legend pos=north east,
+			legend cell align=left,
+		]
+		\addplot+[boxplot, thick, ACMDarkBlue] table[x=x, y=newt] {plots/comp_arctan_errs2.txt};
+		\addplot+[boxplot, thick, ACMOrange] table[x=x, y=oldt] {plots/comp_arctan_errs2.txt};
+		\end{axis}
+	\end{tikzpicture}%
+	\caption{Frequency distribution of inverse tangent computation times under Paillier}
+	\label{fig:times_arctan}
+\end{figure}
+
+% \begin{figure}[!ht]
+% 	\centering
+% 	\begin{tikzpicture}
+% 		\begin{axis}[
+% 			xmin=0, xmax=1,
+% 			ymin=1.5, ymax=2.5,
+% 			xlabel={Absolute error}, ylabel={Time (seconds)},
+% 			grid=major,
+% 			legend pos=south east,
+% 			legend cell align=left,
+% 			tick scale binop=\times,
+% 		]
+% 		\addplot+[scatter, only marks, ACMDarkBlue] table[x=newerr, y=newt] {plots/comp_arctan_errs2.txt};
+% 		\addplot+[scatter, only marks, ACMOrange] table[x=olderr, y=oldt] {plots/comp_arctan_errs2.txt};
+% 		\legend{Gauss--Legendre quadrature, Partial sum of Euler's series}
+% 		\end{axis}
+% 	\end{tikzpicture}%
+% 	\caption{Accuracy vs. time in inverse tangent computation under Paillier}
+% 	\label{fig:acc_vs_time_arctan}
+% \end{figure}

### 2019-02-18 pcsc-paper/parts/03_exponentialandlogarithmic.tex
Remove timing results, tweaked graphs

@@
 		% \addplot[very thick, domain=0:300, samples=300]{abs(1/30*(137*x^5 + 26685*x^4 + 617370*x^3 - 6498630*x^2 - 121239315*x - 257804775)/(x^5 + 405*x^4 + 27210*x^3 + 488810*x^2 + 2536005*x + 3122577) - ln(1/16) - ln(x + 1))};
+		\addplot[thick, ACMOrange, domain=0:300, samples=100]{abs(1/30*(137*x^5 + 2310*x^4 + 9870*x^3 + 15120*x^2 + 7560*x)/(x^5 + 30*x^4 + 210*x^3 + 560*x^2 + 630*x + 252) - ln(x + 1))};
 		\addplot[very thick, ACMDarkBlue] table[x=x, y=error] {plots/abs_err_scaledlog.txt};
-		\addplot[densely dashed, domain=0:300, samples=100]{abs(1/30*(137*x^5 + 2310*x^4 + 9870*x^3 + 15120*x^2 + 7560*x)/(x^5 + 30*x^4 + 210*x^3 + 560*x^2 + 630*x + 252) - ln(x + 1))};
-		\legend{Scaled quadrature ($\alpha = 1/16$), Original quadrature ($\alpha = 1$)}
+		\legend{Original quadrature ($\alpha = 1$), Scaled quadrature ($\alpha = 1/16$)}
 	\end{semilogyaxis}

### 2019-02-28 parts/08_appendices_b_numericalapproximations_updated.tex
WIP - Updating log approximation in manuscript

--- 2019-02-14 pcsc-paper/parts/03_exponentialandlogarithmic.tex
@@
+\subsection{Known Approximations for Transcendental Functions}
+Many methods to compute transcendental functions implemented in computer hardware and software libraries rely on direct knowledge of the function arguments.
+Several such approaches include CORDIC (coordinate rotation digital computer), pseudo-division and pseudo-multiplication algorithms~\cite{walther_cordic_2000}, as well as minimax polynomials, which are determined numerically using the Remez algorithm~\cite{harrison_computation_1999}.
+These algorithms, while efficient, rely on table lookups, which cannot be done in a privacy-preserving system where the function arguments cannot be directly determined.
+
+We must therefore rely on other methods, such as using the Taylor series expansions of these functions.
+While also in common use, not all Taylor series expansions have a convenient radius of convergence.
+To circumvent this, we can rely on an approach presented by Khattri in~\cite{khattri_new_2009} to obtain closed-form approximations to functions by approximating related integrals.
+
+Khattri presents the following method to approximate the function $f(x)=\log\left(1+x\right)$.
+Let $x = 1/n$ and consider the integral
+\begin{align}
+	\label{eq:log_integral}
+	\int_{n}^{n+1}{\frac{1}{t}\diff t}=\log{\left(1+\frac{1}{n}\right)}.
+\end{align}
+
+This integral can be approximated using the five-point Gauss--Legendre quadrature rule~\cite{kythe_quadrature_2002}.
+We first convert the integral to an integral over the interval $[-1,1]$ using the following transformation:
+\begin{align*}
+	\int_a^b{f(x)\diff x}
+	&= \frac{b-a}{2}\int_{-1}^{1}{f\left(\frac{b-a}{2}x+\frac{a+b}{2}\right)\diff x}.
+\end{align*}
+Then, we approximate the integral using the following summation:
+\begin{equation*}
+	\int_{-1}^{1}{f\left(x\right)\diff x} \approx \sum_{i=1}^{5}{w_i f\left(x_i\right)},
+\end{equation*}
+where
+\begin{multicols}{2}
+	\noindent
+	\begin{align*}
+		w_1 &= 0,\\
+		w_2 &= \frac{1}{21}\sqrt{245-14\sqrt{70}},\\
+		w_3 &= -\frac{1}{21}\sqrt{245-14\sqrt{70}},\\
+		w_4 &= \frac{1}{21}\sqrt{245+14\sqrt{70}},\\
+		w_5 &= -\frac{1}{21}\sqrt{245+14\sqrt{70}},
+	\end{align*}
+	\columnbreak
+	\begin{align*}
+		x_1 &= \frac{128}{225},\\
+		x_2 &= \frac{1}{900}\left( 322 + 13\sqrt{70}\right),\\
+		x_3 &= \frac{1}{900}\left( 322 + 13\sqrt{70}\right),\\
+		x_4 &= \frac{1}{900}\left( 322 - 13\sqrt{70}\right),\\
+		x_5 &= \frac{1}{900}\left( 322 - 13\sqrt{70}\right).
+	\end{align*}
+\end{multicols}
+Applying this procedure to the integral in Equation~\ref{eq:log_integral} yields the following approximation:
+\begin{equation}\label{eq:standard_logarithm_quadrature}
+	\log\left(1+x\right) \approx
+	\frac{137x^5 + 2310x^4 + 9870x^3 + 15120x^2 + 7560x}
+	{30x^5 + 900x^4 + 6300x^3 + 16800x^2 + 18900x + 7560}.
+\end{equation}
+
+While the closed-form approximation presented by Khattri (Equation~\ref{eq:standard_logarithm_quadrature}) is accurate for values of $x$ near zero, it diverges from $\log{\left(1+x\right)}$ significantly for large values of $x$, as shown in Figure~\ref{fig:standard_logarithm_quadrature}.
+\begin{figure}[!ht]
+	\centering
+	\begin{tikzpicture}
+		\begin{axis}[
+			% height=6cm, width=9cm,
+			xmin=0, xmax=300,
+			ymin=0, ymax=5.5, ytick={0,...,6},
+			xlabel={$x$}, ylabel={$y$},
+			grid=major,
+			legend pos=south east,
+			legend cell align=left,
+		]
+		\addplot[very thick, ACMDarkBlue, domain=0:300, samples=100]{1/30*(137*x^5 + 2310*x^4 + 9870*x^3 + 15120*x^2 + 7560*x)/(x^5 + 30*x^4 + 210*x^3 + 560*x^2 + 630*x + 252)};
+		\addplot[densely dashed, domain=0:300, samples=100]{ln(x)};
+		\legend{5-point quadrature approximation, Actual value of $\log(1+x)$}
+		\end{axis}
+	\end{tikzpicture}%
+	\caption{Graph of $\log{\left(1+x\right)}$ and the approximation in Equation~\ref{eq:standard_logarithm_quadrature}}
+	\label{fig:standard_logarithm_quadrature}
+\end{figure}
+
+However, the quadrature approach presented by Khattri allows us to approximate the logarithm in a larger range than is possible with the Taylor series, as the Taylor series of $\log\left(1+x\right)$ has an interval of convergence of $[-1,1]$.
+
 \section{Logarithmic Function Approximation}

### 2019-03-02 parts/02_relatedliterature_05partiallyhomomorphic.tex
WIP cryptosystem RRL
working on cryptosystem RRL

--- 2018-10-07 parts/02_relatedliterature_05partiallyhomomorphic.tex
@@
 
-In this section, we will present two classical partially homomorphic cryptosystems which we will be testing in the study: the Paillier cryptosystem and the DGK cryptosystem.
-Both of these cryptosystems encrypt integer plaintexts and are additively homomorphic.
-
-We will then show that the cryptosystems can be modified to support privacy-perserving polynomial evaluation in a client-server protocol: given an encrypted message $m$, evaluate $f(m)$ where $f$ is a polynomial function.
+In this section, we will present two classical partially homomorphic cryptosystems (PHEs) which we will be testing in the study: the Paillier cryptosystem and the DGK cryptosystem.
+Both of these cryptosystems encrypt integer plaintexts and are additively homomorphic and allow for the multiplication of a plaintext scalar.
+We will then show how these PHEs may be adapted for secure floating-point computation.
 
@@
 The Paillier cryptosystem \cite{stern_public-key_1999}, developed by Pascal Paillier, is a probabilistic encryption scheme which is based on the composite residuosity class problem.
-The scheme allows for the encryption and decryption of integer messages, and is known to be additively homomorphic.
-We now state the encryption and decryption algorithms of the Paillier cryptosystem and its homomorphic properties.
 
 \subsubsection{Key Generation}
-We first define a function $L(x)$ as the largest integer $v$ greater than zero such that $x-1 \geq vn$.
-We choose two large primes $p$ and $q$, and set $n = pq, \lambda = \mathrm{lcm}(p-1,q-1)$.
-Then we select an integer $g$, $0\leq g \leq n^2$ such that $\mathrm{gcd}(L(g^\lambda \bmod n^2), n) = 1$.
-We denote the public key as $(g,n)$ and the private key $(p,q)$.
+We choose two large primes $p$ and $q$, and set $n = pq $ and $ \lambda = \mathrm{lcm}\left(p-1,q-1\right)$.
+We then define $L\left(x\right)$ to be the largest integer $v$ greater than zero such that $x-1 \geq vn$.
+Then we select an integer $g$ such that $\gcd\left(L\left(g^\lambda \bmod n^2\right), n\right) = 1$ and $0\leq g \leq n^2$.
+We define the public key as $(g,n)$ and the private key as $(p,q)$.
 
@@
 \begin{align*}
-  D(E(m_1)g^k\bmod n^2)=(m_1+k)\bmod n & \text{ (used to add a constant)}\\
-  D(E(m_1)E(m_2)\bmod n^2)=(m_1+m_2)\bmod n & \text{ (used for binary addition)}\\
-  D(E(m_1)^k\bmod n^2)= km_1\bmod n & \text{ (used to multiply a plaintext constant)}
+  D(E(m_1)g^k\bmod n^2)=(m_1+k)\bmod n & \text{ (add a plaintext constant)}\\
+  D(E(m_1)E(m_2)\bmod n^2)=(m_1+m_2)\bmod n & \text{ (ciphertext addition)}\\
+  D(E(m_1)^k\bmod n^2)= km_1\bmod n & \text{ (multiply a plaintext constant)}
 \end{align*}
-
-%In order to implement some image operations covered in this study, we require the exponentiation %of ciphertexts to integer powers, i.e. we require a function $f$ so that
-%\begin{align*}
-%	D(f(E(m))) = m^k\bmod n
-%\end{align*}
-%for any plaintext $m \in \mathbb{Z}_n$, and positive integer $k$.
-
-%This is trivially feasible if $m^2 \bmod n$ and $E(m^2 \bmod n)$ are known, since one can use the following equation to raise $m$ to any positive integer power.
-%\begin{align*}
-%	D(E(m^k)^{m^2 \bmod n}\bmod n^2) &= m^2m^k\bmod n \\
-%	&= m^{k+2}\bmod n
-%\end{align*}
-
-%We now show that including $m^2 \bmod n$ and $E(m^2 \bmod n)$ in a transmitted message does not compromise the security of the Paillier cryptosystem.
-Clearly, $E(m^2 \bmod n)$ can be shared without compromising security, as it is an encrypted quantity.
-The quantity $m^2 \bmod n$ does not expose the value of $m$ as finding the value of $m \bmod n$ given $m^2 \bmod n$ is a problem equivalent in hardness to the factorization of large integers \cite{crandall_prime_2005}.
 
@@
 \begin{align*}
-    D(E(m_1)g^k)=(m_1+k)\bmod u & \text{ (used to add a constant)}\\
-    D(E(m_1)E(m_2))=(m_1+m_2)\bmod u & \text{ (used for binary addition)}\\
-    D(E(m_1)^k)= km_1\bmod u & \text{ (used to multiply a plaintext constant)}
+    D(E(m_1)g^k)=(m_1+k)\bmod u & \text{ (add a plaintext constant)}\\
+    D(E(m_1)E(m_2))=(m_1+m_2)\bmod u & \text{ (ciphertext addition)}\\
+    D(E(m_1)^k)= km_1\bmod u & \text{ (multiply a plaintext constant)}
 \end{align*}
@@
     &= (g^m)^k \cdot (h^r)^k \bmod{n}\\
-    &= g^{km} \cdot (h^kr) \bmod{n}\\
+    &= g^{km} \cdot (h^{kr}) \bmod{n}
   \end{align*}
-  Since $r$ is a random integer, $kr$ is also a random integer, Therefore, $g^{km} \cdot (h^kr) \bmod{n} = D(E(m_1)^k)$ is a valid encryption of the message $km$.
+  Since $r$ is a random integer, $kr$ is also a random integer, Therefore, $g^{km} \cdot (h^{kr}) \bmod{n} = D(E(m)^k)$ is a valid encryption of the message $km$.
 \end{proof}
 
-%\subsection{DGK Comparison Protocol}
-%The DGK system was primarily developed as part of a comparison protocol, a protocol which allows
-%It is known that $E(m)^{v_pv_q} \bmod n = 1$ if and only if $m=0$. This allows
+\subsection{Floating-Point Arithmetic using PHEs}
+\label{sec:fp_arithmetic}
+We have discussed the Paillier and DGK cryptosystems, which encrypt and allow similar operations on encrypted integers.
+We will now show how these PHEs may be extended to a system which allows for secure floating-point computation.
 
-%\subsection{The Benaloh cryptosystem}
-%The Benaloh cryptosystem, initially proposed by Josh Benaloh in \cite{benaloh_dense_1994}, allows for the encryption of integers in $\mathbb{Z}_r$ for some odd integer $r$.
-It relies on the hardness of the \textit{discrete logarithm problem}, and is a generalization of the classic Goldwasser--Micali cryptosystem~\cite{goldwasser_probabilistic_1984}.
-We present here a corrected version by Fousse, et al.
-\cite{fousse_benalohs_2010} which corrects an error in the key generation algorithm which prevents accurate decryption in some cases.
+In this section, we let $\oplus$ and $\otimes$ represent the homomorphic operations which correspond to the addition and multiplication of integers in a PHE, respectively.
 
-%\subsubsection{Benaloh Cryptosystem Description}
-%We choose an integer $r$ and two large primes $p$ and $q$ such that the following conditions hold:
-%\begin{itemize}
-%  \item $r$ divides $(p-1)$;
-%  \item $\mathrm{gcd}(r,(p-1)/r)=1$;
-%  \item $\mathrm{gcd}(r,q-1)=1$.
-%\end{itemize}
-%Next, let $n=pq$ and $\phi = (p-1)(q-1)$, and choose $y\in \mathbb{Z}_n^* = \{ x \in \mathbb{Z}_n | \mathrm{gcd}(x,n)=1 \}$ such that the following conditions hold:
-%\begin{itemize}
-%  \item $y^{\phi/r}\neq 1 \bmod n$;
-%  \item For all prime factors $s$ of $r$, $y^{\phi/s}\neq 1 \bmod n$.
-%\end{itemize}
-%We denote the public key to be $(y,r,n)$ and the private key to be $(p,q)$.
+\subsubsection{Extension to Floating-Point Numbers}
+\label{sec:fp_operations}
+We can use the following protocol described in~\cite{ziad_cryptoimg:_2016} in order to extend Paillier and DGK to floating-point numbers.
 
-%The encryption function to encrypt a plaintext $m \in \mathbb{Z}_r$ is defined as
-%\begin{align*}
-%  E(m) = y^m \cdot u^r \mod{n},
-%\end{align*}
-%where $u$ is a random integer in $\mathbb{Z}_n^*$.
+We represent a floating-point (FP) number as a pair of two integers $(m,e)$ representing the mantissa and exponent of the FP number with respect to a base $b$.
+The mantissa $m$ is encrypted, while the exponent $e$ is unencrypted.
+Let $a,b,c$ be FP numbers represented by the pairs $(m_a,e_a),(m_b,e_b),(m_c,e_c)$ respectively. We define the corresponding FP number operations as follows:
+\begin{description}
+  \item[Addition.]
+    To compute $E\left(c\right)=E\left(a+b\right)$ we compute
+	\begin{align*}
+		E\left(m_c\right) &= 
+		\begin{cases}
+			E\left(m_a\right) \oplus \left(b^{e_b-e_a} \otimes E\left(m_b\right)\right) & \text{if } e_a \leq e_b \\
+			E\left(m_b\right) \oplus \left(b^{e_a-e_b} \otimes E\left(m_a\right)\right) & \text{if } e_a > e_b
+		\end{cases}, \\
+		e_c &= 
+		\begin{cases}
+			e_a & \text{if } e_a \leq e_b \\
+			e_b & \text{if } e_a > e_b
+		\end{cases}.
+	\end{align*}
+  \item[Scalar multiplication.]
+    To compute $E\left(c\right) = E\left(ab\right)$, where $a$ and $E\left(b\right)$ are known (i.e., $m_a$ is not encrypted), we compute
+    \begin{align*}
+      E\left(m_c\right) &= m_a \otimes E\left(m_b\right),\\
+      e_c &= e_a + e_b.
+    \end{align*}
+\end{description}
 
-%The decryption function to decrypt a ciphertext $c \in \mathbb{Z}_{n}$ is defined as:
-%\begin{align*}
-%  D(c) = \log_x{c^{\phi/r}} \mod n
-%\end{align*}
-%where $x = y^{\phi/r}$ and $\log_x{y} = k$ such that $x^k = y \bmod n$.
+\subsubsection{Secure Division}
+We can use the following two-party scheme defined in~\cite{boukoros_lightweight_2017} to perform privacy-preserving division.
 
-%Decryption requires the computation of the discrete logarithm, which can be done using a linear search when $r$ is small.
-For large values of $r$, the baby-step giant-step algorithm can be used to perform decryption in $O(\sqrt{r})$ time \cite{benaloh_dense_1994}.
-
-%\subsubsection{Homomorphic Properties of the Benaloh Cryptosystem}
-%Similar to the Paillier cryptosystem, the Benaloh cryptosystem supports additive homomorphism as well as the multiplication of a plaintext scalar to an encrypted message.
-%For all $m_1,m_2 \in \mathbb{Z}_r$ and $k\in \mathbb{N}$, the following homomorphic properties hold.
-%\begin{description}
-%  \item[Additive homomorphism]
-%  \begin{align*}
-%    D(E(m_1)y^{m_2}\bmod n^2)=(m_1+m_2)\bmod n & \text{ (used to add a constant)}\\
-%    D(E(m_1)E(m_2)\bmod n^2)=(m_1+m_2)\bmod n & \text{ (used for binary addition)}
-%  \end{align*}
-%  \item[Multiplicative homomorphism]
-%  \begin{align*}
-%    D(E(m_1)^k\bmod n)= km_1\bmod n & \text{ (used to multiply a plaintext constant)}
-%  \end{align*}
-%\end{description}
-
-%As the multiplicative homomorphism was not presented in the original paper, we provide a short proof here.
-%\begin{proof}
-%  Let $m \in \mathbb{Z}_r$ and $k\in \mathbb{N}$.
-%  We consider $E(m)^k\bmod n = (y^m \cdot u^r \bmod{n})^k\bmod n$.
-%  \begin{align*}
-%    (y^m \cdot u^r \bmod{n})^k\bmod n
-%    &= (y^m \cdot u^r)^k \bmod{n}\\
-%    &= (y^m)^k \cdot (u^r)^k \bmod{n}\\
-%    &= y^{km} \cdot (u^k)^r \bmod{n}\\
-%    &= y^{km} \cdot (u^k \bmod{n})^r \bmod{n}
-%  \end{align*}
-%  Since $u$ is a random integer in $\mathbb{Z}_n^*$, $\mathrm{gcd}(u,n)=1$.
-%  This implies $\mathrm{gcd}(u^k,n)=1$, so $u^k \bmod n$ is a random integer in $\mathbb{Z}_n^*$.
-%  Therefore, $y^{km} \cdot (u^k \bmod{n})^r \bmod{n} = E(m)^k\bmod n$ is a valid encryption of the message $km$.
-%\end{proof}
-
-\subsection{General Exponentiation Protocol for Paillier and DGK}
-\label{ssec:exponentiationprotocol}
-In order to perform polynomial evaluation, we first present a protocol for privacy-preserving exponentiation to a positive integer power, adapted from the protocol to calculate Euclidean distances used in \cite{hutchison_privacy-preserving_2009}.
-
-The following protocols apply to both the Paillier and DGK cryptosystems, as they share similar homomorphisms.
-
-Suppose Alice encrypts an integer $x$ and sends it so Bob has $E(x)$, and wants to obtain $E(x^2)$ without exposing the value of $x$.
+Suppose Bob has $E\left(x\right)$ and $E\left(y\right)$ and wants to obtain $E\left(x/y\right)$ without exposing the value of either variable.
 \begin{itemize}
-	\item Bob first selects a random integer $r$ and computes $E(x+r)$. Bob can do this since $r$ is a plaintext constant.
-	\item Bob sends $E(x+r)$ to Alice, who decrypts the ciphertext to obtain $x+r$.
-	\item Alice squares $x+r$ and encrypts the result. She sends $E((x+r)^2)$ to Bob.
-	\item Bob computes $E(-2rx + r^2)$. He then computes $E((x+r)^2)E(-2rx + r^2) = E(x^2)$.
+	\item Bob first selects a random non-zero number $r$ and computes $E\left(rx\right)$ and $E\left(ry\right)$. Bob can do this since $r$ is a plaintext constant.
+	\item Bob sends $E\left(rx\right)$ and $E\left(ry\right)$ to Alice, who decrypts both values and computes $x/y$ in the plaintext domain.
+	\item Alice encrypts and sends $E\left(x/y\right)$ to Bob.
 \end{itemize}
 
-This can be extended to arbitrary integer powers.
-Suppose Alice encrypts and integer $x$, and Bob has $E(x), E(x^2), ..., E(x^{n-1})$ and wants to obtain $E(x^n)$.
+\subsubsection{Secure Exponentiation}
+\label{ssec:exponentiationprotocol}
+ We can use the following two-party scheme, adapted from the protocol to calculate Euclidean distances used in \cite{hutchison_privacy-preserving_2009}, in order to perform secure exponentiation.
+
+Suppose Alice encrypts an integer $x$ and sends it so Bob has $E\left(x\right)$, and wants to obtain $E\left(x^2\right)$ without exposing the value of $x$.
 \begin{itemize}
-	\item Bob first selects a random integer $r$ and computes $E(x+r)$. Bob can do this since $r$ is a plaintext constant.
-	\item Bob sends $E(x+r)$ to Alice, who decrypts the ciphertext to obtain $x+r$.
-	\item Alice sends $E((x+r)^n)$ to Bob.
+	\item Bob first selects a random integer $r$ and computes $E\left(x+r\right)$. Bob can do this since $r$ is a plaintext constant.
+	\item Bob sends $E\left(x+r\right)$ to Alice, who decrypts the ciphertext to obtain $x+r$.
+	\item Alice squares $x+r$ and encrypts the result. She sends $E\left(\left(x+r\right)^2\right)$ to Bob.
+	\item Bob computes $E\left(-2rx + r^2\right)$. He then computes
+	\begin{align*}
+		E\left(\left(x+r\right)^2\right)E\left(-2rx + r^2\right) = E\left(x^2\right).
+	\end{align*}
+\end{itemize}
+
+\subsubsection{Secure Multiplication}
+We can use the secure squaring protocol to arrive at a secure multiplication protocol, which then allows for the evaluation of polynomials.
+Suppose Alice encrypts integers $x$ and $y$, and Bob has $E\left(x\right), E\left(y\right)$ and wants to obtain $E\left(xy\right)$.
+\begin{itemize}
+	\item Bob acquires $E\left(x^2\right)$ and $E\left(y^2\right)$ using the secure squaring protocol.
+	\item Bob sends $E\left(x+y\right)$ to Alice, who decrypts the ciphertext to obtain $x+y$.
+	\item Alice sends $E\left(\left(x+y\right)^2\right)$ to Bob.
 	\item Bob then computes
 	\begin{align*}
-		E((x+r)^n) - E\left(\sum_{i=1}^{n-1}{\binom{n}{i}x^ir^{n-i}}\right),
+		\frac{1}{2}E\left(\left(x+y\right)^2\right)E\left(x^2\right)^{-1}E\left(y^2\right)^{-1} &= \frac{1}{2}E\left(\left(x+y\right)^2 - x^2 - y^2\right)\\
+		&= \frac{1}{2}E\left(2xy\right)\\
+		&= E\left(xy\right).
 	\end{align*}
-	which evaluates to $E(x^n)$ by the binomial theorem.
 \end{itemize}
+
+By applying these extensions to the Paillier and DGK cryptosystems, privacy-preserving floating-point arithmetic can be acheived.

### 2019-03-02 parts/02_relatedliterature_06fullyhomomorphic.tex
WIP cryptosystem RRL
working on cryptosystem RRL

@@
 
-We will also be testing fully homomorphic cryptosytems, which allow aribitrary computation on encrypted data.
-While generally being more flexible, fully homomorphic cryptosytems are known to be significantly slower than partially homomorphic cryptosytems; improving the efficiency of fully homomorphic cryptosytems is an active area of research \cite{sen_homomorphic_2013}.
+We will also be testing fully homomorphic cryptosytems (FHEs), which allow aribitrary computation on encrypted data.
 
-We will present two such cryptosystems, the Dasgupta--Pal cryptosystem, which we present in full to explain a correction we propose to it, and the BGV cryptosystem, which has open source implementations availble primarily used in homomorphic cryptography research.
+The first ever fully homomorphic cryptosystem was invented by Gentry \cite{gentry_fully_2009}, which operates over ideal lattices.
+Gentry's original construction showed that fully homomorphic cryptosystems are possible, although they are known to be significantly slower than partially homomorphic cryptosytems.
+Improving the efficiency of fully homomorphic cryptosytems is an active area of research \cite{sen_homomorphic_2013}.
 
-\subsection{The Dasgupta--Pal Cryptosystem}
-The Dasgupta--Pal cryptosystem is a fully homomorphic cryptosystem proposed in 2016 by Smaranika Dasgupta and S.
-K.
-Pal \cite{dasgupta_design_2016}, which encrypts integer plaintexts in $\mathbb{Z}_n$ to polynomial ciphertexts.
-We begin our presentation of the Dasgupta--Pal cryptosystem with the following definition.
+We will present two FHEs, the DGHV cryptosystem and the BGV cryptosystem, which both have open source implementations availble primarily used in homomorphic cryptography research.
+Since the mathematical details of these fully homomorphic cryptosystems are not relevant to describing their potential uses in secure image operations, we will instead briefly describe pertinent developements and implementations of each cryptosystem.
 
-Given a message $m \in \mathbb{Z}$, we denote
-\begin{align*}
-		m_p(x) = a_0 + a_1x + a_2x^2 + \cdots + a_kx^k
-\end{align*}
-where $a_ka_{k-1}\cdots a_2a_1_0$ is the binary representation of $m$.
+\subsection{DGHV Cryptosystem}
+In 2009, Dijk, Gentry, Halevi, and Vaikuntanathan created a fully homomorphic cryptosystem which operates primarily through elementary modular arithmetic, commonly called the DGHV cryptosystem \cite{cryptoeprint:2009:616}.
+This was further improved in 2011 \cite{cryptoeprint:2011:277, cryptoeprint:2011:440} to support shorter public keys, reducing the size of secure public keys from 12.5 GB to 2.5 MB.
 
-In the original scheme presented in \cite{dasgupta_design_2016}, the secret key $S_k$ is set to be a large prime.
-In Appendix \ref{chap:correction}, we present a case where the Dasgupta--Pal cryptosystem fails and prove that setting the secret key $S_k = 2p$, where $p$ is a large prime, corrects errors in the Dasgupta--Pal cryptosystem.
-We now decribe the correct cryptosystem.
-\subsubsection{Corrected Dasgupta--Pal Cryptosystem Description}
-Let $\ell$ denote the security parameter of the cryptosystem.
-Let $S_k = 2p$, where $p$ is a prime number with $\ell - 1$ bits.
-Choose a random even integer $z$ of length $\log_2{\ell}$.
+The DGHV cryptosystem encrypts single bits as integer ciphertexts.
+XOR and AND binary operations on encrypted bits are achieved by modular addition and modular multiplication on the integer ciphertexts.
+When operations are performed on ciphertexts, noise accumulates in the ciphertexts, which may prevent successful decryption.
 
-Let the secret key be $S_k$, and let the refresh key be $R_k = z \cdot S_k$. The secret key is kept private to the encrypting/decrypting parties, while the refresh key is made publicly available.
+A C++ implementation of the improved DGHV cryptosystem \cite{cryptoeprint:2011:440} using the GNU Multiple Precision Arithmetic Library may be found at https://github.com/deevashwer/Fully-Homomorphic-DGHV-and-Variants.
 
-The scheme defines the encryption algorithm for a message $m$ as follows:
-\begin{align*}
-	E(m) = y(x) + S_k\times d(x)
-\end{align*}
-where
-$y(x)$ is a polynomial of degree $n$ such that $m_p(x) \equiv y(x) \bmod S_k$ and $d(x)$ is a randomly chosen polynomial of degree $n$.
-This encrypts each coefficient of of $m_p(x)$ by adding some multiple of $S_k$ to it.
-Through this process, each bit of the message is encrypted separately.
-
-Furthermore, the decryption algorithm to recover $m_p(x)$ from a ciphertext polynomial $c(x)$ as
-\begin{align*}
-	m_p(x) = c(x) \bmod S_k \bmod 2.
-\end{align*}
-Thus $D(c(x))$ is defined as the integer recovered from the coefficients of the polynomial $c(x) \bmod S_k \bmod 2$.
-
-Dasgupta and Pal note that homomorphic operations on ciphertext introduce noise which may interfere with decryption, due to the potential increase in ciphertext values.
-To eliminate noise from a polynomial ciphertext, the following refresh function is used:
-\begin{align*}
-	R(c(x)) = c(x) \bmod R_k.
-\end{align*}
-
-\subsubsection{Homomorphic Properties of the Dasgupta--Pal Cryptosystem}
-It has been shown \cite{dasgupta_design_2016} that the following properties hold for all integer messages $m_1, m_2 \in \mathbb{Z}_n$ in the Dasgupta--Pal cryptosystem.
-These properties arise since each coefficient in a ciphertext polynomial is essentially an independently encrypted bit of the original message.
-\begin{description}
-	\item[XOR on ciphertexts]
-	A bitwise exclusive or (XOR) operation on integer messages can be achieved by adding the coefficients pairwise between two ciphertexts.
-	\begin{align*}
-		D(E(m_1)+E(m_2)) = m_1 \text{ XOR } m_2
-	\end{align*}
-	\item[AND on ciphertexts]
-	Similarly, pair-wise multiplication corresponds to bitwise AND of integer messages.
-	\begin{align*}
-		D(E(a) \otimes E(b)) = a \text{ AND } b = ab \bmod 2
-	\end{align*}
-	where $\otimes$ denotes pairwise multiplication,
-	\begin{align*}
-		\sum_{i=1}^n{a_ix^i} \otimes \sum_{i=1}^n{b_ix^i} = \sum_{i=1}^n{a_ib_ix^i}.
-	\end{align*}
-\end{description}
-
-Arbitrary computation on data can thus be achived using these bitwise operations.
-While the Dasgupta--Pal cryptosystem requires significant amounts of memory, as each bit of plaintext is encrypted into an integer, this approach provides a flexible method to perform relatively fast arbitrary computation on encrypted data.
-Encryption and decryption in the Dasgupta--Pal cryptosystem are accomplished using few arithmetic operations.
+For small security parameters, initial experiments using the DGHV cryptosystem have shown it takes 4.38 seconds for key generation, and
 
@@
 
-The details regarding the construction of the BGV cryptosystem are beyond the scope of this paper.
 For this study, we will be using \textit{HElib} \cite{garay_algorithms_2014}, an open-source library which implements the BGV cryptosystem with optimizations to improve efficiency.

### 2019-03-02 parts/03_methodology_02nonlinearintensitytransformations.tex
WIP cryptosystem RRL
working on cryptosystem RRL

@@
 In order to perform this transformation under a homomorphic cryptosystem, we must provide an approximation for $\log\left(1 + x\right)$ in terms of addition and multiplication operations (or their inverses).
-We have derived a closed form approximation in Appendix \ref{sec:logapproximation}.
+We have derived a closed form approximation in % Appendix \ref{sec:logapproximation}.
 \begin{align}
@@
 Similar to the logarithm transformation, we must provide an approximation for $x^\gamma$.
-We have derived an infinite series in Appendix \ref{sec:logapproximation}.
+We have derived an infinite series in Appendix %\ref{sec:logapproximation}.
 \begin{align*}

### 2019-03-03 parts/02_relatedliterature.tex
Applied most comments for chapter 2
Add citation for scikit-image
WIP cryptosystem RRL
working on cryptosystem RRL
Done with first pass of sections 2.1 to 2.3 of RRL
Note: linebreaking in URLs in section 2.3 have to be addressed

@@
 
-We will now provide an overview of the \textit{CryptoImg} project, which our study is primarily based on.
-Then, we define the specific image processing operations we are interested in implementing in this study.
-Then we will introduce concepts in cryptography and define the four homomorphic cryptosystems we will be testing in the study.
+We will now describe homomorphic cryptosystems in detail to provide a concrete description of their current capabilities and limitations.
+Then, we will describe our target applications in image processing and facial recognition.
 
+\input{parts/02_relatedliterature_04homomorphiccryptosystems}
+\input{parts/02_relatedliterature_05partiallyhomomorphic}
+\input{parts/02_relatedliterature_06fullyhomomorphic}
 \input{parts/02_relatedliterature_01cryptoimg}
@@
 \input{parts/02_relatedliterature_03facialrecognition}
-\input{parts/02_relatedliterature_04homomorphiccryptosystems}
-\input{parts/02_relatedliterature_05partiallyhomomorphic}
-\input{parts/02_relatedliterature_06fullyhomomorphic}
 %facial recognition - implementation

### 2019-03-03 parts/02_relatedliterature_05partiallyhomomorphic.tex
Done with first pass of sections 2.1 to 2.3 of RRL
Note: linebreaking in URLs in section 2.3 have to be addressed

@@
 
-In this section, we will present two classical partially homomorphic cryptosystems (PHEs) which we will be testing in the study: the Paillier cryptosystem and the DGK cryptosystem.
+In this section, we will present two classical partially homomorphic encryption (PHE) schemes which we will be testing in the study: the Paillier cryptosystem and the DGK cryptosystem.
 Both of these cryptosystems encrypt integer plaintexts and are additively homomorphic and allow for the multiplication of a plaintext scalar.
-We will then show how these PHEs may be adapted for secure floating-point computation.
+We will then show how these PHE schemes may be adapted for secure floating-point computation.
 
@@
 
-\subsection{Floating-Point Arithmetic using PHEs}
+\subsection{Floating-Point Arithmetic using PHE}
 \label{sec:fp_arithmetic}
 We have discussed the Paillier and DGK cryptosystems, which encrypt and allow similar operations on encrypted integers.
-We will now show how these PHEs may be extended to a system which allows for secure floating-point computation.
+We will now show how these PHE schemes may be extended to a system which allows for secure floating-point computation.
 
-In this section, we let $\oplus$ and $\otimes$ represent the homomorphic operations which correspond to the addition and multiplication of integers in a PHE, respectively.
+In this section, we let $\oplus$ and $\otimes$ represent the homomorphic operations which correspond to the addition and multiplication of integers in a PHE scheme, respectively.
 

### 2019-03-03 parts/02_relatedliterature_06fullyhomomorphic.tex
Done with first pass of sections 2.1 to 2.3 of RRL
Note: linebreaking in URLs in section 2.3 have to be addressed

@@
 
-We will also be testing fully homomorphic cryptosytems (FHEs), which allow aribitrary computation on encrypted data.
+We will also be testing fully homomorphic encryption (FHEs), which allow aribitrary computation on encrypted data.
 
 The first ever fully homomorphic cryptosystem was invented by Gentry \cite{gentry_fully_2009}, which operates over ideal lattices.
-Gentry's original construction showed that fully homomorphic cryptosystems are possible, although they are known to be significantly slower than partially homomorphic cryptosytems.
-Improving the efficiency of fully homomorphic cryptosytems is an active area of research \cite{sen_homomorphic_2013}.
+Gentry's original construction showed that FHE are possible, although they are known to be significantly slower than PHE.
+Improving the efficiency of FHis an active area of research \cite{sen_homomorphic_2013}.
 
 We will present two FHEs, the DGHV cryptosystem and the BGV cryptosystem, which both have open source implementations availble primarily used in homomorphic cryptography research.
-Since the mathematical details of these fully homomorphic cryptosystems are not relevant to describing their potential uses in secure image operations, we will instead briefly describe pertinent developements and implementations of each cryptosystem.
+Since the mathematical details of these fully homomorphic cryptosystems are not relevant to describing their potential uses in secure image operations, we will instead briefly describe important developments and implementations of each cryptosystem.
 
@@
 In 2009, Dijk, Gentry, Halevi, and Vaikuntanathan created a fully homomorphic cryptosystem which operates primarily through elementary modular arithmetic, commonly called the DGHV cryptosystem \cite{cryptoeprint:2009:616}.
-This was further improved in 2011 \cite{cryptoeprint:2011:277, cryptoeprint:2011:440} to support shorter public keys, reducing the size of secure public keys from 12.5 GB to 2.5 MB.
+This was further improved in 2011 by Coron, Naccache, and Tibouchi, \cite{cryptoeprint:2011:277, cryptoeprint:2011:440} to support shorter public keys, reducing the size of secure public keys from 12.5 GB to 2.5 MB.
 
@@
 When operations are performed on ciphertexts, noise accumulates in the ciphertexts, which may prevent successful decryption.
+To eliminate this noise, a \textit{refresh} or \textit{recrypt} procedure is used to reduce noise in a ciphertext.
+The refresh procedure for DGHV involves operating on a ciphertext with a \textit{recryption matrix}, which is more time-intensive than key generation, encryption, decryption, addition, and multiplication procedures.
 
-A C++ implementation of the improved DGHV cryptosystem \cite{cryptoeprint:2011:440} using the GNU Multiple Precision Arithmetic Library may be found at https://github.com/deevashwer/Fully-Homomorphic-DGHV-and-Variants.
+A Sage 4.7.2 implementation of the improved DGHV cryptosystem by Coron, et al.
+\cite{cryptoeprint:2011:440} may be found at \texttt{https://github.com/coron/fhe}.
+For small security parameters,  initial experiments using this implementation have shown it takes 0.06 seconds for key generation, 0.05 seconds for encryption, and 0.41 seconds for the recrypt procedure.
+For large security parameters, key generation takes 10 minutes, encryption takes 7 minutes and 15 seconds, and the recrypt procedure takes 11 minutes and 34 seconds \cite{cryptoeprint:2011:440}.
+Since the DGHV cryptosystem encrypts single plaintext bits, we can expect that operations on 32-bit floating point numbers are time-intensive, even under small security parameters.
 
-For small security parameters, initial experiments using the DGHV cryptosystem have shown it takes 4.38 seconds for key generation, and
+A more recent C++ implementation of the improved DGHV cryptosystem \cite{cryptoeprint:2011:440} using the GNU Multiple Precision Arithmetic Library may be found at \texttt{https://github.com/deevashwer/Fully-Homomorphic-DGHV-and-Variants}.
+This implementation is more accessible than the original Sage 4.7.2 implementation, since the original code has compatibility issues with current versions of SageMath.
 
@@
 
-For this study, we will be using \textit{HElib} \cite{garay_algorithms_2014}, an open-source library which implements the BGV cryptosystem with optimizations to improve efficiency.
+One prominent implementation is \textit{HElib} (\texttt{https://github.com/shaih/HElib}) \cite{garay_algorithms_2014}, an open-source library which implements the BGV cryptosystem C++ using the NTL mathematical library, with optimizations to improve efficiency.
 Evaluation of operations on 120 inputs in HELib was performed in around 4 minutes, with an average of 2 seconds to process a single input \cite{hutchison_fully_2010,cryptoeprint:2011:566}.

### 2019-03-03 parts/00_abstract.tex
Misc edits (Ch2,3,appendix,abstract, acknowledgements)

@@
     \noindent
-    This paper is a sample document that serves as a format and content guideline for undergraduate thesis submissions to the Department of Information Systems and Computer Science.
+    Homomorphic cryptography allows for encrypted data to be modified and operated on without requiring decryption, although current homomorphic cryptosystems are either limited in their permitted operations or are significantly more time-intensive than standard non-homomorphic cryptosystems.
+Regardless, homomorphic cryptography has been targeted for use in secure image processing and facial recognition, due to their ability to maintain data privacy.
+In this paper, we compared the viability of the Paillier, Damg{\aa}rd--Geisler--Kr{\o}igaard (DGK), and Brakerski--Gentry--Vaikuntanathan (BGV) cryptosystems for facial image processing applications, by implementing a software library equipped with these cryptosystems, and comparing their time efficiency and accuracy.
+Furthermore, as an extension to previous research, we attempt to support non-linear image processing operations by deriving and implementing applicable closed-form approximations.
+Preliminary results have shown that the Paillier and DGK cryptosystems are comparable in accuracy and may be used for image negation, but only the Paillier cryptosystem is consistent enough to produce reasonable to accurate results.
+
+    % This paper is a sample document that serves as a format and content guideline for undergraduate thesis submissions to the Department of Information Systems and Computer Science.
 In this section, the abstract, the group should be able to give the readers a clear and concise overview of their study.

### 2019-03-03 parts/02_relatedliterature_05partiallyhomomorphic.tex
Misc edits (Ch2,3,appendix,abstract, acknowledgements)

@@
 \subsubsection{Extension to Floating-Point Numbers}
-\label{sec:fp_operations}
+\label{sec:fp_number_extension}
 We can use the following protocol described in~\cite{ziad_cryptoimg:_2016} in order to extend Paillier and DGK to floating-point numbers.

### 2019-03-03 parts/02_relatedliterature_06fullyhomomorphic.tex
Misc edits (Ch2,3,appendix,abstract, acknowledgements)

@@
 
-\subsection{DGHV Cryptosystem}
+\subsection{The DGHV Cryptosystem}
 In 2009, Dijk, Gentry, Halevi, and Vaikuntanathan created a fully homomorphic cryptosystem which operates primarily through elementary modular arithmetic, commonly called the DGHV cryptosystem \cite{cryptoeprint:2009:616}.

### 2019-03-03 parts/08_appendices_b_numericalapproximations_updated.tex
Misc edits (Ch2,3,appendix,abstract, acknowledgements)

@@
-\subsection{Known Approximations for Transcendental Functions}
+\chapter{Logarithm Approximation}
 Many methods to compute transcendental functions implemented in computer hardware and software libraries rely on direct knowledge of the function arguments.
@@
 
-Khattri presents the following method to approximate the function $f(x)=\log\left(1+x\right)$.
+\section{Known Closed-Form Logarithm Approximations}
+Khattri ~\cite{khattri_new_2009} presents the following method to approximate the function $f(x)=\log\left(1+x\right)$.
 Let $x = 1/n$ and consider the integral
@@
 	\centering
-	\begin{tikzpicture}
-		\begin{axis}[
-			% height=6cm, width=9cm,
-			xmin=0, xmax=300,
-			ymin=0, ymax=5.5, ytick={0,...,6},
-			xlabel={$x$}, ylabel={$y$},
-			grid=major,
-			legend pos=south east,
-			legend cell align=left,
-		]
-		\addplot[very thick, ACMDarkBlue, domain=0:300, samples=100]{1/30*(137*x^5 + 2310*x^4 + 9870*x^3 + 15120*x^2 + 7560*x)/(x^5 + 30*x^4 + 210*x^3 + 560*x^2 + 630*x + 252)};
-		\addplot[densely dashed, domain=0:300, samples=100]{ln(x)};
-		\legend{5-point quadrature approximation, Actual value of $\log(1+x)$}
-		\end{axis}
-	\end{tikzpicture}%
+	% \begin{tikzpicture}
+	% 	\begin{axis}[
+	% 		% height=6cm, width=9cm,
+	% 		xmin=0, xmax=300,
+	% 		ymin=0, ymax=5.5, ytick={0,...,6},
+	% 		xlabel={$x$}, ylabel={$y$},
+	% 		grid=major,
+	% 		legend pos=south east,
+	% 		legend cell align=left,
+	% 	]
+	% 	\addplot[very thick, blue, domain=0:300, samples=100]{1/30*(137*x^5 + 2310*x^4 + 9870*x^3 + 15120*x^2 + 7560*x)/(x^5 + 30*x^4 + 210*x^3 + 560*x^2 + 630*x + 252)};
+	% 	\addplot[densely dashed, domain=0:300, samples=100]{ln(x)};
+	% 	\legend{5-point quadrature approximation, Actual value of $\log(1+x)$}
+	% 	\end{axis}
+	% \end{tikzpicture}%
 	\caption{Graph of $\log{\left(1+x\right)}$ and the approximation in Equation~\ref{eq:standard_logarithm_quadrature}}
@@
 
-\section{Logarithmic Function Approximation}
+\section{Scaled Approximation}
 \label{sec:logarithm_approximation}
-We now present our main contribution in this paper: a general method to improve the general accuracy of the logarithm approximation given by Khattri in~\cite{khattri_new_2009} for use in privacy-preserving calculation, provided that accuracy is only required for a specific range.
+This appendix a general method to improve the general accuracy of the logarithm approximation given by Khattri in~\cite{khattri_new_2009} for use in privacy-preserving calculation, provided that accuracy is only required for a specific range.
 
-For this approximation, we assume we only require accurate results in the input range $x \in [0, 255]$.
-This reflects some potential applications such as in logarithm intensity transformations in image processing~\cite{gonzalez_digital_2008}.
+For this approximation, we assume we only require accurate results in the input range $x \in [0, 255]$, to reflect use as part of the logarithm image transformation.
 
@@
 We note that the approximation in Equation~\ref{eq:optimal_log_approximation} requires the value of $\log{16}$.
-This can be computed in the plaintext domain and added to an encrypted value using the properties of the Paillier cryptosystem.
+This can be computed in the plaintext domain and added to an encrypted value using the properties of the Paillier or DGK cryptosystems, while an FHE scheme would have to encrypt the value of $\log{16}$.
 The remaining arithmetic operations in the approximation can be computed in the encrypted domain, using the protocols described in Section~\ref{sec:fp_arithmetic}.
@@
 	\centering
-    \begin{tikzpicture}
-		\begin{semilogyaxis}[
-			% height=6cm, width=9cm,
-			xmin=0, xmax=300,
-			ymin=1e-10, ymax=1.4,
-			xlabel={$x$}, ylabel={Absolute error},
-			grid=major,
-			legend pos=south east,
-			legend cell align=left,
-			tick scale binop=\times,
-		]
-		% \addplot[very thick, domain=0:300, samples=500]{abs(-1/30*(x^5*(30*ln(1/16) - 137) + 45*x^4*(270*ln(1/16) - 593) + 30*x^3*(27210*ln(1/16) - 20579) + 30*x^2*(488810*ln(1/16) + 216621) + 45*x*(1690670*ln(1/16) + 2694207) + 93677310*ln(1/16) + 257804775)/(x^5 + 405*x^4 + 27210*x^3 + 488810*x^2 + 2536005*x + 3122577) - ln(x + 1))};
-		% \addplot[very thick, domain=0:300, samples=300]{abs(1/30*(137*x^5 + 26685*x^4 + 617370*x^3 - 6498630*x^2 - 121239315*x - 257804775)/(x^5 + 405*x^4 + 27210*x^3 + 488810*x^2 + 2536005*x + 3122577) - ln(1/16) - ln(x + 1))};
-		\addplot[very thick, ACMDarkBlue] table[x=x, y=error] {plots/abs_err_scaledlog.txt};
-		\addplot[densely dashed, domain=0:300, samples=100]{abs(1/30*(137*x^5 + 2310*x^4 + 9870*x^3 + 15120*x^2 + 7560*x)/(x^5 + 30*x^4 + 210*x^3 + 560*x^2 + 630*x + 252) - ln(x + 1))};
-		\legend{Scaled quadrature ($\alpha = 1/16$), Original quadrature ($\alpha = 1$)}
-	\end{semilogyaxis}
-	\end{tikzpicture}%
+  %   \begin{tikzpicture}
+	% 	\begin{semilogyaxis}[
+	% 		% height=6cm, width=9cm,
+	% 		xmin=0, xmax=300,
+	% 		ymin=1e-10, ymax=1.4,
+	% 		xlabel={$x$}, ylabel={Absolute error},
+	% 		grid=major,
+	% 		legend pos=south east,
+	% 		legend cell align=left,
+	% 		tick scale binop=\times,
+	% 	]
+	% 	% \addplot[very thick, domain=0:300, samples=500]{abs(-1/30*(x^5*(30*ln(1/16) - 137) + 45*x^4*(270*ln(1/16) - 593) + 30*x^3*(27210*ln(1/16) - 20579) + 30*x^2*(488810*ln(1/16) + 216621) + 45*x*(1690670*ln(1/16) + 2694207) + 93677310*ln(1/16) + 257804775)/(x^5 + 405*x^4 + 27210*x^3 + 488810*x^2 + 2536005*x + 3122577) - ln(x + 1))};
+	% 	% \addplot[very thick, domain=0:300, samples=300]{abs(1/30*(137*x^5 + 26685*x^4 + 617370*x^3 - 6498630*x^2 - 121239315*x - 257804775)/(x^5 + 405*x^4 + 27210*x^3 + 488810*x^2 + 2536005*x + 3122577) - ln(1/16) - ln(x + 1))};
+	% 	\addplot[very thick, blue] table[x=x, y=error] {plots/abs_err_scaledlog.txt};
+	% 	\addplot[densely dashed, domain=0:300, samples=100]{abs(1/30*(137*x^5 + 2310*x^4 + 9870*x^3 + 15120*x^2 + 7560*x)/(x^5 + 30*x^4 + 210*x^3 + 560*x^2 + 630*x + 252) - ln(x + 1))};
+	% 	\legend{Scaled quadrature ($\alpha = 1/16$), Original quadrature ($\alpha = 1$)}
+	% \end{semilogyaxis}
+	% \end{tikzpicture}%
 	\caption{Comparison of the absolute error between the original approximation in Equation~\ref{eq:standard_logarithm_quadrature} and the scaled approximation in Equation~\ref{eq:optimal_log_approximation}}
@@
 	\centering
-    \begin{tikzpicture}
-		\begin{semilogyaxis}[
-			% height=6cm, width=9cm,
-			xmin=0, xmax=1,
-			ymin=5e-7, ymax=1.3,
-			xlabel={$\alpha$}, ylabel={Absolute error},
-			grid=major,
-			extra x ticks={1/16},
-			extra x tick labels={$\frac{1}{16}$},
-			legend pos=south east,
-			legend cell align=left,
-			tick scale binop=\times,
-		]
-		\addplot[thick, ACMDarkBlue, domain=0:1] table[x=alpha, y=x0] {plots/abs_err_sl_0_255.txt};
-		\addplot[thick, ACMOrange, domain=0:1] table[x=alpha, y=x255] {plots/abs_err_sl_0_255.txt};
-		\legend{$x=0$, $x=255$}
-		% \legend{$A\left(0,\alpha \right)$, $A\left(255,\alpha \right)$}
-	\end{semilogyaxis}
-	\end{tikzpicture}%
+  %   \begin{tikzpicture}
+	% 	\begin{semilogyaxis}[
+	% 		% height=6cm, width=9cm,
+	% 		xmin=0, xmax=1,
+	% 		ymin=5e-7, ymax=1.3,
+	% 		xlabel={$\alpha$}, ylabel={Absolute error},
+	% 		grid=major,
+	% 		extra x ticks={1/16},
+	% 		extra x tick labels={$\frac{1}{16}$},
+	% 		legend pos=south east,
+	% 		legend cell align=left,
+	% 		tick scale binop=\times,
+	% 	]
+	% 	\addplot[thick, ACMDarkBlue, domain=0:1] table[x=alpha, y=x0] {plots/abs_err_sl_0_255.txt};
+	% 	\addplot[thick, ACMOrange, domain=0:1] table[x=alpha, y=x255] {plots/abs_err_sl_0_255.txt};
+	% 	\legend{$x=0$, $x=255$}
+	% 	% \legend{$A\left(0,\alpha \right)$, $A\left(255,\alpha \right)$}
+	% \end{semilogyaxis}
+	% \end{tikzpicture}%
 	\caption{Graphs of $A\left(x,\alpha\right)$ at $x=0$ and $x=255$}
@@
 	\centering
-	\begin{tikzpicture}
-		\begin{semilogyaxis}[
-			xmin=0, xmax=300,
-			ymin=1e-15, ymax=0.035,
-			xlabel={$x$}, ylabel={Absolute error},
-			grid=major,
-			legend pos=south east,
-			legend cell align=left,
-			tick scale binop=\times,
-		]
-		% \addplot[very thick, domain=0:300, samples=300]{abs(1/30*(137*x^5 + 26685*x^4 + 617370*x^3 - 6498630*x^2 - 121239315*x - 257804775)/(x^5 + 405*x^4 + 27210*x^3 + 488810*x^2 + 2536005*x + 3122577) - ln(1/16) - ln(x + 1))};
-		\addplot[thick, ACMDarkBlue] table[x=x, y=error] {plots/abs_err_scaledlog.txt};
-	\end{semilogyaxis}
-	\end{tikzpicture}%
+	% \begin{tikzpicture}
+	% 	\begin{semilogyaxis}[
+	% 		xmin=0, xmax=300,
+	% 		ymin=1e-15, ymax=0.035,
+	% 		xlabel={$x$}, ylabel={Absolute error},
+	% 		grid=major,
+	% 		legend pos=south east,
+	% 		legend cell align=left,
+	% 		tick scale binop=\times,
+	% 	]
+	% 	% \addplot[very thick, domain=0:300, samples=300]{abs(1/30*(137*x^5 + 26685*x^4 + 617370*x^3 - 6498630*x^2 - 121239315*x - 257804775)/(x^5 + 405*x^4 + 27210*x^3 + 488810*x^2 + 2536005*x + 3122577) - ln(1/16) - ln(x + 1))};
+	% 	\addplot[thick, ACMDarkBlue] table[x=x, y=error] {plots/abs_err_scaledlog.txt};
+	% \end{semilogyaxis}
+	% \end{tikzpicture}%
 	\caption{Graph of $A\left(x,1/16\right)$, the absolute error of the approximation in Equation~\ref{eq:optimal_log_approximation} given a scaling factor of $\alpha=1/16$}
@@
 We have shown how we can adapt Khattri's approximation to allow for privacy-preserving logarithm computation over a larger interval.
-We note we only require the quadrature approach if series representations of the desired function are not suitable for privacy-preserving calculation using the floating-point arithmetic supported by the Paillier cryptosystem.
 
-As a concrete example, evaluating partial sums of the series representation for the exponential function,
+\section{Approximation for $x^\gamma$}
+To approximate $x^\gamma$ for any $\gamma \in \mathbb{R}$, we rewrite $x^\gamma$ as follows:
 \begin{align*}
-	e^x = \sum_{n=0}^{\infty}{\frac{x^n}{n!}},
+  x^\gamma = e^{\log{x^\gamma}} = e^{\gamma\log{x}}.
 \end{align*}
-is a valid approach for privacy-preserving computation, as this series converges for all $x$.
+This expression can then be approximated using the Maclaurin series expansion for $e^x$, which converges for all $x$.
+\begin{align*}
+  e^x &= \sum_{n=0}^{\infty}{\frac{x^n}{n!}}\\
+  \Rightarrow e^{\gamma\log{x}} &= \sum_{n=0}^{\infty}{\frac{(\gamma\log{x})^n}{n!}}
+\end{align*}
+As we already have an approximation for the natural logarithm, we can evaluate partial sums of the above infinite series to arrive at approximations for $x^\gamma$.

### 2019-03-04 parts/02_relatedliterature_04homomorphiccryptosystems.tex
Done with first pass of sections 2.1 to 2.3 of RRL
Note: linebreaking in URLs in section 2.3 have to be addressed
Cleaned up definition of cryptosystems in Ch2

@@
 
-Now that we've established the image processing operations we wish to implement, we now discuss the homomorphic cryptosystems we will be using to implement privacy-preserving image processing.
+A cryptosystem~\cite{bauer_cryptosystem_2005} consists of an encryption function $\mathcal{E}$ and a decryption function $\mathcal{D}$, which operate on three sets: the plaintext space $\mathcal{P}$, ciphertext space $\mathcal{C}$ and the key space $\mathcal{K}$ A \textit{plaintext}, an element of the \textit{plaintext space}, is text that can be commonly understood within a larger group.
+Given a \textit{key}, an element of the \textit{key space}, the encryption function maps a plaintext to some \textit{ciphertext}, an element of the ciphertext space which can only be understood by authorized parties.
+The decryption function similarly maps a ciphertext back to its corresponding plaintext, given an appropiate key.
+By sending data as ciphertext and only exposing the corresponding plaintexts to authorized parties who have access to the appropiate keys, secure data transmission can be achieved.
 
-A cryptosystem consists of an encryption function $\mathcal{E}$ and a decryption function $\mathcal{D}$, along with the plaintext space $\mathcal{P}$, ciphertext space $\mathcal{C}$ and the key space $\mathcal{K}$~\cite{bauer_cryptosystem_2005}.
-A \textit{plaintext} is text that can be commonly understood, while a \textit{ciphertext} results from encrypting the plaintext using an encryption key.
-The \textit{plaintext space} is the set of all possible plaintexts, the \textit{ciphertext space} is the set of all possible ciphertexts, while the \textit{keyspace} is the set of all possible keys.
-
-There are two kinds of cryptosystems, \textit{symmetric} and \textit{asymmetric}.
+Cryptosystems may be classified as either \textit{symmetric} or \textit{asymmetric}. 
 In symmetric-key cryptosystems, the same key is used for both encryption and decryption.
-As a consequence, symmetric-key cryptosystems must be implemented with a secure key exchange protocol, so that both the sender and receiver have access to the same key.
+As a consequence, symmetric-key cryptosystems must be implemented with a secure key exchange protocol, so that both the sender and receiver have access to the same key while keeping the key secret.
 Prominent examples of symmetric-key cryptosystems are the Data Encryption Standard (DES), and its replacement, the Advanced Encryption Standard (AES).
@@
 The encryption key (also called the \textit{public key}) is shared publicly, while the decryption key (also called the \textit{private key}) is kept secret.
-Since the public key and private keys are different, there is no need to agree upon secure key exchange protocols.
-Usually, the security of asymmetric-key cryptosystems relies on the intractability of certain computational problems, for example, the RSA cryptosystem depends on the difficulty of big integer factorization~\cite{rivest_method_1978}, while the ElGamal cryptosystem depends on the difficulty of the discrete logarithm problem~\cite{blakley_public_1985}.
+Since the public key and private keys differ, secure key exchange protocols are not required.
+The security of asymmetric-key cryptosystems rely on the intractability of certain computational problems, for example, the RSA cryptosystem depends on the difficulty of big integer factorization~\cite{rivest_method_1978}, while the ElGamal cryptosystem depends on the difficulty of the discrete logarithm problem~\cite{blakley_public_1985}.
 
 Homomorphic cryptosystems are a special type of cryptosystem in which operations can be securely performed on encrypted data.
-Suppose that for a public-key cryptosystem, $\mathcal{E}_k \left(p \right)$ is the encryption function using the public key $k \in \mathcal{K}$, and $\mathcal{D}_l \left(c \right)$ be the decryption function using the private key $l$.
-A cryptosystem is said to be homomorphic if its encryption function is homomorphic, that is, if it satisfies the relation
+Suppose that in a public-key cryptosystem, $\mathcal{E}_k \left(p \right)$ is the encryption function which uses a public key $k$, and $\mathcal{D}_l \left(c \right)$ be the decryption function which uses a private key $l$.
+The cryptosystem is said to be homomorphic if its encryption function is homomorphic, that is, if it satisfies the relation
 \begin{equation}
+    \label{eq:homomorphic_definition_encryption}
     \mathcal{E}_k \left(p_1 \boxplus p_2\right) = \mathcal{E}_k \left(p_1\right) \boxdot \mathcal{E}_k \left(p_2\right)
 \end{equation}
-where $p_1, p_2 \in \mathcal{P}$ are the plaintexts, and $\boxplus$ and $\boxdot$ are operations in $\mathcal{P}$ and $\mathcal{C}$ respectively~\cite{fontaine_survey_2007}.
-Furthermore, a homomorphic cryptosystem also satisfies~\cite{li_elliptic_2012}
+where $p_1, p_2 \in \mathcal{P}$ are plaintexts, and $\boxplus$ and $\boxdot$ are operations in $\mathcal{P}$ and $\mathcal{C}$ respectively~\cite{fontaine_survey_2007}.
+By applying the decryption function $\mathcal{D}_l$ to both sides of equation~\ref{eq:homomorphic_definition_encryption}, we can see that a homomorphic cryptosystem also satisfies~\cite{li_elliptic_2012}
 \begin{equation}
+    \label{eq:homomorphic_definition_decryption}
     p_1 \boxplus p_2 = \mathcal{D}_l \left( \mathcal{E}_k \left(p_1\right) \boxdot \mathcal{E}_k \left(p_2\right) \right).
 \end{equation}
-In other words, a homomorphic cryptosystem preserves the operations that can be done with the plaintext without requiring an intermediary step of decrypting the ciphertext beforehand.
-It is important to note that the operations $\boxplus$ and $\boxdot$ need not be the same.
+In other words, a homomorphic cryptosystem allows operations to be performed on recovered plaintexts by performing corresponding operations on ciphertexts.
+Using a homomorphic cryptosystem, secure computation can be achieved by encrypting plaintexts and then operating on the ciphertexts.
+We note that the operations $\boxplus$ and $\boxdot$ need not be the same.
 A simple operation in the plaintext space may require a computationally intensive operation in the ciphertext space.
 
-Homomorphic cryptosystems can be classified according to the plaintext and ciphertext operations, $\boxplus$ and $\boxdot$.
-If the plaintext operation $\boxplus$ is addition, the cryptosystem is said to be \textit{additively homomorphic}, and the cryptosystem is said to be \textit{multiplicatively homomorphic} if the plaintext operation $\boxplus$ is multiplication.
+Homomorphic cryptosystems can be classified according to the supported plaintext operation(s) $\boxplus$ which can be securely computed.
+The cryptosystem is said to be \textit{additively homomorphic} if the plaintext operation $\boxplus$ is addition, and the cryptosystem is said to be \textit{multiplicatively homomorphic} if the plaintext operation $\boxplus$ is multiplication.
+Homomorphic cryptosystems which only allow for a limited set of operations to be computed securely are called \textit{partially homomorphic} while those which allow for arbitrary operations to be computed securely are called \textit{fully homomorphic}.
+Numerous partially homomorphic and fully homomorphic cryptosystems have been developed in the literature.
+This study will compare several of them, which we will now introduce in detail.
 

### 2019-03-04 parts/01_introduction_01contextofstudy.tex
Applied comments for chapter 1
Updated and cleaned up ch1

@@
 To meet these needs, various cryptosystems have been developed.
-A cryptosystem is a system which operates on plaintexts, ciphertexts and keys using an encryption algorithm, which maps a plaintext to a ciphertext, together with a decryption algorithm, which maps a ciphertext to a plaintext, given an appropriate key~\cite{bauer_cryptosystem_2005}.
+Cryptosystems allow plaintexts, data which is commonly understood, to be encrypted as ciphertext, data which can only be understood by authorized parties using a key~\cite{bauer_cryptosystem_2005}.
 The encryption and decryption algorithms are chosen such that the plaintext cannot easily be recovered from the ciphertext without knowledge of the key.
 This allows data to be securely transmitted over an insecure channel.
-Much research has been done on the development and application of various cryptosystems.
 
 One particular application of cryptography is image encryption.
-While cryptosystems used to encrypt digital data in general, such as the Advanced Encryption Standard (AES) or elliptic curve cryptography, can also be used to encrypt images~\cite{jain_image_2016, singh_image_2015} other algorithms created specifically for image encryption have also been developed~\cite{murugan_survey_2018}.
+While cryptosystems used to encrypt general digital data, such as the Advanced Encryption Standard (AES) or elliptic curve cryptography, can also be used to encrypt images~\cite{jain_image_2016, singh_image_2015} other algorithms created specifically for image encryption have also been developed~\cite{murugan_survey_2018}.
 
- In a homomorphic cryptosystem, operations such as addition and multiplication can be performed on encrypted data.
-These operations are then preserved when the data is decrypted.
-In this manner, data is manipulated without compromising data privacy, as the encrypted data being operated on remains secure~\cite{fontaine_survey_2007, sen_homomorphic_2013}.
-While numerous homomorphic cryptosystems exist for use with digital data in general, in the area of homomorphic image encryption, there is additional interest in being able to perform image manipulation operations on the encrypted data such as image adjustment, filtering, and morphological/feature extraction operations~\cite{ziad_cryptoimg:_2016, gonzalez_digital_2008}.
+ Using a homomorphic cryptosystem, operations can be performed on encrypted data while keeping both the operands and resulting value secure.
+The result of the operations can be recovered when the data is decrypted..
+In this manner, data is manipulated without compromising data privacy~\cite{fontaine_survey_2007, sen_homomorphic_2013}.
+While numerous homomorphic cryptosystems exist for use with general digital data, in the area of homomorphic image encryption, there is additional interest in being able to perform image manipulation operations on the encrypted data such as image adjustment, filtering, and morphological/feature extraction operations~\cite{ziad_cryptoimg:_2016, gonzalez_digital_2008}.
 More advanced operations have also been implemented using homomorphic cryptosystems, such as facial recognition \cite{hutchison_privacy-preserving_2009} and neural networks \cite{hesamifard_cryptodl:_2017}.
+This study in particular focuses on facial recognition.

### 2019-03-05 parts/03_methodology_02nonlinearintensitytransformations.tex
Ch 3 updated

--- 2018-10-08 parts/03_methodology_02nonlinearintensitytransformations.tex
@@
 In order to perform this transformation under a homomorphic cryptosystem, we must provide an approximation for $\log\left(1 + x\right)$ in terms of addition and multiplication operations (or their inverses).
-We have derived a closed form approximation in Appendix \ref{sec:logapproximation}.
-\begin{align}
-	\label{eq:scaledquadraturech3}
+We have derived a closed form approximation in Appendix \ref{sec:logarithm_approximation}.
+\begin{align}\label{eq:optimal_log_approximation_ch3}
 	\begin{split}
-    &\log(1+x) \\
-    &=\frac{137x^5 + 33185x^4 + 931370x^3 - 13403630x^2 - 289469315x - 713567363}
-    {30(x^5 + 505x^4 + 42010x^3 + 923010x^2 + 5722005x + 8040501)} + \log{20}
+		&\log\left(1+x\right) \\
+		&\approx \frac{137x^5 + 26685x^4 + 617370x^3 - 6498630x^2 - 121239315x - 257804775}
+		{30(x^5 + 405x^4 + 27210x^3 + 488810x^2 + 2536005x + 3122577)}\\
+		&+ \log{16}.
 	\end{split}
@@
 Similar to the logarithm transformation, we must provide an approximation for $x^\gamma$.
-We have derived an infinite series in Appendix \ref{sec:logapproximation}.
+We have derived an infinite series in Appendix \ref{chap:logarithm_approximation}.
 \begin{align*}

### 2019-03-05 parts/08_appendices_b_numericalapproximations_updated.tex
Ch 3 updated

@@
-\chapter{Logarithm Approximation}
+\chapter{LOGARITHM APPROXIMATION}
+\label{chap:logarithm_approximation}
 Many methods to compute transcendental functions implemented in computer hardware and software libraries rely on direct knowledge of the function arguments.

### 2019-03-05 parts/03_methodology_02nonlinearintensitytransformations.tex
update broken ref

@@
 Similar to the logarithm transformation, we must provide an approximation for $x^\gamma$.
-We have derived an infinite series in Appendix \ref{chap:logarithm_approximation}.
+We have derived an infinite series in Appendix \ref{sec:logarithm_approximation}.
 \begin{align*}
@@
 \end{align*}
-Partial sums of the above infinite series can be calculated based on the closed form approximation for the logarithm in Equation \ref{eq:scaledquadraturech3}.
+Partial sums of the above infinite series can be calculated based on the closed form approximation for the logarithm in Equation \ref{eq:optimal_log_approximation_ch3}.

### 2019-03-05 parts/00_abstract.tex
Added DGHV to abstract

@@
 Regardless, homomorphic cryptography has been targeted for use in secure image processing and facial recognition, due to their ability to maintain data privacy.
-In this paper, we compared the viability of the Paillier, Damg{\aa}rd--Geisler--Kr{\o}igaard (DGK), and Brakerski--Gentry--Vaikuntanathan (BGV) cryptosystems for facial image processing applications, by implementing a software library equipped with these cryptosystems, and comparing their time efficiency and accuracy.
+In this paper, we compared the viability of the Paillier, Damg{\aa}rd--Geisler--Kr{\o}igaard (DGK), Dijk-- Gentry--Halevi--Vaikuntanathan (DGHV), and Brakerski--Gentry--Vaikuntanathan (BGV) cryptosystems for facial image processing applications, by implementing a software library equipped with these cryptosystems, and comparing their time efficiency and accuracy.
 Furthermore, as an extension to previous research, we attempt to support non-linear image processing operations by deriving and implementing applicable closed-form approximations.

### 2019-03-06 parts/02_relatedliterature_06fullyhomomorphic.tex
Add chapter 4 contents

--- 2019-03-02 parts/02_relatedliterature_06fullyhomomorphic.tex
@@
 
-We will also be testing fully homomorphic cryptosytems (FHEs), which allow aribitrary computation on encrypted data.
+We will also be testing fully homomorphic cryptosytems, which allow aribitrary computation on encrypted data.
+While generally being more flexible, fully homomorphic cryptosytems are known to be significantly slower than partially homomorphic cryptosytems; improving the efficiency of fully homomorphic cryptosytems is an active area of research \cite{sen_homomorphic_2013}.
 
-The first ever fully homomorphic cryptosystem was invented by Gentry \cite{gentry_fully_2009}, which operates over ideal lattices.
-Gentry's original construction showed that fully homomorphic cryptosystems are possible, although they are known to be significantly slower than partially homomorphic cryptosytems.
-Improving the efficiency of fully homomorphic cryptosytems is an active area of research \cite{sen_homomorphic_2013}.
+We will present two such cryptosystems, the Dasgupta--Pal cryptosystem, which we present in full to explain a correction we propose to it, and the BGV cryptosystem, which has open source implementations availble primarily used in homomorphic cryptography research.
 
-We will present two FHEs, the DGHV cryptosystem and the BGV cryptosystem, which both have open source implementations availble primarily used in homomorphic cryptography research.
-Since the mathematical details of these fully homomorphic cryptosystems are not relevant to describing their potential uses in secure image operations, we will instead briefly describe pertinent developements and implementations of each cryptosystem.
+\subsection{The Dasgupta--Pal Cryptosystem}
+The Dasgupta--Pal cryptosystem is a fully homomorphic cryptosystem proposed in 2016 by Smaranika Dasgupta and S.
+K.
+Pal \cite{dasgupta_design_2016}, which encrypts integer plaintexts in $\mathbb{Z}_n$ to polynomial ciphertexts.
+We begin our presentation of the Dasgupta--Pal cryptosystem with the following definition.
 
-\subsection{DGHV Cryptosystem}
-In 2009, Dijk, Gentry, Halevi, and Vaikuntanathan created a fully homomorphic cryptosystem which operates primarily through elementary modular arithmetic, commonly called the DGHV cryptosystem \cite{cryptoeprint:2009:616}.
-This was further improved in 2011 \cite{cryptoeprint:2011:277, cryptoeprint:2011:440} to support shorter public keys, reducing the size of secure public keys from 12.5 GB to 2.5 MB.
+Given a message $m \in \mathbb{Z}$, we denote
+\begin{align*}
+		m_p(x) = a_0 + a_1x + a_2x^2 + \cdots + a_kx^k
+\end{align*}
+where $a_k a_{k-1}\cdots a_2a_1_0$ is the binary representation of $m$.
 
-The DGHV cryptosystem encrypts single bits as integer ciphertexts.
-XOR and AND binary operations on encrypted bits are achieved by modular addition and modular multiplication on the integer ciphertexts.
-When operations are performed on ciphertexts, noise accumulates in the ciphertexts, which may prevent successful decryption.
+In the original scheme presented in \cite{dasgupta_design_2016}, the secret key $S_k$ is set to be a large prime.
+In Appendix \ref{chap:correction}, we present a case where the Dasgupta--Pal cryptosystem fails and prove that setting the secret key $S_k = 2p$, where $p$ is a large prime, corrects errors in the Dasgupta--Pal cryptosystem.
+We now decribe the correct cryptosystem.
+\subsubsection{Corrected Dasgupta--Pal Cryptosystem Description}
+Let $\ell$ denote the security parameter of the cryptosystem.
+Let $S_k = 2p$, where $p$ is a prime number with $\ell - 1$ bits.
+Choose a random even integer $z$ of length $\log_2{\ell}$.
 
-A C++ implementation of the improved DGHV cryptosystem \cite{cryptoeprint:2011:440} using the GNU Multiple Precision Arithmetic Library may be found at https://github.com/deevashwer/Fully-Homomorphic-DGHV-and-Variants.
+Let the secret key be $S_k$, and let the refresh key be $R_k = z \cdot S_k$. The secret key is kept private to the encrypting/decrypting parties, while the refresh key is made publicly available.
 
-For small security parameters, initial experiments using the DGHV cryptosystem have shown it takes 4.38 seconds for key generation, and
+The scheme defines the encryption algorithm for a message $m$ as follows:
+\begin{align*}
+	E(m) = y(x) + S_k\times d(x)
+\end{align*}
+where
+$y(x)$ is a polynomial of degree $n$ such that $m_p(x) \equiv y(x) \bmod S_k$ and $d(x)$ is a randomly chosen polynomial of degree $n$.
+This encrypts each coefficient of of $m_p(x)$ by adding some multiple of $S_k$ to it.
+Through this process, each bit of the message is encrypted separately.
+
+Furthermore, the decryption algorithm to recover $m_p(x)$ from a ciphertext polynomial $c(x)$ as
+\begin{align*}
+	m_p(x) = c(x) \bmod S_k \bmod 2.
+\end{align*}
+Thus $D(c(x))$ is defined as the integer recovered from the coefficients of the polynomial $c(x) \bmod S_k \bmod 2$.
+
+Dasgupta and Pal note that homomorphic operations on ciphertext introduce noise which may interfere with decryption, due to the potential increase in ciphertext values.
+To eliminate noise from a polynomial ciphertext, the following refresh function is used:
+\begin{align*}
+	R(c(x)) = c(x) \bmod R_k.
+\end{align*}
+
+\subsubsection{Homomorphic Properties of the Dasgupta--Pal Cryptosystem}
+It has been shown \cite{dasgupta_design_2016} that the following properties hold for all integer messages $m_1, m_2 \in \mathbb{Z}_n$ in the Dasgupta--Pal cryptosystem.
+These properties arise since each coefficient in a ciphertext polynomial is essentially an independently encrypted bit of the original message.
+\begin{description}
+	\item[XOR on ciphertexts]
+	A bitwise exclusive or (XOR) operation on integer messages can be achieved by adding the coefficients pairwise between two ciphertexts.
+	\begin{align*}
+		D(E(m_1)+E(m_2)) = m_1 \text{ XOR } m_2
+	\end{align*}
+	\item[AND on ciphertexts]
+	Similarly, pair-wise multiplication corresponds to bitwise AND of integer messages.
+	\begin{align*}
+		D(E(a) \otimes E(b)) = a \text{ AND } b = ab \bmod 2
+	\end{align*}
+	where $\otimes$ denotes pairwise multiplication,
+	\begin{align*}
+		\sum_{i=1}^n{a_ix^i} \otimes \sum_{i=1}^n{b_ix^i} = \sum_{i=1}^n{a_ib_ix^i}.
+	\end{align*}
+\end{description}
+
+Arbitrary computation on data can thus be achived using these bitwise operations.
+While the Dasgupta--Pal cryptosystem requires significant amounts of memory, as each bit of plaintext is encrypted into an integer, this approach provides a flexible method to perform relatively fast arbitrary computation on encrypted data.
+Encryption and decryption in the Dasgupta--Pal cryptosystem are accomplished using few arithmetic operations.
 
@@
 
+The details regarding the construction of the BGV cryptosystem are beyond the scope of this paper.
 For this study, we will be using \textit{HElib} \cite{garay_algorithms_2014}, an open-source library which implements the BGV cryptosystem with optimizations to improve efficiency.

### 2019-03-06 parts/04_results.tex
Add chapter 4 contents

--- 2018-06-20 parts/04_results.tex
@@
 \chapter{RESULTS AND DISCUSSION}
-After implementing your methodology and gathering all pertinent data, in this section, you will now present the gathered data to your reader.
-By the end of this section, your reader should have an idea of what exactlty happened during the experiment.
-A good way to organize your results is to group them is to present them in the same order which your methodology was presented.
-For instance, if your methodology included the analysis of user logs, the implementation of an application, and the testing of this application, your results should flow in the same way.
-In addition, more often than not, you will be presenting a large volume of data, so utilize figures and tables whenever appropriate.
-Table 5.1 below presents one way of how to go about presenting your data.
-Note the table caption and headers, as mentioned in our framework.
+The results shown in this section are gathered from the tests for intensity transformations under Paillier and DGK cryptosystems.
+During testing, initial results obtained from BGV, particularly with image operations involving floating-point numbers like the logarithmic transformation, were unstable (i.e.
+the results vary drastically every time the same tests were done).
+This is because the Pyfhel library being used for the BGV cryptosystem is still in alpha development stage \cite{pyfhel_2018}.
+
+% One of the authors has already informed the maintainers of the library about a bug involving exponentiation of two real numbers.
+
+\section{Intensity Transformations}
+
+% \begin{table*}
+% 	\centering
+% 	\caption{Comparison of intensity transformations under Paillier}
+% 	\label{tbl:it-pal}
+% 	\begin{tabular}{m{1cm}*{7}{>{\centering\arraybackslash}m{1.75cm}}}
+% 		\hline
+% 		\multirow{2}{*}{Image} & \multirow{2}{*}{Original} & \multicolumn{2}{c}{Image negation} & \multicolumn{2}{c}{Logarithm transformation} & \multicolumn{2}{c}{Power-law transformation} \\
+% 							   &                           & PDT           & CDT          & PDT            & CDT           & PDT               & CDT           \\
+% 		\hline
+% 		\xintForpair #1#2 in {(anpage,a), (bplyce,b), (drbost,c), (ksunth,d), (martin,e), (pmives,f), (rnpwil,g), (sbains,h), (swewin,i), (yfhsie,j)} \do {%
+% 		(#2) & \includegraphics[width=1.75cm]{out_faces/paillier_negate_#1_original.png} & \includegraphics[width=1.75cm]{out_faces/paillier_negate_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/paillier_negate_#1_decrypted.png} & \includegraphics[width=1.75cm]{out_faces/paillier_logtransform_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/paillier_logtransform_#1_decrypted.png} & \includegraphics[width=1.75cm]{out_faces/paillier_pwrtransform_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/paillier_pwrtransform_#1_decrypted.png} \\ }%
+% 		\hline
+% 	\end{tabular}
+% \end{table*}
+%
+% \begin{table*}
+% 	\centering
+% 	\caption{Comparison of intensity transformations under DGK}
+% 	\label{tbl:it-dgk}
+% 	\begin{tabular}{m{1cm}*{7}{>{\centering\arraybackslash}m{1.75cm}}}
+% 		\hline
+% 		\multirow{2}{*}{Image} & \multirow{2}{*}{Original} & \multicolumn{2}{c}{Image negation} & \multicolumn{2}{c}{Logarithm transformation} & \multicolumn{2}{c}{Power-law transformation} \\
+% 							   &                           & PDT           & CDT          & PDT            & CDT           & PDT               & CDT           \\
+% 		\hline
+% 		\xintForpair #1#2 in {(anpage,a), (bplyce,b), (drbost,c), (ksunth,d), (martin,e), (pmives,f), (rnpwil,g), (sbains,h), (swewin,i), (yfhsie,j)} \do {%
+% 		(#2) & \includegraphics[width=1.75cm]{out_faces/dgk_negate_#1_original.png} & \includegraphics[width=1.75cm]{out_faces/dgk_negate_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/dgk_negate_#1_decrypted.png} & \includegraphics[width=1.75cm]{out_faces/dgk_logtransform_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/dgk_logtransform_#1_decrypted.png} & \includegraphics[width=1.75cm]{out_faces/dgk_pwrtransform_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/dgk_pwrtransform_#1_decrypted.png} \\ }%
+% 		\hline
+% 	\end{tabular}
+% \end{table*}
+
+Table~\ref{tbl:it-pal} shows the images obtained from the intensity transformation tests under the Paillier cryptosystem, while Table~\ref{tbl:it-dgk} shows the resulting images from the same tests under the DGK cryptosystem.
+Shown for each image is the original unecrypted image, and for each intensity transformation the \textit{plaintext domain transformation} (PDT) is given which is the resulting image after applying the transformation to the unencrypted image and the \textit{ciphertext domain transformation} (CDT) is the decrypted image of the processed encrypted image.
+
+The following tables show the resulting metric scores for mean squared error (MSE), peak signal to noise ratio (PSNR), and structural similarity index (SSIM), as well as time taken (in seconds) for encrypting the input image ($t_\text{enc}$), applying an operation to the encrypted image ($t_\text{apply}$), and decrypting the resulting encrypted image ($t_\text{dec}$), for each image in the test set.
+Tables~\ref{tbl:neg-pal} and~\ref{tbl:neg-dgk} show the results obtained from applying image negation, Tables~\ref{tbl:log-pal} and~\ref{tbl:log-dgk} from applying logarithm transformation, and Tables~\ref{tbl:pwr-pal} and~\ref{tbl:pwr-dgk} from applying power-law transformation.
+
+\subsection{Image Negation}
+Both the Paillier and DGK cryptosystems were able to perform image negation under the encrypted domain without introducing noise in the resulting image.
+In other words, the resulting image from doing image negation on an image on the clear and doing image negation under the encrypted domain are identical, as evidenced by the mean squared errors being exactly equal to zero, the PSNR being infinite, and the SSIM being exactly equal to one.
+While the time taken to apply image negation is comparable to that of DGK, the Paillier cryptosystem performed better in terms of encryption and decryption time.
 
@@
 	\centering
-\caption {Preliminary Test Result, organized by Problem Type}
-\label{tab:acc_lit} 
-\begin{tabular}{ c  c  c  c  c  c  c  c  c  c  c }
+	\caption{Image negation under Paillier}
+	\label{tbl:neg-pal}
+    \begin{tabular}{lcccccc}
         \hline
-Problem	&Average 	&Standard 	&Average 		&Standard		&Dominant\\
-Type  &Steps   &Deviation   &Duration   &Deviation   &Affective\\
-  &   &(Steps)   &(s)   &(Duration)   &State\\ \hline
-
-A1  &14   &2.30   &23.04   &3.50   &CONF\\
-A2  &2   &5.36   &32.10   &2.01   &FLOW\\
-A3  &31   &1.01   &28.55   &4.03   &FLOW\\
-B1  &24   &4.40   &45.30   &3.30   &BOR\\
-B2  &33   &2.12   &20.56   &2.21   &FLOW\\
-B3  &36   &1.05   &LOSE   &1.15   &CONF\\
-C1  &22   &1.33   &LOSE   &1.40   &FLOW\\
-C2  &23   &3.03   &LOSE   &1.30   &FLOW\\
-D1  &30   &1.79   &LOSE   &1.45   &FLOW\\
-D2  &15   &1.30   &LOSE   &1.05   &FLOW\\ \hline
+        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \hline
+        (a) & 0.000 & $\infty$ & 1.00000 & 0.128 & 0.013 & 0.041 \\
+		(b) & 0.000 & $\infty$ & 1.00000 & 0.084 & 0.013 & 0.024 \\
+		(c) & 0.000 & $\infty$ & 1.00000 & 0.099 & 0.012 & 0.031 \\
+		(d) & 0.000 & $\infty$ & 1.00000 & 0.109 & 0.012 & 0.048 \\
+		(e) & 0.000 & $\infty$ & 1.00000 & 0.117 & 0.015 & 0.043 \\
+		(f) & 0.000 & $\infty$ & 1.00000 & 0.111 & 0.012 & 0.025 \\
+		(g) & 0.000 & $\infty$ & 1.00000 & 0.099 & 0.012 & 0.023 \\
+		(h) & 0.000 & $\infty$ & 1.00000 & 0.084 & 0.012 & 0.024 \\
+		(i) & 0.000 & $\infty$ & 1.00000 & 0.089 & 0.012 & 0.023 \\
+		(j) & 0.000 & $\infty$ & 1.00000 & 0.081 & 0.012 & 0.029 \\
+		\hline
     \end{tabular}
@@
 
-There are, however, some additional notes that must be clarified.
-First, given that you will be gathering a huge volume of data, you must be able to classify which of these were critical in determining the outcome of your study, and which ones need not be presented.
-The critical data must be presented in this section, while the minor ones may be placed in the Appendices of your paper, which will be described later in this template.
+\begin{table}[t]
+	\centering
+	\caption{Image negation under DGK}
+	\label{tbl:neg-dgk}
+    \begin{tabular}{lcccccc}
+        \hline
+        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \hline
+		(a) & 0.000 & $\infty$ & 1.00000 & 0.509 & 0.011 & 0.450 \\
+		(b) & 0.000 & $\infty$ & 1.00000 & 0.512 & 0.009 & 0.462 \\
+		(c) & 0.000 & $\infty$ & 1.00000 & 0.732 & 0.018 & 0.519 \\
+		(d) & 0.000 & $\infty$ & 1.00000 & 0.593 & 0.017 & 0.677 \\
+		(e) & 0.000 & $\infty$ & 1.00000 & 0.607 & 0.010 & 0.454 \\
+		(f) & 0.000 & $\infty$ & 1.00000 & 0.550 & 0.010 & 0.507 \\
+		(g) & 0.000 & $\infty$ & 1.00000 & 0.532 & 0.010 & 0.471 \\
+		(h) & 0.000 & $\infty$ & 1.00000 & 0.538 & 0.010 & 0.513 \\
+		(i) & 0.000 & $\infty$ & 1.00000 & 0.606 & 0.010 & 0.519 \\
+		(j) & 0.000 & $\infty$ & 1.00000 & 0.608 & 0.012 & 0.496 \\
+		\hline
+        \end{tabular}
+\end{table}
 
-Another clarification to be noted is that the presentation of results in this section must be objective, or `as-is'.
-This means that you must describe your results in a way understandable to your reader without putting any form of interpretation.
-In effect, this section’s intent is to provide answers to ``what happened'' questions, not ``what does it mean'' questions.
-The interpretation of results is the subject of a later section.
+\subsection{Logarithm Transformation}
+Unlike image negation, logarithm transformation involves more operations, so the increase in processing times for both cryptosystems are expected.
+Applying the logarithm transformation under Paillier took about 2 seconds per image, while it took about 25 seconds each under DGK.
+Applying the logarithm transformation under Paillier results in faster and more accurate output images (with $\text{MSE} \le 30$ and $\text{SSIM} \approx 0.99$) than under DGK (with $\text{MSE} \le 300$ and $0.61 \le \text{SSIM} \le 0.87$).
 
-Finally, because this is a presentation of what happened in the past, all tenses used in this section must be in the past form, be it active or passive.
-This will also be true for the preceeding sections after the study’s implementation, especially when stating the methodology.
+\begin{table}[t]
+	\centering
+	\caption{Logarithm transformation under Paillier}
+	\label{tbl:log-pal}
+    \begin{tabular}{lcccccc}
+        \hline
+        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \hline
+		(a) & 13.369 & 36.870 & 0.99263 & 0.085 & 1.813 & 0.023 \\
+		(b) & 7.072 & 39.635 & 0.99017 & 0.089 & 2.073 & 0.023 \\
+		(c) & 8.151 & 39.019 & 0.98688 & 0.091 & 1.913 & 0.023 \\
+		(d) & 25.253 & 34.108 & 0.98927 & 0.089 & 1.919 & 0.023 \\
+		(e) & 10.374 & 37.971 & 0.98695 & 0.106 & 1.829 & 0.023 \\
+		(f) & 2.426 & 44.283 & 0.99401 & 0.127 & 1.900 & 0.023 \\
+		(g) & 5.184 & 40.985 & 0.98971 & 0.096 & 1.853 & 0.023 \\
+		(h) & 16.772 & 35.885 & 0.98492 & 0.081 & 1.746 & 0.024 \\
+		(i) & 5.803 & 40.494 & 0.99241 & 0.091 & 1.827 & 0.027 \\
+		(j) & 12.192 & 37.270 & 0.99354 & 0.081 & 1.815 & 0.023 \\
+		\hline
+        \end{tabular}
+\end{table}
+
+\begin{table}[t]
+	\caption{Logarithm transformation under DGK}
+	\label{tbl:log-dgk}
+    \begin{tabular}{lcccccc}
+        \hline
+        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \hline
+		(a) & 222.196 & 24.663 & 0.83568 & 0.635 & 25.556 & 0.488 \\
+		(b) & 180.941 & 25.555 & 0.75159 & 0.542 & 27.102 & 0.460 \\
+		(c) & 295.227 & 23.429 & 0.61360 & 0.534 & 25.720 & 0.486 \\
+		(d) & 286.799 & 23.555 & 0.76514 & 0.622 & 25.118 & 0.467 \\
+		(e) & 215.389 & 24.799 & 0.66924 & 0.557 & 25.500 & 0.452 \\
+		(f) & 65.621 & 29.960 & 0.83973 & 0.561 & 25.014 & 0.458 \\
+		(g) & 133.007 & 26.892 & 0.74749 & 0.572 & 25.605 & 0.497 \\
+		(h) & 225.269 & 24.604 & 0.70342 & 0.548 & 25.088 & 0.468 \\
+		(i) & 171.073 & 25.799 & 0.83257 & 0.538 & 25.410 & 0.494 \\
+		(j) & 203.214 & 25.051 & 0.86675 & 0.528 & 25.383 & 0.516 \\
+		\hline
+    \end{tabular}
+\end{table}
+
+\subsection{Power-Law Transformation}
+Applying the power-law transformation under both cryptosystems produced less than accurate images.
+The accuracy varies greatly across all the images as in the case of Paillier, with mean squared errors as high as 8270.696 and as low as 616.419, and SSIM scores ranging from 0.43185 to 0.92334, as seen in Table~\ref{tbl:pwr-pal}.
+As expected, the total processing time now takes about 15 to 20 seconds per image since the power-law transformation is more computationally intensive due to its approximation of an infinite series consisting of terms using the logarithm function, which is also approximated using a combination of addition and multiplication operations.
+
+\begin{table}[t]
+	\centering
+	\caption{Power-law transformation under Paillier}
+	\label{tbl:pwr-pal}
+    \begin{tabular}{lcccccc}
+        \hline
+        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \hline
+        (a) & 3910.678 & 12.208 & 0.46712 & 0.099 & 14.695 & 0.024 \\
+		(b) & 873.064 & 18.720 & 0.84379 & 0.139 & 16.190 & 0.023 \\
+		(c) & 1261.059 & 17.123 & 0.77229 & 0.082 & 13.866 & 0.023 \\
+		(d) & 653.049 & 19.981 & 0.90673 & 0.083 & 15.507 & 0.023 \\
+		(e) & 646.310 & 20.026 & 0.88157 & 0.108 & 15.727 & 0.045 \\
+		(f) & 2047.933 & 15.018 & 0.69408 & 0.113 & 14.728 & 0.034 \\
+		(g) & 806.473 & 19.065 & 0.85346 & 0.082 & 14.253 & 0.024 \\
+		(h) & 616.419 & 20.232 & 0.92334 & 0.121 & 14.415 & 0.023 \\
+		(i) & 8270.696 & 8.955 & 0.43185 & 0.112 & 14.362 & 0.065 \\
+		(j) & 1715.478 & 15.787 & 0.73857 & 0.145 & 20.239 & 0.023 \\
+		\hline
+        \end{tabular}
+\end{table}
+
+When DGK was used in the power-law transformation, it failed to produce a discernible image and only resulted in an almost black image with a faint shape of a face.
+The mean squared errors for this case is an order of magnitude higher than the results from using Paillier.
+Furthermore, doing a power-law transformation under DGK is not only impractical in terms of accuracy, but also it is somewhat impractical in terms of time efficiency because it took at most 4 minutes to process each image.
+
+\begin{table}[t]
+	\centering
+	\caption{Power-law transformation under DGK}
+	\label{tbl:pwr-dgk}
+    \begin{tabular}{lcccccc}
+        \hline
+        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \hline
+		(a) & 14777.466 & 6.435 & 0.12778 & 0.677 & 204.491 & 0.978 \\
+		(b) & 13343.854 & 6.878 & 0.07894 & 0.913 & 232.692 & 0.663 \\
+		(c) & 10885.568 & 7.762 & 0.09146 & 0.696 & 198.959 & 0.590 \\
+		(d) & 7218.081 & 9.547 & 0.10182 & 0.658 & 160.924 & 0.461 \\
+		(e) & 9994.237 & 8.133 & 0.09100 & 0.518 & 166.274 & 0.507 \\
+		(f) & 19141.793 & 5.311 & 0.08388 & 0.531 & 193.571 & 0.606 \\
+		(g) & 13213.915 & 6.920 & 0.09794 & 0.656 & 163.594 & 0.455 \\
+		(h) & 7444.691 & 9.412 & 0.09291 & 0.522 & 160.426 & 0.463 \\
+		(i) & 21349.488 & 4.837 & 0.17239 & 0.526 & 160.191 & 0.446 \\
+		(j) & 13776.770 & 6.739 & 0.10769 & 0.489 & 156.763 & 0.460 \\
+		\hline
+    \end{tabular}
+\end{table}

### 2019-03-06 paper/paper-conf.tex
Add citation to pcsc paper

@@
   \end{align*}
-  Since $r$ is a random integer, $kr$ is also a random integer, Therefore, $g^{km} \cdot (h^{kr}) \bmod{n} = D(E(m)^k)$ is a valid encryption of the message $km$.
+  Since $r$ is a random integer, $kr$ is also a random integer, Therefore, $g^{km} \cdot (h^{kr}) \bmod{n} = E(m)^k$ is a valid encryption of the message $km$.
 \end{proof}
@@
 
-In order to perform this transformation under Paillier and DGK, we provide the following closed-form approximation for $\log\left(1 + x\right)$.
+In order to perform this transformation under Paillier and DGK, we provide the following closed-form approximation for $\log\left(1 + x\right)$ from~\cite{pcsc-paper}.
 % TODO: IDK HOW TO CITE OUR PCSC PAPER

### 2019-03-06 parts/04_results.tex
\centering
Add table with images

@@
 
-% \begin{table*}
-% 	\centering
-% 	\caption{Comparison of intensity transformations under Paillier}
-% 	\label{tbl:it-pal}
-% 	\begin{tabular}{m{1cm}*{7}{>{\centering\arraybackslash}m{1.75cm}}}
-% 		\hline
-% 		\multirow{2}{*}{Image} & \multirow{2}{*}{Original} & \multicolumn{2}{c}{Image negation} & \multicolumn{2}{c}{Logarithm transformation} & \multicolumn{2}{c}{Power-law transformation} \\
-% 							   &                           & PDT           & CDT          & PDT            & CDT           & PDT               & CDT           \\
-% 		\hline
-% 		\xintForpair #1#2 in {(anpage,a), (bplyce,b), (drbost,c), (ksunth,d), (martin,e), (pmives,f), (rnpwil,g), (sbains,h), (swewin,i), (yfhsie,j)} \do {%
-% 		(#2) & \includegraphics[width=1.75cm]{out_faces/paillier_negate_#1_original.png} & \includegraphics[width=1.75cm]{out_faces/paillier_negate_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/paillier_negate_#1_decrypted.png} & \includegraphics[width=1.75cm]{out_faces/paillier_logtransform_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/paillier_logtransform_#1_decrypted.png} & \includegraphics[width=1.75cm]{out_faces/paillier_pwrtransform_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/paillier_pwrtransform_#1_decrypted.png} \\ }%
-% 		\hline
-% 	\end{tabular}
-% \end{table*}
-%
-% \begin{table*}
-% 	\centering
-% 	\caption{Comparison of intensity transformations under DGK}
-% 	\label{tbl:it-dgk}
-% 	\begin{tabular}{m{1cm}*{7}{>{\centering\arraybackslash}m{1.75cm}}}
-% 		\hline
-% 		\multirow{2}{*}{Image} & \multirow{2}{*}{Original} & \multicolumn{2}{c}{Image negation} & \multicolumn{2}{c}{Logarithm transformation} & \multicolumn{2}{c}{Power-law transformation} \\
-% 							   &                           & PDT           & CDT          & PDT            & CDT           & PDT               & CDT           \\
-% 		\hline
-% 		\xintForpair #1#2 in {(anpage,a), (bplyce,b), (drbost,c), (ksunth,d), (martin,e), (pmives,f), (rnpwil,g), (sbains,h), (swewin,i), (yfhsie,j)} \do {%
-% 		(#2) & \includegraphics[width=1.75cm]{out_faces/dgk_negate_#1_original.png} & \includegraphics[width=1.75cm]{out_faces/dgk_negate_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/dgk_negate_#1_decrypted.png} & \includegraphics[width=1.75cm]{out_faces/dgk_logtransform_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/dgk_logtransform_#1_decrypted.png} & \includegraphics[width=1.75cm]{out_faces/dgk_pwrtransform_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/dgk_pwrtransform_#1_decrypted.png} \\ }%
-% 		\hline
-% 	\end{tabular}
-% \end{table*}
+\begin{table*}
+	\centering
+	\caption{Comparison of intensity transformations under Paillier}
+	\label{tbl:it-pal}
+	\begin{tabular}{m{1cm}*{7}{>{\centering\arraybackslash}m{1.5cm}}}
+		\hline
+		\multirow{2}{*}{Image} & \multirow{2}{*}{Original} & \multicolumn{2}{c}{Image negation} & \multicolumn{2}{c}{Logarithm trans.} & \multicolumn{2}{c}{Power-law trans.} \\
+							   &                           & PDT           & CDT          & PDT            & CDT           & PDT               & CDT           \\
+		\hline
+		\xintForpair #1#2 in {(anpage,a), (bplyce,b), (drbost,c), (ksunth,d), (martin,e), (pmives,f), (rnpwil,g), (sbains,h), (swewin,i), (yfhsie,j)} \do {%
+		(#2) & \includegraphics[width=1.5cm]{out_faces/paillier_negate_#1_original.png} & \includegraphics[width=1.5cm]{out_faces/paillier_negate_#1_reference.png} & \includegraphics[width=1.5cm]{out_faces/paillier_negate_#1_decrypted.png} & \includegraphics[width=1.5cm]{out_faces/paillier_logtransform_#1_reference.png} & \includegraphics[width=1.5cm]{out_faces/paillier_logtransform_#1_decrypted.png} & \includegraphics[width=1.5cm]{out_faces/paillier_pwrtransform_#1_reference.png} & \includegraphics[width=1.5cm]{out_faces/paillier_pwrtransform_#1_decrypted.png} \\ }%
+		\hline
+	\end{tabular}
+\end{table*}
+
+\begin{table*}
+	\centering
+	\caption{Comparison of intensity transformations under DGK}
+	\label{tbl:it-dgk}
+	\begin{tabular}{m{1cm}*{7}{>{\centering\arraybackslash}m{1.5cm}}}
+		\hline
+		\multirow{2}{*}{Image} & \multirow{2}{*}{Original} & \multicolumn{2}{c}{Image negation} & \multicolumn{2}{c}{Logarithm trans.} & \multicolumn{2}{c}{Power-law trans.} \\
+							   &                           & PDT           & CDT          & PDT            & CDT           & PDT               & CDT           \\
+		\hline
+		\xintForpair #1#2 in {(anpage,a), (bplyce,b), (drbost,c), (ksunth,d), (martin,e), (pmives,f), (rnpwil,g), (sbains,h), (swewin,i), (yfhsie,j)} \do {%
+		(#2) & \includegraphics[width=1.5cm]{out_faces/dgk_negate_#1_original.png} & \includegraphics[width=1.5cm]{out_faces/dgk_negate_#1_reference.png} & \includegraphics[width=1.5cm]{out_faces/dgk_negate_#1_decrypted.png} & \includegraphics[width=1.5cm]{out_faces/dgk_logtransform_#1_reference.png} & \includegraphics[width=1.5cm]{out_faces/dgk_logtransform_#1_decrypted.png} & \includegraphics[width=1.5cm]{out_faces/dgk_pwrtransform_#1_reference.png} & \includegraphics[width=1.5cm]{out_faces/dgk_pwrtransform_#1_decrypted.png} \\ }%
+		\hline
+	\end{tabular}
+\end{table*}
 
@@
 \begin{table}[t]
+    \centering
 	\caption{Logarithm transformation under DGK}

### 2019-03-06 parts/09_removed.tex

@@
 \end{description}
+
+%\subsection{DGK Comparison Protocol}
+%The DGK system was primarily developed as part of a comparison protocol, a protocol which allows
+%It is known that $E(m)^{v_pv_q} \bmod n = 1$ if and only if $m=0$. This allows
+
+%\subsection{The Benaloh cryptosystem}
+%The Benaloh cryptosystem, initially proposed by Josh Benaloh in \cite{benaloh_dense_1994}, allows for the encryption of integers in $\mathbb{Z}_r$ for some odd integer $r$.
+It relies on the hardness of the \textit{discrete logarithm problem}, and is a generalization of the classic Goldwasser--Micali cryptosystem~\cite{goldwasser_probabilistic_1984}.
+We present here a corrected version by Fousse, et al.
+\cite{fousse_benalohs_2010} which corrects an error in the key generation algorithm which prevents accurate decryption in some cases.
+
+%\subsubsection{Benaloh Cryptosystem Description}
+%We choose an integer $r$ and two large primes $p$ and $q$ such that the following conditions hold:
+%\begin{itemize}
+%  \item $r$ divides $(p-1)$;
+%  \item $\mathrm{gcd}(r,(p-1)/r)=1$;
+%  \item $\mathrm{gcd}(r,q-1)=1$.
+%\end{itemize}
+%Next, let $n=pq$ and $\phi = (p-1)(q-1)$, and choose $y\in \mathbb{Z}_n^* = \{ x \in \mathbb{Z}_n | \mathrm{gcd}(x,n)=1 \}$ such that the following conditions hold:
+%\begin{itemize}
+%  \item $y^{\phi/r}\neq 1 \bmod n$;
+%  \item For all prime factors $s$ of $r$, $y^{\phi/s}\neq 1 \bmod n$.
+%\end{itemize}
+%We denote the public key to be $(y,r,n)$ and the private key to be $(p,q)$.
+
+%The encryption function to encrypt a plaintext $m \in \mathbb{Z}_r$ is defined as
+%\begin{align*}
+%  E(m) = y^m \cdot u^r \mod{n},
+%\end{align*}
+%where $u$ is a random integer in $\mathbb{Z}_n^*$.
+
+%The decryption function to decrypt a ciphertext $c \in \mathbb{Z}_{n}$ is defined as:
+%\begin{align*}
+%  D(c) = \log_x{c^{\phi/r}} \mod n
+%\end{align*}
+%where $x = y^{\phi/r}$ and $\log_x{y} = k$ such that $x^k = y \bmod n$.
+
+%Decryption requires the computation of the discrete logarithm, which can be done using a linear search when $r$ is small.
+For large values of $r$, the baby-step giant-step algorithm can be used to perform decryption in $O(\sqrt{r})$ time \cite{benaloh_dense_1994}.
+
+%\subsubsection{Homomorphic Properties of the Benaloh Cryptosystem}
+%Similar to the Paillier cryptosystem, the Benaloh cryptosystem supports additive homomorphism as well as the multiplication of a plaintext scalar to an encrypted message.
+%For all $m_1,m_2 \in \mathbb{Z}_r$ and $k\in \mathbb{N}$, the following homomorphic properties hold.
+%\begin{description}
+%  \item[Additive homomorphism]
+%  \begin{align*}
+%    D(E(m_1)y^{m_2}\bmod n^2)=(m_1+m_2)\bmod n & \text{ (used to add a constant)}\\
+%    D(E(m_1)E(m_2)\bmod n^2)=(m_1+m_2)\bmod n & \text{ (used for binary addition)}
+%  \end{align*}
+%  \item[Multiplicative homomorphism]
+%  \begin{align*}
+%    D(E(m_1)^k\bmod n)= km_1\bmod n & \text{ (used to multiply a plaintext constant)}
+%  \end{align*}
+%\end{description}
+
+%As the multiplicative homomorphism was not presented in the original paper, we provide a short proof here.
+%\begin{proof}
+%  Let $m \in \mathbb{Z}_r$ and $k\in \mathbb{N}$.
+%  We consider $E(m)^k\bmod n = (y^m \cdot u^r \bmod{n})^k\bmod n$.
+%  \begin{align*}
+%    (y^m \cdot u^r \bmod{n})^k\bmod n
+%    &= (y^m \cdot u^r)^k \bmod{n}\\
+%    &= (y^m)^k \cdot (u^r)^k \bmod{n}\\
+%    &= y^{km} \cdot (u^k)^r \bmod{n}\\
+%    &= y^{km} \cdot (u^k \bmod{n})^r \bmod{n}
+%  \end{align*}
+%  Since $u$ is a random integer in $\mathbb{Z}_n^*$, $\mathrm{gcd}(u,n)=1$.
+%  This implies $\mathrm{gcd}(u^k,n)=1$, so $u^k \bmod n$ is a random integer in $\mathbb{Z}_n^*$.
+%  Therefore, $y^{km} \cdot (u^k \bmod{n})^r \bmod{n} = E(m)^k\bmod n$ is a valid encryption of the message $km$.
+%\end{proof}
+
+% \subsection{Secure Exponentiation and Multiplication Protocols}
+% \label{ssec:exponentiationprotocol}
+% In order to perform polynomial evaluation, we first present a protocol for privacy-preserving exponentiation to a positive integer power, adapted from the protocol to calculate Euclidean distances used in \cite{hutchison_privacy-preserving_2009}.
+
+% The following protocols apply to both the Paillier and DGK cryptosystems, as they share similar homomorphisms. We first present a secure squaring protocol.
+
+% Suppose Alice encrypts an integer $x$ and sends it so Bob has $E(x)$, and wants to obtain $E(x^2)$ without exposing the value of $x$.
+% \begin{itemize}
+% 	\item Bob first selects a random integer $r$ and computes $E(x+r)$. Bob can do this since $r$ is a plaintext constant.
+% 	\item Bob sends $E(x+r)$ to Alice, who decrypts the ciphertext to obtain $x+r$.
+% 	\item Alice squares $x+r$ and encrypts the result. She sends $E((x+r)^2)$ to Bob.
+% 	\item Bob computes $E(-2rx + r^2)$. He then computes $E((x+r)^2)E(-2rx + r^2) = E(x^2)$.
+% \end{itemize}
+
+% We can use the secure squaring protocol to arrive at a secure multiplication protocol, which then allows for the evaluation of polynomials.
+% Suppose Alice encrypts integers $x$ and $y$, and Bob has $E(x), E(y)$ and wants to obtain $E(xy)$.
+% \begin{itemize}
+% 	\item Bob acquires $E(x^2), E(y^2)$ using the secure squaring protocol.
+% 	\item Bob sends $E(x+y)$ to Alice, who decrypts the ciphertext to obtain $x+y$.
+% 	\item Alice sends $E((x+y)^2)$ to Bob.
+% 	\item Bob then computes
+% 	\begin{align*}
+% 		E((x+y)^2)E(x^2)^{-1}E(y^2)^{-1} &= E((x+y)^2 - x^2 - y^2)\\
+% 		&= E(2xy)
+% 	\end{align*}
+% 	\item Bob can then recover $E(xy)$ by calcuating for the multiplicative inverse of 2 using the Euclidean algorithm, and calculating $2^{-1}E(xy)$.
+Such an inverse exists since the modulus is either a prime (in the DGK cryptosystem) or a product of primes greater than 2 (in the Paillier cryptosystem).
+% \end{itemize}
+
+\subsection{The Dasgupta--Pal Cryptosystem}
+The Dasgupta--Pal cryptosystem is a fully homomorphic cryptosystem proposed in 2016 by Smaranika Dasgupta and S.
+K.
+Pal \cite{dasgupta_design_2016}, which encrypts integer plaintexts in $\mathbb{Z}_n$ to polynomial ciphertexts.
+We begin our presentation of the Dasgupta--Pal cryptosystem with the following definition.
+
+Given a message $m \in \mathbb{Z}$, we denote
+\begin{align*}
+		m_p(x) = a_0 + a_1x + a_2x^2 + \cdots + a_kx^k
+\end{align*}
+where $a_ka_{k-1}\cdots a_2a_1_0$ is the binary representation of $m$.
+
+In the original scheme presented in \cite{dasgupta_design_2016}, the secret key $S_k$ is set to be a large prime.
+In Appendix \ref{chap:correction}, we present a case where the Dasgupta--Pal cryptosystem fails and prove that setting the secret key $S_k = 2p$, where $p$ is a large prime, corrects errors in the Dasgupta--Pal cryptosystem.
+We now decribe the correct cryptosystem.
+\subsubsection{Corrected Dasgupta--Pal Cryptosystem Description}
+Let $\ell$ denote the security parameter of the cryptosystem.
+Let $S_k = 2p$, where $p$ is a prime number with $\ell - 1$ bits.
+Choose a random even integer $z$ of length $\log_2{\ell}$.
+
+Let the secret key be $S_k$, and let the refresh key be $R_k = z \cdot S_k$. The secret key is kept private to the encrypting/decrypting parties, while the refresh key is made publicly available.
+
+The scheme defines the encryption algorithm for a message $m$ as follows:
+\begin{align*}
+	E(m) = y(x) + S_k\times d(x)
+\end{align*}
+where
+$y(x)$ is a polynomial of degree $n$ such that $m_p(x) \equiv y(x) \bmod S_k$ and $d(x)$ is a randomly chosen polynomial of degree $n$.
+This encrypts each coefficient of of $m_p(x)$ by adding some multiple of $S_k$ to it.
+Through this process, each bit of the message is encrypted separately.
+
+Furthermore, the decryption algorithm to recover $m_p(x)$ from a ciphertext polynomial $c(x)$ as
+\begin{align*}
+	m_p(x) = c(x) \bmod S_k \bmod 2.
+\end{align*}
+Thus $D(c(x))$ is defined as the integer recovered from the coefficients of the polynomial $c(x) \bmod S_k \bmod 2$.
+
+Dasgupta and Pal note that homomorphic operations on ciphertext introduce noise which may interfere with decryption, due to the potential increase in ciphertext values.
+To eliminate noise from a polynomial ciphertext, the following refresh function is used:
+\begin{align*}
+	R(c(x)) = c(x) \bmod R_k.
+\end{align*}
+
+\subsubsection{Homomorphic Properties of the Dasgupta--Pal Cryptosystem}
+It has been shown \cite{dasgupta_design_2016} that the following properties hold for all integer messages $m_1, m_2 \in \mathbb{Z}_n$ in the Dasgupta--Pal cryptosystem.
+These properties arise since each coefficient in a ciphertext polynomial is essentially an independently encrypted bit of the original message.
+\begin{description}
+	\item[XOR on ciphertexts]
+	A bitwise exclusive or (XOR) operation on integer messages can be achieved by adding the coefficients pairwise between two ciphertexts.
+	\begin{align*}
+		D(E(m_1)+E(m_2)) = m_1 \text{ XOR } m_2
+	\end{align*}
+	\item[AND on ciphertexts]
+	Similarly, pair-wise multiplication corresponds to bitwise AND of integer messages.
+	\begin{align*}
+		D(E(a) \otimes E(b)) = a \text{ AND } b = ab \bmod 2
+	\end{align*}
+	where $\otimes$ denotes pairwise multiplication,
+	\begin{align*}
+		\sum_{i=1}^n{a_ix^i} \otimes \sum_{i=1}^n{b_ix^i} = \sum_{i=1}^n{a_ib_ix^i}.
+	\end{align*}
+\end{description}
+
+Arbitrary computation on data can thus be achived using these bitwise operations.
+While the Dasgupta--Pal cryptosystem requires significant amounts of memory, as each bit of plaintext is encrypted into an integer, this approach provides a flexible method to perform relatively fast arbitrary computation on encrypted data.
+Encryption and decryption in the Dasgupta--Pal cryptosystem are accomplished using few arithmetic operations.

### 2019-03-06 parts/02_relatedliterature_01cryptoimg.tex
WIP cryptosystem RRL
working on cryptosystem RRL
Add chapter 4 contents
Add chapter 5

@@
 \section{CryptoImg}
-A paper published in 2009 by Ziad, et.
-al.
+A paper published in 2009 by Ziad, et al.
 attempts to implement privacy-preserving image processing using \textit{CryptoImg}, a library for the Open Source Computer Vision Library (OpenCV)~\cite{bradski_opencv_2000} which implements various homomorphic encryption and image processing routines using the Paillier homomorphic cryptosystem~\cite{ziad_cryptoimg:_2016}.
@@
 Then the resulting image is sent back to the client, which decrypts the image to recover the desired output.
-\begin{figure*}[!ht]
+\begin{figure}[!ht]
     \centering
-    \includegraphics[width=\textwidth,\keepaspectratio]{Figures/ClientServerModel.png}
+    \includegraphics[width=\textwidth,keepaspectratio=true]{Figures/ClientServerModel.png}
     \caption{Client-server architecture used by \textit{CryptoImg} \cite{ziad_cryptoimg:_2016}}
     \label{fig:clientserver}
-\end{figure*}
+\end{figure}
 The \textit{CryptoImg} library implemented the following:

### 2019-03-06 parts/05_conclusions.tex
Add chapter 5

@@
 \chapter{CONCLUSIONS}
-Upon presenting your results, the conclusion is where you will now tie up these results with the original intent of the study, as indicated by the research questions given in the Introduction.
-It is in this section where you will also discuss any difficulties or issues encountered during the study, as well as your recommended method for addressing these problems.
+In this study, we have assessed the feasibility and practicality of various homomorphic cryptosystems with regard to secure processing and manipulation of facial image data through creation of a software library that facilitates image processing operations within the encrypted domain, as well as our own implementation of some homomorphic cryptosystems like DGK.
 
-The general way to organize your conclusion is to present each research sub-question as a subsection, and thoroughly answer each of them by interpreting your results with respect to the question.
-With these answered, you may then tie up all of your findings in each subsection to answer your main research question, providing any needed additional information or explanation.
-Last on the list would be your unsolved issues and difficulties, presenting them as avenues to motivate continued work on your chosen topic.
+Even though an operation in a partially homomorphic cryptosystem is not theoretically possible, like multiplication of two ciphertexts under Paillier, it has been shown that such operations are indeed possible in a two-party system.
+Protocols for secure multiplication and exponentiation have been proposed and also applied to more complex image operations such as facial recognition.
+Thus, a partially homomorphic cryptosystem can be modified to admit more image processing operations by assuming a two-party system.
+
+Preliminary results have shown that both Paillier and DGK apply image negation accurately and efficiently, as evidenced by the perfect zero MSE and infinite PSNR.
+For the logarithm transformation, Paillier was faster and accurate enough (with $\text{MSE} \le 30$ and $\text{SSIM} \approx 0.99$) which was rather unexpected.
+However both Paillier and DGK fail to produce accurate results in applying the power-law transformation, with the latter failing to produce discernible results.
+Based from these results, the Paillier cryptosystem is consistent enough to produce reasonable to accurate results.
+
+A wrapper library has been made which implements the various functions and methods of the cryptosystems into a single interface.
+This allowed us to express various image operations with a unified syntax, thus facilitating easier testing.
+
+\section{Ongoing and Future Work}
+Testing intensity transformations under the BGV cryptosystem will be started once the Pyfhel library is deemed stable enough to use, or another Python library that implements BGV becomes available.
+One of the authors of this paper has already informed the developers of the Pyfhel library about a bug involving exponentiation of two real numbers.
+
+Efforts are ongoing with regard to the facial recognition tests.
+Our own implementation of the privacy-preserving  eigenfaces by Erkin, et al.
+does not yet use the DGK cryptosystem for secure integer comparison in the match finding step, thus we are working on implementing DGK from scratch.
+
+Another promising image operation to consider is \textit{facial detection} under a homomorphic cryptosystem.
+Work has been started in order to assess the feasibility of using Haar cascades in a privacy-preserving manner.
+
+Future work would involve improving and optimizing our implementation of non-linear intensity transformations in terms of number of operations, numerical accuracy and stability, and time efficiency.
+% Future work would involve improving and optimizing our implementation of the DGK cryptosystem so that it performs faster.
+% A suggestion would be to port the existing implementation to C/C++ and then create a Python library that acts as a wrapper to the C/C++ methods.
+For future studies, an implementation of a client-server framework or system dealing with secure image processing can be considered.

### 2019-03-07 parts/05_conclusions.tex
Fixed typo
fix ch5

@@
 \chapter{CONCLUSIONS}
-In this study, we have assessed the feasibility and practicality of various homomorphic cryptosystems with regard to secure processing and manipulation of facial image data through creation of a software library that facilitates image processing operations within the encrypted domain, as well as our own implementation of some homomorphic cryptosystems like DGK.
+In this study, we have assessed the feasibility and practicality of various homomorphic cryptosystems with regard to secure processing and manipulation of facial image data through creation of a software library that facilitates image processing operations within the encrypted domain.
 
@@
 Our own implementation of the privacy-preserving eigenfaces by Erkin, et al.
-does not yet use the DGK cryptosystem for secure integer comparison in the match finding step, thus we are working on implementing DGK from scratch.
+does not yet use the DGK cryptosystem for secure integer comparison in the match finding step.
 

### 2019-03-12 icmssp-paper/appendix.tex
Change folder structure
- renamed paper folder to icmssp-paper
- split icmssp paper into parts

--- 2019-01-11 paper/appendix.tex
@@
 	\end{align*}
-	\columnbreak
+	% \columnbreak
 	\begin{align*}
@@
 \end{multicols}
-Applying this procedure to the integral in equation \ref{eq:log_integral} using SageMath 8.3 yields the following approximation:
+
+Applying this procedure to the integral in Equation~\ref{eq:log_integral} using SageMath 8.3 yields the following approximation:
 \begin{equation}\label{eq:standardquadrature}
@@
 
-While the closed form approximation in equation \ref{eq:standardquadrature} is accurate for values of $x$ near zero, it diverges from $\log{(1+x)}$ significantly for large values of $x$, as shown in figure \ref{fig:standardquadrature}.
+% \pgfplotsset{
+% 	every axis legend/.append style={anchor=south east},
+% }
+
+While the closed form approximation in Equation~\ref{eq:standardquadrature} is accurate for values of $x$ near zero, it diverges from $\log{(1+x)}$ significantly for large values of $x$, as shown in Figure~\ref{fig:standardquadrature}.
+% \begin{figure}[!ht]
+%     \centering
+%     \includegraphics[width=.8\linewidth]{figures/StandardQuadrature.png}
+%     \caption{Graph of $\log{(1+x)}$ and the approximation in equation \ref{eq:standardquadrature}}
+%     \label{fig:standardquadrature}
+% \end{figure}
 \begin{figure}[!ht]
     \centering
-    \includegraphics[width=.8\linewidth]{figures/StandardQuadrature.png}
-    \caption{Graph of $\log{(1+x)}$ and the approximation in equation \ref{eq:standardquadrature}}
+	\begin{tikzpicture}
+		\begin{axis}[
+			% height=6cm, width=9cm,
+			xmin=0, xmax=300,
+			ymin=0, ymax=5.5, ytick={0,...,6},
+			xlabel={$x$}, ylabel={$y$},
+			grid=major,
+			legend pos=south east,
+			legend cell align=left,
+		]
+		\addplot[very thick, domain=0:300, samples=100]{1/30*(137*x^5 + 2310*x^4 + 9870*x^3 + 15120*x^2 + 7560*x)/(x^5 + 30*x^4 + 210*x^3 + 560*x^2 + 630*x + 252)};
+		\addplot[densely dashed, domain=0:300, samples=100]{ln(x)};
+		\legend{5-point quadrature approximation, Actual value of $\log(1+x)$}
+		\end{axis}
+	\end{tikzpicture}%
+    \caption{Graph of $\log{(1+x)}$ and the approximation in Equation~\ref{eq:standardquadrature}}
     \label{fig:standardquadrature}
@@
 
-Figure \ref{fig:scaledquadrature} is a graph of the absolute error of the scaled approximation and the exact value of $\log{(1+x)}$.
+Figure~\ref{fig:scaledquadrature} is a graph of the absolute error of the scaled approximation and the exact value of $\log{(1+x)}$.
 Using SageMath 8.3, it was numerically determined that the maximum absolute error of this approximation in the range $x\in[0,255]$ is approximately $0.0103315865985758$, occurring at $x=255$.
-This is an improvement from the approximation in equation \ref{eq:standardquadrature}, which has a maximum absolute error of $1.19717868468392$, similarly occurring at $x=255$.
+This is an improvement from the approximation in Equation~\ref{eq:standardquadrature}, which has a maximum absolute error of $1.19717868468392$, similarly occurring at $x=255$.
 
+% \begin{figure}[h]
+%     \centering
+%     \includegraphics[width=.9\linewidth]{figures/ModifiedQuadratureAbsoluteError.png}
+%     \caption{Graph of the absolute error of $\log{(1+x)}$ and the approximation in equation \ref{eq:scaledquadrature}}
+%     \label{fig:scaledquadrature}
+% \end{figure}
 \begin{figure}[h]
     \centering
-    \includegraphics[width=.9\linewidth]{figures/ModifiedQuadratureAbsoluteError.png}
-    \caption{Graph of the absolute error of $\log{(1+x)}$ and the approximation in equation \ref{eq:scaledquadrature}}
+    \begin{tikzpicture}
+		\begin{axis}[
+			% height=6cm, width=9cm,
+			xmin=0, xmax=300,
+			ymin=0, ymax=0.04,
+			xlabel={$x$}, ylabel={Absolute error},
+			grid=major,
+			legend pos=south east,
+			legend cell align=left,
+			tick scale binop=\times,
+		]
+		\addplot[thick, domain=0:300, samples=100]{abs((1/30*(137*x^5 + 33185*x^4 + 931370*x^3 - 13403630*x^2 - 289469315*x - 713567363)/(x^5 + 505*x^4 + 42010*x^3 + 923010*x^2 + 5722005*x + 8040501))-ln((1/20)+(1/20)*x))};
+		\end{axis}
+	\end{tikzpicture}%
+    \caption{Graph of the absolute error of $\log{(1+x)}$ and the approximation in Equation~\ref{eq:scaledquadrature}}
     \label{fig:scaledquadrature}
@@
 \subsection{Approximation for $x^\gamma$}
+\label{sec:approx-pwr}
 To approximate $x^\gamma$ for any $\gamma \in \mathbb{R}$, we rewrite $x^\gamma$ as follows:
@@
   e^x &= \sum_{n=0}^{\infty}{\frac{x^n}{n!}}\\
-  \Rightarrow e^{\gamma\log{x}} &= \sum_{n=0}^{\infty}{\frac{(\gamma\log{x})^n}{n!}}
+  \Rightarrow \quad e^{\gamma\log{x}} &= \sum_{n=0}^{\infty}{\frac{(\gamma\log{x})^n}{n!}}
 \end{align*}

### 2019-03-12 icmssp-paper/icmssp2019-sigconf.tex
Change folder structure
- renamed paper folder to icmssp-paper
- split icmssp paper into parts

--- 2019-02-08 paper/icmssp2019-sigconf.tex
@@
 % \acmYear{2019}
+\doi{http://dx.doi.org/10.1145/12345.67890}
 \CopyrightYear{2019}
@@
 
-\numberofauthors{2}
+\numberofauthors{3}
 \author{
@@
 \affaddr{Ateneo de Manila University}\\
-\affaddr{Katipunan Avenue, Loyola Heights}\\
+% \affaddr{Katipunan Ave., Loyola Heights}\\
 \affaddr{Quezon City, Philippines}\\
-\email{aldrich.asuncion@obf.ateneo.edu}
+\email{aldrich.asuncion@obf.\linebreak[0]ateneo.edu}
 \alignauthor Brian Christopher T. Guadalupe\\
 \affaddr{Ateneo de Manila University}\\
-\affaddr{Katipunan Avenue, Loyola Heights}\\
+% \affaddr{Katipunan Ave., Loyola Heights}\\
 \affaddr{Quezon City, Philippines}\\
-\email{brian.guadalupe@obf.ateneo.edu}
+\email{brian.guadalupe@obf.\linebreak[0]ateneo.edu}
+\alignauthor William Emmanuel S. Yu\\
+\affaddr{Ateneo de Manila University}\\
+% \affaddr{Katipunan Ave., Loyola Heights}\\
+\affaddr{Quezon City, Philippines}\\
+\email{wyu@ateneo.edu}
 }
@@
 Regardless, homomorphic cryptography has been targeted for use in secure image processing and facial recognition, due to their ability to maintain data privacy.
-In this paper, we compared the viability of the Paillier, Damg{\aa}rd--Geisler--Kr{\o}igaard (DGK), Dasgupta--Pal, and Brakerski--Gentry--Vaikuntanathan (BGV) cryptosystems for facial image processing applications, by implementing a software library equipped with these cryptosystems, and comparing their time efficiency and accuracy.
+In this paper, we compared the viability of the Paillier, Damg{\aa}rd--Geisler--Kr{\o}igaard (DGK), and Brakerski--Gentry--Vaikuntanathan (BGV) cryptosystems for facial image processing applications, by implementing a software library equipped with these cryptosystems, and comparing their time efficiency and accuracy.
 Furthermore, as an extension to previous research, we attempt to support non-linear image processing operations.
-Preliminary results have shown that the Paillier and Dasgupta--Pal cryptosystems are comparable in accuracy and may be used to approximate a logarithm transformation, but the Dasgupta--Pal cryptosystem is significantly slower.
+Preliminary results have shown that the Paillier and DGK cryptosystems are comparable in accuracy and may be used for image negation, but only the Paillier cryptosystem is consistent enough to produce reasonable to accurate results.
 \end{abstract}

### 2019-03-12 icmssp-paper/parts/01_introduction.tex
Change folder structure
- renamed paper folder to icmssp-paper
- split icmssp paper into parts

--- 2019-02-10 paper/paper-conf.tex
@@
 Our software library would allow service providers to perform image manipulation for clients without compromising data privacy.
-
-\section{Review of Related Literature}
-\subsection{Homomorphic Cryptosystems}
-A cryptosystem consists of an encryption function $\mathcal{E}$ and a decryption function $\mathcal{D}$, along with the plaintext space $\mathcal{P}$, ciphertext space $\mathcal{C}$ and the key space $\mathcal{K}$~\cite{bauer_cryptosystem_2005}.
-A \textit{plaintext} is text that can be commonly understood, while a \textit{ciphertext} results from encrypting the plaintext using an encryption key.
-The \textit{plaintext space} is the set of all possible plaintexts, the \textit{ciphertext space} is the set of all possible ciphertexts, while the \textit{keyspace} is the set of all possible keys.
-
-% There are two kinds of cryptosystems, \textit{symmetric} and \textit{asymmetric}.
-In symmetric-key cryptosystems, the same key is used for both encryption and decryption.
-As a consequence, symmetric-key cryptosystems must be implemented with a secure key exchange protocol, so that both the sender and receiver have access to the same key.
-Prominent examples of symmetric-key cryptosystems are the Data Encryption Standard (DES), and its replacement, the Advanced Encryption Standard (AES).
-
-% On the other hand, asymmetric-key (or public-key) cryptosystems use separate keys for encryption and decryption.
-The encryption key (also called the \textit{public key}) is shared publicly, while the decryption key (also called the \textit{private key}) is kept secret.
-Since the public key and private keys are different, there is no need to agree upon secure key exchange protocols.
-Usually, the security of asymmetric-key cryptosystems relies on the intractability of certain computational problems, for example, the RSA cryptosystem depends on the difficulty of big integer factorization~\cite{rivest_method_1978}, while the ElGamal cryptosystem depends on the difficulty of the discrete logarithm problem~\cite{blakley_public_1985}.
-
-% Homomorphic cryptosystems are a special type of cryptosystem in which operations can be securely performed on encrypted data.
-Suppose that for a public-key cryptosystem, $\mathcal{E}_k \left(p \right)$ is the encryption function using the public key $k \in \mathcal{K}$, and $\mathcal{D}_l \left(c \right)$ be the decryption function using the private key $l$.
-A cryptosystem is said to be homomorphic if its encryption function is homomorphic, that is, if it satisfies the relation
-% \begin{equation}
-%     \mathcal{E}_k \left(p_1 \boxplus p_2\right) = \mathcal{E}_k \left(p_1\right) \boxdot \mathcal{E}_k \left(p_2\right)
-% \end{equation}
-% where $p_1, p_2 \in \mathcal{P}$ are the plaintexts, and $\boxplus$ and $\boxdot$ are operations in $\mathcal{P}$ and $\mathcal{C}$ respectively~\cite{fontaine_survey_2007}.
-Furthermore, a homomorphic cryptosystem also satisfies~\cite{li_elliptic_2012}
-% \begin{equation}
-%     p_1 \boxplus p_2 = \mathcal{D}_l \left( \mathcal{E}_k \left(p_1\right) \boxdot \mathcal{E}_k \left(p_2\right) \right).
-% \end{equation}
-
-% In other words, 
-A homomorphic cryptosystem preserves the operations that can be done with the plaintext without requiring an intermediary step of decrypting the ciphertext beforehand.
-It is important to note that the operations in the plaintext space and ciphertext space need not be the same.
-A simple operation in the plaintext space may require a computationally intensive operation in the ciphertext space.
-
-% Homomorphic cryptosystems can be classified according to the plaintext and ciphertext operations, $\boxplus$ and $\boxdot$.
-If the plaintext operation $\boxplus$ is addition, the cryptosystem is said to be \textit{additively homomorphic}, and the cryptosystem is said to be \textit{multiplicatively homomorphic} if the plaintext operation $\boxplus$ is multiplication.
-
-\subsection{Partially Homomorphic Cryptosystems}
-In this section, we will present two classical partially homomorphic cryptosystems which we will be testing in the study: the Paillier cryptosystem and the DGK cryptosystem.
-Both of these cryptosystems encrypt integer plaintexts as integer ciphertexts.
-In our description of each cryptosystem, we use $E(m)$ to denote the encryption of a plaintext $m$, and $D(c)$ to denote the decryption of a ciphertext $c$.
-
-% We will then show that the cryptosystems can be modified to support privacy-perserving polynomial evaluation in a client-server protocol: given an encrypted message $m$, evaluate $f(m)$ where $f$ is a polynomial function.
-
-\subsubsection{The Paillier Cryptosystem}
-The Paillier cryptosystem \cite{stern_public-key_1999}, developed by Pascal Paillier, is a probabilistic encryption scheme which is based on the composite residuosity class problem.
-The scheme has several well--known homomorphic properties.
-% The scheme allows for the encryption and decryption of integer messages, and is known to be additively homomorphic.
-% We now state the encryption and decryption algorithms of the Paillier cryptosystem and its homomorphic properties.
-
-% \paragraph{Key Generation}
-% We first define a function $L(x)$ as the largest integer $v$ greater than zero such that $x-1 \geq vn$.
-% We choose two large primes $p$ and $q$, and set $n = pq, \lambda = \mathrm{lcm}(p-1,q-1)$.
-% Then we select an integer $g$, $0\leq g \leq n^2$ such that $\mathrm{gcd}(L(g^\lambda \bmod n^2), n) = 1$.
-% We denote the public key as $(g,n)$ and the private key $(p,q)$.
-
-% \paragraph{Encryption and Decryption}
-% The encryption function to encrypt a plaintext $m \in \mathbb{Z}_n$ given a public key $(g,n)$ is defined as
-% \begin{align*}
-%   E(m) = g^m \cdot r^n \mod{n^2},
-% \end{align*}
-% where $r$ is a random non-negative integer less than $n^2$.
-
-% The decryption function to decrypt a ciphertext $c \in \mathbb{Z}^\ast_{n^2}$ given a private key $(p,q)$ is defined as:
-% \begin{align*}
-%   D(c) = L(c^\lambda \bmod n^2) \times (L(g^\lambda \bmod n^2))^{-1} \mod n
-% \end{align*}
-
-% \paragraph{Homomorphic Properties of the Paillier Cryptosystem}
-% The Paillier cryptosystem supports additive homomorphism as well as the multiplication of a plaintext scalar to an encrypted message.
-These homomorphic properties are used to add a plaintext scalar to a ciphertext, add two ciphertexts, and multiply a ciphertext by a plaintext scalar, respectively.
-They are defined as follows.
-
-For all $m_1,m_2 \in \mathbb{Z}_n$ and $k\in \mathbb{N}$, the following homomorphic properties hold for the Paillier cryptosystem with public key $(g,n)$.
-\begin{align*}
-  D(E(m_1)g^k\bmod n^2) &=(m_1+k)\bmod n\\
-  D(E(m_1)E(m_2)\bmod n^2) &=(m_1+m_2)\bmod n\\
-  D(E(m_1)^k\bmod n^2) &= km_1\bmod n
-\end{align*}
-
-These homomorphic properties are used to add a plaintext scalar to a ciphertext, add two ciphertexts, and multiply a ciphertext by a plaintext scalar, respectively.
-
-\subsubsection{The DGK Cryptosystem}
-The DGK cryptosystem was published by Damg{\aa}rd, Geisler, and Kr{\o}igaard in 2007 in an effort to create a secure integer comparison scheme \cite{pieprzyk_efficient_2007, cryptoeprint:2008:321} which is widely used in the literature \cite{veugen_improving_2012}.
-The DGK cryptosystem has homomorphic properties similar to the Paillier cryptosystem.
-
-% \paragraph{Key Generation}
-% We denote $k,t,\ell$ as security parameters of the scheme, where $k>t>\ell$.
-% Let $p,q$ be primes such that
-% we can choose two $t$-bit primes $v_p$ and $v_q$ such that $v_p | (p-1)$ and $v_q | (q-1)$, and a small prime $u$ such that $u | (p-1)$ and $u | (q-1)$.
-% We denote $n = pq$.
-% We choose $g$ to be an integer of order $uv_pv_q$ and $h$ to be of order $v_pv_q$.
-
-% The DGK cryptosystem encrypts plaintexts in $\mathbb{Z}_u$ to ciphertexts in $\mathbb{Z}_n^\ast$.
-
-% The public key is $(n,g,h,u)$ and the private key is $(p,q,v_p,v_q)$.
-
-% \paragraph{Encryption and Decryption}
-% To encrypt a message $m \in \mathbb{Z}_u$, the encryption function is defined as:
-% \begin{align*}
-%   E(m) = g^m \cdot h^r \mod{n},
-% \end{align*}
-% where $r$ is a random integer in $\mathbb{Z}_n$ which is longer than $2t$ bits.
-
-% To decrypt a ciphertext $c \in \mathbb{Z}_n^\ast$, decryption is achieved by first computing $c^{v_pv_q}$.
-% \begin{align*}
-% 	c^{v_pv_q} \bmod n
-% 	&= (g^m \cdot h^r)^{v_pv_q} \bmod n\\
-% 	&= (g^{v_pv_q})^m \bmod n
-% \end{align*}
-% Since $(g^{v_pv_q})^m$ has order $u$, there is a one-to-one correspondence between plaintexts in $\mathbb{Z}_u$ and  $(g^{v_pv_q})^m$.
-A lookup table can thus be generated privately to successfully recover $m$.
-
-% \paragraph{Homomorphic Properties of the DGK Cryptosystem}
-% The DGK cryptosystem supports additive homomorphism as well as the multiplication of a plaintext scalar to an encrypted message.
-These homomorphic properties are used to add a plaintext scalar to a ciphertext, add two ciphertexts, and multiply a ciphertext by a plaintext scalar, respectively.
-They are defined as follows.
-
-For all $m_1,m_2 \in \mathbb{Z}_u$ and $k\in \mathbb{N}$, the following homomorphic properties hold for the DGK cryptosystem with public key $(n,g,h,u)$.
-\begin{align*}
-    D(E(m_1)g^k) &=(m_1+k)\bmod u\\
-    D(E(m_1)E(m_2)) &=(m_1+m_2)\bmod u\\
-    D(E(m_1)^k) &= km_1\bmod u
-\end{align*}
-
-As the multiplicative homomorphism was not presented in the original paper, we provide a short proof here.
-\begin{proof}
-  Let $m \in \mathbb{Z}_u$ and $k\in \mathbb{N}$.
-  We consider $E(m)^k = (g^m \cdot h^r \bmod{n})^k\bmod n$.
-  \begin{align*}
-    (g^m \cdot h^r \bmod{n})^k \bmod n
-    &= (g^m \cdot h^r)^k \bmod{n}\\
-    &= (g^m)^k \cdot (h^r)^k \bmod{n}\\
-    &= g^{km} \cdot (h^kr) \bmod{n}
-  \end{align*}
-  Since $r$ is a random integer, $kr$ is also a random integer, Therefore, $g^{km} \cdot (h^kr) \bmod{n} = D(E(m_1)^k)$ is a valid encryption of the message $km$.
-\end{proof}
-
-% \subsubsection{Secure Exponentiation and Multiplication Protocols}
-% \label{ssec:exponentiationprotocol}
-% [TO-DO: This is further explained in another paper.]
-% In order to perform polynomial evaluation, we first present a protocol for privacy-preserving exponentiation to a positive integer power, adapted from the protocol to calculate Euclidean distances used in \cite{hutchison_privacy-preserving_2009}.
-
-% The following protocols apply to both the Paillier and DGK cryptosystems, as they share similar homomorphisms. We first present a secure squaring protocol.
-
-% Suppose Alice encrypts an integer $x$ and sends it so Bob has $E(x)$, and wants to obtain $E(x^2)$ without exposing the value of $x$.
-% \begin{itemize}
-% 	\item Bob first selects a random integer $r$ and computes $E(x+r)$. Bob can do this since $r$ is a plaintext constant.
-% 	\item Bob sends $E(x+r)$ to Alice, who decrypts the ciphertext to obtain $x+r$.
-% 	\item Alice squares $x+r$ and encrypts the result. She sends $E((x+r)^2)$ to Bob.
-% 	\item Bob computes $E(-2rx + r^2)$. He then computes $E((x+r)^2)E(-2rx + r^2) = E(x^2)$.
-% \end{itemize}
-
-% We can use the secure squaring protocol to arrive at a secure multiplication protocol, which then allows for the evaluation of polynomials.
-% Suppose Alice encrypts integers $x$ and $y$, and Bob has $E(x), E(y)$ and wants to obtain $E(xy)$.
-% \begin{itemize}
-% 	\item Bob acquires $E(x^2), E(y^2)$ using the secure squaring protocol.
-% 	\item Bob sends $E(x+y)$ to Alice, who decrypts the ciphertext to obtain $x+y$.
-% 	\item Alice sends $E((x+y)^2)$ to Bob.
-% 	\item Bob then computes
-% 	\begin{align*}
-% 		E((x+y)^2)E(x^2)^{-1}E(y^2)^{-1} &= E((x+y)^2 - x^2 - y^2)\\
-% 		&= E(2xy)
-% 	\end{align*}
-% 	\item Bob can then recover $E(xy)$ by calcuating for the multiplicative inverse of 2 using the Euclidean algorithm, and calculating $2^{-1}E(xy)$.
-Such an inverse exists since the modulus is either a prime (in the DGK cryptosystem) or a product of primes greater than 2 (in the Paillier cryptosystem).
-% \end{itemize}
-
-\subsection{Fully Homomorphic Cryptosystems}
-We will also be testing fully homomorphic cryptosytems, which allow aribitrary computation on encrypted data.
-While generally being more flexible, fully homomorphic cryptosytems are known to be significantly slower than partially homomorphic cryptosytems; improving the efficiency of fully homomorphic cryptosytems is an active area of research \cite{sen_homomorphic_2013}.
-
-% We will present two such cryptosystems, the Dasgupta--Pal cryptosystem, which we present in full to explain a correction we propose to it, and the BGV cryptosystem, which has open source implementations availble primarily used in homomorphic cryptography research.
-
-% \subsubsection{The Dasgupta--Pal Cryptosystem}
-% The Dasgupta--Pal cryptosystem is a fully homomorphic cryptosystem proposed in 2016 by Smaranika Dasgupta and S.
-K.
-Pal \cite{dasgupta_design_2016}, which encrypts integer plaintexts in $\mathbb{Z}_n$ to polynomial ciphertexts.
-We begin our presentation of the Dasgupta--Pal cryptosystem with the following definition.
-
-% Given a message $m \in \mathbb{Z}$, we denote
-% \begin{align*}
-% 		m_p(x) = a_0 + a_1 x + a_2 x^2 + \cdots + a_k x^k
-% \end{align*}
-% where $a_k a_{k-1}\cdots a_2 a_1 a_0$ is the binary representation of $m$.
-
-% In the original scheme presented in \cite{dasgupta_design_2016}, the secret key $S_k$ is set to be a large prime.
-In Appendix \ref{chap:correction}, we present a case where the Dasgupta--Pal cryptosystem fails and prove that setting the secret key $S_k = 2p$, where $p$ is a large prime, corrects errors in the Dasgupta--Pal cryptosystem.
-% We now decribe the correct cryptosystem.
-% \paragraph{Corrected Dasgupta--Pal Cryptosystem Description}
-% Let $\ell$ denote the security parameter of the cryptosystem.
-% Let $S_k = 2p$, where $p$ is a prime number with $\ell - 1$ bits.
-% Choose a random even integer $z$ of length $\log_2{\ell}$.
-
-% Let the secret key be $S_k$, and let the refresh key be $R_k = z \cdot S_k$. The secret key is kept private to the encrypting/decrypting parties, while the refresh key is made publicly available.
-
-% The scheme defines the encryption algorithm for a message $m$ as follows:
-% \begin{align*}
-% 	E(m) = y(x) + S_k\times d(x)
-% \end{align*}
-% where
-% $y(x)$ is a polynomial of degree $n$ such that $m_p(x) \equiv y(x) \bmod S_k$ and $d(x)$ is a randomly chosen polynomial of degree $n$.
-This encrypts each coefficient of $m_p(x)$ by adding some multiple of $S_k$ to it.
-Through this process, each bit of the message is encrypted separately.
-
-% Furthermore, the decryption algorithm to recover $m_p(x)$ from a ciphertext polynomial $c(x)$ as
-% \begin{align*}
-% 	m_p(x) = c(x) \bmod S_k \bmod 2.
-% \end{align*}
-% Thus $D(c(x))$ is defined as the integer recovered from the coefficients of the polynomial $c(x) \bmod S_k \bmod 2$.
-
-% Dasgupta and Pal note that homomorphic operations on ciphertext introduce noise which may interfere with decryption, due to the potential increase in ciphertext values.
-% To eliminate noise from a polynomial ciphertext, the following refresh function is used:
-% \begin{align*}
-% 	R(c(x)) = c(x) \bmod R_k.
-% \end{align*}
-
-% \paragraph{Homomorphic Properties of the Dasgupta--Pal Cryptosystem}
-% It has been shown \cite{dasgupta_design_2016} that the following properties hold for all integer messages $m_1, m_2 \in \mathbb{Z}_n$ in the Dasgupta--Pal cryptosystem.
-These properties arise since each coefficient in a ciphertext polynomial is essentially an independently encrypted bit of the original message.
-% \begin{description}
-% 	\item[\textsc{xor} on ciphertexts]
-% 	A bitwise exclusive or (\textsc{xor}) operation on integer messages can be achieved by adding the coefficients pairwise between two ciphertexts.
-% 	\begin{align*}
-% 		D(E(m_1)+E(m_2)) = m_1 \textsc{ xor } m_2
-% 	\end{align*}
-% 	\item[\textsc{and} on ciphertexts]
-% 	Similarly, pair-wise multiplication corresponds to bitwise \textsc{and} of integer messages.
-% 	\begin{align*}
-% 		D(E(a) \otimes E(b)) = a \textsc{ and } b = ab \bmod 2
-% 	\end{align*}
-% 	where $\otimes$ denotes pairwise multiplication,
-% 	\begin{align*}
-% 		\sum_{i=1}^n{a_ix^i} \otimes \sum_{i=1}^n{b_ix^i} = \sum_{i=1}^n{a_ib_ix^i}.
-% 	\end{align*}
-% \end{description}
-
-% Arbitrary computation on data can thus be achived using these bitwise operations.
-While the Dasgupta--Pal cryptosystem requires significant amounts of memory, as each bit of plaintext is encrypted into an integer, this approach provides a flexible method to perform relatively fast arbitrary computation on encrypted data.
-Encryption and decryption in the Dasgupta--Pal cryptosystem are accomplished using few arithmetic operations.
-
-% \subsubsection{HElib and the BGV Cryptosystem}
-The BGV (Brakerski--Gentry--Vaikuntanathan) cryptosystem \cite{cryptoeprint:2011:277} is a fully homomorphic cryptosystem created based on the ring-learning with error problem.
-The BGV cryptosystem was constructed to surpass the limitations of prior fully homomorphic cryptosystems, which were based on the first fully homomorphic cryptosystem by Gentry \cite{gentry_fully_2009}.
-
-The details regarding the construction of the BGV cryptosystem are beyond the scope of this paper.
-For this study, we will be using \textit{HElib} \cite{garay_algorithms_2014}, an open-source library which implements the BGV cryptosystem with optimizations to improve efficiency.
-Evaluation of operations on 120 inputs in HELib was performed in around 4 minutes, with an average of 2 seconds to process a single input \cite{hutchison_fully_2010,cryptoeprint:2011:566}.
-
-The \textit{HElib} library has been adapted to Python using the Pyfhel library \cite{pyfhel_2018} maintained by Ibarrondo, Laurent (SAP) and Onen (EURECOM), and licensed under the GNU GPL v3 license.
-The Pyfhel library is a Python API for the \textit{HElib} library, which supports the following operations on vectors/scalars of integers or binary ciphertexts:
-\begin{itemize}
-	\item Arithmetic operations: addition, subtraction, multiplication;
-	\item Binary operations: \textsc{and}, \textsc{or}, \textsc{not}, \textsc{xor}.
-\end{itemize}
-
-\subsection{CryptoImg}
-A paper published in 2009 by Ziad, et al.
-attempts to implement privacy-preserving image processing using \textit{CryptoImg}, a library for the Open Source Computer Vision Library (OpenCV)~\cite{bradski_opencv_2000} which implements various homomorphic encryption and image processing routines using the Paillier homomorphic cryptosystem~\cite{ziad_cryptoimg:_2016}.
-The CryptoImg library assumed a client-server model wherein a client requests image processing operations from a server.
-A client first encrypts a digital image and sends the image securely to a server, which then operates on the encrypted image without revealing its contents.
-Then the resulting image is sent back to the client, which decrypts the image to recover the desired output.
-\begin{figure}[!ht]
-    \centering
-    \includegraphics[width=0.4\textwidth]{figures/ClientServerModel.png}
-    \caption{Client-server architecture used by \textit{CryptoImg} \cite{ziad_cryptoimg:_2016}}
-    \label{fig:clientserver}
-\end{figure}
-
-The \textit{CryptoImg} library implemented the following:
-\begin{enumerate}
-	\item Extending the Paillier homomorphic cryptosystem which operate on integer plaintexts so that they can operate on real number plaintexts;
-	\item Developing protocols for and implementing the following image processing operations
-	\begin{enumerate}
-		\item Image negation and brightness adjustment
-		\item Spatial filters (for noise reduction, edge detection and sharpening)
-		\item Morphological operations
-		\item Histogram equalization
-	\end{enumerate}
-\end{enumerate}
-For image negation and spatial filters, the protocols specified by \textit{CryptoImg} allow all image processing operations to be performed on the server.
-However, due to limitations in the Paillier cryptosystem, the protocols presented for morphological operations and histogram equalization require both the client and the server to perform image processing calculations, although the server performs a significant portion of the processing.
-
-Ziad, et al.
-also showed experimental results establishing the slow performance of image operations under a homomorphic cryptosystem.
-For instance, while sharpening and applying a Sobel filter each take less than a second when applied to a $512\times 512$ plaintext image, when applied to an encrypted image, sharpening required at least 238.257 seconds, and applying the Sobel filter required at least 147.567 seconds \cite{ziad_cryptoimg:_2016}.
-
-We now discuss several limitations in the \textit{CryptoImg} study which we focus on for our research.
-First, the \textit{CryptoImg} library was limited in the image intensity transformations it implemented.
-We propose additional protocols to support more computationally intensive intensity transformations.
-Second, the \textit{CryptoImg} library only considered the Paillier cryptosystem.
-We consider testing the performance of other homomorphic cryptosystems, which differ in their processing time and supported operations.
-
-\subsection{Image Intensity Transformations}
-We represent a digital image $R$ as an $M \times N$ matrix of pixel intensity values, each value in the range $\left[0, L-1\right]$, for some positive integer $L$.
-We denote with $R(x,y)$ the entry at the $x$th row and $y$th column of a matrix $R$.
-An intensity transformation on an image $R$ can be defined as a function $T$ which maps a pixel value $r$ to a new value $r^\prime$, which we can write as $r^\prime = T\left(r\right)$.
-This function is then applied to every pixel in $R$.
-The \textit{CryptoImg} library implemented two types of linear intensity transformations: image negation and brightness control.
-
-An image negation transformation is defined as:
-\begin{equation}
-    T\left(r\right) = L-1-r
-\end{equation}
-After applying image negation, the resulting image would be similar to a photographic negative~\cite{gonzalez_digital_2008}.
-
-A brightness control transformation with parameter $v$ is defined as:
-\begin{equation}
-    T\left(r,v\right) = r+v
-\end{equation}
-The above transformations are linear in terms of the input $r$, and are thus simple to implement under a homomorphic cryptosystem.
-
-In this study we extend the range of intensity transformations to non-linear transformations.
-Two common non-linear image transformations are the logarithm transformation and power-law transformation~\cite{gonzalez_digital_2008}.
-
-The logarithm transformation is used to enhance dark pixels or increase the dark details of an image by mapping low intensity values to a wider range of values~\cite{gonzalez_digital_2008}.
-This has the general formula
-\begin{equation}
-    T\left(r\right) = c \log\left(1 + r\right)
-\end{equation}
-where $c$ is a constant.
-
-The power-law transformation is a family of transformations that have the form
-\begin{equation}
-    T\left(r\right) = c r^{\gamma}
-\end{equation}
-where $c>0$ and $\gamma > 0$.
-A power-law transformation defined by the above equation can calibrate the operation of many image capture and output devices such as cameras, printers and displays in a process called \textit{gamma correction}.
-% This ensures reproducibility and accuracy of images being displayed by digital output devices~\cite{gonzalez_digital_2008}.
-
-To implement non-linear intensity transformations using addition and multiplication in a homomorphic system, it is necessary to approximate the logarithm and exponential functions, which may result in higher computational overhead.
-In our software library implementation, we investigate methods required to approximate the logarithm and power functions.
-Non-linear intensity transformations such as the logarithm transformation have applications in intensity normalization \cite{oravec_illumination_2010}, which is used in some facial recognition algorithms to account for differences in lighting which make facial recognition difficult.
-
-\subsection{Facial Detection and Recognition}
-
-Since simple image operations mentioned earlier can be done within a homomorphic cryptosystem, these operations can be assembled together in order to do more complex operations.
-A prominent application of image processing that often uses complex image operations is \textit{facial recognition}.
-
-Traditional facial recognition algorithms rely on detecting salient features in a face image. One of the popular facial recognition algorithms is \textit{eigenfaces}.
-% Traditional facial recognition algorithms rely on detecting salient features in a face image. Two of the popular facial recognition algorithms are \textit{eigenfaces} and \textit{Haar cascades}.
-
-\subsubsection{Eigenfaces}
-Proposed by Matthew Turk and Alex Pentland, the eigenfaces method uses principal component analysis (PCA) in order to express an input image as a linear combination of eigenfaces \cite{turk_eigenfaces_1991}.
-An \textit{eigenface} is a principal component, or more simply an eigenvector that represents a certain variation between the face images which are taken from the initial training set.
-The number of resulting eigenfaces is equal to the number of face images in the training set.
-
-% In the enrollment process, $M$ face images $\Theta_1, \ldots, \Theta_M$, each of size $p \times q$, are taken in to comprise the initial training set.
-The training images can be represented as vectors of length $N = pq$, where each row of an image is concatenated together.
-
-% The average of the training images, denoted as $\Psi$, is 
-% \begin{equation}
-% 	\Psi = \frac{1}{M} \sum_{i=1}^{M} \Theta_i
-% \end{equation}
-
-% The \textit{difference vectors} are then computed as $\Phi_i = \Theta_i - \Psi$. PCA is applied on the covariance matrix of the vectors
-% \begin{equation}
-% 	\mathbf{C} = \frac{1}{M} \sum_{i=1}^M \Phi_i \Phi_i^\top = \frac{1}{M} \mathbf{A}\mathbf{A}^\top,
-% \end{equation}
-% where $\mathbf{A}$ is an $N \times M$ matrix defined by $\left[\Theta_1 \quad \Theta_2 \quad \cdots \quad \Theta_M\right]$, in order to determine the orthonormal eigenvectors \cite{hutchison_privacy-preserving_2009}.
-
-% Directly computing the covariance matrix and then applying PCA will become inefficient for large sizes of $\mathbf{A}$, since computing for $\mathbf{A}\mathbf{A}^\top$ results in an $N \times N$ matrix, which can get drastically large because it is dependent on the size of the image.
-On the other hand, computing for $\mathbf{A}^\top\mathbf{A}$ only results in an $M \times M$ matrix, which is much smaller than the previous one because it is just dependent on the number of face images in the training set.
-Now, we can apply PCA to $\mathbf{A}^\top\mathbf{A}$ along with some post-processing to obtain the eigenvectors \cite{hutchison_privacy-preserving_2009}.
-
-% Instead of getting the eigendecomposition of the covariance matrix by explicitly computing the eigenvalues and eigenvectors of $\mathbf{C}$, we can also apply \textit{singular value decomposition} (SVD) on the matrix $\Phi^\top$.
-This is because SVD works through a divide-and-conquer method which results in greater numerical stability, while eigendecomposition simply uses the traditional QR factorization \cite{nakatsukasa_stable_2013, gu_divide-and-conquer_1995}.
-Upon applying SVD, we now get the eigenvectors $\mathbf{u}_1, \ldots, \mathbf{u}_M$ and their corresponding eigenvalues $\lambda_1, \ldots, \lambda_M$.
-
-% We choose $K$ eigenvectors $\mathbf{u}_1, \ldots, \mathbf{u}_K$ such that it comprises a set associated with the $K$ largest eigenvalues, where $K$ is much smaller than $M$.
-This set is now the \textit{face space}.
-Then, the images $\Theta_1, \ldots, \Theta_K$ are projected onto the face space spanned by the eigenfaces to determine the weight vectors $\Omega_1, \ldots, \Omega_K$.
-
-% To perform the recognition process, the algorithm projects the input image $\Gamma$ onto the face space, and then comparing the projected image $\bar{\Omega} = \mathbf{u}_i\left(\Gamma - \Psi\right)$ with each eigenface in the face space using a metric such as the Euclidean distance.
-Thus it is computed as $d_i = \left\lVert \Omega_i -\bar{\Omega} \right\rVert$ for all $i=1,\ldots,K$, where $\left\lVert \cdot \right\rVert$ denotes the Euclidean norm.
-
-% Then, a match can be reported if the smallest possible distance is smaller than the given threshold value $T$. 
-% \newcommand{\argmin}{\mathop{\mathrm{arg\,min}}}  
-% \begin{equation}
-% 	\text{ID} = \begin{cases}\argmin_i d_i & \text{if } \min_i d_i \le T \\\emptyset & \text {otherwise}\end{cases}
-% \end{equation}
-
-\subsection{Previous Implementations of Secure Facial Recognition}
-Erkin, et al.
-\cite{hutchison_privacy-preserving_2009} devised a method to incorporate the use of homomorphic cryptosystems into the eigenfaces method.
-In their study, they proposed a two-party system where Alice holds an encrypted image $\left[\Gamma\right]$, while Bob maintains a database of $K$ eigenfaces $\mathbf{u}_1, \ldots, \mathbf{u}_K$, and feature vectors $\Omega_1, \ldots, \Omega_M$ in the clear.
-
-\begin{figure}[!h]
-    \centering
-    \includegraphics[width=0.4\textwidth]{figures/secure_eigenfaces.png}
-    \caption{Diagram of the privacy-preserving facial recognition process \cite{hutchison_privacy-preserving_2009}}
-\end{figure}
-
-In order to ensure privacy, the steps in the eigenfaces algorithm, namely: projection, distance computation, and match finding, are done within the encrypted domain, i.e., using the operations in the Paillier cryptosystem.
-
-Projection is similar to that of the original eigenfaces algorithm, except the operations are replaced with their respective operations in the cryptosystem.
-Distance computation in this version is somewhat different from the original eigenfaces method, in that it deals with the square of the Euclidean distance since the relative order of the distances is only important when comparing these during the match finding step \cite{hutchison_privacy-preserving_2009}.
-\begin{align}
-    d_i &= \left\lVert \Omega_i - \bar{\Omega} \right\rVert ^2 = \sum_{j=1}^{K} \left(\omega_{ij} - \bar{\omega}_j\right)^2 \\
-        &= \underbrace{\sum_{j=1}^{K} \omega_{ij}^2}_{\mathcal{S}_1} + \underbrace{\sum_{j=1}^{K} \left(-2 \omega_{ij} \bar{\omega_j}\right)}_{\mathcal{S}_2} + \underbrace{\sum_{j=1}^{K} \bar{\omega}_{j}^2}_{\mathcal{S}_3}
-\end{align}
-
-Computing for the distances within Paillier would just be multiplying the encrypted sums together.
-\begin{equation}
-	\left[d_i\right] = \left[\mathcal{S}_1\right] \cdot \left[\mathcal{S}_2\right] \cdot \left[\mathcal{S}_3\right]
-\end{equation}
-
-The terms $\left[\mathcal{S}_1\right]$ and $\left[\mathcal{S}_2\right]$ can be easily computed by Bob, since he already knows both $\omega_i$ in the clear and $\left[\bar{\omega}_i\right]$ which is in encrypted form.
-Computing for $\left[\mathcal{S}_3\right]$ is trickier because Bob cannot compute for $\left[\bar{\omega}_i^2\right]$ because pairwise multiplication is not supported in Paillier, that is why Bob needs help from Alice to square a number through a protocol described below \cite{hutchison_privacy-preserving_2009}.
-
-Before Bob sends $\left[\bar{\omega}_i\right]$ to Alice for squaring, he adds a random number $r_i$ to compute $\left[x_i\right] = \left[\bar{\omega}_i + r_i\right] = \left[\bar{\omega}_i\right] \cdot \left[r_i\right]$, where $r_i$ is obviously distinct for every $i$, then sends $\left[x_i\right]$ to Alice.
-She then decrypts it and computes $x_i^2$, and then computes $\mathcal{S}_3^\prime = \sum_{i=1}^{K} x_i^2$, after which she encrypts the sum and sends $\left[\mathcal{S}_3^\prime\right]$ to Bob.
-Now, he can compute for $\left[\mathcal{S}_3\right]$ as follows:
-\begin{equation}
-	\left[\mathcal{S}_3\right] = \left[\mathcal{S}_3^\prime\right] \cdot \prod_{j=1}^{K} \left(\left[\bar{\omega}_j\right]^{-2r_j} \cdot \left[-r_j^2\right]\right)
-\end{equation}
-
-The protocol for squaring a number as described earlier is a workaround for the limitations of Paillier or any other partially homomorphic cryptosystem that only supports addition and scalar multiplication.
-% This can be possibly extended so that operations such as pairwise multiplication and exponentiation are also supported, provided that the protocol involves two parties.
-
-The match finding step is done by comparing the distances obtained from the previous step to a specified threshold $T$.
-If the minimum distance is smaller than $T$, then a match is found, and the encrypted identity of the match is returned to Alice \cite{hutchison_privacy-preserving_2009}.
-Getting the minimum among the encrypted distances would involve comparing two encrypted numbers, which Paillier does not support.
-Instead, the DGK cryptosystem \cite{pieprzyk_efficient_2007} is used for the comparison protocol.
-
-\section{Methodology}
-In this study we apply three homomorphic encryption schemes~\cite{ziad_cryptoimg:_2016, pieprzyk_efficient_2007, garay_algorithms_2014} for use in image processing and facial recognition applications.
-In particular, the study consists of the following:
-\begin{itemize}
-	\item Creating a wrapper library that acts as a unified interface which implements the Paillier, DGK, and BGV homomorphic cryptosystems.
-	\item An implementation of image processing operations (intensity transformations, facial recognition) under the above cryptosystems.
-	\item Conducting tests for image quality, processing time, using images from the \texttt{faces94} dataset.
-\end{itemize}
-
-% While the Paillier and DGK cryptosystems have been implemented for use in image processing in~\cite{ziad_cryptoimg:_2016, hutchison_privacy-preserving_2009}, the other cryptosystems have to be adapted for this study.
-% Two experiments are conducted in this study:
-% \begin{enumerate}
-% 	\item Assessment of non-linear image intensity transformations under each of the three cryptosystems.
-% 	\item Assessment of efficiency of each of the four cryptosystems when applied for use in privacy-preserving facial recognition and detection using eigenfaces.
-% \end{enumerate}
-% The results of the image intensity transformations are tested for image quality using benchmarks in~\cite{ahmed_benchmark_2016}.
-
-\subsection{Cryptosystem Implementation}
-Three homomorphic encryption schemes are investigated, and a wrapper library was created in Python that integrates these cryptosystems into a unified interface.
-\begin{itemize}
-	\item The Paillier cryptosystem is incorporated using the python-paillier library at \url{https://github.com/n1analytics/python-paillier} developed by Data61 - CSIRO.
-	\item The DGK cryptosystem is ported from the C++ implementation at \url{https://github.com/encryptogroup/ENCRYPTO_utils}, developed by Daniel Demmler from EC-SPRIDE.
-	\item The BGV cryptosystem is implemented using the Pyfhel library (\url{https://github.com/ibarrond/Pyfhel}) using a HElib backend from (\url{https://github.com/shaih/HElib}).
-\end{itemize}
-
-\subsubsection{Extension of Partially Homomorphic Cryptosystems}
-\label{sssec:pheextension}
-In order to use Paillier and DGK for secure image processing, we require the two schemes to support the encryption of floating-point (FP)numbers, as well as multiplication and division of arbitrary ciphertexts.
-We extend the two cryptosystems to FP operations by using an approach shown in~\cite{ziad_cryptoimg:_2016}.
-This approach represents FP numbers using a pair $(m,e)$, where $m$ represents the mantissa (which is encrypted), and $e$ represents the exponent (which is not encrypted).
-This approach is also used by the python-paillier library.
-This represntation allows us to extend the addition and plaintext multiplication homomorphisms of the Paillier and DGK cryptosystems to floating-point numbers.
-
-Various two-party protocols can be used to facilitate ciphertext multiplication and division.
-These allow a server armed with only knowledge of the public key, to obtain the product and quotient of ciphertexts, by communicating with the client, who has the private key.
-For division, we use the protocol defined in~\cite{boukoros_lightweight_2017}: to obtain $E(x/y)$ from $E(x)$ and $E(y)$, the server sends $E(rx)$ and $E(ry)$ to the client, (where $r$ is a random non-zero number), allowing the client to compute $E(rx/ry)$ and give the result back to the server.
-
-For multiplication, we adapt the protocol to calculate Euclidean distances used in \cite{hutchison_privacy-preserving_2009}, which provides a two-party protocol which yields $E(x^2)$ given $E(x)$.
-We use this protocol together with the additive homomorphism of the partially homomorphic cryptosystems to instead compute $E((x + y)^2 - x^2 - y^2) = E(2xy)$, from which we can easily obtain $E(xy)$ through plaintext multiplication.
-
-% [TO-DO: This is further explained in another paper.]
-% We will briefly discuss a protocol to enable cryptosystems built for integer inputs to handle real number inputs.
-% The following protocol was also used by \textit{CryptoImg} for image processing \cite{ziad_cryptoimg:_2016}.
-% This is also used for our own implementation of the Dasgupta--Pal cryptosystem in order to handle real numbers.
-
-% We represent a floating-point (FP) number as a pair of two integers $(m,e)$ representing the mantissa and exponent of the FP number with respect to a base $b$.
-The mantissa $m$ is encrypted, while the exponent $e$ is unencrypted.
-% Let $a,b,c$ be FP numbers represented by the pairs $(m_a,e_a),(m_b,e_b),(m_c,e_c)$ respectively.
-Let $\oplus,\otimes$ represent the homomorphic operations which correspond to the addition and multiplication, respectively.
-We define the secure real number operations as follows:
-% \begin{description}
-%   \item[Addition.]
-%     To compute $E(c)=E(a+b)$ we compute
-%     \begin{align*}
-%       E(m_c) &= E(m_1) \oplus (b^{e_b-e_a} \otimes E(m_b)), e_c = e_a & \text{ if } e_a \leq e_b \\
-%       E(m_c) &= E(m_b) \oplus (b^{e_a-e_b} \otimes E(m_a)), e_c = e_b & \text{ if } e_a > e_b
-%     \end{align*}
-%   \item[Scalar multiplication.]
-%     To compute $E(c) = E(ab)$, where $a$ and $E(b)$ are known (i.e. $m_a$ is not encrypted), we compute
-%     \begin{align*}
-%       E(m_c) &= m_a \otimes E(m_b)\\
-%       e_c &= e_a + e_b
-%     \end{align*}
-% \end{description}
-
-\subsection{Non-Linear Intensity Transformations}
-We will implement library functions for image negation, logarithm transformation and power-law transformation, as they are defined in~\cite{gonzalez_digital_2008}.
-We now describe how we implement the logarithm and power-law image intensity transformations.
-In the case of partially homomorphic cryptosystems (Paillier, DGK), if ciphertext multiplication or division is required, the secure protocols in section \ref{sssec:pheextension} will be used.
-
-\subsubsection{Logarithm Transformation}
-The logarithm transformation of a pixel intensity value $x$ is defined as
-\begin{align}
-	T\left(x\right) = c \log\left(1 + x\right)
-\end{align}
-where $c$ is a constant.
-
-In order to perform this transformation under Paillier and DGK, we provide the following closed-form approximation for $\log\left(1 + x\right)$.
-% TODO: IDK HOW TO CITE OUR PCSC PAPER
-\begin{align}\label{eq:optimal_log_approximation}
-	\begin{split}
-		&\log\left(1+x\right) \approx \frac{a(x)}{b(x)} + \log{16}
-	\end{split}
-\end{align}
-where
-\begin{align*}
-	\begin{split}
-	a(x) &= 137x^5 + 26685x^4 + 617370x^3 - 6498630x^2 \\
-	&- 121239315x - 257804775\\
-	b(x) &= 30(x^5 + 405x^4 + 27210x^3 + 488810x^2 + 2536005x \\
-	&+ 3122577).
-	\end{split}
-\end{align*}
-% \begin{align}\label{eq:optimal_log_approximation}
-% 	\begin{split}
-% 		&\log\left(1+x\right) \\
-% 		&\approx \frac{137x^5 + 26685x^4 + 617370x^3 - 6498630x^2 - 121239315x - 257804775}
-% 		{30(x^5 + 405x^4 + 27210x^3 + 488810x^2 + 2536005x + 3122577)}\\
-% 		&+ \log{16}.
-% 	\end{split}
-% \end{align}
-
-\subsubsection{Power-Law Transformation}
-The power-law transformation of a pixel intensity value $x$ is defined as
-\begin{equation}
-    T\left(x\right) = cx^{\gamma}
-\end{equation}
-where $c>0$ and $\gamma > 0$.
-
-Similar to the logarithm transformation, to apply this transformation using Paillier and DGK, we must provide an approximation for $x^\gamma$.
-We can use partial sums of the following series, which relies on the logarithm function.
-\begin{align}
-	x^\gamma &= \sum_{n=0}^{\infty}{\frac{(\gamma\log{x})^n}{n!}}
-\end{align}
-% Partial sums of the above infinite series can be calculated based on the closed form approximation for the logarithm in Equation \ref{eq:scaledquadraturech3}. 
-For the implementation of the power-law transformation for this paper, a partial sum consisting of the first five terms of the infinite series were used.
-
-\subsection{Assessment of Homomorphic Encryption Schemes}
-A laptop computer with a 2.5 GHz Intel Core i7 quad-core processor and 8 GB of RAM is used to perform the computations, and processing time was tracked using built-in timing functions.
-The processing time for all cases were recorded.
-All of the tests are done using Python 3.7.1 running on Linux.
-
-\subsubsection{Image Quality of Intensity Transformations}
-In this section, we discuss the image quality metrics we used for assessing the performance of non-linear intensity transformations.
-
-We first obtained test images from the \texttt{faces94} dataset (\url{https://cswww.essex.ac.uk/mv/allfaces/faces94.html}) maintained by the University of Essex.
-However, only ten distinct facial images from the dataset were selected for the purposes of this test.
-Since only grayscale images are used in the study, the images were converted to grayscale and then downsampled to $40 \times 36$ pixels.
-
-For each cryptosystem, three image operations are tested:
-\begin{enumerate}
-	\item Image negation
-	\item Logarithm transformation, with $c = 30$
-	\item Power-law transformation, with $c = 1$ and $\gamma = 0.4$
-\end{enumerate}
-
-For each plaintext image (PT), we considered each image operation listed above and generate three images: a plaintext domain transformation (PDT), a ciphertext image (CT), and an ciphertext domain transformation (CDT).
-The PDT was generated by running the image operation on the original image.
-The CT was generated by encrypting the image, then applying the operation, and the CDT was generated by decrypting the CT.
-The four images (PT, PDT, CT, CDT) were then compared using various benchmarks to evaluate the quality and security of each homomorphic encryption scheme.
-
-The benchmarks to be used in the study, adopted from~\cite{ahmed_benchmark_2016, ahmad_efficiency_2012, wu_npcr_2011} are listed below.
-We let $X_i$ denote a value in an image $X$, where $1 \leq i \leq N$.
-We first perform three tests to ascertain the preservation of image quality after encryption and decryption: MSE, PSNR, and SSIM.
-\begin{description}
-	\item [Mean Squared Error (MSE).] The MSE is defined in~\cite{ahmed_benchmark_2016} as
-	\begin{align}
-        \mathrm{MSE} = \frac{1}{N}\sum_{i=1}^{N}{(\mathrm{CDT}_i - \mathrm{PDT}_i)^2}.
-	\end{align}
-	The MSE provides a measure of how much data is recovered if an image operation is applied on the encrypted image, which is then decrypted.
-Lower values of MSE indicate higher preservation of image quality~\cite{ahmed_benchmark_2016, ahmad_efficiency_2012}.
-	\item [Peak Signal to Noise Ratio (PSNR).]
-	According to Ahmed, et al.~\cite{ahmed_benchmark_2016}, PSNR is ``an estimator for human visual perception of reconstruction quality.'' It has been used to ascertain image quality in various studies and is a known metric for image and video quality~\cite{upmanyu_efficient_2009, jain_image_2016, akramullah_video_2014}.
-Although it may produce results which do not correlate with human visual perception~\cite{huynh-thu_accuracy_2012, ahmed_benchmark_2016}, it is a valid indicator of image quality when media containing the same visual content is compared~\cite{huynh-thu_accuracy_2012}.
-	PSNR is defined by
-	\begin{align}
-        \mathrm{PSNR} = 10\log_{10}{\left( \frac{L^2}{\mathrm{MSE}} \right)}
-	\end{align}
-	where $L$ is the maximum pixel intensity value of an image.
-	Despite the known limitations of PSNR, since we are going to compare the effect of each encryption scheme on recovered image quality, given a fixed library of images, it is a valid measure of image quality for the study.
-A higher PSNR indicates higher image quality preservation.
-	\item [Structural Similarity Index (SSIM).]
-	The SSIM for two random variables $X$ and $Y$ is defined in~\cite{ahmed_benchmark_2016, akramullah_video_2014} as
-	\begin{align}
-        \mathrm{SSIM}(X,Y) = \frac{(2\mu_X\mu_Y+c_1)(2\sigma_{XY}+c_2)}{(\mu_X^2+\mu_Y^2+c_1)(\mu_X^2+\mu_Y^2+c_2)}
-	\end{align}
-	where
-	\begin{itemize}
-		\item $\mu_X, \mu_Y$ are the averages of $X$ and $Y$, respectively;
-		\item $\sigma_X, \sigma_Y$ are the variances of $X$ and $Y$, respectively;
-		\item $\sigma_{XY}$ is the covariance of $X$ and $Y$;
-		\item $c_1 = (k_1L)^2, c_2 = (k_2L)^2$ are two variables used to stabilize the measure when $\mu_X^2+\mu_Y^2$ is close to zero~\cite{akramullah_video_2014};
-		\item $L$ is the the maximum pixel intensity value of an image;
-		\item $k_1 = 0.01, k_2 = 0.03$ by default, given in~\cite{ahmed_benchmark_2016}.
-	\end{itemize}
-	The SSIM is applied to the luminance value of two images to gauge structural similarity between neighboring pixels.
-	For the study, we computed $\mathrm{SSIM}(\mathrm{PDT}, \mathrm{CDT})$ for every image operation, under each homomorphic cryptosystem.
-Higher values of SSIM indicate higher structural similarity, and an SSIM of $1$ indicates that the two images are identical~\cite{ahmed_benchmark_2016}.
-\end{description}
-
-Computing for MSE, PSNR, and SSIM was done using the corresponding built-in functions from the scikit-image Python library \cite{scikit-image}.
-
-\subsubsection{Facial Recognition Tests}
-The method for secure facial recognition using eigenfaces by Erkin, et al. \cite{hutchison_privacy-preserving_2009} was implemented for this study.
-
-As before, training and test data were also secured from the \texttt{faces94} dataset. The images were first converted to grayscale but it is not downsampled, unlike in the previous test.
-
-The facial recognition tests are done using ten-fold cross-validation for each cryptosystem, where the number of principal components used by the algorithm is fixed at $K=5$.
-
-Prior to splitting the dataset, the images within each set are shuffled.
-Since there are twenty (20) images per set, two images are taken at a time for each round of cross-validation.
-The first round would take the first two images from each set as part of the test set, and the rest of the images will be part of the training set.
-Then, the succeeding round would take the next two images from each set as part of the test set, and so on until ten rounds have been done.
-After every round of cross-validation, the accuracy score, confusion matrix, and total processing time are obtained.
-
-%% Summary not needed, this was only important for the thesis proposal - Aldrich
-% \subsection{Summary}
-% In summary, the study consists of:
-% \begin{itemize}
-% 	\item Creating a wrapper library that acts as a unified interface which implements the Paillier, DGK, Dasgupta--Pal, and BGV homomorphic cryptosystems.
-% 	\item An implementation of image processing operations (intensity transformations, facial recognition) under the above cryptosystems.
-% 	\item Conducting tests for image quality, processing time, using images from the \texttt{faces94} dataset.
-% \end{itemize}
-
-\section{Preliminary Results and Discussion}
-The results shown in this section are gathered from the tests for intensity transformations under Paillier and Dasgupta--Pal cryptosystems.
-During testing, initial results obtained from BGV, particularly with image operations involving floating-point numbers like the logarithmic transformation, were unstable (i.e.
-the results vary drastically every time the same tests were done).
-This is because the Pyfhel library being used for the BGV cryptosystem is still in alpha development stage \cite{pyfhel_2018}.
-
-% One of the authors has already informed the maintainers of the library about a bug involving exponentiation of two real numbers.
-
-\subsection{Intensity Transformations}
-
-\begin{table*}
-	\centering
-	\caption{Comparison of intensity transformations under Paillier}
-	\label{tbl:it-pal}
-	\begin{tabular}{m{1cm}*{7}{>{\centering\arraybackslash}m{1.75cm}}}
-		\toprule
-		\multirow{2}{*}{Image} & \multirow{2}{*}{Original} & \multicolumn{2}{c}{Image negation} & \multicolumn{2}{c}{Logarithm transformation} & \multicolumn{2}{c}{Power-law transformation} \\
-							   &                           & PDT           & CDT          & PDT            & CDT           & PDT               & CDT           \\ 
-		\midrule
-		\xintForpair #1#2 in {(anpage,a), (bplyce,b), (drbost,c), (ksunth,d), (martin,e), (pmives,f), (rnpwil,g), (sbains,h), (swewin,i), (yfhsie,j)} \do {%
-		(#2) & \includegraphics[width=1.75cm]{out_faces/paillier_negate_#1_original.png} & \includegraphics[width=1.75cm]{out_faces/paillier_negate_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/paillier_negate_#1_decrypted.png} & \includegraphics[width=1.75cm]{out_faces/paillier_logtransform_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/paillier_logtransform_#1_decrypted.png} & \includegraphics[width=1.75cm]{out_faces/paillier_pwrtransform_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/paillier_pwrtransform_#1_decrypted.png} \\ }%
-		\bottomrule         
-	\end{tabular}
-\end{table*}
-
-\begin{table*}
-	\centering
-	\caption{Comparison of intensity transformations under Dasgupta--Pal}
-	\label{tbl:it-dp}
-	\begin{tabular}{m{1cm}*{7}{>{\centering\arraybackslash}m{1.75cm}}}
-		\toprule
-		\multirow{2}{*}{Image} & \multirow{2}{*}{Original} & \multicolumn{2}{c}{Image negation} & \multicolumn{2}{c}{Logarithm transformation} & \multicolumn{2}{c}{Power-law transformation} \\
-							   &                           & PDT           & CDT          & PDT            & CDT           & PDT               & CDT           \\ 
-		\midrule
-		\xintForpair #1#2 in {(anpage,a), (bplyce,b), (drbost,c), (ksunth,d), (martin,e), (pmives,f), (rnpwil,g), (sbains,h), (swewin,i), (yfhsie,j)} \do {%
-		(#2) & \includegraphics[width=1.75cm]{out_faces/dp_negate_#1_original.png} & \includegraphics[width=1.75cm]{out_faces/dp_negate_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/dp_negate_#1_decrypted.png} & \includegraphics[width=1.75cm]{out_faces/dp_logtransform_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/dp_logtransform_#1_decrypted.png} & \includegraphics[width=1.75cm]{out_faces/paillier_pwrtransform_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/dp_pwrtransform_#1_decrypted.png} \\ }%
-		\bottomrule
-	\end{tabular}
-\end{table*}
-
-Table~\ref{tbl:it-pal} shows the images obtained from the intensity transformation tests under the Paillier cryptosystem, while Table~\ref{tbl:it-dp} shows the resulting images from the same tests under the Dasgupta--Pal cryptosystem.
-Shown for each image is the original unecrypted image, and for each intensity transformation the \textit{plaintext domain transformation} (PDT) is given which is the resulting image after applying the transformation to the unencrypted image and the \textit{ciphertext domain transformation} (CDT) is the decrypted image of the processed encrypted image.
-
-The following tables show the resulting metric scores for mean squared error (MSE), peak signal to noise ratio (PSNR), and structural similarity index (SSIM), as well as time taken (in seconds) for encrypting the input image ($t_\text{enc}$), applying an operation to the encrypted image ($t_\text{apply}$), and decrypting the resulting encrypted image ($t_\text{dec}$), for each image in the test set.
-Tables~\ref{tbl:neg-pal} and~\ref{tbl:neg-dp} show the results obtained from applying image negation, Tables~\ref{tbl:log-pal} and~\ref{tbl:log-dp} from applying logarithm transformation, and Tables~\ref{tbl:pwr-pal} and~\ref{tbl:pwr-dp} from applying power-law transformation.
-
-\subsubsection{Image Negation}
-Both the Paillier and Dasgupta--Pal cryptosystems were able to perform image negation under the encrypted domain without introducing noise in the resulting image.
-In other words, the resulting image from doing image negation on an image on the clear and doing image negation under the encrypted domain are identical, as evidenced by the mean squared errors being exactly equal to zero, the PSNR being infinite, and the SSIM being exactly equal to one.
-
-The Paillier cryptosystem performed better in terms of time, only taking about 0.01 seconds to apply image negation.
-On the other hand, the Dasgupta--Pal cryptosystem took about 22 seconds each to apply the same operation, which is expected since the implementation for Dasgupta--Pal was done in Python without using any external libraries.
-
-\begin{table}[h]
-	\centering
-	\caption{Image negation under Paillier}
-	\label{tbl:neg-pal}
-    \begin{tabular}{lcccccc}
-        \toprule
-        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
-        (a) & 0.000 & $\infty$ & 1.00000 & 0.128 & 0.013 & 0.041 \\
-		(b) & 0.000 & $\infty$ & 1.00000 & 0.084 & 0.013 & 0.024 \\
-		(c) & 0.000 & $\infty$ & 1.00000 & 0.099 & 0.012 & 0.031 \\
-		(d) & 0.000 & $\infty$ & 1.00000 & 0.109 & 0.012 & 0.048 \\
-		(e) & 0.000 & $\infty$ & 1.00000 & 0.117 & 0.015 & 0.043 \\
-		(f) & 0.000 & $\infty$ & 1.00000 & 0.111 & 0.012 & 0.025 \\
-		(g) & 0.000 & $\infty$ & 1.00000 & 0.099 & 0.012 & 0.023 \\
-		(h) & 0.000 & $\infty$ & 1.00000 & 0.084 & 0.012 & 0.024 \\
-		(i) & 0.000 & $\infty$ & 1.00000 & 0.089 & 0.012 & 0.023 \\
-		(j) & 0.000 & $\infty$ & 1.00000 & 0.081 & 0.012 & 0.029 \\
-		\bottomrule
-    \end{tabular}
-\end{table}
-\begin{table}[h]
-	\centering
-	\caption{Image negation under Dasgupta--Pal}
-	\label{tbl:neg-dp}
-    \begin{tabular}{lcccccc}
-        \toprule
-        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
-		(a) & 0.000 & $\infty$ & 1.00000 & 0.221 & 30.217 & 0.239 \\
-		(b) & 0.000 & $\infty$ & 1.00000 & 0.190 & 30.919 & 0.216 \\
-		(c) & 0.000 & $\infty$ & 1.00000 & 0.284 & 31.182 & 0.268 \\
-		(d) & 0.000 & $\infty$ & 1.00000 & 0.225 & 32.581 & 0.223 \\
-		(e) & 0.000 & $\infty$ & 1.00000 & 0.220 & 32.220 & 0.271 \\
-		(f) & 0.000 & $\infty$ & 1.00000 & 0.287 & 31.224 & 0.294 \\
-		(g) & 0.000 & $\infty$ & 1.00000 & 0.285 & 29.478 & 0.284 \\
-		(h) & 0.000 & $\infty$ & 1.00000 & 0.186 & 29.784 & 0.362 \\
-		(i) & 0.000 & $\infty$ & 1.00000 & 0.243 & 38.407 & 0.220 \\
-		(j) & 0.000 & $\infty$ & 1.00000 & 0.285 & 29.488 & 0.449 \\		
-		\bottomrule
-        \end{tabular}
-\end{table}
-
-\subsubsection{Logarithm Transformation}
-Unlike image negation, logarithm transformation involves more operations, so the increase in processing time for both cryptosystems are expected.
-Applying the logarithm transformation under Paillier took about 2 seconds per image, while it took about 13.5 minutes each under Dasgupta--Pal.
-
-The logarithm transformation under Dasgupta--Pal turned out to be more accurate than Paillier, whose mean squared errors approach zero and the SSIM values approach one for every image as shown in Table~\ref{tbl:log-dp}.
-Although the results from using Paillier show that it is also accurate enough with the mean squared errors being less than 30 and the SSIM values average to 0.99, Dasgupta--Pal has been able to produce an almost identical result to that of the plaintext domain transformation counterparts.
-This observation is rather unexpected, considering that the implementation used for Paillier is more robust (due to its use of external C/C++ libraries which makes computations faster).
-
-\begin{table}[h]
-	\centering
-	\caption{Logarithm transformation under Paillier}
-	\label{tbl:log-pal}
-    \begin{tabular}{lcccccc}
-        \toprule
-        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
-		(a) & 13.369 & 36.870 & 0.99263 & 0.085 & 1.813 & 0.023 \\
-		(b) & 7.072 & 39.635 & 0.99017 & 0.089 & 2.073 & 0.023 \\
-		(c) & 8.151 & 39.019 & 0.98688 & 0.091 & 1.913 & 0.023 \\
-		(d) & 25.253 & 34.108 & 0.98927 & 0.089 & 1.919 & 0.023 \\
-		(e) & 10.374 & 37.971 & 0.98695 & 0.106 & 1.829 & 0.023 \\
-		(f) & 2.426 & 44.283 & 0.99401 & 0.127 & 1.900 & 0.023 \\
-		(g) & 5.184 & 40.985 & 0.98971 & 0.096 & 1.853 & 0.023 \\
-		(h) & 16.772 & 35.885 & 0.98492 & 0.081 & 1.746 & 0.024 \\
-		(i) & 5.803 & 40.494 & 0.99241 & 0.091 & 1.827 & 0.027 \\
-		(j) & 12.192 & 37.270 & 0.99354 & 0.081 & 1.815 & 0.023 \\
-		\bottomrule
-        \end{tabular}
-\end{table}
-\begin{table}[h]
-	\caption{Logarithm transformation under Dasgupta--Pal}
-	\label{tbl:log-dp}
-    \begin{tabular}{lcccccc}
-        \toprule
-        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
-		(a) & 0.004 & 71.624 & 0.99999 & 0.287 & 802.957 & 0.036 \\
-		(b) & 0.000 & 82.043 & 1.00000 & 0.190 & 815.384 & 0.048 \\
-		(c) & 0.004 & 72.480 & 1.00000 & 0.270 & 813.640 & 0.036 \\
-		(d) & 0.000 & 87.372 & 1.00000 & 0.204 & 804.629 & 0.047 \\
-		(e) & 0.001 & 77.421 & 1.00000 & 0.245 & 822.940 & 0.036 \\
-		(f) & 0.001 & 76.934 & 1.00000 & 0.194 & 814.132 & 0.036 \\
-		(g) & 0.000 & 83.135 & 1.00000 & 0.197 & 808.503 & 0.047 \\
-		(h) & 0.001 & 77.301 & 1.00000 & 0.270 & 809.406 & 0.047 \\
-		(i) & 0.006 & 70.004 & 0.99999 & 0.268 & 813.217 & 0.051 \\
-		(j) & 0.001 & 78.576 & 1.00000 & 0.243 & 830.640 & 0.039 \\
-		\bottomrule
-        \end{tabular}
-\end{table}
-
-\subsubsection{Power-Law Transformation}
-Applying the power-law transformation under both cryptosystems produced less than accurate images.
-The accuracy varies greatly across all the images as in the case of Paillier, with mean squared errors as high as 8270.696 and as low as 616.419, and SSIM scores ranging from 0.43185 to 0.92334, as seen in Table~\ref{tbl:pwr-pal}.
-As expected, the total processing time now takes about 15 to 20 seconds per image since the power-law transformation is more computationally intensive due to its approximation of an infinite series consisting of terms using the logarithm function, which is also approximated using a combination of addition and multiplication operations.
-
-\begin{table}[h]
-	\centering
-	\caption{Power-law transformation under Paillier}
-	\label{tbl:pwr-pal}
-    \begin{tabular}{lcccccc}
-        \toprule
-        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
-        (a) & 3910.678 & 12.208 & 0.46712 & 0.099 & 14.695 & 0.024 \\
-		(b) & 873.064 & 18.720 & 0.84379 & 0.139 & 16.190 & 0.023 \\
-		(c) & 1261.059 & 17.123 & 0.77229 & 0.082 & 13.866 & 0.023 \\
-		(d) & 653.049 & 19.981 & 0.90673 & 0.083 & 15.507 & 0.023 \\
-		(e) & 646.310 & 20.026 & 0.88157 & 0.108 & 15.727 & 0.045 \\
-		(f) & 2047.933 & 15.018 & 0.69408 & 0.113 & 14.728 & 0.034 \\
-		(g) & 806.473 & 19.065 & 0.85346 & 0.082 & 14.253 & 0.024 \\
-		(h) & 616.419 & 20.232 & 0.92334 & 0.121 & 14.415 & 0.023 \\
-		(i) & 8270.696 & 8.955 & 0.43185 & 0.112 & 14.362 & 0.065 \\
-		(j) & 1715.478 & 15.787 & 0.73857 & 0.145 & 20.239 & 0.023 \\
-		\bottomrule
-        \end{tabular}
-\end{table}
-
-When Dasgupta--Pal was used in the power-law transformation, it completely failed to produce a discernible image and only resulted in a blank image.
-The mean squared errors for this case is an order of magnitude higher than the results from using Paillier.
-Furthermore, doing a power-law transformation under Dasgupta--Pal is not only impractical in terms of accuracy, but also it is impractical in terms of time efficiency because it took about 2 hours and 40 minutes on average to process each image.
-
-\begin{table}[h]
-	\centering
-	\caption{Power-law transformation under Dasgupta--Pal}
-	\label{tbl:pwr-dp}
-    \begin{tabular}{lcccccc}
-        \toprule
-        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
-		% \texttt{anpage} & 25115.891 & 4.131 & 0.00000 & 0.016 & 741.872 & 0.031 \\ 10x10
-		% \texttt{bplyce} & 22777.187 & 4.556 & 0.00000 & 0.017 & 730.873 & 0.003 \\ 10x10
-		% \texttt{drbost} & 18899.906 & 5.366 & 0.00000 & 0.014 & 733.409 & 0.003 \\
-		(a) & 25008.723 & 4.150 & 0.000 & 0.376 & 9700.926 & 1.269 \\
-		(b) & 22700.522 & 4.570 & 0.000 & 0.230 & 9196.609 & 0.043 \\
-		(c) & 18902.214 & 5.366 & 0.000 & 0.277 & 9261.407 & 0.150 \\
-		(d) & 12585.729 & 7.132 & 0.000 & 0.257 & 9259.010 & 0.051 \\
-		(e) & 17012.423 & 5.823 & 0.000 & 0.279 & 9440.351 & 0.051 \\
-		(f) & 31124.615 & 3.200 & 0.000 & 0.285 & 9492.149 & 0.052 \\
-		(g) & 22982.917 & 4.517 & 0.000 & 0.289 & 9321.928 & 0.048 \\
-		(h) & 13469.155 & 6.837 & 0.000 & 0.257 & 9233.818 & 0.048 \\
-		(i) & 37453.834 & 2.396 & 0.000 & 0.262 & 9203.045 & 0.048 \\
-		(j) & 23037.762 & 4.506 & 0.000 & 0.258 & 9210.393 & 0.048 \\
-		% \texttt{drbost} & 18902.214 & 5.366 & 0.00000 & 0.064 & 2261.407 & 0.110 \\ % 20x18
-		% \texttt{ksunth} & 12585.729 & 7.132 & 0.00000 & 0.044 & 2259.010 & 0.011 \\ % 20x18
-		% \texttt{martin} & 17012.423 & 5.823 & 0.00000 & 0.066 & 2440.351 & 0.011 \\
-		% \texttt{pmives} & 31124.615 & 3.200 & 0.00000 & 0.072 & 2492.149 & 0.012 \\
-		% \texttt{rnpwil} & 22982.917 & 4.517 & 0.00000 & 0.076 & 2321.928 & 0.008 \\
-		% \texttt{sbains} & 13469.155 & 6.837 & 0.00000 & 0.044 & 2233.818 & 0.008 \\
-		% \texttt{swewin} & 37453.834 & 2.396 & 0.00000 & 0.049 & 2203.045 & 0.008 \\
-		% \texttt{yfhsie} & 23037.762 & 4.506 & 0.00000 & 0.045 & 2210.393 & 0.008 \\
-		\bottomrule
-        \end{tabular}
-\end{table}
-
-\section{Conclusion}
-In this paper, we have assessed the feasibility and practicality of various homomorphic cryptosystems with regard to secure processing and manipulation of facial image data through creation of a software library that facilitates image processing operations within the encrypted domain, as well as our own implementation of some homomorphic cryptosystems like Dasgupta--Pal for which existing third-party libraries dedicated for this purpose are not yet available.
-
-% This paper also proposes a correction to the Dasgupta--Pal cryptosystem which is further explained in Appendix~\ref{chap:correction}.
-
-Even though an operation in a partially homomorphic cryptosystem is not theoretically possible, like multiplication of two ciphertexts under Paillier, it has been shown that such operations are indeed possible in a two-party system.
-Protocols for secure multiplication and exponentiation have been proposed and also applied to more complex image operations such as facial recognition.
-Thus, a partially homomorphic cryptosystem can be modified to admit more image processing operations by assuming a two-party system.
-
-Preliminary results have shown that both Paillier and Dasgupta--Pal apply image negation accurately and efficiently, as evidenced by the perfect zero MSE and infinite PSNR.
-For the logarithm transformation, Paillier was faster and accurate enough (with $\text{MSE} \le 30$ and $\text{SSIM} \approx 0.99$), but Dasgupta--Pal was slower but more accurate (with $\text{MSE} \le 0.01$ and $\text{SSIM} \approx 0.99999$) which was rather unexpected.
-However both Paillier and Dasgupta--Pal fail to produce accurate results in applying the power-law transformation, with the latter completely failing to produce discernible results.
-Based from these results, the Paillier cryptosystem is consistent enough to produce reasonable to accurate results.
-
-A wrapper library has been made which implements the various functions and methods of the cryptosystems into a single interface.
-This allowed us to express various image operations with a unified syntax, thus facilitating easier testing.
-
-\subsection{Ongoing and Future Work}
-Testing intensity transformations under the BGV cryptosystem will be started once the Pyfhel library is deemed stable enough to use, or another Python library that implements BGV becomes available. 
-One of the authors of this paper has already informed the developers of the Pyfhel library about a bug involving exponentiation of two real numbers.
-
-Efforts are ongoing with regard to the facial recognition tests.
-Our own implementation of the privacy-preserving  eigenfaces by Erkin, et al.
-does not yet use the DGK cryptosystem for secure integer comparison in the match finding step, thus we are working on implementing DGK from scratch.
-
-Another promising image operation to consider is \textit{facial detection} under a homomorphic cryptosystem.
-Work has been started in order to assess the feasibility of using Haar cascades in a privacy-preserving manner.
-
-Future work would involve improving and optimizing our implementation of the Dasgupta--Pal cryptosystem so that it performs faster.
-A suggestion would be to port the existing implementation to C/C++ and then create a Python library that acts as a wrapper to the C/C++ methods.
-For future studies, an implementation of a client-server framework or system dealing with secure image processing can be considered.

### 2019-03-12 icmssp-paper/parts/02_reviewofrelatedliterature.tex
Change folder structure
- renamed paper folder to icmssp-paper
- split icmssp paper into parts

--- 2019-02-10 paper/paper-conf.tex
@@
-\section{Introduction}
-\subsection{Context of the Study}
-Digital data privacy and security is a growing concern in various fields, such as cloud computing~\cite{potey_homomorphic_2016}, health information systems~\cite{kester_cryptographic_2015}, and video surveillance~\cite{upmanyu_efficient_2009}.
-To meet these needs, various cryptosystems have been developed.
-A cryptosystem is a system which operates on plaintexts, ciphertexts and keys using an encryption algorithm, which maps a plaintext to a ciphertext, together with a decryption algorithm, which maps a ciphertext to a plaintext, given an appropriate key~\cite{bauer_cryptosystem_2005}.
-The encryption and decryption algorithms are chosen such that the plaintext cannot easily be recovered from the ciphertext without knowledge of the key.
-This allows data to be securely transmitted over an insecure channel.
-
-One particular application of cryptography is image encryption.
-While cryptosystems used to encrypt digital data in general, such as the Advanced Encryption Standard (AES) or elliptic curve cryptography, can also be used to encrypt images~\cite{jain_image_2016, singh_image_2015} other algorithms created specifically for image encryption have also been developed~\cite{murugan_survey_2018}.
-
-In a homomorphic cryptosystem, operations such as addition and multiplication can be performed on encrypted data.
-These operations are then preserved when the data is decrypted.
-In this manner, data is manipulated without compromising data privacy, as the encrypted data being operated on remains secure~\cite{fontaine_survey_2007, sen_homomorphic_2013}.
-In the area of homomorphic image encryption, there is interest in being able to perform image manipulation operations on the encrypted data such as image adjustment, filtering, and morphological/feature extraction operations~\cite{ziad_cryptoimg:_2016, gonzalez_digital_2008}.
-More advanced operations have also been implemented using homomorphic cryptosystems, such as facial recognition \cite{hutchison_privacy-preserving_2009} and neural networks \cite{hesamifard_cryptodl:_2017}.
-This study in particular focuses on facial recognition.
-
-% \subsection{Research Questions}
-% By implementing homomorphic cryptosystems and creating a library so they can be easily used, we aim to address our main research question: What is the best method for facial image data to be encrypted and manipulated for practical applications?
-
-% More specifically, our research will address the following sub-questions:
-% \begin{enumerate}
-% 	\item Which homomorphic cryptosystems admit more image processing operations? How can existing homomorphic cryptosystems be modified to admit more image processing operations?
-% 	\item Which homomorphic cryptosystems are the most time-efficient and the most accurate in applying image processing operations?
-% 	\item Which homomorphic cryptosystems best preserve image quality in applying image processing operations?
-% \end{enumerate}
-
-\subsection{Research Objectives}
-% Previous attempts in the literature to provide image processing tasks such as image manipulation \cite{ziad_cryptoimg:_2016} and  facial recognition \cite{hutchison_privacy-preserving_2009} have primarily used the Paillier and  Damg{\aa}rd--Geisler--Kr{\o}igaard (DGK) cryptosystems to perform linear operations on encrypted data.
-% In this study, we extend this research to provide an objective comparison of various homomorphic cryptosystems currently in the literature in performing non-linear operations, and facial detection, as opposed to just linear operations and facial recognition.
-
-Our main research objective is to assess the practicality of various homomorphic cryptosystems with regard to image processing on faces. 
-% Homomorphic cryptosystems are known to be slower in terms of encryption, operation, and decryption time~\cite{sen_homomorphic_2013}.
-Furthermore, the operations on encrypted data supported by homomorphic cryptosystems are limited, and some schemes require preprocessing to be performed on images, limiting the range of operations which can be performed efficiently~\cite{li_elliptic_2012}.
-
-% In summary, in this study, we wish to
-More specifically, we wish to do the following:
-\begin{enumerate}
-    \item Implement common linear and non-linear image processing operations using known homomorphic encryption schemes, then determine which schemes admit more image processing operations and extend known cryptosystems to support more operations, if possible;
-    \item Compare the time efficiency and accuracy of common image processing operations under known homomorphic encryption schemes, and of common image processing operations without using homomorphic encryption;
-    \item Create a library to allow for convenient use and comparison of these homomorphic encryption schemes for image processing and facial recognition.
-\end{enumerate}
-
-\subsection{Scope and Limitations}
-% Our study will be limited in terms of the cryptosystems to be tested, the image processing operations we will implement, and the statistical tests we will use to gauge the security of the cryptosystems.
-Below is a listing of the scope of the study.
-
-% We will implement and test the following algorithms:
-In this study, we will implement and test the following cryptosystems:
-\begin{enumerate}
-	\item A variant of the Paillier cryptosystem~\cite{stern_public-key_1999} which supports floating-point operations, used in \textit{CryptoImg}~\cite{ziad_cryptoimg:_2016}.
-    \item The Damg{\aa}rd--Geisler--Kr{\o}igaard (DGK) cryptosystem~\cite{pieprzyk_efficient_2007, cryptoeprint:2008:321} which is primarily used for secure integer comparison.
-	% \item A fully homomorphic encryption scheme by Dasgupta and Pal, which uses polynomial rings~\cite{dasgupta_design_2016}.
-	\item The Brakerski--Gentry--Vaikuntanathan (BGV) cryptosystem \cite{cryptoeprint:2011:277}, an improvement on the lattice-based cryptosystem by Gentry~\cite{gentry_fully_2009}, with optimizations from Smart, Vercauteren, and Halevi \cite{hutchison_fully_2010, cryptoeprint:2011:566}.
-\end{enumerate}
-We will implement and test the following categories of image manipulation operations:
-\begin{enumerate}
-	\item Non-linear image intensity adjustment (logarithm and power-log transformations)
-	\item Facial detection and recognition using the eigenface approach \cite{turk_eigenfaces_1991}.
-\end{enumerate}
-We will adopt the benchmark for evaluating image quality of image encryption schemes presented by Ahmed, et.
-al~\cite{ahmed_benchmark_2016}.
-The presented benchmark reflects many tests used in other literature~\cite{ahmad_efficiency_2012, wu_npcr_2011}.
-\begin{enumerate}
-    \item Mean Squared Error (MSE)
-    \item Peak Signal to Noise Ratio (PSNR)
-    \item Structural Similarity Index (SSIM)
-\end{enumerate}
-A detailed overview of the above will be provided in the methodology. Grayscale images will be used in the study.
-A client-server model for secure computation will be assumed to allow operations such as secure comparison and exponentiation.
-Training and test data are taken from the publicly available \texttt{faces94} dataset (\url{https://cswww.essex.ac.uk/mv/allfaces/faces94.html}) maintained by the University of Essex.
-
-\subsection{Significance of the Study}
-This study aims to directly address one of the current problems in the research of homomorphic cryptosystems: the practicality of homomorphic encryption~\cite{sen_homomorphic_2013}.
-The literature shows existing homomorphic cryptosystems and how they support primitive operations (usually addition and multiplication) on encrypted data, however, for homomorphic cryptosystems to be useful for practical use, efficient support for more complicated image processing operation must be demonstrated as well.
-While implementations of image processing operations in a homomorphic cryptosystem exist in the literature~\cite{ziad_cryptoimg:_2016, garay_algorithms_2014}, our study targets the more computationally intensive task of facial detection.
-
-We wish to contribute to existing models for the secure transmission and modification of image data by developing a software library which allows the use and comparison of various homomorphic encryption algorithms.
-Our software library would allow service providers to perform image manipulation for clients without compromising data privacy.
-
 \section{Review of Related Literature}
@@
     &= (g^m)^k \cdot (h^r)^k \bmod{n}\\
-    &= g^{km} \cdot (h^kr) \bmod{n}
+    &= g^{km} \cdot (h^{kr}) \bmod{n}
   \end{align*}
-  Since $r$ is a random integer, $kr$ is also a random integer, Therefore, $g^{km} \cdot (h^kr) \bmod{n} = D(E(m_1)^k)$ is a valid encryption of the message $km$.
+  Since $r$ is a random integer, $kr$ is also a random integer, Therefore, $g^{km} \cdot (h^{kr}) \bmod{n} = E(m)^k$ is a valid encryption of the message $km$.
 \end{proof}
@@
 Instead, the DGK cryptosystem \cite{pieprzyk_efficient_2007} is used for the comparison protocol.
-
-\section{Methodology}
-In this study we apply three homomorphic encryption schemes~\cite{ziad_cryptoimg:_2016, pieprzyk_efficient_2007, garay_algorithms_2014} for use in image processing and facial recognition applications.
-In particular, the study consists of the following:
-\begin{itemize}
-	\item Creating a wrapper library that acts as a unified interface which implements the Paillier, DGK, and BGV homomorphic cryptosystems.
-	\item An implementation of image processing operations (intensity transformations, facial recognition) under the above cryptosystems.
-	\item Conducting tests for image quality, processing time, using images from the \texttt{faces94} dataset.
-\end{itemize}
-
-% While the Paillier and DGK cryptosystems have been implemented for use in image processing in~\cite{ziad_cryptoimg:_2016, hutchison_privacy-preserving_2009}, the other cryptosystems have to be adapted for this study.
-% Two experiments are conducted in this study:
-% \begin{enumerate}
-% 	\item Assessment of non-linear image intensity transformations under each of the three cryptosystems.
-% 	\item Assessment of efficiency of each of the four cryptosystems when applied for use in privacy-preserving facial recognition and detection using eigenfaces.
-% \end{enumerate}
-% The results of the image intensity transformations are tested for image quality using benchmarks in~\cite{ahmed_benchmark_2016}.
-
-\subsection{Cryptosystem Implementation}
-Three homomorphic encryption schemes are investigated, and a wrapper library was created in Python that integrates these cryptosystems into a unified interface.
-\begin{itemize}
-	\item The Paillier cryptosystem is incorporated using the python-paillier library at \url{https://github.com/n1analytics/python-paillier} developed by Data61 - CSIRO.
-	\item The DGK cryptosystem is ported from the C++ implementation at \url{https://github.com/encryptogroup/ENCRYPTO_utils}, developed by Daniel Demmler from EC-SPRIDE.
-	\item The BGV cryptosystem is implemented using the Pyfhel library (\url{https://github.com/ibarrond/Pyfhel}) using a HElib backend from (\url{https://github.com/shaih/HElib}).
-\end{itemize}
-
-\subsubsection{Extension of Partially Homomorphic Cryptosystems}
-\label{sssec:pheextension}
-In order to use Paillier and DGK for secure image processing, we require the two schemes to support the encryption of floating-point (FP)numbers, as well as multiplication and division of arbitrary ciphertexts.
-We extend the two cryptosystems to FP operations by using an approach shown in~\cite{ziad_cryptoimg:_2016}.
-This approach represents FP numbers using a pair $(m,e)$, where $m$ represents the mantissa (which is encrypted), and $e$ represents the exponent (which is not encrypted).
-This approach is also used by the python-paillier library.
-This represntation allows us to extend the addition and plaintext multiplication homomorphisms of the Paillier and DGK cryptosystems to floating-point numbers.
-
-Various two-party protocols can be used to facilitate ciphertext multiplication and division.
-These allow a server armed with only knowledge of the public key, to obtain the product and quotient of ciphertexts, by communicating with the client, who has the private key.
-For division, we use the protocol defined in~\cite{boukoros_lightweight_2017}: to obtain $E(x/y)$ from $E(x)$ and $E(y)$, the server sends $E(rx)$ and $E(ry)$ to the client, (where $r$ is a random non-zero number), allowing the client to compute $E(rx/ry)$ and give the result back to the server.
-
-For multiplication, we adapt the protocol to calculate Euclidean distances used in \cite{hutchison_privacy-preserving_2009}, which provides a two-party protocol which yields $E(x^2)$ given $E(x)$.
-We use this protocol together with the additive homomorphism of the partially homomorphic cryptosystems to instead compute $E((x + y)^2 - x^2 - y^2) = E(2xy)$, from which we can easily obtain $E(xy)$ through plaintext multiplication.
-
-% [TO-DO: This is further explained in another paper.]
-% We will briefly discuss a protocol to enable cryptosystems built for integer inputs to handle real number inputs.
-% The following protocol was also used by \textit{CryptoImg} for image processing \cite{ziad_cryptoimg:_2016}.
-% This is also used for our own implementation of the Dasgupta--Pal cryptosystem in order to handle real numbers.
-
-% We represent a floating-point (FP) number as a pair of two integers $(m,e)$ representing the mantissa and exponent of the FP number with respect to a base $b$.
-The mantissa $m$ is encrypted, while the exponent $e$ is unencrypted.
-% Let $a,b,c$ be FP numbers represented by the pairs $(m_a,e_a),(m_b,e_b),(m_c,e_c)$ respectively.
-Let $\oplus,\otimes$ represent the homomorphic operations which correspond to the addition and multiplication, respectively.
-We define the secure real number operations as follows:
-% \begin{description}
-%   \item[Addition.]
-%     To compute $E(c)=E(a+b)$ we compute
-%     \begin{align*}
-%       E(m_c) &= E(m_1) \oplus (b^{e_b-e_a} \otimes E(m_b)), e_c = e_a & \text{ if } e_a \leq e_b \\
-%       E(m_c) &= E(m_b) \oplus (b^{e_a-e_b} \otimes E(m_a)), e_c = e_b & \text{ if } e_a > e_b
-%     \end{align*}
-%   \item[Scalar multiplication.]
-%     To compute $E(c) = E(ab)$, where $a$ and $E(b)$ are known (i.e. $m_a$ is not encrypted), we compute
-%     \begin{align*}
-%       E(m_c) &= m_a \otimes E(m_b)\\
-%       e_c &= e_a + e_b
-%     \end{align*}
-% \end{description}
-
-\subsection{Non-Linear Intensity Transformations}
-We will implement library functions for image negation, logarithm transformation and power-law transformation, as they are defined in~\cite{gonzalez_digital_2008}.
-We now describe how we implement the logarithm and power-law image intensity transformations.
-In the case of partially homomorphic cryptosystems (Paillier, DGK), if ciphertext multiplication or division is required, the secure protocols in section \ref{sssec:pheextension} will be used.
-
-\subsubsection{Logarithm Transformation}
-The logarithm transformation of a pixel intensity value $x$ is defined as
-\begin{align}
-	T\left(x\right) = c \log\left(1 + x\right)
-\end{align}
-where $c$ is a constant.
-
-In order to perform this transformation under Paillier and DGK, we provide the following closed-form approximation for $\log\left(1 + x\right)$.
-% TODO: IDK HOW TO CITE OUR PCSC PAPER
-\begin{align}\label{eq:optimal_log_approximation}
-	\begin{split}
-		&\log\left(1+x\right) \approx \frac{a(x)}{b(x)} + \log{16}
-	\end{split}
-\end{align}
-where
-\begin{align*}
-	\begin{split}
-	a(x) &= 137x^5 + 26685x^4 + 617370x^3 - 6498630x^2 \\
-	&- 121239315x - 257804775\\
-	b(x) &= 30(x^5 + 405x^4 + 27210x^3 + 488810x^2 + 2536005x \\
-	&+ 3122577).
-	\end{split}
-\end{align*}
-% \begin{align}\label{eq:optimal_log_approximation}
-% 	\begin{split}
-% 		&\log\left(1+x\right) \\
-% 		&\approx \frac{137x^5 + 26685x^4 + 617370x^3 - 6498630x^2 - 121239315x - 257804775}
-% 		{30(x^5 + 405x^4 + 27210x^3 + 488810x^2 + 2536005x + 3122577)}\\
-% 		&+ \log{16}.
-% 	\end{split}
-% \end{align}
-
-\subsubsection{Power-Law Transformation}
-The power-law transformation of a pixel intensity value $x$ is defined as
-\begin{equation}
-    T\left(x\right) = cx^{\gamma}
-\end{equation}
-where $c>0$ and $\gamma > 0$.
-
-Similar to the logarithm transformation, to apply this transformation using Paillier and DGK, we must provide an approximation for $x^\gamma$.
-We can use partial sums of the following series, which relies on the logarithm function.
-\begin{align}
-	x^\gamma &= \sum_{n=0}^{\infty}{\frac{(\gamma\log{x})^n}{n!}}
-\end{align}
-% Partial sums of the above infinite series can be calculated based on the closed form approximation for the logarithm in Equation \ref{eq:scaledquadraturech3}. 
-For the implementation of the power-law transformation for this paper, a partial sum consisting of the first five terms of the infinite series were used.
-
-\subsection{Assessment of Homomorphic Encryption Schemes}
-A laptop computer with a 2.5 GHz Intel Core i7 quad-core processor and 8 GB of RAM is used to perform the computations, and processing time was tracked using built-in timing functions.
-The processing time for all cases were recorded.
-All of the tests are done using Python 3.7.1 running on Linux.
-
-\subsubsection{Image Quality of Intensity Transformations}
-In this section, we discuss the image quality metrics we used for assessing the performance of non-linear intensity transformations.
-
-We first obtained test images from the \texttt{faces94} dataset (\url{https://cswww.essex.ac.uk/mv/allfaces/faces94.html}) maintained by the University of Essex.
-However, only ten distinct facial images from the dataset were selected for the purposes of this test.
-Since only grayscale images are used in the study, the images were converted to grayscale and then downsampled to $40 \times 36$ pixels.
-
-For each cryptosystem, three image operations are tested:
-\begin{enumerate}
-	\item Image negation
-	\item Logarithm transformation, with $c = 30$
-	\item Power-law transformation, with $c = 1$ and $\gamma = 0.4$
-\end{enumerate}
-
-For each plaintext image (PT), we considered each image operation listed above and generate three images: a plaintext domain transformation (PDT), a ciphertext image (CT), and an ciphertext domain transformation (CDT).
-The PDT was generated by running the image operation on the original image.
-The CT was generated by encrypting the image, then applying the operation, and the CDT was generated by decrypting the CT.
-The four images (PT, PDT, CT, CDT) were then compared using various benchmarks to evaluate the quality and security of each homomorphic encryption scheme.
-
-The benchmarks to be used in the study, adopted from~\cite{ahmed_benchmark_2016, ahmad_efficiency_2012, wu_npcr_2011} are listed below.
-We let $X_i$ denote a value in an image $X$, where $1 \leq i \leq N$.
-We first perform three tests to ascertain the preservation of image quality after encryption and decryption: MSE, PSNR, and SSIM.
-\begin{description}
-	\item [Mean Squared Error (MSE).] The MSE is defined in~\cite{ahmed_benchmark_2016} as
-	\begin{align}
-        \mathrm{MSE} = \frac{1}{N}\sum_{i=1}^{N}{(\mathrm{CDT}_i - \mathrm{PDT}_i)^2}.
-	\end{align}
-	The MSE provides a measure of how much data is recovered if an image operation is applied on the encrypted image, which is then decrypted.
-Lower values of MSE indicate higher preservation of image quality~\cite{ahmed_benchmark_2016, ahmad_efficiency_2012}.
-	\item [Peak Signal to Noise Ratio (PSNR).]
-	According to Ahmed, et al.~\cite{ahmed_benchmark_2016}, PSNR is ``an estimator for human visual perception of reconstruction quality.'' It has been used to ascertain image quality in various studies and is a known metric for image and video quality~\cite{upmanyu_efficient_2009, jain_image_2016, akramullah_video_2014}.
-Although it may produce results which do not correlate with human visual perception~\cite{huynh-thu_accuracy_2012, ahmed_benchmark_2016}, it is a valid indicator of image quality when media containing the same visual content is compared~\cite{huynh-thu_accuracy_2012}.
-	PSNR is defined by
-	\begin{align}
-        \mathrm{PSNR} = 10\log_{10}{\left( \frac{L^2}{\mathrm{MSE}} \right)}
-	\end{align}
-	where $L$ is the maximum pixel intensity value of an image.
-	Despite the known limitations of PSNR, since we are going to compare the effect of each encryption scheme on recovered image quality, given a fixed library of images, it is a valid measure of image quality for the study.
-A higher PSNR indicates higher image quality preservation.
-	\item [Structural Similarity Index (SSIM).]
-	The SSIM for two random variables $X$ and $Y$ is defined in~\cite{ahmed_benchmark_2016, akramullah_video_2014} as
-	\begin{align}
-        \mathrm{SSIM}(X,Y) = \frac{(2\mu_X\mu_Y+c_1)(2\sigma_{XY}+c_2)}{(\mu_X^2+\mu_Y^2+c_1)(\mu_X^2+\mu_Y^2+c_2)}
-	\end{align}
-	where
-	\begin{itemize}
-		\item $\mu_X, \mu_Y$ are the averages of $X$ and $Y$, respectively;
-		\item $\sigma_X, \sigma_Y$ are the variances of $X$ and $Y$, respectively;
-		\item $\sigma_{XY}$ is the covariance of $X$ and $Y$;
-		\item $c_1 = (k_1L)^2, c_2 = (k_2L)^2$ are two variables used to stabilize the measure when $\mu_X^2+\mu_Y^2$ is close to zero~\cite{akramullah_video_2014};
-		\item $L$ is the the maximum pixel intensity value of an image;
-		\item $k_1 = 0.01, k_2 = 0.03$ by default, given in~\cite{ahmed_benchmark_2016}.
-	\end{itemize}
-	The SSIM is applied to the luminance value of two images to gauge structural similarity between neighboring pixels.
-	For the study, we computed $\mathrm{SSIM}(\mathrm{PDT}, \mathrm{CDT})$ for every image operation, under each homomorphic cryptosystem.
-Higher values of SSIM indicate higher structural similarity, and an SSIM of $1$ indicates that the two images are identical~\cite{ahmed_benchmark_2016}.
-\end{description}
-
-Computing for MSE, PSNR, and SSIM was done using the corresponding built-in functions from the scikit-image Python library \cite{scikit-image}.
-
-\subsubsection{Facial Recognition Tests}
-The method for secure facial recognition using eigenfaces by Erkin, et al. \cite{hutchison_privacy-preserving_2009} was implemented for this study.
-
-As before, training and test data were also secured from the \texttt{faces94} dataset. The images were first converted to grayscale but it is not downsampled, unlike in the previous test.
-
-The facial recognition tests are done using ten-fold cross-validation for each cryptosystem, where the number of principal components used by the algorithm is fixed at $K=5$.
-
-Prior to splitting the dataset, the images within each set are shuffled.
-Since there are twenty (20) images per set, two images are taken at a time for each round of cross-validation.
-The first round would take the first two images from each set as part of the test set, and the rest of the images will be part of the training set.
-Then, the succeeding round would take the next two images from each set as part of the test set, and so on until ten rounds have been done.
-After every round of cross-validation, the accuracy score, confusion matrix, and total processing time are obtained.
-
-%% Summary not needed, this was only important for the thesis proposal - Aldrich
-% \subsection{Summary}
-% In summary, the study consists of:
-% \begin{itemize}
-% 	\item Creating a wrapper library that acts as a unified interface which implements the Paillier, DGK, Dasgupta--Pal, and BGV homomorphic cryptosystems.
-% 	\item An implementation of image processing operations (intensity transformations, facial recognition) under the above cryptosystems.
-% 	\item Conducting tests for image quality, processing time, using images from the \texttt{faces94} dataset.
-% \end{itemize}
-
-\section{Preliminary Results and Discussion}
-The results shown in this section are gathered from the tests for intensity transformations under Paillier and Dasgupta--Pal cryptosystems.
-During testing, initial results obtained from BGV, particularly with image operations involving floating-point numbers like the logarithmic transformation, were unstable (i.e.
-the results vary drastically every time the same tests were done).
-This is because the Pyfhel library being used for the BGV cryptosystem is still in alpha development stage \cite{pyfhel_2018}.
-
-% One of the authors has already informed the maintainers of the library about a bug involving exponentiation of two real numbers.
-
-\subsection{Intensity Transformations}
-
-\begin{table*}
-	\centering
-	\caption{Comparison of intensity transformations under Paillier}
-	\label{tbl:it-pal}
-	\begin{tabular}{m{1cm}*{7}{>{\centering\arraybackslash}m{1.75cm}}}
-		\toprule
-		\multirow{2}{*}{Image} & \multirow{2}{*}{Original} & \multicolumn{2}{c}{Image negation} & \multicolumn{2}{c}{Logarithm transformation} & \multicolumn{2}{c}{Power-law transformation} \\
-							   &                           & PDT           & CDT          & PDT            & CDT           & PDT               & CDT           \\ 
-		\midrule
-		\xintForpair #1#2 in {(anpage,a), (bplyce,b), (drbost,c), (ksunth,d), (martin,e), (pmives,f), (rnpwil,g), (sbains,h), (swewin,i), (yfhsie,j)} \do {%
-		(#2) & \includegraphics[width=1.75cm]{out_faces/paillier_negate_#1_original.png} & \includegraphics[width=1.75cm]{out_faces/paillier_negate_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/paillier_negate_#1_decrypted.png} & \includegraphics[width=1.75cm]{out_faces/paillier_logtransform_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/paillier_logtransform_#1_decrypted.png} & \includegraphics[width=1.75cm]{out_faces/paillier_pwrtransform_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/paillier_pwrtransform_#1_decrypted.png} \\ }%
-		\bottomrule         
-	\end{tabular}
-\end{table*}
-
-\begin{table*}
-	\centering
-	\caption{Comparison of intensity transformations under Dasgupta--Pal}
-	\label{tbl:it-dp}
-	\begin{tabular}{m{1cm}*{7}{>{\centering\arraybackslash}m{1.75cm}}}
-		\toprule
-		\multirow{2}{*}{Image} & \multirow{2}{*}{Original} & \multicolumn{2}{c}{Image negation} & \multicolumn{2}{c}{Logarithm transformation} & \multicolumn{2}{c}{Power-law transformation} \\
-							   &                           & PDT           & CDT          & PDT            & CDT           & PDT               & CDT           \\ 
-		\midrule
-		\xintForpair #1#2 in {(anpage,a), (bplyce,b), (drbost,c), (ksunth,d), (martin,e), (pmives,f), (rnpwil,g), (sbains,h), (swewin,i), (yfhsie,j)} \do {%
-		(#2) & \includegraphics[width=1.75cm]{out_faces/dp_negate_#1_original.png} & \includegraphics[width=1.75cm]{out_faces/dp_negate_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/dp_negate_#1_decrypted.png} & \includegraphics[width=1.75cm]{out_faces/dp_logtransform_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/dp_logtransform_#1_decrypted.png} & \includegraphics[width=1.75cm]{out_faces/paillier_pwrtransform_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/dp_pwrtransform_#1_decrypted.png} \\ }%
-		\bottomrule
-	\end{tabular}
-\end{table*}
-
-Table~\ref{tbl:it-pal} shows the images obtained from the intensity transformation tests under the Paillier cryptosystem, while Table~\ref{tbl:it-dp} shows the resulting images from the same tests under the Dasgupta--Pal cryptosystem.
-Shown for each image is the original unecrypted image, and for each intensity transformation the \textit{plaintext domain transformation} (PDT) is given which is the resulting image after applying the transformation to the unencrypted image and the \textit{ciphertext domain transformation} (CDT) is the decrypted image of the processed encrypted image.
-
-The following tables show the resulting metric scores for mean squared error (MSE), peak signal to noise ratio (PSNR), and structural similarity index (SSIM), as well as time taken (in seconds) for encrypting the input image ($t_\text{enc}$), applying an operation to the encrypted image ($t_\text{apply}$), and decrypting the resulting encrypted image ($t_\text{dec}$), for each image in the test set.
-Tables~\ref{tbl:neg-pal} and~\ref{tbl:neg-dp} show the results obtained from applying image negation, Tables~\ref{tbl:log-pal} and~\ref{tbl:log-dp} from applying logarithm transformation, and Tables~\ref{tbl:pwr-pal} and~\ref{tbl:pwr-dp} from applying power-law transformation.
-
-\subsubsection{Image Negation}
-Both the Paillier and Dasgupta--Pal cryptosystems were able to perform image negation under the encrypted domain without introducing noise in the resulting image.
-In other words, the resulting image from doing image negation on an image on the clear and doing image negation under the encrypted domain are identical, as evidenced by the mean squared errors being exactly equal to zero, the PSNR being infinite, and the SSIM being exactly equal to one.
-
-The Paillier cryptosystem performed better in terms of time, only taking about 0.01 seconds to apply image negation.
-On the other hand, the Dasgupta--Pal cryptosystem took about 22 seconds each to apply the same operation, which is expected since the implementation for Dasgupta--Pal was done in Python without using any external libraries.
-
-\begin{table}[h]
-	\centering
-	\caption{Image negation under Paillier}
-	\label{tbl:neg-pal}
-    \begin{tabular}{lcccccc}
-        \toprule
-        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
-        (a) & 0.000 & $\infty$ & 1.00000 & 0.128 & 0.013 & 0.041 \\
-		(b) & 0.000 & $\infty$ & 1.00000 & 0.084 & 0.013 & 0.024 \\
-		(c) & 0.000 & $\infty$ & 1.00000 & 0.099 & 0.012 & 0.031 \\
-		(d) & 0.000 & $\infty$ & 1.00000 & 0.109 & 0.012 & 0.048 \\
-		(e) & 0.000 & $\infty$ & 1.00000 & 0.117 & 0.015 & 0.043 \\
-		(f) & 0.000 & $\infty$ & 1.00000 & 0.111 & 0.012 & 0.025 \\
-		(g) & 0.000 & $\infty$ & 1.00000 & 0.099 & 0.012 & 0.023 \\
-		(h) & 0.000 & $\infty$ & 1.00000 & 0.084 & 0.012 & 0.024 \\
-		(i) & 0.000 & $\infty$ & 1.00000 & 0.089 & 0.012 & 0.023 \\
-		(j) & 0.000 & $\infty$ & 1.00000 & 0.081 & 0.012 & 0.029 \\
-		\bottomrule
-    \end{tabular}
-\end{table}
-\begin{table}[h]
-	\centering
-	\caption{Image negation under Dasgupta--Pal}
-	\label{tbl:neg-dp}
-    \begin{tabular}{lcccccc}
-        \toprule
-        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
-		(a) & 0.000 & $\infty$ & 1.00000 & 0.221 & 30.217 & 0.239 \\
-		(b) & 0.000 & $\infty$ & 1.00000 & 0.190 & 30.919 & 0.216 \\
-		(c) & 0.000 & $\infty$ & 1.00000 & 0.284 & 31.182 & 0.268 \\
-		(d) & 0.000 & $\infty$ & 1.00000 & 0.225 & 32.581 & 0.223 \\
-		(e) & 0.000 & $\infty$ & 1.00000 & 0.220 & 32.220 & 0.271 \\
-		(f) & 0.000 & $\infty$ & 1.00000 & 0.287 & 31.224 & 0.294 \\
-		(g) & 0.000 & $\infty$ & 1.00000 & 0.285 & 29.478 & 0.284 \\
-		(h) & 0.000 & $\infty$ & 1.00000 & 0.186 & 29.784 & 0.362 \\
-		(i) & 0.000 & $\infty$ & 1.00000 & 0.243 & 38.407 & 0.220 \\
-		(j) & 0.000 & $\infty$ & 1.00000 & 0.285 & 29.488 & 0.449 \\		
-		\bottomrule
-        \end{tabular}
-\end{table}
-
-\subsubsection{Logarithm Transformation}
-Unlike image negation, logarithm transformation involves more operations, so the increase in processing time for both cryptosystems are expected.
-Applying the logarithm transformation under Paillier took about 2 seconds per image, while it took about 13.5 minutes each under Dasgupta--Pal.
-
-The logarithm transformation under Dasgupta--Pal turned out to be more accurate than Paillier, whose mean squared errors approach zero and the SSIM values approach one for every image as shown in Table~\ref{tbl:log-dp}.
-Although the results from using Paillier show that it is also accurate enough with the mean squared errors being less than 30 and the SSIM values average to 0.99, Dasgupta--Pal has been able to produce an almost identical result to that of the plaintext domain transformation counterparts.
-This observation is rather unexpected, considering that the implementation used for Paillier is more robust (due to its use of external C/C++ libraries which makes computations faster).
-
-\begin{table}[h]
-	\centering
-	\caption{Logarithm transformation under Paillier}
-	\label{tbl:log-pal}
-    \begin{tabular}{lcccccc}
-        \toprule
-        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
-		(a) & 13.369 & 36.870 & 0.99263 & 0.085 & 1.813 & 0.023 \\
-		(b) & 7.072 & 39.635 & 0.99017 & 0.089 & 2.073 & 0.023 \\
-		(c) & 8.151 & 39.019 & 0.98688 & 0.091 & 1.913 & 0.023 \\
-		(d) & 25.253 & 34.108 & 0.98927 & 0.089 & 1.919 & 0.023 \\
-		(e) & 10.374 & 37.971 & 0.98695 & 0.106 & 1.829 & 0.023 \\
-		(f) & 2.426 & 44.283 & 0.99401 & 0.127 & 1.900 & 0.023 \\
-		(g) & 5.184 & 40.985 & 0.98971 & 0.096 & 1.853 & 0.023 \\
-		(h) & 16.772 & 35.885 & 0.98492 & 0.081 & 1.746 & 0.024 \\
-		(i) & 5.803 & 40.494 & 0.99241 & 0.091 & 1.827 & 0.027 \\
-		(j) & 12.192 & 37.270 & 0.99354 & 0.081 & 1.815 & 0.023 \\
-		\bottomrule
-        \end{tabular}
-\end{table}
-\begin{table}[h]
-	\caption{Logarithm transformation under Dasgupta--Pal}
-	\label{tbl:log-dp}
-    \begin{tabular}{lcccccc}
-        \toprule
-        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
-		(a) & 0.004 & 71.624 & 0.99999 & 0.287 & 802.957 & 0.036 \\
-		(b) & 0.000 & 82.043 & 1.00000 & 0.190 & 815.384 & 0.048 \\
-		(c) & 0.004 & 72.480 & 1.00000 & 0.270 & 813.640 & 0.036 \\
-		(d) & 0.000 & 87.372 & 1.00000 & 0.204 & 804.629 & 0.047 \\
-		(e) & 0.001 & 77.421 & 1.00000 & 0.245 & 822.940 & 0.036 \\
-		(f) & 0.001 & 76.934 & 1.00000 & 0.194 & 814.132 & 0.036 \\
-		(g) & 0.000 & 83.135 & 1.00000 & 0.197 & 808.503 & 0.047 \\
-		(h) & 0.001 & 77.301 & 1.00000 & 0.270 & 809.406 & 0.047 \\
-		(i) & 0.006 & 70.004 & 0.99999 & 0.268 & 813.217 & 0.051 \\
-		(j) & 0.001 & 78.576 & 1.00000 & 0.243 & 830.640 & 0.039 \\
-		\bottomrule
-        \end{tabular}
-\end{table}
-
-\subsubsection{Power-Law Transformation}
-Applying the power-law transformation under both cryptosystems produced less than accurate images.
-The accuracy varies greatly across all the images as in the case of Paillier, with mean squared errors as high as 8270.696 and as low as 616.419, and SSIM scores ranging from 0.43185 to 0.92334, as seen in Table~\ref{tbl:pwr-pal}.
-As expected, the total processing time now takes about 15 to 20 seconds per image since the power-law transformation is more computationally intensive due to its approximation of an infinite series consisting of terms using the logarithm function, which is also approximated using a combination of addition and multiplication operations.
-
-\begin{table}[h]
-	\centering
-	\caption{Power-law transformation under Paillier}
-	\label{tbl:pwr-pal}
-    \begin{tabular}{lcccccc}
-        \toprule
-        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
-        (a) & 3910.678 & 12.208 & 0.46712 & 0.099 & 14.695 & 0.024 \\
-		(b) & 873.064 & 18.720 & 0.84379 & 0.139 & 16.190 & 0.023 \\
-		(c) & 1261.059 & 17.123 & 0.77229 & 0.082 & 13.866 & 0.023 \\
-		(d) & 653.049 & 19.981 & 0.90673 & 0.083 & 15.507 & 0.023 \\
-		(e) & 646.310 & 20.026 & 0.88157 & 0.108 & 15.727 & 0.045 \\
-		(f) & 2047.933 & 15.018 & 0.69408 & 0.113 & 14.728 & 0.034 \\
-		(g) & 806.473 & 19.065 & 0.85346 & 0.082 & 14.253 & 0.024 \\
-		(h) & 616.419 & 20.232 & 0.92334 & 0.121 & 14.415 & 0.023 \\
-		(i) & 8270.696 & 8.955 & 0.43185 & 0.112 & 14.362 & 0.065 \\
-		(j) & 1715.478 & 15.787 & 0.73857 & 0.145 & 20.239 & 0.023 \\
-		\bottomrule
-        \end{tabular}
-\end{table}
-
-When Dasgupta--Pal was used in the power-law transformation, it completely failed to produce a discernible image and only resulted in a blank image.
-The mean squared errors for this case is an order of magnitude higher than the results from using Paillier.
-Furthermore, doing a power-law transformation under Dasgupta--Pal is not only impractical in terms of accuracy, but also it is impractical in terms of time efficiency because it took about 2 hours and 40 minutes on average to process each image.
-
-\begin{table}[h]
-	\centering
-	\caption{Power-law transformation under Dasgupta--Pal}
-	\label{tbl:pwr-dp}
-    \begin{tabular}{lcccccc}
-        \toprule
-        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
-		% \texttt{anpage} & 25115.891 & 4.131 & 0.00000 & 0.016 & 741.872 & 0.031 \\ 10x10
-		% \texttt{bplyce} & 22777.187 & 4.556 & 0.00000 & 0.017 & 730.873 & 0.003 \\ 10x10
-		% \texttt{drbost} & 18899.906 & 5.366 & 0.00000 & 0.014 & 733.409 & 0.003 \\
-		(a) & 25008.723 & 4.150 & 0.000 & 0.376 & 9700.926 & 1.269 \\
-		(b) & 22700.522 & 4.570 & 0.000 & 0.230 & 9196.609 & 0.043 \\
-		(c) & 18902.214 & 5.366 & 0.000 & 0.277 & 9261.407 & 0.150 \\
-		(d) & 12585.729 & 7.132 & 0.000 & 0.257 & 9259.010 & 0.051 \\
-		(e) & 17012.423 & 5.823 & 0.000 & 0.279 & 9440.351 & 0.051 \\
-		(f) & 31124.615 & 3.200 & 0.000 & 0.285 & 9492.149 & 0.052 \\
-		(g) & 22982.917 & 4.517 & 0.000 & 0.289 & 9321.928 & 0.048 \\
-		(h) & 13469.155 & 6.837 & 0.000 & 0.257 & 9233.818 & 0.048 \\
-		(i) & 37453.834 & 2.396 & 0.000 & 0.262 & 9203.045 & 0.048 \\
-		(j) & 23037.762 & 4.506 & 0.000 & 0.258 & 9210.393 & 0.048 \\
-		% \texttt{drbost} & 18902.214 & 5.366 & 0.00000 & 0.064 & 2261.407 & 0.110 \\ % 20x18
-		% \texttt{ksunth} & 12585.729 & 7.132 & 0.00000 & 0.044 & 2259.010 & 0.011 \\ % 20x18
-		% \texttt{martin} & 17012.423 & 5.823 & 0.00000 & 0.066 & 2440.351 & 0.011 \\
-		% \texttt{pmives} & 31124.615 & 3.200 & 0.00000 & 0.072 & 2492.149 & 0.012 \\
-		% \texttt{rnpwil} & 22982.917 & 4.517 & 0.00000 & 0.076 & 2321.928 & 0.008 \\
-		% \texttt{sbains} & 13469.155 & 6.837 & 0.00000 & 0.044 & 2233.818 & 0.008 \\
-		% \texttt{swewin} & 37453.834 & 2.396 & 0.00000 & 0.049 & 2203.045 & 0.008 \\
-		% \texttt{yfhsie} & 23037.762 & 4.506 & 0.00000 & 0.045 & 2210.393 & 0.008 \\
-		\bottomrule
-        \end{tabular}
-\end{table}
-
-\section{Conclusion}
-In this paper, we have assessed the feasibility and practicality of various homomorphic cryptosystems with regard to secure processing and manipulation of facial image data through creation of a software library that facilitates image processing operations within the encrypted domain, as well as our own implementation of some homomorphic cryptosystems like Dasgupta--Pal for which existing third-party libraries dedicated for this purpose are not yet available.
-
-% This paper also proposes a correction to the Dasgupta--Pal cryptosystem which is further explained in Appendix~\ref{chap:correction}.
-
-Even though an operation in a partially homomorphic cryptosystem is not theoretically possible, like multiplication of two ciphertexts under Paillier, it has been shown that such operations are indeed possible in a two-party system.
-Protocols for secure multiplication and exponentiation have been proposed and also applied to more complex image operations such as facial recognition.
-Thus, a partially homomorphic cryptosystem can be modified to admit more image processing operations by assuming a two-party system.
-
-Preliminary results have shown that both Paillier and Dasgupta--Pal apply image negation accurately and efficiently, as evidenced by the perfect zero MSE and infinite PSNR.
-For the logarithm transformation, Paillier was faster and accurate enough (with $\text{MSE} \le 30$ and $\text{SSIM} \approx 0.99$), but Dasgupta--Pal was slower but more accurate (with $\text{MSE} \le 0.01$ and $\text{SSIM} \approx 0.99999$) which was rather unexpected.
-However both Paillier and Dasgupta--Pal fail to produce accurate results in applying the power-law transformation, with the latter completely failing to produce discernible results.
-Based from these results, the Paillier cryptosystem is consistent enough to produce reasonable to accurate results.
-
-A wrapper library has been made which implements the various functions and methods of the cryptosystems into a single interface.
-This allowed us to express various image operations with a unified syntax, thus facilitating easier testing.
-
-\subsection{Ongoing and Future Work}
-Testing intensity transformations under the BGV cryptosystem will be started once the Pyfhel library is deemed stable enough to use, or another Python library that implements BGV becomes available. 
-One of the authors of this paper has already informed the developers of the Pyfhel library about a bug involving exponentiation of two real numbers.
-
-Efforts are ongoing with regard to the facial recognition tests.
-Our own implementation of the privacy-preserving  eigenfaces by Erkin, et al.
-does not yet use the DGK cryptosystem for secure integer comparison in the match finding step, thus we are working on implementing DGK from scratch.
-
-Another promising image operation to consider is \textit{facial detection} under a homomorphic cryptosystem.
-Work has been started in order to assess the feasibility of using Haar cascades in a privacy-preserving manner.
-
-Future work would involve improving and optimizing our implementation of the Dasgupta--Pal cryptosystem so that it performs faster.
-A suggestion would be to port the existing implementation to C/C++ and then create a Python library that acts as a wrapper to the C/C++ methods.
-For future studies, an implementation of a client-server framework or system dealing with secure image processing can be considered.

### 2019-03-12 icmssp-paper/parts/03_methodology.tex
Change folder structure
- renamed paper folder to icmssp-paper
- split icmssp paper into parts

--- 2019-02-10 paper/paper-conf.tex
@@
-\section{Introduction}
-\subsection{Context of the Study}
-Digital data privacy and security is a growing concern in various fields, such as cloud computing~\cite{potey_homomorphic_2016}, health information systems~\cite{kester_cryptographic_2015}, and video surveillance~\cite{upmanyu_efficient_2009}.
-To meet these needs, various cryptosystems have been developed.
-A cryptosystem is a system which operates on plaintexts, ciphertexts and keys using an encryption algorithm, which maps a plaintext to a ciphertext, together with a decryption algorithm, which maps a ciphertext to a plaintext, given an appropriate key~\cite{bauer_cryptosystem_2005}.
-The encryption and decryption algorithms are chosen such that the plaintext cannot easily be recovered from the ciphertext without knowledge of the key.
-This allows data to be securely transmitted over an insecure channel.
-
-One particular application of cryptography is image encryption.
-While cryptosystems used to encrypt digital data in general, such as the Advanced Encryption Standard (AES) or elliptic curve cryptography, can also be used to encrypt images~\cite{jain_image_2016, singh_image_2015} other algorithms created specifically for image encryption have also been developed~\cite{murugan_survey_2018}.
-
-In a homomorphic cryptosystem, operations such as addition and multiplication can be performed on encrypted data.
-These operations are then preserved when the data is decrypted.
-In this manner, data is manipulated without compromising data privacy, as the encrypted data being operated on remains secure~\cite{fontaine_survey_2007, sen_homomorphic_2013}.
-In the area of homomorphic image encryption, there is interest in being able to perform image manipulation operations on the encrypted data such as image adjustment, filtering, and morphological/feature extraction operations~\cite{ziad_cryptoimg:_2016, gonzalez_digital_2008}.
-More advanced operations have also been implemented using homomorphic cryptosystems, such as facial recognition \cite{hutchison_privacy-preserving_2009} and neural networks \cite{hesamifard_cryptodl:_2017}.
-This study in particular focuses on facial recognition.
-
-% \subsection{Research Questions}
-% By implementing homomorphic cryptosystems and creating a library so they can be easily used, we aim to address our main research question: What is the best method for facial image data to be encrypted and manipulated for practical applications?
-
-% More specifically, our research will address the following sub-questions:
-% \begin{enumerate}
-% 	\item Which homomorphic cryptosystems admit more image processing operations? How can existing homomorphic cryptosystems be modified to admit more image processing operations?
-% 	\item Which homomorphic cryptosystems are the most time-efficient and the most accurate in applying image processing operations?
-% 	\item Which homomorphic cryptosystems best preserve image quality in applying image processing operations?
-% \end{enumerate}
-
-\subsection{Research Objectives}
-% Previous attempts in the literature to provide image processing tasks such as image manipulation \cite{ziad_cryptoimg:_2016} and  facial recognition \cite{hutchison_privacy-preserving_2009} have primarily used the Paillier and  Damg{\aa}rd--Geisler--Kr{\o}igaard (DGK) cryptosystems to perform linear operations on encrypted data.
-% In this study, we extend this research to provide an objective comparison of various homomorphic cryptosystems currently in the literature in performing non-linear operations, and facial detection, as opposed to just linear operations and facial recognition.
-
-Our main research objective is to assess the practicality of various homomorphic cryptosystems with regard to image processing on faces. 
-% Homomorphic cryptosystems are known to be slower in terms of encryption, operation, and decryption time~\cite{sen_homomorphic_2013}.
-Furthermore, the operations on encrypted data supported by homomorphic cryptosystems are limited, and some schemes require preprocessing to be performed on images, limiting the range of operations which can be performed efficiently~\cite{li_elliptic_2012}.
-
-% In summary, in this study, we wish to
-More specifically, we wish to do the following:
-\begin{enumerate}
-    \item Implement common linear and non-linear image processing operations using known homomorphic encryption schemes, then determine which schemes admit more image processing operations and extend known cryptosystems to support more operations, if possible;
-    \item Compare the time efficiency and accuracy of common image processing operations under known homomorphic encryption schemes, and of common image processing operations without using homomorphic encryption;
-    \item Create a library to allow for convenient use and comparison of these homomorphic encryption schemes for image processing and facial recognition.
-\end{enumerate}
-
-\subsection{Scope and Limitations}
-% Our study will be limited in terms of the cryptosystems to be tested, the image processing operations we will implement, and the statistical tests we will use to gauge the security of the cryptosystems.
-Below is a listing of the scope of the study.
-
-% We will implement and test the following algorithms:
-In this study, we will implement and test the following cryptosystems:
-\begin{enumerate}
-	\item A variant of the Paillier cryptosystem~\cite{stern_public-key_1999} which supports floating-point operations, used in \textit{CryptoImg}~\cite{ziad_cryptoimg:_2016}.
-    \item The Damg{\aa}rd--Geisler--Kr{\o}igaard (DGK) cryptosystem~\cite{pieprzyk_efficient_2007, cryptoeprint:2008:321} which is primarily used for secure integer comparison.
-	% \item A fully homomorphic encryption scheme by Dasgupta and Pal, which uses polynomial rings~\cite{dasgupta_design_2016}.
-	\item The Brakerski--Gentry--Vaikuntanathan (BGV) cryptosystem \cite{cryptoeprint:2011:277}, an improvement on the lattice-based cryptosystem by Gentry~\cite{gentry_fully_2009}, with optimizations from Smart, Vercauteren, and Halevi \cite{hutchison_fully_2010, cryptoeprint:2011:566}.
-\end{enumerate}
-We will implement and test the following categories of image manipulation operations:
-\begin{enumerate}
-	\item Non-linear image intensity adjustment (logarithm and power-log transformations)
-	\item Facial detection and recognition using the eigenface approach \cite{turk_eigenfaces_1991}.
-\end{enumerate}
-We will adopt the benchmark for evaluating image quality of image encryption schemes presented by Ahmed, et.
-al~\cite{ahmed_benchmark_2016}.
-The presented benchmark reflects many tests used in other literature~\cite{ahmad_efficiency_2012, wu_npcr_2011}.
-\begin{enumerate}
-    \item Mean Squared Error (MSE)
-    \item Peak Signal to Noise Ratio (PSNR)
-    \item Structural Similarity Index (SSIM)
-\end{enumerate}
-A detailed overview of the above will be provided in the methodology. Grayscale images will be used in the study.
-A client-server model for secure computation will be assumed to allow operations such as secure comparison and exponentiation.
-Training and test data are taken from the publicly available \texttt{faces94} dataset (\url{https://cswww.essex.ac.uk/mv/allfaces/faces94.html}) maintained by the University of Essex.
-
-\subsection{Significance of the Study}
-This study aims to directly address one of the current problems in the research of homomorphic cryptosystems: the practicality of homomorphic encryption~\cite{sen_homomorphic_2013}.
-The literature shows existing homomorphic cryptosystems and how they support primitive operations (usually addition and multiplication) on encrypted data, however, for homomorphic cryptosystems to be useful for practical use, efficient support for more complicated image processing operation must be demonstrated as well.
-While implementations of image processing operations in a homomorphic cryptosystem exist in the literature~\cite{ziad_cryptoimg:_2016, garay_algorithms_2014}, our study targets the more computationally intensive task of facial detection.
-
-We wish to contribute to existing models for the secure transmission and modification of image data by developing a software library which allows the use and comparison of various homomorphic encryption algorithms.
-Our software library would allow service providers to perform image manipulation for clients without compromising data privacy.
-
-\section{Review of Related Literature}
-\subsection{Homomorphic Cryptosystems}
-A cryptosystem consists of an encryption function $\mathcal{E}$ and a decryption function $\mathcal{D}$, along with the plaintext space $\mathcal{P}$, ciphertext space $\mathcal{C}$ and the key space $\mathcal{K}$~\cite{bauer_cryptosystem_2005}.
-A \textit{plaintext} is text that can be commonly understood, while a \textit{ciphertext} results from encrypting the plaintext using an encryption key.
-The \textit{plaintext space} is the set of all possible plaintexts, the \textit{ciphertext space} is the set of all possible ciphertexts, while the \textit{keyspace} is the set of all possible keys.
-
-% There are two kinds of cryptosystems, \textit{symmetric} and \textit{asymmetric}.
-In symmetric-key cryptosystems, the same key is used for both encryption and decryption.
-As a consequence, symmetric-key cryptosystems must be implemented with a secure key exchange protocol, so that both the sender and receiver have access to the same key.
-Prominent examples of symmetric-key cryptosystems are the Data Encryption Standard (DES), and its replacement, the Advanced Encryption Standard (AES).
-
-% On the other hand, asymmetric-key (or public-key) cryptosystems use separate keys for encryption and decryption.
-The encryption key (also called the \textit{public key}) is shared publicly, while the decryption key (also called the \textit{private key}) is kept secret.
-Since the public key and private keys are different, there is no need to agree upon secure key exchange protocols.
-Usually, the security of asymmetric-key cryptosystems relies on the intractability of certain computational problems, for example, the RSA cryptosystem depends on the difficulty of big integer factorization~\cite{rivest_method_1978}, while the ElGamal cryptosystem depends on the difficulty of the discrete logarithm problem~\cite{blakley_public_1985}.
-
-% Homomorphic cryptosystems are a special type of cryptosystem in which operations can be securely performed on encrypted data.
-Suppose that for a public-key cryptosystem, $\mathcal{E}_k \left(p \right)$ is the encryption function using the public key $k \in \mathcal{K}$, and $\mathcal{D}_l \left(c \right)$ be the decryption function using the private key $l$.
-A cryptosystem is said to be homomorphic if its encryption function is homomorphic, that is, if it satisfies the relation
-% \begin{equation}
-%     \mathcal{E}_k \left(p_1 \boxplus p_2\right) = \mathcal{E}_k \left(p_1\right) \boxdot \mathcal{E}_k \left(p_2\right)
-% \end{equation}
-% where $p_1, p_2 \in \mathcal{P}$ are the plaintexts, and $\boxplus$ and $\boxdot$ are operations in $\mathcal{P}$ and $\mathcal{C}$ respectively~\cite{fontaine_survey_2007}.
-Furthermore, a homomorphic cryptosystem also satisfies~\cite{li_elliptic_2012}
-% \begin{equation}
-%     p_1 \boxplus p_2 = \mathcal{D}_l \left( \mathcal{E}_k \left(p_1\right) \boxdot \mathcal{E}_k \left(p_2\right) \right).
-% \end{equation}
-
-% In other words, 
-A homomorphic cryptosystem preserves the operations that can be done with the plaintext without requiring an intermediary step of decrypting the ciphertext beforehand.
-It is important to note that the operations in the plaintext space and ciphertext space need not be the same.
-A simple operation in the plaintext space may require a computationally intensive operation in the ciphertext space.
-
-% Homomorphic cryptosystems can be classified according to the plaintext and ciphertext operations, $\boxplus$ and $\boxdot$.
-If the plaintext operation $\boxplus$ is addition, the cryptosystem is said to be \textit{additively homomorphic}, and the cryptosystem is said to be \textit{multiplicatively homomorphic} if the plaintext operation $\boxplus$ is multiplication.
-
-\subsection{Partially Homomorphic Cryptosystems}
-In this section, we will present two classical partially homomorphic cryptosystems which we will be testing in the study: the Paillier cryptosystem and the DGK cryptosystem.
-Both of these cryptosystems encrypt integer plaintexts as integer ciphertexts.
-In our description of each cryptosystem, we use $E(m)$ to denote the encryption of a plaintext $m$, and $D(c)$ to denote the decryption of a ciphertext $c$.
-
-% We will then show that the cryptosystems can be modified to support privacy-perserving polynomial evaluation in a client-server protocol: given an encrypted message $m$, evaluate $f(m)$ where $f$ is a polynomial function.
-
-\subsubsection{The Paillier Cryptosystem}
-The Paillier cryptosystem \cite{stern_public-key_1999}, developed by Pascal Paillier, is a probabilistic encryption scheme which is based on the composite residuosity class problem.
-The scheme has several well--known homomorphic properties.
-% The scheme allows for the encryption and decryption of integer messages, and is known to be additively homomorphic.
-% We now state the encryption and decryption algorithms of the Paillier cryptosystem and its homomorphic properties.
-
-% \paragraph{Key Generation}
-% We first define a function $L(x)$ as the largest integer $v$ greater than zero such that $x-1 \geq vn$.
-% We choose two large primes $p$ and $q$, and set $n = pq, \lambda = \mathrm{lcm}(p-1,q-1)$.
-% Then we select an integer $g$, $0\leq g \leq n^2$ such that $\mathrm{gcd}(L(g^\lambda \bmod n^2), n) = 1$.
-% We denote the public key as $(g,n)$ and the private key $(p,q)$.
-
-% \paragraph{Encryption and Decryption}
-% The encryption function to encrypt a plaintext $m \in \mathbb{Z}_n$ given a public key $(g,n)$ is defined as
-% \begin{align*}
-%   E(m) = g^m \cdot r^n \mod{n^2},
-% \end{align*}
-% where $r$ is a random non-negative integer less than $n^2$.
-
-% The decryption function to decrypt a ciphertext $c \in \mathbb{Z}^\ast_{n^2}$ given a private key $(p,q)$ is defined as:
-% \begin{align*}
-%   D(c) = L(c^\lambda \bmod n^2) \times (L(g^\lambda \bmod n^2))^{-1} \mod n
-% \end{align*}
-
-% \paragraph{Homomorphic Properties of the Paillier Cryptosystem}
-% The Paillier cryptosystem supports additive homomorphism as well as the multiplication of a plaintext scalar to an encrypted message.
-These homomorphic properties are used to add a plaintext scalar to a ciphertext, add two ciphertexts, and multiply a ciphertext by a plaintext scalar, respectively.
-They are defined as follows.
-
-For all $m_1,m_2 \in \mathbb{Z}_n$ and $k\in \mathbb{N}$, the following homomorphic properties hold for the Paillier cryptosystem with public key $(g,n)$.
-\begin{align*}
-  D(E(m_1)g^k\bmod n^2) &=(m_1+k)\bmod n\\
-  D(E(m_1)E(m_2)\bmod n^2) &=(m_1+m_2)\bmod n\\
-  D(E(m_1)^k\bmod n^2) &= km_1\bmod n
-\end{align*}
-
-These homomorphic properties are used to add a plaintext scalar to a ciphertext, add two ciphertexts, and multiply a ciphertext by a plaintext scalar, respectively.
-
-\subsubsection{The DGK Cryptosystem}
-The DGK cryptosystem was published by Damg{\aa}rd, Geisler, and Kr{\o}igaard in 2007 in an effort to create a secure integer comparison scheme \cite{pieprzyk_efficient_2007, cryptoeprint:2008:321} which is widely used in the literature \cite{veugen_improving_2012}.
-The DGK cryptosystem has homomorphic properties similar to the Paillier cryptosystem.
-
-% \paragraph{Key Generation}
-% We denote $k,t,\ell$ as security parameters of the scheme, where $k>t>\ell$.
-% Let $p,q$ be primes such that
-% we can choose two $t$-bit primes $v_p$ and $v_q$ such that $v_p | (p-1)$ and $v_q | (q-1)$, and a small prime $u$ such that $u | (p-1)$ and $u | (q-1)$.
-% We denote $n = pq$.
-% We choose $g$ to be an integer of order $uv_pv_q$ and $h$ to be of order $v_pv_q$.
-
-% The DGK cryptosystem encrypts plaintexts in $\mathbb{Z}_u$ to ciphertexts in $\mathbb{Z}_n^\ast$.
-
-% The public key is $(n,g,h,u)$ and the private key is $(p,q,v_p,v_q)$.
-
-% \paragraph{Encryption and Decryption}
-% To encrypt a message $m \in \mathbb{Z}_u$, the encryption function is defined as:
-% \begin{align*}
-%   E(m) = g^m \cdot h^r \mod{n},
-% \end{align*}
-% where $r$ is a random integer in $\mathbb{Z}_n$ which is longer than $2t$ bits.
-
-% To decrypt a ciphertext $c \in \mathbb{Z}_n^\ast$, decryption is achieved by first computing $c^{v_pv_q}$.
-% \begin{align*}
-% 	c^{v_pv_q} \bmod n
-% 	&= (g^m \cdot h^r)^{v_pv_q} \bmod n\\
-% 	&= (g^{v_pv_q})^m \bmod n
-% \end{align*}
-% Since $(g^{v_pv_q})^m$ has order $u$, there is a one-to-one correspondence between plaintexts in $\mathbb{Z}_u$ and  $(g^{v_pv_q})^m$.
-A lookup table can thus be generated privately to successfully recover $m$.
-
-% \paragraph{Homomorphic Properties of the DGK Cryptosystem}
-% The DGK cryptosystem supports additive homomorphism as well as the multiplication of a plaintext scalar to an encrypted message.
-These homomorphic properties are used to add a plaintext scalar to a ciphertext, add two ciphertexts, and multiply a ciphertext by a plaintext scalar, respectively.
-They are defined as follows.
-
-For all $m_1,m_2 \in \mathbb{Z}_u$ and $k\in \mathbb{N}$, the following homomorphic properties hold for the DGK cryptosystem with public key $(n,g,h,u)$.
-\begin{align*}
-    D(E(m_1)g^k) &=(m_1+k)\bmod u\\
-    D(E(m_1)E(m_2)) &=(m_1+m_2)\bmod u\\
-    D(E(m_1)^k) &= km_1\bmod u
-\end{align*}
-
-As the multiplicative homomorphism was not presented in the original paper, we provide a short proof here.
-\begin{proof}
-  Let $m \in \mathbb{Z}_u$ and $k\in \mathbb{N}$.
-  We consider $E(m)^k = (g^m \cdot h^r \bmod{n})^k\bmod n$.
-  \begin{align*}
-    (g^m \cdot h^r \bmod{n})^k \bmod n
-    &= (g^m \cdot h^r)^k \bmod{n}\\
-    &= (g^m)^k \cdot (h^r)^k \bmod{n}\\
-    &= g^{km} \cdot (h^kr) \bmod{n}
-  \end{align*}
-  Since $r$ is a random integer, $kr$ is also a random integer, Therefore, $g^{km} \cdot (h^kr) \bmod{n} = D(E(m_1)^k)$ is a valid encryption of the message $km$.
-\end{proof}
-
-% \subsubsection{Secure Exponentiation and Multiplication Protocols}
-% \label{ssec:exponentiationprotocol}
-% [TO-DO: This is further explained in another paper.]
-% In order to perform polynomial evaluation, we first present a protocol for privacy-preserving exponentiation to a positive integer power, adapted from the protocol to calculate Euclidean distances used in \cite{hutchison_privacy-preserving_2009}.
-
-% The following protocols apply to both the Paillier and DGK cryptosystems, as they share similar homomorphisms. We first present a secure squaring protocol.
-
-% Suppose Alice encrypts an integer $x$ and sends it so Bob has $E(x)$, and wants to obtain $E(x^2)$ without exposing the value of $x$.
-% \begin{itemize}
-% 	\item Bob first selects a random integer $r$ and computes $E(x+r)$. Bob can do this since $r$ is a plaintext constant.
-% 	\item Bob sends $E(x+r)$ to Alice, who decrypts the ciphertext to obtain $x+r$.
-% 	\item Alice squares $x+r$ and encrypts the result. She sends $E((x+r)^2)$ to Bob.
-% 	\item Bob computes $E(-2rx + r^2)$. He then computes $E((x+r)^2)E(-2rx + r^2) = E(x^2)$.
-% \end{itemize}
-
-% We can use the secure squaring protocol to arrive at a secure multiplication protocol, which then allows for the evaluation of polynomials.
-% Suppose Alice encrypts integers $x$ and $y$, and Bob has $E(x), E(y)$ and wants to obtain $E(xy)$.
-% \begin{itemize}
-% 	\item Bob acquires $E(x^2), E(y^2)$ using the secure squaring protocol.
-% 	\item Bob sends $E(x+y)$ to Alice, who decrypts the ciphertext to obtain $x+y$.
-% 	\item Alice sends $E((x+y)^2)$ to Bob.
-% 	\item Bob then computes
-% 	\begin{align*}
-% 		E((x+y)^2)E(x^2)^{-1}E(y^2)^{-1} &= E((x+y)^2 - x^2 - y^2)\\
-% 		&= E(2xy)
-% 	\end{align*}
-% 	\item Bob can then recover $E(xy)$ by calcuating for the multiplicative inverse of 2 using the Euclidean algorithm, and calculating $2^{-1}E(xy)$.
-Such an inverse exists since the modulus is either a prime (in the DGK cryptosystem) or a product of primes greater than 2 (in the Paillier cryptosystem).
-% \end{itemize}
-
-\subsection{Fully Homomorphic Cryptosystems}
-We will also be testing fully homomorphic cryptosytems, which allow aribitrary computation on encrypted data.
-While generally being more flexible, fully homomorphic cryptosytems are known to be significantly slower than partially homomorphic cryptosytems; improving the efficiency of fully homomorphic cryptosytems is an active area of research \cite{sen_homomorphic_2013}.
-
-% We will present two such cryptosystems, the Dasgupta--Pal cryptosystem, which we present in full to explain a correction we propose to it, and the BGV cryptosystem, which has open source implementations availble primarily used in homomorphic cryptography research.
-
-% \subsubsection{The Dasgupta--Pal Cryptosystem}
-% The Dasgupta--Pal cryptosystem is a fully homomorphic cryptosystem proposed in 2016 by Smaranika Dasgupta and S.
-K.
-Pal \cite{dasgupta_design_2016}, which encrypts integer plaintexts in $\mathbb{Z}_n$ to polynomial ciphertexts.
-We begin our presentation of the Dasgupta--Pal cryptosystem with the following definition.
-
-% Given a message $m \in \mathbb{Z}$, we denote
-% \begin{align*}
-% 		m_p(x) = a_0 + a_1 x + a_2 x^2 + \cdots + a_k x^k
-% \end{align*}
-% where $a_k a_{k-1}\cdots a_2 a_1 a_0$ is the binary representation of $m$.
-
-% In the original scheme presented in \cite{dasgupta_design_2016}, the secret key $S_k$ is set to be a large prime.
-In Appendix \ref{chap:correction}, we present a case where the Dasgupta--Pal cryptosystem fails and prove that setting the secret key $S_k = 2p$, where $p$ is a large prime, corrects errors in the Dasgupta--Pal cryptosystem.
-% We now decribe the correct cryptosystem.
-% \paragraph{Corrected Dasgupta--Pal Cryptosystem Description}
-% Let $\ell$ denote the security parameter of the cryptosystem.
-% Let $S_k = 2p$, where $p$ is a prime number with $\ell - 1$ bits.
-% Choose a random even integer $z$ of length $\log_2{\ell}$.
-
-% Let the secret key be $S_k$, and let the refresh key be $R_k = z \cdot S_k$. The secret key is kept private to the encrypting/decrypting parties, while the refresh key is made publicly available.
-
-% The scheme defines the encryption algorithm for a message $m$ as follows:
-% \begin{align*}
-% 	E(m) = y(x) + S_k\times d(x)
-% \end{align*}
-% where
-% $y(x)$ is a polynomial of degree $n$ such that $m_p(x) \equiv y(x) \bmod S_k$ and $d(x)$ is a randomly chosen polynomial of degree $n$.
-This encrypts each coefficient of $m_p(x)$ by adding some multiple of $S_k$ to it.
-Through this process, each bit of the message is encrypted separately.
-
-% Furthermore, the decryption algorithm to recover $m_p(x)$ from a ciphertext polynomial $c(x)$ as
-% \begin{align*}
-% 	m_p(x) = c(x) \bmod S_k \bmod 2.
-% \end{align*}
-% Thus $D(c(x))$ is defined as the integer recovered from the coefficients of the polynomial $c(x) \bmod S_k \bmod 2$.
-
-% Dasgupta and Pal note that homomorphic operations on ciphertext introduce noise which may interfere with decryption, due to the potential increase in ciphertext values.
-% To eliminate noise from a polynomial ciphertext, the following refresh function is used:
-% \begin{align*}
-% 	R(c(x)) = c(x) \bmod R_k.
-% \end{align*}
-
-% \paragraph{Homomorphic Properties of the Dasgupta--Pal Cryptosystem}
-% It has been shown \cite{dasgupta_design_2016} that the following properties hold for all integer messages $m_1, m_2 \in \mathbb{Z}_n$ in the Dasgupta--Pal cryptosystem.
-These properties arise since each coefficient in a ciphertext polynomial is essentially an independently encrypted bit of the original message.
-% \begin{description}
-% 	\item[\textsc{xor} on ciphertexts]
-% 	A bitwise exclusive or (\textsc{xor}) operation on integer messages can be achieved by adding the coefficients pairwise between two ciphertexts.
-% 	\begin{align*}
-% 		D(E(m_1)+E(m_2)) = m_1 \textsc{ xor } m_2
-% 	\end{align*}
-% 	\item[\textsc{and} on ciphertexts]
-% 	Similarly, pair-wise multiplication corresponds to bitwise \textsc{and} of integer messages.
-% 	\begin{align*}
-% 		D(E(a) \otimes E(b)) = a \textsc{ and } b = ab \bmod 2
-% 	\end{align*}
-% 	where $\otimes$ denotes pairwise multiplication,
-% 	\begin{align*}
-% 		\sum_{i=1}^n{a_ix^i} \otimes \sum_{i=1}^n{b_ix^i} = \sum_{i=1}^n{a_ib_ix^i}.
-% 	\end{align*}
-% \end{description}
-
-% Arbitrary computation on data can thus be achived using these bitwise operations.
-While the Dasgupta--Pal cryptosystem requires significant amounts of memory, as each bit of plaintext is encrypted into an integer, this approach provides a flexible method to perform relatively fast arbitrary computation on encrypted data.
-Encryption and decryption in the Dasgupta--Pal cryptosystem are accomplished using few arithmetic operations.
-
-% \subsubsection{HElib and the BGV Cryptosystem}
-The BGV (Brakerski--Gentry--Vaikuntanathan) cryptosystem \cite{cryptoeprint:2011:277} is a fully homomorphic cryptosystem created based on the ring-learning with error problem.
-The BGV cryptosystem was constructed to surpass the limitations of prior fully homomorphic cryptosystems, which were based on the first fully homomorphic cryptosystem by Gentry \cite{gentry_fully_2009}.
-
-The details regarding the construction of the BGV cryptosystem are beyond the scope of this paper.
-For this study, we will be using \textit{HElib} \cite{garay_algorithms_2014}, an open-source library which implements the BGV cryptosystem with optimizations to improve efficiency.
-Evaluation of operations on 120 inputs in HELib was performed in around 4 minutes, with an average of 2 seconds to process a single input \cite{hutchison_fully_2010,cryptoeprint:2011:566}.
-
-The \textit{HElib} library has been adapted to Python using the Pyfhel library \cite{pyfhel_2018} maintained by Ibarrondo, Laurent (SAP) and Onen (EURECOM), and licensed under the GNU GPL v3 license.
-The Pyfhel library is a Python API for the \textit{HElib} library, which supports the following operations on vectors/scalars of integers or binary ciphertexts:
-\begin{itemize}
-	\item Arithmetic operations: addition, subtraction, multiplication;
-	\item Binary operations: \textsc{and}, \textsc{or}, \textsc{not}, \textsc{xor}.
-\end{itemize}
-
-\subsection{CryptoImg}
-A paper published in 2009 by Ziad, et al.
-attempts to implement privacy-preserving image processing using \textit{CryptoImg}, a library for the Open Source Computer Vision Library (OpenCV)~\cite{bradski_opencv_2000} which implements various homomorphic encryption and image processing routines using the Paillier homomorphic cryptosystem~\cite{ziad_cryptoimg:_2016}.
-The CryptoImg library assumed a client-server model wherein a client requests image processing operations from a server.
-A client first encrypts a digital image and sends the image securely to a server, which then operates on the encrypted image without revealing its contents.
-Then the resulting image is sent back to the client, which decrypts the image to recover the desired output.
-\begin{figure}[!ht]
-    \centering
-    \includegraphics[width=0.4\textwidth]{figures/ClientServerModel.png}
-    \caption{Client-server architecture used by \textit{CryptoImg} \cite{ziad_cryptoimg:_2016}}
-    \label{fig:clientserver}
-\end{figure}
-
-The \textit{CryptoImg} library implemented the following:
-\begin{enumerate}
-	\item Extending the Paillier homomorphic cryptosystem which operate on integer plaintexts so that they can operate on real number plaintexts;
-	\item Developing protocols for and implementing the following image processing operations
-	\begin{enumerate}
-		\item Image negation and brightness adjustment
-		\item Spatial filters (for noise reduction, edge detection and sharpening)
-		\item Morphological operations
-		\item Histogram equalization
-	\end{enumerate}
-\end{enumerate}
-For image negation and spatial filters, the protocols specified by \textit{CryptoImg} allow all image processing operations to be performed on the server.
-However, due to limitations in the Paillier cryptosystem, the protocols presented for morphological operations and histogram equalization require both the client and the server to perform image processing calculations, although the server performs a significant portion of the processing.
-
-Ziad, et al.
-also showed experimental results establishing the slow performance of image operations under a homomorphic cryptosystem.
-For instance, while sharpening and applying a Sobel filter each take less than a second when applied to a $512\times 512$ plaintext image, when applied to an encrypted image, sharpening required at least 238.257 seconds, and applying the Sobel filter required at least 147.567 seconds \cite{ziad_cryptoimg:_2016}.
-
-We now discuss several limitations in the \textit{CryptoImg} study which we focus on for our research.
-First, the \textit{CryptoImg} library was limited in the image intensity transformations it implemented.
-We propose additional protocols to support more computationally intensive intensity transformations.
-Second, the \textit{CryptoImg} library only considered the Paillier cryptosystem.
-We consider testing the performance of other homomorphic cryptosystems, which differ in their processing time and supported operations.
-
-\subsection{Image Intensity Transformations}
-We represent a digital image $R$ as an $M \times N$ matrix of pixel intensity values, each value in the range $\left[0, L-1\right]$, for some positive integer $L$.
-We denote with $R(x,y)$ the entry at the $x$th row and $y$th column of a matrix $R$.
-An intensity transformation on an image $R$ can be defined as a function $T$ which maps a pixel value $r$ to a new value $r^\prime$, which we can write as $r^\prime = T\left(r\right)$.
-This function is then applied to every pixel in $R$.
-The \textit{CryptoImg} library implemented two types of linear intensity transformations: image negation and brightness control.
-
-An image negation transformation is defined as:
-\begin{equation}
-    T\left(r\right) = L-1-r
-\end{equation}
-After applying image negation, the resulting image would be similar to a photographic negative~\cite{gonzalez_digital_2008}.
-
-A brightness control transformation with parameter $v$ is defined as:
-\begin{equation}
-    T\left(r,v\right) = r+v
-\end{equation}
-The above transformations are linear in terms of the input $r$, and are thus simple to implement under a homomorphic cryptosystem.
-
-In this study we extend the range of intensity transformations to non-linear transformations.
-Two common non-linear image transformations are the logarithm transformation and power-law transformation~\cite{gonzalez_digital_2008}.
-
-The logarithm transformation is used to enhance dark pixels or increase the dark details of an image by mapping low intensity values to a wider range of values~\cite{gonzalez_digital_2008}.
-This has the general formula
-\begin{equation}
-    T\left(r\right) = c \log\left(1 + r\right)
-\end{equation}
-where $c$ is a constant.
-
-The power-law transformation is a family of transformations that have the form
-\begin{equation}
-    T\left(r\right) = c r^{\gamma}
-\end{equation}
-where $c>0$ and $\gamma > 0$.
-A power-law transformation defined by the above equation can calibrate the operation of many image capture and output devices such as cameras, printers and displays in a process called \textit{gamma correction}.
-% This ensures reproducibility and accuracy of images being displayed by digital output devices~\cite{gonzalez_digital_2008}.
-
-To implement non-linear intensity transformations using addition and multiplication in a homomorphic system, it is necessary to approximate the logarithm and exponential functions, which may result in higher computational overhead.
-In our software library implementation, we investigate methods required to approximate the logarithm and power functions.
-Non-linear intensity transformations such as the logarithm transformation have applications in intensity normalization \cite{oravec_illumination_2010}, which is used in some facial recognition algorithms to account for differences in lighting which make facial recognition difficult.
-
-\subsection{Facial Detection and Recognition}
-
-Since simple image operations mentioned earlier can be done within a homomorphic cryptosystem, these operations can be assembled together in order to do more complex operations.
-A prominent application of image processing that often uses complex image operations is \textit{facial recognition}.
-
-Traditional facial recognition algorithms rely on detecting salient features in a face image. One of the popular facial recognition algorithms is \textit{eigenfaces}.
-% Traditional facial recognition algorithms rely on detecting salient features in a face image. Two of the popular facial recognition algorithms are \textit{eigenfaces} and \textit{Haar cascades}.
-
-\subsubsection{Eigenfaces}
-Proposed by Matthew Turk and Alex Pentland, the eigenfaces method uses principal component analysis (PCA) in order to express an input image as a linear combination of eigenfaces \cite{turk_eigenfaces_1991}.
-An \textit{eigenface} is a principal component, or more simply an eigenvector that represents a certain variation between the face images which are taken from the initial training set.
-The number of resulting eigenfaces is equal to the number of face images in the training set.
-
-% In the enrollment process, $M$ face images $\Theta_1, \ldots, \Theta_M$, each of size $p \times q$, are taken in to comprise the initial training set.
-The training images can be represented as vectors of length $N = pq$, where each row of an image is concatenated together.
-
-% The average of the training images, denoted as $\Psi$, is 
-% \begin{equation}
-% 	\Psi = \frac{1}{M} \sum_{i=1}^{M} \Theta_i
-% \end{equation}
-
-% The \textit{difference vectors} are then computed as $\Phi_i = \Theta_i - \Psi$. PCA is applied on the covariance matrix of the vectors
-% \begin{equation}
-% 	\mathbf{C} = \frac{1}{M} \sum_{i=1}^M \Phi_i \Phi_i^\top = \frac{1}{M} \mathbf{A}\mathbf{A}^\top,
-% \end{equation}
-% where $\mathbf{A}$ is an $N \times M$ matrix defined by $\left[\Theta_1 \quad \Theta_2 \quad \cdots \quad \Theta_M\right]$, in order to determine the orthonormal eigenvectors \cite{hutchison_privacy-preserving_2009}.
-
-% Directly computing the covariance matrix and then applying PCA will become inefficient for large sizes of $\mathbf{A}$, since computing for $\mathbf{A}\mathbf{A}^\top$ results in an $N \times N$ matrix, which can get drastically large because it is dependent on the size of the image.
-On the other hand, computing for $\mathbf{A}^\top\mathbf{A}$ only results in an $M \times M$ matrix, which is much smaller than the previous one because it is just dependent on the number of face images in the training set.
-Now, we can apply PCA to $\mathbf{A}^\top\mathbf{A}$ along with some post-processing to obtain the eigenvectors \cite{hutchison_privacy-preserving_2009}.
-
-% Instead of getting the eigendecomposition of the covariance matrix by explicitly computing the eigenvalues and eigenvectors of $\mathbf{C}$, we can also apply \textit{singular value decomposition} (SVD) on the matrix $\Phi^\top$.
-This is because SVD works through a divide-and-conquer method which results in greater numerical stability, while eigendecomposition simply uses the traditional QR factorization \cite{nakatsukasa_stable_2013, gu_divide-and-conquer_1995}.
-Upon applying SVD, we now get the eigenvectors $\mathbf{u}_1, \ldots, \mathbf{u}_M$ and their corresponding eigenvalues $\lambda_1, \ldots, \lambda_M$.
-
-% We choose $K$ eigenvectors $\mathbf{u}_1, \ldots, \mathbf{u}_K$ such that it comprises a set associated with the $K$ largest eigenvalues, where $K$ is much smaller than $M$.
-This set is now the \textit{face space}.
-Then, the images $\Theta_1, \ldots, \Theta_K$ are projected onto the face space spanned by the eigenfaces to determine the weight vectors $\Omega_1, \ldots, \Omega_K$.
-
-% To perform the recognition process, the algorithm projects the input image $\Gamma$ onto the face space, and then comparing the projected image $\bar{\Omega} = \mathbf{u}_i\left(\Gamma - \Psi\right)$ with each eigenface in the face space using a metric such as the Euclidean distance.
-Thus it is computed as $d_i = \left\lVert \Omega_i -\bar{\Omega} \right\rVert$ for all $i=1,\ldots,K$, where $\left\lVert \cdot \right\rVert$ denotes the Euclidean norm.
-
-% Then, a match can be reported if the smallest possible distance is smaller than the given threshold value $T$. 
-% \newcommand{\argmin}{\mathop{\mathrm{arg\,min}}}  
-% \begin{equation}
-% 	\text{ID} = \begin{cases}\argmin_i d_i & \text{if } \min_i d_i \le T \\\emptyset & \text {otherwise}\end{cases}
-% \end{equation}
-
-\subsection{Previous Implementations of Secure Facial Recognition}
-Erkin, et al.
-\cite{hutchison_privacy-preserving_2009} devised a method to incorporate the use of homomorphic cryptosystems into the eigenfaces method.
-In their study, they proposed a two-party system where Alice holds an encrypted image $\left[\Gamma\right]$, while Bob maintains a database of $K$ eigenfaces $\mathbf{u}_1, \ldots, \mathbf{u}_K$, and feature vectors $\Omega_1, \ldots, \Omega_M$ in the clear.
-
-\begin{figure}[!h]
-    \centering
-    \includegraphics[width=0.4\textwidth]{figures/secure_eigenfaces.png}
-    \caption{Diagram of the privacy-preserving facial recognition process \cite{hutchison_privacy-preserving_2009}}
-\end{figure}
-
-In order to ensure privacy, the steps in the eigenfaces algorithm, namely: projection, distance computation, and match finding, are done within the encrypted domain, i.e., using the operations in the Paillier cryptosystem.
-
-Projection is similar to that of the original eigenfaces algorithm, except the operations are replaced with their respective operations in the cryptosystem.
-Distance computation in this version is somewhat different from the original eigenfaces method, in that it deals with the square of the Euclidean distance since the relative order of the distances is only important when comparing these during the match finding step \cite{hutchison_privacy-preserving_2009}.
-\begin{align}
-    d_i &= \left\lVert \Omega_i - \bar{\Omega} \right\rVert ^2 = \sum_{j=1}^{K} \left(\omega_{ij} - \bar{\omega}_j\right)^2 \\
-        &= \underbrace{\sum_{j=1}^{K} \omega_{ij}^2}_{\mathcal{S}_1} + \underbrace{\sum_{j=1}^{K} \left(-2 \omega_{ij} \bar{\omega_j}\right)}_{\mathcal{S}_2} + \underbrace{\sum_{j=1}^{K} \bar{\omega}_{j}^2}_{\mathcal{S}_3}
-\end{align}
-
-Computing for the distances within Paillier would just be multiplying the encrypted sums together.
-\begin{equation}
-	\left[d_i\right] = \left[\mathcal{S}_1\right] \cdot \left[\mathcal{S}_2\right] \cdot \left[\mathcal{S}_3\right]
-\end{equation}
-
-The terms $\left[\mathcal{S}_1\right]$ and $\left[\mathcal{S}_2\right]$ can be easily computed by Bob, since he already knows both $\omega_i$ in the clear and $\left[\bar{\omega}_i\right]$ which is in encrypted form.
-Computing for $\left[\mathcal{S}_3\right]$ is trickier because Bob cannot compute for $\left[\bar{\omega}_i^2\right]$ because pairwise multiplication is not supported in Paillier, that is why Bob needs help from Alice to square a number through a protocol described below \cite{hutchison_privacy-preserving_2009}.
-
-Before Bob sends $\left[\bar{\omega}_i\right]$ to Alice for squaring, he adds a random number $r_i$ to compute $\left[x_i\right] = \left[\bar{\omega}_i + r_i\right] = \left[\bar{\omega}_i\right] \cdot \left[r_i\right]$, where $r_i$ is obviously distinct for every $i$, then sends $\left[x_i\right]$ to Alice.
-She then decrypts it and computes $x_i^2$, and then computes $\mathcal{S}_3^\prime = \sum_{i=1}^{K} x_i^2$, after which she encrypts the sum and sends $\left[\mathcal{S}_3^\prime\right]$ to Bob.
-Now, he can compute for $\left[\mathcal{S}_3\right]$ as follows:
-\begin{equation}
-	\left[\mathcal{S}_3\right] = \left[\mathcal{S}_3^\prime\right] \cdot \prod_{j=1}^{K} \left(\left[\bar{\omega}_j\right]^{-2r_j} \cdot \left[-r_j^2\right]\right)
-\end{equation}
-
-The protocol for squaring a number as described earlier is a workaround for the limitations of Paillier or any other partially homomorphic cryptosystem that only supports addition and scalar multiplication.
-% This can be possibly extended so that operations such as pairwise multiplication and exponentiation are also supported, provided that the protocol involves two parties.
-
-The match finding step is done by comparing the distances obtained from the previous step to a specified threshold $T$.
-If the minimum distance is smaller than $T$, then a match is found, and the encrypted identity of the match is returned to Alice \cite{hutchison_privacy-preserving_2009}.
-Getting the minimum among the encrypted distances would involve comparing two encrypted numbers, which Paillier does not support.
-Instead, the DGK cryptosystem \cite{pieprzyk_efficient_2007} is used for the comparison protocol.
-
 \section{Methodology}
@@
 % \end{itemize}
-
-\section{Preliminary Results and Discussion}
-The results shown in this section are gathered from the tests for intensity transformations under Paillier and Dasgupta--Pal cryptosystems.
-During testing, initial results obtained from BGV, particularly with image operations involving floating-point numbers like the logarithmic transformation, were unstable (i.e.
-the results vary drastically every time the same tests were done).
-This is because the Pyfhel library being used for the BGV cryptosystem is still in alpha development stage \cite{pyfhel_2018}.
-
-% One of the authors has already informed the maintainers of the library about a bug involving exponentiation of two real numbers.
-
-\subsection{Intensity Transformations}
-
-\begin{table*}
-	\centering
-	\caption{Comparison of intensity transformations under Paillier}
-	\label{tbl:it-pal}
-	\begin{tabular}{m{1cm}*{7}{>{\centering\arraybackslash}m{1.75cm}}}
-		\toprule
-		\multirow{2}{*}{Image} & \multirow{2}{*}{Original} & \multicolumn{2}{c}{Image negation} & \multicolumn{2}{c}{Logarithm transformation} & \multicolumn{2}{c}{Power-law transformation} \\
-							   &                           & PDT           & CDT          & PDT            & CDT           & PDT               & CDT           \\ 
-		\midrule
-		\xintForpair #1#2 in {(anpage,a), (bplyce,b), (drbost,c), (ksunth,d), (martin,e), (pmives,f), (rnpwil,g), (sbains,h), (swewin,i), (yfhsie,j)} \do {%
-		(#2) & \includegraphics[width=1.75cm]{out_faces/paillier_negate_#1_original.png} & \includegraphics[width=1.75cm]{out_faces/paillier_negate_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/paillier_negate_#1_decrypted.png} & \includegraphics[width=1.75cm]{out_faces/paillier_logtransform_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/paillier_logtransform_#1_decrypted.png} & \includegraphics[width=1.75cm]{out_faces/paillier_pwrtransform_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/paillier_pwrtransform_#1_decrypted.png} \\ }%
-		\bottomrule         
-	\end{tabular}
-\end{table*}
-
-\begin{table*}
-	\centering
-	\caption{Comparison of intensity transformations under Dasgupta--Pal}
-	\label{tbl:it-dp}
-	\begin{tabular}{m{1cm}*{7}{>{\centering\arraybackslash}m{1.75cm}}}
-		\toprule
-		\multirow{2}{*}{Image} & \multirow{2}{*}{Original} & \multicolumn{2}{c}{Image negation} & \multicolumn{2}{c}{Logarithm transformation} & \multicolumn{2}{c}{Power-law transformation} \\
-							   &                           & PDT           & CDT          & PDT            & CDT           & PDT               & CDT           \\ 
-		\midrule
-		\xintForpair #1#2 in {(anpage,a), (bplyce,b), (drbost,c), (ksunth,d), (martin,e), (pmives,f), (rnpwil,g), (sbains,h), (swewin,i), (yfhsie,j)} \do {%
-		(#2) & \includegraphics[width=1.75cm]{out_faces/dp_negate_#1_original.png} & \includegraphics[width=1.75cm]{out_faces/dp_negate_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/dp_negate_#1_decrypted.png} & \includegraphics[width=1.75cm]{out_faces/dp_logtransform_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/dp_logtransform_#1_decrypted.png} & \includegraphics[width=1.75cm]{out_faces/paillier_pwrtransform_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/dp_pwrtransform_#1_decrypted.png} \\ }%
-		\bottomrule
-	\end{tabular}
-\end{table*}
-
-Table~\ref{tbl:it-pal} shows the images obtained from the intensity transformation tests under the Paillier cryptosystem, while Table~\ref{tbl:it-dp} shows the resulting images from the same tests under the Dasgupta--Pal cryptosystem.
-Shown for each image is the original unecrypted image, and for each intensity transformation the \textit{plaintext domain transformation} (PDT) is given which is the resulting image after applying the transformation to the unencrypted image and the \textit{ciphertext domain transformation} (CDT) is the decrypted image of the processed encrypted image.
-
-The following tables show the resulting metric scores for mean squared error (MSE), peak signal to noise ratio (PSNR), and structural similarity index (SSIM), as well as time taken (in seconds) for encrypting the input image ($t_\text{enc}$), applying an operation to the encrypted image ($t_\text{apply}$), and decrypting the resulting encrypted image ($t_\text{dec}$), for each image in the test set.
-Tables~\ref{tbl:neg-pal} and~\ref{tbl:neg-dp} show the results obtained from applying image negation, Tables~\ref{tbl:log-pal} and~\ref{tbl:log-dp} from applying logarithm transformation, and Tables~\ref{tbl:pwr-pal} and~\ref{tbl:pwr-dp} from applying power-law transformation.
-
-\subsubsection{Image Negation}
-Both the Paillier and Dasgupta--Pal cryptosystems were able to perform image negation under the encrypted domain without introducing noise in the resulting image.
-In other words, the resulting image from doing image negation on an image on the clear and doing image negation under the encrypted domain are identical, as evidenced by the mean squared errors being exactly equal to zero, the PSNR being infinite, and the SSIM being exactly equal to one.
-
-The Paillier cryptosystem performed better in terms of time, only taking about 0.01 seconds to apply image negation.
-On the other hand, the Dasgupta--Pal cryptosystem took about 22 seconds each to apply the same operation, which is expected since the implementation for Dasgupta--Pal was done in Python without using any external libraries.
-
-\begin{table}[h]
-	\centering
-	\caption{Image negation under Paillier}
-	\label{tbl:neg-pal}
-    \begin{tabular}{lcccccc}
-        \toprule
-        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
-        (a) & 0.000 & $\infty$ & 1.00000 & 0.128 & 0.013 & 0.041 \\
-		(b) & 0.000 & $\infty$ & 1.00000 & 0.084 & 0.013 & 0.024 \\
-		(c) & 0.000 & $\infty$ & 1.00000 & 0.099 & 0.012 & 0.031 \\
-		(d) & 0.000 & $\infty$ & 1.00000 & 0.109 & 0.012 & 0.048 \\
-		(e) & 0.000 & $\infty$ & 1.00000 & 0.117 & 0.015 & 0.043 \\
-		(f) & 0.000 & $\infty$ & 1.00000 & 0.111 & 0.012 & 0.025 \\
-		(g) & 0.000 & $\infty$ & 1.00000 & 0.099 & 0.012 & 0.023 \\
-		(h) & 0.000 & $\infty$ & 1.00000 & 0.084 & 0.012 & 0.024 \\
-		(i) & 0.000 & $\infty$ & 1.00000 & 0.089 & 0.012 & 0.023 \\
-		(j) & 0.000 & $\infty$ & 1.00000 & 0.081 & 0.012 & 0.029 \\
-		\bottomrule
-    \end{tabular}
-\end{table}
-\begin{table}[h]
-	\centering
-	\caption{Image negation under Dasgupta--Pal}
-	\label{tbl:neg-dp}
-    \begin{tabular}{lcccccc}
-        \toprule
-        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
-		(a) & 0.000 & $\infty$ & 1.00000 & 0.221 & 30.217 & 0.239 \\
-		(b) & 0.000 & $\infty$ & 1.00000 & 0.190 & 30.919 & 0.216 \\
-		(c) & 0.000 & $\infty$ & 1.00000 & 0.284 & 31.182 & 0.268 \\
-		(d) & 0.000 & $\infty$ & 1.00000 & 0.225 & 32.581 & 0.223 \\
-		(e) & 0.000 & $\infty$ & 1.00000 & 0.220 & 32.220 & 0.271 \\
-		(f) & 0.000 & $\infty$ & 1.00000 & 0.287 & 31.224 & 0.294 \\
-		(g) & 0.000 & $\infty$ & 1.00000 & 0.285 & 29.478 & 0.284 \\
-		(h) & 0.000 & $\infty$ & 1.00000 & 0.186 & 29.784 & 0.362 \\
-		(i) & 0.000 & $\infty$ & 1.00000 & 0.243 & 38.407 & 0.220 \\
-		(j) & 0.000 & $\infty$ & 1.00000 & 0.285 & 29.488 & 0.449 \\		
-		\bottomrule
-        \end{tabular}
-\end{table}
-
-\subsubsection{Logarithm Transformation}
-Unlike image negation, logarithm transformation involves more operations, so the increase in processing time for both cryptosystems are expected.
-Applying the logarithm transformation under Paillier took about 2 seconds per image, while it took about 13.5 minutes each under Dasgupta--Pal.
-
-The logarithm transformation under Dasgupta--Pal turned out to be more accurate than Paillier, whose mean squared errors approach zero and the SSIM values approach one for every image as shown in Table~\ref{tbl:log-dp}.
-Although the results from using Paillier show that it is also accurate enough with the mean squared errors being less than 30 and the SSIM values average to 0.99, Dasgupta--Pal has been able to produce an almost identical result to that of the plaintext domain transformation counterparts.
-This observation is rather unexpected, considering that the implementation used for Paillier is more robust (due to its use of external C/C++ libraries which makes computations faster).
-
-\begin{table}[h]
-	\centering
-	\caption{Logarithm transformation under Paillier}
-	\label{tbl:log-pal}
-    \begin{tabular}{lcccccc}
-        \toprule
-        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
-		(a) & 13.369 & 36.870 & 0.99263 & 0.085 & 1.813 & 0.023 \\
-		(b) & 7.072 & 39.635 & 0.99017 & 0.089 & 2.073 & 0.023 \\
-		(c) & 8.151 & 39.019 & 0.98688 & 0.091 & 1.913 & 0.023 \\
-		(d) & 25.253 & 34.108 & 0.98927 & 0.089 & 1.919 & 0.023 \\
-		(e) & 10.374 & 37.971 & 0.98695 & 0.106 & 1.829 & 0.023 \\
-		(f) & 2.426 & 44.283 & 0.99401 & 0.127 & 1.900 & 0.023 \\
-		(g) & 5.184 & 40.985 & 0.98971 & 0.096 & 1.853 & 0.023 \\
-		(h) & 16.772 & 35.885 & 0.98492 & 0.081 & 1.746 & 0.024 \\
-		(i) & 5.803 & 40.494 & 0.99241 & 0.091 & 1.827 & 0.027 \\
-		(j) & 12.192 & 37.270 & 0.99354 & 0.081 & 1.815 & 0.023 \\
-		\bottomrule
-        \end{tabular}
-\end{table}
-\begin{table}[h]
-	\caption{Logarithm transformation under Dasgupta--Pal}
-	\label{tbl:log-dp}
-    \begin{tabular}{lcccccc}
-        \toprule
-        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
-		(a) & 0.004 & 71.624 & 0.99999 & 0.287 & 802.957 & 0.036 \\
-		(b) & 0.000 & 82.043 & 1.00000 & 0.190 & 815.384 & 0.048 \\
-		(c) & 0.004 & 72.480 & 1.00000 & 0.270 & 813.640 & 0.036 \\
-		(d) & 0.000 & 87.372 & 1.00000 & 0.204 & 804.629 & 0.047 \\
-		(e) & 0.001 & 77.421 & 1.00000 & 0.245 & 822.940 & 0.036 \\
-		(f) & 0.001 & 76.934 & 1.00000 & 0.194 & 814.132 & 0.036 \\
-		(g) & 0.000 & 83.135 & 1.00000 & 0.197 & 808.503 & 0.047 \\
-		(h) & 0.001 & 77.301 & 1.00000 & 0.270 & 809.406 & 0.047 \\
-		(i) & 0.006 & 70.004 & 0.99999 & 0.268 & 813.217 & 0.051 \\
-		(j) & 0.001 & 78.576 & 1.00000 & 0.243 & 830.640 & 0.039 \\
-		\bottomrule
-        \end{tabular}
-\end{table}
-
-\subsubsection{Power-Law Transformation}
-Applying the power-law transformation under both cryptosystems produced less than accurate images.
-The accuracy varies greatly across all the images as in the case of Paillier, with mean squared errors as high as 8270.696 and as low as 616.419, and SSIM scores ranging from 0.43185 to 0.92334, as seen in Table~\ref{tbl:pwr-pal}.
-As expected, the total processing time now takes about 15 to 20 seconds per image since the power-law transformation is more computationally intensive due to its approximation of an infinite series consisting of terms using the logarithm function, which is also approximated using a combination of addition and multiplication operations.
-
-\begin{table}[h]
-	\centering
-	\caption{Power-law transformation under Paillier}
-	\label{tbl:pwr-pal}
-    \begin{tabular}{lcccccc}
-        \toprule
-        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
-        (a) & 3910.678 & 12.208 & 0.46712 & 0.099 & 14.695 & 0.024 \\
-		(b) & 873.064 & 18.720 & 0.84379 & 0.139 & 16.190 & 0.023 \\
-		(c) & 1261.059 & 17.123 & 0.77229 & 0.082 & 13.866 & 0.023 \\
-		(d) & 653.049 & 19.981 & 0.90673 & 0.083 & 15.507 & 0.023 \\
-		(e) & 646.310 & 20.026 & 0.88157 & 0.108 & 15.727 & 0.045 \\
-		(f) & 2047.933 & 15.018 & 0.69408 & 0.113 & 14.728 & 0.034 \\
-		(g) & 806.473 & 19.065 & 0.85346 & 0.082 & 14.253 & 0.024 \\
-		(h) & 616.419 & 20.232 & 0.92334 & 0.121 & 14.415 & 0.023 \\
-		(i) & 8270.696 & 8.955 & 0.43185 & 0.112 & 14.362 & 0.065 \\
-		(j) & 1715.478 & 15.787 & 0.73857 & 0.145 & 20.239 & 0.023 \\
-		\bottomrule
-        \end{tabular}
-\end{table}
-
-When Dasgupta--Pal was used in the power-law transformation, it completely failed to produce a discernible image and only resulted in a blank image.
-The mean squared errors for this case is an order of magnitude higher than the results from using Paillier.
-Furthermore, doing a power-law transformation under Dasgupta--Pal is not only impractical in terms of accuracy, but also it is impractical in terms of time efficiency because it took about 2 hours and 40 minutes on average to process each image.
-
-\begin{table}[h]
-	\centering
-	\caption{Power-law transformation under Dasgupta--Pal}
-	\label{tbl:pwr-dp}
-    \begin{tabular}{lcccccc}
-        \toprule
-        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
-		% \texttt{anpage} & 25115.891 & 4.131 & 0.00000 & 0.016 & 741.872 & 0.031 \\ 10x10
-		% \texttt{bplyce} & 22777.187 & 4.556 & 0.00000 & 0.017 & 730.873 & 0.003 \\ 10x10
-		% \texttt{drbost} & 18899.906 & 5.366 & 0.00000 & 0.014 & 733.409 & 0.003 \\
-		(a) & 25008.723 & 4.150 & 0.000 & 0.376 & 9700.926 & 1.269 \\
-		(b) & 22700.522 & 4.570 & 0.000 & 0.230 & 9196.609 & 0.043 \\
-		(c) & 18902.214 & 5.366 & 0.000 & 0.277 & 9261.407 & 0.150 \\
-		(d) & 12585.729 & 7.132 & 0.000 & 0.257 & 9259.010 & 0.051 \\
-		(e) & 17012.423 & 5.823 & 0.000 & 0.279 & 9440.351 & 0.051 \\
-		(f) & 31124.615 & 3.200 & 0.000 & 0.285 & 9492.149 & 0.052 \\
-		(g) & 22982.917 & 4.517 & 0.000 & 0.289 & 9321.928 & 0.048 \\
-		(h) & 13469.155 & 6.837 & 0.000 & 0.257 & 9233.818 & 0.048 \\
-		(i) & 37453.834 & 2.396 & 0.000 & 0.262 & 9203.045 & 0.048 \\
-		(j) & 23037.762 & 4.506 & 0.000 & 0.258 & 9210.393 & 0.048 \\
-		% \texttt{drbost} & 18902.214 & 5.366 & 0.00000 & 0.064 & 2261.407 & 0.110 \\ % 20x18
-		% \texttt{ksunth} & 12585.729 & 7.132 & 0.00000 & 0.044 & 2259.010 & 0.011 \\ % 20x18
-		% \texttt{martin} & 17012.423 & 5.823 & 0.00000 & 0.066 & 2440.351 & 0.011 \\
-		% \texttt{pmives} & 31124.615 & 3.200 & 0.00000 & 0.072 & 2492.149 & 0.012 \\
-		% \texttt{rnpwil} & 22982.917 & 4.517 & 0.00000 & 0.076 & 2321.928 & 0.008 \\
-		% \texttt{sbains} & 13469.155 & 6.837 & 0.00000 & 0.044 & 2233.818 & 0.008 \\
-		% \texttt{swewin} & 37453.834 & 2.396 & 0.00000 & 0.049 & 2203.045 & 0.008 \\
-		% \texttt{yfhsie} & 23037.762 & 4.506 & 0.00000 & 0.045 & 2210.393 & 0.008 \\
-		\bottomrule
-        \end{tabular}
-\end{table}
-
-\section{Conclusion}
-In this paper, we have assessed the feasibility and practicality of various homomorphic cryptosystems with regard to secure processing and manipulation of facial image data through creation of a software library that facilitates image processing operations within the encrypted domain, as well as our own implementation of some homomorphic cryptosystems like Dasgupta--Pal for which existing third-party libraries dedicated for this purpose are not yet available.
-
-% This paper also proposes a correction to the Dasgupta--Pal cryptosystem which is further explained in Appendix~\ref{chap:correction}.
-
-Even though an operation in a partially homomorphic cryptosystem is not theoretically possible, like multiplication of two ciphertexts under Paillier, it has been shown that such operations are indeed possible in a two-party system.
-Protocols for secure multiplication and exponentiation have been proposed and also applied to more complex image operations such as facial recognition.
-Thus, a partially homomorphic cryptosystem can be modified to admit more image processing operations by assuming a two-party system.
-
-Preliminary results have shown that both Paillier and Dasgupta--Pal apply image negation accurately and efficiently, as evidenced by the perfect zero MSE and infinite PSNR.
-For the logarithm transformation, Paillier was faster and accurate enough (with $\text{MSE} \le 30$ and $\text{SSIM} \approx 0.99$), but Dasgupta--Pal was slower but more accurate (with $\text{MSE} \le 0.01$ and $\text{SSIM} \approx 0.99999$) which was rather unexpected.
-However both Paillier and Dasgupta--Pal fail to produce accurate results in applying the power-law transformation, with the latter completely failing to produce discernible results.
-Based from these results, the Paillier cryptosystem is consistent enough to produce reasonable to accurate results.
-
-A wrapper library has been made which implements the various functions and methods of the cryptosystems into a single interface.
-This allowed us to express various image operations with a unified syntax, thus facilitating easier testing.
-
-\subsection{Ongoing and Future Work}
-Testing intensity transformations under the BGV cryptosystem will be started once the Pyfhel library is deemed stable enough to use, or another Python library that implements BGV becomes available. 
-One of the authors of this paper has already informed the developers of the Pyfhel library about a bug involving exponentiation of two real numbers.
-
-Efforts are ongoing with regard to the facial recognition tests.
-Our own implementation of the privacy-preserving  eigenfaces by Erkin, et al.
-does not yet use the DGK cryptosystem for secure integer comparison in the match finding step, thus we are working on implementing DGK from scratch.
-
-Another promising image operation to consider is \textit{facial detection} under a homomorphic cryptosystem.
-Work has been started in order to assess the feasibility of using Haar cascades in a privacy-preserving manner.
-
-Future work would involve improving and optimizing our implementation of the Dasgupta--Pal cryptosystem so that it performs faster.
-A suggestion would be to port the existing implementation to C/C++ and then create a Python library that acts as a wrapper to the C/C++ methods.
-For future studies, an implementation of a client-server framework or system dealing with secure image processing can be considered.

### 2019-03-12 icmssp-paper/parts/04_results.tex
Change folder structure
- renamed paper folder to icmssp-paper
- split icmssp paper into parts

--- 2019-02-11 paper/paper-conf.tex
@@
-\section{Introduction}
-\subsection{Context of the Study}
-Digital data privacy and security is a growing concern in various fields, such as cloud computing~\cite{potey_homomorphic_2016}, health information systems~\cite{kester_cryptographic_2015}, and video surveillance~\cite{upmanyu_efficient_2009}.
-To meet these needs, various cryptosystems have been developed.
-% A cryptosystem is a system which operates on plaintexts, ciphertexts and keys using an encryption algorithm, which maps a plaintext to a ciphertext, together with a decryption algorithm, which maps a ciphertext to a plaintext, given an appropriate key~\cite{bauer_cryptosystem_2005}.
-The encryption and decryption algorithms are chosen such that the plaintext cannot easily be recovered from the ciphertext without knowledge of the key.
-This allows data to be securely transmitted over an insecure channel.
-
-One particular application of cryptography is image encryption.
-While cryptosystems used to encrypt digital data in general, such as the Advanced Encryption Standard (AES) or elliptic curve cryptography, can also be used to encrypt images~\cite{jain_image_2016, singh_image_2015} other algorithms created specifically for image encryption have also been developed~\cite{murugan_survey_2018}.
-
-In a homomorphic cryptosystem, operations such as addition and multiplication can be performed on encrypted data.
-These operations are then preserved when the data is decrypted.
-In this manner, data is manipulated without compromising data privacy, as the encrypted data being operated on remains secure~\cite{fontaine_survey_2007, sen_homomorphic_2013}.
-In the area of homomorphic image encryption, there is interest in being able to perform image manipulation operations on the encrypted data such as image adjustment, filtering, and morphological/feature extraction operations~\cite{ziad_cryptoimg:_2016, gonzalez_digital_2008}.
-More advanced operations have also been implemented using homomorphic cryptosystems, such as facial recognition \cite{hutchison_privacy-preserving_2009} and neural networks \cite{hesamifard_cryptodl:_2017}.
-This study in particular focuses on facial recognition.
-
-% \subsection{Research Questions}
-% By implementing homomorphic cryptosystems and creating a library so they can be easily used, we aim to address our main research question: What is the best method for facial image data to be encrypted and manipulated for practical applications?
-
-% More specifically, our research will address the following sub-questions:
-% \begin{enumerate}
-% 	\item Which homomorphic cryptosystems admit more image processing operations? How can existing homomorphic cryptosystems be modified to admit more image processing operations?
-% 	\item Which homomorphic cryptosystems are the most time-efficient and the most accurate in applying image processing operations?
-% 	\item Which homomorphic cryptosystems best preserve image quality in applying image processing operations?
-% \end{enumerate}
-
-\subsection{Research Objectives}
-% Previous attempts in the literature to provide image processing tasks such as image manipulation \cite{ziad_cryptoimg:_2016} and  facial recognition \cite{hutchison_privacy-preserving_2009} have primarily used the Paillier and  Damg{\aa}rd--Geisler--Kr{\o}igaard (DGK) cryptosystems to perform linear operations on encrypted data.
-% In this study, we extend this research to provide an objective comparison of various homomorphic cryptosystems currently in the literature in performing non-linear operations, and facial detection, as opposed to just linear operations and facial recognition.
-
-Our main research objective is to assess the practicality of various homomorphic cryptosystems with regard to image processing on faces. 
-% Homomorphic cryptosystems are known to be slower in terms of encryption, operation, and decryption time~\cite{sen_homomorphic_2013}.
-Furthermore, the operations on encrypted data supported by homomorphic cryptosystems are limited, and some schemes require preprocessing to be performed on images, limiting the range of operations which can be performed efficiently~\cite{li_elliptic_2012}.
-
-% In summary, in this study, we wish to
-More specifically, we wish to do the following:
-\begin{enumerate}
-    \item Implement common linear and non-linear image processing operations using known homomorphic encryption schemes, then determine which schemes admit more image processing operations and extend known cryptosystems to support more operations, if possible;
-    \item Compare the time efficiency and accuracy of common image processing operations under known homomorphic encryption schemes, and of common image processing operations without using homomorphic encryption;
-    \item Create a library to allow for convenient use and comparison of these homomorphic encryption schemes for image processing and facial recognition.
-\end{enumerate}
-
-\subsection{Scope and Limitations}
-% Our study will be limited in terms of the cryptosystems to be tested, the image processing operations we will implement, and the statistical tests we will use to gauge the security of the cryptosystems.
-Below is a listing of the scope of the study.
-
-% We will implement and test the following algorithms:
-In this study, we will implement and test the following cryptosystems:
-\begin{enumerate}
-	\item A variant of the Paillier cryptosystem~\cite{stern_public-key_1999} which supports floating-point operations, used in \textit{CryptoImg}~\cite{ziad_cryptoimg:_2016}.
-    \item The Damg{\aa}rd--Geisler--Kr{\o}igaard (DGK) cryptosystem~\cite{pieprzyk_efficient_2007, cryptoeprint:2008:321} which is primarily used for secure integer comparison.
-	% \item A fully homomorphic encryption scheme by Dasgupta and Pal, which uses polynomial rings~\cite{dasgupta_design_2016}.
-	\item The Brakerski--Gentry--Vaikuntanathan (BGV) cryptosystem \cite{cryptoeprint:2011:277}, an improvement on the lattice-based cryptosystem by Gentry~\cite{gentry_fully_2009}, with optimizations from Smart, Vercauteren, and Halevi \cite{hutchison_fully_2010, cryptoeprint:2011:566}.
-\end{enumerate}
-We will implement and test the following categories of image manipulation operations:
-\begin{enumerate}
-	\item Non-linear image intensity adjustment (logarithm and power-log transformations)
-	\item Facial detection and recognition using the eigenface approach \cite{turk_eigenfaces_1991}.
-\end{enumerate}
-We will adopt the benchmark for evaluating image quality of image encryption schemes presented by Ahmed, et.
-al~\cite{ahmed_benchmark_2016}.
-The presented benchmark reflects many tests used in other literature~\cite{ahmad_efficiency_2012, wu_npcr_2011}.
-\begin{enumerate}
-    \item Mean Squared Error (MSE)
-    \item Peak Signal to Noise Ratio (PSNR)
-    \item Structural Similarity Index (SSIM)
-\end{enumerate}
-A detailed overview of the above will be provided in the methodology. Grayscale images will be used in the study.
-A client-server model for secure computation will be assumed to allow operations such as secure comparison and exponentiation.
-% Training and test data are taken from the publicly available \texttt{faces94} dataset (\url{https://cswww.essex.ac.uk/mv/allfaces/faces94.html}) maintained by the University of Essex.
-
-\subsection{Significance of the Study}
-This study aims to directly address one of the current problems in the research of homomorphic cryptosystems: the practicality of homomorphic encryption~\cite{sen_homomorphic_2013}.
-The literature shows existing homomorphic cryptosystems and how they support primitive operations (usually addition and multiplication) on encrypted data, however, for homomorphic cryptosystems to be useful for practical use, efficient support for more complicated image processing operation must be demonstrated as well.
-While implementations of image processing operations in a homomorphic cryptosystem exist in the literature~\cite{ziad_cryptoimg:_2016, garay_algorithms_2014}, our study targets the more computationally intensive task of facial recognition and detection.
-
-In the Philippine setting, preservation of data privacy is of utmost importance when it comes to outsourcing work involving sensitive data to local companies with the ratification of the Data Privacy Act of 2012.
-Thus recent developments in applications of homomorphic encryption on non-text-based data (such as images) are becoming relevant today.
-
-We wish to contribute to existing models for the secure transmission and modification of image data by developing a software library which allows the use and comparison of various homomorphic encryption algorithms.
-Our software library would allow service providers to perform image manipulation for clients without compromising data privacy.
-
-\section{Review of Related Literature}
-\subsection{Homomorphic Cryptosystems}
-A cryptosystem consists of an encryption function $\mathcal{E}$ and a decryption function $\mathcal{D}$, along with the plaintext space $\mathcal{P}$, ciphertext space $\mathcal{C}$ and the key space $\mathcal{K}$~\cite{bauer_cryptosystem_2005}.
-A \textit{plaintext} is text that can be commonly understood, while a \textit{ciphertext} results from encrypting the plaintext using an encryption key.
-The \textit{plaintext space} is the set of all possible plaintexts, the \textit{ciphertext space} is the set of all possible ciphertexts, while the \textit{keyspace} is the set of all possible keys.
-
-% There are two kinds of cryptosystems, \textit{symmetric} and \textit{asymmetric}.
-In symmetric-key cryptosystems, the same key is used for both encryption and decryption.
-As a consequence, symmetric-key cryptosystems must be implemented with a secure key exchange protocol, so that both the sender and receiver have access to the same key.
-Prominent examples of symmetric-key cryptosystems are the Data Encryption Standard (DES), and its replacement, the Advanced Encryption Standard (AES).
-
-% On the other hand, asymmetric-key (or public-key) cryptosystems use separate keys for encryption and decryption.
-The encryption key (also called the \textit{public key}) is shared publicly, while the decryption key (also called the \textit{private key}) is kept secret.
-Since the public key and private keys are different, there is no need to agree upon secure key exchange protocols.
-Usually, the security of asymmetric-key cryptosystems relies on the intractability of certain computational problems, for example, the RSA cryptosystem depends on the difficulty of big integer factorization~\cite{rivest_method_1978}, while the ElGamal cryptosystem depends on the difficulty of the discrete logarithm problem~\cite{blakley_public_1985}.
-
-% Homomorphic cryptosystems are a special type of cryptosystem in which operations can be securely performed on encrypted data.
-Suppose that for a public-key cryptosystem, $\mathcal{E}_k \left(p \right)$ is the encryption function using the public key $k \in \mathcal{K}$, and $\mathcal{D}_l \left(c \right)$ be the decryption function using the private key $l$.
-A cryptosystem is said to be homomorphic if its encryption function is homomorphic, that is, if it satisfies the relation
-% \begin{equation}
-%     \mathcal{E}_k \left(p_1 \boxplus p_2\right) = \mathcal{E}_k \left(p_1\right) \boxdot \mathcal{E}_k \left(p_2\right)
-% \end{equation}
-% where $p_1, p_2 \in \mathcal{P}$ are the plaintexts, and $\boxplus$ and $\boxdot$ are operations in $\mathcal{P}$ and $\mathcal{C}$ respectively~\cite{fontaine_survey_2007}.
-Furthermore, a homomorphic cryptosystem also satisfies~\cite{li_elliptic_2012}
-% \begin{equation}
-%     p_1 \boxplus p_2 = \mathcal{D}_l \left( \mathcal{E}_k \left(p_1\right) \boxdot \mathcal{E}_k \left(p_2\right) \right).
-% \end{equation}
-
-% In other words, 
-A homomorphic cryptosystem preserves the operations that can be done with the plaintext without requiring an intermediary step of decrypting the ciphertext beforehand.
-It is important to note that the operations in the plaintext space and ciphertext space need not be the same.
-A simple operation in the plaintext space may require a computationally intensive operation in the ciphertext space.
-
-% Homomorphic cryptosystems can be classified according to the plaintext and ciphertext operations, $\boxplus$ and $\boxdot$.
-If the plaintext operation $\boxplus$ is addition, the cryptosystem is said to be \textit{additively homomorphic}, and the cryptosystem is said to be \textit{multiplicatively homomorphic} if the plaintext operation $\boxplus$ is multiplication.
-
-\subsection{Partially Homomorphic Cryptosystems}
-In this section, we will present two classical partially homomorphic cryptosystems which we will be testing in the study: the Paillier cryptosystem and the DGK cryptosystem.
-Both of these cryptosystems encrypt integer plaintexts as integer ciphertexts.
-In our description of each cryptosystem, we use $E(m)$ to denote the encryption of a plaintext $m$, and $D(c)$ to denote the decryption of a ciphertext $c$.
-
-% We will then show that the cryptosystems can be modified to support privacy-perserving polynomial evaluation in a client-server protocol: given an encrypted message $m$, evaluate $f(m)$ where $f$ is a polynomial function.
-
-\subsubsection{The Paillier Cryptosystem}
-The Paillier cryptosystem \cite{stern_public-key_1999}, developed by Pascal Paillier, is a probabilistic encryption scheme which is based on the composite residuosity class problem.
-The scheme has several well--known homomorphic properties.
-% The scheme allows for the encryption and decryption of integer messages, and is known to be additively homomorphic.
-% We now state the encryption and decryption algorithms of the Paillier cryptosystem and its homomorphic properties.
-
-% \paragraph{Key Generation}
-% We first define a function $L(x)$ as the largest integer $v$ greater than zero such that $x-1 \geq vn$.
-% We choose two large primes $p$ and $q$, and set $n = pq, \lambda = \mathrm{lcm}(p-1,q-1)$.
-% Then we select an integer $g$, $0\leq g \leq n^2$ such that $\mathrm{gcd}(L(g^\lambda \bmod n^2), n) = 1$.
-% We denote the public key as $(g,n)$ and the private key $(p,q)$.
-
-% \paragraph{Encryption and Decryption}
-% The encryption function to encrypt a plaintext $m \in \mathbb{Z}_n$ given a public key $(g,n)$ is defined as
-% \begin{align*}
-%   E(m) = g^m \cdot r^n \mod{n^2},
-% \end{align*}
-% where $r$ is a random non-negative integer less than $n^2$.
-
-% The decryption function to decrypt a ciphertext $c \in \mathbb{Z}^\ast_{n^2}$ given a private key $(p,q)$ is defined as:
-% \begin{align*}
-%   D(c) = L(c^\lambda \bmod n^2) \times (L(g^\lambda \bmod n^2))^{-1} \mod n
-% \end{align*}
-
-% \paragraph{Homomorphic Properties of the Paillier Cryptosystem}
-% The Paillier cryptosystem supports additive homomorphism as well as the multiplication of a plaintext scalar to an encrypted message.
-These homomorphic properties are used to add a plaintext scalar to a ciphertext, add two ciphertexts, and multiply a ciphertext by a plaintext scalar, respectively.
-They are defined as follows.
-
-For all $m_1,m_2 \in \mathbb{Z}_n$ and $k\in \mathbb{N}$, the following homomorphic properties hold for the Paillier cryptosystem with public key $(g,n)$.
-\begin{align*}
-  D(E(m_1)g^k\bmod n^2) &=(m_1+k)\bmod n\\
-  D(E(m_1)E(m_2)\bmod n^2) &=(m_1+m_2)\bmod n\\
-  D(E(m_1)^k\bmod n^2) &= km_1\bmod n
-\end{align*}
-
-These homomorphic properties are used to add a plaintext scalar to a ciphertext, add two ciphertexts, and multiply a ciphertext by a plaintext scalar, respectively.
-
-\subsubsection{The DGK Cryptosystem}
-The DGK cryptosystem was published by Damg{\aa}rd, Geisler, and Kr{\o}igaard in 2007 in an effort to create a secure integer comparison scheme \cite{pieprzyk_efficient_2007, cryptoeprint:2008:321} which is widely used in the literature \cite{veugen_improving_2012}.
-The DGK cryptosystem has homomorphic properties similar to the Paillier cryptosystem.
-
-% \paragraph{Key Generation}
-% We denote $k,t,\ell$ as security parameters of the scheme, where $k>t>\ell$.
-% Let $p,q$ be primes such that
-% we can choose two $t$-bit primes $v_p$ and $v_q$ such that $v_p | (p-1)$ and $v_q | (q-1)$, and a small prime $u$ such that $u | (p-1)$ and $u | (q-1)$.
-% We denote $n = pq$.
-% We choose $g$ to be an integer of order $uv_pv_q$ and $h$ to be of order $v_pv_q$.
-
-% The DGK cryptosystem encrypts plaintexts in $\mathbb{Z}_u$ to ciphertexts in $\mathbb{Z}_n^\ast$.
-
-% The public key is $(n,g,h,u)$ and the private key is $(p,q,v_p,v_q)$.
-
-% \paragraph{Encryption and Decryption}
-% To encrypt a message $m \in \mathbb{Z}_u$, the encryption function is defined as:
-% \begin{align*}
-%   E(m) = g^m \cdot h^r \mod{n},
-% \end{align*}
-% where $r$ is a random integer in $\mathbb{Z}_n$ which is longer than $2t$ bits.
-
-% To decrypt a ciphertext $c \in \mathbb{Z}_n^\ast$, decryption is achieved by first computing $c^{v_pv_q}$.
-% \begin{align*}
-% 	c^{v_pv_q} \bmod n
-% 	&= (g^m \cdot h^r)^{v_pv_q} \bmod n\\
-% 	&= (g^{v_pv_q})^m \bmod n
-% \end{align*}
-% Since $(g^{v_pv_q})^m$ has order $u$, there is a one-to-one correspondence between plaintexts in $\mathbb{Z}_u$ and  $(g^{v_pv_q})^m$.
-A lookup table can thus be generated privately to successfully recover $m$.
-
-% \paragraph{Homomorphic Properties of the DGK Cryptosystem}
-% The DGK cryptosystem supports additive homomorphism as well as the multiplication of a plaintext scalar to an encrypted message.
-These homomorphic properties are used to add a plaintext scalar to a ciphertext, add two ciphertexts, and multiply a ciphertext by a plaintext scalar, respectively.
-They are defined as follows.
-
-For all $m_1,m_2 \in \mathbb{Z}_u$ and $k\in \mathbb{N}$, the following homomorphic properties hold for the DGK cryptosystem with public key $(n,g,h,u)$.
-\begin{align*}
-    D(E(m_1)g^k) &=(m_1+k)\bmod u\\
-    D(E(m_1)E(m_2)) &=(m_1+m_2)\bmod u\\
-    D(E(m_1)^k) &= km_1\bmod u
-\end{align*}
-
-As the multiplicative homomorphism was not presented in the original paper, we provide a short proof here.
-\begin{proof}
-  Let $m \in \mathbb{Z}_u$ and $k\in \mathbb{N}$.
-  We consider $E(m)^k = (g^m \cdot h^r \bmod{n})^k\bmod n$.
-  \begin{align*}
-    (g^m \cdot h^r \bmod{n})^k \bmod n
-    &= (g^m \cdot h^r)^k \bmod{n}\\
-    &= (g^m)^k \cdot (h^r)^k \bmod{n}\\
-    &= g^{km} \cdot (h^{kr}) \bmod{n}
-  \end{align*}
-  Since $r$ is a random integer, $kr$ is also a random integer, Therefore, $g^{km} \cdot (h^{kr}) \bmod{n} = D(E(m)^k)$ is a valid encryption of the message $km$.
-\end{proof}
-
-% \subsubsection{Secure Exponentiation and Multiplication Protocols}
-% \label{ssec:exponentiationprotocol}
-% [TO-DO: This is further explained in another paper.]
-% In order to perform polynomial evaluation, we first present a protocol for privacy-preserving exponentiation to a positive integer power, adapted from the protocol to calculate Euclidean distances used in \cite{hutchison_privacy-preserving_2009}.
-
-% The following protocols apply to both the Paillier and DGK cryptosystems, as they share similar homomorphisms. We first present a secure squaring protocol.
-
-% Suppose Alice encrypts an integer $x$ and sends it so Bob has $E(x)$, and wants to obtain $E(x^2)$ without exposing the value of $x$.
-% \begin{itemize}
-% 	\item Bob first selects a random integer $r$ and computes $E(x+r)$. Bob can do this since $r$ is a plaintext constant.
-% 	\item Bob sends $E(x+r)$ to Alice, who decrypts the ciphertext to obtain $x+r$.
-% 	\item Alice squares $x+r$ and encrypts the result. She sends $E((x+r)^2)$ to Bob.
-% 	\item Bob computes $E(-2rx + r^2)$. He then computes $E((x+r)^2)E(-2rx + r^2) = E(x^2)$.
-% \end{itemize}
-
-% We can use the secure squaring protocol to arrive at a secure multiplication protocol, which then allows for the evaluation of polynomials.
-% Suppose Alice encrypts integers $x$ and $y$, and Bob has $E(x), E(y)$ and wants to obtain $E(xy)$.
-% \begin{itemize}
-% 	\item Bob acquires $E(x^2), E(y^2)$ using the secure squaring protocol.
-% 	\item Bob sends $E(x+y)$ to Alice, who decrypts the ciphertext to obtain $x+y$.
-% 	\item Alice sends $E((x+y)^2)$ to Bob.
-% 	\item Bob then computes
-% 	\begin{align*}
-% 		E((x+y)^2)E(x^2)^{-1}E(y^2)^{-1} &= E((x+y)^2 - x^2 - y^2)\\
-% 		&= E(2xy)
-% 	\end{align*}
-% 	\item Bob can then recover $E(xy)$ by calcuating for the multiplicative inverse of 2 using the Euclidean algorithm, and calculating $2^{-1}E(xy)$.
-Such an inverse exists since the modulus is either a prime (in the DGK cryptosystem) or a product of primes greater than 2 (in the Paillier cryptosystem).
-% \end{itemize}
-
-\subsection{Fully Homomorphic Cryptosystems}
-We will also be testing fully homomorphic cryptosytems, which allow aribitrary computation on encrypted data.
-While generally being more flexible, fully homomorphic cryptosytems are known to be significantly slower than partially homomorphic cryptosytems; improving the efficiency of fully homomorphic cryptosytems is an active area of research \cite{sen_homomorphic_2013}.
-
-% We will present two such cryptosystems, the Dasgupta--Pal cryptosystem, which we present in full to explain a correction we propose to it, and the BGV cryptosystem, which has open source implementations availble primarily used in homomorphic cryptography research.
-
-% \subsubsection{The Dasgupta--Pal Cryptosystem}
-% The Dasgupta--Pal cryptosystem is a fully homomorphic cryptosystem proposed in 2016 by Smaranika Dasgupta and S.
-K.
-Pal \cite{dasgupta_design_2016}, which encrypts integer plaintexts in $\mathbb{Z}_n$ to polynomial ciphertexts.
-We begin our presentation of the Dasgupta--Pal cryptosystem with the following definition.
-
-% Given a message $m \in \mathbb{Z}$, we denote
-% \begin{align*}
-% 		m_p(x) = a_0 + a_1 x + a_2 x^2 + \cdots + a_k x^k
-% \end{align*}
-% where $a_k a_{k-1}\cdots a_2 a_1 a_0$ is the binary representation of $m$.
-
-% In the original scheme presented in \cite{dasgupta_design_2016}, the secret key $S_k$ is set to be a large prime.
-In Appendix \ref{chap:correction}, we present a case where the Dasgupta--Pal cryptosystem fails and prove that setting the secret key $S_k = 2p$, where $p$ is a large prime, corrects errors in the Dasgupta--Pal cryptosystem.
-% We now decribe the correct cryptosystem.
-% \paragraph{Corrected Dasgupta--Pal Cryptosystem Description}
-% Let $\ell$ denote the security parameter of the cryptosystem.
-% Let $S_k = 2p$, where $p$ is a prime number with $\ell - 1$ bits.
-% Choose a random even integer $z$ of length $\log_2{\ell}$.
-
-% Let the secret key be $S_k$, and let the refresh key be $R_k = z \cdot S_k$. The secret key is kept private to the encrypting/decrypting parties, while the refresh key is made publicly available.
-
-% The scheme defines the encryption algorithm for a message $m$ as follows:
-% \begin{align*}
-% 	E(m) = y(x) + S_k\times d(x)
-% \end{align*}
-% where
-% $y(x)$ is a polynomial of degree $n$ such that $m_p(x) \equiv y(x) \bmod S_k$ and $d(x)$ is a randomly chosen polynomial of degree $n$.
-This encrypts each coefficient of $m_p(x)$ by adding some multiple of $S_k$ to it.
-Through this process, each bit of the message is encrypted separately.
-
-% Furthermore, the decryption algorithm to recover $m_p(x)$ from a ciphertext polynomial $c(x)$ as
-% \begin{align*}
-% 	m_p(x) = c(x) \bmod S_k \bmod 2.
-% \end{align*}
-% Thus $D(c(x))$ is defined as the integer recovered from the coefficients of the polynomial $c(x) \bmod S_k \bmod 2$.
-
-% Dasgupta and Pal note that homomorphic operations on ciphertext introduce noise which may interfere with decryption, due to the potential increase in ciphertext values.
-% To eliminate noise from a polynomial ciphertext, the following refresh function is used:
-% \begin{align*}
-% 	R(c(x)) = c(x) \bmod R_k.
-% \end{align*}
-
-% \paragraph{Homomorphic Properties of the Dasgupta--Pal Cryptosystem}
-% It has been shown \cite{dasgupta_design_2016} that the following properties hold for all integer messages $m_1, m_2 \in \mathbb{Z}_n$ in the Dasgupta--Pal cryptosystem.
-These properties arise since each coefficient in a ciphertext polynomial is essentially an independently encrypted bit of the original message.
-% \begin{description}
-% 	\item[\textsc{xor} on ciphertexts]
-% 	A bitwise exclusive or (\textsc{xor}) operation on integer messages can be achieved by adding the coefficients pairwise between two ciphertexts.
-% 	\begin{align*}
-% 		D(E(m_1)+E(m_2)) = m_1 \textsc{ xor } m_2
-% 	\end{align*}
-% 	\item[\textsc{and} on ciphertexts]
-% 	Similarly, pair-wise multiplication corresponds to bitwise \textsc{and} of integer messages.
-% 	\begin{align*}
-% 		D(E(a) \otimes E(b)) = a \textsc{ and } b = ab \bmod 2
-% 	\end{align*}
-% 	where $\otimes$ denotes pairwise multiplication,
-% 	\begin{align*}
-% 		\sum_{i=1}^n{a_ix^i} \otimes \sum_{i=1}^n{b_ix^i} = \sum_{i=1}^n{a_ib_ix^i}.
-% 	\end{align*}
-% \end{description}
-
-% Arbitrary computation on data can thus be achived using these bitwise operations.
-While the Dasgupta--Pal cryptosystem requires significant amounts of memory, as each bit of plaintext is encrypted into an integer, this approach provides a flexible method to perform relatively fast arbitrary computation on encrypted data.
-Encryption and decryption in the Dasgupta--Pal cryptosystem are accomplished using few arithmetic operations.
-
-% \subsubsection{HElib and the BGV Cryptosystem}
-The BGV (Brakerski--Gentry--Vaikuntanathan) cryptosystem \cite{cryptoeprint:2011:277} is a fully homomorphic cryptosystem created based on the ring-learning with error problem.
-The BGV cryptosystem was constructed to surpass the limitations of prior fully homomorphic cryptosystems, which were based on the first fully homomorphic cryptosystem by Gentry \cite{gentry_fully_2009}.
-
-The details regarding the construction of the BGV cryptosystem are beyond the scope of this paper.
-For this study, we will be using \textit{HElib} \cite{garay_algorithms_2014}, an open-source library which implements the BGV cryptosystem with optimizations to improve efficiency.
-Evaluation of operations on 120 inputs in \textit{HELib} was performed in around 4 minutes, with an average of 2 seconds to process a single input \cite{hutchison_fully_2010,cryptoeprint:2011:566}.
-
-The \textit{HElib} library has been adapted to Python using the Pyfhel library \cite{pyfhel_2018} maintained by Ibarrondo, Laurent (SAP) and Onen (EURECOM), and licensed under the GNU GPL v3 license.
-The Pyfhel library is a Python API for the \textit{HElib} library, which supports the following operations on vectors/scalars of integers or binary ciphertexts:
-\begin{itemize}
-	\item Arithmetic operations: addition, subtraction, multiplication;
-	\item Binary operations: \textsc{and}, \textsc{or}, \textsc{not}, \textsc{xor}.
-\end{itemize}
-
-\subsection{CryptoImg}
-A paper published in 2009 by Ziad, et al.
-attempts to implement privacy-preserving image processing using \textit{CryptoImg}, a library for the Open Source Computer Vision Library (OpenCV)~\cite{bradski_opencv_2000} which implements various homomorphic encryption and image processing routines using the Paillier homomorphic cryptosystem~\cite{ziad_cryptoimg:_2016}.
-The \textit{CryptoImg} library assumed a client-server model wherein a client requests image processing operations from a server.
-A client first encrypts a digital image and sends the image securely to a server, which then operates on the encrypted image without revealing its contents.
-Then the resulting image is sent back to the client, which decrypts the image to recover the desired output.
-\begin{figure}[!ht]
-    \centering
-    \includegraphics[width=0.4\textwidth]{figures/ClientServerModel.png}
-    \caption{Client-server architecture used by \textit{CryptoImg} \cite{ziad_cryptoimg:_2016}}
-    \label{fig:clientserver}
-\end{figure}
-
-The \textit{CryptoImg} library implemented the following:
-\begin{enumerate}
-	\item Extending the Paillier homomorphic cryptosystem which operate on integer plaintexts so that they can operate on real number plaintexts;
-	\item Developing protocols for and implementing the following image processing operations
-	\begin{enumerate}
-		\item Image negation and brightness adjustment
-		\item Spatial filters (for noise reduction, edge detection and sharpening)
-		\item Morphological operations
-		\item Histogram equalization
-	\end{enumerate}
-\end{enumerate}
-For image negation and spatial filters, the protocols specified by \textit{CryptoImg} allow all image processing operations to be performed on the server.
-However, due to limitations in the Paillier cryptosystem, the protocols presented for morphological operations and histogram equalization require both the client and the server to perform image processing calculations, although the server performs a significant portion of the processing.
-
-Ziad, et al.
-also showed experimental results establishing the slow performance of image operations under a homomorphic cryptosystem.
-For instance, while sharpening and applying a Sobel filter each take less than a second when applied to a $512\times 512$ plaintext image, when applied to an encrypted image, sharpening required at least 238.257 seconds, and applying the Sobel filter required at least 147.567 seconds \cite{ziad_cryptoimg:_2016}.
-
-We now discuss several limitations in the \textit{CryptoImg} study which we focus on for our research.
-First, the \textit{CryptoImg} library was limited in the image intensity transformations it implemented.
-We propose additional protocols to support more computationally intensive intensity transformations.
-Second, the \textit{CryptoImg} library only considered the Paillier cryptosystem.
-We consider testing the performance of other homomorphic cryptosystems, which differ in their processing time and supported operations.
-
-\subsection{Image Intensity Transformations}
-We represent a digital image $R$ as an $M \times N$ matrix of pixel intensity values, each value in the range $\left[0, L-1\right]$, for some positive integer $L$.
-We denote with $R(x,y)$ the entry at the $x$th row and $y$th column of a matrix $R$.
-An intensity transformation on an image $R$ can be defined as a function $T$ which maps a pixel value $r$ to a new value $r^\prime$, which we can write as $r^\prime = T\left(r\right)$.
-This function is then applied to every pixel in $R$.
-The \textit{CryptoImg} library implemented two types of linear intensity transformations: image negation and brightness control.
-
-An image negation transformation is defined as:
-\begin{equation}
-    T\left(r\right) = L-1-r
-\end{equation}
-After applying image negation, the resulting image would be similar to a photographic negative~\cite{gonzalez_digital_2008}.
-
-A brightness control transformation with parameter $v$ is defined as:
-\begin{equation}
-    T\left(r,v\right) = r+v
-\end{equation}
-The above transformations are linear in terms of the input $r$, and are thus simple to implement under a homomorphic cryptosystem.
-
-In this study we extend the range of intensity transformations to non-linear transformations.
-Two common non-linear image transformations are the logarithm transformation and power-law transformation~\cite{gonzalez_digital_2008}.
-
-The logarithm transformation is used to enhance dark pixels or increase the dark details of an image by mapping low intensity values to a wider range of values~\cite{gonzalez_digital_2008}.
-This has the general formula
-\begin{equation}
-    T\left(r\right) = c \log\left(1 + r\right)
-\end{equation}
-where $c$ is a constant.
-
-The power-law transformation is a family of transformations that have the form
-\begin{equation}
-    T\left(r\right) = c r^{\gamma}
-\end{equation}
-where $c>0$ and $\gamma > 0$.
-A power-law transformation defined by the above equation can calibrate the operation of many image capture and output devices such as cameras, printers and displays in a process called \textit{gamma correction}.
-% This ensures reproducibility and accuracy of images being displayed by digital output devices~\cite{gonzalez_digital_2008}.
-
-To implement non-linear intensity transformations using addition and multiplication in a homomorphic system, it is necessary to approximate the logarithm and exponential functions, which may result in higher computational overhead.
-In our software library implementation, we investigate methods required to approximate the logarithm and power functions.
-Non-linear intensity transformations such as the logarithm transformation have applications in intensity normalization \cite{oravec_illumination_2010}, which is used in some facial recognition algorithms to account for differences in lighting which make facial recognition difficult.
-
-\subsection{Facial Detection and Recognition}
-
-Since simple image operations mentioned earlier can be done within a homomorphic cryptosystem, these operations can be assembled together in order to do more complex operations.
-A prominent application of image processing that often uses complex image operations is \textit{facial recognition}.
-
-Traditional facial recognition algorithms rely on detecting salient features in a face image. One of the popular facial recognition algorithms is \textit{eigenfaces}.
-% Traditional facial recognition algorithms rely on detecting salient features in a face image. Two of the popular facial recognition algorithms are \textit{eigenfaces} and \textit{Haar cascades}.
-
-\subsubsection{Eigenfaces}
-Proposed by Matthew Turk and Alex Pentland, the eigenfaces method uses principal component analysis (PCA) in order to express an input image as a linear combination of eigenfaces \cite{turk_eigenfaces_1991}.
-An \textit{eigenface} is a principal component, or more simply an eigenvector that represents a certain variation between the face images which are taken from the initial training set.
-The number of resulting eigenfaces is equal to the number of face images in the training set.
-
-% In the enrollment process, $M$ face images $\Theta_1, \ldots, \Theta_M$, each of size $p \times q$, are taken in to comprise the initial training set.
-The training images can be represented as vectors of length $N = pq$, where each row of an image is concatenated together.
-
-% The average of the training images, denoted as $\Psi$, is 
-% \begin{equation}
-% 	\Psi = \frac{1}{M} \sum_{i=1}^{M} \Theta_i
-% \end{equation}
-
-% The \textit{difference vectors} are then computed as $\Phi_i = \Theta_i - \Psi$. PCA is applied on the covariance matrix of the vectors
-% \begin{equation}
-% 	\mathbf{C} = \frac{1}{M} \sum_{i=1}^M \Phi_i \Phi_i^\top = \frac{1}{M} \mathbf{A}\mathbf{A}^\top,
-% \end{equation}
-% where $\mathbf{A}$ is an $N \times M$ matrix defined by $\left[\Theta_1 \quad \Theta_2 \quad \cdots \quad \Theta_M\right]$, in order to determine the orthonormal eigenvectors \cite{hutchison_privacy-preserving_2009}.
-
-% Directly computing the covariance matrix and then applying PCA will become inefficient for large sizes of $\mathbf{A}$, since computing for $\mathbf{A}\mathbf{A}^\top$ results in an $N \times N$ matrix, which can get drastically large because it is dependent on the size of the image.
-On the other hand, computing for $\mathbf{A}^\top\mathbf{A}$ only results in an $M \times M$ matrix, which is much smaller than the previous one because it is just dependent on the number of face images in the training set.
-Now, we can apply PCA to $\mathbf{A}^\top\mathbf{A}$ along with some post-processing to obtain the eigenvectors \cite{hutchison_privacy-preserving_2009}.
-
-% Instead of getting the eigendecomposition of the covariance matrix by explicitly computing the eigenvalues and eigenvectors of $\mathbf{C}$, we can also apply \textit{singular value decomposition} (SVD) on the matrix $\Phi^\top$.
-This is because SVD works through a divide-and-conquer method which results in greater numerical stability, while eigendecomposition simply uses the traditional QR factorization \cite{nakatsukasa_stable_2013, gu_divide-and-conquer_1995}.
-Upon applying SVD, we now get the eigenvectors $\mathbf{u}_1, \ldots, \mathbf{u}_M$ and their corresponding eigenvalues $\lambda_1, \ldots, \lambda_M$.
-
-% We choose $K$ eigenvectors $\mathbf{u}_1, \ldots, \mathbf{u}_K$ such that it comprises a set associated with the $K$ largest eigenvalues, where $K$ is much smaller than $M$.
-This set is now the \textit{face space}.
-Then, the images $\Theta_1, \ldots, \Theta_K$ are projected onto the face space spanned by the eigenfaces to determine the weight vectors $\Omega_1, \ldots, \Omega_K$.
-
-% To perform the recognition process, the algorithm projects the input image $\Gamma$ onto the face space, and then comparing the projected image $\bar{\Omega} = \mathbf{u}_i\left(\Gamma - \Psi\right)$ with each eigenface in the face space using a metric such as the Euclidean distance.
-Thus it is computed as $d_i = \left\lVert \Omega_i -\bar{\Omega} \right\rVert$ for all $i=1,\ldots,K$, where $\left\lVert \cdot \right\rVert$ denotes the Euclidean norm.
-
-% Then, a match can be reported if the smallest possible distance is smaller than the given threshold value $T$. 
-% \newcommand{\argmin}{\mathop{\mathrm{arg\,min}}}  
-% \begin{equation}
-% 	\text{ID} = \begin{cases}\argmin_i d_i & \text{if } \min_i d_i \le T \\\emptyset & \text {otherwise}\end{cases}
-% \end{equation}
-
-\subsection{Previous Implementations of Secure Facial Recognition}
-Erkin, et al.
-\cite{hutchison_privacy-preserving_2009} devised a method to incorporate the use of homomorphic cryptosystems into the eigenfaces method.
-In their study, they proposed a two-party system where Alice holds an encrypted image $\left[\Gamma\right]$, while Bob maintains a database of $K$ eigenfaces $\mathbf{u}_1, \ldots, \mathbf{u}_K$, and feature vectors $\Omega_1, \ldots, \Omega_M$ in the clear.
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=0.4\textwidth]{figures/secure_eigenfaces.png}
-    \caption{Diagram of the privacy-preserving facial recognition process \cite{hutchison_privacy-preserving_2009}}
-\end{figure}
-
-In order to ensure privacy, the steps in the eigenfaces algorithm, namely: projection, distance computation, and match finding, are done within the encrypted domain, i.e., using the operations in the Paillier cryptosystem.
-
-Projection is similar to that of the original eigenfaces algorithm, except the operations are replaced with their respective operations in the cryptosystem.
-Distance computation in this version is somewhat different from the original eigenfaces method, in that it deals with the square of the Euclidean distance since the relative order of the distances is only important when comparing these during the match finding step \cite{hutchison_privacy-preserving_2009}.
-\begin{align}
-    d_i &= \left\lVert \Omega_i - \bar{\Omega} \right\rVert ^2 = \sum_{j=1}^{K} \left(\omega_{ij} - \bar{\omega}_j\right)^2 \\
-        &= \underbrace{\sum_{j=1}^{K} \omega_{ij}^2}_{\mathcal{S}_1} + \underbrace{\sum_{j=1}^{K} \left(-2 \omega_{ij} \bar{\omega_j}\right)}_{\mathcal{S}_2} + \underbrace{\sum_{j=1}^{K} \bar{\omega}_{j}^2}_{\mathcal{S}_3}
-\end{align}
-
-Computing for the distances within Paillier would just be multiplying the encrypted sums together.
-\begin{equation}
-	\left[d_i\right] = \left[\mathcal{S}_1\right] \cdot \left[\mathcal{S}_2\right] \cdot \left[\mathcal{S}_3\right]
-\end{equation}
-
-The terms $\left[\mathcal{S}_1\right]$ and $\left[\mathcal{S}_2\right]$ can be easily computed by Bob, since he already knows both $\omega_i$ in the clear and $\left[\bar{\omega}_i\right]$ which is in encrypted form.
-Computing for $\left[\mathcal{S}_3\right]$ is trickier because Bob cannot compute for $\left[\bar{\omega}_i^2\right]$ because pairwise multiplication is not supported in Paillier, that is why Bob needs help from Alice to square a number through a protocol described below \cite{hutchison_privacy-preserving_2009}.
-
-Before Bob sends $\left[\bar{\omega}_i\right]$ to Alice for squaring, he adds a random number $r_i$ to compute $\left[x_i\right] = \left[\bar{\omega}_i + r_i\right] = \left[\bar{\omega}_i\right] \cdot \left[r_i\right]$, where $r_i$ is obviously distinct for every $i$, then sends $\left[x_i\right]$ to Alice.
-She then decrypts it and computes $x_i^2$, and then computes $\mathcal{S}_3^\prime = \sum_{i=1}^{K} x_i^2$, after which she encrypts the sum and sends $\left[\mathcal{S}_3^\prime\right]$ to Bob.
-Now, he can compute for $\left[\mathcal{S}_3\right]$ as follows:
-\begin{equation}
-	\left[\mathcal{S}_3\right] = \left[\mathcal{S}_3^\prime\right] \cdot \prod_{j=1}^{K} \left(\left[\bar{\omega}_j\right]^{-2r_j} \cdot \left[-r_j^2\right]\right)
-\end{equation}
-
-The protocol for squaring a number as described earlier is a workaround for the limitations of Paillier or any other partially homomorphic cryptosystem that only supports addition and scalar multiplication.
-% This can be possibly extended so that operations such as pairwise multiplication and exponentiation are also supported, provided that the protocol involves two parties.
-
-The match-finding step is done by comparing the distances obtained from the previous step to a specified threshold $T$.
-If the minimum distance is smaller than $T$, then a match is found, and the encrypted identity of the match is returned to Alice \cite{hutchison_privacy-preserving_2009}.
-Getting the minimum among the encrypted distances would involve comparing two encrypted numbers, which Paillier does not support.
-Instead, the DGK cryptosystem \cite{pieprzyk_efficient_2007} is used for the comparison protocol.
-
-\section{Methodology}
-In this study we apply three homomorphic encryption schemes~\cite{ziad_cryptoimg:_2016, pieprzyk_efficient_2007, garay_algorithms_2014} for use in image processing and facial recognition applications.
-In particular, the study consists of the following:
-\begin{itemize}
-	\item Creating a wrapper library that acts as a unified interface which implements the Paillier, DGK, and BGV homomorphic cryptosystems.
-	\item An implementation of image processing operations (intensity transformations, facial recognition) under the above cryptosystems.
-	\item Conducting tests for image quality, processing time, using images from the \texttt{faces94} dataset.
-\end{itemize}
-
-% While the Paillier and DGK cryptosystems have been implemented for use in image processing in~\cite{ziad_cryptoimg:_2016, hutchison_privacy-preserving_2009}, the other cryptosystems have to be adapted for this study.
-% Two experiments are conducted in this study:
-% \begin{enumerate}
-% 	\item Assessment of non-linear image intensity transformations under each of the three cryptosystems.
-% 	\item Assessment of efficiency of each of the four cryptosystems when applied for use in privacy-preserving facial recognition and detection using eigenfaces.
-% \end{enumerate}
-% The results of the image intensity transformations are tested for image quality using benchmarks in~\cite{ahmed_benchmark_2016}.
-
-\subsection{Cryptosystem Implementation}
-Three homomorphic encryption schemes are investigated, and a wrapper library was created in Python that integrates these cryptosystems into a unified interface.
-\begin{itemize}
-	\item The Paillier cryptosystem is incorporated using the python-paillier library at \url{https://github.com/n1analytics/python-paillier} developed by Data61 - CSIRO.
-	\item The DGK cryptosystem is ported from the C++ implementation at \url{https://github.com/encryptogroup/ENCRYPTO_utils}, developed by Daniel Demmler from EC-SPRIDE.
-	\item The BGV cryptosystem is implemented using the Pyfhel library (\url{https://github.com/ibarrond/Pyfhel}) using a HElib backend from (\url{https://github.com/shaih/HElib}).
-\end{itemize}
-
-\subsubsection{Extension of Partially Homomorphic Cryptosystems}
-\label{sssec:pheextension}
-In order to use Paillier and DGK for secure image processing, we require the two schemes to support the encryption of floating-point (FP) numbers, as well as multiplication and division of arbitrary ciphertexts.
-We extend the two cryptosystems to FP operations by using an approach shown in~\cite{ziad_cryptoimg:_2016}.
-This approach represents FP numbers using a pair $(m,e)$, where $m$ represents the mantissa (which is encrypted), and $e$ represents the exponent (which is not encrypted).
-This approach is also used by the python-paillier library.
-This represntation allows us to extend the addition and plaintext multiplication homomorphisms of the Paillier and DGK cryptosystems to floating-point numbers.
-
-Various two-party protocols can be used to facilitate ciphertext multiplication and division.
-These allow a server armed with only knowledge of the public key, to obtain the product and quotient of ciphertexts, by communicating with the client, who has the private key.
-For division, we use the protocol defined in~\cite{boukoros_lightweight_2017}: to obtain $E(x/y)$ from $E(x)$ and $E(y)$, the server sends $E(rx)$ and $E(ry)$ to the client, (where $r$ is a random non-zero number), allowing the client to compute $E(rx/ry)$ and give the result back to the server.
-
-For multiplication, we adapt the protocol to calculate Euclidean distances used in \cite{hutchison_privacy-preserving_2009}, which provides a two-party protocol which yields $E(x^2)$ given $E(x)$.
-We use this protocol together with the additive homomorphism of the partially homomorphic cryptosystems to instead compute $E((x + y)^2 - x^2 - y^2) = E(2xy)$, from which we can easily obtain $E(xy)$ through plaintext multiplication.
-
-% [TO-DO: This is further explained in another paper.]
-% We will briefly discuss a protocol to enable cryptosystems built for integer inputs to handle real number inputs.
-% The following protocol was also used by \textit{CryptoImg} for image processing \cite{ziad_cryptoimg:_2016}.
-% This is also used for our own implementation of the Dasgupta--Pal cryptosystem in order to handle real numbers.
-
-% We represent a floating-point (FP) number as a pair of two integers $(m,e)$ representing the mantissa and exponent of the FP number with respect to a base $b$.
-The mantissa $m$ is encrypted, while the exponent $e$ is unencrypted.
-% Let $a,b,c$ be FP numbers represented by the pairs $(m_a,e_a),(m_b,e_b),(m_c,e_c)$ respectively.
-Let $\oplus,\otimes$ represent the homomorphic operations which correspond to the addition and multiplication, respectively.
-We define the secure real number operations as follows:
-% \begin{description}
-%   \item[Addition.]
-%     To compute $E(c)=E(a+b)$ we compute
-%     \begin{align*}
-%       E(m_c) &= E(m_1) \oplus (b^{e_b-e_a} \otimes E(m_b)), e_c = e_a & \text{ if } e_a \leq e_b \\
-%       E(m_c) &= E(m_b) \oplus (b^{e_a-e_b} \otimes E(m_a)), e_c = e_b & \text{ if } e_a > e_b
-%     \end{align*}
-%   \item[Scalar multiplication.]
-%     To compute $E(c) = E(ab)$, where $a$ and $E(b)$ are known (i.e. $m_a$ is not encrypted), we compute
-%     \begin{align*}
-%       E(m_c) &= m_a \otimes E(m_b)\\
-%       e_c &= e_a + e_b
-%     \end{align*}
-% \end{description}
-
-\subsection{Non-Linear Intensity Transformations}
-We will implement library functions for image negation, logarithm transformation and power-law transformation, as they are defined in~\cite{gonzalez_digital_2008}.
-We now describe how we implement the logarithm and power-law image intensity transformations.
-In the case of partially homomorphic cryptosystems (Paillier and DGK), if ciphertext multiplication or division is required, the secure protocols in section~\ref{sssec:pheextension} will be used.
-
-\subsubsection{Logarithm Transformation}
-The logarithm transformation of a pixel intensity value $x$ is defined as
-\begin{align}
-	T\left(x\right) = c \log\left(1 + x\right)
-\end{align}
-where $c$ is a constant.
-
-In order to perform this transformation under Paillier and DGK, we provide the following closed-form approximation for $\log\left(1 + x\right)$.
-% TODO: IDK HOW TO CITE OUR PCSC PAPER
-\begin{align}\label{eq:optimal_log_approximation}
-	\begin{split}
-		&\log\left(1+x\right) \approx \frac{a(x)}{b(x)} + \log{16}
-	\end{split}
-\end{align}
-where
-\begin{align*}
-	\begin{split}
-	a(x) &= 137x^5 + 26685x^4 + 617370x^3 - 6498630x^2 \\
-	&- 121239315x - 257804775\\
-	b(x) &= 30(x^5 + 405x^4 + 27210x^3 + 488810x^2 + 2536005x \\
-	&+ 3122577).
-	\end{split}
-\end{align*}
-% \begin{align}\label{eq:optimal_log_approximation}
-% 	\begin{split}
-% 		&\log\left(1+x\right) \\
-% 		&\approx \frac{137x^5 + 26685x^4 + 617370x^3 - 6498630x^2 - 121239315x - 257804775}
-% 		{30(x^5 + 405x^4 + 27210x^3 + 488810x^2 + 2536005x + 3122577)}\\
-% 		&+ \log{16}.
-% 	\end{split}
-% \end{align}
-
-\subsubsection{Power-Law Transformation}
-The power-law transformation of a pixel intensity value $x$ is defined as
-\begin{equation}
-    T\left(x\right) = cx^{\gamma}
-\end{equation}
-where $c>0$ and $\gamma > 0$.
-
-Similar to the logarithm transformation, to apply this transformation using Paillier and DGK, we must provide an approximation for $x^\gamma$.
-We can use partial sums of the following series, which relies on the logarithm function.
-\begin{align}
-	x^\gamma &= \sum_{n=0}^{\infty}{\frac{(\gamma\log{x})^n}{n!}}
-\end{align}
-% Partial sums of the above infinite series can be calculated based on the closed form approximation for the logarithm in Equation \ref{eq:scaledquadraturech3}. 
-For the implementation of the power-law transformation for this paper, a partial sum consisting of the first five terms of the infinite series were used.
-
-\subsection{Assessment of Homomorphic Encryption Schemes}
-A laptop computer with a 2.5 GHz Intel Core i7 quad-core processor and 8 GB of RAM is used to perform the computations, and processing time was tracked using built-in timing functions.
-The processing time for all cases were recorded.
-All of the tests are done using Python 3.7.1 running on Linux.
-
-\subsubsection{Image Quality of Intensity Transformations}
-In this section, we discuss the image quality metrics we used for assessing the performance of non-linear intensity transformations.
-
-We first obtained test images from the \texttt{faces94} dataset (\url{https://cswww.essex.ac.uk/mv/allfaces/faces94.html}) maintained by the University of Essex.
-However, only ten distinct facial images from the dataset were selected for the purposes of this test.
-Since only grayscale images are used in the study, the images were converted to grayscale and then downsampled to $40 \times 36$ pixels.
-
-For each cryptosystem, three image operations are tested:
-\begin{enumerate}
-	\item Image negation
-	\item Logarithm transformation, with $c = 30$
-	\item Power-law transformation, with $c = 1$ and $\gamma = 0.4$
-\end{enumerate}
-
-For each plaintext image (PT), we considered each image operation listed above and generate three images: a plaintext domain transformation (PDT), a ciphertext image (CT), and an ciphertext domain transformation (CDT).
-The PDT was generated by running the image operation on the original image.
-The CT was generated by encrypting the image, then applying the operation, and the CDT was generated by decrypting the CT.
-The three images (PT, PDT, CDT) were then compared using various benchmarks to evaluate the quality and security of each homomorphic encryption scheme.
-
-The benchmarks to be used in the study, adopted from~\cite{ahmed_benchmark_2016, ahmad_efficiency_2012, wu_npcr_2011} are listed below.
-We let $X_i$ denote a value in an image $X$, where $1 \leq i \leq N$.
-We first perform three tests to ascertain the preservation of image quality after encryption and decryption: MSE, PSNR, and SSIM.
-\begin{description}
-	\item [Mean Squared Error (MSE).] The MSE is defined in~\cite{ahmed_benchmark_2016} as
-	\begin{align}
-        \mathrm{MSE} = \frac{1}{N}\sum_{i=1}^{N}{(\mathrm{CDT}_i - \mathrm{PDT}_i)^2}.
-	\end{align}
-	The MSE provides a measure of how much data is recovered if an image operation is applied on the encrypted image, which is then decrypted.
-Lower values of MSE indicate higher preservation of image quality~\cite{ahmed_benchmark_2016, ahmad_efficiency_2012}.
-	\item [Peak Signal to Noise Ratio (PSNR).]
-	According to Ahmed, et al.~\cite{ahmed_benchmark_2016}, PSNR is ``an estimator for human visual perception of reconstruction quality.'' It has been used to ascertain image quality in various studies and is a known metric for image and video quality~\cite{upmanyu_efficient_2009, jain_image_2016, akramullah_video_2014}.
-Although it may produce results which do not correlate with human visual perception~\cite{huynh-thu_accuracy_2012, ahmed_benchmark_2016}, it is a valid indicator of image quality when media containing the same visual content is compared~\cite{huynh-thu_accuracy_2012}.
-	PSNR is defined by
-	\begin{align}
-        \mathrm{PSNR} = 10\log_{10}{\left( \frac{L^2}{\mathrm{MSE}} \right)}
-	\end{align}
-	where $L$ is the maximum pixel intensity value of an image.
-	Despite the known limitations of PSNR, since we are going to compare the effect of each encryption scheme on recovered image quality, given a fixed library of images, it is a valid measure of image quality for the study.
-A higher PSNR indicates higher image quality preservation.
-	\item [Structural Similarity Index (SSIM).]
-	The SSIM for two random variables $X$ and $Y$ is defined in~\cite{ahmed_benchmark_2016, akramullah_video_2014} as
-	\begin{align}
-        \mathrm{SSIM}(X,Y) = \frac{(2\mu_X\mu_Y+c_1)(2\sigma_{XY}+c_2)}{(\mu_X^2+\mu_Y^2+c_1)(\mu_X^2+\mu_Y^2+c_2)}
-	\end{align}
-	where
-	\begin{itemize}
-		\item $\mu_X, \mu_Y$ are the averages of $X$ and $Y$, respectively;
-		\item $\sigma_X, \sigma_Y$ are the variances of $X$ and $Y$, respectively;
-		\item $\sigma_{XY}$ is the covariance of $X$ and $Y$;
-		\item $c_1 = (k_1L)^2, c_2 = (k_2L)^2$ are two variables used to stabilize the measure when $\mu_X^2+\mu_Y^2$ is close to zero~\cite{akramullah_video_2014};
-		\item $L$ is the the maximum pixel intensity value of an image;
-		\item $k_1 = 0.01, k_2 = 0.03$ by default, given in~\cite{ahmed_benchmark_2016}.
-	\end{itemize}
-	The SSIM is applied to the luminance value of two images to gauge structural similarity between neighboring pixels.
-	For the study, we computed $\mathrm{SSIM}(\mathrm{PDT}, \mathrm{CDT})$ for every image operation, under each homomorphic cryptosystem.
-Higher values of SSIM indicate higher structural similarity, and an SSIM of $1$ indicates that the two images are identical~\cite{ahmed_benchmark_2016}.
-\end{description}
-
-Computing for MSE, PSNR, and SSIM was done using the corresponding built-in functions from the scikit-image Python library \cite{scikit-image}.
-
-\subsubsection{Facial Recognition Tests}
-The method for secure facial recognition using eigenfaces by Erkin, et al. \cite{hutchison_privacy-preserving_2009} was implemented for this study.
-
-As before, training and test data were also secured from the \texttt{faces94} dataset. The images were first converted to grayscale and then downsampled to $40 \times 36$ pixels.
-
-The facial recognition tests are done using ten-fold cross-validation for each cryptosystem, where the number of principal components used by the algorithm is fixed at $K=5$.
-
-Prior to splitting the dataset, the images within each set are shuffled.
-Since there are twenty (20) images per set, two images are taken at a time for each round of cross-validation.
-The first round would take the first two images from each set as part of the test set, and the rest of the images will be part of the training set.
-Then, the succeeding round would take the next two images from each set as part of the test set, and so on until ten rounds have been done.
-After every round of cross-validation, the accuracy score, confusion matrix, and total processing time are obtained.
-
-%% Summary not needed, this was only important for the thesis proposal - Aldrich
-% \subsection{Summary}
-% In summary, the study consists of:
-% \begin{itemize}
-% 	\item Creating a wrapper library that acts as a unified interface which implements the Paillier, DGK, Dasgupta--Pal, and BGV homomorphic cryptosystems.
-% 	\item An implementation of image processing operations (intensity transformations, facial recognition) under the above cryptosystems.
-% 	\item Conducting tests for image quality, processing time, using images from the \texttt{faces94} dataset.
-% \end{itemize}
-
 \section{Preliminary Results and Discussion}
@@
 \end{table}
-
-\section{Conclusion}
-In this paper, we have assessed the feasibility and practicality of various homomorphic cryptosystems with regard to secure processing and manipulation of facial image data through creation of a software library that facilitates image processing operations within the encrypted domain, as well as our own implementation of some homomorphic cryptosystems like DGK.
-
-% This paper also proposes a correction to the Dasgupta--Pal cryptosystem which is further explained in Appendix~\ref{chap:correction}.
-
-Even though an operation in a partially homomorphic cryptosystem is not theoretically possible, like multiplication of two ciphertexts under Paillier, it has been shown that such operations are indeed possible in a two-party system.
-Protocols for secure multiplication and exponentiation have been proposed and also applied to more complex image operations such as facial recognition.
-Thus, a partially homomorphic cryptosystem can be modified to admit more image processing operations by assuming a two-party system.
-
-Preliminary results have shown that both Paillier and DGK apply image negation accurately and efficiently, as evidenced by the perfect zero MSE and infinite PSNR.
-For the logarithm transformation, Paillier was faster and accurate enough (with $\text{MSE} \le 30$ and $\text{SSIM} \approx 0.99$) which was rather unexpected.
-However both Paillier and DGK fail to produce accurate results in applying the power-law transformation, with the latter failing to produce discernible results.
-Based from these results, the Paillier cryptosystem is consistent enough to produce reasonable to accurate results.
-
-A wrapper library has been made which implements the various functions and methods of the cryptosystems into a single interface.
-This allowed us to express various image operations with a unified syntax, thus facilitating easier testing.
-
-\subsection{Ongoing and Future Work}
-Testing intensity transformations under the BGV cryptosystem will be started once the Pyfhel library is deemed stable enough to use, or another Python library that implements BGV becomes available. 
-One of the authors of this paper has already informed the developers of the Pyfhel library about a bug involving exponentiation of two real numbers.
-
-Efforts are ongoing with regard to the facial recognition tests.
-Our own implementation of the privacy-preserving  eigenfaces by Erkin, et al.
-does not yet use the DGK cryptosystem for secure integer comparison in the match finding step, thus we are working on implementing DGK from scratch.
-
-Another promising image operation to consider is \textit{facial detection} under a homomorphic cryptosystem.
-Work has been started in order to assess the feasibility of using Haar cascades in a privacy-preserving manner.
-
-Future work would involve improving and optimizing our implementation of non-linear intensity transformations in terms of number of operations, numerical accuracy and stability, and time efficiency.
-% Future work would involve improving and optimizing our implementation of the DGK cryptosystem so that it performs faster. 
-% A suggestion would be to port the existing implementation to C/C++ and then create a Python library that acts as a wrapper to the C/C++ methods. 
-For future studies, an implementation of a client-server framework or system dealing with secure image processing can be considered.

### 2019-03-12 icmssp-paper/parts/05_conclusion.tex
Change folder structure
- renamed paper folder to icmssp-paper
- split icmssp paper into parts

--- 2019-02-10 paper/paper-conf.tex
@@
-\section{Introduction}
-\subsection{Context of the Study}
-Digital data privacy and security is a growing concern in various fields, such as cloud computing~\cite{potey_homomorphic_2016}, health information systems~\cite{kester_cryptographic_2015}, and video surveillance~\cite{upmanyu_efficient_2009}.
-To meet these needs, various cryptosystems have been developed.
-A cryptosystem is a system which operates on plaintexts, ciphertexts and keys using an encryption algorithm, which maps a plaintext to a ciphertext, together with a decryption algorithm, which maps a ciphertext to a plaintext, given an appropriate key~\cite{bauer_cryptosystem_2005}.
-The encryption and decryption algorithms are chosen such that the plaintext cannot easily be recovered from the ciphertext without knowledge of the key.
-This allows data to be securely transmitted over an insecure channel.
-
-One particular application of cryptography is image encryption.
-While cryptosystems used to encrypt digital data in general, such as the Advanced Encryption Standard (AES) or elliptic curve cryptography, can also be used to encrypt images~\cite{jain_image_2016, singh_image_2015} other algorithms created specifically for image encryption have also been developed~\cite{murugan_survey_2018}.
-
-In a homomorphic cryptosystem, operations such as addition and multiplication can be performed on encrypted data.
-These operations are then preserved when the data is decrypted.
-In this manner, data is manipulated without compromising data privacy, as the encrypted data being operated on remains secure~\cite{fontaine_survey_2007, sen_homomorphic_2013}.
-In the area of homomorphic image encryption, there is interest in being able to perform image manipulation operations on the encrypted data such as image adjustment, filtering, and morphological/feature extraction operations~\cite{ziad_cryptoimg:_2016, gonzalez_digital_2008}.
-More advanced operations have also been implemented using homomorphic cryptosystems, such as facial recognition \cite{hutchison_privacy-preserving_2009} and neural networks \cite{hesamifard_cryptodl:_2017}.
-This study in particular focuses on facial recognition.
-
-% \subsection{Research Questions}
-% By implementing homomorphic cryptosystems and creating a library so they can be easily used, we aim to address our main research question: What is the best method for facial image data to be encrypted and manipulated for practical applications?
-
-% More specifically, our research will address the following sub-questions:
-% \begin{enumerate}
-% 	\item Which homomorphic cryptosystems admit more image processing operations? How can existing homomorphic cryptosystems be modified to admit more image processing operations?
-% 	\item Which homomorphic cryptosystems are the most time-efficient and the most accurate in applying image processing operations?
-% 	\item Which homomorphic cryptosystems best preserve image quality in applying image processing operations?
-% \end{enumerate}
-
-\subsection{Research Objectives}
-% Previous attempts in the literature to provide image processing tasks such as image manipulation \cite{ziad_cryptoimg:_2016} and  facial recognition \cite{hutchison_privacy-preserving_2009} have primarily used the Paillier and  Damg{\aa}rd--Geisler--Kr{\o}igaard (DGK) cryptosystems to perform linear operations on encrypted data.
-% In this study, we extend this research to provide an objective comparison of various homomorphic cryptosystems currently in the literature in performing non-linear operations, and facial detection, as opposed to just linear operations and facial recognition.
-
-Our main research objective is to assess the practicality of various homomorphic cryptosystems with regard to image processing on faces. 
-% Homomorphic cryptosystems are known to be slower in terms of encryption, operation, and decryption time~\cite{sen_homomorphic_2013}.
-Furthermore, the operations on encrypted data supported by homomorphic cryptosystems are limited, and some schemes require preprocessing to be performed on images, limiting the range of operations which can be performed efficiently~\cite{li_elliptic_2012}.
-
-% In summary, in this study, we wish to
-More specifically, we wish to do the following:
-\begin{enumerate}
-    \item Implement common linear and non-linear image processing operations using known homomorphic encryption schemes, then determine which schemes admit more image processing operations and extend known cryptosystems to support more operations, if possible;
-    \item Compare the time efficiency and accuracy of common image processing operations under known homomorphic encryption schemes, and of common image processing operations without using homomorphic encryption;
-    \item Create a library to allow for convenient use and comparison of these homomorphic encryption schemes for image processing and facial recognition.
-\end{enumerate}
-
-\subsection{Scope and Limitations}
-% Our study will be limited in terms of the cryptosystems to be tested, the image processing operations we will implement, and the statistical tests we will use to gauge the security of the cryptosystems.
-Below is a listing of the scope of the study.
-
-% We will implement and test the following algorithms:
-In this study, we will implement and test the following cryptosystems:
-\begin{enumerate}
-	\item A variant of the Paillier cryptosystem~\cite{stern_public-key_1999} which supports floating-point operations, used in \textit{CryptoImg}~\cite{ziad_cryptoimg:_2016}.
-    \item The Damg{\aa}rd--Geisler--Kr{\o}igaard (DGK) cryptosystem~\cite{pieprzyk_efficient_2007, cryptoeprint:2008:321} which is primarily used for secure integer comparison.
-	% \item A fully homomorphic encryption scheme by Dasgupta and Pal, which uses polynomial rings~\cite{dasgupta_design_2016}.
-	\item The Brakerski--Gentry--Vaikuntanathan (BGV) cryptosystem \cite{cryptoeprint:2011:277}, an improvement on the lattice-based cryptosystem by Gentry~\cite{gentry_fully_2009}, with optimizations from Smart, Vercauteren, and Halevi \cite{hutchison_fully_2010, cryptoeprint:2011:566}.
-\end{enumerate}
-We will implement and test the following categories of image manipulation operations:
-\begin{enumerate}
-	\item Non-linear image intensity adjustment (logarithm and power-log transformations)
-	\item Facial detection and recognition using the eigenface approach \cite{turk_eigenfaces_1991}.
-\end{enumerate}
-We will adopt the benchmark for evaluating image quality of image encryption schemes presented by Ahmed, et.
-al~\cite{ahmed_benchmark_2016}.
-The presented benchmark reflects many tests used in other literature~\cite{ahmad_efficiency_2012, wu_npcr_2011}.
-\begin{enumerate}
-    \item Mean Squared Error (MSE)
-    \item Peak Signal to Noise Ratio (PSNR)
-    \item Structural Similarity Index (SSIM)
-\end{enumerate}
-A detailed overview of the above will be provided in the methodology. Grayscale images will be used in the study.
-A client-server model for secure computation will be assumed to allow operations such as secure comparison and exponentiation.
-Training and test data are taken from the publicly available \texttt{faces94} dataset (\url{https://cswww.essex.ac.uk/mv/allfaces/faces94.html}) maintained by the University of Essex.
-
-\subsection{Significance of the Study}
-This study aims to directly address one of the current problems in the research of homomorphic cryptosystems: the practicality of homomorphic encryption~\cite{sen_homomorphic_2013}.
-The literature shows existing homomorphic cryptosystems and how they support primitive operations (usually addition and multiplication) on encrypted data, however, for homomorphic cryptosystems to be useful for practical use, efficient support for more complicated image processing operation must be demonstrated as well.
-While implementations of image processing operations in a homomorphic cryptosystem exist in the literature~\cite{ziad_cryptoimg:_2016, garay_algorithms_2014}, our study targets the more computationally intensive task of facial detection.
-
-We wish to contribute to existing models for the secure transmission and modification of image data by developing a software library which allows the use and comparison of various homomorphic encryption algorithms.
-Our software library would allow service providers to perform image manipulation for clients without compromising data privacy.
-
-\section{Review of Related Literature}
-\subsection{Homomorphic Cryptosystems}
-A cryptosystem consists of an encryption function $\mathcal{E}$ and a decryption function $\mathcal{D}$, along with the plaintext space $\mathcal{P}$, ciphertext space $\mathcal{C}$ and the key space $\mathcal{K}$~\cite{bauer_cryptosystem_2005}.
-A \textit{plaintext} is text that can be commonly understood, while a \textit{ciphertext} results from encrypting the plaintext using an encryption key.
-The \textit{plaintext space} is the set of all possible plaintexts, the \textit{ciphertext space} is the set of all possible ciphertexts, while the \textit{keyspace} is the set of all possible keys.
-
-% There are two kinds of cryptosystems, \textit{symmetric} and \textit{asymmetric}.
-In symmetric-key cryptosystems, the same key is used for both encryption and decryption.
-As a consequence, symmetric-key cryptosystems must be implemented with a secure key exchange protocol, so that both the sender and receiver have access to the same key.
-Prominent examples of symmetric-key cryptosystems are the Data Encryption Standard (DES), and its replacement, the Advanced Encryption Standard (AES).
-
-% On the other hand, asymmetric-key (or public-key) cryptosystems use separate keys for encryption and decryption.
-The encryption key (also called the \textit{public key}) is shared publicly, while the decryption key (also called the \textit{private key}) is kept secret.
-Since the public key and private keys are different, there is no need to agree upon secure key exchange protocols.
-Usually, the security of asymmetric-key cryptosystems relies on the intractability of certain computational problems, for example, the RSA cryptosystem depends on the difficulty of big integer factorization~\cite{rivest_method_1978}, while the ElGamal cryptosystem depends on the difficulty of the discrete logarithm problem~\cite{blakley_public_1985}.
-
-% Homomorphic cryptosystems are a special type of cryptosystem in which operations can be securely performed on encrypted data.
-Suppose that for a public-key cryptosystem, $\mathcal{E}_k \left(p \right)$ is the encryption function using the public key $k \in \mathcal{K}$, and $\mathcal{D}_l \left(c \right)$ be the decryption function using the private key $l$.
-A cryptosystem is said to be homomorphic if its encryption function is homomorphic, that is, if it satisfies the relation
-% \begin{equation}
-%     \mathcal{E}_k \left(p_1 \boxplus p_2\right) = \mathcal{E}_k \left(p_1\right) \boxdot \mathcal{E}_k \left(p_2\right)
-% \end{equation}
-% where $p_1, p_2 \in \mathcal{P}$ are the plaintexts, and $\boxplus$ and $\boxdot$ are operations in $\mathcal{P}$ and $\mathcal{C}$ respectively~\cite{fontaine_survey_2007}.
-Furthermore, a homomorphic cryptosystem also satisfies~\cite{li_elliptic_2012}
-% \begin{equation}
-%     p_1 \boxplus p_2 = \mathcal{D}_l \left( \mathcal{E}_k \left(p_1\right) \boxdot \mathcal{E}_k \left(p_2\right) \right).
-% \end{equation}
-
-% In other words, 
-A homomorphic cryptosystem preserves the operations that can be done with the plaintext without requiring an intermediary step of decrypting the ciphertext beforehand.
-It is important to note that the operations in the plaintext space and ciphertext space need not be the same.
-A simple operation in the plaintext space may require a computationally intensive operation in the ciphertext space.
-
-% Homomorphic cryptosystems can be classified according to the plaintext and ciphertext operations, $\boxplus$ and $\boxdot$.
-If the plaintext operation $\boxplus$ is addition, the cryptosystem is said to be \textit{additively homomorphic}, and the cryptosystem is said to be \textit{multiplicatively homomorphic} if the plaintext operation $\boxplus$ is multiplication.
-
-\subsection{Partially Homomorphic Cryptosystems}
-In this section, we will present two classical partially homomorphic cryptosystems which we will be testing in the study: the Paillier cryptosystem and the DGK cryptosystem.
-Both of these cryptosystems encrypt integer plaintexts as integer ciphertexts.
-In our description of each cryptosystem, we use $E(m)$ to denote the encryption of a plaintext $m$, and $D(c)$ to denote the decryption of a ciphertext $c$.
-
-% We will then show that the cryptosystems can be modified to support privacy-perserving polynomial evaluation in a client-server protocol: given an encrypted message $m$, evaluate $f(m)$ where $f$ is a polynomial function.
-
-\subsubsection{The Paillier Cryptosystem}
-The Paillier cryptosystem \cite{stern_public-key_1999}, developed by Pascal Paillier, is a probabilistic encryption scheme which is based on the composite residuosity class problem.
-The scheme has several well--known homomorphic properties.
-% The scheme allows for the encryption and decryption of integer messages, and is known to be additively homomorphic.
-% We now state the encryption and decryption algorithms of the Paillier cryptosystem and its homomorphic properties.
-
-% \paragraph{Key Generation}
-% We first define a function $L(x)$ as the largest integer $v$ greater than zero such that $x-1 \geq vn$.
-% We choose two large primes $p$ and $q$, and set $n = pq, \lambda = \mathrm{lcm}(p-1,q-1)$.
-% Then we select an integer $g$, $0\leq g \leq n^2$ such that $\mathrm{gcd}(L(g^\lambda \bmod n^2), n) = 1$.
-% We denote the public key as $(g,n)$ and the private key $(p,q)$.
-
-% \paragraph{Encryption and Decryption}
-% The encryption function to encrypt a plaintext $m \in \mathbb{Z}_n$ given a public key $(g,n)$ is defined as
-% \begin{align*}
-%   E(m) = g^m \cdot r^n \mod{n^2},
-% \end{align*}
-% where $r$ is a random non-negative integer less than $n^2$.
-
-% The decryption function to decrypt a ciphertext $c \in \mathbb{Z}^\ast_{n^2}$ given a private key $(p,q)$ is defined as:
-% \begin{align*}
-%   D(c) = L(c^\lambda \bmod n^2) \times (L(g^\lambda \bmod n^2))^{-1} \mod n
-% \end{align*}
-
-% \paragraph{Homomorphic Properties of the Paillier Cryptosystem}
-% The Paillier cryptosystem supports additive homomorphism as well as the multiplication of a plaintext scalar to an encrypted message.
-These homomorphic properties are used to add a plaintext scalar to a ciphertext, add two ciphertexts, and multiply a ciphertext by a plaintext scalar, respectively.
-They are defined as follows.
-
-For all $m_1,m_2 \in \mathbb{Z}_n$ and $k\in \mathbb{N}$, the following homomorphic properties hold for the Paillier cryptosystem with public key $(g,n)$.
-\begin{align*}
-  D(E(m_1)g^k\bmod n^2) &=(m_1+k)\bmod n\\
-  D(E(m_1)E(m_2)\bmod n^2) &=(m_1+m_2)\bmod n\\
-  D(E(m_1)^k\bmod n^2) &= km_1\bmod n
-\end{align*}
-
-These homomorphic properties are used to add a plaintext scalar to a ciphertext, add two ciphertexts, and multiply a ciphertext by a plaintext scalar, respectively.
-
-\subsubsection{The DGK Cryptosystem}
-The DGK cryptosystem was published by Damg{\aa}rd, Geisler, and Kr{\o}igaard in 2007 in an effort to create a secure integer comparison scheme \cite{pieprzyk_efficient_2007, cryptoeprint:2008:321} which is widely used in the literature \cite{veugen_improving_2012}.
-The DGK cryptosystem has homomorphic properties similar to the Paillier cryptosystem.
-
-% \paragraph{Key Generation}
-% We denote $k,t,\ell$ as security parameters of the scheme, where $k>t>\ell$.
-% Let $p,q$ be primes such that
-% we can choose two $t$-bit primes $v_p$ and $v_q$ such that $v_p | (p-1)$ and $v_q | (q-1)$, and a small prime $u$ such that $u | (p-1)$ and $u | (q-1)$.
-% We denote $n = pq$.
-% We choose $g$ to be an integer of order $uv_pv_q$ and $h$ to be of order $v_pv_q$.
-
-% The DGK cryptosystem encrypts plaintexts in $\mathbb{Z}_u$ to ciphertexts in $\mathbb{Z}_n^\ast$.
-
-% The public key is $(n,g,h,u)$ and the private key is $(p,q,v_p,v_q)$.
-
-% \paragraph{Encryption and Decryption}
-% To encrypt a message $m \in \mathbb{Z}_u$, the encryption function is defined as:
-% \begin{align*}
-%   E(m) = g^m \cdot h^r \mod{n},
-% \end{align*}
-% where $r$ is a random integer in $\mathbb{Z}_n$ which is longer than $2t$ bits.
-
-% To decrypt a ciphertext $c \in \mathbb{Z}_n^\ast$, decryption is achieved by first computing $c^{v_pv_q}$.
-% \begin{align*}
-% 	c^{v_pv_q} \bmod n
-% 	&= (g^m \cdot h^r)^{v_pv_q} \bmod n\\
-% 	&= (g^{v_pv_q})^m \bmod n
-% \end{align*}
-% Since $(g^{v_pv_q})^m$ has order $u$, there is a one-to-one correspondence between plaintexts in $\mathbb{Z}_u$ and  $(g^{v_pv_q})^m$.
-A lookup table can thus be generated privately to successfully recover $m$.
-
-% \paragraph{Homomorphic Properties of the DGK Cryptosystem}
-% The DGK cryptosystem supports additive homomorphism as well as the multiplication of a plaintext scalar to an encrypted message.
-These homomorphic properties are used to add a plaintext scalar to a ciphertext, add two ciphertexts, and multiply a ciphertext by a plaintext scalar, respectively.
-They are defined as follows.
-
-For all $m_1,m_2 \in \mathbb{Z}_u$ and $k\in \mathbb{N}$, the following homomorphic properties hold for the DGK cryptosystem with public key $(n,g,h,u)$.
-\begin{align*}
-    D(E(m_1)g^k) &=(m_1+k)\bmod u\\
-    D(E(m_1)E(m_2)) &=(m_1+m_2)\bmod u\\
-    D(E(m_1)^k) &= km_1\bmod u
-\end{align*}
-
-As the multiplicative homomorphism was not presented in the original paper, we provide a short proof here.
-\begin{proof}
-  Let $m \in \mathbb{Z}_u$ and $k\in \mathbb{N}$.
-  We consider $E(m)^k = (g^m \cdot h^r \bmod{n})^k\bmod n$.
-  \begin{align*}
-    (g^m \cdot h^r \bmod{n})^k \bmod n
-    &= (g^m \cdot h^r)^k \bmod{n}\\
-    &= (g^m)^k \cdot (h^r)^k \bmod{n}\\
-    &= g^{km} \cdot (h^kr) \bmod{n}
-  \end{align*}
-  Since $r$ is a random integer, $kr$ is also a random integer, Therefore, $g^{km} \cdot (h^kr) \bmod{n} = D(E(m_1)^k)$ is a valid encryption of the message $km$.
-\end{proof}
-
-% \subsubsection{Secure Exponentiation and Multiplication Protocols}
-% \label{ssec:exponentiationprotocol}
-% [TO-DO: This is further explained in another paper.]
-% In order to perform polynomial evaluation, we first present a protocol for privacy-preserving exponentiation to a positive integer power, adapted from the protocol to calculate Euclidean distances used in \cite{hutchison_privacy-preserving_2009}.
-
-% The following protocols apply to both the Paillier and DGK cryptosystems, as they share similar homomorphisms. We first present a secure squaring protocol.
-
-% Suppose Alice encrypts an integer $x$ and sends it so Bob has $E(x)$, and wants to obtain $E(x^2)$ without exposing the value of $x$.
-% \begin{itemize}
-% 	\item Bob first selects a random integer $r$ and computes $E(x+r)$. Bob can do this since $r$ is a plaintext constant.
-% 	\item Bob sends $E(x+r)$ to Alice, who decrypts the ciphertext to obtain $x+r$.
-% 	\item Alice squares $x+r$ and encrypts the result. She sends $E((x+r)^2)$ to Bob.
-% 	\item Bob computes $E(-2rx + r^2)$. He then computes $E((x+r)^2)E(-2rx + r^2) = E(x^2)$.
-% \end{itemize}
-
-% We can use the secure squaring protocol to arrive at a secure multiplication protocol, which then allows for the evaluation of polynomials.
-% Suppose Alice encrypts integers $x$ and $y$, and Bob has $E(x), E(y)$ and wants to obtain $E(xy)$.
-% \begin{itemize}
-% 	\item Bob acquires $E(x^2), E(y^2)$ using the secure squaring protocol.
-% 	\item Bob sends $E(x+y)$ to Alice, who decrypts the ciphertext to obtain $x+y$.
-% 	\item Alice sends $E((x+y)^2)$ to Bob.
-% 	\item Bob then computes
-% 	\begin{align*}
-% 		E((x+y)^2)E(x^2)^{-1}E(y^2)^{-1} &= E((x+y)^2 - x^2 - y^2)\\
-% 		&= E(2xy)
-% 	\end{align*}
-% 	\item Bob can then recover $E(xy)$ by calcuating for the multiplicative inverse of 2 using the Euclidean algorithm, and calculating $2^{-1}E(xy)$.
-Such an inverse exists since the modulus is either a prime (in the DGK cryptosystem) or a product of primes greater than 2 (in the Paillier cryptosystem).
-% \end{itemize}
-
-\subsection{Fully Homomorphic Cryptosystems}
-We will also be testing fully homomorphic cryptosytems, which allow aribitrary computation on encrypted data.
-While generally being more flexible, fully homomorphic cryptosytems are known to be significantly slower than partially homomorphic cryptosytems; improving the efficiency of fully homomorphic cryptosytems is an active area of research \cite{sen_homomorphic_2013}.
-
-% We will present two such cryptosystems, the Dasgupta--Pal cryptosystem, which we present in full to explain a correction we propose to it, and the BGV cryptosystem, which has open source implementations availble primarily used in homomorphic cryptography research.
-
-% \subsubsection{The Dasgupta--Pal Cryptosystem}
-% The Dasgupta--Pal cryptosystem is a fully homomorphic cryptosystem proposed in 2016 by Smaranika Dasgupta and S.
-K.
-Pal \cite{dasgupta_design_2016}, which encrypts integer plaintexts in $\mathbb{Z}_n$ to polynomial ciphertexts.
-We begin our presentation of the Dasgupta--Pal cryptosystem with the following definition.
-
-% Given a message $m \in \mathbb{Z}$, we denote
-% \begin{align*}
-% 		m_p(x) = a_0 + a_1 x + a_2 x^2 + \cdots + a_k x^k
-% \end{align*}
-% where $a_k a_{k-1}\cdots a_2 a_1 a_0$ is the binary representation of $m$.
-
-% In the original scheme presented in \cite{dasgupta_design_2016}, the secret key $S_k$ is set to be a large prime.
-In Appendix \ref{chap:correction}, we present a case where the Dasgupta--Pal cryptosystem fails and prove that setting the secret key $S_k = 2p$, where $p$ is a large prime, corrects errors in the Dasgupta--Pal cryptosystem.
-% We now decribe the correct cryptosystem.
-% \paragraph{Corrected Dasgupta--Pal Cryptosystem Description}
-% Let $\ell$ denote the security parameter of the cryptosystem.
-% Let $S_k = 2p$, where $p$ is a prime number with $\ell - 1$ bits.
-% Choose a random even integer $z$ of length $\log_2{\ell}$.
-
-% Let the secret key be $S_k$, and let the refresh key be $R_k = z \cdot S_k$. The secret key is kept private to the encrypting/decrypting parties, while the refresh key is made publicly available.
-
-% The scheme defines the encryption algorithm for a message $m$ as follows:
-% \begin{align*}
-% 	E(m) = y(x) + S_k\times d(x)
-% \end{align*}
-% where
-% $y(x)$ is a polynomial of degree $n$ such that $m_p(x) \equiv y(x) \bmod S_k$ and $d(x)$ is a randomly chosen polynomial of degree $n$.
-This encrypts each coefficient of $m_p(x)$ by adding some multiple of $S_k$ to it.
-Through this process, each bit of the message is encrypted separately.
-
-% Furthermore, the decryption algorithm to recover $m_p(x)$ from a ciphertext polynomial $c(x)$ as
-% \begin{align*}
-% 	m_p(x) = c(x) \bmod S_k \bmod 2.
-% \end{align*}
-% Thus $D(c(x))$ is defined as the integer recovered from the coefficients of the polynomial $c(x) \bmod S_k \bmod 2$.
-
-% Dasgupta and Pal note that homomorphic operations on ciphertext introduce noise which may interfere with decryption, due to the potential increase in ciphertext values.
-% To eliminate noise from a polynomial ciphertext, the following refresh function is used:
-% \begin{align*}
-% 	R(c(x)) = c(x) \bmod R_k.
-% \end{align*}
-
-% \paragraph{Homomorphic Properties of the Dasgupta--Pal Cryptosystem}
-% It has been shown \cite{dasgupta_design_2016} that the following properties hold for all integer messages $m_1, m_2 \in \mathbb{Z}_n$ in the Dasgupta--Pal cryptosystem.
-These properties arise since each coefficient in a ciphertext polynomial is essentially an independently encrypted bit of the original message.
-% \begin{description}
-% 	\item[\textsc{xor} on ciphertexts]
-% 	A bitwise exclusive or (\textsc{xor}) operation on integer messages can be achieved by adding the coefficients pairwise between two ciphertexts.
-% 	\begin{align*}
-% 		D(E(m_1)+E(m_2)) = m_1 \textsc{ xor } m_2
-% 	\end{align*}
-% 	\item[\textsc{and} on ciphertexts]
-% 	Similarly, pair-wise multiplication corresponds to bitwise \textsc{and} of integer messages.
-% 	\begin{align*}
-% 		D(E(a) \otimes E(b)) = a \textsc{ and } b = ab \bmod 2
-% 	\end{align*}
-% 	where $\otimes$ denotes pairwise multiplication,
-% 	\begin{align*}
-% 		\sum_{i=1}^n{a_ix^i} \otimes \sum_{i=1}^n{b_ix^i} = \sum_{i=1}^n{a_ib_ix^i}.
-% 	\end{align*}
-% \end{description}
-
-% Arbitrary computation on data can thus be achived using these bitwise operations.
-While the Dasgupta--Pal cryptosystem requires significant amounts of memory, as each bit of plaintext is encrypted into an integer, this approach provides a flexible method to perform relatively fast arbitrary computation on encrypted data.
-Encryption and decryption in the Dasgupta--Pal cryptosystem are accomplished using few arithmetic operations.
-
-% \subsubsection{HElib and the BGV Cryptosystem}
-The BGV (Brakerski--Gentry--Vaikuntanathan) cryptosystem \cite{cryptoeprint:2011:277} is a fully homomorphic cryptosystem created based on the ring-learning with error problem.
-The BGV cryptosystem was constructed to surpass the limitations of prior fully homomorphic cryptosystems, which were based on the first fully homomorphic cryptosystem by Gentry \cite{gentry_fully_2009}.
-
-The details regarding the construction of the BGV cryptosystem are beyond the scope of this paper.
-For this study, we will be using \textit{HElib} \cite{garay_algorithms_2014}, an open-source library which implements the BGV cryptosystem with optimizations to improve efficiency.
-Evaluation of operations on 120 inputs in HELib was performed in around 4 minutes, with an average of 2 seconds to process a single input \cite{hutchison_fully_2010,cryptoeprint:2011:566}.
-
-The \textit{HElib} library has been adapted to Python using the Pyfhel library \cite{pyfhel_2018} maintained by Ibarrondo, Laurent (SAP) and Onen (EURECOM), and licensed under the GNU GPL v3 license.
-The Pyfhel library is a Python API for the \textit{HElib} library, which supports the following operations on vectors/scalars of integers or binary ciphertexts:
-\begin{itemize}
-	\item Arithmetic operations: addition, subtraction, multiplication;
-	\item Binary operations: \textsc{and}, \textsc{or}, \textsc{not}, \textsc{xor}.
-\end{itemize}
-
-\subsection{CryptoImg}
-A paper published in 2009 by Ziad, et al.
-attempts to implement privacy-preserving image processing using \textit{CryptoImg}, a library for the Open Source Computer Vision Library (OpenCV)~\cite{bradski_opencv_2000} which implements various homomorphic encryption and image processing routines using the Paillier homomorphic cryptosystem~\cite{ziad_cryptoimg:_2016}.
-The CryptoImg library assumed a client-server model wherein a client requests image processing operations from a server.
-A client first encrypts a digital image and sends the image securely to a server, which then operates on the encrypted image without revealing its contents.
-Then the resulting image is sent back to the client, which decrypts the image to recover the desired output.
-\begin{figure}[!ht]
-    \centering
-    \includegraphics[width=0.4\textwidth]{figures/ClientServerModel.png}
-    \caption{Client-server architecture used by \textit{CryptoImg} \cite{ziad_cryptoimg:_2016}}
-    \label{fig:clientserver}
-\end{figure}
-
-The \textit{CryptoImg} library implemented the following:
-\begin{enumerate}
-	\item Extending the Paillier homomorphic cryptosystem which operate on integer plaintexts so that they can operate on real number plaintexts;
-	\item Developing protocols for and implementing the following image processing operations
-	\begin{enumerate}
-		\item Image negation and brightness adjustment
-		\item Spatial filters (for noise reduction, edge detection and sharpening)
-		\item Morphological operations
-		\item Histogram equalization
-	\end{enumerate}
-\end{enumerate}
-For image negation and spatial filters, the protocols specified by \textit{CryptoImg} allow all image processing operations to be performed on the server.
-However, due to limitations in the Paillier cryptosystem, the protocols presented for morphological operations and histogram equalization require both the client and the server to perform image processing calculations, although the server performs a significant portion of the processing.
-
-Ziad, et al.
-also showed experimental results establishing the slow performance of image operations under a homomorphic cryptosystem.
-For instance, while sharpening and applying a Sobel filter each take less than a second when applied to a $512\times 512$ plaintext image, when applied to an encrypted image, sharpening required at least 238.257 seconds, and applying the Sobel filter required at least 147.567 seconds \cite{ziad_cryptoimg:_2016}.
-
-We now discuss several limitations in the \textit{CryptoImg} study which we focus on for our research.
-First, the \textit{CryptoImg} library was limited in the image intensity transformations it implemented.
-We propose additional protocols to support more computationally intensive intensity transformations.
-Second, the \textit{CryptoImg} library only considered the Paillier cryptosystem.
-We consider testing the performance of other homomorphic cryptosystems, which differ in their processing time and supported operations.
-
-\subsection{Image Intensity Transformations}
-We represent a digital image $R$ as an $M \times N$ matrix of pixel intensity values, each value in the range $\left[0, L-1\right]$, for some positive integer $L$.
-We denote with $R(x,y)$ the entry at the $x$th row and $y$th column of a matrix $R$.
-An intensity transformation on an image $R$ can be defined as a function $T$ which maps a pixel value $r$ to a new value $r^\prime$, which we can write as $r^\prime = T\left(r\right)$.
-This function is then applied to every pixel in $R$.
-The \textit{CryptoImg} library implemented two types of linear intensity transformations: image negation and brightness control.
-
-An image negation transformation is defined as:
-\begin{equation}
-    T\left(r\right) = L-1-r
-\end{equation}
-After applying image negation, the resulting image would be similar to a photographic negative~\cite{gonzalez_digital_2008}.
-
-A brightness control transformation with parameter $v$ is defined as:
-\begin{equation}
-    T\left(r,v\right) = r+v
-\end{equation}
-The above transformations are linear in terms of the input $r$, and are thus simple to implement under a homomorphic cryptosystem.
-
-In this study we extend the range of intensity transformations to non-linear transformations.
-Two common non-linear image transformations are the logarithm transformation and power-law transformation~\cite{gonzalez_digital_2008}.
-
-The logarithm transformation is used to enhance dark pixels or increase the dark details of an image by mapping low intensity values to a wider range of values~\cite{gonzalez_digital_2008}.
-This has the general formula
-\begin{equation}
-    T\left(r\right) = c \log\left(1 + r\right)
-\end{equation}
-where $c$ is a constant.
-
-The power-law transformation is a family of transformations that have the form
-\begin{equation}
-    T\left(r\right) = c r^{\gamma}
-\end{equation}
-where $c>0$ and $\gamma > 0$.
-A power-law transformation defined by the above equation can calibrate the operation of many image capture and output devices such as cameras, printers and displays in a process called \textit{gamma correction}.
-% This ensures reproducibility and accuracy of images being displayed by digital output devices~\cite{gonzalez_digital_2008}.
-
-To implement non-linear intensity transformations using addition and multiplication in a homomorphic system, it is necessary to approximate the logarithm and exponential functions, which may result in higher computational overhead.
-In our software library implementation, we investigate methods required to approximate the logarithm and power functions.
-Non-linear intensity transformations such as the logarithm transformation have applications in intensity normalization \cite{oravec_illumination_2010}, which is used in some facial recognition algorithms to account for differences in lighting which make facial recognition difficult.
-
-\subsection{Facial Detection and Recognition}
-
-Since simple image operations mentioned earlier can be done within a homomorphic cryptosystem, these operations can be assembled together in order to do more complex operations.
-A prominent application of image processing that often uses complex image operations is \textit{facial recognition}.
-
-Traditional facial recognition algorithms rely on detecting salient features in a face image. One of the popular facial recognition algorithms is \textit{eigenfaces}.
-% Traditional facial recognition algorithms rely on detecting salient features in a face image. Two of the popular facial recognition algorithms are \textit{eigenfaces} and \textit{Haar cascades}.
-
-\subsubsection{Eigenfaces}
-Proposed by Matthew Turk and Alex Pentland, the eigenfaces method uses principal component analysis (PCA) in order to express an input image as a linear combination of eigenfaces \cite{turk_eigenfaces_1991}.
-An \textit{eigenface} is a principal component, or more simply an eigenvector that represents a certain variation between the face images which are taken from the initial training set.
-The number of resulting eigenfaces is equal to the number of face images in the training set.
-
-% In the enrollment process, $M$ face images $\Theta_1, \ldots, \Theta_M$, each of size $p \times q$, are taken in to comprise the initial training set.
-The training images can be represented as vectors of length $N = pq$, where each row of an image is concatenated together.
-
-% The average of the training images, denoted as $\Psi$, is 
-% \begin{equation}
-% 	\Psi = \frac{1}{M} \sum_{i=1}^{M} \Theta_i
-% \end{equation}
-
-% The \textit{difference vectors} are then computed as $\Phi_i = \Theta_i - \Psi$. PCA is applied on the covariance matrix of the vectors
-% \begin{equation}
-% 	\mathbf{C} = \frac{1}{M} \sum_{i=1}^M \Phi_i \Phi_i^\top = \frac{1}{M} \mathbf{A}\mathbf{A}^\top,
-% \end{equation}
-% where $\mathbf{A}$ is an $N \times M$ matrix defined by $\left[\Theta_1 \quad \Theta_2 \quad \cdots \quad \Theta_M\right]$, in order to determine the orthonormal eigenvectors \cite{hutchison_privacy-preserving_2009}.
-
-% Directly computing the covariance matrix and then applying PCA will become inefficient for large sizes of $\mathbf{A}$, since computing for $\mathbf{A}\mathbf{A}^\top$ results in an $N \times N$ matrix, which can get drastically large because it is dependent on the size of the image.
-On the other hand, computing for $\mathbf{A}^\top\mathbf{A}$ only results in an $M \times M$ matrix, which is much smaller than the previous one because it is just dependent on the number of face images in the training set.
-Now, we can apply PCA to $\mathbf{A}^\top\mathbf{A}$ along with some post-processing to obtain the eigenvectors \cite{hutchison_privacy-preserving_2009}.
-
-% Instead of getting the eigendecomposition of the covariance matrix by explicitly computing the eigenvalues and eigenvectors of $\mathbf{C}$, we can also apply \textit{singular value decomposition} (SVD) on the matrix $\Phi^\top$.
-This is because SVD works through a divide-and-conquer method which results in greater numerical stability, while eigendecomposition simply uses the traditional QR factorization \cite{nakatsukasa_stable_2013, gu_divide-and-conquer_1995}.
-Upon applying SVD, we now get the eigenvectors $\mathbf{u}_1, \ldots, \mathbf{u}_M$ and their corresponding eigenvalues $\lambda_1, \ldots, \lambda_M$.
-
-% We choose $K$ eigenvectors $\mathbf{u}_1, \ldots, \mathbf{u}_K$ such that it comprises a set associated with the $K$ largest eigenvalues, where $K$ is much smaller than $M$.
-This set is now the \textit{face space}.
-Then, the images $\Theta_1, \ldots, \Theta_K$ are projected onto the face space spanned by the eigenfaces to determine the weight vectors $\Omega_1, \ldots, \Omega_K$.
-
-% To perform the recognition process, the algorithm projects the input image $\Gamma$ onto the face space, and then comparing the projected image $\bar{\Omega} = \mathbf{u}_i\left(\Gamma - \Psi\right)$ with each eigenface in the face space using a metric such as the Euclidean distance.
-Thus it is computed as $d_i = \left\lVert \Omega_i -\bar{\Omega} \right\rVert$ for all $i=1,\ldots,K$, where $\left\lVert \cdot \right\rVert$ denotes the Euclidean norm.
-
-% Then, a match can be reported if the smallest possible distance is smaller than the given threshold value $T$. 
-% \newcommand{\argmin}{\mathop{\mathrm{arg\,min}}}  
-% \begin{equation}
-% 	\text{ID} = \begin{cases}\argmin_i d_i & \text{if } \min_i d_i \le T \\\emptyset & \text {otherwise}\end{cases}
-% \end{equation}
-
-\subsection{Previous Implementations of Secure Facial Recognition}
-Erkin, et al.
-\cite{hutchison_privacy-preserving_2009} devised a method to incorporate the use of homomorphic cryptosystems into the eigenfaces method.
-In their study, they proposed a two-party system where Alice holds an encrypted image $\left[\Gamma\right]$, while Bob maintains a database of $K$ eigenfaces $\mathbf{u}_1, \ldots, \mathbf{u}_K$, and feature vectors $\Omega_1, \ldots, \Omega_M$ in the clear.
-
-\begin{figure}[!h]
-    \centering
-    \includegraphics[width=0.4\textwidth]{figures/secure_eigenfaces.png}
-    \caption{Diagram of the privacy-preserving facial recognition process \cite{hutchison_privacy-preserving_2009}}
-\end{figure}
-
-In order to ensure privacy, the steps in the eigenfaces algorithm, namely: projection, distance computation, and match finding, are done within the encrypted domain, i.e., using the operations in the Paillier cryptosystem.
-
-Projection is similar to that of the original eigenfaces algorithm, except the operations are replaced with their respective operations in the cryptosystem.
-Distance computation in this version is somewhat different from the original eigenfaces method, in that it deals with the square of the Euclidean distance since the relative order of the distances is only important when comparing these during the match finding step \cite{hutchison_privacy-preserving_2009}.
-\begin{align}
-    d_i &= \left\lVert \Omega_i - \bar{\Omega} \right\rVert ^2 = \sum_{j=1}^{K} \left(\omega_{ij} - \bar{\omega}_j\right)^2 \\
-        &= \underbrace{\sum_{j=1}^{K} \omega_{ij}^2}_{\mathcal{S}_1} + \underbrace{\sum_{j=1}^{K} \left(-2 \omega_{ij} \bar{\omega_j}\right)}_{\mathcal{S}_2} + \underbrace{\sum_{j=1}^{K} \bar{\omega}_{j}^2}_{\mathcal{S}_3}
-\end{align}
-
-Computing for the distances within Paillier would just be multiplying the encrypted sums together.
-\begin{equation}
-	\left[d_i\right] = \left[\mathcal{S}_1\right] \cdot \left[\mathcal{S}_2\right] \cdot \left[\mathcal{S}_3\right]
-\end{equation}
-
-The terms $\left[\mathcal{S}_1\right]$ and $\left[\mathcal{S}_2\right]$ can be easily computed by Bob, since he already knows both $\omega_i$ in the clear and $\left[\bar{\omega}_i\right]$ which is in encrypted form.
-Computing for $\left[\mathcal{S}_3\right]$ is trickier because Bob cannot compute for $\left[\bar{\omega}_i^2\right]$ because pairwise multiplication is not supported in Paillier, that is why Bob needs help from Alice to square a number through a protocol described below \cite{hutchison_privacy-preserving_2009}.
-
-Before Bob sends $\left[\bar{\omega}_i\right]$ to Alice for squaring, he adds a random number $r_i$ to compute $\left[x_i\right] = \left[\bar{\omega}_i + r_i\right] = \left[\bar{\omega}_i\right] \cdot \left[r_i\right]$, where $r_i$ is obviously distinct for every $i$, then sends $\left[x_i\right]$ to Alice.
-She then decrypts it and computes $x_i^2$, and then computes $\mathcal{S}_3^\prime = \sum_{i=1}^{K} x_i^2$, after which she encrypts the sum and sends $\left[\mathcal{S}_3^\prime\right]$ to Bob.
-Now, he can compute for $\left[\mathcal{S}_3\right]$ as follows:
-\begin{equation}
-	\left[\mathcal{S}_3\right] = \left[\mathcal{S}_3^\prime\right] \cdot \prod_{j=1}^{K} \left(\left[\bar{\omega}_j\right]^{-2r_j} \cdot \left[-r_j^2\right]\right)
-\end{equation}
-
-The protocol for squaring a number as described earlier is a workaround for the limitations of Paillier or any other partially homomorphic cryptosystem that only supports addition and scalar multiplication.
-% This can be possibly extended so that operations such as pairwise multiplication and exponentiation are also supported, provided that the protocol involves two parties.
-
-The match finding step is done by comparing the distances obtained from the previous step to a specified threshold $T$.
-If the minimum distance is smaller than $T$, then a match is found, and the encrypted identity of the match is returned to Alice \cite{hutchison_privacy-preserving_2009}.
-Getting the minimum among the encrypted distances would involve comparing two encrypted numbers, which Paillier does not support.
-Instead, the DGK cryptosystem \cite{pieprzyk_efficient_2007} is used for the comparison protocol.
-
-\section{Methodology}
-In this study we apply three homomorphic encryption schemes~\cite{ziad_cryptoimg:_2016, pieprzyk_efficient_2007, garay_algorithms_2014} for use in image processing and facial recognition applications.
-In particular, the study consists of the following:
-\begin{itemize}
-	\item Creating a wrapper library that acts as a unified interface which implements the Paillier, DGK, and BGV homomorphic cryptosystems.
-	\item An implementation of image processing operations (intensity transformations, facial recognition) under the above cryptosystems.
-	\item Conducting tests for image quality, processing time, using images from the \texttt{faces94} dataset.
-\end{itemize}
-
-% While the Paillier and DGK cryptosystems have been implemented for use in image processing in~\cite{ziad_cryptoimg:_2016, hutchison_privacy-preserving_2009}, the other cryptosystems have to be adapted for this study.
-% Two experiments are conducted in this study:
-% \begin{enumerate}
-% 	\item Assessment of non-linear image intensity transformations under each of the three cryptosystems.
-% 	\item Assessment of efficiency of each of the four cryptosystems when applied for use in privacy-preserving facial recognition and detection using eigenfaces.
-% \end{enumerate}
-% The results of the image intensity transformations are tested for image quality using benchmarks in~\cite{ahmed_benchmark_2016}.
-
-\subsection{Cryptosystem Implementation}
-Three homomorphic encryption schemes are investigated, and a wrapper library was created in Python that integrates these cryptosystems into a unified interface.
-\begin{itemize}
-	\item The Paillier cryptosystem is incorporated using the python-paillier library at \url{https://github.com/n1analytics/python-paillier} developed by Data61 - CSIRO.
-	\item The DGK cryptosystem is ported from the C++ implementation at \url{https://github.com/encryptogroup/ENCRYPTO_utils}, developed by Daniel Demmler from EC-SPRIDE.
-	\item The BGV cryptosystem is implemented using the Pyfhel library (\url{https://github.com/ibarrond/Pyfhel}) using a HElib backend from (\url{https://github.com/shaih/HElib}).
-\end{itemize}
-
-\subsubsection{Extension of Partially Homomorphic Cryptosystems}
-\label{sssec:pheextension}
-In order to use Paillier and DGK for secure image processing, we require the two schemes to support the encryption of floating-point (FP)numbers, as well as multiplication and division of arbitrary ciphertexts.
-We extend the two cryptosystems to FP operations by using an approach shown in~\cite{ziad_cryptoimg:_2016}.
-This approach represents FP numbers using a pair $(m,e)$, where $m$ represents the mantissa (which is encrypted), and $e$ represents the exponent (which is not encrypted).
-This approach is also used by the python-paillier library.
-This represntation allows us to extend the addition and plaintext multiplication homomorphisms of the Paillier and DGK cryptosystems to floating-point numbers.
-
-Various two-party protocols can be used to facilitate ciphertext multiplication and division.
-These allow a server armed with only knowledge of the public key, to obtain the product and quotient of ciphertexts, by communicating with the client, who has the private key.
-For division, we use the protocol defined in~\cite{boukoros_lightweight_2017}: to obtain $E(x/y)$ from $E(x)$ and $E(y)$, the server sends $E(rx)$ and $E(ry)$ to the client, (where $r$ is a random non-zero number), allowing the client to compute $E(rx/ry)$ and give the result back to the server.
-
-For multiplication, we adapt the protocol to calculate Euclidean distances used in \cite{hutchison_privacy-preserving_2009}, which provides a two-party protocol which yields $E(x^2)$ given $E(x)$.
-We use this protocol together with the additive homomorphism of the partially homomorphic cryptosystems to instead compute $E((x + y)^2 - x^2 - y^2) = E(2xy)$, from which we can easily obtain $E(xy)$ through plaintext multiplication.
-
-% [TO-DO: This is further explained in another paper.]
-% We will briefly discuss a protocol to enable cryptosystems built for integer inputs to handle real number inputs.
-% The following protocol was also used by \textit{CryptoImg} for image processing \cite{ziad_cryptoimg:_2016}.
-% This is also used for our own implementation of the Dasgupta--Pal cryptosystem in order to handle real numbers.
-
-% We represent a floating-point (FP) number as a pair of two integers $(m,e)$ representing the mantissa and exponent of the FP number with respect to a base $b$.
-The mantissa $m$ is encrypted, while the exponent $e$ is unencrypted.
-% Let $a,b,c$ be FP numbers represented by the pairs $(m_a,e_a),(m_b,e_b),(m_c,e_c)$ respectively.
-Let $\oplus,\otimes$ represent the homomorphic operations which correspond to the addition and multiplication, respectively.
-We define the secure real number operations as follows:
-% \begin{description}
-%   \item[Addition.]
-%     To compute $E(c)=E(a+b)$ we compute
-%     \begin{align*}
-%       E(m_c) &= E(m_1) \oplus (b^{e_b-e_a} \otimes E(m_b)), e_c = e_a & \text{ if } e_a \leq e_b \\
-%       E(m_c) &= E(m_b) \oplus (b^{e_a-e_b} \otimes E(m_a)), e_c = e_b & \text{ if } e_a > e_b
-%     \end{align*}
-%   \item[Scalar multiplication.]
-%     To compute $E(c) = E(ab)$, where $a$ and $E(b)$ are known (i.e. $m_a$ is not encrypted), we compute
-%     \begin{align*}
-%       E(m_c) &= m_a \otimes E(m_b)\\
-%       e_c &= e_a + e_b
-%     \end{align*}
-% \end{description}
-
-\subsection{Non-Linear Intensity Transformations}
-We will implement library functions for image negation, logarithm transformation and power-law transformation, as they are defined in~\cite{gonzalez_digital_2008}.
-We now describe how we implement the logarithm and power-law image intensity transformations.
-In the case of partially homomorphic cryptosystems (Paillier, DGK), if ciphertext multiplication or division is required, the secure protocols in section \ref{sssec:pheextension} will be used.
-
-\subsubsection{Logarithm Transformation}
-The logarithm transformation of a pixel intensity value $x$ is defined as
-\begin{align}
-	T\left(x\right) = c \log\left(1 + x\right)
-\end{align}
-where $c$ is a constant.
-
-In order to perform this transformation under Paillier and DGK, we provide the following closed-form approximation for $\log\left(1 + x\right)$.
-% TODO: IDK HOW TO CITE OUR PCSC PAPER
-\begin{align}\label{eq:optimal_log_approximation}
-	\begin{split}
-		&\log\left(1+x\right) \approx \frac{a(x)}{b(x)} + \log{16}
-	\end{split}
-\end{align}
-where
-\begin{align*}
-	\begin{split}
-	a(x) &= 137x^5 + 26685x^4 + 617370x^3 - 6498630x^2 \\
-	&- 121239315x - 257804775\\
-	b(x) &= 30(x^5 + 405x^4 + 27210x^3 + 488810x^2 + 2536005x \\
-	&+ 3122577).
-	\end{split}
-\end{align*}
-% \begin{align}\label{eq:optimal_log_approximation}
-% 	\begin{split}
-% 		&\log\left(1+x\right) \\
-% 		&\approx \frac{137x^5 + 26685x^4 + 617370x^3 - 6498630x^2 - 121239315x - 257804775}
-% 		{30(x^5 + 405x^4 + 27210x^3 + 488810x^2 + 2536005x + 3122577)}\\
-% 		&+ \log{16}.
-% 	\end{split}
-% \end{align}
-
-\subsubsection{Power-Law Transformation}
-The power-law transformation of a pixel intensity value $x$ is defined as
-\begin{equation}
-    T\left(x\right) = cx^{\gamma}
-\end{equation}
-where $c>0$ and $\gamma > 0$.
-
-Similar to the logarithm transformation, to apply this transformation using Paillier and DGK, we must provide an approximation for $x^\gamma$.
-We can use partial sums of the following series, which relies on the logarithm function.
-\begin{align}
-	x^\gamma &= \sum_{n=0}^{\infty}{\frac{(\gamma\log{x})^n}{n!}}
-\end{align}
-% Partial sums of the above infinite series can be calculated based on the closed form approximation for the logarithm in Equation \ref{eq:scaledquadraturech3}. 
-For the implementation of the power-law transformation for this paper, a partial sum consisting of the first five terms of the infinite series were used.
-
-\subsection{Assessment of Homomorphic Encryption Schemes}
-A laptop computer with a 2.5 GHz Intel Core i7 quad-core processor and 8 GB of RAM is used to perform the computations, and processing time was tracked using built-in timing functions.
-The processing time for all cases were recorded.
-All of the tests are done using Python 3.7.1 running on Linux.
-
-\subsubsection{Image Quality of Intensity Transformations}
-In this section, we discuss the image quality metrics we used for assessing the performance of non-linear intensity transformations.
-
-We first obtained test images from the \texttt{faces94} dataset (\url{https://cswww.essex.ac.uk/mv/allfaces/faces94.html}) maintained by the University of Essex.
-However, only ten distinct facial images from the dataset were selected for the purposes of this test.
-Since only grayscale images are used in the study, the images were converted to grayscale and then downsampled to $40 \times 36$ pixels.
-
-For each cryptosystem, three image operations are tested:
-\begin{enumerate}
-	\item Image negation
-	\item Logarithm transformation, with $c = 30$
-	\item Power-law transformation, with $c = 1$ and $\gamma = 0.4$
-\end{enumerate}
-
-For each plaintext image (PT), we considered each image operation listed above and generate three images: a plaintext domain transformation (PDT), a ciphertext image (CT), and an ciphertext domain transformation (CDT).
-The PDT was generated by running the image operation on the original image.
-The CT was generated by encrypting the image, then applying the operation, and the CDT was generated by decrypting the CT.
-The four images (PT, PDT, CT, CDT) were then compared using various benchmarks to evaluate the quality and security of each homomorphic encryption scheme.
-
-The benchmarks to be used in the study, adopted from~\cite{ahmed_benchmark_2016, ahmad_efficiency_2012, wu_npcr_2011} are listed below.
-We let $X_i$ denote a value in an image $X$, where $1 \leq i \leq N$.
-We first perform three tests to ascertain the preservation of image quality after encryption and decryption: MSE, PSNR, and SSIM.
-\begin{description}
-	\item [Mean Squared Error (MSE).] The MSE is defined in~\cite{ahmed_benchmark_2016} as
-	\begin{align}
-        \mathrm{MSE} = \frac{1}{N}\sum_{i=1}^{N}{(\mathrm{CDT}_i - \mathrm{PDT}_i)^2}.
-	\end{align}
-	The MSE provides a measure of how much data is recovered if an image operation is applied on the encrypted image, which is then decrypted.
-Lower values of MSE indicate higher preservation of image quality~\cite{ahmed_benchmark_2016, ahmad_efficiency_2012}.
-	\item [Peak Signal to Noise Ratio (PSNR).]
-	According to Ahmed, et al.~\cite{ahmed_benchmark_2016}, PSNR is ``an estimator for human visual perception of reconstruction quality.'' It has been used to ascertain image quality in various studies and is a known metric for image and video quality~\cite{upmanyu_efficient_2009, jain_image_2016, akramullah_video_2014}.
-Although it may produce results which do not correlate with human visual perception~\cite{huynh-thu_accuracy_2012, ahmed_benchmark_2016}, it is a valid indicator of image quality when media containing the same visual content is compared~\cite{huynh-thu_accuracy_2012}.
-	PSNR is defined by
-	\begin{align}
-        \mathrm{PSNR} = 10\log_{10}{\left( \frac{L^2}{\mathrm{MSE}} \right)}
-	\end{align}
-	where $L$ is the maximum pixel intensity value of an image.
-	Despite the known limitations of PSNR, since we are going to compare the effect of each encryption scheme on recovered image quality, given a fixed library of images, it is a valid measure of image quality for the study.
-A higher PSNR indicates higher image quality preservation.
-	\item [Structural Similarity Index (SSIM).]
-	The SSIM for two random variables $X$ and $Y$ is defined in~\cite{ahmed_benchmark_2016, akramullah_video_2014} as
-	\begin{align}
-        \mathrm{SSIM}(X,Y) = \frac{(2\mu_X\mu_Y+c_1)(2\sigma_{XY}+c_2)}{(\mu_X^2+\mu_Y^2+c_1)(\mu_X^2+\mu_Y^2+c_2)}
-	\end{align}
-	where
-	\begin{itemize}
-		\item $\mu_X, \mu_Y$ are the averages of $X$ and $Y$, respectively;
-		\item $\sigma_X, \sigma_Y$ are the variances of $X$ and $Y$, respectively;
-		\item $\sigma_{XY}$ is the covariance of $X$ and $Y$;
-		\item $c_1 = (k_1L)^2, c_2 = (k_2L)^2$ are two variables used to stabilize the measure when $\mu_X^2+\mu_Y^2$ is close to zero~\cite{akramullah_video_2014};
-		\item $L$ is the the maximum pixel intensity value of an image;
-		\item $k_1 = 0.01, k_2 = 0.03$ by default, given in~\cite{ahmed_benchmark_2016}.
-	\end{itemize}
-	The SSIM is applied to the luminance value of two images to gauge structural similarity between neighboring pixels.
-	For the study, we computed $\mathrm{SSIM}(\mathrm{PDT}, \mathrm{CDT})$ for every image operation, under each homomorphic cryptosystem.
-Higher values of SSIM indicate higher structural similarity, and an SSIM of $1$ indicates that the two images are identical~\cite{ahmed_benchmark_2016}.
-\end{description}
-
-Computing for MSE, PSNR, and SSIM was done using the corresponding built-in functions from the scikit-image Python library \cite{scikit-image}.
-
-\subsubsection{Facial Recognition Tests}
-The method for secure facial recognition using eigenfaces by Erkin, et al. \cite{hutchison_privacy-preserving_2009} was implemented for this study.
-
-As before, training and test data were also secured from the \texttt{faces94} dataset. The images were first converted to grayscale but it is not downsampled, unlike in the previous test.
-
-The facial recognition tests are done using ten-fold cross-validation for each cryptosystem, where the number of principal components used by the algorithm is fixed at $K=5$.
-
-Prior to splitting the dataset, the images within each set are shuffled.
-Since there are twenty (20) images per set, two images are taken at a time for each round of cross-validation.
-The first round would take the first two images from each set as part of the test set, and the rest of the images will be part of the training set.
-Then, the succeeding round would take the next two images from each set as part of the test set, and so on until ten rounds have been done.
-After every round of cross-validation, the accuracy score, confusion matrix, and total processing time are obtained.
-
-%% Summary not needed, this was only important for the thesis proposal - Aldrich
-% \subsection{Summary}
-% In summary, the study consists of:
-% \begin{itemize}
-% 	\item Creating a wrapper library that acts as a unified interface which implements the Paillier, DGK, Dasgupta--Pal, and BGV homomorphic cryptosystems.
-% 	\item An implementation of image processing operations (intensity transformations, facial recognition) under the above cryptosystems.
-% 	\item Conducting tests for image quality, processing time, using images from the \texttt{faces94} dataset.
-% \end{itemize}
-
-\section{Preliminary Results and Discussion}
-The results shown in this section are gathered from the tests for intensity transformations under Paillier and Dasgupta--Pal cryptosystems.
-During testing, initial results obtained from BGV, particularly with image operations involving floating-point numbers like the logarithmic transformation, were unstable (i.e.
-the results vary drastically every time the same tests were done).
-This is because the Pyfhel library being used for the BGV cryptosystem is still in alpha development stage \cite{pyfhel_2018}.
-
-% One of the authors has already informed the maintainers of the library about a bug involving exponentiation of two real numbers.
-
-\subsection{Intensity Transformations}
-
-\begin{table*}
-	\centering
-	\caption{Comparison of intensity transformations under Paillier}
-	\label{tbl:it-pal}
-	\begin{tabular}{m{1cm}*{7}{>{\centering\arraybackslash}m{1.75cm}}}
-		\toprule
-		\multirow{2}{*}{Image} & \multirow{2}{*}{Original} & \multicolumn{2}{c}{Image negation} & \multicolumn{2}{c}{Logarithm transformation} & \multicolumn{2}{c}{Power-law transformation} \\
-							   &                           & PDT           & CDT          & PDT            & CDT           & PDT               & CDT           \\ 
-		\midrule
-		\xintForpair #1#2 in {(anpage,a), (bplyce,b), (drbost,c), (ksunth,d), (martin,e), (pmives,f), (rnpwil,g), (sbains,h), (swewin,i), (yfhsie,j)} \do {%
-		(#2) & \includegraphics[width=1.75cm]{out_faces/paillier_negate_#1_original.png} & \includegraphics[width=1.75cm]{out_faces/paillier_negate_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/paillier_negate_#1_decrypted.png} & \includegraphics[width=1.75cm]{out_faces/paillier_logtransform_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/paillier_logtransform_#1_decrypted.png} & \includegraphics[width=1.75cm]{out_faces/paillier_pwrtransform_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/paillier_pwrtransform_#1_decrypted.png} \\ }%
-		\bottomrule         
-	\end{tabular}
-\end{table*}
-
-\begin{table*}
-	\centering
-	\caption{Comparison of intensity transformations under Dasgupta--Pal}
-	\label{tbl:it-dp}
-	\begin{tabular}{m{1cm}*{7}{>{\centering\arraybackslash}m{1.75cm}}}
-		\toprule
-		\multirow{2}{*}{Image} & \multirow{2}{*}{Original} & \multicolumn{2}{c}{Image negation} & \multicolumn{2}{c}{Logarithm transformation} & \multicolumn{2}{c}{Power-law transformation} \\
-							   &                           & PDT           & CDT          & PDT            & CDT           & PDT               & CDT           \\ 
-		\midrule
-		\xintForpair #1#2 in {(anpage,a), (bplyce,b), (drbost,c), (ksunth,d), (martin,e), (pmives,f), (rnpwil,g), (sbains,h), (swewin,i), (yfhsie,j)} \do {%
-		(#2) & \includegraphics[width=1.75cm]{out_faces/dp_negate_#1_original.png} & \includegraphics[width=1.75cm]{out_faces/dp_negate_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/dp_negate_#1_decrypted.png} & \includegraphics[width=1.75cm]{out_faces/dp_logtransform_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/dp_logtransform_#1_decrypted.png} & \includegraphics[width=1.75cm]{out_faces/paillier_pwrtransform_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/dp_pwrtransform_#1_decrypted.png} \\ }%
-		\bottomrule
-	\end{tabular}
-\end{table*}
-
-Table~\ref{tbl:it-pal} shows the images obtained from the intensity transformation tests under the Paillier cryptosystem, while Table~\ref{tbl:it-dp} shows the resulting images from the same tests under the Dasgupta--Pal cryptosystem.
-Shown for each image is the original unecrypted image, and for each intensity transformation the \textit{plaintext domain transformation} (PDT) is given which is the resulting image after applying the transformation to the unencrypted image and the \textit{ciphertext domain transformation} (CDT) is the decrypted image of the processed encrypted image.
-
-The following tables show the resulting metric scores for mean squared error (MSE), peak signal to noise ratio (PSNR), and structural similarity index (SSIM), as well as time taken (in seconds) for encrypting the input image ($t_\text{enc}$), applying an operation to the encrypted image ($t_\text{apply}$), and decrypting the resulting encrypted image ($t_\text{dec}$), for each image in the test set.
-Tables~\ref{tbl:neg-pal} and~\ref{tbl:neg-dp} show the results obtained from applying image negation, Tables~\ref{tbl:log-pal} and~\ref{tbl:log-dp} from applying logarithm transformation, and Tables~\ref{tbl:pwr-pal} and~\ref{tbl:pwr-dp} from applying power-law transformation.
-
-\subsubsection{Image Negation}
-Both the Paillier and Dasgupta--Pal cryptosystems were able to perform image negation under the encrypted domain without introducing noise in the resulting image.
-In other words, the resulting image from doing image negation on an image on the clear and doing image negation under the encrypted domain are identical, as evidenced by the mean squared errors being exactly equal to zero, the PSNR being infinite, and the SSIM being exactly equal to one.
-
-The Paillier cryptosystem performed better in terms of time, only taking about 0.01 seconds to apply image negation.
-On the other hand, the Dasgupta--Pal cryptosystem took about 22 seconds each to apply the same operation, which is expected since the implementation for Dasgupta--Pal was done in Python without using any external libraries.
-
-\begin{table}[h]
-	\centering
-	\caption{Image negation under Paillier}
-	\label{tbl:neg-pal}
-    \begin{tabular}{lcccccc}
-        \toprule
-        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
-        (a) & 0.000 & $\infty$ & 1.00000 & 0.128 & 0.013 & 0.041 \\
-		(b) & 0.000 & $\infty$ & 1.00000 & 0.084 & 0.013 & 0.024 \\
-		(c) & 0.000 & $\infty$ & 1.00000 & 0.099 & 0.012 & 0.031 \\
-		(d) & 0.000 & $\infty$ & 1.00000 & 0.109 & 0.012 & 0.048 \\
-		(e) & 0.000 & $\infty$ & 1.00000 & 0.117 & 0.015 & 0.043 \\
-		(f) & 0.000 & $\infty$ & 1.00000 & 0.111 & 0.012 & 0.025 \\
-		(g) & 0.000 & $\infty$ & 1.00000 & 0.099 & 0.012 & 0.023 \\
-		(h) & 0.000 & $\infty$ & 1.00000 & 0.084 & 0.012 & 0.024 \\
-		(i) & 0.000 & $\infty$ & 1.00000 & 0.089 & 0.012 & 0.023 \\
-		(j) & 0.000 & $\infty$ & 1.00000 & 0.081 & 0.012 & 0.029 \\
-		\bottomrule
-    \end{tabular}
-\end{table}
-\begin{table}[h]
-	\centering
-	\caption{Image negation under Dasgupta--Pal}
-	\label{tbl:neg-dp}
-    \begin{tabular}{lcccccc}
-        \toprule
-        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
-		(a) & 0.000 & $\infty$ & 1.00000 & 0.221 & 30.217 & 0.239 \\
-		(b) & 0.000 & $\infty$ & 1.00000 & 0.190 & 30.919 & 0.216 \\
-		(c) & 0.000 & $\infty$ & 1.00000 & 0.284 & 31.182 & 0.268 \\
-		(d) & 0.000 & $\infty$ & 1.00000 & 0.225 & 32.581 & 0.223 \\
-		(e) & 0.000 & $\infty$ & 1.00000 & 0.220 & 32.220 & 0.271 \\
-		(f) & 0.000 & $\infty$ & 1.00000 & 0.287 & 31.224 & 0.294 \\
-		(g) & 0.000 & $\infty$ & 1.00000 & 0.285 & 29.478 & 0.284 \\
-		(h) & 0.000 & $\infty$ & 1.00000 & 0.186 & 29.784 & 0.362 \\
-		(i) & 0.000 & $\infty$ & 1.00000 & 0.243 & 38.407 & 0.220 \\
-		(j) & 0.000 & $\infty$ & 1.00000 & 0.285 & 29.488 & 0.449 \\		
-		\bottomrule
-        \end{tabular}
-\end{table}
-
-\subsubsection{Logarithm Transformation}
-Unlike image negation, logarithm transformation involves more operations, so the increase in processing time for both cryptosystems are expected.
-Applying the logarithm transformation under Paillier took about 2 seconds per image, while it took about 13.5 minutes each under Dasgupta--Pal.
-
-The logarithm transformation under Dasgupta--Pal turned out to be more accurate than Paillier, whose mean squared errors approach zero and the SSIM values approach one for every image as shown in Table~\ref{tbl:log-dp}.
-Although the results from using Paillier show that it is also accurate enough with the mean squared errors being less than 30 and the SSIM values average to 0.99, Dasgupta--Pal has been able to produce an almost identical result to that of the plaintext domain transformation counterparts.
-This observation is rather unexpected, considering that the implementation used for Paillier is more robust (due to its use of external C/C++ libraries which makes computations faster).
-
-\begin{table}[h]
-	\centering
-	\caption{Logarithm transformation under Paillier}
-	\label{tbl:log-pal}
-    \begin{tabular}{lcccccc}
-        \toprule
-        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
-		(a) & 13.369 & 36.870 & 0.99263 & 0.085 & 1.813 & 0.023 \\
-		(b) & 7.072 & 39.635 & 0.99017 & 0.089 & 2.073 & 0.023 \\
-		(c) & 8.151 & 39.019 & 0.98688 & 0.091 & 1.913 & 0.023 \\
-		(d) & 25.253 & 34.108 & 0.98927 & 0.089 & 1.919 & 0.023 \\
-		(e) & 10.374 & 37.971 & 0.98695 & 0.106 & 1.829 & 0.023 \\
-		(f) & 2.426 & 44.283 & 0.99401 & 0.127 & 1.900 & 0.023 \\
-		(g) & 5.184 & 40.985 & 0.98971 & 0.096 & 1.853 & 0.023 \\
-		(h) & 16.772 & 35.885 & 0.98492 & 0.081 & 1.746 & 0.024 \\
-		(i) & 5.803 & 40.494 & 0.99241 & 0.091 & 1.827 & 0.027 \\
-		(j) & 12.192 & 37.270 & 0.99354 & 0.081 & 1.815 & 0.023 \\
-		\bottomrule
-        \end{tabular}
-\end{table}
-\begin{table}[h]
-	\caption{Logarithm transformation under Dasgupta--Pal}
-	\label{tbl:log-dp}
-    \begin{tabular}{lcccccc}
-        \toprule
-        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
-		(a) & 0.004 & 71.624 & 0.99999 & 0.287 & 802.957 & 0.036 \\
-		(b) & 0.000 & 82.043 & 1.00000 & 0.190 & 815.384 & 0.048 \\
-		(c) & 0.004 & 72.480 & 1.00000 & 0.270 & 813.640 & 0.036 \\
-		(d) & 0.000 & 87.372 & 1.00000 & 0.204 & 804.629 & 0.047 \\
-		(e) & 0.001 & 77.421 & 1.00000 & 0.245 & 822.940 & 0.036 \\
-		(f) & 0.001 & 76.934 & 1.00000 & 0.194 & 814.132 & 0.036 \\
-		(g) & 0.000 & 83.135 & 1.00000 & 0.197 & 808.503 & 0.047 \\
-		(h) & 0.001 & 77.301 & 1.00000 & 0.270 & 809.406 & 0.047 \\
-		(i) & 0.006 & 70.004 & 0.99999 & 0.268 & 813.217 & 0.051 \\
-		(j) & 0.001 & 78.576 & 1.00000 & 0.243 & 830.640 & 0.039 \\
-		\bottomrule
-        \end{tabular}
-\end{table}
-
-\subsubsection{Power-Law Transformation}
-Applying the power-law transformation under both cryptosystems produced less than accurate images.
-The accuracy varies greatly across all the images as in the case of Paillier, with mean squared errors as high as 8270.696 and as low as 616.419, and SSIM scores ranging from 0.43185 to 0.92334, as seen in Table~\ref{tbl:pwr-pal}.
-As expected, the total processing time now takes about 15 to 20 seconds per image since the power-law transformation is more computationally intensive due to its approximation of an infinite series consisting of terms using the logarithm function, which is also approximated using a combination of addition and multiplication operations.
-
-\begin{table}[h]
-	\centering
-	\caption{Power-law transformation under Paillier}
-	\label{tbl:pwr-pal}
-    \begin{tabular}{lcccccc}
-        \toprule
-        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
-        (a) & 3910.678 & 12.208 & 0.46712 & 0.099 & 14.695 & 0.024 \\
-		(b) & 873.064 & 18.720 & 0.84379 & 0.139 & 16.190 & 0.023 \\
-		(c) & 1261.059 & 17.123 & 0.77229 & 0.082 & 13.866 & 0.023 \\
-		(d) & 653.049 & 19.981 & 0.90673 & 0.083 & 15.507 & 0.023 \\
-		(e) & 646.310 & 20.026 & 0.88157 & 0.108 & 15.727 & 0.045 \\
-		(f) & 2047.933 & 15.018 & 0.69408 & 0.113 & 14.728 & 0.034 \\
-		(g) & 806.473 & 19.065 & 0.85346 & 0.082 & 14.253 & 0.024 \\
-		(h) & 616.419 & 20.232 & 0.92334 & 0.121 & 14.415 & 0.023 \\
-		(i) & 8270.696 & 8.955 & 0.43185 & 0.112 & 14.362 & 0.065 \\
-		(j) & 1715.478 & 15.787 & 0.73857 & 0.145 & 20.239 & 0.023 \\
-		\bottomrule
-        \end{tabular}
-\end{table}
-
-When Dasgupta--Pal was used in the power-law transformation, it completely failed to produce a discernible image and only resulted in a blank image.
-The mean squared errors for this case is an order of magnitude higher than the results from using Paillier.
-Furthermore, doing a power-law transformation under Dasgupta--Pal is not only impractical in terms of accuracy, but also it is impractical in terms of time efficiency because it took about 2 hours and 40 minutes on average to process each image.
-
-\begin{table}[h]
-	\centering
-	\caption{Power-law transformation under Dasgupta--Pal}
-	\label{tbl:pwr-dp}
-    \begin{tabular}{lcccccc}
-        \toprule
-        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
-		% \texttt{anpage} & 25115.891 & 4.131 & 0.00000 & 0.016 & 741.872 & 0.031 \\ 10x10
-		% \texttt{bplyce} & 22777.187 & 4.556 & 0.00000 & 0.017 & 730.873 & 0.003 \\ 10x10
-		% \texttt{drbost} & 18899.906 & 5.366 & 0.00000 & 0.014 & 733.409 & 0.003 \\
-		(a) & 25008.723 & 4.150 & 0.000 & 0.376 & 9700.926 & 1.269 \\
-		(b) & 22700.522 & 4.570 & 0.000 & 0.230 & 9196.609 & 0.043 \\
-		(c) & 18902.214 & 5.366 & 0.000 & 0.277 & 9261.407 & 0.150 \\
-		(d) & 12585.729 & 7.132 & 0.000 & 0.257 & 9259.010 & 0.051 \\
-		(e) & 17012.423 & 5.823 & 0.000 & 0.279 & 9440.351 & 0.051 \\
-		(f) & 31124.615 & 3.200 & 0.000 & 0.285 & 9492.149 & 0.052 \\
-		(g) & 22982.917 & 4.517 & 0.000 & 0.289 & 9321.928 & 0.048 \\
-		(h) & 13469.155 & 6.837 & 0.000 & 0.257 & 9233.818 & 0.048 \\
-		(i) & 37453.834 & 2.396 & 0.000 & 0.262 & 9203.045 & 0.048 \\
-		(j) & 23037.762 & 4.506 & 0.000 & 0.258 & 9210.393 & 0.048 \\
-		% \texttt{drbost} & 18902.214 & 5.366 & 0.00000 & 0.064 & 2261.407 & 0.110 \\ % 20x18
-		% \texttt{ksunth} & 12585.729 & 7.132 & 0.00000 & 0.044 & 2259.010 & 0.011 \\ % 20x18
-		% \texttt{martin} & 17012.423 & 5.823 & 0.00000 & 0.066 & 2440.351 & 0.011 \\
-		% \texttt{pmives} & 31124.615 & 3.200 & 0.00000 & 0.072 & 2492.149 & 0.012 \\
-		% \texttt{rnpwil} & 22982.917 & 4.517 & 0.00000 & 0.076 & 2321.928 & 0.008 \\
-		% \texttt{sbains} & 13469.155 & 6.837 & 0.00000 & 0.044 & 2233.818 & 0.008 \\
-		% \texttt{swewin} & 37453.834 & 2.396 & 0.00000 & 0.049 & 2203.045 & 0.008 \\
-		% \texttt{yfhsie} & 23037.762 & 4.506 & 0.00000 & 0.045 & 2210.393 & 0.008 \\
-		\bottomrule
-        \end{tabular}
-\end{table}
-
 \section{Conclusion}
-In this paper, we have assessed the feasibility and practicality of various homomorphic cryptosystems with regard to secure processing and manipulation of facial image data through creation of a software library that facilitates image processing operations within the encrypted domain, as well as our own implementation of some homomorphic cryptosystems like Dasgupta--Pal for which existing third-party libraries dedicated for this purpose are not yet available.
+In this paper, we have assessed the feasibility and practicality of various homomorphic cryptosystems with regard to secure processing and manipulation of facial image data through creation of a software library that facilitates image processing operations within the encrypted domain, as well as our own implementation of some homomorphic cryptosystems like DGK.
 
@@
 
-Future work would involve improving and optimizing our implementation of the Dasgupta--Pal cryptosystem so that it performs faster.
-A suggestion would be to port the existing implementation to C/C++ and then create a Python library that acts as a wrapper to the C/C++ methods.
+Future work would involve improving and optimizing our implementation of non-linear intensity transformations in terms of number of operations, numerical accuracy and stability, and time efficiency.
+% Future work would involve improving and optimizing our implementation of the DGK cryptosystem so that it performs faster.
+% A suggestion would be to port the existing implementation to C/C++ and then create a Python library that acts as a wrapper to the C/C++ methods.
 For future studies, an implementation of a client-server framework or system dealing with secure image processing can be considered.

### 2019-03-17 icmssp-paper/parts/01_introduction.tex
[WIP] Shortening introduction

@@
 \section{Introduction}
-\subsection{Context of the Study}
-Digital data privacy and security is a growing concern in various fields, such as cloud computing~\cite{potey_homomorphic_2016}, health information systems~\cite{kester_cryptographic_2015}, and video surveillance~\cite{upmanyu_efficient_2009}.
-To meet these needs, various cryptosystems have been developed.
-% A cryptosystem is a system which operates on plaintexts, ciphertexts and keys using an encryption algorithm, which maps a plaintext to a ciphertext, together with a decryption algorithm, which maps a ciphertext to a plaintext, given an appropriate key~\cite{bauer_cryptosystem_2005}.
-The encryption and decryption algorithms are chosen such that the plaintext cannot easily be recovered from the ciphertext without knowledge of the key.
-This allows data to be securely transmitted over an insecure channel.
+% \subsection{Context of the Study}
+% Digital data privacy and security is a growing concern in various fields, such as cloud computing~\cite{potey_homomorphic_2016}, health information systems~\cite{kester_cryptographic_2015}, and video surveillance~\cite{upmanyu_efficient_2009}.
+Digital image encryption is a growing concern today, with many algorithms existing in the literature~\cite{murugan_survey_2018}.
 
-One particular application of cryptography is image encryption.
-While cryptosystems used to encrypt digital data in general, such as the Advanced Encryption Standard (AES) or elliptic curve cryptography, can also be used to encrypt images~\cite{jain_image_2016, singh_image_2015} other algorithms created specifically for image encryption have also been developed~\cite{murugan_survey_2018}.
-
-In a homomorphic cryptosystem, operations such as addition and multiplication can be performed on encrypted data.
+% TODO : Mention the four HE schemes here
+Of particular interest is homomorphic encryption, where operations such as addition and multiplication can be performed on encrypted data.
 These operations are then preserved when the data is decrypted.
@@
 
-% \subsection{Research Questions}
-% By implementing homomorphic cryptosystems and creating a library so they can be easily used, we aim to address our main research question: What is the best method for facial image data to be encrypted and manipulated for practical applications?
-
-% More specifically, our research will address the following sub-questions:
-% \begin{enumerate}
-% 	\item Which homomorphic cryptosystems admit more image processing operations? How can existing homomorphic cryptosystems be modified to admit more image processing operations?
-% 	\item Which homomorphic cryptosystems are the most time-efficient and the most accurate in applying image processing operations?
-% 	\item Which homomorphic cryptosystems best preserve image quality in applying image processing operations?
-% \end{enumerate}
-
-\subsection{Research Objectives}
-% Previous attempts in the literature to provide image processing tasks such as image manipulation \cite{ziad_cryptoimg:_2016} and  facial recognition \cite{hutchison_privacy-preserving_2009} have primarily used the Paillier and  Damg{\aa}rd--Geisler--Kr{\o}igaard (DGK) cryptosystems to perform linear operations on encrypted data.
-% In this study, we extend this research to provide an objective comparison of various homomorphic cryptosystems currently in the literature in performing non-linear operations, and facial detection, as opposed to just linear operations and facial recognition.
-
 Our main research objective is to assess the practicality of various homomorphic cryptosystems with regard to image processing on faces.
@@
 
-% In summary, in this study, we wish to
-More specifically, we wish to do the following:
+% TODO: be specific here, integrate objectives and scope
+% Focus objectives on new developments
+In this study, we accomplish the following:
 \begin{enumerate}
-    \item Implement common linear and non-linear image processing operations using known homomorphic encryption schemes, then determine which schemes admit more image processing operations and extend known cryptosystems to support more operations, if possible;
-    \item Compare the time efficiency and accuracy of common image processing operations under known homomorphic encryption schemes, and of common image processing operations without using homomorphic encryption;
+    \item Implement common linear and non-linear image processing operations using the Paillier, DGK, DGHV, and BGV homomorphic encryption schemes.
+    \item Compare the time efficiency and accuracy of common image processing operations under these homomorphic encryption schemes, and of common image processing operations without using homomorphic encryption;
     \item Create a library to allow for convenient use and comparison of these homomorphic encryption schemes for image processing and facial recognition.
-\end{enumerate}
-
-\subsection{Scope and Limitations}
-% Our study will be limited in terms of the cryptosystems to be tested, the image processing operations we will implement, and the statistical tests we will use to gauge the security of the cryptosystems.
-Below is a listing of the scope of the study.
-
-% We will implement and test the following algorithms:
-In this study, we will implement and test the following cryptosystems:
-\begin{enumerate}
-	\item A variant of the Paillier cryptosystem~\cite{stern_public-key_1999} which supports floating-point operations, used in \textit{CryptoImg}~\cite{ziad_cryptoimg:_2016}.
-    \item The Damg{\aa}rd--Geisler--Kr{\o}igaard (DGK) cryptosystem~\cite{pieprzyk_efficient_2007, cryptoeprint:2008:321} which is primarily used for secure integer comparison.
-	% \item A fully homomorphic encryption scheme by Dasgupta and Pal, which uses polynomial rings~\cite{dasgupta_design_2016}.
-	\item The Brakerski--Gentry--Vaikuntanathan (BGV) cryptosystem \cite{cryptoeprint:2011:277}, an improvement on the lattice-based cryptosystem by Gentry~\cite{gentry_fully_2009}, with optimizations from Smart, Vercauteren, and Halevi \cite{hutchison_fully_2010, cryptoeprint:2011:566}.
 \end{enumerate}
@@
 \end{enumerate}
-We will adopt the benchmark for evaluating image quality of image encryption schemes presented by Ahmed, et.
+For this study, we adopted the benchmark for evaluating image quality of image encryption schemes presented by Ahmed, et.
 al~\cite{ahmed_benchmark_2016}.
@@
 A detailed overview of the above will be provided in the methodology. Grayscale images will be used in the study.
-A client-server model for secure computation will be assumed to allow operations such as secure comparison and exponentiation.
+A client-server model for secure computation will be assumed
+
 % Training and test data are taken from the publicly available \texttt{faces94} dataset (\url{https://cswww.essex.ac.uk/mv/allfaces/faces94.html}) maintained by the University of Essex.
 
-\subsection{Significance of the Study}
+% TODO: shorten this
+% \subsection{Significance of the Study}
 This study aims to directly address one of the current problems in the research of homomorphic cryptosystems: the practicality of homomorphic encryption~\cite{sen_homomorphic_2013}.

### 2019-03-17 icmssp-paper/parts/03_methodology.tex
[WIP] Shortening introduction

@@
 \section{Methodology}
-In this study we apply three homomorphic encryption schemes~\cite{ziad_cryptoimg:_2016, pieprzyk_efficient_2007, garay_algorithms_2014} for use in image processing and facial recognition applications.
+We apply three homomorphic encryption schemes~\cite{ziad_cryptoimg:_2016, pieprzyk_efficient_2007, garay_algorithms_2014} for use in image processing and facial recognition applications.
 In particular, the study consists of the following:

### 2019-03-17 icmssp-paper/icmssp2019-sigconf.tex
Rewrite Chapter 1 for conference paper

@@
 \begin{abstract}
-Homomorphic cryptography allows for encrypted data to be modified and operated on without requiring decryption, although current homomorphic cryptosystems are either limited in their permitted operations or are significantly more time-intensive than standard non-homomorphic cryptosystems.
-Regardless, homomorphic cryptography has been targeted for use in secure image processing and facial recognition, due to their ability to maintain data privacy.
-In this paper, we compared the viability of the Paillier, Damg{\aa}rd--Geisler--Kr{\o}igaard (DGK), and Brakerski--Gentry--Vaikuntanathan (BGV) cryptosystems for facial image processing applications, by implementing a software library equipped with these cryptosystems, and comparing their time efficiency and accuracy.
-Furthermore, as an extension to previous research, we attempt to support non-linear image processing operations.
-Preliminary results have shown that the Paillier and DGK cryptosystems are comparable in accuracy and may be used for image negation, but only the Paillier cryptosystem is consistent enough to produce reasonable to accurate results.
+\input{parts/00_abstract.tex}
 \end{abstract}

### 2019-03-17 icmssp-paper/parts/00_abstract.tex
Rewrite Chapter 1 for conference paper

Homomorphic cryptography allows for encrypted data to be operated on securely without requiring decryption. Current homomorphic cryptosystems are either limited in their permitted operations or are significantly more time-intensive than standard non-homomorphic cryptosystems. Regardless, homomorphic cryptography has been targeted for use in secure image processing and facial recognition, due to their ability to maintain data privacy. In this paper, we assessed the viability of the Paillier, Damg{\aa}rd--Geisler--Kr{\o}igaard (DGK), and Brakerski--Gentry--Vaikuntanathan (BGV) cryptosystems for facial image processing applications, by implementing a software library equipped with these cryptosystems, and comparing their time efficiency and accuracy. As an extension to previous research, we attempt to support non-linear image processing operations. Preliminary results have shown that the Paillier and DGK cryptosystems are comparable in accuracy and may be used for image negation, but only the Paillier cryptosystem is consistent enough to produce reasonable to accurate results.

### 2019-03-17 icmssp-paper/parts/01_introduction.tex
Rewrite Chapter 1 for conference paper

@@
 \section{Introduction}
-% \subsection{Context of the Study}
-% Digital data privacy and security is a growing concern in various fields, such as cloud computing~\cite{potey_homomorphic_2016}, health information systems~\cite{kester_cryptographic_2015}, and video surveillance~\cite{upmanyu_efficient_2009}.
-Digital image encryption is a growing concern today, with many algorithms existing in the literature~\cite{murugan_survey_2018}.
-
-% TODO : Mention the four HE schemes here
-Of particular interest is homomorphic encryption, where operations such as addition and multiplication can be performed on encrypted data.
-These operations are then preserved when the data is decrypted.
-In this manner, data is manipulated without compromising data privacy, as the encrypted data being operated on remains secure~\cite{fontaine_survey_2007, sen_homomorphic_2013}.
-In the area of homomorphic image encryption, there is interest in being able to perform image manipulation operations on the encrypted data such as image adjustment, filtering, and morphological/feature extraction operations~\cite{ziad_cryptoimg:_2016, gonzalez_digital_2008}.
-More advanced operations have also been implemented using homomorphic cryptosystems, such as facial recognition \cite{hutchison_privacy-preserving_2009} and neural networks \cite{hesamifard_cryptodl:_2017}.
-This study in particular focuses on facial recognition.
-
-Our main research objective is to assess the practicality of various homomorphic cryptosystems with regard to image processing on faces.
-% Homomorphic cryptosystems are known to be slower in terms of encryption, operation, and decryption time~\cite{sen_homomorphic_2013}.
-Furthermore, the operations on encrypted data supported by homomorphic cryptosystems are limited, and some schemes require preprocessing to be performed on images, limiting the range of operations which can be performed efficiently~\cite{li_elliptic_2012}.
-
-% TODO: be specific here, integrate objectives and scope
-% Focus objectives on new developments
-In this study, we accomplish the following:
-\begin{enumerate}
-    \item Implement common linear and non-linear image processing operations using the Paillier, DGK, DGHV, and BGV homomorphic encryption schemes.
-    \item Compare the time efficiency and accuracy of common image processing operations under these homomorphic encryption schemes, and of common image processing operations without using homomorphic encryption;
-    \item Create a library to allow for convenient use and comparison of these homomorphic encryption schemes for image processing and facial recognition.
-\end{enumerate}
-We will implement and test the following categories of image manipulation operations:
-\begin{enumerate}
-	\item Non-linear image intensity adjustment (logarithm and power-log transformations)
-	\item Facial detection and recognition using the eigenface approach \cite{turk_eigenfaces_1991}.
-\end{enumerate}
-For this study, we adopted the benchmark for evaluating image quality of image encryption schemes presented by Ahmed, et.
-al~\cite{ahmed_benchmark_2016}.
-The presented benchmark reflects many tests used in other literature~\cite{ahmad_efficiency_2012, wu_npcr_2011}.
-\begin{enumerate}
-    \item Mean Squared Error (MSE)
-    \item Peak Signal to Noise Ratio (PSNR)
-    \item Structural Similarity Index (SSIM)
-\end{enumerate}
-A detailed overview of the above will be provided in the methodology. Grayscale images will be used in the study.
-A client-server model for secure computation will be assumed
-
-% Training and test data are taken from the publicly available \texttt{faces94} dataset (\url{https://cswww.essex.ac.uk/mv/allfaces/faces94.html}) maintained by the University of Essex.
-
-% TODO: shorten this
-% \subsection{Significance of the Study}
-This study aims to directly address one of the current problems in the research of homomorphic cryptosystems: the practicality of homomorphic encryption~\cite{sen_homomorphic_2013}.
-The literature shows existing homomorphic cryptosystems and how they support primitive operations (usually addition and multiplication) on encrypted data, however, for homomorphic cryptosystems to be useful for practical use, efficient support for more complicated image processing operation must be demonstrated as well.
-While implementations of image processing operations in a homomorphic cryptosystem exist in the literature~\cite{ziad_cryptoimg:_2016, garay_algorithms_2014}, our study targets the more computationally intensive task of facial recognition and detection.
+Digital image security is a growing concern, and various image encryption schemes have been developed and analyzed in the literature~\cite{murugan_survey_2018, kester_cryptographic_2015, jain_image_2016, singh_image_2015, khoirom_cryptanalysis_2018}.
+Cryptosystems allow for the secure transmission of data by way of encryption and decryption schemes.
+Of particular interest is homomorphic image encryption, which allows operations to be performed on encrypted images.
+These operations are then preserved when the images is decrypted.
+In this manner, images are manipulated without compromising data privacy, as the image being operated on remains secure~\cite{fontaine_survey_2007, sen_homomorphic_2013}.
 
@@
 
-We wish to contribute to existing models for the secure transmission and modification of image data by developing a software library which allows the use and comparison of various homomorphic encryption algorithms.
+In the area of homomorphic image encryption, there is interest in being able to perform image manipulation operations such as image adjustment, image filtering, and morphological extraction operations~\cite{ziad_cryptoimg:_2016, gonzalez_digital_2008}.
+The \textit{CryptoImg} software library implements common linear operations on encrypted images~\cite{ziad_cryptoimg:_2016}.
+There is also work on facial recognition on encrypted images\cite{turk_eigenfaces_1991, hutchison_privacy-preserving_2009}.
+However, preprocessing which requires non-linear operations, such as those in~\cite{oravec_illumination_2010}, has yet to be performed in the encrypted domain.
+
+Homomorphic encryption schemes have two main limitations: first, they are limited in the operations that can be performed on encrypted data efficiently~\cite{li_elliptic_2012}, and second, they are slower than non-homomorphic schemes~\cite{sen_homomorphic_2013}.
+This paper presents implementations of non-linear image operations under a homomorphic encryption scheme, and evaluates their applicability and performance.
+
+To investigate the applicability of homomorphic image manipulation, in Section \ref{sec:chapter_2}, we introduce three homomorphic cryptosystems prominent in the literature: Paillier, Damg{\aa}rd--Geisler--Kr{\o}igaard (DGK), and Brakerski--Gentry--Vaikuntanathan (BGV) cryptosystems.
+We list important properties of each cryptosystem and show how they can be used for non-linear image processing operations, compared to previous uses in the literature.
+In Section \ref{sec:chapter_3}, we implement a software library allowing for common linear and non-linear image processing operations using each of the three cryptosystems, assuming a client-server model for secure computation.
+
+To evaluate the performance of homomorphic image manipulation, in Section \ref{sec:chapter_4}, we test the time efficiency and accuracy of common image processing operations under homomorphic encryption.
+We test for image quality of the resulting images using Mean Squared Error (MSE), Peak Signal to Noise Ratio (PSNR), and Structural Similarity Index (SSIM), which are measures of image quality used for assessing image encryption schemes~\cite{ahmed_benchmark_2016}.
+
+% Training and test data are taken from the publicly available \texttt{faces94} dataset (\url{https://cswww.essex.ac.uk/mv/allfaces/faces94.html}) maintained by the University of Essex.
+
+% \subsection{Significance of the Study}
+% This study aims to directly address one of the current problems in the research of homomorphic cryptosystems: the practicality of homomorphic encryption~\cite{sen_homomorphic_2013}.
+The literature shows existing homomorphic cryptosystems and how they support primitive operations (usually addition and multiplication) on encrypted data, however, for homomorphic cryptosystems to be useful for practical use, efficient support for more complicated image processing operation must be demonstrated as well.
+While implementations of image processing operations in a homomorphic cryptosystem exist in the literature~\cite{ziad_cryptoimg:_2016, garay_algorithms_2014}, our study targets the more computationally intensive task of facial recognition and detection.
+
+% We wish to contribute to existing models for the secure transmission and modification of image data by developing a software library which allows the use and comparison of various homomorphic encryption algorithms.
 Our software library would allow service providers to perform image manipulation for clients without compromising data privacy.

### 2019-03-17 icmssp-paper/parts/03_methodology.tex
Rewrite Chapter 1 for conference paper

@@
 \section{Methodology}
+\label{sec:chapter_3}
 We apply three homomorphic encryption schemes~\cite{ziad_cryptoimg:_2016, pieprzyk_efficient_2007, garay_algorithms_2014} for use in image processing and facial recognition applications.

### 2019-03-17 icmssp-paper/parts/04_results.tex
[WIP] Shortening introduction
Rewrite Chapter 1 for conference paper

@@
 \section{Preliminary Results and Discussion}
+\label{sec:chapter_4}
 The results shown in this section are gathered from the tests for intensity transformations under Paillier and DGK cryptosystems.
@@
 
-\begin{table}[h]
+\begin{table}[ht]
 	\centering
@@
 % \end{table}
-\begin{table}[h]
+\begin{table}[ht]
 	\centering
@@
 % \end{table}
-\begin{table}[h]
+\begin{table}[ht]
 	\caption{Logarithm transformation under DGK}

### 2019-03-17 icmssp-paper/parts/01_introduction.tex
Shortening Ch2-3

@@
 In the area of homomorphic image encryption, there is interest in being able to perform image manipulation operations such as image adjustment, image filtering, and morphological extraction operations~\cite{ziad_cryptoimg:_2016, gonzalez_digital_2008}.
-The \textit{CryptoImg} software library implements common linear operations on encrypted images~\cite{ziad_cryptoimg:_2016}.
 There is also work on facial recognition on encrypted images\cite{turk_eigenfaces_1991, hutchison_privacy-preserving_2009}.
-However, preprocessing which requires non-linear operations, such as those in~\cite{oravec_illumination_2010}, has yet to be performed in the encrypted domain.
+While secure linear image operations have been implemented~\cite{ziad_cryptoimg:_2016}, preprocessing which requires non-linear operations, such as those in~\cite{oravec_illumination_2010}, has yet to be performed in the encrypted domain.
 
@@
 
-To investigate the applicability of homomorphic image manipulation, in Section \ref{sec:chapter_2}, we introduce three homomorphic cryptosystems prominent in the literature: Paillier, Damg{\aa}rd--Geisler--Kr{\o}igaard (DGK), and Brakerski--Gentry--Vaikuntanathan (BGV) cryptosystems.
-We list important properties of each cryptosystem and show how they can be used for non-linear image processing operations, compared to previous uses in the literature.
+To investigate the applicability of homomorphic image manipulation, in Section \ref{sec:chapter_2}, we introduce three homomorphic cryptosystems prominent in the literature: the Paillier, Damg{\aa}rd--Geisler--Kr{\o}igaard (DGK), and Brakerski--Gentry--Vaikuntanathan (BGV) cryptosystems, as well as relevant past implementations.
 In Section \ref{sec:chapter_3}, we implement a software library allowing for common linear and non-linear image processing operations using each of the three cryptosystems, assuming a client-server model for secure computation.

### 2019-03-17 icmssp-paper/parts/02_reviewofrelatedliterature.tex
Rewrite Chapter 1 for conference paper
Shortening Ch2-3

@@
 \section{Review of Related Literature}
+\label{sec:chapter_2}
 \subsection{Homomorphic Cryptosystems}
-A cryptosystem consists of an encryption function $\mathcal{E}$ and a decryption function $\mathcal{D}$, along with the plaintext space $\mathcal{P}$, ciphertext space $\mathcal{C}$ and the key space $\mathcal{K}$~\cite{bauer_cryptosystem_2005}.
-A \textit{plaintext} is text that can be commonly understood, while a \textit{ciphertext} results from encrypting the plaintext using an encryption key.
-The \textit{plaintext space} is the set of all possible plaintexts, the \textit{ciphertext space} is the set of all possible ciphertexts, while the \textit{keyspace} is the set of all possible keys.
+A cryptosystem~\cite{bauer_cryptosystem_2005} consists of an encryption function and a decryption function, which operate on plaintexts, ciphertexts and keys.
+A \textit{plaintext}, is text that can be commonly understood within a larger group.
+Given a \textit{key} the encryption function maps a plaintext to some \textit{ciphertext}, which can only be understood by authorized parties.
+The decryption function similarly maps a ciphertext back to its corresponding plaintext, given an appropiate key.
+By sending data as ciphertext and only exposing the corresponding plaintexts to authorized parties who have access to the appropiate keys, secure data transmission can be achieved.
 
-% There are two kinds of cryptosystems, \textit{symmetric} and \textit{asymmetric}.
-In symmetric-key cryptosystems, the same key is used for both encryption and decryption.
-As a consequence, symmetric-key cryptosystems must be implemented with a secure key exchange protocol, so that both the sender and receiver have access to the same key.
-Prominent examples of symmetric-key cryptosystems are the Data Encryption Standard (DES), and its replacement, the Advanced Encryption Standard (AES).
-
-% On the other hand, asymmetric-key (or public-key) cryptosystems use separate keys for encryption and decryption.
-The encryption key (also called the \textit{public key}) is shared publicly, while the decryption key (also called the \textit{private key}) is kept secret.
-Since the public key and private keys are different, there is no need to agree upon secure key exchange protocols.
-Usually, the security of asymmetric-key cryptosystems relies on the intractability of certain computational problems, for example, the RSA cryptosystem depends on the difficulty of big integer factorization~\cite{rivest_method_1978}, while the ElGamal cryptosystem depends on the difficulty of the discrete logarithm problem~\cite{blakley_public_1985}.
-
-% Homomorphic cryptosystems are a special type of cryptosystem in which operations can be securely performed on encrypted data.
-Suppose that for a public-key cryptosystem, $\mathcal{E}_k \left(p \right)$ is the encryption function using the public key $k \in \mathcal{K}$, and $\mathcal{D}_l \left(c \right)$ be the decryption function using the private key $l$.
-A cryptosystem is said to be homomorphic if its encryption function is homomorphic, that is, if it satisfies the relation
-% \begin{equation}
-%     \mathcal{E}_k \left(p_1 \boxplus p_2\right) = \mathcal{E}_k \left(p_1\right) \boxdot \mathcal{E}_k \left(p_2\right)
-% \end{equation}
-% where $p_1, p_2 \in \mathcal{P}$ are the plaintexts, and $\boxplus$ and $\boxdot$ are operations in $\mathcal{P}$ and $\mathcal{C}$ respectively~\cite{fontaine_survey_2007}.
-Furthermore, a homomorphic cryptosystem also satisfies~\cite{li_elliptic_2012}
-% \begin{equation}
-%     p_1 \boxplus p_2 = \mathcal{D}_l \left( \mathcal{E}_k \left(p_1\right) \boxdot \mathcal{E}_k \left(p_2\right) \right).
-% \end{equation}
-
-% In other words,
-A homomorphic cryptosystem preserves the operations that can be done with the plaintext without requiring an intermediary step of decrypting the ciphertext beforehand.
+A \textit{homomorphic cryptosystem} allows operations to be performed on recovered plaintexts by performing corresponding operations on ciphertexts.
+This allows for secure computation by performing operations in the ciphertext domain.
 It is important to note that the operations in the plaintext space and ciphertext space need not be the same.
@@
 
-% Homomorphic cryptosystems can be classified according to the plaintext and ciphertext operations, $\boxplus$ and $\boxdot$.
-If the plaintext operation $\boxplus$ is addition, the cryptosystem is said to be \textit{additively homomorphic}, and the cryptosystem is said to be \textit{multiplicatively homomorphic} if the plaintext operation $\boxplus$ is multiplication.
+% \subsection{Partially Homomorphic Cryptosystems}
+% A cryptosystem is called \textit{partially homomorphic} if it only admits limited types of operations on ciphtertexts.
+We present two partially homomorphic encryption (PHE) schemes: the Paillier cryptosystem and the DGK cryptosystem.
+We then show how to use these PHE schemes for secure floating-point computation using two-party protocols.
 
-\subsection{Partially Homomorphic Cryptosystems}
-In this section, we will present two classical partially homomorphic cryptosystems which we will be testing in the study: the Paillier cryptosystem and the DGK cryptosystem.
-Both of these cryptosystems encrypt integer plaintexts as integer ciphertexts.
-In our description of each cryptosystem, we use $E(m)$ to denote the encryption of a plaintext $m$, and $D(c)$ to denote the decryption of a ciphertext $c$.
-
-% We will then show that the cryptosystems can be modified to support privacy-perserving polynomial evaluation in a client-server protocol: given an encrypted message $m$, evaluate $f(m)$ where $f$ is a polynomial function.
-
-\subsubsection{The Paillier Cryptosystem}
+% big table to summarize Paillier and DGK
+% \begin{table*}[ht]
+% 	\caption{Summary of partially homomorphic cryptosystems}
+% 	\label{tab:phe_summary}
+%     \begin{tabular}{
+%         p{\dimexpr 0.2\linewidth-2\tabcolsep}
+%         p{\dimexpr 0.4\linewidth-2\tabcolsep}
+%         p{\dimexpr 0.4\linewidth-2\tabcolsep}}
+% 		\toprule
+% 		 & Paillier & DGK\\
+%         \midrule
+%             Plaintext space &
+%             $\mathbb{Z}_n$ &
+%             $\mathbb{Z}_u$ 
+%             \\
+%             Ciphertext space &
+%             $\mathbb{Z}_{n^2}$ &
+%             $\mathbb{Z}^*_n$
+%             \\
+%             Key generation &
+%             Define a function $L(x)$ as the largest integer $v$ greater than zero such that $x-1 \geq vn$.\newline
+%             Choose two large primes $p$ and $q$, and set $n = pq, \lambda = \mathrm{lcm}(p-1,q-1)$.\newline
+%             Select an integer $g$, $0\leq g \leq n^2$ such that $\mathrm{gcd}(L(g^\lambda \bmod n^2), n) = 1$\newline
+%             The public key as $(g,n)$ and the private key $(p,q)$
+%             &
+%             Let $p,q$ be primes such that we can choose two primes $v_p$ and $v_q$ such that $v_p | (p-1)$ and $v_q | (q-1)$, and a small prime $u$ such that $u | (p-1)$ and $u | (q-1)$. \newline
+%             Denote $n = pq$. \newline
+%             Choose $g$ to be an integer of order $uv_pv_q$ and $h$ to be of order $v_pv_q$.\newline
+%             The public key is $(n,g,h,u)$ and the private key is $(p,q,v_p,v_q)$.
+%             \\
+%             Encryption function &
+%             $E(m) = g^m \cdot r^n \mod{n^2}$ &
+%             $E(m) = g^m \cdot h^r \mod{n}$
+%             \\
+%             Decryption function &
+%             $D(c) = L(c^\lambda \bmod n^2) \times (L(g^\lambda \bmod n^2))^{-1} \mod n$ &
+%             Compute $c^{v_pv_q} \bmod n$. There is a one-to-one correspondence between this quantity and the plaintexts.
+%             \\
+% 	    \bottomrule
+%     \end{tabular}
+% \end{table*}
+\subsection{Paillier and DGK Cryptosystems}
 The Paillier cryptosystem \cite{stern_public-key_1999}, developed by Pascal Paillier, is a probabilistic encryption scheme which is based on the composite residuosity class problem.
 The scheme has several well--known homomorphic properties.
+Table \ref{tab:paillier_summary} shows the key generation, encryption, and decryption procedures of the Paillier cryptosystem, which encrypts plaintexts in $\mathbb{Z}_n$ as ciphertexts in $\mathbb{Z}_{n^2}$.
+\begin{table}[ht]
+	\caption{The Paillier cryptosystem}
+	\label{tab:paillier_summary}
+    \begin{tabular}{
+        p{\dimexpr 0.2\linewidth-2\tabcolsep}
+        p{\dimexpr 0.8\linewidth-2\tabcolsep}}
+		\toprule
+		Step & Description\\
+        \midrule
+            Key\newline Generation &
+            Let $L(x)$ be the largest integer $v$ greater than zero such that $x-1 \geq vn$.\newline
+            Choose two large primes $p$ and $q$, and set $n = pq$, and $ \lambda = \mathrm{lcm}(p-1,q-1)$.\newline
+            Select an integer $g$, $0\leq g \leq n^2$ such that $\mathrm{gcd}(L(g^\lambda \bmod n^2), n) = 1$\newline
+            The public key as $(g,n)$ and the private key is $(p,q)$.
+            \\
+            Encryption &
+            $E(m) = g^m \cdot r^n \mod{n^2}$ 
+            \\
+            Decryption &
+            $D(c) = L(c^\lambda \bmod n^2) \times (L(g^\lambda \bmod n^2))^{-1} \mod n$ 
+            \\
+	    \bottomrule
+    \end{tabular}
+\end{table}
 % The scheme allows for the encryption and decryption of integer messages, and is known to be additively homomorphic.
@@
 
-These homomorphic properties are used to add a plaintext scalar to a ciphertext, add two ciphertexts, and multiply a ciphertext by a plaintext scalar, respectively.
+These homomorphic properties are used to add a plaintext to a ciphertext, add two ciphertexts, and multiply a ciphertext by a plaintext scalar, respectively.
 
-\subsubsection{The DGK Cryptosystem}
 The DGK cryptosystem was published by Damg{\aa}rd, Geisler, and Kr{\o}igaard in 2007 in an effort to create a secure integer comparison scheme \cite{pieprzyk_efficient_2007, cryptoeprint:2008:321} which is widely used in the literature \cite{veugen_improving_2012}.
-The DGK cryptosystem has homomorphic properties similar to the Paillier cryptosystem.
+ The details of the DGK cryptosystem may be found in Table \ref{tab:dgk_summary}.
+The DGK cryptosystem encrypts plaintexts in $\mathbb{Z}_u$ as ciphertexts in $\mathbb{Z}_n^\ast$, and has homomorphic properties similar to the Paillier cryptosystem.
 
-% \paragraph{Key Generation}
-% We denote $k,t,\ell$ as security parameters of the scheme, where $k>t>\ell$.
-% Let $p,q$ be primes such that
-% we can choose two $t$-bit primes $v_p$ and $v_q$ such that $v_p | (p-1)$ and $v_q | (q-1)$, and a small prime $u$ such that $u | (p-1)$ and $u | (q-1)$.
-% We denote $n = pq$.
-% We choose $g$ to be an integer of order $uv_pv_q$ and $h$ to be of order $v_pv_q$.
-
-% The DGK cryptosystem encrypts plaintexts in $\mathbb{Z}_u$ to ciphertexts in $\mathbb{Z}_n^\ast$.
-
-% The public key is $(n,g,h,u)$ and the private key is $(p,q,v_p,v_q)$.
-
-% \paragraph{Encryption and Decryption}
-% To encrypt a message $m \in \mathbb{Z}_u$, the encryption function is defined as:
-% \begin{align*}
-%   E(m) = g^m \cdot h^r \mod{n},
-% \end{align*}
-% where $r$ is a random integer in $\mathbb{Z}_n$ which is longer than $2t$ bits.
-
-% To decrypt a ciphertext $c \in \mathbb{Z}_n^\ast$, decryption is achieved by first computing $c^{v_pv_q}$.
-% \begin{align*}
-% 	c^{v_pv_q} \bmod n
-% 	&= (g^m \cdot h^r)^{v_pv_q} \bmod n\\
-% 	&= (g^{v_pv_q})^m \bmod n
-% \end{align*}
-% Since $(g^{v_pv_q})^m$ has order $u$, there is a one-to-one correspondence between plaintexts in $\mathbb{Z}_u$ and  $(g^{v_pv_q})^m$.
-A lookup table can thus be generated privately to successfully recover $m$.
-
-% \paragraph{Homomorphic Properties of the DGK Cryptosystem}
-% The DGK cryptosystem supports additive homomorphism as well as the multiplication of a plaintext scalar to an encrypted message.
-These homomorphic properties are used to add a plaintext scalar to a ciphertext, add two ciphertexts, and multiply a ciphertext by a plaintext scalar, respectively.
-They are defined as follows.
+\begin{table}[ht]
+	\caption{The DGK cryptosystem}
+	\label{tab:dgk_summary}
+    \begin{tabular}{
+        p{\dimexpr 0.2\linewidth-2\tabcolsep}
+        p{\dimexpr 0.8\linewidth-2\tabcolsep}}
+		\toprule
+		Step & Description\\
+        \midrule
+            Key\newline Generation &
+            Let $p,q$ be primes such that we can choose two primes $v_p$ and $v_q$ such that $v_p | (p-1)$ and $v_q | (q-1)$, and a small prime $u$ such that $u | (p-1)$ and $u | (q-1)$. \newline
+            Denote $n = pq$. \newline
+            Choose $g$ to be an integer of order $uv_pv_q$ and $h$ to be of order $v_pv_q$.\newline
+            The public key is $(n,g,h,u)$ and the private key is $(p,q,v_p,v_q)$.
+            \\
+            Encryption &
+            $E(m) = g^m \cdot h^r \mod{n}$
+            \\
+            Decryption &
+            Compute $c^{v_pv_q} \bmod n$. There is a one-to-one correspondence between this quantity and the plaintexts, so the plaintext can be recovered using a lookup table.
+            \\
+	    \bottomrule
+    \end{tabular}
+\end{table}
 
@@
 As the multiplicative homomorphism was not presented in the original paper, we provide a short proof here.
+\begin{theorem}
+    In the DGK cryptosystem with public key $(n,g,h,u)$ and private key $(p,q,v_p,v_q)$, it holds that $D(E(m_1)^k) = km_1\bmod u$.
+\end{theorem}
 \begin{proof}
@@
 
-% \subsubsection{Secure Exponentiation and Multiplication Protocols}
-% \label{ssec:exponentiationprotocol}
-% [TO-DO: This is further explained in another paper.]
-% In order to perform polynomial evaluation, we first present a protocol for privacy-preserving exponentiation to a positive integer power, adapted from the protocol to calculate Euclidean distances used in \cite{hutchison_privacy-preserving_2009}.
+We have shown how the Paillier and DGK cryptosystems have similar homomorphic properties.
+In both cryptosystems, we are able to add a plaintext to a ciphertext, add two ciphertexts, and multiply a ciphertext by a plaintext scalar.
+In order to use these cryptosystems in secure image processing, we require the two schemes to support the encryption and manipulation of floating-point (FP) numbers, which can be done by using an approach shown in~\cite{ziad_cryptoimg:_2016}.
+This approach represents FP numbers using an encrypted mantissa and an unencrypted exponent.
+This representation extends the addition and plaintext multiplication homomorphisms of the Paillier and DGK cryptosystems to floating-point numbers.
 
-% The following protocols apply to both the Paillier and DGK cryptosystems, as they share similar homomorphisms. We first present a secure squaring protocol.
+Table \ref{tab:flop_summary} describes protocols such as division~\cite{boukoros_lightweight_2017}, exponentiation~\cite{hutchison_privacy-preserving_2009}, and multiplication.
+These protocols, used in conjunction with the FP extension, allow for secure floating-point arithmetic~\cite{pcsc-paper}.
 
-% Suppose Alice encrypts an integer $x$ and sends it so Bob has $E(x)$, and wants to obtain $E(x^2)$ without exposing the value of $x$.
-% \begin{itemize}
-% 	\item Bob first selects a random integer $r$ and computes $E(x+r)$. Bob can do this since $r$ is a plaintext constant.
-% 	\item Bob sends $E(x+r)$ to Alice, who decrypts the ciphertext to obtain $x+r$.
-% 	\item Alice squares $x+r$ and encrypts the result. She sends $E((x+r)^2)$ to Bob.
-% 	\item Bob computes $E(-2rx + r^2)$. He then computes $E((x+r)^2)E(-2rx + r^2) = E(x^2)$.
-% \end{itemize}
+\begin{table}[ht]
+	\caption{Two-party FP protocols}
+	\label{tab:flop_summary}
+    \begin{tabular}{
+        p{\dimexpr 0.25\linewidth-2\tabcolsep}
+        p{\dimexpr 0.75\linewidth-2\tabcolsep}}
+		\toprule
+		Operation & Protocol\\
+        \midrule
+            Division &
+            The server selects a random number $r$ and sends $E(rx)$ and $E(ry)$ to the client, who can decrypt to obtain $rx$ and $ry$.
+The client then encrypts the quotient and sends $E(rx/ry) = E(x/y)$ to the server.
+            \\
+            Exponentiation &
+            The server selects a random number $r$ and computes $E\left(x+r\right)$.
+The server sends $E(x+r)$  to the client, who can decrypt to obtain $x+r$.
+The client then encrypts and sends $E((x+r)^2)$ to the server.
+The server then computes $E\left(\left(x+r\right)^2\right)E\left(-2rx + r^2\right) = E\left(x^2\right)$.
+            \\
+            Multiplication &
+            The server obtains $E(x^2)$, $E(y^2)$, and $E((x+y)^2)$ using the exponentiation protocol.
+It can then compute $\frac{1}{2}E\left(\left(x+y\right)^2\right)E\left(x^2\right)^{-1}E\left(y^2\right)^{-1} = E\left(xy\right)$.\\
+	    \bottomrule
+    \end{tabular}
+\end{table}
+\subsection{The BGV Cryptosystem}
+The BGV (Brakerski--Gentry--Vaikuntanathan) cryptosystem \cite{cryptoeprint:2011:277} is a fully homomorphic cryptosystem created based on the ring-learning with error problem.
+A \textit{fully homomorphic cryptosytem} allows aribitrary computation on encrypted data.
+However, they are known to be significantly slower than partially homomorphic cryptosytems; improving the efficiency of fully homomorphic cryptosytems is an active area of research \cite{sen_homomorphic_2013}.
+The details regarding the construction of the BGV cryptosystem are beyond the scope of this paper.
 
-% We can use the secure squaring protocol to arrive at a secure multiplication protocol, which then allows for the evaluation of polynomials.
-% Suppose Alice encrypts integers $x$ and $y$, and Bob has $E(x), E(y)$ and wants to obtain $E(xy)$.
-% \begin{itemize}
-% 	\item Bob acquires $E(x^2), E(y^2)$ using the secure squaring protocol.
-% 	\item Bob sends $E(x+y)$ to Alice, who decrypts the ciphertext to obtain $x+y$.
-% 	\item Alice sends $E((x+y)^2)$ to Bob.
-% 	\item Bob then computes
-% 	\begin{align*}
-% 		E((x+y)^2)E(x^2)^{-1}E(y^2)^{-1} &= E((x+y)^2 - x^2 - y^2)\\
-% 		&= E(2xy)
-% 	\end{align*}
-% 	\item Bob can then recover $E(xy)$ by calcuating for the multiplicative inverse of 2 using the Euclidean algorithm, and calculating $2^{-1}E(xy)$.
-Such an inverse exists since the modulus is either a prime (in the DGK cryptosystem) or a product of primes greater than 2 (in the Paillier cryptosystem).
-% \end{itemize}
-
-\subsection{Fully Homomorphic Cryptosystems}
-We will also be testing fully homomorphic cryptosytems, which allow aribitrary computation on encrypted data.
-While generally being more flexible, fully homomorphic cryptosytems are known to be significantly slower than partially homomorphic cryptosytems; improving the efficiency of fully homomorphic cryptosytems is an active area of research \cite{sen_homomorphic_2013}.
-
-% We will present two such cryptosystems, the Dasgupta--Pal cryptosystem, which we present in full to explain a correction we propose to it, and the BGV cryptosystem, which has open source implementations availble primarily used in homomorphic cryptography research.
-
-% \subsubsection{The Dasgupta--Pal Cryptosystem}
-% The Dasgupta--Pal cryptosystem is a fully homomorphic cryptosystem proposed in 2016 by Smaranika Dasgupta and S.
-K.
-Pal \cite{dasgupta_design_2016}, which encrypts integer plaintexts in $\mathbb{Z}_n$ to polynomial ciphertexts.
-We begin our presentation of the Dasgupta--Pal cryptosystem with the following definition.
-
-% Given a message $m \in \mathbb{Z}$, we denote
-% \begin{align*}
-% 		m_p(x) = a_0 + a_1 x + a_2 x^2 + \cdots + a_k x^k
-% \end{align*}
-% where $a_k a_{k-1}\cdots a_2 a_1 a_0$ is the binary representation of $m$.
-
-% In the original scheme presented in \cite{dasgupta_design_2016}, the secret key $S_k$ is set to be a large prime.
-In Appendix \ref{chap:correction}, we present a case where the Dasgupta--Pal cryptosystem fails and prove that setting the secret key $S_k = 2p$, where $p$ is a large prime, corrects errors in the Dasgupta--Pal cryptosystem.
-% We now decribe the correct cryptosystem.
-% \paragraph{Corrected Dasgupta--Pal Cryptosystem Description}
-% Let $\ell$ denote the security parameter of the cryptosystem.
-% Let $S_k = 2p$, where $p$ is a prime number with $\ell - 1$ bits.
-% Choose a random even integer $z$ of length $\log_2{\ell}$.
-
-% Let the secret key be $S_k$, and let the refresh key be $R_k = z \cdot S_k$. The secret key is kept private to the encrypting/decrypting parties, while the refresh key is made publicly available.
-
-% The scheme defines the encryption algorithm for a message $m$ as follows:
-% \begin{align*}
-% 	E(m) = y(x) + S_k\times d(x)
-% \end{align*}
-% where
-% $y(x)$ is a polynomial of degree $n$ such that $m_p(x) \equiv y(x) \bmod S_k$ and $d(x)$ is a randomly chosen polynomial of degree $n$.
-This encrypts each coefficient of $m_p(x)$ by adding some multiple of $S_k$ to it.
-Through this process, each bit of the message is encrypted separately.
-
-% Furthermore, the decryption algorithm to recover $m_p(x)$ from a ciphertext polynomial $c(x)$ as
-% \begin{align*}
-% 	m_p(x) = c(x) \bmod S_k \bmod 2.
-% \end{align*}
-% Thus $D(c(x))$ is defined as the integer recovered from the coefficients of the polynomial $c(x) \bmod S_k \bmod 2$.
-
-% Dasgupta and Pal note that homomorphic operations on ciphertext introduce noise which may interfere with decryption, due to the potential increase in ciphertext values.
-% To eliminate noise from a polynomial ciphertext, the following refresh function is used:
-% \begin{align*}
-% 	R(c(x)) = c(x) \bmod R_k.
-% \end{align*}
-
-% \paragraph{Homomorphic Properties of the Dasgupta--Pal Cryptosystem}
-% It has been shown \cite{dasgupta_design_2016} that the following properties hold for all integer messages $m_1, m_2 \in \mathbb{Z}_n$ in the Dasgupta--Pal cryptosystem.
-These properties arise since each coefficient in a ciphertext polynomial is essentially an independently encrypted bit of the original message.
-% \begin{description}
-% 	\item[\textsc{xor} on ciphertexts]
-% 	A bitwise exclusive or (\textsc{xor}) operation on integer messages can be achieved by adding the coefficients pairwise between two ciphertexts.
-% 	\begin{align*}
-% 		D(E(m_1)+E(m_2)) = m_1 \textsc{ xor } m_2
-% 	\end{align*}
-% 	\item[\textsc{and} on ciphertexts]
-% 	Similarly, pair-wise multiplication corresponds to bitwise \textsc{and} of integer messages.
-% 	\begin{align*}
-% 		D(E(a) \otimes E(b)) = a \textsc{ and } b = ab \bmod 2
-% 	\end{align*}
-% 	where $\otimes$ denotes pairwise multiplication,
-% 	\begin{align*}
-% 		\sum_{i=1}^n{a_ix^i} \otimes \sum_{i=1}^n{b_ix^i} = \sum_{i=1}^n{a_ib_ix^i}.
-% 	\end{align*}
-% \end{description}
-
-% Arbitrary computation on data can thus be achived using these bitwise operations.
-While the Dasgupta--Pal cryptosystem requires significant amounts of memory, as each bit of plaintext is encrypted into an integer, this approach provides a flexible method to perform relatively fast arbitrary computation on encrypted data.
-Encryption and decryption in the Dasgupta--Pal cryptosystem are accomplished using few arithmetic operations.
-
-% \subsubsection{HElib and the BGV Cryptosystem}
-The BGV (Brakerski--Gentry--Vaikuntanathan) cryptosystem \cite{cryptoeprint:2011:277} is a fully homomorphic cryptosystem created based on the ring-learning with error problem.
-The BGV cryptosystem was constructed to surpass the limitations of prior fully homomorphic cryptosystems, which were based on the first fully homomorphic cryptosystem by Gentry \cite{gentry_fully_2009}.
-
-The details regarding the construction of the BGV cryptosystem are beyond the scope of this paper.
-For this study, we will be using \textit{HElib} \cite{garay_algorithms_2014}, an open-source library which implements the BGV cryptosystem with optimizations to improve efficiency.
-Evaluation of operations on 120 inputs in \textit{HELib} was performed in around 4 minutes, with an average of 2 seconds to process a single input \cite{hutchison_fully_2010,cryptoeprint:2011:566}.
-
-The \textit{HElib} library has been adapted to Python using the Pyfhel library \cite{pyfhel_2018} maintained by Ibarrondo, Laurent (SAP) and Onen (EURECOM), and licensed under the GNU GPL v3 license.
-The Pyfhel library is a Python API for the \textit{HElib} library, which supports the following operations on vectors/scalars of integers or binary ciphertexts:
-\begin{itemize}
-	\item Arithmetic operations: addition, subtraction, multiplication;
-	\item Binary operations: \textsc{and}, \textsc{or}, \textsc{not}, \textsc{xor}.
-\end{itemize}
-
+For this study, we will be using \textit{HELib}~\cite{garay_algorithms_2014}, an open-source library which implements the BGV cryptosystem with optimizations.
+\textit{HELib} supports arithmetic operations on integer ciphertexts and logical operations on binary ciphertexts.
+Evaluation of operations on 120 inputs in \textit{HELib} was performed in around 4 minutes, with an average of 2 seconds to process a single input~\cite{hutchison_fully_2010,cryptoeprint:2011:566}.
+The \textit{HELib} library has been adapted to Python using the Pyfhel library \cite{pyfhel_2018} maintained by Ibarrondo, Laurent (SAP) and Onen (EURECOM), and licensed under the GNU GPL v3 license.
 \subsection{CryptoImg}
 A paper published in 2009 by Ziad, et al.
-attempts to implement privacy-preserving image processing using \textit{CryptoImg}, a library for the Open Source Computer Vision Library (OpenCV)~\cite{bradski_opencv_2000} which implements various homomorphic encryption and image processing routines using the Paillier homomorphic cryptosystem~\cite{ziad_cryptoimg:_2016}.
+implements privacy-preserving image processing using \textit{CryptoImg}, a library for the Open Source Computer Vision Library (OpenCV)~\cite{bradski_opencv_2000} which implements various homomorphic encryption and image processing routines using the Paillier homomorphic cryptosystem~\cite{ziad_cryptoimg:_2016}.
 The \textit{CryptoImg} library assumed a client-server model wherein a client requests image processing operations from a server.
@@
 
-The \textit{CryptoImg} library implemented the following:
-\begin{enumerate}
-	\item Extending the Paillier homomorphic cryptosystem which operate on integer plaintexts so that they can operate on real number plaintexts;
-	\item Developing protocols for and implementing the following image processing operations
-	\begin{enumerate}
-		\item Image negation and brightness adjustment
-		\item Spatial filters (for noise reduction, edge detection and sharpening)
-		\item Morphological operations
-		\item Histogram equalization
-	\end{enumerate}
-\end{enumerate}
-For image negation and spatial filters, the protocols specified by \textit{CryptoImg} allow all image processing operations to be performed on the server.
+The \textit{CryptoImg} library implemented the following image processing operations: image negation, brightness adjustment, spatial filters (for noise reduction, edge detection and sharpening), morphological operations, and histogram equalization.
+
+% For image negation and spatial filters, the protocols specified by \textit{CryptoImg} allow all image processing operations to be performed on the server.
 However, due to limitations in the Paillier cryptosystem, the protocols presented for morphological operations and histogram equalization require both the client and the server to perform image processing calculations, although the server performs a significant portion of the processing.
@@
 Ziad, et al.
-also showed experimental results establishing the slow performance of image operations under a homomorphic cryptosystem.
+also showed experimental results establishing the relatively slow performance of image operations under a homomorphic cryptosystem.
 For instance, while sharpening and applying a Sobel filter each take less than a second when applied to a $512\times 512$ plaintext image, when applied to an encrypted image, sharpening required at least 238.257 seconds, and applying the Sobel filter required at least 147.567 seconds \cite{ziad_cryptoimg:_2016}.
 
-We now discuss several limitations in the \textit{CryptoImg} study which we focus on for our research.
+% We now discuss several limitations in the \textit{CryptoImg} study which we focus on for our research.
 First, the \textit{CryptoImg} library was limited in the image intensity transformations it implemented.
 We propose additional protocols to support more computationally intensive intensity transformations.
-Second, the \textit{CryptoImg} library only considered the Paillier cryptosystem.
+% Second, the \textit{CryptoImg} library only considered the Paillier cryptosystem.
 We consider testing the performance of other homomorphic cryptosystems, which differ in their processing time and supported operations.
 
+% Convert to single table
 \subsection{Image Intensity Transformations}
@@
 This function is then applied to every pixel in $R$.
-The \textit{CryptoImg} library implemented two types of linear intensity transformations: image negation and brightness control.
-
-An image negation transformation is defined as:
+The \textit{CryptoImg} library implemented two types of linear intensity transformations: image negation and brightness control. An image negation transformation is defined as
 \begin{equation}
-    T\left(r\right) = L-1-r
+    T\left(r\right) = L-1-r,
 \end{equation}
-After applying image negation, the resulting image would be similar to a photographic negative~\cite{gonzalez_digital_2008}.
-
-A brightness control transformation with parameter $v$ is defined as:
+which results in an image similar to a photographic negative~\cite{gonzalez_digital_2008}.
+A brightness control transformation with parameter $v$ is defined as
 \begin{equation}
-    T\left(r,v\right) = r+v
+    T\left(r,v\right) = r+v.
 \end{equation}
@@
 where $c$ is a constant.
-
 The power-law transformation is a family of transformations that have the form
@@
 where $c>0$ and $\gamma > 0$.
-A power-law transformation defined by the above equation can calibrate the operation of many image capture and output devices such as cameras, printers and displays in a process called \textit{gamma correction}.
+A power-law transformation can calibrate the operation of many image capture and output devices such as cameras, printers and displays in a process called \textit{gamma correction}.
 % This ensures reproducibility and accuracy of images being displayed by digital output devices~\cite{gonzalez_digital_2008}.
@@
 To implement non-linear intensity transformations using addition and multiplication in a homomorphic system, it is necessary to approximate the logarithm and exponential functions, which may result in higher computational overhead.
-In our software library implementation, we investigate methods required to approximate the logarithm and power functions.
+An applicable approximation for the logarithm may be found in \cite{pcsc-paper}.
+% In our software library implementation, we investigate methods required to approximate the logarithm and power functions. 
 Non-linear intensity transformations such as the logarithm transformation have applications in intensity normalization \cite{oravec_illumination_2010}, which is used in some facial recognition algorithms to account for differences in lighting which make facial recognition difficult.

### 2019-03-17 icmssp-paper/parts/03_methodology.tex
Shortening Ch2-3

@@
 \label{sec:chapter_3}
-We apply three homomorphic encryption schemes~\cite{ziad_cryptoimg:_2016, pieprzyk_efficient_2007, garay_algorithms_2014} for use in image processing and facial recognition applications.
+% We apply three homomorphic encryption schemes~\cite{ziad_cryptoimg:_2016, pieprzyk_efficient_2007, garay_algorithms_2014} for use in image processing and facial recognition applications.
 In particular, the study consists of the following:
-\begin{itemize}
-	\item Creating a wrapper library that acts as a unified interface which implements the Paillier, DGK, and BGV homomorphic cryptosystems.
-	\item An implementation of image processing operations (intensity transformations, facial recognition) under the above cryptosystems.
-	\item Conducting tests for image quality, processing time, using images from the \texttt{faces94} dataset.
-\end{itemize}
+% \begin{itemize}
+% 	\item Creating a wrapper library that acts as a unified interface which implements the Paillier, DGK, and BGV homomorphic cryptosystems.
+% 	\item An implementation of image processing operations (intensity transformations, facial recognition) under the above cryptosystems.
+% 	\item Conducting tests for image quality, processing time, using images from the \texttt{faces94} dataset.
+% \end{itemize}
 
@@
 \subsection{Cryptosystem Implementation}
-Three homomorphic encryption schemes are investigated, and a wrapper library was created in Python that integrates these cryptosystems into a unified interface.
+A wrapper library was created in Python that integrates the Paillier, DGK, and BGV cryptosystems into a unified interface.
 \begin{itemize}
@@
 \end{itemize}
-
-\subsubsection{Extension of Partially Homomorphic Cryptosystems}
-\label{sssec:pheextension}
-In order to use Paillier and DGK for secure image processing, we require the two schemes to support the encryption of floating-point (FP) numbers, as well as multiplication and division of arbitrary ciphertexts.
-We extend the two cryptosystems to FP operations by using an approach shown in~\cite{ziad_cryptoimg:_2016}.
-This approach represents FP numbers using a pair $(m,e)$, where $m$ represents the mantissa (which is encrypted), and $e$ represents the exponent (which is not encrypted).
-This approach is also used by the python-paillier library.
-This represntation allows us to extend the addition and plaintext multiplication homomorphisms of the Paillier and DGK cryptosystems to floating-point numbers.
-
-Various two-party protocols can be used to facilitate ciphertext multiplication and division.
-These allow a server armed with only knowledge of the public key, to obtain the product and quotient of ciphertexts, by communicating with the client, who has the private key.
-For division, we use the protocol defined in~\cite{boukoros_lightweight_2017}: to obtain $E(x/y)$ from $E(x)$ and $E(y)$, the server sends $E(rx)$ and $E(ry)$ to the client, (where $r$ is a random non-zero number), allowing the client to compute $E(rx/ry)$ and give the result back to the server.
-
-For multiplication, we adapt the protocol to calculate Euclidean distances used in \cite{hutchison_privacy-preserving_2009}, which provides a two-party protocol which yields $E(x^2)$ given $E(x)$.
-We use this protocol together with the additive homomorphism of the partially homomorphic cryptosystems to instead compute $E((x + y)^2 - x^2 - y^2) = E(2xy)$, from which we can easily obtain $E(xy)$ through plaintext multiplication.
 
@@
 	\item [Peak Signal to Noise Ratio (PSNR).]
-	According to Ahmed, et al.~\cite{ahmed_benchmark_2016}, PSNR is ``an estimator for human visual perception of reconstruction quality.'' It has been used to ascertain image quality in various studies and is a known metric for image and video quality~\cite{upmanyu_efficient_2009, jain_image_2016, akramullah_video_2014}.
-Although it may produce results which do not correlate with human visual perception~\cite{huynh-thu_accuracy_2012, ahmed_benchmark_2016}, it is a valid indicator of image quality when media containing the same visual content is compared~\cite{huynh-thu_accuracy_2012}.
+	The PSNR is ``an estimator for human visual perception of reconstruction quality.''~\cite{ahmed_benchmark_2016}.
+Although it may produce results which do not correlate with human visual perception~\cite{huynh-thu_accuracy_2012, ahmed_benchmark_2016}, it is a valid indicator of image quality when media containing the same visual content is compared~\cite{huynh-thu_accuracy_2012}, and is a known metric for image and video quality~\cite{upmanyu_efficient_2009, jain_image_2016, akramullah_video_2014}.
 	PSNR is defined by
@@
 	\end{align}
-	where $L$ is the maximum pixel intensity value of an image.
-	Despite the known limitations of PSNR, since we are going to compare the effect of each encryption scheme on recovered image quality, given a fixed library of images, it is a valid measure of image quality for the study.
-A higher PSNR indicates higher image quality preservation.
+	where $L$ is the maximum pixel intensity value of an image. A higher PSNR indicates higher image quality preservation.
 	\item [Structural Similarity Index (SSIM).]

### 2019-03-17 icmssp-paper/parts/02_reviewofrelatedliterature.tex
Reduced paper to 10 pages

@@
 We denote with $R(x,y)$ the entry at the $x$th row and $y$th column of a matrix $R$.
-An intensity transformation on an image $R$ can be defined as a function $T$ which maps a pixel value $r$ to a new value $r^\prime$, which we can write as $r^\prime = T\left(r\right)$.
-This function is then applied to every pixel in $R$.
+An intensity transformation on an image $R$ can be defined as a function $T$ which is applied to every pixel $r$ in $R$.
 The \textit{CryptoImg} library implemented two types of linear intensity transformations: image negation and brightness control. An image negation transformation is defined as

### 2019-03-17 icmssp-paper/parts/03_methodology.tex
Reduced paper to 10 pages

@@
 We will implement library functions for image negation, logarithm transformation and power-law transformation, as they are defined in~\cite{gonzalez_digital_2008}.
-We now describe how we implement the logarithm and power-law image intensity transformations.
-In the case of partially homomorphic cryptosystems (Paillier and DGK), if ciphertext multiplication or division is required, the secure protocols in section~\ref{sssec:pheextension} will be used.
-
-\subsubsection{Logarithm Transformation}
-The logarithm transformation of a pixel intensity value $x$ is defined as
-\begin{align}
-	T\left(x\right) = c \log\left(1 + x\right)
-\end{align}
-where $c$ is a constant.
-
-In order to perform this transformation under Paillier and DGK, we provide the following closed-form approximation for $\log\left(1 + x\right)$ from~\cite{pcsc-paper}.
-% TODO: IDK HOW TO CITE OUR PCSC PAPER
+% \subsubsection{Logarithm Transformation}
+In order to perform the logarithm transformation under Paillier and DGK, we use the following closed-form approximation for $\log\left(1 + x\right)$ from~\cite{pcsc-paper}.
+% TODO: HOW ABOUT BGV
 \begin{align}\label{eq:optimal_log_approximation}
@@
 
-\subsubsection{Power-Law Transformation}
-The power-law transformation of a pixel intensity value $x$ is defined as
-\begin{equation}
-    T\left(x\right) = cx^{\gamma}
-\end{equation}
-where $c>0$ and $\gamma > 0$.
-
-Similar to the logarithm transformation, to apply this transformation using Paillier and DGK, we must provide an approximation for $x^\gamma$.
-We can use partial sums of the following series, which relies on the logarithm function.
+% \subsubsection{Power-Law Transformation}
+To apply the power-law transformation using Paillier and DGK, we must provide an approximation for $x^\gamma$.
+We use partial sums of the following series, which relies on the logarithm function.
 \begin{align}
@@
 \end{align}
-% Partial sums of the above infinite series can be calculated based on the closed form approximation for the logarithm in Equation \ref{eq:scaledquadraturech3}.
 For the implementation of the power-law transformation for this paper, a partial sum consisting of the first five terms of the infinite series were used.
@@
 
-The benchmarks to be used in the study, adopted from~\cite{ahmed_benchmark_2016, ahmad_efficiency_2012, wu_npcr_2011} are listed below.
-We let $X_i$ denote a value in an image $X$, where $1 \leq i \leq N$.
-We first perform three tests to ascertain the preservation of image quality after encryption and decryption: MSE, PSNR, and SSIM.
+We perform three tests to ascertain the preservation of image quality after encryption and decryption: MSE, PSNR, and SSIM, adopted from~\cite{ahmed_benchmark_2016, ahmad_efficiency_2012, wu_npcr_2011}.
+In describing each test, we let $X_i$ denote a value in an image $X$, where $1 \leq i \leq N$.
 \begin{description}
@@
 		\item $\sigma_{XY}$ is the covariance of $X$ and $Y$;
-		\item $c_1 = (k_1L)^2, c_2 = (k_2L)^2$ are two variables used to stabilize the measure when $\mu_X^2+\mu_Y^2$ is close to zero~\cite{akramullah_video_2014};
+		\item $c_1 = (k_1L)^2$ and $c_2 = (k_2L)^2$ are two variables used to stabilize the measure when $\mu_X^2+\mu_Y^2$ is close to zero~\cite{akramullah_video_2014};
 		\item $L$ is the the maximum pixel intensity value of an image;
@@
 	The SSIM is applied to the luminance value of two images to gauge structural similarity between neighboring pixels.
-	For the study, we computed $\mathrm{SSIM}(\mathrm{PDT}, \mathrm{CDT})$ for every image operation, under each homomorphic cryptosystem.
 Higher values of SSIM indicate higher structural similarity, and an SSIM of $1$ indicates that the two images are identical~\cite{ahmed_benchmark_2016}.
@@
 
-Computing for MSE, PSNR, and SSIM was done using the corresponding built-in functions from the scikit-image Python library \cite{scikit-image}.
+Computation of the MSE between the PDT and CDT, PSNR of the CDT, and SSIM(PDT,CDT) was done using the corresponding built-in functions from the scikit-image Python library \cite{scikit-image}.
 

### 2019-03-18 icmssp-paper/parts/02_01_cryptosystems.tex
Finalize sections 2.1 to 2.3

--- 2019-03-17 icmssp-paper/parts/02_reviewofrelatedliterature.tex
@@
-\section{Review of Related Literature}
-\label{sec:chapter_2}
 \subsection{Homomorphic Cryptosystems}
 A cryptosystem~\cite{bauer_cryptosystem_2005} consists of an encryption function and a decryption function, which operate on plaintexts, ciphertexts and keys.
-A \textit{plaintext}, is text that can be commonly understood within a larger group.
-Given a \textit{key} the encryption function maps a plaintext to some \textit{ciphertext}, which can only be understood by authorized parties.
+A \textit{plaintext} is text that can be commonly understood within a larger group.
+Given a \textit{key}, the encryption function maps a plaintext to some \textit{ciphertext}, which can only be understood by authorized parties.
 The decryption function similarly maps a ciphertext back to its corresponding plaintext, given an appropiate key.
@@
 This allows for secure computation by performing operations in the ciphertext domain.
-It is important to note that the operations in the plaintext space and ciphertext space need not be the same.
-A simple operation in the plaintext space may require a computationally intensive operation in the ciphertext space.
-
-% \subsection{Partially Homomorphic Cryptosystems}
-% A cryptosystem is called \textit{partially homomorphic} if it only admits limited types of operations on ciphtertexts.
-We present two partially homomorphic encryption (PHE) schemes: the Paillier cryptosystem and the DGK cryptosystem.
-We then show how to use these PHE schemes for secure floating-point computation using two-party protocols.
+It is important to note that a simple operation in the plaintext space may require a computationally intensive operation in the ciphertext space.
 
@@
 % \end{table*}
-\subsection{Paillier and DGK Cryptosystems}
+\subsection{The Paillier and DGK Cryptosystems}
 The Paillier cryptosystem \cite{stern_public-key_1999}, developed by Pascal Paillier, is a probabilistic encryption scheme which is based on the composite residuosity class problem.
-The scheme has several well--known homomorphic properties.
-Table \ref{tab:paillier_summary} shows the key generation, encryption, and decryption procedures of the Paillier cryptosystem, which encrypts plaintexts in $\mathbb{Z}_n$ as ciphertexts in $\mathbb{Z}_{n^2}$.
+Table \ref{tab:paillier_summary} shows the key generation, encryption, and decryption procedures of the Paillier cryptosystem.
 \begin{table}[ht]
@@
     \begin{tabular}{
-        p{\dimexpr 0.2\linewidth-2\tabcolsep}
-        p{\dimexpr 0.8\linewidth-2\tabcolsep}}
+        p{\dimexpr 0.20\linewidth-2\tabcolsep}
+        p{\dimexpr 0.80\linewidth-2\tabcolsep}}
 		\toprule
@@
         \midrule
-            Key\newline Generation &
+            Generate\newline Keys &
             Let $L(x)$ be the largest integer $v$ greater than zero such that $x-1 \geq vn$.\newline
@@
             \\
-            Encryption &
-            $E(m) = g^m \cdot r^n \mod{n^2}$ 
+            Encrypt &
+            The encryption of a plaintext $m \in  \mathbb{Z}_n$ given the public key is  $E(m) = g^m \cdot r^n \mod{n^2}$, where $r$ is a random integer in $\mathbb{Z}_{n^2}$.
             \\
-            Decryption &
-            $D(c) = L(c^\lambda \bmod n^2) \times (L(g^\lambda \bmod n^2))^{-1} \mod n$ 
+            Decrypt &
+            The decryption of a plaintext $c \in  \mathbb{Z}_{n^2}$ given the private key is $D(c) = L(c^\lambda \bmod n^2) \times (L(g^\lambda \bmod n^2))^{-1} \mod n$. 
             \\
@@
 
-% \paragraph{Homomorphic Properties of the Paillier Cryptosystem}
-% The Paillier cryptosystem supports additive homomorphism as well as the multiplication of a plaintext scalar to an encrypted message.
-These homomorphic properties are used to add a plaintext scalar to a ciphertext, add two ciphertexts, and multiply a ciphertext by a plaintext scalar, respectively.
-They are defined as follows.
-
-For all $m_1,m_2 \in \mathbb{Z}_n$ and $k\in \mathbb{N}$, the following homomorphic properties hold for the Paillier cryptosystem with public key $(g,n)$.
-\begin{align*}
-  D(E(m_1)g^k\bmod n^2) &=(m_1+k)\bmod n\\
-  D(E(m_1)E(m_2)\bmod n^2) &=(m_1+m_2)\bmod n\\
-  D(E(m_1)^k\bmod n^2) &= km_1\bmod n
-\end{align*}
-
-These homomorphic properties are used to add a plaintext to a ciphertext, add two ciphertexts, and multiply a ciphertext by a plaintext scalar, respectively.
+For all plaintexts $m_1,m_2 \in \mathbb{Z}_n$, the following properties hold for the Paillier cryptosystem:
+\begin{align}
+  D(E(m_1)g^{m_2}\bmod n^2) &=(m_1+m_2)\bmod n \label{eq:paillier_ctpluspt} \\ 
+  D(E(m_1)E(m_2)\bmod n^2) &=(m_1+m_2)\bmod n \label{eq:paillier_ctplusct} \\ 
+  D(E(m_1)^{m_2}\bmod n^2) &= m_1m_2\bmod n. \label{eq:paillier_cttimespt}
+\end{align}
+These identities allow for the addition of a ciphertext with a plaintext (Equation \ref{eq:paillier_ctpluspt}), the addition of two ciphertexts (Equation \ref{eq:paillier_ctplusct}), and the multiplication of a ciphertext by a plaintext (Equation \ref{eq:paillier_cttimespt}) under the Paillier cryptosystem.
 
 The DGK cryptosystem was published by Damg{\aa}rd, Geisler, and Kr{\o}igaard in 2007 in an effort to create a secure integer comparison scheme \cite{pieprzyk_efficient_2007, cryptoeprint:2008:321} which is widely used in the literature \cite{veugen_improving_2012}.
- The details of the DGK cryptosystem may be found in Table \ref{tab:dgk_summary}.
-The DGK cryptosystem encrypts plaintexts in $\mathbb{Z}_u$ as ciphertexts in $\mathbb{Z}_n^\ast$, and has homomorphic properties similar to the Paillier cryptosystem.
+Table \ref{tab:dgk_summary} shows the key generation, encryption, and decryption procedures of the DGK cryptosystem.
 
+Similar to the Paillier cryptosystem, for all $m_1,m_2 \in \mathbb{Z}_u$, the following homomorphic properties hold for the DGK cryptosystem:
+\begin{align}
+    D(E(m_1)g^{m_2}) &=(m_1+m_2)\bmod u \label{eq:dgk_ctpluspt}\\
+    D(E(m_1)E(m_2)) &=(m_1+m_2)\bmod u \label{eq:dgk_ctplusct}\\
+    D(E(m_1)^{m_2}) &= m_1m_2\bmod u. \label{eq:dgk_cttimespt},
+\end{align}
+which allow for homomorphic operations similar to to that of the Paillier cryptosystem.
+As the multiplicative homomorphism (Equation \ref{eq:dgk_cttimespt}) was not presented in the original paper, we provide a short proof here.
 \begin{table}[ht]
@@
         \midrule
-            Key\newline Generation &
+            Generate \newline Keys &
             Let $p,q$ be primes such that we can choose two primes $v_p$ and $v_q$ such that $v_p | (p-1)$ and $v_q | (q-1)$, and a small prime $u$ such that $u | (p-1)$ and $u | (q-1)$. \newline
@@
             \\
-            Encryption &
-            $E(m) = g^m \cdot h^r \mod{n}$
+            Encrypt &
+            The encryption of a plaintext $m \in \mathbb{Z}_u$ given the public key is $E(m) = g^m \cdot h^r \mod{n}$, where $r$ is a random integer in $\mathbb{Z}_n$.
             \\
-            Decryption &
-            Compute $c^{v_pv_q} \bmod n$. There is a one-to-one correspondence between this quantity and the plaintexts, so the plaintext can be recovered using a lookup table.
+            Decrypt &
+            To decrypt a ciphertext $c \in \mathbb{Z}_n^\ast$, we compute $c^{v_pv_q} \bmod n$.
+There is a one-to-one correspondence between this quantity and the plaintexts, so the plaintext can be recovered using a lookup table.
             \\
@@
 
-For all $m_1,m_2 \in \mathbb{Z}_u$ and $k\in \mathbb{N}$, the following homomorphic properties hold for the DGK cryptosystem with public key $(n,g,h,u)$.
-\begin{align*}
-    D(E(m_1)g^k) &=(m_1+k)\bmod u\\
-    D(E(m_1)E(m_2)) &=(m_1+m_2)\bmod u\\
-    D(E(m_1)^k) &= km_1\bmod u
-\end{align*}
-
-As the multiplicative homomorphism was not presented in the original paper, we provide a short proof here.
 \begin{theorem}
-    In the DGK cryptosystem with public key $(n,g,h,u)$ and private key $(p,q,v_p,v_q)$, it holds that $D(E(m_1)^k) = km_1\bmod u$.
+    In the DGK cryptosystem with public key $(n,g,h,u)$ and private key $(p,q,v_p,v_q)$, it holds that $D(E(m_1)^{m_2}) = m_1m_2\bmod u$ for all plaintexts $m_1,m_2 \in \mathbb{Z}_u$.
 \end{theorem}
 \begin{proof}
-  Let $m \in \mathbb{Z}_u$ and $k\in \mathbb{N}$.
-  We consider $E(m)^k = (g^m \cdot h^r \bmod{n})^k\bmod n$.
+  Let $m_1,m_2 \in \mathbb{Z}_u$.
+  We note that
   \begin{align*}
-    (g^m \cdot h^r \bmod{n})^k \bmod n
-    &= (g^m \cdot h^r)^k \bmod{n}\\
-    &= (g^m)^k \cdot (h^r)^k \bmod{n}\\
-    &= g^{km} \cdot (h^{kr}) \bmod{n}
+    E(m_1)^{m_2} 
+    &= (g^{m_1} \cdot h^r \bmod{n})^{m_2} \bmod n \\
+    &= (g^{m_1} \cdot h^r)^{m_2} \bmod{n}\\
+    &= g^{m_1m_2} \cdot (h^{m_2r}) \bmod{n}.
   \end{align*}
-  Since $r$ is a random integer, $kr$ is also a random integer, Therefore, $g^{km} \cdot (h^{kr}) \bmod{n} = E(m)^k$ is a valid encryption of the message $km$.
+  Since $r$ is a random integer, $m_2r$ is also a random integer, Therefore, $g^{m_1m_2} \cdot (h^{m_2r}) \bmod{n} = E(m_1)^{m_2}$ is a valid encryption of the message $m_1m_2$.
 \end{proof}
 
-We have shown how the Paillier and DGK cryptosystems have similar homomorphic properties.
-In both cryptosystems, we are able to add a plaintext to a ciphertext, add two ciphertexts, and multiply a ciphertext by a plaintext scalar.
-In order to use these cryptosystems in secure image processing, we require the two schemes to support the encryption and manipulation of floating-point (FP) numbers, which can be done by using an approach shown in~\cite{ziad_cryptoimg:_2016}.
-This approach represents FP numbers using an encrypted mantissa and an unencrypted exponent.
-This representation extends the addition and plaintext multiplication homomorphisms of the Paillier and DGK cryptosystems to floating-point numbers.
+We have shown how the Paillier and DGK cryptosystems have similar homomorphic properties,allowing the addition of integers and multiplication of ciphertexts by plaintexts.
+In order to use these cryptosystems in secure non-linear image processing, we require the two schemes to support the encryption and manipulation of floating-point numbers.
+To do this, we represent floating-point numbers using an encrypted mantissa and an unencrypted exponent, an approach seen in~\cite{ziad_cryptoimg:_2016}.
 
-Table \ref{tab:flop_summary} describes protocols such as division~\cite{boukoros_lightweight_2017}, exponentiation~\cite{hutchison_privacy-preserving_2009}, and multiplication.
-These protocols, used in conjunction with the FP extension, allow for secure floating-point arithmetic~\cite{pcsc-paper}.
+Table \ref{tab:flop_summary} describes two-party protocols which allow a server to perform division~\cite{boukoros_lightweight_2017}, squaring~\cite{hutchison_privacy-preserving_2009}, and multiplication on messages $x$ and $y$ encrypted by a client.
+These protocols, used in conjunction with the floating-point extension, allow for secure floating-point arithmetic~\cite{pcsc-paper}.
 
@@
             The server selects a random number $r$ and sends $E(rx)$ and $E(ry)$ to the client, who can decrypt to obtain $rx$ and $ry$.
-The client then encrypts the quotient and sends $E(rx/ry) = E(x/y)$ to the server.
+The client then computes and encrypts the quotient and sends $E(rx/ry) = E(x/y)$ to the server.
             \\
-            Exponentiation &
+            Squaring &
             The server selects a random number $r$ and computes $E\left(x+r\right)$.
@@
 \textit{HELib} supports arithmetic operations on integer ciphertexts and logical operations on binary ciphertexts.
-Evaluation of operations on 120 inputs in \textit{HELib} was performed in around 4 minutes, with an average of 2 seconds to process a single input~\cite{hutchison_fully_2010,cryptoeprint:2011:566}.
-The \textit{HELib} library has been adapted to Python using the Pyfhel library \cite{pyfhel_2018} maintained by Ibarrondo, Laurent (SAP) and Onen (EURECOM), and licensed under the GNU GPL v3 license.
-\subsection{CryptoImg}
-A paper published in 2009 by Ziad, et al.
-implements privacy-preserving image processing using \textit{CryptoImg}, a library for the Open Source Computer Vision Library (OpenCV)~\cite{bradski_opencv_2000} which implements various homomorphic encryption and image processing routines using the Paillier homomorphic cryptosystem~\cite{ziad_cryptoimg:_2016}.
-The \textit{CryptoImg} library assumed a client-server model wherein a client requests image processing operations from a server.
-A client first encrypts a digital image and sends the image securely to a server, which then operates on the encrypted image without revealing its contents.
-Then the resulting image is sent back to the client, which decrypts the image to recover the desired output.
-\begin{figure}[!ht]
-    \centering
-    \includegraphics[width=0.4\textwidth]{figures/ClientServerModel.png}
-    \caption{Client-server architecture used by \textit{CryptoImg} \cite{ziad_cryptoimg:_2016}}
-    \label{fig:clientserver}
-\end{figure}
-
-The \textit{CryptoImg} library implemented the following image processing operations: image negation, brightness adjustment, spatial filters (for noise reduction, edge detection and sharpening), morphological operations, and histogram equalization.
-
-% For image negation and spatial filters, the protocols specified by \textit{CryptoImg} allow all image processing operations to be performed on the server.
-However, due to limitations in the Paillier cryptosystem, the protocols presented for morphological operations and histogram equalization require both the client and the server to perform image processing calculations, although the server performs a significant portion of the processing.
-
-Ziad, et al.
-also showed experimental results establishing the relatively slow performance of image operations under a homomorphic cryptosystem.
-For instance, while sharpening and applying a Sobel filter each take less than a second when applied to a $512\times 512$ plaintext image, when applied to an encrypted image, sharpening required at least 238.257 seconds, and applying the Sobel filter required at least 147.567 seconds \cite{ziad_cryptoimg:_2016}.
-
-% We now discuss several limitations in the \textit{CryptoImg} study which we focus on for our research.
-First, the \textit{CryptoImg} library was limited in the image intensity transformations it implemented.
-We propose additional protocols to support more computationally intensive intensity transformations.
-% Second, the \textit{CryptoImg} library only considered the Paillier cryptosystem.
-We consider testing the performance of other homomorphic cryptosystems, which differ in their processing time and supported operations.
-
-% Convert to single table
-\subsection{Image Intensity Transformations}
-We represent a digital image $R$ as an $M \times N$ matrix of pixel intensity values, each value in the range $\left[0, L-1\right]$, for some positive integer $L$.
-We denote with $R(x,y)$ the entry at the $x$th row and $y$th column of a matrix $R$.
-An intensity transformation on an image $R$ can be defined as a function $T$ which is applied to every pixel $r$ in $R$.
-The \textit{CryptoImg} library implemented two types of linear intensity transformations: image negation and brightness control. An image negation transformation is defined as
-\begin{equation}
-    T\left(r\right) = L-1-r,
-\end{equation}
-which results in an image similar to a photographic negative~\cite{gonzalez_digital_2008}.
-A brightness control transformation with parameter $v$ is defined as
-\begin{equation}
-    T\left(r,v\right) = r+v.
-\end{equation}
-The above transformations are linear in terms of the input $r$, and are thus simple to implement under a homomorphic cryptosystem.
-
-In this study we extend the range of intensity transformations to non-linear transformations.
-Two common non-linear image transformations are the logarithm transformation and power-law transformation~\cite{gonzalez_digital_2008}.
-
-The logarithm transformation is used to enhance dark pixels or increase the dark details of an image by mapping low intensity values to a wider range of values~\cite{gonzalez_digital_2008}.
-This has the general formula
-\begin{equation}
-    T\left(r\right) = c \log\left(1 + r\right)
-\end{equation}
-where $c$ is a constant.
-The power-law transformation is a family of transformations that have the form
-\begin{equation}
-    T\left(r\right) = c r^{\gamma}
-\end{equation}
-where $c>0$ and $\gamma > 0$.
-A power-law transformation can calibrate the operation of many image capture and output devices such as cameras, printers and displays in a process called \textit{gamma correction}.
-% This ensures reproducibility and accuracy of images being displayed by digital output devices~\cite{gonzalez_digital_2008}.
-
-To implement non-linear intensity transformations using addition and multiplication in a homomorphic system, it is necessary to approximate the logarithm and exponential functions, which may result in higher computational overhead.
-An applicable approximation for the logarithm may be found in \cite{pcsc-paper}.
-% In our software library implementation, we investigate methods required to approximate the logarithm and power functions. 
-Non-linear intensity transformations such as the logarithm transformation have applications in intensity normalization \cite{oravec_illumination_2010}, which is used in some facial recognition algorithms to account for differences in lighting which make facial recognition difficult.
-
-\subsection{Facial Detection and Recognition}
-
-Since simple image operations mentioned earlier can be done within a homomorphic cryptosystem, these operations can be assembled together in order to do more complex operations.
-A prominent application of image processing that often uses complex image operations is \textit{facial recognition}.
-
-Traditional facial recognition algorithms rely on detecting salient features in a face image. One of the popular facial recognition algorithms is \textit{eigenfaces}.
-% Traditional facial recognition algorithms rely on detecting salient features in a face image. Two of the popular facial recognition algorithms are \textit{eigenfaces} and \textit{Haar cascades}.
-
-\subsubsection{Eigenfaces}
-Proposed by Matthew Turk and Alex Pentland, the eigenfaces method uses principal component analysis (PCA) in order to express an input image as a linear combination of eigenfaces \cite{turk_eigenfaces_1991}.
-An \textit{eigenface} is a principal component, or more simply an eigenvector that represents a certain variation between the face images which are taken from the initial training set.
-The number of resulting eigenfaces is equal to the number of face images in the training set.
-
-% In the enrollment process, $M$ face images $\Theta_1, \ldots, \Theta_M$, each of size $p \times q$, are taken in to comprise the initial training set.
-The training images can be represented as vectors of length $N = pq$, where each row of an image is concatenated together.
-
-% The average of the training images, denoted as $\Psi$, is
-% \begin{equation}
-% 	\Psi = \frac{1}{M} \sum_{i=1}^{M} \Theta_i
-% \end{equation}
-
-% The \textit{difference vectors} are then computed as $\Phi_i = \Theta_i - \Psi$. PCA is applied on the covariance matrix of the vectors
-% \begin{equation}
-% 	\mathbf{C} = \frac{1}{M} \sum_{i=1}^M \Phi_i \Phi_i^\top = \frac{1}{M} \mathbf{A}\mathbf{A}^\top,
-% \end{equation}
-% where $\mathbf{A}$ is an $N \times M$ matrix defined by $\left[\Theta_1 \quad \Theta_2 \quad \cdots \quad \Theta_M\right]$, in order to determine the orthonormal eigenvectors \cite{hutchison_privacy-preserving_2009}.
-
-% Directly computing the covariance matrix and then applying PCA will become inefficient for large sizes of $\mathbf{A}$, since computing for $\mathbf{A}\mathbf{A}^\top$ results in an $N \times N$ matrix, which can get drastically large because it is dependent on the size of the image.
-On the other hand, computing for $\mathbf{A}^\top\mathbf{A}$ only results in an $M \times M$ matrix, which is much smaller than the previous one because it is just dependent on the number of face images in the training set.
-Now, we can apply PCA to $\mathbf{A}^\top\mathbf{A}$ along with some post-processing to obtain the eigenvectors \cite{hutchison_privacy-preserving_2009}.
-
-% Instead of getting the eigendecomposition of the covariance matrix by explicitly computing the eigenvalues and eigenvectors of $\mathbf{C}$, we can also apply \textit{singular value decomposition} (SVD) on the matrix $\Phi^\top$.
-This is because SVD works through a divide-and-conquer method which results in greater numerical stability, while eigendecomposition simply uses the traditional QR factorization \cite{nakatsukasa_stable_2013, gu_divide-and-conquer_1995}.
-Upon applying SVD, we now get the eigenvectors $\mathbf{u}_1, \ldots, \mathbf{u}_M$ and their corresponding eigenvalues $\lambda_1, \ldots, \lambda_M$.
-
-% We choose $K$ eigenvectors $\mathbf{u}_1, \ldots, \mathbf{u}_K$ such that it comprises a set associated with the $K$ largest eigenvalues, where $K$ is much smaller than $M$.
-This set is now the \textit{face space}.
-Then, the images $\Theta_1, \ldots, \Theta_K$ are projected onto the face space spanned by the eigenfaces to determine the weight vectors $\Omega_1, \ldots, \Omega_K$.
-
-% To perform the recognition process, the algorithm projects the input image $\Gamma$ onto the face space, and then comparing the projected image $\bar{\Omega} = \mathbf{u}_i\left(\Gamma - \Psi\right)$ with each eigenface in the face space using a metric such as the Euclidean distance.
-Thus it is computed as $d_i = \left\lVert \Omega_i -\bar{\Omega} \right\rVert$ for all $i=1,\ldots,K$, where $\left\lVert \cdot \right\rVert$ denotes the Euclidean norm.
-
-% Then, a match can be reported if the smallest possible distance is smaller than the given threshold value $T$.
-% \newcommand{\argmin}{\mathop{\mathrm{arg\,min}}}
-% \begin{equation}
-% 	\text{ID} = \begin{cases}\argmin_i d_i & \text{if } \min_i d_i \le T \\\emptyset & \text {otherwise}\end{cases}
-% \end{equation}
-
-\subsection{Previous Implementations of Secure Facial Recognition}
-Erkin, et al.
-\cite{hutchison_privacy-preserving_2009} devised a method to incorporate the use of homomorphic cryptosystems into the eigenfaces method.
-In their study, they proposed a two-party system where Alice holds an encrypted image $\left[\Gamma\right]$, while Bob maintains a database of $K$ eigenfaces $\mathbf{u}_1, \ldots, \mathbf{u}_K$, and feature vectors $\Omega_1, \ldots, \Omega_M$ in the clear.
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=0.4\textwidth]{figures/secure_eigenfaces.png}
-    \caption{Diagram of the privacy-preserving facial recognition process \cite{hutchison_privacy-preserving_2009}}
-\end{figure}
-
-In order to ensure privacy, the steps in the eigenfaces algorithm, namely: projection, distance computation, and match finding, are done within the encrypted domain, i.e., using the operations in the Paillier cryptosystem.
-
-Projection is similar to that of the original eigenfaces algorithm, except the operations are replaced with their respective operations in the cryptosystem.
-Distance computation in this version is somewhat different from the original eigenfaces method, in that it deals with the square of the Euclidean distance since the relative order of the distances is only important when comparing these during the match finding step \cite{hutchison_privacy-preserving_2009}.
-\begin{align}
-    d_i &= \left\lVert \Omega_i - \bar{\Omega} \right\rVert ^2 = \sum_{j=1}^{K} \left(\omega_{ij} - \bar{\omega}_j\right)^2 \\
-        &= \underbrace{\sum_{j=1}^{K} \omega_{ij}^2}_{\mathcal{S}_1} + \underbrace{\sum_{j=1}^{K} \left(-2 \omega_{ij} \bar{\omega_j}\right)}_{\mathcal{S}_2} + \underbrace{\sum_{j=1}^{K} \bar{\omega}_{j}^2}_{\mathcal{S}_3}
-\end{align}
-
-Computing for the distances within Paillier would just be multiplying the encrypted sums together.
-\begin{equation}
-	\left[d_i\right] = \left[\mathcal{S}_1\right] \cdot \left[\mathcal{S}_2\right] \cdot \left[\mathcal{S}_3\right]
-\end{equation}
-
-The terms $\left[\mathcal{S}_1\right]$ and $\left[\mathcal{S}_2\right]$ can be easily computed by Bob, since he already knows both $\omega_i$ in the clear and $\left[\bar{\omega}_i\right]$ which is in encrypted form.
-Computing for $\left[\mathcal{S}_3\right]$ is trickier because Bob cannot compute for $\left[\bar{\omega}_i^2\right]$ because pairwise multiplication is not supported in Paillier, that is why Bob needs help from Alice to square a number through a protocol described below \cite{hutchison_privacy-preserving_2009}.
-
-Before Bob sends $\left[\bar{\omega}_i\right]$ to Alice for squaring, he adds a random number $r_i$ to compute $\left[x_i\right] = \left[\bar{\omega}_i + r_i\right] = \left[\bar{\omega}_i\right] \cdot \left[r_i\right]$, where $r_i$ is obviously distinct for every $i$, then sends $\left[x_i\right]$ to Alice.
-She then decrypts it and computes $x_i^2$, and then computes $\mathcal{S}_3^\prime = \sum_{i=1}^{K} x_i^2$, after which she encrypts the sum and sends $\left[\mathcal{S}_3^\prime\right]$ to Bob.
-Now, he can compute for $\left[\mathcal{S}_3\right]$ as follows:
-\begin{equation}
-	\left[\mathcal{S}_3\right] = \left[\mathcal{S}_3^\prime\right] \cdot \prod_{j=1}^{K} \left(\left[\bar{\omega}_j\right]^{-2r_j} \cdot \left[-r_j^2\right]\right)
-\end{equation}
-
-The protocol for squaring a number as described earlier is a workaround for the limitations of Paillier or any other partially homomorphic cryptosystem that only supports addition and scalar multiplication.
-% This can be possibly extended so that operations such as pairwise multiplication and exponentiation are also supported, provided that the protocol involves two parties.
-
-The match-finding step is done by comparing the distances obtained from the previous step to a specified threshold $T$.
-If the minimum distance is smaller than $T$, then a match is found, and the encrypted identity of the match is returned to Alice \cite{hutchison_privacy-preserving_2009}.
-Getting the minimum among the encrypted distances would involve comparing two encrypted numbers, which Paillier does not support.
-Instead, the DGK cryptosystem \cite{pieprzyk_efficient_2007} is used for the comparison protocol.
+% Evaluation of operations on 120 inputs in \textit{HELib} was performed in around 4 minutes, with an average of 2 seconds to process a single input~\cite{hutchison_fully_2010,cryptoeprint:2011:566}. 
+It has also been adapted to Python using the Pyfhel library \cite{pyfhel_2018} maintained by Ibarrondo, Laurent (SAP) and Onen (EURECOM), and licensed under the GNU GPL v3 license.

### 2019-03-18 icmssp-paper/parts/02_02_cryptoimg.tex
Finalize sections 2.1 to 2.3

--- 2019-03-17 icmssp-paper/parts/02_reviewofrelatedliterature.tex
@@
-\section{Review of Related Literature}
-\label{sec:chapter_2}
-\subsection{Homomorphic Cryptosystems}
-A cryptosystem~\cite{bauer_cryptosystem_2005} consists of an encryption function and a decryption function, which operate on plaintexts, ciphertexts and keys.
-A \textit{plaintext}, is text that can be commonly understood within a larger group.
-Given a \textit{key} the encryption function maps a plaintext to some \textit{ciphertext}, which can only be understood by authorized parties.
-The decryption function similarly maps a ciphertext back to its corresponding plaintext, given an appropiate key.
-By sending data as ciphertext and only exposing the corresponding plaintexts to authorized parties who have access to the appropiate keys, secure data transmission can be achieved.
-
-A \textit{homomorphic cryptosystem} allows operations to be performed on recovered plaintexts by performing corresponding operations on ciphertexts.
-This allows for secure computation by performing operations in the ciphertext domain.
-It is important to note that the operations in the plaintext space and ciphertext space need not be the same.
-A simple operation in the plaintext space may require a computationally intensive operation in the ciphertext space.
-
-% \subsection{Partially Homomorphic Cryptosystems}
-% A cryptosystem is called \textit{partially homomorphic} if it only admits limited types of operations on ciphtertexts.
-We present two partially homomorphic encryption (PHE) schemes: the Paillier cryptosystem and the DGK cryptosystem.
-We then show how to use these PHE schemes for secure floating-point computation using two-party protocols.
-
-% big table to summarize Paillier and DGK
-% \begin{table*}[ht]
-% 	\caption{Summary of partially homomorphic cryptosystems}
-% 	\label{tab:phe_summary}
-%     \begin{tabular}{
-%         p{\dimexpr 0.2\linewidth-2\tabcolsep}
-%         p{\dimexpr 0.4\linewidth-2\tabcolsep}
-%         p{\dimexpr 0.4\linewidth-2\tabcolsep}}
-% 		\toprule
-% 		 & Paillier & DGK\\
-%         \midrule
-%             Plaintext space &
-%             $\mathbb{Z}_n$ &
-%             $\mathbb{Z}_u$ 
-%             \\
-%             Ciphertext space &
-%             $\mathbb{Z}_{n^2}$ &
-%             $\mathbb{Z}^*_n$
-%             \\
-%             Key generation &
-%             Define a function $L(x)$ as the largest integer $v$ greater than zero such that $x-1 \geq vn$.\newline
-%             Choose two large primes $p$ and $q$, and set $n = pq, \lambda = \mathrm{lcm}(p-1,q-1)$.\newline
-%             Select an integer $g$, $0\leq g \leq n^2$ such that $\mathrm{gcd}(L(g^\lambda \bmod n^2), n) = 1$\newline
-%             The public key as $(g,n)$ and the private key $(p,q)$
-%             &
-%             Let $p,q$ be primes such that we can choose two primes $v_p$ and $v_q$ such that $v_p | (p-1)$ and $v_q | (q-1)$, and a small prime $u$ such that $u | (p-1)$ and $u | (q-1)$. \newline
-%             Denote $n = pq$. \newline
-%             Choose $g$ to be an integer of order $uv_pv_q$ and $h$ to be of order $v_pv_q$.\newline
-%             The public key is $(n,g,h,u)$ and the private key is $(p,q,v_p,v_q)$.
-%             \\
-%             Encryption function &
-%             $E(m) = g^m \cdot r^n \mod{n^2}$ &
-%             $E(m) = g^m \cdot h^r \mod{n}$
-%             \\
-%             Decryption function &
-%             $D(c) = L(c^\lambda \bmod n^2) \times (L(g^\lambda \bmod n^2))^{-1} \mod n$ &
-%             Compute $c^{v_pv_q} \bmod n$. There is a one-to-one correspondence between this quantity and the plaintexts.
-%             \\
-% 	    \bottomrule
-%     \end{tabular}
-% \end{table*}
-\subsection{Paillier and DGK Cryptosystems}
-The Paillier cryptosystem \cite{stern_public-key_1999}, developed by Pascal Paillier, is a probabilistic encryption scheme which is based on the composite residuosity class problem.
-The scheme has several well--known homomorphic properties.
-Table \ref{tab:paillier_summary} shows the key generation, encryption, and decryption procedures of the Paillier cryptosystem, which encrypts plaintexts in $\mathbb{Z}_n$ as ciphertexts in $\mathbb{Z}_{n^2}$.
-\begin{table}[ht]
-	\caption{The Paillier cryptosystem}
-	\label{tab:paillier_summary}
-    \begin{tabular}{
-        p{\dimexpr 0.2\linewidth-2\tabcolsep}
-        p{\dimexpr 0.8\linewidth-2\tabcolsep}}
-		\toprule
-		Step & Description\\
-        \midrule
-            Key\newline Generation &
-            Let $L(x)$ be the largest integer $v$ greater than zero such that $x-1 \geq vn$.\newline
-            Choose two large primes $p$ and $q$, and set $n = pq$, and $ \lambda = \mathrm{lcm}(p-1,q-1)$.\newline
-            Select an integer $g$, $0\leq g \leq n^2$ such that $\mathrm{gcd}(L(g^\lambda \bmod n^2), n) = 1$\newline
-            The public key as $(g,n)$ and the private key is $(p,q)$.
-            \\
-            Encryption &
-            $E(m) = g^m \cdot r^n \mod{n^2}$ 
-            \\
-            Decryption &
-            $D(c) = L(c^\lambda \bmod n^2) \times (L(g^\lambda \bmod n^2))^{-1} \mod n$ 
-            \\
-	    \bottomrule
-    \end{tabular}
-\end{table}
-% The scheme allows for the encryption and decryption of integer messages, and is known to be additively homomorphic.
-% We now state the encryption and decryption algorithms of the Paillier cryptosystem and its homomorphic properties.
-
-% \paragraph{Key Generation}
-% We first define a function $L(x)$ as the largest integer $v$ greater than zero such that $x-1 \geq vn$.
-% We choose two large primes $p$ and $q$, and set $n = pq, \lambda = \mathrm{lcm}(p-1,q-1)$.
-% Then we select an integer $g$, $0\leq g \leq n^2$ such that $\mathrm{gcd}(L(g^\lambda \bmod n^2), n) = 1$.
-% We denote the public key as $(g,n)$ and the private key $(p,q)$.
-
-% \paragraph{Encryption and Decryption}
-% The encryption function to encrypt a plaintext $m \in \mathbb{Z}_n$ given a public key $(g,n)$ is defined as
-% \begin{align*}
-%   E(m) = g^m \cdot r^n \mod{n^2},
-% \end{align*}
-% where $r$ is a random non-negative integer less than $n^2$.
-
-% The decryption function to decrypt a ciphertext $c \in \mathbb{Z}^\ast_{n^2}$ given a private key $(p,q)$ is defined as:
-% \begin{align*}
-%   D(c) = L(c^\lambda \bmod n^2) \times (L(g^\lambda \bmod n^2))^{-1} \mod n
-% \end{align*}
-
-% \paragraph{Homomorphic Properties of the Paillier Cryptosystem}
-% The Paillier cryptosystem supports additive homomorphism as well as the multiplication of a plaintext scalar to an encrypted message.
-These homomorphic properties are used to add a plaintext scalar to a ciphertext, add two ciphertexts, and multiply a ciphertext by a plaintext scalar, respectively.
-They are defined as follows.
-
-For all $m_1,m_2 \in \mathbb{Z}_n$ and $k\in \mathbb{N}$, the following homomorphic properties hold for the Paillier cryptosystem with public key $(g,n)$.
-\begin{align*}
-  D(E(m_1)g^k\bmod n^2) &=(m_1+k)\bmod n\\
-  D(E(m_1)E(m_2)\bmod n^2) &=(m_1+m_2)\bmod n\\
-  D(E(m_1)^k\bmod n^2) &= km_1\bmod n
-\end{align*}
-
-These homomorphic properties are used to add a plaintext to a ciphertext, add two ciphertexts, and multiply a ciphertext by a plaintext scalar, respectively.
-
-The DGK cryptosystem was published by Damg{\aa}rd, Geisler, and Kr{\o}igaard in 2007 in an effort to create a secure integer comparison scheme \cite{pieprzyk_efficient_2007, cryptoeprint:2008:321} which is widely used in the literature \cite{veugen_improving_2012}.
- The details of the DGK cryptosystem may be found in Table \ref{tab:dgk_summary}.
-The DGK cryptosystem encrypts plaintexts in $\mathbb{Z}_u$ as ciphertexts in $\mathbb{Z}_n^\ast$, and has homomorphic properties similar to the Paillier cryptosystem.
-
-\begin{table}[ht]
-	\caption{The DGK cryptosystem}
-	\label{tab:dgk_summary}
-    \begin{tabular}{
-        p{\dimexpr 0.2\linewidth-2\tabcolsep}
-        p{\dimexpr 0.8\linewidth-2\tabcolsep}}
-		\toprule
-		Step & Description\\
-        \midrule
-            Key\newline Generation &
-            Let $p,q$ be primes such that we can choose two primes $v_p$ and $v_q$ such that $v_p | (p-1)$ and $v_q | (q-1)$, and a small prime $u$ such that $u | (p-1)$ and $u | (q-1)$. \newline
-            Denote $n = pq$. \newline
-            Choose $g$ to be an integer of order $uv_pv_q$ and $h$ to be of order $v_pv_q$.\newline
-            The public key is $(n,g,h,u)$ and the private key is $(p,q,v_p,v_q)$.
-            \\
-            Encryption &
-            $E(m) = g^m \cdot h^r \mod{n}$
-            \\
-            Decryption &
-            Compute $c^{v_pv_q} \bmod n$. There is a one-to-one correspondence between this quantity and the plaintexts, so the plaintext can be recovered using a lookup table.
-            \\
-	    \bottomrule
-    \end{tabular}
-\end{table}
-
-For all $m_1,m_2 \in \mathbb{Z}_u$ and $k\in \mathbb{N}$, the following homomorphic properties hold for the DGK cryptosystem with public key $(n,g,h,u)$.
-\begin{align*}
-    D(E(m_1)g^k) &=(m_1+k)\bmod u\\
-    D(E(m_1)E(m_2)) &=(m_1+m_2)\bmod u\\
-    D(E(m_1)^k) &= km_1\bmod u
-\end{align*}
-
-As the multiplicative homomorphism was not presented in the original paper, we provide a short proof here.
-\begin{theorem}
-    In the DGK cryptosystem with public key $(n,g,h,u)$ and private key $(p,q,v_p,v_q)$, it holds that $D(E(m_1)^k) = km_1\bmod u$.
-\end{theorem}
-\begin{proof}
-  Let $m \in \mathbb{Z}_u$ and $k\in \mathbb{N}$.
-  We consider $E(m)^k = (g^m \cdot h^r \bmod{n})^k\bmod n$.
-  \begin{align*}
-    (g^m \cdot h^r \bmod{n})^k \bmod n
-    &= (g^m \cdot h^r)^k \bmod{n}\\
-    &= (g^m)^k \cdot (h^r)^k \bmod{n}\\
-    &= g^{km} \cdot (h^{kr}) \bmod{n}
-  \end{align*}
-  Since $r$ is a random integer, $kr$ is also a random integer, Therefore, $g^{km} \cdot (h^{kr}) \bmod{n} = E(m)^k$ is a valid encryption of the message $km$.
-\end{proof}
-
-We have shown how the Paillier and DGK cryptosystems have similar homomorphic properties.
-In both cryptosystems, we are able to add a plaintext to a ciphertext, add two ciphertexts, and multiply a ciphertext by a plaintext scalar.
-In order to use these cryptosystems in secure image processing, we require the two schemes to support the encryption and manipulation of floating-point (FP) numbers, which can be done by using an approach shown in~\cite{ziad_cryptoimg:_2016}.
-This approach represents FP numbers using an encrypted mantissa and an unencrypted exponent.
-This representation extends the addition and plaintext multiplication homomorphisms of the Paillier and DGK cryptosystems to floating-point numbers.
-
-Table \ref{tab:flop_summary} describes protocols such as division~\cite{boukoros_lightweight_2017}, exponentiation~\cite{hutchison_privacy-preserving_2009}, and multiplication.
-These protocols, used in conjunction with the FP extension, allow for secure floating-point arithmetic~\cite{pcsc-paper}.
-
-\begin{table}[ht]
-	\caption{Two-party FP protocols}
-	\label{tab:flop_summary}
-    \begin{tabular}{
-        p{\dimexpr 0.25\linewidth-2\tabcolsep}
-        p{\dimexpr 0.75\linewidth-2\tabcolsep}}
-		\toprule
-		Operation & Protocol\\
-        \midrule
-            Division &
-            The server selects a random number $r$ and sends $E(rx)$ and $E(ry)$ to the client, who can decrypt to obtain $rx$ and $ry$.
-The client then encrypts the quotient and sends $E(rx/ry) = E(x/y)$ to the server.
-            \\
-            Exponentiation &
-            The server selects a random number $r$ and computes $E\left(x+r\right)$.
-The server sends $E(x+r)$  to the client, who can decrypt to obtain $x+r$.
-The client then encrypts and sends $E((x+r)^2)$ to the server.
-The server then computes $E\left(\left(x+r\right)^2\right)E\left(-2rx + r^2\right) = E\left(x^2\right)$.
-            \\
-            Multiplication &
-            The server obtains $E(x^2)$, $E(y^2)$, and $E((x+y)^2)$ using the exponentiation protocol.
-It can then compute $\frac{1}{2}E\left(\left(x+y\right)^2\right)E\left(x^2\right)^{-1}E\left(y^2\right)^{-1} = E\left(xy\right)$.\\
-	    \bottomrule
-    \end{tabular}
-\end{table}
-\subsection{The BGV Cryptosystem}
-The BGV (Brakerski--Gentry--Vaikuntanathan) cryptosystem \cite{cryptoeprint:2011:277} is a fully homomorphic cryptosystem created based on the ring-learning with error problem.
-A \textit{fully homomorphic cryptosytem} allows aribitrary computation on encrypted data.
-However, they are known to be significantly slower than partially homomorphic cryptosytems; improving the efficiency of fully homomorphic cryptosytems is an active area of research \cite{sen_homomorphic_2013}.
-The details regarding the construction of the BGV cryptosystem are beyond the scope of this paper.
-
-For this study, we will be using \textit{HELib}~\cite{garay_algorithms_2014}, an open-source library which implements the BGV cryptosystem with optimizations.
-\textit{HELib} supports arithmetic operations on integer ciphertexts and logical operations on binary ciphertexts.
-Evaluation of operations on 120 inputs in \textit{HELib} was performed in around 4 minutes, with an average of 2 seconds to process a single input~\cite{hutchison_fully_2010,cryptoeprint:2011:566}.
-The \textit{HELib} library has been adapted to Python using the Pyfhel library \cite{pyfhel_2018} maintained by Ibarrondo, Laurent (SAP) and Onen (EURECOM), and licensed under the GNU GPL v3 license.
 \subsection{CryptoImg}
@@
 A client first encrypts a digital image and sends the image securely to a server, which then operates on the encrypted image without revealing its contents.
-Then the resulting image is sent back to the client, which decrypts the image to recover the desired output.
+The resulting image is sent back to the client, which decrypts the image to recover the desired output.
 \begin{figure}[!ht]
@@
 Non-linear intensity transformations such as the logarithm transformation have applications in intensity normalization \cite{oravec_illumination_2010}, which is used in some facial recognition algorithms to account for differences in lighting which make facial recognition difficult.
-
-\subsection{Facial Detection and Recognition}
-
-Since simple image operations mentioned earlier can be done within a homomorphic cryptosystem, these operations can be assembled together in order to do more complex operations.
-A prominent application of image processing that often uses complex image operations is \textit{facial recognition}.
-
-Traditional facial recognition algorithms rely on detecting salient features in a face image. One of the popular facial recognition algorithms is \textit{eigenfaces}.
-% Traditional facial recognition algorithms rely on detecting salient features in a face image. Two of the popular facial recognition algorithms are \textit{eigenfaces} and \textit{Haar cascades}.
-
-\subsubsection{Eigenfaces}
-Proposed by Matthew Turk and Alex Pentland, the eigenfaces method uses principal component analysis (PCA) in order to express an input image as a linear combination of eigenfaces \cite{turk_eigenfaces_1991}.
-An \textit{eigenface} is a principal component, or more simply an eigenvector that represents a certain variation between the face images which are taken from the initial training set.
-The number of resulting eigenfaces is equal to the number of face images in the training set.
-
-% In the enrollment process, $M$ face images $\Theta_1, \ldots, \Theta_M$, each of size $p \times q$, are taken in to comprise the initial training set.
-The training images can be represented as vectors of length $N = pq$, where each row of an image is concatenated together.
-
-% The average of the training images, denoted as $\Psi$, is
-% \begin{equation}
-% 	\Psi = \frac{1}{M} \sum_{i=1}^{M} \Theta_i
-% \end{equation}
-
-% The \textit{difference vectors} are then computed as $\Phi_i = \Theta_i - \Psi$. PCA is applied on the covariance matrix of the vectors
-% \begin{equation}
-% 	\mathbf{C} = \frac{1}{M} \sum_{i=1}^M \Phi_i \Phi_i^\top = \frac{1}{M} \mathbf{A}\mathbf{A}^\top,
-% \end{equation}
-% where $\mathbf{A}$ is an $N \times M$ matrix defined by $\left[\Theta_1 \quad \Theta_2 \quad \cdots \quad \Theta_M\right]$, in order to determine the orthonormal eigenvectors \cite{hutchison_privacy-preserving_2009}.
-
-% Directly computing the covariance matrix and then applying PCA will become inefficient for large sizes of $\mathbf{A}$, since computing for $\mathbf{A}\mathbf{A}^\top$ results in an $N \times N$ matrix, which can get drastically large because it is dependent on the size of the image.
-On the other hand, computing for $\mathbf{A}^\top\mathbf{A}$ only results in an $M \times M$ matrix, which is much smaller than the previous one because it is just dependent on the number of face images in the training set.
-Now, we can apply PCA to $\mathbf{A}^\top\mathbf{A}$ along with some post-processing to obtain the eigenvectors \cite{hutchison_privacy-preserving_2009}.
-
-% Instead of getting the eigendecomposition of the covariance matrix by explicitly computing the eigenvalues and eigenvectors of $\mathbf{C}$, we can also apply \textit{singular value decomposition} (SVD) on the matrix $\Phi^\top$.
-This is because SVD works through a divide-and-conquer method which results in greater numerical stability, while eigendecomposition simply uses the traditional QR factorization \cite{nakatsukasa_stable_2013, gu_divide-and-conquer_1995}.
-Upon applying SVD, we now get the eigenvectors $\mathbf{u}_1, \ldots, \mathbf{u}_M$ and their corresponding eigenvalues $\lambda_1, \ldots, \lambda_M$.
-
-% We choose $K$ eigenvectors $\mathbf{u}_1, \ldots, \mathbf{u}_K$ such that it comprises a set associated with the $K$ largest eigenvalues, where $K$ is much smaller than $M$.
-This set is now the \textit{face space}.
-Then, the images $\Theta_1, \ldots, \Theta_K$ are projected onto the face space spanned by the eigenfaces to determine the weight vectors $\Omega_1, \ldots, \Omega_K$.
-
-% To perform the recognition process, the algorithm projects the input image $\Gamma$ onto the face space, and then comparing the projected image $\bar{\Omega} = \mathbf{u}_i\left(\Gamma - \Psi\right)$ with each eigenface in the face space using a metric such as the Euclidean distance.
-Thus it is computed as $d_i = \left\lVert \Omega_i -\bar{\Omega} \right\rVert$ for all $i=1,\ldots,K$, where $\left\lVert \cdot \right\rVert$ denotes the Euclidean norm.
-
-% Then, a match can be reported if the smallest possible distance is smaller than the given threshold value $T$.
-% \newcommand{\argmin}{\mathop{\mathrm{arg\,min}}}
-% \begin{equation}
-% 	\text{ID} = \begin{cases}\argmin_i d_i & \text{if } \min_i d_i \le T \\\emptyset & \text {otherwise}\end{cases}
-% \end{equation}
-
-\subsection{Previous Implementations of Secure Facial Recognition}
-Erkin, et al.
-\cite{hutchison_privacy-preserving_2009} devised a method to incorporate the use of homomorphic cryptosystems into the eigenfaces method.
-In their study, they proposed a two-party system where Alice holds an encrypted image $\left[\Gamma\right]$, while Bob maintains a database of $K$ eigenfaces $\mathbf{u}_1, \ldots, \mathbf{u}_K$, and feature vectors $\Omega_1, \ldots, \Omega_M$ in the clear.
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=0.4\textwidth]{figures/secure_eigenfaces.png}
-    \caption{Diagram of the privacy-preserving facial recognition process \cite{hutchison_privacy-preserving_2009}}
-\end{figure}
-
-In order to ensure privacy, the steps in the eigenfaces algorithm, namely: projection, distance computation, and match finding, are done within the encrypted domain, i.e., using the operations in the Paillier cryptosystem.
-
-Projection is similar to that of the original eigenfaces algorithm, except the operations are replaced with their respective operations in the cryptosystem.
-Distance computation in this version is somewhat different from the original eigenfaces method, in that it deals with the square of the Euclidean distance since the relative order of the distances is only important when comparing these during the match finding step \cite{hutchison_privacy-preserving_2009}.
-\begin{align}
-    d_i &= \left\lVert \Omega_i - \bar{\Omega} \right\rVert ^2 = \sum_{j=1}^{K} \left(\omega_{ij} - \bar{\omega}_j\right)^2 \\
-        &= \underbrace{\sum_{j=1}^{K} \omega_{ij}^2}_{\mathcal{S}_1} + \underbrace{\sum_{j=1}^{K} \left(-2 \omega_{ij} \bar{\omega_j}\right)}_{\mathcal{S}_2} + \underbrace{\sum_{j=1}^{K} \bar{\omega}_{j}^2}_{\mathcal{S}_3}
-\end{align}
-
-Computing for the distances within Paillier would just be multiplying the encrypted sums together.
-\begin{equation}
-	\left[d_i\right] = \left[\mathcal{S}_1\right] \cdot \left[\mathcal{S}_2\right] \cdot \left[\mathcal{S}_3\right]
-\end{equation}
-
-The terms $\left[\mathcal{S}_1\right]$ and $\left[\mathcal{S}_2\right]$ can be easily computed by Bob, since he already knows both $\omega_i$ in the clear and $\left[\bar{\omega}_i\right]$ which is in encrypted form.
-Computing for $\left[\mathcal{S}_3\right]$ is trickier because Bob cannot compute for $\left[\bar{\omega}_i^2\right]$ because pairwise multiplication is not supported in Paillier, that is why Bob needs help from Alice to square a number through a protocol described below \cite{hutchison_privacy-preserving_2009}.
-
-Before Bob sends $\left[\bar{\omega}_i\right]$ to Alice for squaring, he adds a random number $r_i$ to compute $\left[x_i\right] = \left[\bar{\omega}_i + r_i\right] = \left[\bar{\omega}_i\right] \cdot \left[r_i\right]$, where $r_i$ is obviously distinct for every $i$, then sends $\left[x_i\right]$ to Alice.
-She then decrypts it and computes $x_i^2$, and then computes $\mathcal{S}_3^\prime = \sum_{i=1}^{K} x_i^2$, after which she encrypts the sum and sends $\left[\mathcal{S}_3^\prime\right]$ to Bob.
-Now, he can compute for $\left[\mathcal{S}_3\right]$ as follows:
-\begin{equation}
-	\left[\mathcal{S}_3\right] = \left[\mathcal{S}_3^\prime\right] \cdot \prod_{j=1}^{K} \left(\left[\bar{\omega}_j\right]^{-2r_j} \cdot \left[-r_j^2\right]\right)
-\end{equation}
-
-The protocol for squaring a number as described earlier is a workaround for the limitations of Paillier or any other partially homomorphic cryptosystem that only supports addition and scalar multiplication.
-% This can be possibly extended so that operations such as pairwise multiplication and exponentiation are also supported, provided that the protocol involves two parties.
-
-The match-finding step is done by comparing the distances obtained from the previous step to a specified threshold $T$.
-If the minimum distance is smaller than $T$, then a match is found, and the encrypted identity of the match is returned to Alice \cite{hutchison_privacy-preserving_2009}.
-Getting the minimum among the encrypted distances would involve comparing two encrypted numbers, which Paillier does not support.
-Instead, the DGK cryptosystem \cite{pieprzyk_efficient_2007} is used for the comparison protocol.

### 2019-03-18 icmssp-paper/parts/02_03_facialrecognition.tex
Finalize sections 2.1 to 2.3

--- 2019-03-17 icmssp-paper/parts/02_reviewofrelatedliterature.tex
@@
-\section{Review of Related Literature}
-\label{sec:chapter_2}
-\subsection{Homomorphic Cryptosystems}
-A cryptosystem~\cite{bauer_cryptosystem_2005} consists of an encryption function and a decryption function, which operate on plaintexts, ciphertexts and keys.
-A \textit{plaintext}, is text that can be commonly understood within a larger group.
-Given a \textit{key} the encryption function maps a plaintext to some \textit{ciphertext}, which can only be understood by authorized parties.
-The decryption function similarly maps a ciphertext back to its corresponding plaintext, given an appropiate key.
-By sending data as ciphertext and only exposing the corresponding plaintexts to authorized parties who have access to the appropiate keys, secure data transmission can be achieved.
-
-A \textit{homomorphic cryptosystem} allows operations to be performed on recovered plaintexts by performing corresponding operations on ciphertexts.
-This allows for secure computation by performing operations in the ciphertext domain.
-It is important to note that the operations in the plaintext space and ciphertext space need not be the same.
-A simple operation in the plaintext space may require a computationally intensive operation in the ciphertext space.
-
-% \subsection{Partially Homomorphic Cryptosystems}
-% A cryptosystem is called \textit{partially homomorphic} if it only admits limited types of operations on ciphtertexts.
-We present two partially homomorphic encryption (PHE) schemes: the Paillier cryptosystem and the DGK cryptosystem.
-We then show how to use these PHE schemes for secure floating-point computation using two-party protocols.
-
-% big table to summarize Paillier and DGK
-% \begin{table*}[ht]
-% 	\caption{Summary of partially homomorphic cryptosystems}
-% 	\label{tab:phe_summary}
-%     \begin{tabular}{
-%         p{\dimexpr 0.2\linewidth-2\tabcolsep}
-%         p{\dimexpr 0.4\linewidth-2\tabcolsep}
-%         p{\dimexpr 0.4\linewidth-2\tabcolsep}}
-% 		\toprule
-% 		 & Paillier & DGK\\
-%         \midrule
-%             Plaintext space &
-%             $\mathbb{Z}_n$ &
-%             $\mathbb{Z}_u$ 
-%             \\
-%             Ciphertext space &
-%             $\mathbb{Z}_{n^2}$ &
-%             $\mathbb{Z}^*_n$
-%             \\
-%             Key generation &
-%             Define a function $L(x)$ as the largest integer $v$ greater than zero such that $x-1 \geq vn$.\newline
-%             Choose two large primes $p$ and $q$, and set $n = pq, \lambda = \mathrm{lcm}(p-1,q-1)$.\newline
-%             Select an integer $g$, $0\leq g \leq n^2$ such that $\mathrm{gcd}(L(g^\lambda \bmod n^2), n) = 1$\newline
-%             The public key as $(g,n)$ and the private key $(p,q)$
-%             &
-%             Let $p,q$ be primes such that we can choose two primes $v_p$ and $v_q$ such that $v_p | (p-1)$ and $v_q | (q-1)$, and a small prime $u$ such that $u | (p-1)$ and $u | (q-1)$. \newline
-%             Denote $n = pq$. \newline
-%             Choose $g$ to be an integer of order $uv_pv_q$ and $h$ to be of order $v_pv_q$.\newline
-%             The public key is $(n,g,h,u)$ and the private key is $(p,q,v_p,v_q)$.
-%             \\
-%             Encryption function &
-%             $E(m) = g^m \cdot r^n \mod{n^2}$ &
-%             $E(m) = g^m \cdot h^r \mod{n}$
-%             \\
-%             Decryption function &
-%             $D(c) = L(c^\lambda \bmod n^2) \times (L(g^\lambda \bmod n^2))^{-1} \mod n$ &
-%             Compute $c^{v_pv_q} \bmod n$. There is a one-to-one correspondence between this quantity and the plaintexts.
-%             \\
-% 	    \bottomrule
-%     \end{tabular}
-% \end{table*}
-\subsection{Paillier and DGK Cryptosystems}
-The Paillier cryptosystem \cite{stern_public-key_1999}, developed by Pascal Paillier, is a probabilistic encryption scheme which is based on the composite residuosity class problem.
-The scheme has several well--known homomorphic properties.
-Table \ref{tab:paillier_summary} shows the key generation, encryption, and decryption procedures of the Paillier cryptosystem, which encrypts plaintexts in $\mathbb{Z}_n$ as ciphertexts in $\mathbb{Z}_{n^2}$.
-\begin{table}[ht]
-	\caption{The Paillier cryptosystem}
-	\label{tab:paillier_summary}
-    \begin{tabular}{
-        p{\dimexpr 0.2\linewidth-2\tabcolsep}
-        p{\dimexpr 0.8\linewidth-2\tabcolsep}}
-		\toprule
-		Step & Description\\
-        \midrule
-            Key\newline Generation &
-            Let $L(x)$ be the largest integer $v$ greater than zero such that $x-1 \geq vn$.\newline
-            Choose two large primes $p$ and $q$, and set $n = pq$, and $ \lambda = \mathrm{lcm}(p-1,q-1)$.\newline
-            Select an integer $g$, $0\leq g \leq n^2$ such that $\mathrm{gcd}(L(g^\lambda \bmod n^2), n) = 1$\newline
-            The public key as $(g,n)$ and the private key is $(p,q)$.
-            \\
-            Encryption &
-            $E(m) = g^m \cdot r^n \mod{n^2}$ 
-            \\
-            Decryption &
-            $D(c) = L(c^\lambda \bmod n^2) \times (L(g^\lambda \bmod n^2))^{-1} \mod n$ 
-            \\
-	    \bottomrule
-    \end{tabular}
-\end{table}
-% The scheme allows for the encryption and decryption of integer messages, and is known to be additively homomorphic.
-% We now state the encryption and decryption algorithms of the Paillier cryptosystem and its homomorphic properties.
-
-% \paragraph{Key Generation}
-% We first define a function $L(x)$ as the largest integer $v$ greater than zero such that $x-1 \geq vn$.
-% We choose two large primes $p$ and $q$, and set $n = pq, \lambda = \mathrm{lcm}(p-1,q-1)$.
-% Then we select an integer $g$, $0\leq g \leq n^2$ such that $\mathrm{gcd}(L(g^\lambda \bmod n^2), n) = 1$.
-% We denote the public key as $(g,n)$ and the private key $(p,q)$.
-
-% \paragraph{Encryption and Decryption}
-% The encryption function to encrypt a plaintext $m \in \mathbb{Z}_n$ given a public key $(g,n)$ is defined as
-% \begin{align*}
-%   E(m) = g^m \cdot r^n \mod{n^2},
-% \end{align*}
-% where $r$ is a random non-negative integer less than $n^2$.
-
-% The decryption function to decrypt a ciphertext $c \in \mathbb{Z}^\ast_{n^2}$ given a private key $(p,q)$ is defined as:
-% \begin{align*}
-%   D(c) = L(c^\lambda \bmod n^2) \times (L(g^\lambda \bmod n^2))^{-1} \mod n
-% \end{align*}
-
-% \paragraph{Homomorphic Properties of the Paillier Cryptosystem}
-% The Paillier cryptosystem supports additive homomorphism as well as the multiplication of a plaintext scalar to an encrypted message.
-These homomorphic properties are used to add a plaintext scalar to a ciphertext, add two ciphertexts, and multiply a ciphertext by a plaintext scalar, respectively.
-They are defined as follows.
-
-For all $m_1,m_2 \in \mathbb{Z}_n$ and $k\in \mathbb{N}$, the following homomorphic properties hold for the Paillier cryptosystem with public key $(g,n)$.
-\begin{align*}
-  D(E(m_1)g^k\bmod n^2) &=(m_1+k)\bmod n\\
-  D(E(m_1)E(m_2)\bmod n^2) &=(m_1+m_2)\bmod n\\
-  D(E(m_1)^k\bmod n^2) &= km_1\bmod n
-\end{align*}
-
-These homomorphic properties are used to add a plaintext to a ciphertext, add two ciphertexts, and multiply a ciphertext by a plaintext scalar, respectively.
-
-The DGK cryptosystem was published by Damg{\aa}rd, Geisler, and Kr{\o}igaard in 2007 in an effort to create a secure integer comparison scheme \cite{pieprzyk_efficient_2007, cryptoeprint:2008:321} which is widely used in the literature \cite{veugen_improving_2012}.
- The details of the DGK cryptosystem may be found in Table \ref{tab:dgk_summary}.
-The DGK cryptosystem encrypts plaintexts in $\mathbb{Z}_u$ as ciphertexts in $\mathbb{Z}_n^\ast$, and has homomorphic properties similar to the Paillier cryptosystem.
-
-\begin{table}[ht]
-	\caption{The DGK cryptosystem}
-	\label{tab:dgk_summary}
-    \begin{tabular}{
-        p{\dimexpr 0.2\linewidth-2\tabcolsep}
-        p{\dimexpr 0.8\linewidth-2\tabcolsep}}
-		\toprule
-		Step & Description\\
-        \midrule
-            Key\newline Generation &
-            Let $p,q$ be primes such that we can choose two primes $v_p$ and $v_q$ such that $v_p | (p-1)$ and $v_q | (q-1)$, and a small prime $u$ such that $u | (p-1)$ and $u | (q-1)$. \newline
-            Denote $n = pq$. \newline
-            Choose $g$ to be an integer of order $uv_pv_q$ and $h$ to be of order $v_pv_q$.\newline
-            The public key is $(n,g,h,u)$ and the private key is $(p,q,v_p,v_q)$.
-            \\
-            Encryption &
-            $E(m) = g^m \cdot h^r \mod{n}$
-            \\
-            Decryption &
-            Compute $c^{v_pv_q} \bmod n$. There is a one-to-one correspondence between this quantity and the plaintexts, so the plaintext can be recovered using a lookup table.
-            \\
-	    \bottomrule
-    \end{tabular}
-\end{table}
-
-For all $m_1,m_2 \in \mathbb{Z}_u$ and $k\in \mathbb{N}$, the following homomorphic properties hold for the DGK cryptosystem with public key $(n,g,h,u)$.
-\begin{align*}
-    D(E(m_1)g^k) &=(m_1+k)\bmod u\\
-    D(E(m_1)E(m_2)) &=(m_1+m_2)\bmod u\\
-    D(E(m_1)^k) &= km_1\bmod u
-\end{align*}
-
-As the multiplicative homomorphism was not presented in the original paper, we provide a short proof here.
-\begin{theorem}
-    In the DGK cryptosystem with public key $(n,g,h,u)$ and private key $(p,q,v_p,v_q)$, it holds that $D(E(m_1)^k) = km_1\bmod u$.
-\end{theorem}
-\begin{proof}
-  Let $m \in \mathbb{Z}_u$ and $k\in \mathbb{N}$.
-  We consider $E(m)^k = (g^m \cdot h^r \bmod{n})^k\bmod n$.
-  \begin{align*}
-    (g^m \cdot h^r \bmod{n})^k \bmod n
-    &= (g^m \cdot h^r)^k \bmod{n}\\
-    &= (g^m)^k \cdot (h^r)^k \bmod{n}\\
-    &= g^{km} \cdot (h^{kr}) \bmod{n}
-  \end{align*}
-  Since $r$ is a random integer, $kr$ is also a random integer, Therefore, $g^{km} \cdot (h^{kr}) \bmod{n} = E(m)^k$ is a valid encryption of the message $km$.
-\end{proof}
-
-We have shown how the Paillier and DGK cryptosystems have similar homomorphic properties.
-In both cryptosystems, we are able to add a plaintext to a ciphertext, add two ciphertexts, and multiply a ciphertext by a plaintext scalar.
-In order to use these cryptosystems in secure image processing, we require the two schemes to support the encryption and manipulation of floating-point (FP) numbers, which can be done by using an approach shown in~\cite{ziad_cryptoimg:_2016}.
-This approach represents FP numbers using an encrypted mantissa and an unencrypted exponent.
-This representation extends the addition and plaintext multiplication homomorphisms of the Paillier and DGK cryptosystems to floating-point numbers.
-
-Table \ref{tab:flop_summary} describes protocols such as division~\cite{boukoros_lightweight_2017}, exponentiation~\cite{hutchison_privacy-preserving_2009}, and multiplication.
-These protocols, used in conjunction with the FP extension, allow for secure floating-point arithmetic~\cite{pcsc-paper}.
-
-\begin{table}[ht]
-	\caption{Two-party FP protocols}
-	\label{tab:flop_summary}
-    \begin{tabular}{
-        p{\dimexpr 0.25\linewidth-2\tabcolsep}
-        p{\dimexpr 0.75\linewidth-2\tabcolsep}}
-		\toprule
-		Operation & Protocol\\
-        \midrule
-            Division &
-            The server selects a random number $r$ and sends $E(rx)$ and $E(ry)$ to the client, who can decrypt to obtain $rx$ and $ry$.
-The client then encrypts the quotient and sends $E(rx/ry) = E(x/y)$ to the server.
-            \\
-            Exponentiation &
-            The server selects a random number $r$ and computes $E\left(x+r\right)$.
-The server sends $E(x+r)$  to the client, who can decrypt to obtain $x+r$.
-The client then encrypts and sends $E((x+r)^2)$ to the server.
-The server then computes $E\left(\left(x+r\right)^2\right)E\left(-2rx + r^2\right) = E\left(x^2\right)$.
-            \\
-            Multiplication &
-            The server obtains $E(x^2)$, $E(y^2)$, and $E((x+y)^2)$ using the exponentiation protocol.
-It can then compute $\frac{1}{2}E\left(\left(x+y\right)^2\right)E\left(x^2\right)^{-1}E\left(y^2\right)^{-1} = E\left(xy\right)$.\\
-	    \bottomrule
-    \end{tabular}
-\end{table}
-\subsection{The BGV Cryptosystem}
-The BGV (Brakerski--Gentry--Vaikuntanathan) cryptosystem \cite{cryptoeprint:2011:277} is a fully homomorphic cryptosystem created based on the ring-learning with error problem.
-A \textit{fully homomorphic cryptosytem} allows aribitrary computation on encrypted data.
-However, they are known to be significantly slower than partially homomorphic cryptosytems; improving the efficiency of fully homomorphic cryptosytems is an active area of research \cite{sen_homomorphic_2013}.
-The details regarding the construction of the BGV cryptosystem are beyond the scope of this paper.
-
-For this study, we will be using \textit{HELib}~\cite{garay_algorithms_2014}, an open-source library which implements the BGV cryptosystem with optimizations.
-\textit{HELib} supports arithmetic operations on integer ciphertexts and logical operations on binary ciphertexts.
-Evaluation of operations on 120 inputs in \textit{HELib} was performed in around 4 minutes, with an average of 2 seconds to process a single input~\cite{hutchison_fully_2010,cryptoeprint:2011:566}.
-The \textit{HELib} library has been adapted to Python using the Pyfhel library \cite{pyfhel_2018} maintained by Ibarrondo, Laurent (SAP) and Onen (EURECOM), and licensed under the GNU GPL v3 license.
-\subsection{CryptoImg}
-A paper published in 2009 by Ziad, et al.
-implements privacy-preserving image processing using \textit{CryptoImg}, a library for the Open Source Computer Vision Library (OpenCV)~\cite{bradski_opencv_2000} which implements various homomorphic encryption and image processing routines using the Paillier homomorphic cryptosystem~\cite{ziad_cryptoimg:_2016}.
-The \textit{CryptoImg} library assumed a client-server model wherein a client requests image processing operations from a server.
-A client first encrypts a digital image and sends the image securely to a server, which then operates on the encrypted image without revealing its contents.
-Then the resulting image is sent back to the client, which decrypts the image to recover the desired output.
-\begin{figure}[!ht]
-    \centering
-    \includegraphics[width=0.4\textwidth]{figures/ClientServerModel.png}
-    \caption{Client-server architecture used by \textit{CryptoImg} \cite{ziad_cryptoimg:_2016}}
-    \label{fig:clientserver}
-\end{figure}
-
-The \textit{CryptoImg} library implemented the following image processing operations: image negation, brightness adjustment, spatial filters (for noise reduction, edge detection and sharpening), morphological operations, and histogram equalization.
-
-% For image negation and spatial filters, the protocols specified by \textit{CryptoImg} allow all image processing operations to be performed on the server.
-However, due to limitations in the Paillier cryptosystem, the protocols presented for morphological operations and histogram equalization require both the client and the server to perform image processing calculations, although the server performs a significant portion of the processing.
-
-Ziad, et al.
-also showed experimental results establishing the relatively slow performance of image operations under a homomorphic cryptosystem.
-For instance, while sharpening and applying a Sobel filter each take less than a second when applied to a $512\times 512$ plaintext image, when applied to an encrypted image, sharpening required at least 238.257 seconds, and applying the Sobel filter required at least 147.567 seconds \cite{ziad_cryptoimg:_2016}.
-
-% We now discuss several limitations in the \textit{CryptoImg} study which we focus on for our research.
-First, the \textit{CryptoImg} library was limited in the image intensity transformations it implemented.
-We propose additional protocols to support more computationally intensive intensity transformations.
-% Second, the \textit{CryptoImg} library only considered the Paillier cryptosystem.
-We consider testing the performance of other homomorphic cryptosystems, which differ in their processing time and supported operations.
-
-% Convert to single table
-\subsection{Image Intensity Transformations}
-We represent a digital image $R$ as an $M \times N$ matrix of pixel intensity values, each value in the range $\left[0, L-1\right]$, for some positive integer $L$.
-We denote with $R(x,y)$ the entry at the $x$th row and $y$th column of a matrix $R$.
-An intensity transformation on an image $R$ can be defined as a function $T$ which is applied to every pixel $r$ in $R$.
-The \textit{CryptoImg} library implemented two types of linear intensity transformations: image negation and brightness control. An image negation transformation is defined as
-\begin{equation}
-    T\left(r\right) = L-1-r,
-\end{equation}
-which results in an image similar to a photographic negative~\cite{gonzalez_digital_2008}.
-A brightness control transformation with parameter $v$ is defined as
-\begin{equation}
-    T\left(r,v\right) = r+v.
-\end{equation}
-The above transformations are linear in terms of the input $r$, and are thus simple to implement under a homomorphic cryptosystem.
-
-In this study we extend the range of intensity transformations to non-linear transformations.
-Two common non-linear image transformations are the logarithm transformation and power-law transformation~\cite{gonzalez_digital_2008}.
-
-The logarithm transformation is used to enhance dark pixels or increase the dark details of an image by mapping low intensity values to a wider range of values~\cite{gonzalez_digital_2008}.
-This has the general formula
-\begin{equation}
-    T\left(r\right) = c \log\left(1 + r\right)
-\end{equation}
-where $c$ is a constant.
-The power-law transformation is a family of transformations that have the form
-\begin{equation}
-    T\left(r\right) = c r^{\gamma}
-\end{equation}
-where $c>0$ and $\gamma > 0$.
-A power-law transformation can calibrate the operation of many image capture and output devices such as cameras, printers and displays in a process called \textit{gamma correction}.
-% This ensures reproducibility and accuracy of images being displayed by digital output devices~\cite{gonzalez_digital_2008}.
-
-To implement non-linear intensity transformations using addition and multiplication in a homomorphic system, it is necessary to approximate the logarithm and exponential functions, which may result in higher computational overhead.
-An applicable approximation for the logarithm may be found in \cite{pcsc-paper}.
-% In our software library implementation, we investigate methods required to approximate the logarithm and power functions. 
-Non-linear intensity transformations such as the logarithm transformation have applications in intensity normalization \cite{oravec_illumination_2010}, which is used in some facial recognition algorithms to account for differences in lighting which make facial recognition difficult.
-
 \subsection{Facial Detection and Recognition}

### 2019-03-18 icmssp-paper/parts/02_02_cryptoimg.tex
Finished first pass of revisions

@@
-\subsection{CryptoImg}
+\subsection{Intensity Transformations in CryptoImg}
 A paper published in 2009 by Ziad, et al.
@@
 
-The \textit{CryptoImg} library implemented the following image processing operations: image negation, brightness adjustment, spatial filters (for noise reduction, edge detection and sharpening), morphological operations, and histogram equalization.
+An intensity transformation on a digital image $R$ can be defined as a function $T$ which is applied to every pixel $r$ in $R$.
+Table \ref{tab:imageoperation_summary} shows common image intensity transformations~\cite{gonzalez_digital_2008}.
+
+% The \textit{CryptoImg} library implemented the following image processing operations: image negation, brightness adjustment, spatial filters (for noise reduction, edge detection and sharpening), morphological operations, and histogram equalization.
+The \textit{CryptoImg} library implemented two types of intensity transformations: image negation and brightness control, which are both linear transformations.
+In this study,we consider two common non-linear transformations.
+the logarithm transformation and power-law transformation~\cite{gonzalez_digital_2008}, seen in Table \ref{tab:imageoperation_summary}.
 
@@
 
-Ziad, et al.
+% Ziad, et al.
 also showed experimental results establishing the relatively slow performance of image operations under a homomorphic cryptosystem.
@@
 % Convert to single table
-\subsection{Image Intensity Transformations}
-We represent a digital image $R$ as an $M \times N$ matrix of pixel intensity values, each value in the range $\left[0, L-1\right]$, for some positive integer $L$.
+\begin{table}[ht]
+	\caption{Summary of intensity transformations}
+	\label{tab:imageoperation_summary}
+    \begin{tabular}{
+        p{\dimexpr 0.65\linewidth-2\tabcolsep}
+        p{\dimexpr 0.35\linewidth-2\tabcolsep}}
+		\toprule
+		Operation & Transformation\\
+        \midrule
+            Image negation &
+            $T\left(r\right) = L-1-r$
+            \\
+            Brightness adjustment transformation with parameter $v$ &
+            $T\left(r\right) = r+v$
+            \\
+            Logarithm transformation with parameter $c$ &
+            $T\left(r\right) = c \log\left(1 + r\right)$\\
+            Power-law transformation with parameters $c$ and $\gamma$, where $c>0$ and $\gamma > 0$&
+            $T\left(r\right) = c r^{\gamma}$\\
+	    \bottomrule
+    \end{tabular}
+\end{table}
+% We represent a digital image $R$ as an $M \times N$ matrix of pixel intensity values, each value in the range $\left[0, L-1\right]$, for some positive integer $L$.
 We denote with $R(x,y)$ the entry at the $x$th row and $y$th column of a matrix $R$.
-An intensity transformation on an image $R$ can be defined as a function $T$ which is applied to every pixel $r$ in $R$.
-The \textit{CryptoImg} library implemented two types of linear intensity transformations: image negation and brightness control. An image negation transformation is defined as
-\begin{equation}
-    T\left(r\right) = L-1-r,
-\end{equation}
-which results in an image similar to a photographic negative~\cite{gonzalez_digital_2008}.
-A brightness control transformation with parameter $v$ is defined as
-\begin{equation}
-    T\left(r,v\right) = r+v.
-\end{equation}
-The above transformations are linear in terms of the input $r$, and are thus simple to implement under a homomorphic cryptosystem.
+The logarithm transformation is used to enhance dark pixels or increase the dark details of an image by mapping low intensity values to a wider range of values.
+A power-law transformation can calibrate the operation of many image capture and output devices such as cameras, printers and displays in a process called \textit{gamma correction}~\cite{gonzalez_digital_2008}.
+Both of these transformation can be used in intensity normalization \cite{oravec_illumination_2010}, which is used in some facial recognition algorithms to account for differences in lighting which make facial recognition difficult.
 
-In this study we extend the range of intensity transformations to non-linear transformations.
-Two common non-linear image transformations are the logarithm transformation and power-law transformation~\cite{gonzalez_digital_2008}.
+To implement non-linear intensity transformations in a privacy--preserving system, it is necessary to evaluate logarithm and exponential functions using closed--form approximations, since the arguments of the functions are unknown.
+An applicable approximation for the logarithm, found in \cite{pcsc-paper}, is
+% TODO: HOW ABOUT BGV
+\begin{align}\label{eq:optimal_log_approximation}
+	\begin{split}
+		&\log\left(1+x\right) \approx \frac{a(x)}{b(x)} + \log{16}
+	\end{split}
+\end{align}
+where
+\begin{align*}
+	\begin{split}
+	a(x) &= 137x^5 + 26685x^4 + 617370x^3 - 6498630x^2 \\
+	&- 121239315x - 257804775\\
+	b(x) &= 30(x^5 + 405x^4 + 27210x^3 + 488810x^2 + 2536005x \\
+	&+ 3122577).
+	\end{split}
+\end{align*}
+This approximation can be computed under a homomorphic cryptosystem which supports floating--point operations by precomputing the value of $\log{16}$ in the plaintext domain.
+% \begin{align}\label{eq:optimal_log_approximation}
+% 	\begin{split}
+% 		&\log\left(1+x\right) \\
+% 		&\approx \frac{137x^5 + 26685x^4 + 617370x^3 - 6498630x^2 - 121239315x - 257804775}
+% 		{30(x^5 + 405x^4 + 27210x^3 + 488810x^2 + 2536005x + 3122577)}\\
+% 		&+ \log{16}.
+% 	\end{split}
+% \end{align}
 
-The logarithm transformation is used to enhance dark pixels or increase the dark details of an image by mapping low intensity values to a wider range of values~\cite{gonzalez_digital_2008}.
-This has the general formula
-\begin{equation}
-    T\left(r\right) = c \log\left(1 + r\right)
-\end{equation}
-where $c$ is a constant.
-The power-law transformation is a family of transformations that have the form
-\begin{equation}
-    T\left(r\right) = c r^{\gamma}
-\end{equation}
-where $c>0$ and $\gamma > 0$.
-A power-law transformation can calibrate the operation of many image capture and output devices such as cameras, printers and displays in a process called \textit{gamma correction}.
-% This ensures reproducibility and accuracy of images being displayed by digital output devices~\cite{gonzalez_digital_2008}.
-
-To implement non-linear intensity transformations using addition and multiplication in a homomorphic system, it is necessary to approximate the logarithm and exponential functions, which may result in higher computational overhead.
-An applicable approximation for the logarithm may be found in \cite{pcsc-paper}.
-% In our software library implementation, we investigate methods required to approximate the logarithm and power functions. 
-Non-linear intensity transformations such as the logarithm transformation have applications in intensity normalization \cite{oravec_illumination_2010}, which is used in some facial recognition algorithms to account for differences in lighting which make facial recognition difficult.
+% \subsubsection{Power-Law Transformation}
+To apply the power-law transformation we can use partial sums of the infinite series,
+\begin{align} \label{eq:power_approximation}
+	x^\gamma &= \sum_{n=0}^{\infty}{\frac{(\gamma\log{x})^n}{n!}},
+\end{align}
+which relies on the logarithm function.
+For the implementation of the power-law transformation for this paper, a partial sum consisting of the first five terms of the infinite series were used.

### 2019-03-18 icmssp-paper/parts/02_03_facialrecognition.tex
Finished first pass of revisions

@@
 
-\subsubsection{Eigenfaces}
+% \subsubsection{Eigenfaces}
 Proposed by Matthew Turk and Alex Pentland, the eigenfaces method uses principal component analysis (PCA) in order to express an input image as a linear combination of eigenfaces \cite{turk_eigenfaces_1991}.
@@
 
-\subsection{Previous Implementations of Secure Facial Recognition}
+% \subsection{Previous Implementations of Secure Facial Recognition}
 Erkin, et al.
@@
 \end{equation}
-
 The terms $\left[\mathcal{S}_1\right]$ and $\left[\mathcal{S}_2\right]$ can be easily computed by Bob, since he already knows both $\omega_i$ in the clear and $\left[\bar{\omega}_i\right]$ which is in encrypted form.
+Computing for $\left[\mathcal{S}_3\right]$ requires the use of the secure squaring protocol outlined in Table \ref{tab:flop_summary}.
+% The terms $\left[\mathcal{S}_1\right]$ and $\left[\mathcal{S}_2\right]$ can be easily computed by Bob, since he already knows both $\omega_i$ in the clear and $\left[\bar{\omega}_i\right]$ which is in encrypted form.
 Computing for $\left[\mathcal{S}_3\right]$ is trickier because Bob cannot compute for $\left[\bar{\omega}_i^2\right]$ because pairwise multiplication is not supported in Paillier, that is why Bob needs help from Alice to square a number through a protocol described below \cite{hutchison_privacy-preserving_2009}.
 
-Before Bob sends $\left[\bar{\omega}_i\right]$ to Alice for squaring, he adds a random number $r_i$ to compute $\left[x_i\right] = \left[\bar{\omega}_i + r_i\right] = \left[\bar{\omega}_i\right] \cdot \left[r_i\right]$, where $r_i$ is obviously distinct for every $i$, then sends $\left[x_i\right]$ to Alice.
+% Before Bob sends $\left[\bar{\omega}_i\right]$ to Alice for squaring, he adds a random number $r_i$ to compute $\left[x_i\right] = \left[\bar{\omega}_i + r_i\right] = \left[\bar{\omega}_i\right] \cdot \left[r_i\right]$, where $r_i$ is obviously distinct for every $i$, then sends $\left[x_i\right]$ to Alice.
 She then decrypts it and computes $x_i^2$, and then computes $\mathcal{S}_3^\prime = \sum_{i=1}^{K} x_i^2$, after which she encrypts the sum and sends $\left[\mathcal{S}_3^\prime\right]$ to Bob.
 Now, he can compute for $\left[\mathcal{S}_3\right]$ as follows:
-\begin{equation}
-	\left[\mathcal{S}_3\right] = \left[\mathcal{S}_3^\prime\right] \cdot \prod_{j=1}^{K} \left(\left[\bar{\omega}_j\right]^{-2r_j} \cdot \left[-r_j^2\right]\right)
-\end{equation}
+% \begin{equation}
+% 	\left[\mathcal{S}_3\right] = \left[\mathcal{S}_3^\prime\right] \cdot \prod_{j=1}^{K} \left(\left[\bar{\omega}_j\right]^{-2r_j} \cdot \left[-r_j^2\right]\right)
+% \end{equation}
 
-The protocol for squaring a number as described earlier is a workaround for the limitations of Paillier or any other partially homomorphic cryptosystem that only supports addition and scalar multiplication.
+% The protocol for squaring a number as described earlier is a workaround for the limitations of Paillier or any other partially homomorphic cryptosystem that only supports addition and scalar multiplication.
 % This can be possibly extended so that operations such as pairwise multiplication and exponentiation are also supported, provided that the protocol involves two parties.
@@
 If the minimum distance is smaller than $T$, then a match is found, and the encrypted identity of the match is returned to Alice \cite{hutchison_privacy-preserving_2009}.
-Getting the minimum among the encrypted distances would involve comparing two encrypted numbers, which Paillier does not support.
-Instead, the DGK cryptosystem \cite{pieprzyk_efficient_2007} is used for the comparison protocol.
+Getting the minimum among the encrypted distances involves comparing two numbers which can be performed using the DGK secure comparison protocol \cite{pieprzyk_efficient_2007}.

### 2019-03-18 icmssp-paper/parts/03_methodology.tex
Finished first pass of revisions

@@
 
-\subsection{Cryptosystem Implementation}
+\subsection{System Implementation}
 A wrapper library was created in Python that integrates the Paillier, DGK, and BGV cryptosystems into a unified interface.
@@
 
-% [TO-DO: This is further explained in another paper.]
-% We will briefly discuss a protocol to enable cryptosystems built for integer inputs to handle real number inputs.
-% The following protocol was also used by \textit{CryptoImg} for image processing \cite{ziad_cryptoimg:_2016}.
-% This is also used for our own implementation of the Dasgupta--Pal cryptosystem in order to handle real numbers.
-
-% We represent a floating-point (FP) number as a pair of two integers $(m,e)$ representing the mantissa and exponent of the FP number with respect to a base $b$.
-The mantissa $m$ is encrypted, while the exponent $e$ is unencrypted.
-% Let $a,b,c$ be FP numbers represented by the pairs $(m_a,e_a),(m_b,e_b),(m_c,e_c)$ respectively.
-Let $\oplus,\otimes$ represent the homomorphic operations which correspond to the addition and multiplication, respectively.
-We define the secure real number operations as follows:
-% \begin{description}
-%   \item[Addition.]
-%     To compute $E(c)=E(a+b)$ we compute
-%     \begin{align*}
-%       E(m_c) &= E(m_1) \oplus (b^{e_b-e_a} \otimes E(m_b)), e_c = e_a & \text{ if } e_a \leq e_b \\
-%       E(m_c) &= E(m_b) \oplus (b^{e_a-e_b} \otimes E(m_a)), e_c = e_b & \text{ if } e_a > e_b
-%     \end{align*}
-%   \item[Scalar multiplication.]
-%     To compute $E(c) = E(ab)$, where $a$ and $E(b)$ are known (i.e. $m_a$ is not encrypted), we compute
-%     \begin{align*}
-%       E(m_c) &= m_a \otimes E(m_b)\\
-%       e_c &= e_a + e_b
-%     \end{align*}
-% \end{description}
-
-\subsection{Non-Linear Intensity Transformations}
-We will implement library functions for image negation, logarithm transformation and power-law transformation, as they are defined in~\cite{gonzalez_digital_2008}.
-% \subsubsection{Logarithm Transformation}
-In order to perform the logarithm transformation under Paillier and DGK, we use the following closed-form approximation for $\log\left(1 + x\right)$ from~\cite{pcsc-paper}.
-% TODO: HOW ABOUT BGV
-\begin{align}\label{eq:optimal_log_approximation}
-	\begin{split}
-		&\log\left(1+x\right) \approx \frac{a(x)}{b(x)} + \log{16}
-	\end{split}
-\end{align}
-where
-\begin{align*}
-	\begin{split}
-	a(x) &= 137x^5 + 26685x^4 + 617370x^3 - 6498630x^2 \\
-	&- 121239315x - 257804775\\
-	b(x) &= 30(x^5 + 405x^4 + 27210x^3 + 488810x^2 + 2536005x \\
-	&+ 3122577).
-	\end{split}
-\end{align*}
-% \begin{align}\label{eq:optimal_log_approximation}
-% 	\begin{split}
-% 		&\log\left(1+x\right) \\
-% 		&\approx \frac{137x^5 + 26685x^4 + 617370x^3 - 6498630x^2 - 121239315x - 257804775}
-% 		{30(x^5 + 405x^4 + 27210x^3 + 488810x^2 + 2536005x + 3122577)}\\
-% 		&+ \log{16}.
-% 	\end{split}
-% \end{align}
-
-% \subsubsection{Power-Law Transformation}
-To apply the power-law transformation using Paillier and DGK, we must provide an approximation for $x^\gamma$.
-We use partial sums of the following series, which relies on the logarithm function.
-\begin{align}
-	x^\gamma &= \sum_{n=0}^{\infty}{\frac{(\gamma\log{x})^n}{n!}}
-\end{align}
-For the implementation of the power-law transformation for this paper, a partial sum consisting of the first five terms of the infinite series were used.
-
 \subsection{Assessment of Homomorphic Encryption Schemes}
-A laptop computer with a 2.5 GHz Intel Core i7 quad-core processor and 8 GB of RAM is used to perform the computations, and processing time was tracked using built-in timing functions.
-The processing time for all cases were recorded.
-All of the tests are done using Python 3.7.1 running on Linux.
-
 \subsubsection{Image Quality of Intensity Transformations}
-In this section, we discuss the image quality metrics we used for assessing the performance of non-linear intensity transformations.
-
-We first obtained test images from the \texttt{faces94} dataset (\url{https://cswww.essex.ac.uk/mv/allfaces/faces94.html}) maintained by the University of Essex.
-However, only ten distinct facial images from the dataset were selected for the purposes of this test.
-Since only grayscale images are used in the study, the images were converted to grayscale and then downsampled to $40 \times 36$ pixels.
-
-For each cryptosystem, three image operations are tested:
+We  obtained ten test images from the \texttt{faces94} dataset (\url{https://cswww.essex.ac.uk/mv/allfaces/faces94.html}) maintained by the University of Essex.
+The images were converted to grayscale and then downsampled to $40 \times 36$ pixels.
+For each cryptosystem, three image operations are tested, as they are defined in Table \ref{tab:imageoperation_summary}:
 \begin{enumerate}
@@
 \end{enumerate}
+The logarithm transformation was implemented using the approximation in Equation \ref{eq:optimal_log_approximation}, while the exponentiation in the power-law transformation was implemented by evaluating the sum of the first five terms of the infinite series in Equation \ref{eq:power_approximation}.
+
+A laptop computer with a 2.5 GHz Intel Core i7 quad-core processor and 8 GB of RAM is used to perform the computations, and processing time was tracked using built-in timing functions.
+The processing time for all cases were recorded.
+All of the tests are done using Python 3.7.1 running on Linux.
 
@@
 We perform three tests to ascertain the preservation of image quality after encryption and decryption: MSE, PSNR, and SSIM, adopted from~\cite{ahmed_benchmark_2016, ahmad_efficiency_2012, wu_npcr_2011}.
-In describing each test, we let $X_i$ denote a value in an image $X$, where $1 \leq i \leq N$.
+In describing each test, we let $R_i$ denote a value in an image $R$, where $1 \leq i \leq N$.
 \begin{description}

### 2019-03-18 icmssp-paper/parts/02_02_cryptoimg.tex
Minor changes

@@
     \includegraphics[width=0.4\textwidth]{figures/ClientServerModel.png}
-    \caption{Client-server architecture used by \textit{CryptoImg} \cite{ziad_cryptoimg:_2016}}
+    \caption{Architecture used by \textit{CryptoImg}, from \cite{ziad_cryptoimg:_2016}}
     \label{fig:clientserver}
@@
 Table \ref{tab:imageoperation_summary} shows common image intensity transformations~\cite{gonzalez_digital_2008}.
+The \textit{CryptoImg} library implemented two types of intensity transformations: image negation and brightness control, which are both linear transformations. 
+In this study, we consider two common non-linear transformations.
+the logarithm transformation and power-law transformation~\cite{gonzalez_digital_2008}, seen in Table \ref{tab:imageoperation_summary}.
 
 % The \textit{CryptoImg} library implemented the following image processing operations: image negation, brightness adjustment, spatial filters (for noise reduction, edge detection and sharpening), morphological operations, and histogram equalization.
-The \textit{CryptoImg} library implemented two types of intensity transformations: image negation and brightness control, which are both linear transformations.
-In this study,we consider two common non-linear transformations.
-the logarithm transformation and power-law transformation~\cite{gonzalez_digital_2008}, seen in Table \ref{tab:imageoperation_summary}.
 

### 2019-03-18 icmssp-paper/parts/02_03_facialrecognition.tex
Minor changes

@@
 
-Traditional facial recognition algorithms rely on detecting salient features in a face image. One of the popular facial recognition algorithms is \textit{eigenfaces}.
+Traditional facial recognition algorithms rely on detecting salient features in a face image.
+Proposed by Matthew Turk and Alex Pentland, the \textit{eigenfaces} method uses principal component analysis (PCA) in order to express an input image as a linear combination of eigenfaces \cite{turk_eigenfaces_1991}.
+An \textit{eigenface} is a principal component, or more simply an eigenvector that represents a certain variation between the face images which are taken from the initial training set.
+The number of resulting eigenfaces is equal to the number of face images in the training set.
+% One of the popular facial recognition algorithms is \textit{eigenfaces}.
 % Traditional facial recognition algorithms rely on detecting salient features in a face image. Two of the popular facial recognition algorithms are \textit{eigenfaces} and \textit{Haar cascades}.
@@
 % \subsubsection{Eigenfaces}
-Proposed by Matthew Turk and Alex Pentland, the eigenfaces method uses principal component analysis (PCA) in order to express an input image as a linear combination of eigenfaces \cite{turk_eigenfaces_1991}.
-An \textit{eigenface} is a principal component, or more simply an eigenvector that represents a certain variation between the face images which are taken from the initial training set.
-The number of resulting eigenfaces is equal to the number of face images in the training set.
 
@@
 Erkin, et al.
-\cite{hutchison_privacy-preserving_2009} devised a method to incorporate the use of homomorphic cryptosystems into the eigenfaces method.
-In their study, they proposed a two-party system where Alice holds an encrypted image $\left[\Gamma\right]$, while Bob maintains a database of $K$ eigenfaces $\mathbf{u}_1, \ldots, \mathbf{u}_K$, and feature vectors $\Omega_1, \ldots, \Omega_M$ in the clear.
+\cite{hutchison_privacy-preserving_2009} devised a method to incorporate the use of homomorphic cryptosystems into the eigenfaces method, primarily using the Paillier cryptosystem.
+In their study, they proposed a two-party system where Alice holds an encrypted image $\left[\Gamma\right]$, while Bob maintains a database of $K$ eigenfaces $\mathbf{u}_1, \ldots, \mathbf{u}_K$, and feature vectors $\Omega_1, \ldots, \Omega_M$ in the plaintext domain.
 
@@
     \includegraphics[width=0.4\textwidth]{figures/secure_eigenfaces.png}
-    \caption{Diagram of the privacy-preserving facial recognition process \cite{hutchison_privacy-preserving_2009}}
+    \caption{Diagram of the privacy-preserving facial recognition process, from \cite{hutchison_privacy-preserving_2009}}
 \end{figure}

### 2019-03-18 icmssp-paper/parts/01_introduction.tex
Final pass by Aldrich
Reduced ICMSSP paper to 9 pages.

@@
 \section{Introduction}
-Digital image security is a growing concern, and various image encryption schemes have been developed and analyzed in the literature~\cite{murugan_survey_2018, kester_cryptographic_2015, jain_image_2016, singh_image_2015, khoirom_cryptanalysis_2018}.
+Digital image security is a growing concern, and various image encryption schemes have been developed and analyzed in the literature~\cite{murugan_survey_2018, jain_image_2016, khoirom_cryptanalysis_2018}.
 Cryptosystems allow for the secure transmission of data by way of encryption and decryption schemes.
@@
 In the area of homomorphic image encryption, there is interest in being able to perform image manipulation operations such as image adjustment, image filtering, and morphological extraction operations~\cite{ziad_cryptoimg:_2016, gonzalez_digital_2008}.
-There is also work on facial recognition on encrypted images\cite{turk_eigenfaces_1991, hutchison_privacy-preserving_2009}.
+There is also work on facial recognition on encrypted images~\cite{turk_eigenfaces_1991, hutchison_privacy-preserving_2009}.
 While secure linear image operations have been implemented~\cite{ziad_cryptoimg:_2016}, preprocessing which requires non-linear operations, such as those in~\cite{oravec_illumination_2010}, has yet to be performed in the encrypted domain.
@@
 To evaluate the performance of homomorphic image manipulation, in Section \ref{sec:chapter_4}, we test the time efficiency and accuracy of common image processing operations under homomorphic encryption.
-We test for image quality of the resulting images using Mean Squared Error (MSE), Peak Signal to Noise Ratio (PSNR), and Structural Similarity Index (SSIM), which are measures of image quality used for assessing image encryption schemes~\cite{ahmed_benchmark_2016}.
+We test for image quality of the resulting images using mean squared error (MSE), peak signal to noise ratio (PSNR), and structural similarity index (SSIM), which are measures of image quality used for assessing image encryption schemes~\cite{ahmed_benchmark_2016}.
 

### 2019-03-18 icmssp-paper/parts/02_01_cryptosystems.tex
Final pass by Aldrich
Reduced ICMSSP paper to 9 pages.

@@
     D(E(m_1)E(m_2)) &=(m_1+m_2)\bmod u \label{eq:dgk_ctplusct}\\
-    D(E(m_1)^{m_2}) &= m_1m_2\bmod u. \label{eq:dgk_cttimespt},
+    D(E(m_1)^{m_2}) &= m_1m_2\bmod u, \label{eq:dgk_cttimespt}
 \end{align}

### 2019-03-18 icmssp-paper/parts/02_02_cryptoimg.tex
Final pass by Aldrich
Reduced ICMSSP paper to 9 pages.

@@
 	\begin{split}
-		&\log\left(1+x\right) \approx \frac{a(x)}{b(x)} + \log{16}
+		&\log\left(1+x\right) \approx \frac{a(x)}{b(x)} + \log{16} ,
 	\end{split}
@@
 \end{align*}
-This approximation can be computed under a homomorphic cryptosystem which supports floating--point operations by precomputing the value of $\log{16}$ in the plaintext domain.
+This approximation can be computed under a homomorphic cryptosystem which supports floating-point operations by precomputing the value of $\log{16}$ in the plaintext domain.
 % \begin{align}\label{eq:optimal_log_approximation}

### 2019-03-18 icmssp-paper/parts/03_methodology.tex
Final pass by Aldrich
Reduced ICMSSP paper to 9 pages.

@@
 \label{sec:chapter_3}
-% We apply three homomorphic encryption schemes~\cite{ziad_cryptoimg:_2016, pieprzyk_efficient_2007, garay_algorithms_2014} for use in image processing and facial recognition applications.
-In particular, the study consists of the following:
-% \begin{itemize}
-% 	\item Creating a wrapper library that acts as a unified interface which implements the Paillier, DGK, and BGV homomorphic cryptosystems.
-% 	\item An implementation of image processing operations (intensity transformations, facial recognition) under the above cryptosystems.
-% 	\item Conducting tests for image quality, processing time, using images from the \texttt{faces94} dataset.
-% \end{itemize}
-
-% While the Paillier and DGK cryptosystems have been implemented for use in image processing in~\cite{ziad_cryptoimg:_2016, hutchison_privacy-preserving_2009}, the other cryptosystems have to be adapted for this study.
-% Two experiments are conducted in this study:
-% \begin{enumerate}
-% 	\item Assessment of non-linear image intensity transformations under each of the three cryptosystems.
-% 	\item Assessment of efficiency of each of the four cryptosystems when applied for use in privacy-preserving facial recognition and detection using eigenfaces.
-% \end{enumerate}
-% The results of the image intensity transformations are tested for image quality using benchmarks in~\cite{ahmed_benchmark_2016}.
-
 \subsection{System Implementation}
-A wrapper library was created in Python that integrates the Paillier, DGK, and BGV cryptosystems into a unified interface.
+A wrapper library was created in Python 3.7.1 that combines the Paillier, DGK, and BGV cryptosystems into a unified interface.
 \begin{itemize}
@@
 The CT was generated by encrypting the image, then applying the operation, and the CDT was generated by decrypting the CT.
-The three images (PT, PDT, CDT) were then compared using various benchmarks to evaluate the quality and security of each homomorphic encryption scheme.
+The PT, PDT, and CDT were then compared using image quality benchmarks to evaluate the applicability of each homomorphic encryption scheme.
 
-We perform three tests to ascertain the preservation of image quality after encryption and decryption: MSE, PSNR, and SSIM, adopted from~\cite{ahmed_benchmark_2016, ahmad_efficiency_2012, wu_npcr_2011}.
-In describing each test, we let $R_i$ denote a value in an image $R$, where $1 \leq i \leq N$.
+We perform three tests to ascertain the preservation of image quality after encryption and decryption: mean squared error (MSE), peak signal to noise ratio (PSNR), and structural similarity index (SSIM), adopted from~\cite{ahmed_benchmark_2016, ahmad_efficiency_2012, wu_npcr_2011}.
+These statistics were computed using the corresponding built-in functions from the scikit-image Python library \cite{scikit-image}.
 \begin{description}
-	\item [Mean Squared Error (MSE).] The MSE is defined in~\cite{ahmed_benchmark_2016} as
-	\begin{align}
-        \mathrm{MSE} = \frac{1}{N}\sum_{i=1}^{N}{(\mathrm{CDT}_i - \mathrm{PDT}_i)^2}.
-	\end{align}
-	The MSE provides a measure of how much data is recovered if an image operation is applied on the encrypted image, which is then decrypted.
+	\item [Mean Squared Error (MSE).]
+	By computing mean squared error between the PDT and the CDT, we obtain a measure of how much image quality is retained after encryption, transformation, and decryption.
 Lower values of MSE indicate higher preservation of image quality~\cite{ahmed_benchmark_2016, ahmad_efficiency_2012}.
 	\item [Peak Signal to Noise Ratio (PSNR).]
+	We compute the PSNR from the MSE.
 The PSNR is ``an estimator for human visual perception of reconstruction quality.''~\cite{ahmed_benchmark_2016}.
 Although it may produce results which do not correlate with human visual perception~\cite{huynh-thu_accuracy_2012, ahmed_benchmark_2016}, it is a valid indicator of image quality when media containing the same visual content is compared~\cite{huynh-thu_accuracy_2012}, and is a known metric for image and video quality~\cite{upmanyu_efficient_2009, jain_image_2016, akramullah_video_2014}.
-	PSNR is defined by
-	\begin{align}
-        \mathrm{PSNR} = 10\log_{10}{\left( \frac{L^2}{\mathrm{MSE}} \right)}
-	\end{align}
-	where $L$ is the maximum pixel intensity value of an image. A higher PSNR indicates higher image quality preservation.
+A higher PSNR indicates higher image quality preservation.
 	\item [Structural Similarity Index (SSIM).]
-	The SSIM for two random variables $X$ and $Y$ is defined in~\cite{ahmed_benchmark_2016, akramullah_video_2014} as
-	\begin{align}
-        \mathrm{SSIM}(X,Y) = \frac{(2\mu_X\mu_Y+c_1)(2\sigma_{XY}+c_2)}{(\mu_X^2+\mu_Y^2+c_1)(\mu_X^2+\mu_Y^2+c_2)}
-	\end{align}
-	where
-	\begin{itemize}
-		\item $\mu_X, \mu_Y$ are the averages of $X$ and $Y$, respectively;
-		\item $\sigma_X, \sigma_Y$ are the variances of $X$ and $Y$, respectively;
-		\item $\sigma_{XY}$ is the covariance of $X$ and $Y$;
-		\item $c_1 = (k_1L)^2$ and $c_2 = (k_2L)^2$ are two variables used to stabilize the measure when $\mu_X^2+\mu_Y^2$ is close to zero~\cite{akramullah_video_2014};
-		\item $L$ is the the maximum pixel intensity value of an image;
-		\item $k_1 = 0.01, k_2 = 0.03$ by default, given in~\cite{ahmed_benchmark_2016}.
-	\end{itemize}
+	We compute the SSIM between the PDT and the CDT.
 The SSIM is applied to the luminance value of two images to gauge structural similarity between neighboring pixels.
@@
 \end{description}
-
-Computation of the MSE between the PDT and CDT, PSNR of the CDT, and SSIM(PDT,CDT) was done using the corresponding built-in functions from the scikit-image Python library \cite{scikit-image}.
-
 \subsubsection{Facial Recognition Tests}

### 2019-03-18 icmssp-paper/parts/04_results.tex
Finished first pass of revisions
Final pass by Aldrich
Reduced ICMSSP paper to 9 pages.

@@
 This is because the Pyfhel library being used for the BGV cryptosystem is still in alpha development stage \cite{pyfhel_2018}.
-
-% One of the authors has already informed the maintainers of the library about a bug involving exponentiation of two real numbers.
 
@@
 Both the Paillier and DGK cryptosystems were able to perform image negation under the encrypted domain without introducing noise in the resulting image.
-In other words, the resulting image from doing image negation on an image on the clear and doing image negation under the encrypted domain are identical, as evidenced by the mean squared errors being exactly equal to zero, the PSNR being infinite, and the SSIM being exactly equal to one.
-While the time taken to apply image negation is comparable to that of DGK, the Paillier cryptosystem performed better in terms of encryption and decryption time.
+In other words, the resulting image from doing image negation on an image in the plaintext domain and doing image negation under the encrypted domain are identical, as evidenced by the MSE being exactly equal to zero, the PSNR being infinite, and the SSIM being exactly equal to one.
+While the time taken to apply image negation using Paillier is comparable to that of DGK, the Paillier cryptosystem performed better in terms of encryption and decryption time.
 
-\begin{table}[ht]
+\begin{table}[!ht]
 	\centering
@@
 % \end{table}
-\begin{table}[ht]
+\begin{table}[!ht]
 	\centering
@@
 \subsubsection{Logarithm Transformation}
-Unlike image negation, logarithm transformation involves more operations, so the increase in processing times for both cryptosystems are expected.
+Unlike image negation, logarithm transformation involves more operations, so the increase in processing times for both cryptosystems is expected.
 Applying the logarithm transformation under Paillier took about 2 seconds per image, while it took about 25 seconds each under DGK.
@@
 
-\begin{table}[ht]
+\begin{table}[!ht]
 	\centering
@@
 % \end{table}
-\begin{table}[ht]
+\begin{table}[!ht]
 	\caption{Logarithm transformation under DGK}
@@
 The accuracy varies greatly across all the images as in the case of Paillier, with mean squared errors as high as 8270.696 and as low as 616.419, and SSIM scores ranging from 0.43185 to 0.92334, as seen in Table~\ref{tbl:pwr-pal}.
-As expected, the total processing time now takes about 15 to 20 seconds per image since the power-law transformation is more computationally intensive due to its approximation of an infinite series consisting of terms using the logarithm function, which is also approximated using a combination of addition and multiplication operations.
+As expected, the total processing time now takes about 15 to 20 seconds per image since the power-law transformation is more computationally intensive, relying on numerous additions, multiplications, and evaluations of the logarithm approximation.
 
-\begin{table}[ht]
+\begin{table}[!ht]
 	\centering
@@
 \end{table}
-
-When DGK was used in the power-law transformation, it failed to produce a discernible image and only resulted in an almost black image with a faint shape of a face.
-The mean squared errors for this case is an order of magnitude higher than the results from using Paillier.
-Furthermore, doing a power-law transformation under DGK is not only impractical in terms of accuracy, but also it is somewhat impractical in terms of time efficiency because it took at most 4 minutes to process each image.
 
@@
 \end{table}
+
+When DGK was used in the power-law transformation, it failed to produce a discernible image and only resulted in an almost black image with a faint shape of a face.
+The mean squared errors for this case is an order of magnitude higher than the results from using Paillier.
+Furthermore, doing a power-law transformation under DGK is not only impractical in terms of accuracy, but also it is somewhat impractical in terms of time efficiency because it took at most 4 minutes to process each image.

### 2019-03-18 icmssp-paper/parts/05_conclusion.tex
Final pass by Aldrich
Reduced ICMSSP paper to 9 pages.

@@
 \section{Conclusion}
-In this paper, we have assessed the feasibility and practicality of various homomorphic cryptosystems with regard to secure processing and manipulation of facial image data through creation of a software library that facilitates image processing operations within the encrypted domain, as well as our own implementation of some homomorphic cryptosystems like DGK.
-
-% This paper also proposes a correction to the Dasgupta--Pal cryptosystem which is further explained in Appendix~\ref{chap:correction}.
-
-Even though an operation in a partially homomorphic cryptosystem is not theoretically possible, like multiplication of two ciphertexts under Paillier, it has been shown that such operations are indeed possible in a two-party system.
-Protocols for secure multiplication and exponentiation have been proposed and also applied to more complex image operations such as facial recognition.
-Thus, a partially homomorphic cryptosystem can be modified to admit more image processing operations by assuming a two-party system.
+In this paper, we have assessed the feasibility and practicality of various homomorphic cryptosystems with regard to secure processing and manipulation of facial image data through creation of a software library that facilitates image processing operations within the encrypted domain.
+We have also extended the Paillier and DGK cryptosystems to support limited floating-point arithmetic, demonstrated in the implementation of the logarithm and power-law image intensity transformations.
 
@@
 
-A wrapper library has been made which implements the various functions and methods of the cryptosystems into a single interface.
-This allowed us to express various image operations with a unified syntax, thus facilitating easier testing.
-
 \subsection{Ongoing and Future Work}
-Testing intensity transformations under the BGV cryptosystem will be started once the Pyfhel library is deemed stable enough to use, or another Python library that implements BGV becomes available.
+Testing of intensity transformations under the BGV cryptosystem will be started once the Pyfhel library is deemed stable enough to use, or until a similar library becomes available.
 One of the authors of this paper has already informed the developers of the Pyfhel library about a bug involving exponentiation of two real numbers.
@@
 Our own implementation of the privacy-preserving eigenfaces by Erkin, et al.
-does not yet use the DGK cryptosystem for secure integer comparison in the match finding step, thus we are working on implementing DGK from scratch.
-
+does not yet use the DGK cryptosystem for secure integer comparison in the match finding step.
 Another promising image operation to consider is \textit{facial detection} under a homomorphic cryptosystem.
@@
 Future work would involve improving and optimizing our implementation of non-linear intensity transformations in terms of number of operations, numerical accuracy and stability, and time efficiency.
-% Future work would involve improving and optimizing our implementation of the DGK cryptosystem so that it performs faster.
-% A suggestion would be to port the existing implementation to C/C++ and then create a Python library that acts as a wrapper to the C/C++ methods.
-For future studies, an implementation of a client-server framework or system dealing with secure image processing can be considered.
+An implementation of a client-server system dealing with secure image processing can be considered.

### 2019-04-04 pcsc-paper/parts/02_01_paillier.tex
Fix math typos

@@
 where $r$ is a random non-negative integer less than $n^2$.
-The decryption function to decrypt a ciphertext $c \in \mathbb{Z}^*_{n^2}$ given a private key $(p,q)$ is defined as:
+The decryption function to decrypt a ciphertext $c \in \mathbb{Z}^*_{n^2}$ given a private key $(p,q)$ is defined as
 \begin{equation*}
-	D\left(c\right) = L\left(c^\lambda \bmod n^2\right) \cdot \left(L\left(g^\lambda \bmod n^2\right)\right)^{-1} \mod n.
+	D\left(c\right) = L\left(c^\lambda \bmod n^2\right) \cdot \left(L\left(g^\lambda \bmod n^2\right)\right)^{-1} \mod n,
 \end{equation*}
+where the function $L(x)$ is the largest integer $v$ greater than zero such that $x-1 \geq vn$.
 \subsubsection{Homomorphic Properties of the Paillier Cryptosystem}
@@
 	\item Bob sends $E\left(x+r\right)$ to Alice, who decrypts the ciphertext to obtain $x+r$.
-	\item Alice squares $x+r$ and encrypts the result. She sends $E\left(\left(x+r\right)^2\right)$ to Bob.
-	\item Bob computes $E\left(-2rx + r^2\right)$. He then computes
-	\begin{align*}
-		E\left(\left(x+r\right)^2\right)E\left(-2rx + r^2\right) = E\left(x^2\right).
-	\end{align*}
+	\item Alice squares $x+r$ and encrypts, sending $E\left(\left(x+r\right)^2\right)$ to Bob.
+	\item Bob then computes $E\left( \left(x+r\right)^2 + (-2rx + r^2)\right) = E\left(x^2\right)$.
 \end{itemize}
@@
 	\item Alice sends $E\left(\left(x+y\right)^2\right)$ to Bob.
-	\item Bob then computes
-	\begin{align*}
-		\frac{1}{2}E\left(\left(x+y\right)^2\right)E\left(x^2\right)^{-1}E\left(y^2\right)^{-1} &= \frac{1}{2}E\left(\left(x+y\right)^2 - x^2 - y^2\right)\\
-		&= \frac{1}{2}E\left(2xy\right)\\
-		&= E\left(xy\right).
-	\end{align*}
+	\item Bob then computes $ E\left(\frac{1}{2} \left( \left(x+y\right)^2 - x^2 - y^2\right)\right) = E\left(xy\right)$.
 \end{itemize}

### 2019-04-09 icmssp-paper/parts/02_03_facialrecognition.tex

@@
 Distance computation in this version is somewhat different from the original eigenfaces method, in that it deals with the square of the Euclidean distance since the relative order of the distances is only important when comparing these during the match finding step \cite{hutchison_privacy-preserving_2009}.
-\begin{align}
-    d_i &= \left\lVert \Omega_i - \bar{\Omega} \right\rVert ^2 = \sum_{j=1}^{K} \left(\omega_{ij} - \bar{\omega}_j\right)^2 \\
-        &= \underbrace{\sum_{j=1}^{K} \omega_{ij}^2}_{\mathcal{S}_1} + \underbrace{\sum_{j=1}^{K} \left(-2 \omega_{ij} \bar{\omega_j}\right)}_{\mathcal{S}_2} + \underbrace{\sum_{j=1}^{K} \bar{\omega}_{j}^2}_{\mathcal{S}_3}
-\end{align}
+Computation of the distances  uses the secure squaring protocol outlined in Table \ref{tab:flop_summary}.
+% \begin{align}
+%     d_i &= \left\lVert \Omega_i - \bar{\Omega} \right\rVert ^2 = \sum_{j=1}^{K} \left(\omega_{ij} - \bar{\omega}_j\right)^2 \\
+%         &= \underbrace{\sum_{j=1}^{K} \omega_{ij}^2}_{\mathcal{S}_1} + \underbrace{\sum_{j=1}^{K} \left(-2 \omega_{ij} \bar{\omega_j}\right)}_{\mathcal{S}_2} + \underbrace{\sum_{j=1}^{K} \bar{\omega}_{j}^2}_{\mathcal{S}_3}
+% \end{align}
 
-Computing for the distances within Paillier would just be multiplying the encrypted sums together.
-\begin{equation}
-	\left[d_i\right] = \left[\mathcal{S}_1\right] \cdot \left[\mathcal{S}_2\right] \cdot \left[\mathcal{S}_3\right]
-\end{equation}
-The terms $\left[\mathcal{S}_1\right]$ and $\left[\mathcal{S}_2\right]$ can be easily computed by Bob, since he already knows both $\omega_i$ in the clear and $\left[\bar{\omega}_i\right]$ which is in encrypted form.
+% Computing for the distances within Paillier would just be multiplying the encrypted sums together.
+% \begin{equation}
+% 	\left[d_i\right] = \left[\mathcal{S}_1\right] \cdot \left[\mathcal{S}_2\right] \cdot \left[\mathcal{S}_3\right]
+% \end{equation}
+% The terms $\left[\mathcal{S}_1\right]$ and $\left[\mathcal{S}_2\right]$ can be easily computed by Bob, since he already knows both $\omega_i$ in the clear and $\left[\bar{\omega}_i\right]$ which is in encrypted form.
 Computing for $\left[\mathcal{S}_3\right]$ requires the use of the secure squaring protocol outlined in Table \ref{tab:flop_summary}.

### 2019-04-09 parts/00_abstract.tex
Add chapter 4 contents

--- 2019-03-03 parts/00_abstract.tex
@@
 Regardless, homomorphic cryptography has been targeted for use in secure image processing and facial recognition, due to their ability to maintain data privacy.
-In this paper, we compared the viability of the Paillier, Damg{\aa}rd--Geisler--Kr{\o}igaard (DGK), and Brakerski--Gentry--Vaikuntanathan (BGV) cryptosystems for facial image processing applications, by implementing a software library equipped with these cryptosystems, and comparing their time efficiency and accuracy.
+In this paper, we compared the viability of the Paillier, Damg{\aa}rd--Geisler--Kr{\o}igaard (DGK), Dijk--Gentry--Halevi--Vaikuntanathan (DGHV), and Brakerski--Gentry--Vaikuntanathan (BGV) cryptosystems for facial image processing applications, by implementing a software library equipped with these cryptosystems, and comparing their time efficiency and accuracy.
 Furthermore, as an extension to previous research, we attempt to support non-linear image processing operations by deriving and implementing applicable closed-form approximations.

### 2019-04-09 parts/00_acknowledgements.tex

@@
     \noindent
-    We would like to thank Dr.
+    We would like to thank our adviser, Dr.
+William Emmanuel S.
+Yu, and our panelists Dr.
+Andrei D.
+Coronel and Dr.
+Mari-Jo P.
+Ruiz for lending their expertise and for giving their invaluable comments and insights.
+Due acknowlegement is also given to the University of Essex for making the \texttt{faces94} dataset publicly available for research purposes.
+
+    % We would like to thank Dr.
 Ma.
@@
 
-    This section, as the name suggests, is the place in your paper where you may acknowledge individuals or groups who, with their help or guidance, made your study feasible and ultimately a reality.
+    % This section, as the name suggests, is the place in your paper where you may acknowledge individuals or groups who, with their help or guidance, made your study feasible and ultimately a reality.
 Some of these people include your adviser, volunteers for your study, other professors who may have contributed to your study, and if applicable, any group or organization who provided support in any way for your research.

### 2019-04-09 parts/01_introduction_05scopeandlimitations.tex
Applied comments for chapter 1

@@
 \section{Scope and Limitations of the Study}
-Our study will be limited in terms of the cryptosystems to be tested, the image processing operations we will implement, and the statistical tests we will use to gauge the security of the cryptosystems.
-Below is a listing of the scope of the study.
-
+Our study will test a fixed set of cryptosystems and image processing operations. 
 We will implement and test the following algorithms:
@@
 	\item A variant of the Paillier cryptosystem~\cite{stern_public-key_1999} which supports floating-point operations, used in \textit{CryptoImg}~\cite{ziad_cryptoimg:_2016}.
-    \item The Damg{\aa}rd--Geisler--Kr{\o}igaard (DGK) cryptosystem~\cite{pieprzyk_efficient_2007, cryptoeprint:2008:321} which is primarily used for secure integer comparison.
-	\item A fully homomorphic encryption scheme by Dasgupta and Pal, which uses polynomial rings~\cite{dasgupta_design_2016}.
+  \item The Damg{\aa}rd--Geisler--Kr{\o}igaard (DGK) cryptosystem~\cite{pieprzyk_efficient_2007, cryptoeprint:2008:321}.
+	\item The DGHV cryptosystem by Dijk, Gentry, Halevi, and Vaikuntanathan \cite{cryptoeprint:2009:616}, with optimizations from Coron, Naccache, and Tibouchi, \cite{cryptoeprint:2011:277, cryptoeprint:2011:440} to support shorter public keys.
 	\item The Brakerski--Gentry--Vaikuntanathan (BGV) cryptosystem \cite{cryptoeprint:2011:277}, an improvement on the lattice-based cryptosystem by Gentry~\cite{gentry_fully_2009}, with optimizations from Smart, Vercauteren and Halevi \cite{hutchison_fully_2010, cryptoeprint:2011:566}.
@@
 \begin{enumerate}
-	\item Non-linear image intensity adjustment (logarithm and power-log transformations)
+	\item Non-linear intensity adjustment (logarithm, power-log transformations)
 	\item Facial detection and recognition using the eigenface approach \cite{turk_eigenfaces_1991}.
 \end{enumerate}
-We will adopt the benchmark for evaluating image quality of image encryption schemes presented by Ahmed, et.
+To test for image quality, we will adopt the benchmark for evaluating image quality of image encryption schemes presented by Ahmed, et.
 al~\cite{ahmed_benchmark_2016}.
-The presented benchmark reflects many tests used in other literature~\cite{ahmad_efficiency_2012, wu_npcr_2011}.
+The presented benchmark uses many tests used in other literature~\cite{ahmad_efficiency_2012, wu_npcr_2011}.
 \begin{enumerate}
@@
 A client-server model for secure computation will be assumed to allow operations such as secure comparison and exponentiation.
+Training and test data are taken from the publicly available \texttt{faces94} dataset (\url{https://cswww.essex.ac.uk/mv/allfaces/faces94.html}) maintained by the University of Essex.

### 2019-04-09 parts/02_relatedliterature.tex

@@
 We have shown that there are basic image processing operations which are non-linear, which we can implement.
-  \item While privacy-preserving facial recognition has been accomplished by Erkin, et al., privacy-preserving facial detection is an area of research which has yet to explored.
+  \item While privacy-preserving facial recognition has been accomplished by Erkin, et al., privacy-preserving facial detection has yet to explored.
 \end{enumerate}

### 2019-04-09 parts/02_relatedliterature_02commonimageprocessingoperations.tex
final final final
final final final

@@
 We represent a digital image $R$ as an $M \times N$ matrix of pixel intensity values, each value in the range $\left[0, L-1\right]$, for some positive integer $L$.
-We use $R(x,y)$ represents the entry at the $x$th row and $y$th column of a matrix $R$.
+We use $R(x,y)$ to represent the entry at the $x$th row and $y$th column of a matrix $R$.
 An intensity transformation on an image $R$ can be defined as a function $T$ which maps a pixel value $r$ to a new value $r^\prime$, which we can write as $r^\prime = T\left(r\right)$.
@@
 
-\begin{comment}
-\subsection{Spatial Filtering}
-The \textit{CryptoImg} library also implemented \textit{spatial filters}.
+% \subsection{Spatial Filtering}
+% The \textit{CryptoImg} library also implemented \textit{spatial filters}.
 Spatial filters are operators which determine output pixels using information from neighboring input pixels.
 To apply a spatial filter to obtain a resulting image $R^\prime$, a convolution is performed between an $m \times n$ matrix $k$, called a kernel, and the original $M\times N$ image $R$.
-A convolution between a kernel $k$ and image $R$ which yields a resulting image $R^\prime$, denoted as $R^\prime = k \ast R$, is defined by
-\begin{align} \label{eq:spatialfilter}
-	R^\prime(x,y) = \sum_{s=1}^m{\sum_{t=1}^n{k(s,t)R(x+s,y+t)}}, \text{ for all } 0\leq x \leq M, 0 \leq y \leq N,
-\end{align}
+% A convolution between a kernel $k$ and image $R$ which yields a resulting image $R^\prime$, denoted as $R^\prime = k \ast R$, is defined by
+% \begin{align} \label{eq:spatialfilter}
+% 	R^\prime(x,y) = \sum_{s=1}^m{\sum_{t=1}^n{k(s,t)R(x+s,y+t)}}, \text{ for all } 0\leq x \leq M, 0 \leq y \leq N,
+% \end{align}
 
-\begin{figure*}[!ht]
-    \centering
-    \includegraphics[width=\textwidth,\keepaspectratio]{Figures/SpatialFilter.png}
-    \caption{A sample image $R$ and sample kernel $k$.}
-    \label{fig:spatialfilter}
-\end{figure*}
-For example, using the image and $3 \times 3$ kernel given in Figure \ref{fig:spatialfilter}, we can calculate the value in the third row and fourth column of the resulting image $R^\prime$ by adding the products of entries in $k$ with the corresponding entries in $R$, found in an $3 \times 3$ region around $R(3,4)$.
-\begin{align*}
-	R^\prime(3,4) &= \sum_{s=1}^m{\sum_{t=1}^n{k(s,t)R(3+s,4+t)}}\\
-	&= (0.0625\times 200) + (0.1250\times 249) + (0.0625\times 255) \\
-	&+ (0.1250\times 143) + (0.2500\times 223) + (0.1250\times 255) \\
-	&+ (0.0625\times 196) + (0.1250\times 236) + (0.0625\times 255)\\
-	&= 223.
-\end{align*}
-Since spatial filters take values from a contiguous region of pixels, this presents a difficulty in homomorphic cryptosystems: in order for spatial filters to be performed, the location of each pixel relative to neighboring pixels has to be preserved.
+% \begin{figure*}[!ht]
+%     \centering
+%     \includegraphics[width=\textwidth,\keepaspectratio]{Figures/SpatialFilter.png}
+%     \caption{A sample image $R$ and sample kernel $k$.}
+%     \label{fig:spatialfilter}
+% \end{figure*}
+% For example, using the image and $3 \times 3$ kernel given in Figure \ref{fig:spatialfilter}, we can calculate the value in the third row and fourth column of the resulting image $R^\prime$ by adding the products of entries in $k$ with the corresponding entries in $R$, found in an $3 \times 3$ region around $R(3,4)$.
+% \begin{align*}
+% 	R^\prime(3,4) &= \sum_{s=1}^m{\sum_{t=1}^n{k(s,t)R(3+s,4+t)}}\\
+% 	&= (0.0625\times 200) + (0.1250\times 249) + (0.0625\times 255) \\
+% 	&+ (0.1250\times 143) + (0.2500\times 223) + (0.1250\times 255) \\
+% 	&+ (0.0625\times 196) + (0.1250\times 236) + (0.0625\times 255)\\
+% 	&= 223.
+% \end{align*}
+% Since spatial filters take values from a contiguous region of pixels, this presents a difficulty in homomorphic cryptosystems: in order for spatial filters to be performed, the location of each pixel relative to neighboring pixels has to be preserved.
 This was performed in the implementation of spatial filters in the \textit{CryptoImg} library~\cite{ziad_cryptoimg:_2016}.
@@
 
-\subsection{Common Spatial Filtering Kernels}
-Edge detection is used to find and determine the boundaries in an image, commonly used in applications such as image segmentation and feature extraction.
+% \subsection{Common Spatial Filtering Kernels}
+% Edge detection is used to find and determine the boundaries in an image, commonly used in applications such as image segmentation and feature extraction.
 This works by detecting so-called \textit{edges}, areas that have abrupt changes in intensity.
-One common method of performing edge detection is the Sobel operator, which uses two spatial filters to approximate the gradient of an image. Given an image $R$, and the kernels
-\begin{equation}
-    g_x =
-    \begin{bmatrix}
-        -1 & 0 & 1 \\
-        -2 & 0 & 2 \\
-        -1 & 0 & 1
-    \end{bmatrix}
-    \qquad\text{and}\qquad
-    g_y =
-    \begin{bmatrix}
-        1 & 2 & 1 \\
-        0 & 0 & 0 \\
-        -1 & -2 & -1
-    \end{bmatrix},
-\end{equation}
-$g_x \ast R$ yields the horizontal component of the gradient, while $g_y \ast R$ yields the vertical component of the gradient.
+% One common method of performing edge detection is the Sobel operator, which uses two spatial filters to approximate the gradient of an image. Given an image $R$, and the kernels
+% \begin{equation}
+%     g_x =
+%     \begin{bmatrix}
+%         -1 & 0 & 1 \\
+%         -2 & 0 & 2 \\
+%         -1 & 0 & 1
+%     \end{bmatrix}
+%     \qquad\text{and}\qquad
+%     g_y =
+%     \begin{bmatrix}
+%         1 & 2 & 1 \\
+%         0 & 0 & 0 \\
+%         -1 & -2 & -1
+%     \end{bmatrix},
+% \end{equation}
+% $g_x \ast R$ yields the horizontal component of the gradient, while $g_y \ast R$ yields the vertical component of the gradient.
 
-There are also spatial filters that perform image smoothing (such as Gaussian blur and box blur, which use the kernels $b_g$ and $b$ respectively in Equation~\ref{eqn:smooth-filters}) and image sharpening~\cite{gonzalez_digital_2008}.
-\begin{equation}
-    \label{eqn:smooth-filters}
-    b_g = \frac{1}{16}
-    \begin{bmatrix}
-        1 & 2 & 1 \\
-        2 & 4 & 2 \\
-        1 & 2 & 1
-    \end{bmatrix}
-    \qquad
-    b = \frac{1}{9}
-    \begin{bmatrix}
-        1 & 1 & 1 \\
-        1 & 1 & 1 \\
-        1 & 1 & 1
-    \end{bmatrix}
-\end{equation}
+% There are also spatial filters that perform image smoothing (such as Gaussian blur and box blur, which use the kernels $b_g$ and $b$ respectively in Equation~\ref{eqn:smooth-filters}) and image sharpening~\cite{gonzalez_digital_2008}.
+% \begin{equation}
+%     \label{eqn:smooth-filters}
+%     b_g = \frac{1}{16}
+%     \begin{bmatrix}
+%         1 & 2 & 1 \\
+%         2 & 4 & 2 \\
+%         1 & 2 & 1
+%     \end{bmatrix}
+%     \qquad
+%     b = \frac{1}{9}
+%     \begin{bmatrix}
+%         1 & 1 & 1 \\
+%         1 & 1 & 1 \\
+%         1 & 1 & 1
+%     \end{bmatrix}
+% \end{equation}
 
 %% TODO: specific list of kernels to use for this study
-\end{comment}

### 2019-04-09 parts/02_relatedliterature_05partiallyhomomorphic.tex

--- 2019-03-03 parts/02_relatedliterature_05partiallyhomomorphic.tex
@@
 In this section, we will present two classical partially homomorphic encryption (PHE) schemes which we will be testing in the study: the Paillier cryptosystem and the DGK cryptosystem.
-Both of these cryptosystems encrypt integer plaintexts and are additively homomorphic and allow for the multiplication of a plaintext scalar.
-We will then show how these PHE schemes may be adapted for secure floating-point computation.
+Both of these cryptosystems encrypt integer plaintexts, are additively homomorphic, and allow for the multiplication of a plaintext scalar.
+We will then show how these PHE schemes may be adapted for secure floating-point computation using two-party protocols.
 
@@
 
-As the multiplicative homomorphism was not presented in the original paper, we provide a short proof here.
+As the multiplicative homomorphism was not presented in the original paper \cite{pieprzyk_efficient_2007, cryptoeprint:2008:321}, we provide a short proof here.
 \begin{proof}
@@
 We will now show how these PHE schemes may be extended to a system which allows for secure floating-point computation.
-
-In this section, we let $\oplus$ and $\otimes$ represent the homomorphic operations which correspond to the addition and multiplication of integers in a PHE scheme, respectively.
+In this section, we let $\oplus$ and $\otimes$ represent the homomorphic operations corresponding to the addition and multiplication of integers in a PHE scheme, respectively.
 
 \subsubsection{Extension to Floating-Point Numbers}
-\label{sec:fp_operations}
-We can use the following protocol described in~\cite{ziad_cryptoimg:_2016} in order to extend Paillier and DGK to floating-point numbers.
+\label{sec:fp_number_extension}
+We can use the following protocol, described in~\cite{ziad_cryptoimg:_2016}, in order to extend Paillier and DGK to floating-point numbers.
 
@@
 
-By applying these extensions to the Paillier and DGK cryptosystems, privacy-preserving floating-point arithmetic can be acheived.
+By applying these extensions to the Paillier and DGK cryptosystems, privacy-preserving floating-point arithmetic can be acheived with PHE schemes.

### 2019-04-09 parts/03_methodology.tex
Add citation for scikit-image
Misc edits (Ch2,3,appendix,abstract, acknowledgements)

@@
 \end{enumerate}
-The results of the image intensity transformations were tested for image quality using benchmarks in~\cite{ahmed_benchmark_2016}.
+% redundant sentence, this is explained later:
+% The results of the image intensity transformations were tested for image quality using benchmarks in~\cite{ahmed_benchmark_2016}.
 
 \section{Cryptosystem Implementation}
-
 % The current version of the OpenCV library (3.4.2) will be forked from the open-source GitHub repository at \url{https://github.com/opencv/opencv})~\cite{bradski_opencv_2000}.
@@
 \begin{itemize}
-	\item The Paillier cryptosystem was incorporated using the implementation at \url{https://github.com/n1analytics/python-paillier} developed by Data61 - CSIRO.
-	\item The BGV cryptosystem was implemented using the Pyfhel library (\url{https://github.com/ibarrond/Pyfhel}) using a HElib backend from (\url{https://github.com/shaih/HElib}).
-	\item The DGK and Dasgupta--Pal cryptosystem were implemented from scratch.
+	\item The Paillier cryptosystem is incorporated using the \texttt{python-paillier} library at \url{https://github.com/n1analytics/python-paillier} developed by Data61 - CSIRO.
+	\item The DGK cryptosystem is ported from the C++ implementation at \url{https://github.com/encryptogroup/ENCRYPTO_utils}, developed by Daniel Demmler from EC-SPRIDE.
+	\item The DGHV cryptosystem is ported from the C++ implementation at 
+	\url{https://github.com/deevashwer/Fully-Homomorphic-DGHV-and-Variants}.
+	\item The BGV cryptosystem is implemented using the Pyfhel library (\url{https://github.com/ibarrond/Pyfhel}) using a HElib backend from (\url{https://github.com/shaih/HElib}).
 \end{itemize}
@@
 
-\input{parts/03_methodology_01integertorealnumbers}
+The Paillier and DGK cryptosystems were adapted for floating-point computations using the protocols described in section \ref{sec:fp_arithmetic}.
+
 \input{parts/03_methodology_02nonlinearintensitytransformations}
@@
 
-Lab computers in Faura Hall, Ateneo de Manila University were used to perform the computations, and processing time was tracked using built-in timing functions.
+A laptop computer with a 2.5 GHz Intel Core i7 quad-core processor and 8 GB of RAM is used to perform the computations, and processing time was tracked using built-in timing functions.
 The processing time for all cases were recorded.
+All of the tests are done using Python 3.7.1 running on Linux.
 
@@
 
-We first obtained standard test images from~\cite{gonzalez_image_nodate}. Grayscale images were used in the study.
+We first obtained test images from the \texttt{faces94} dataset (\url{https://cswww.essex.ac.uk/mv/allfaces/faces94.html}) maintained by the University of Essex.
+However, only ten distinct facial images from the dataset were selected for the purposes of this test.
+Since only grayscale images are used in the study, the images were converted to grayscale and then downsampled to $40 \times 36$ pixels.
+
+For each cryptosystem, three image operations are tested:
+\begin{enumerate}
+	\item Image negation
+	\item Logarithm transformation, with $c = 30$
+	\item Power-law transformation, with $c = 1$ and $\gamma = 0.4$
+\end{enumerate}
 
@@
 
+Computing for MSE, PSNR, and SSIM was done using the corresponding built-in functions from the scikit-image Python library \cite{scikit-image}.
+
 \subsection{Facial Recognition Tests}
-%% TODO: Brian, can you fill this part up? Yes
+%% TODO: Brian, can you fill this part up? Yes. OK Thanks
 The method for secure facial recognition using eigenfaces by Erkin, et al. \cite{hutchison_privacy-preserving_2009-2} was implemented for this study.
@@
 
-\section{Summary}
-In summary, the study consists of:
-\begin{itemize}
-	\item Creating a wrapper library that acts as a unified interface which implements the Paillier, DGK, Dasgupta--Pal, and BGV homomorphic cryptosystems.
-	\item An implementation of image processing operations (intensity transformations, facial recognition) under the above cryptosystems.
-	\item Conducting tests for image quality, processing time, using standard test images from~\cite{gonzalez_image_nodate}.
-\end{itemize}
+% \section{Summary}
+% In summary, the study consists of:
+% \begin{itemize}
+% 	\item Creating a wrapper library that acts as a unified interface which implements the Paillier, DGK, DGHV, and BGV homomorphic cryptosystems.
+% 	\item An implementation of image processing operations (intensity transformations, facial recognition) under the above cryptosystems.
+% 	\item Conducting tests for image quality, processing time, using standard test images from~\cite{gonzalez_image_nodate}.
+% \end{itemize}
 
 %% insert flowchart/diagrams here
+% sure

### 2019-04-09 pcsc-paper/parts/00_abstract.tex

@@
 Second, protocols using a two-party scheme are described for secure multiplication, division, and exponentiation, in order for such operations to be supported by a partially homomorphic cryptosystem such as the Paillier cryptosystem, where these operations are theoretically infeasible to do under a single-party system.
-Finally, new closed-form approximations to the logarithm and the inverse tangent functions are derived using the Gauss--Legendre quadrature, which yield more accurate results than other closed-form approximations that involve a similar number of secure operations.
+Finally, new closed-form approximations to the logarithm and the inverse tangent function are derived using the Gauss--Legendre quadrature, which yield more accurate results than other closed-form approximations that involve a similar number of secure operations.

### 2019-04-09 pcsc-paper/parts/05__00_experiments.tex

@@
-\section{Experiments}
+\section{Experiments on Accuracy}
 We implemented privacy-preserving floating-point arithmetic using the system described in Section~\ref{sec:fp_arithmetic}, through the \texttt{python-paillier} library (\url{https://github.com/n1analytics/python-paillier}) running on Python~3.6.5.

### 2019-04-09 pcsc-paper/parts/05_testsforaccuracy.tex

--- 2019-02-14 pcsc-paper/parts/05_testsforaccuracy.tex
@@
 \begin{table}[ht]
-	\caption{Comparison of logarithm approximation errors under Paillier}
+	\caption{Comparison of logarithm approximation errors under Paillier for selected inputs}
 	\label{tab:log_approximation}
@@
 		]
+		\addplot[thick, ACMOrange] table[x=x, y=olderr] {plots/comp_log_errs.txt};
 		\addplot[very thick, ACMDarkBlue] table[x=x, y=newerr] {plots/comp_log_errs.txt};
-		\addplot[thick, ACMOrange] table[x=x, y=olderr] {plots/comp_log_errs.txt};
-		\legend{Scaled quadrature, Original quadrature}
+		\legend{Original quadrature, Scaled quadrature}
 		\end{semilogyaxis}
 	\end{tikzpicture}%
-	\caption{Comparison of logarithm approximation errors under Paillier}
+	\caption{Comparison of logarithm approximation errors under Paillier over the interval $[0, 255]$}
 	\label{fig:comp_log}
@@
 \begin{table}[ht]
-	\caption{Comparison of inverse tangent approximation errors under Paillier}
+	\caption{Comparison of inverse tangent approximation errors under Paillier for selected inputs}
 	\label{tab:arctan_approximation}
@@
 		]
+		\addplot[thick, ACMOrange] table[x=x, y=olderr] {plots/comp_arctan_errs.txt};
 		\addplot[very thick, ACMDarkBlue] table[x=x, y=newerr] {plots/comp_arctan_errs.txt};
-		\addplot[thick, ACMOrange] table[x=x, y=olderr] {plots/comp_arctan_errs.txt};
-		\legend{Gauss--Legendre quadrature, Partial sum of Euler's series}
+		\legend{Partial sum of Euler's series, Gauss--Legendre quadrature}
 		\end{semilogyaxis}
 	\end{tikzpicture}%
-	\caption{Comparison of inverse tangent approximation errors under Paillier}
+	\caption{Comparison of inverse tangent approximation errors under Paillier over the interval $[-1, 1]$}
 	\label{fig:comp_arctan}
 \end{figure}
+
+% \subsection{Timing Results}
+% Timing data was based on a laptop computer with a 2.5 GHz Intel Core i7 quad-core processor and 8 GB of RAM.
+
+% \begin{figure}[!ht]
+% 	\centering
+% 	\begin{tikzpicture}
+% 		\begin{axis}[
+% 			% xmin=0, xmax=255,
+% 			ytick={1,2},
+% 			yticklabels={Scaled quadrature, Original quadrature},
+% 			xlabel={Time (seconds)},
+% 			grid=major,
+% 			legend pos=north east,
+% 			legend cell align=left,
+% 		]
+% 		\addplot+[boxplot, thick, ACMDarkBlue] table[x=x, y=newt] {plots/comp_log_errs.txt};
+% 		\addplot+[boxplot, thick, ACMOrange] table[x=x, y=oldt] {plots/comp_log_errs.txt};
+% 		\end{axis}
+% 	\end{tikzpicture}%
+% 	\caption{Comparison of logarithm computation times under Paillier}
+% 	\label{fig:times_log}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\centering
+% 	\begin{tikzpicture}
+% 		\begin{axis}[
+% 			% xmin=0, xmax=255,
+% 			ytick={1,2},
+% 			yticklabels={Gauss--Legendre quadrature, Euler's series},
+% 			xlabel={Time (seconds)},
+% 			grid=major,
+% 			legend pos=north east,
+% 			legend cell align=left,
+% 		]
+% 		\addplot+[boxplot, thick, ACMDarkBlue] table[x=x, y=newt] {plots/comp_arctan_errs2.txt};
+% 		\addplot+[boxplot, thick, ACMOrange] table[x=x, y=oldt] {plots/comp_arctan_errs2.txt};
+% 		\end{axis}
+% 	\end{tikzpicture}%
+% 	\caption{Frequency distribution of inverse tangent computation times under Paillier}
+% 	\label{fig:times_arctan}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\centering
+% 	\begin{tikzpicture}
+% 		\begin{axis}[
+% 			xmin=0, xmax=1,
+% 			ymin=1.5, ymax=2.5,
+% 			xlabel={Absolute error}, ylabel={Time (seconds)},
+% 			grid=major,
+% 			legend pos=south east,
+% 			legend cell align=left,
+% 			tick scale binop=\times,
+% 		]
+% 		\addplot+[scatter, only marks, ACMDarkBlue] table[x=newerr, y=newt] {plots/comp_arctan_errs2.txt};
+% 		\addplot+[scatter, only marks, ACMOrange] table[x=olderr, y=oldt] {plots/comp_arctan_errs2.txt};
+% 		\legend{Gauss--Legendre quadrature, Partial sum of Euler's series}
+% 		\end{axis}
+% 	\end{tikzpicture}%
+% 	\caption{Accuracy vs. time in inverse tangent computation under Paillier}
+% 	\label{fig:acc_vs_time_arctan}
+% \end{figure}

### 2019-04-09 pcsc-paper/parts/06_conclusionreccomendations.tex

@@
 Different methods for numerical integration can also be explored and applied for use in deriving formulas for privacy-preserving computation.
-Furthermore, testing with other types of homomorphic cryptosystems can be done, to potentially reduce noise encountered in secure floating-point operations.
+Furthermore, testing with other types of homomorphic cryptosystems can be done to potentially reduce noise encountered in secure floating-point operations.
+Additional testing to determine time efficiency among approximation methods under various homomorphic cryptosystems can also be done.

### 2019-04-29 parts/00_abstract.tex
Final revisions and cleanup

@@
 Furthermore, as an extension to previous research, we attempt to support non-linear image processing operations by deriving and implementing applicable closed-form approximations.
-Preliminary results have shown that the Paillier and DGK cryptosystems are comparable in accuracy and may be used for image negation, but only the Paillier cryptosystem is consistent enough to produce reasonable to accurate results.
+Eesults have shown that the Paillier and DGK cryptosystems are comparable in accuracy and may be used for image negation, but only the Paillier cryptosystem is consistent enough to produce reasonable to accurate results for logarithm intensity transformation.
 

### 2019-04-29 parts/01_introduction_01contextofstudy.tex
Final revisions and cleanup

@@
 Digital data privacy and security is a growing concern in various fields, such as cloud computing~\cite{potey_homomorphic_2016}, health information systems~\cite{kester_cryptographic_2015}, and video surveillance~\cite{upmanyu_efficient_2009}.
-To meet these needs, various cryptosystems have been developed.
-Cryptosystems allow plaintexts, data which is commonly understood, to be encrypted as ciphertext, data which can only be understood by authorized parties using a key~\cite{bauer_cryptosystem_2005}.
-The encryption and decryption algorithms are chosen such that the plaintext cannot easily be recovered from the ciphertext without knowledge of the key.
-This allows data to be securely transmitted over an insecure channel.
+Various cryptosystems have been developed, which allow for the secure transmission of data using encryption and decryption schemes~\cite{bauer_cryptosystem_2005}.
 
@@
  Using a homomorphic cryptosystem, operations can be performed on encrypted data while keeping both the operands and resulting value secure.
-The result of the operations can be recovered when the data is decrypted..
+The result of the operations can be recovered when the data is decrypted.
 In this manner, data is manipulated without compromising data privacy~\cite{fontaine_survey_2007, sen_homomorphic_2013}.
-While numerous homomorphic cryptosystems exist for use with general digital data, in the area of homomorphic image encryption, there is additional interest in being able to perform image manipulation operations on the encrypted data such as image adjustment, filtering, and morphological/feature extraction operations~\cite{ziad_cryptoimg:_2016, gonzalez_digital_2008}.
+There is additional interest in being able to perform image manipulation operations on encrypted images such as image adjustment, filtering, and morphological/feature extraction operations~\cite{ziad_cryptoimg:_2016, gonzalez_digital_2008}.
 More advanced operations have also been implemented using homomorphic cryptosystems, such as facial recognition \cite{hutchison_privacy-preserving_2009} and neural networks \cite{hesamifard_cryptodl:_2017}.
+While secure linear image operations have been implemented \cite{ziad_cryptoimg:_2016}, preprocessing which requires non-linear operations, such as certain methods of illumination processing \cite{oravec_illumination_2010}, has yet to be performed in the encrypted domain.
 This study in particular focuses on facial recognition.

### 2019-04-29 parts/01_introduction_02researchquestions.tex
Final revisions and cleanup

@@
 
-By implementing homomorphic cryptosystems and creating an OpenCV library so they can be easily used, we aim to address our main research question: What is the best method for image data to be encrypted and manipulated for practical applications?
+By creating a sofware library which implements various homomorphic cryptosystems, we aim to address our main research question: What is the best method for image data to be encrypted and manipulated for practical applications?
 
-More specifically, our research will address the following sub-questions:
+Specifically, the study addresses the following research sub-questions:
 \begin{enumerate}
 	\item Which homomorphic cryptosystems admit more image processing operations? How can existing homomorphic cryptosystems be modified to admit more image processing operations?
-	\item Which homomorphic cryptosystems are the most time-efficient in applying image processing operations?
+	\item Which homomorphic cryptosystems are the most time-efficient and the most accurate in applying image processing operations?
 	\item Which homomorphic cryptosystems best preserve image quality in applying image processing operations?

### 2019-04-29 parts/01_introduction_03objectives.tex
Final revisions and cleanup

@@
 
-Previous attempts in the literature to provide image processing tasks such as image manipulation \cite{ziad_cryptoimg:_2016} and  facial recognition \cite{hutchison_privacy-preserving_2009} have primarily used the Paillier and  Damg{\aa}rd--Geisler--Kr{\o}igaard (DGK) cryptosystems to perform linear operations on encrypted data.
-In this study, we extend this research to provide an objective comparison of various homomorphic cryptosystems currently in the literature in performing non-linear operations, as opposed to just linear operations, and facial detection, as opposed to just facial recognition.
+Previous attempts in the literature to provide privacy-preserving image processing tasks have primarily used the Paillier and  Damg{\aa}rd--Geisler--Kr{\o}igaard (DGK) cryptosystems to perform linear operations on encrypted data~\cite{ziad_cryptoimg:_2016,hutchison_privacy-preserving_2009}.
+In this study, we extend this research to provide an objective comparison of various homomorphic cryptosystems currently in the literature in performing non-linear image operations.
 
-Our main research objective is to assess the practicality of various homomorphic cryptosystems with regard to image processing on faces.
+Our main research objective is the assessment of the practicality of various homomorphic cryptosystems with regard to image processing on faces.
 Homomorphic cryptosystems are known to be slower in terms of encryption, operation, and decryption time~\cite{sen_homomorphic_2013}.
@@
 
-In summary, in this study, we wish to
+In summary, in this study, we 
 \begin{enumerate}
@@
     \item Compare the time efficiency and accuracy of common image processing operations under known homomorphic encryption schemes, and of common image processing operations without using homomorphic encryption;
-    \item Create a library for the Open Source Computer Vision Library (OpenCV) to allow for convenient use and comparison of these homomorphic encryption schemes for image processing and facial recognition.
+    \item Create a software library to allow for convenient use and comparison of these homomorphic encryption schemes for image processing and facial recognition.
 \end{enumerate}

### 2019-04-29 parts/01_introduction_04significanceofstudy.tex
Final revisions and cleanup

@@
 
-This study aims to directly address one of the current problems in the research of homomorphic cryptosystems: the practicality of homomorphic encryption~\cite{sen_homomorphic_2013}.
+This study investigates one of the current problems in the research of homomorphic cryptosystems: the practicality of homomorphic encryption~\cite{sen_homomorphic_2013}.
 The literature shows existing homomorphic cryptosystems and how they support primitive operations (usually addition and multiplication) on encrypted data, however, for homomorphic cryptosystems to be useful for practical use, efficient support for more complicated image processing operation must be demonstrated as well.

### 2019-04-29 parts/01_introduction_05scopeandlimitations.tex
Final revisions and cleanup

@@
 \section{Scope and Limitations of the Study}
-Our study will test a fixed set of cryptosystems and image processing operations. 
-We will implement and test the following algorithms:
+The study tests a fixed set of cryptosystems and image processing operations. 
+We test the following algorithms:
 \begin{enumerate}
@@
 \end{enumerate}
-We will implement and test the following categories of image manipulation operations:
+We implement and test the following categories of image manipulation operations:
 \begin{enumerate}
@@
 \end{enumerate}
-To test for image quality, we will adopt the benchmark for evaluating image quality of image encryption schemes presented by Ahmed, et.
+To test for image quality, we adopt the benchmark for evaluating image quality of image encryption schemes presented by Ahmed, et.
 al~\cite{ahmed_benchmark_2016}.

### 2019-04-29 parts/02_relatedliterature.tex
Final revisions and cleanup

@@
 
-We will now describe homomorphic cryptosystems in detail to provide a concrete description of their current capabilities and limitations.
-Then, we will describe our target applications in image processing and facial recognition.
+We now describe homomorphic cryptosystems in detail to provide a concrete description of their current capabilities and limitations.
+We then describe our target applications in image processing and facial recognition.
 
@@
 \begin{enumerate}
-  \item We have shown two fully homomorphic cryptosystems, the Dasgupta-Pal cryptosystem and the BGV cryptosystem.
-While these cryptosystems are generally less efficient than partially homomorphic cryptosystems, they do not require additional protocols for exponentiation.
+  \item We have shown two fully homomorphic cryptosystems, the DGHV cryptosystem and the BGV cryptosystem.
+While these cryptosystems are generally less efficient than partially homomorphic cryptosystems, they do not require additional protocols for division, multiplication, and exponentiation.
   \item Due to the general limitations of partially homomorphic systems, attempts at applying homomorphic cryptography to applications such as image processing and facial recognition have mainly been restricted to linear operations on ciphertext.
-We have shown that there are basic image processing operations which are non-linear, which we can implement.
+We have shown that there are basic image processing operations which are non-linear, which can be approximated.
   \item While privacy-preserving facial recognition has been accomplished by Erkin, et al., privacy-preserving facial detection has yet to explored.

### 2019-04-29 parts/02_relatedliterature_02commonimageprocessingoperations.tex
Final revisions and cleanup

@@
 \section{Image Intensity Transformations}
-We represent a digital image $R$ as an $M \times N$ matrix of pixel intensity values, each value in the range $\left[0, L-1\right]$, for some positive integer $L$.
+% We represent a digital image $R$ as an $M \times N$ matrix of pixel intensity values, each value in the range $\left[0, L-1\right]$, for some positive integer $L$.
 We use $R(x,y)$ to represent the entry at the $x$th row and $y$th column of a matrix $R$.
-An intensity transformation on an image $R$ can be defined as a function $T$ which maps a pixel value $r$ to a new value $r^\prime$, which we can write as $r^\prime = T\left(r\right)$.
+An intensity transformation on an image $R$ can be defined as a function $T$ which maps a pixel intensity value $r$ to a new value $r^\prime$, which we can write as $r^\prime = T\left(r\right)$.
 This function is then applied to every pixel in $R$.
@@
 
-To implement non-linear intensity transformations using addition and multiplication in a homomorphic system, it is necessary to approximate the logarithm and exponential functions, which may result in higher computational overhead.
-In our software library implementation, we investigate methods required to approximate the logarithm and power functions.
-Non-linear intensity transformations such as the logarithm transformation have applications in intensity normalization \cite{oravec_illumination_2010}, which is used in some facial recognition algorithms to account for differences in lighting which make facial recognition difficult.
+To implement non-linear intensity transformations using addition and multiplication in a homomorphic system, it is necessary to approximate the logarithm and exponential functions, which we investigate in Appendix \ref{chap:logarithm_approximation}.
+Non-linear intensity transformations have applications in intensity normalization \cite{oravec_illumination_2010}, which is used in some facial recognition algorithms to account for differences in lighting which make facial recognition difficult.
 

### 2019-04-29 parts/02_relatedliterature_03facialrecognition.tex
Final revisions and cleanup

@@
 
-Since simple image operations mentioned earlier can be done within a homomorphic cryptosystem, these operations can be assembled together in order to do more complex operations.
+Since simple image operations an be done within a homomorphic cryptosystem, these operations can be assembled together in order to do more complex operations.
 A prominent application of image processing that often uses complex image operations is \textit{facial recognition}.
 
-Traditional facial recognition algorithms rely on detecting salient features in a face image. Two of the popular facial recognition algorithms are \textit{eigenfaces} and \textit{Haar cascades}.
+Traditional facial recognition algorithms rely on detecting salient features in a face image. One of the popular facial recognition algorithms is \textit{eigenfaces}.
+% Traditional facial recognition algorithms rely on detecting salient features in a face image. Two of the popular facial recognition algorithms are \textit{eigenfaces} and \textit{Haar cascades}.
 

### 2019-04-29 parts/02_relatedliterature_04homomorphiccryptosystems.tex
Final revisions and cleanup

@@
 
-A cryptosystem~\cite{bauer_cryptosystem_2005} consists of an encryption function $\mathcal{E}$ and a decryption function $\mathcal{D}$, which operate on three sets: the plaintext space $\mathcal{P}$, ciphertext space $\mathcal{C}$ and the key space $\mathcal{K}$ A \textit{plaintext}, an element of the \textit{plaintext space}, is text that can be commonly understood within a larger group.
-Given a \textit{key}, an element of the \textit{key space}, the encryption function maps a plaintext to some \textit{ciphertext}, an element of the ciphertext space which can only be understood by authorized parties.
-The decryption function similarly maps a ciphertext back to its corresponding plaintext, given an appropiate key.
-By sending data as ciphertext and only exposing the corresponding plaintexts to authorized parties who have access to the appropiate keys, secure data transmission can be achieved.
+A cryptosystem~\cite{bauer_cryptosystem_2005} consists of an encryption function $\mathcal{E}$ and a decryption function $\mathcal{D}$, which operate on plaintexts, ciphertexts and keys.
+A \textit{plaintext} is text that can be commonly understood within a larger group.
+Given a \textit{key}, the encryption function maps a plaintext to some \textit{ciphertext}, which can only be understood by authorized parties.
+The decryption function similarly maps a ciphertext back to its corresponding plaintext, given an appropriate key.
+By sending data as ciphertext and only exposing the corresponding plaintexts to authorized parties who have access to the appropriate keys, secure data transmission can be achieved.
 
@@
 
-Homomorphic cryptosystems are a special type of cryptosystem in which operations can be securely performed on encrypted data.
-Suppose that in a public-key cryptosystem, $\mathcal{E}_k \left(p \right)$ is the encryption function which uses a public key $k$, and $\mathcal{D}_l \left(c \right)$ be the decryption function which uses a private key $l$.
+Homomorphic cryptosystems are a special type of cryptosystem which allows operations to be performed on recovered plaintexts by performing corresponding operations on ciphertexts.
+This allows for secure computation in the plaintext space $\mathcal{P}$, the set of all plaintexts, by performing operations in the ciphertext space $\mathcal{C}$, the set of all ciphertexts.
+
+Suppose that in a public-key cryptosystem, $\mathcal{E}_k \left(p \right)$ is the encryption function which uses a public key $k$, and $\mathcal{D}_l \left(c \right)$ is the decryption function which uses a private key $l$.
 The cryptosystem is said to be homomorphic if its encryption function is homomorphic, that is, if it satisfies the relation
@@
 where $p_1, p_2 \in \mathcal{P}$ are plaintexts, and $\boxplus$ and $\boxdot$ are operations in $\mathcal{P}$ and $\mathcal{C}$ respectively~\cite{fontaine_survey_2007}.
-By applying the decryption function $\mathcal{D}_l$ to both sides of equation~\ref{eq:homomorphic_definition_encryption}, we can see that a homomorphic cryptosystem also satisfies~\cite{li_elliptic_2012}
+By applying the decryption function $\mathcal{D}_l$ to both sides of equation~\ref{eq:homomorphic_definition_encryption}, we see that a homomorphic cryptosystem also satisfies~\cite{li_elliptic_2012}
 \begin{equation}
@@
 Numerous partially homomorphic and fully homomorphic cryptosystems have been developed in the literature.
-This study will compare several of them, which we will now introduce in detail.
+This study compares several of them, which we will now introduce in detail.
 

### 2019-04-29 parts/02_relatedliterature_05partiallyhomomorphic.tex
Final revisions and cleanup

@@
 We will now show how these PHE schemes may be extended to a system which allows for secure floating-point computation.
-In this section, we let $\oplus$ and $\otimes$ represent the homomorphic operations corresponding to the addition and multiplication of integers in a PHE scheme, respectively.
+In this section, we let $\oplus$ and $\otimes$ represent the homomorphic operations corresponding to the secure addition and multiplication of integers in a PHE scheme, respectively.
 
@@
 	\begin{align*}
-		E\left(\left(x+r\right)^2\right)E\left(-2rx + r^2\right) = E\left(x^2\right).
+		E\left(\left(x+r\right)^2+ \left(-2rx + r^2\right)\right) = E\left(x^2\right).
 	\end{align*}
@@
 	\begin{align*}
-		\frac{1}{2}E\left(\left(x+y\right)^2\right)E\left(x^2\right)^{-1}E\left(y^2\right)^{-1} &= \frac{1}{2}E\left(\left(x+y\right)^2 - x^2 - y^2\right)\\
-		&= \frac{1}{2}E\left(2xy\right)\\
+		E\left(\frac{1}{2}\left(\left(x+y\right)^2\ - x^2 - y^2\right)\right) 
 		&= E\left(xy\right).

### 2019-04-29 parts/02_relatedliterature_06fullyhomomorphic.tex
Final revisions and cleanup

--- 2019-03-03 parts/02_relatedliterature_06fullyhomomorphic.tex
@@
 
-We will also be testing fully homomorphic encryption (FHEs), which allow aribitrary computation on encrypted data.
+We also test fully homomorphic encryption (FHE), which allow aribitrary computation on encrypted data.
 
@@
 Gentry's original construction showed that FHE are possible, although they are known to be significantly slower than PHE.
-Improving the efficiency of FHis an active area of research \cite{sen_homomorphic_2013}.
+Improving the efficiency of FHE is an active area of research \cite{sen_homomorphic_2013}.
 
-We will present two FHEs, the DGHV cryptosystem and the BGV cryptosystem, which both have open source implementations availble primarily used in homomorphic cryptography research.
+We will present two FHE schemes, the DGHV cryptosystem and the BGV cryptosystem, which both have open source implementations availble primarily used in homomorphic cryptography research.
 Since the mathematical details of these fully homomorphic cryptosystems are not relevant to describing their potential uses in secure image operations, we will instead briefly describe important developments and implementations of each cryptosystem.

### 2019-04-29 parts/03_methodology.tex
Final revisions and cleanup

@@
 For cryptosystems with readily available open-source implementations, such implementations were used.
-For the remaining cryptosystems, the encryption and decryption methods were implemented in Python.
+For the remaining cryptosystems, the encryption and decryption methods were implemented in Python 3.7.1.
 \begin{itemize}
@@
 
-For convenience, a wrapper library was created that integrates the four cryptosystems into a unified interface.
-
+A wrapper library was created that integrates the four cryptosystems into a unified interface.
 The Paillier and DGK cryptosystems were adapted for floating-point computations using the protocols described in section \ref{sec:fp_arithmetic}.
@@
 \subsection{Facial Recognition Tests}
-%% TODO: Brian, can you fill this part up? Yes. OK Thanks
 The method for secure facial recognition using eigenfaces by Erkin, et al. \cite{hutchison_privacy-preserving_2009-2} was implemented for this study.

### 2019-04-29 parts/03_methodology_02nonlinearintensitytransformations.tex
Final revisions and cleanup

@@
 We now describe how we implement the logarithm and power-law image intensity transformations.
-In the case of partially homomorphic cryptosystems (Paillier, DGK), if  exponentiation and multiplication is required, the secure protocols in section \ref{ssec:exponentiationprotocol} will be used.
 
@@
 Similar to the logarithm transformation, we must provide an approximation for $x^\gamma$.
-We have derived an infinite series in Appendix \ref{sec:logarithm_approximation}.
+We have derived an infinite series in Appendix \ref{sec:power_approximation}.
 \begin{align*}
@@
 Partial sums of the above infinite series can be calculated based on the closed form approximation for the logarithm in Equation \ref{eq:optimal_log_approximation_ch3}.
+For the implementation of the power-law transformation, a partial sum consisting of the first five terms of the infinite series were used.

### 2019-04-29 parts/04_results.tex
Add chapter 5
Final revisions and cleanup

@@
 This is because the Pyfhel library being used for the BGV cryptosystem is still in alpha development stage \cite{pyfhel_2018}.
+Results obtained from the DGHV cryptosystem were also unstable, but DGHV was also impractical, taking over 5 minutes to perform a single floating-point addition operation.
 
@@
 
-\begin{table*}
+\begin{table}
 	\centering
@@
 	\end{tabular}
-\end{table*}
+\end{table}
 
-\begin{table*}
+\begin{table}
 	\centering
@@
 	\end{tabular}
-\end{table*}
+\end{table}
 
@@
 \subsection{Power-Law Transformation}
-Applying the power-law transformation under both cryptosystems produced less than accurate images.
-The accuracy varies greatly across all the images as in the case of Paillier, with mean squared errors as high as 8270.696 and as low as 616.419, and SSIM scores ranging from 0.43185 to 0.92334, as seen in Table~\ref{tbl:pwr-pal}.
-As expected, the total processing time now takes about 15 to 20 seconds per image since the power-law transformation is more computationally intensive due to its approximation of an infinite series consisting of terms using the logarithm function, which is also approximated using a combination of addition and multiplication operations.
+Applying the power-law transformation under both cryptosystems did not produce accurate images.
+The accuracy varies greatly across all the images.
+When Paillier was used, mean squared errors ranged from 616.419 to 8270.696, and SSIM scores ranged from 0.43185 to 0.92334, as seen in Table~\ref{tbl:pwr-pal}.
+As expected, the total processing time now takes about 15 to 20 seconds per image since the power-law transformation is more computationally intensive, requiring repeated evaluation of the logarithm approximation.
 
@@
 When DGK was used in the power-law transformation, it failed to produce a discernible image and only resulted in an almost black image with a faint shape of a face.
-The mean squared errors for this case is an order of magnitude higher than the results from using Paillier.
-Furthermore, doing a power-law transformation under DGK is not only impractical in terms of accuracy, but also it is somewhat impractical in terms of time efficiency because it took at most 4 minutes to process each image.
+The mean squared errors under DGK are an order of magnitude higher than the results from using Paillier.
+Furthermore, doing a power-law transformation under DGK is somewhat impractical in terms of time efficiency because it took at most 4 minutes to process each image.
 
-\begin{table}[t]
+\begin{table}[!ht]
 	\centering

### 2019-04-29 parts/05_conclusions.tex
Final revisions and cleanup

@@
 
-\section{Ongoing and Future Work}
-Testing intensity transformations under the BGV cryptosystem will be started once the Pyfhel library is deemed stable enough to use, or another Python library that implements BGV becomes available.
+\section{Recommendations for Future Work}
+Testing intensity transformations under the BGV cryptosystem may be started once the Pyfhel library is deemed stable enough to use, or another Python library that implements BGV becomes available.
 One of the authors of this paper has already informed the developers of the Pyfhel library about a bug involving exponentiation of two real numbers.
 
-Efforts are ongoing with regard to the facial recognition tests.
+% Efforts are ongoing with regard to the facial recognition tests.
 Our own implementation of the privacy-preserving eigenfaces by Erkin, et al.
@@
 Another promising image operation to consider is \textit{facial detection} under a homomorphic cryptosystem. 
-Work has been started in order to assess the feasibility of using Haar cascades in a privacy-preserving manner.
+As secure floating-point operations and secure comparisons are feasible, it may be feasible to implement secure Haar cascades.
+% Work has been started in order to assess the feasibility of using Haar cascades in a privacy-preserving manner.
 
-Future work would involve improving and optimizing our implementation of non-linear intensity transformations in terms of number of operations, numerical accuracy and stability, and time efficiency.
+Future studies would involve improving and optimizing our implementation of non-linear intensity transformations in terms of number of operations, numerical accuracy and stability, and time efficiency.
 % Future work would involve improving and optimizing our implementation of the DGK cryptosystem so that it performs faster.
 % A suggestion would be to port the existing implementation to C/C++ and then create a Python library that acts as a wrapper to the C/C++ methods.
-For future studies, an implementation of a client-server framework or system dealing with secure image processing can be considered.
+Furthermore, an implementation of a client-server framework or system dealing with secure image processing can be considered.

### 2019-04-29 parts/08_appendices_b_numericalapproximations_updated.tex
Fixed graphs in appendix
Final revisions and cleanup

@@
-\chapter{LOGARITHM APPROXIMATION}
+\chapter{PRIVACY-PRESERVING LOGARITHM APPROXIMATION}
 \label{chap:logarithm_approximation}
@@
 These algorithms, while efficient, rely on table lookups, which cannot be done in a privacy-preserving system where the function arguments cannot be directly determined.
+We must rely on other methods such as series expansions.
 
-We must therefore rely on other methods, such as using the Taylor series expansions of these functions.
-While also in common use, not all Taylor series expansions have a convenient radius of convergence.
+While in common use, not all series expansions have a convenient radius of convergence.
 To circumvent this, we can rely on an approach presented by Khattri in~\cite{khattri_new_2009} to obtain closed-form approximations to functions by approximating related integrals.
@@
 	% \end{tikzpicture}%
+    \includegraphics[width=12cm]{figures/graph_log_a2.png}
 	\caption{Graph of $\log{\left(1+x\right)}$ and the approximation in Equation~\ref{eq:standard_logarithm_quadrature}}
@@
 \label{sec:logarithm_approximation}
-This appendix a general method to improve the general accuracy of the logarithm approximation given by Khattri in~\cite{khattri_new_2009} for use in privacy-preserving calculation, provided that accuracy is only required for a specific range.
+We now present a method to improve the general accuracy of the logarithm approximation given by Khattri in~\cite{khattri_new_2009} for use in privacy-preserving calculation, provided that accuracy is only required for a specific range.
 
@@
 	% \end{tikzpicture}%
+    \includegraphics[width=12cm]{figures/comp_errs.png}
 	\caption{Comparison of the absolute error between the original approximation in Equation~\ref{eq:standard_logarithm_quadrature} and the scaled approximation in Equation~\ref{eq:optimal_log_approximation}}
@@
 	% \end{tikzpicture}%
+    \includegraphics[width=12cm]{figures/graph_0_255.png}
 	\caption{Graphs of $A\left(x,\alpha\right)$ at $x=0$ and $x=255$}
@@
 	% \end{tikzpicture}%
+    \includegraphics[width=12cm]{figures/graph_approx_16.png}
 	\caption{Graph of $A\left(x,1/16\right)$, the absolute error of the approximation in Equation~\ref{eq:optimal_log_approximation} given a scaling factor of $\alpha=1/16$}
@@
 \section{Approximation for $x^\gamma$}
+\label{sec:power_approximation}
 To approximate $x^\gamma$ for any $\gamma \in \mathbb{R}$, we rewrite $x^\gamma$ as follows:
@@
 \begin{align*}
-  e^x &= \sum_{n=0}^{\infty}{\frac{x^n}{n!}}\\
-  \Rightarrow e^{\gamma\log{x}} &= \sum_{n=0}^{\infty}{\frac{(\gamma\log{x})^n}{n!}}
+  e^x &= \sum_{n=0}^{\infty}{\frac{x^n}{n!}}
+  &e^{\gamma\log{x}} = \sum_{n=0}^{\infty}{\frac{(\gamma\log{x})^n}{n!}}
 \end{align*}

### 2019-04-30 parts/00_abstract.tex
More revisions

--- 2019-04-09 parts/00_abstract.tex
@@
 Regardless, homomorphic cryptography has been targeted for use in secure image processing and facial recognition, due to their ability to maintain data privacy.
-In this paper, we compared the viability of the Paillier, Damg{\aa}rd--Geisler--Kr{\o}igaard (DGK), Dijk--Gentry--Halevi--Vaikuntanathan (DGHV), and Brakerski--Gentry--Vaikuntanathan (BGV) cryptosystems for facial image processing applications, by implementing a software library equipped with these cryptosystems, and comparing their time efficiency and accuracy.
-Furthermore, as an extension to previous research, we attempt to support non-linear image processing operations by deriving and implementing applicable closed-form approximations.
-Preliminary results have shown that the Paillier and DGK cryptosystems are comparable in accuracy and may be used for image negation, but only the Paillier cryptosystem is consistent enough to produce reasonable to accurate results.
+We compared the viability of the Paillier, Damg{\aa}rd--Geisler--Kr{\o}igaard (DGK), Dijk--Gentry--Halevi--Vaikuntanathan (DGHV), and Brakerski--Gentry--Vaikuntanathan (BGV) cryptosystems for facial image processing applications by implementing a software library equipped with these cryptosystems and comparing their time efficiency and accuracy.
+We attempt to support non-linear image processing operations by deriving and implementing applicable closed-form approximations.
+Results have shown that the Paillier and DGK cryptosystems are comparable in accuracy and may be used for image negation, but only the Paillier cryptosystem is consistent enough to produce reasonable to accurate results for logarithm intensity transformation.
+The DGHV and BGV cryptosystems are significantly slower and are not applicable for practical use.
 

### 2019-04-30 parts/01_introduction_01contextofstudy.tex
More revisions

@@
 Digital data privacy and security is a growing concern in various fields, such as cloud computing~\cite{potey_homomorphic_2016}, health information systems~\cite{kester_cryptographic_2015}, and video surveillance~\cite{upmanyu_efficient_2009}.
-Various cryptosystems have been developed, which allow for the secure transmission of data using encryption and decryption schemes~\cite{bauer_cryptosystem_2005}.
+Various cryptosystems have been developed which allow for the secure transmission of data using encryption and decryption schemes~\cite{bauer_cryptosystem_2005}.
 
 One particular application of cryptography is image encryption.
-While cryptosystems used to encrypt general digital data, such as the Advanced Encryption Standard (AES) or elliptic curve cryptography, can also be used to encrypt images~\cite{jain_image_2016, singh_image_2015} other algorithms created specifically for image encryption have also been developed~\cite{murugan_survey_2018}.
+While cryptosystems used to encrypt general digital data, such as the Advanced Encryption Standard (AES) and elliptic curve cryptography, can also be used to encrypt images~\cite{jain_image_2016, singh_image_2015} other algorithms created specifically for image encryption have also been developed~\cite{murugan_survey_2018}.
 
- Using a homomorphic cryptosystem, operations can be performed on encrypted data while keeping both the operands and resulting value secure.
-The result of the operations can be recovered when the data is decrypted.
+ Using a homomorphic cryptosystem, operations can be performed on encrypted data while keeping both the operands and resulting values secure.
+The result of the operations can then be recovered when the data is decrypted.
 In this manner, data is manipulated without compromising data privacy~\cite{fontaine_survey_2007, sen_homomorphic_2013}.

### 2019-04-30 parts/01_introduction_05scopeandlimitations.tex
More revisions

@@
 \begin{enumerate}
-	\item Non-linear intensity adjustment (logarithm, power-log transformations)
+	\item Non-linear intensity adjustment (logarithm, power-log transformations);
 	\item Facial detection and recognition using the eigenface approach \cite{turk_eigenfaces_1991}.
@@
 \end{enumerate}
-A detailed overview of the above will be provided in the methodology. Grayscale images will be used in the study.
-A client-server model for secure computation will be assumed to allow operations such as secure comparison and exponentiation.
-Training and test data are taken from the publicly available \texttt{faces94} dataset (\url{https://cswww.essex.ac.uk/mv/allfaces/faces94.html}) maintained by the University of Essex.
+A detailed overview of the above is provided in the methodology. A client-server model for secure computation will be assumed to allow a larger range of secure operations. 
+Grayscale images are used in the study.
+Training and test data taken from the publicly available \texttt{faces94} dataset (\url{https://cswww.essex.ac.uk/mv/allfaces/faces94.html}) maintained by the University of Essex.

### 2019-04-30 parts/02_relatedliterature.tex
More revisions

@@
 \textit{CryptoImg} provided a suite of linear image processing operations using the Paillier cryptosystem, while Erkin, et al.
-have implemented a privacy-preserving version of the eigenfaces approach to facial recognition developed by Turk and Pentland.
+have implemented a privacy-preserving facial recognition system using eigenfaces.
 
-We have presented as well several areas in which our study will expand on the research so far.
-\begin{enumerate}
-  \item We have shown two fully homomorphic cryptosystems, the DGHV cryptosystem and the BGV cryptosystem.
+We have shown two fully homomorphic cryptosystems, the DGHV cryptosystem and the BGV cryptosystem.
 While these cryptosystems are generally less efficient than partially homomorphic cryptosystems, they do not require additional protocols for division, multiplication, and exponentiation.
-  \item Due to the general limitations of partially homomorphic systems, attempts at applying homomorphic cryptography to applications such as image processing and facial recognition have mainly been restricted to linear operations on ciphertext.
+Due to the general limitations of partially homomorphic systems, attempts at applying homomorphic cryptography to applications such as image processing and facial recognition have mainly been restricted to linear operations on ciphertext.
 We have shown that there are basic image processing operations which are non-linear, which can be approximated.
-  \item While privacy-preserving facial recognition has been accomplished by Erkin, et al., privacy-preserving facial detection has yet to explored.
+
+Lastly, while privacy-preserving facial recognition has been accomplished by Erkin, et al., privacy-preserving facial detection has yet to explored.
 \end{enumerate}

### 2019-04-30 parts/02_relatedliterature_02commonimageprocessingoperations.tex
More revisions

@@
 
-An image negation transformation is defined as:
+An image negation transformation is defined as
 \begin{equation}
-    T\left(r\right) = L-1-r
+    T\left(r\right) = L-r
 \end{equation}
+where $L$ is the maximum pixel intensity value of an image.
 After applying image negation, the resulting image would be similar to a photographic negative~\cite{gonzalez_digital_2008}.
 
-A brightness control transformation with parameter $v$ is defined as:
+A brightness control transformation with parameter $v$ is defined as
 \begin{equation}
-    T\left(r,v\right) = r+v
+    T\left(r,v\right) = r+v.
 \end{equation}

### 2019-04-30 parts/05_conclusions.tex
More revisions

@@
 However both Paillier and DGK fail to produce accurate results in applying the power-law transformation, with the latter failing to produce discernible results.
-Based from these results, the Paillier cryptosystem is consistent enough to produce reasonable to accurate results.
+Based on these results, the Paillier cryptosystem is consistent enough to produce reasonable to accurate results.
 
@@
 % A suggestion would be to port the existing implementation to C/C++ and then create a Python library that acts as a wrapper to the C/C++ methods.
-Furthermore, an implementation of a client-server framework or system dealing with secure image processing can be considered.
+Furthermore, an implementation of a client-server system dealing with secure image processing can be considered.

### 2019-05-01 thesis.tex
Changed the names and did some formatting fixes
fixed title, fixed formula for log operations in methodology
Common image operations
[WIP] algorithms and approximations
adding algorithm descriptions
[WIP] Numerical approximation section
Added work on numerical approximation, fixed appendix templates
Cleaned up some wording on Ch1
Added Benaloh cryptosystem
Added Benaloh cryptosystem to algorithm descriptions
RRL summary and fixes
- Commented out spatial filter section
- Updated summary to reflect new research
- Fixed some typesetting errors in D-P section
Various edits
Applied comments for cha

@@
-\documentclass[oneside,12pt]{discsugthesis}
+\documentclass[oneside,12pt]{discsthesis}
+\usepackage{hyperref}
+\usepackage{graphicx}
+\usepackage{amsthm}
+\usepackage{multirow}
+%\usepackage{fancyvrb}
+% \usepackage{tabularx}
+\usepackage[titletoc]{appendix}
+\usepackage{subcaption}
+%%\usepackage{rotating}
+%%\usepackage{pdfpages}
+%\usepackage{lscape}
+%\usepackage{adjustbox}
+%\usepackage{longtable}
+% \usepackage{booktabs}
+\usepackage{url}
+\usepackage{verbatim}
+\usepackage{xinttools}
+% commands
+\newcommand*\diff{\mathop{}\!\mathrm{d}}
+\newtheorem{theorem}{Theorem}[chapter]
+
+\title{FinalManuscript_DISCS_UG}
+\author{acalab.imagegroup }
+\date{March 1, 2018}
 
 \begin{document}
-\ThesisAuthor{John H. Smith}
-\ThesisTitle{THIS IS A THESIS TITLE}
-\ThesisDegree{Computer Science}
+
+\ThesisAuthor{Aldrich Ellis C. Asuncion \\ Brian Christopher T. Guadalupe}
+\ThesisTitle{IMPLEMENTATION AND ANALYSIS OF HOMOMORPHIC FACIAL IMAGE ENCRYPTION AND MANIPULATION}
+\ThesisArea{Computer Science}
 \ThesisDefenseYear{2019}
-\DefenseDate{}
-\DepartmentHead{The Head}
-\SchoolHead{The Head 2}
-\FirstThesisAdviser{Ayun}
-\FirstPanelMember{}
-\SecondPanelMember{}
-\ThirdPanelMember{}
+\DefenseDate{March 1, 2018}
+
+\DepartmentHead{ANDREI D. CORONEL, Ph.D.}
+\SchoolHead{EVANGELINE P. BAUTISTA, Ph.D.}
+\ThesisAdviser{MARLENE M. DE LEON, Ph.D.}
+\FirstPanelMember{MA. MERCEDES T. RODRIGO, Ph.D.}
+\SecondPanelMember{JOHN PAUL C. VERGARA, Ph.D.}
+\ThirdPanelMember{MA. REGINA JUSTINA E. ESTUAR, Ph.D.}
+
+\ThesisStyle{MS}{Draft}{-10pt}{15pt}
+
+%% Choices for the 1st argument: MS, PhD
+%% Choices for the 2nd argument: Final, FinalWithCorner, Draft
 
 \FrontMatter
-\ThesisTitlePage
-\input{parts/abstract.tex}
+\input{parts/00_abstract}
+\input{parts/00_acknowledgements}
 \tableofcontents
 \listoffigures
+\listoftables
 
-\MainMatter
-\input{parts/chapter1.tex}
+% \MainMatter
+\input{parts/01_introduction_00}
+\input{parts/02_relatedliterature}
+\input{parts/03_methodology}
+\input{parts/04_results}
+%\input{parts/04_results_pub}
+%\input{parts/04_results_unpub}
+\input{parts/05_conclusions}
+%\input{parts/06_recommendations}
 
+% BIBLIOGRAPHY
+%\bibliographystyle{abbrv}
+%\bibliography{sigproc}
+%\input{parts/09_references}
+% \BackMatter
+\bibliographystyle{acm}
 \bibliography{thesis_refs}
-\bibliographystyle{acm}
-\nocite{*}
+
+\addappheadtotoc
+\begin{appendices}
+% \input{parts/08_appendices_a_cryptosystems}
+\input{parts/08_appendices_b_numericalapproximations_updated}
+\chapter{ACCEPTED PAPERS}
+The following pages include related papers accepted in the following conferences.
+\begin{itemize}
+    \item 19th Philippine Computing Science Congress (PCSC 2019)
+    \item 2019 4th International Conference on Multimedia Systems and Signal Processing (ICMSSP 2019)
+\end{itemize}
+\end{appendices}
+
 \end{document}

### 2019-05-02 parts/05_conclusions.tex
Final comments from adviser

@@
 Even though an operation in a partially homomorphic cryptosystem is not theoretically possible, like multiplication of two ciphertexts under Paillier, it has been shown that such operations are indeed possible in a two-party system.
-Protocols for secure multiplication and exponentiation have been proposed and also applied to more complex image operations such as facial recognition.
+Protocols for secure floating-point operations have been proposed and also applied to more complex image operations such as facial recognition.
 Thus, a partially homomorphic cryptosystem can be modified to admit more image processing operations by assuming a two-party system.
 
+We have derived a new closed-form approximation to the logarithm which is more accurate than previous closed-form approximations, while requiring similar computational effort.
+We have applied this closed-form approximation to achieve non-linear image transformations under homomorphic cryptosystems.
 Preliminary results have shown that both Paillier and DGK apply image negation accurately and efficiently, as evidenced by the perfect zero MSE and infinite PSNR.
@@
 However both Paillier and DGK fail to produce accurate results in applying the power-law transformation, with the latter failing to produce discernible results.
-Based on these results, the Paillier cryptosystem is consistent enough to produce reasonable to accurate results.
+Based on these results, the Paillier cryptosystem is consistent enough to produce reasonable to accurate results for image negation and logarithm transformation.
 
@@
 This allowed us to express various image operations with a unified syntax, thus facilitating easier testing.
+
+In summary, we make the following conclusions regarding our research questions.
+\begin{itemize}
+    \item While fully homomorphic cryptosystems such as DGHV and BGV allow for arbitrary secure computation, it is possible to extend a partially homomorphic cryptosystem, such as Paillier and DGK, to allow efficient secure floating-point operations.
+Secure calculation of non-linear functions, such as the natural logarithm, can be implemented with closed-form approximations.
+    \item Out of the cryptosystems tested, the Paillier cryptosystem is the most viable homomorphic cryptosystem for use in secure image processing, as it is the most time-efficient, most accurate and best preserves image quality.
+However, it is not perfect, as there is an observed inaccuracy with respect to the intented output of the logarithm transformation.
+\end{itemize}
 

### 2019-05-02 thesis.tex
Final comments from adviser

@@
 \chapter{ACCEPTED PAPERS}
-The following pages include related papers accepted in the following conferences.
+The following pages include papers accepted in national and international conferences as a part of this thesis.
 \begin{itemize}
-    \item 19th Philippine Computing Science Congress (PCSC 2019)
-    \item 2019 4th International Conference on Multimedia Systems and Signal Processing (ICMSSP 2019)
+    \item ``Privacy-Preserving Approximation of Transcendental Functions'', accepted in the \textit{19th Philippine Computing Science Congress} (PCSC 2019).
+    \item ``Implementation and Analysis of Homomorphic Facial
+    Image Encryption and Manipulation'', accepted in the \textit{2019 4th International Conference on Multimedia Systems and Signal Processing} (ICMSSP 2019).
 \end{itemize}
